### 2019-02-18 latex/egpaper_for_review.tex
Add introduction and related work

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{iccv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \iccvfinalcopy % *** Uncomment this line for the final submission

\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{mathrsfs}
\newcommand{\RED}[1]{#1}

\newcommand\TODO[1]{{\color{red}{TODO: #1}}}
\newcommand\UPDATE[1]{{\color{blue}{#1}}}
\newcommand\SOURCE[1]{{\color{green}{(from: #1)}}}
% \newcommand\CHANGED[2]{{{\color{blue}{#1}}\color{green}{#2}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ificcvfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Author Guidelines for ICCV Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous ICCV abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

\begin{itemize}
\item \textbf{Intro about CNN:} \textit{The successes of deep convolutional neural nets (CNNs) at image classiﬁcation has spawned a ﬂurry of work in computer vision on adapting these models to pixel-level image understanding tasks, such as boundary detection [1, 90, 64], semantic segmentation [60, 10, 46], optical ﬂow [87, 20], and pose estimation [85, 7].} \SOURCE{Rec. embeddings}
\item Intro about instance segmentation
\item \textbf{Mask R-CNN:} why we do not like it 
\begin{itemize}
\item \textit{most recent successful approaches to instance segmentation have adopted more heuristic approaches that first use an object detector to enumerate candidate instances and then perform pixel-level segmentation of each instance [57, 17, 55, 56, 2]. Alternately one can generate generic proposal segments and then label each one with a semantic detector [31, 12, 32, 16, 82, 34]. In either case the detection and segmentation steps can both be mapped to standard binary classiﬁcation losses. While effective, these approaches are somewhat unsatisfying since: (1) they rely on the object detector and non-maximum suppression heuristics to accurately “count” the number of instances, (2) they are difﬁcult to train in an end-to-end manner since the interface between instance segmentation and detection is non-differentiable, and (3) they underperform in cluttered scenes as the assignment of pixels to detections is carried out independently for each detection 1.} \SOURCE{Rec. embeddings}
\item elongated segments
\item \textit{There are three fundamental flaws in a proposal-based instance segmentation architecture. First, two objects may share the same bounding box, or a very similar boxes. In this case, the mask head, has no way of telling which object to pick in the box. This is a serious problem with stringy like object that have low fill rate in their bounding box (e.g. bicycles and chairs). Second, there is nothing in the architecture preventing a pixel to be shared between two instance. Third, the number of instances is limited by the number of proposals processed by the network (usually hundreds). More over, the architecture is complex and hard to tune and “debug”. In object detection, a precursor to this problem, there are already successes being made to use a simpler, single-stage, architectures e.g. RetinaNet.}
\end{itemize}
\item More intro about proposal-free instance segmentation? Perhaps not needed

\item One common method: \textbf{predict pixel embedding vectors.} For each pixel in the image, a CNN predicts an embedding vector, such that pixels in the same instance are represented by the same vector. (\textit{by training a model that labels pixels with unit-length vectors that live in some ﬁxed dimension embedding space} \SOURCE{Rec. embeddings} ). \textit{With instance embedding, each object is assigned a “color” in a n-dimensional space. The network processes the image and produces a dense output, same size as the input image. Each pixel in the output of the network is a point in the embedding space. Pixels that belong to the same object are close in the embedding space while pixels that belong to different objects are distant in the embedding space. Parsing the image embedding space involves some sort of clustering algorithm.} \SOURCE{online} 
\item use clustering algorithms like DBSCAN, mean-shift or similar ones working directly in the embedding space. \UPDATE{More clustering options..?}
\item Other methods directly \textbf{Predict short and long-range affinities}: for each pixel we fix a set of neighboring pixels (not necessarily limited to the direct neighbors);  a CNN predicts then affinities, that represent how likely it is for each pair of neighboring pixels to be in the same instance.
\item Even with pixel embedding vectors we can deduce affinities or signed costs
\item It was shown that it is good to describe the problem in terms of a signed graph, or better: pixel-grid graph with short- and long-range connections; segmentation given by (signed) graph partitioning algorithm  
\item makes sense to use repulsion/attraction; directly predicted by CNN; no need to fix threshold/number of seeds/etc...
\item \textit{Multicut has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region. Its great drawback is that its optimization is NP-hard.} \SOURCE{MWS}. (too big even for multicut approximations)
\item Efficient alternatives proposed independently: local-search approximations, MWS, graph-merge with average \TODO{Expand this part (add more items to the list) and highlight the fact that so far a clear comparison was missing and everyone was using something kind of random}
\item To summarize our contributions:
\begin{itemize}
\item we propose a unified and simple formalization of Signed Graph Edge Contraction Clustering and show how many of the recently proposed methods can be seen as special cases
\item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and energy) 
\item we propose a new a constrained version of average agglomerative clustering that proved to be quite robust in most of our experiments
\end{itemize}
\end{itemize}

\section{Related work}
\begin{itemize}
\item \textbf{Pixel embedding vectors:} unsupervised or supervised; different types of loss \TODO{Find good summary}
\item clustering algorithms like DBSCAN, mean-shift orsimilar ones working directly in the embedding space  \TODO{Add refs, discuss with Roman}
\item \textbf{Predicting affinities (and long-range):} superhuman, MWS, graph-merge on cityscapes, holistically edge detection (see MWS paper for a good review) \TODO{Add more}
\item \textbf{Pipelines in connectomics (or better: merge trees):} \textit{Similar to the boundary detection/region segmentation pipeline for natural image segmentation [6,7,8,9], most recent EM image segmentation methods use a membrane detection/cell segmentation pipeline. First, a membrane detector generates pixel-wise conﬁdence maps of membrane predictions using local image cues [10,11,12]. Next, region-based methods are applied to transforming the membrane conﬁdence maps into cell segments. It has been shown that region-based methods are necessary for improving the segmentation accuracy from membrane detections for EM images [13]. A common approach to region-based segmentation is to transform a membrane conﬁdence map into over-segmenting superpixels and use them as “building blocks” for ﬁnal segmentation. To correctly combine superpixels, greedy region agglomeration based on certain boundary saliency has been shown to work [14]. Meanwhile, structures, such as loopy graphs [15,16] or trees [17,18,19], are more often imposed to represent the region merging hierarchy and help transform the superpixel combination search into graph labeling problems. To this end, local [17,16] or structured [18,19] learning based methods are developed.} \SOURCE{SSHMT}
\item \textbf{Cannot-link constraints:} initially introduced as hard-contraints, then relaxed (MWS, Greedy Fixation)
\item \textbf{Unsigned clustering methods:} Felzenszwalb Efficient Graph-based Image segmentation
\end{itemize}

\section{Grand Unified Edge Contraction Algorithm}
\begin{itemize}
\item Rows in the table:
\begin{itemize}
\item Mutex Watershed (MWS), [proof of equivalence included in Appendix]
\item Greedy Additive Edge Contraction (GAEC), 
\item Greedy Fixation (GF), 
\item Hierarchical Agglomerative Clustering with single, complete, average (UPGMA) and weighted average (WPGMA) linkage criteria
\item GALA (learned update rule)
\item (Felzenszwalb Efficient Graph-based Image segmentation: can be included, but probably better to just mention it in the related work)
\end{itemize}
\end{itemize}

\section{Experiments}
\begin{itemize}
\item Nevertheless, in both approaches we can define a grid graph (each vertex representing a pixel) with signed weights and find the final instance segmentation by using a graph partitioning algorithm:
\begin{itemize}
\item In Method 1, the graph is complete and the edge weights represent similarities between pairs of pixel embedding vectors. In most proposed approaches, embedding vectors representing distinct instances should be "distant enough" in the embedding space (a minimum distance is usually used during the training of the CNN). Thus, this threshold distance can be used to define signed affinities, representing attraction or repulsion between pairs of pixels;
\item  In Method 2, the short- and long-range affinities predicted by the CNN are directly used as signed edge weights in the grid graph
\end{itemize}
\end{itemize}

\subsection{Results summary}
\begin{itemize}
\item in the proposed simple formalism for Signed Graph Edge Contraction Clustering, we also include a modified version of Hierarchical agglomerative clustering with cannot-link constraints that was not mentioned in literature so far and in our experiments proved to be quite robust to noise and outliers
\item we compare different types of Signed Graph Edge Contraction Clustering, showing in which situations is preferable to use one or the other and which one can make a better use of the long-range CNN predictions; 
\item we focus our comparison on efficiency and robustness to mistakes in the CNN predictions 
\item in general, our experiments show that long-range predictions should be used not only during the CNN training, but also as an input of the clustering algorithm

\end{itemize}

%-------------------------------------------------------------------------
\section{ICCV stuff}
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

Please refer to the author guidelines on the ICCV 2019 web page for a
discussion of the policy on dual submissions.

\subsection{Paper length}
Papers, excluding the references section,
must be no longer than eight pages in length. The references section
will not be included in the page count, and there is no limit on the
length of the references section. For example, a paper of eight pages
with two pages of references would have a total length of 10 pages.

Overlength papers will simply not be reviewed.  This includes papers
where the margins and formatting are deemed to have been significantly
altered from those laid down by this style guide.  Note that this
\LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for
supervised revisions of manuscripts.  The reviewing process cannot determine
the suitability of the paper for presentation in eight pages if it is
reviewed in eleven.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the \verb'\iccvfinalcopy' command in the document preamble.)  Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g.\ this line is $095.5$), although in most cases one would
expect that the approximate location will be adequate.

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove
citations to one's own work---in fact it is often impossible to
review a paper unless the previous citations are known and
available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say
that you are Lucy Smith; it says that you are building on her
work.  If you are Smith and Jones, do not say ``as we show in
[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our
   previous paper [1], and show it to be inferior to all
   previously known methods.  Why the previous paper was
   accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the
   paper of Smith \etal [1], and show it to be inferior to
   all previously known methods.  Why the previous paper
   was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo
   filter, a fundamental contribution to human knowledge''.
   Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to that
submission in order to explain the differences, just as you would if you
had previously published related work.  In such cases, include the
anonymized parallel submission~\cite{Authors14} as additional material and
cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be
found elsewhere, and refer them to a technical report.  For conference
submissions, the paper must stand on its own, and not {\em require} the
reviewer to go to a techreport for further details.  Thus, you may say in
the body of the paper ``further details may be found
in~\cite{Authors14b}''.  Then submit the techreport as additional material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the ICCV70 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how to
improve our previous work [Anonymous, 1968].  This time we tested the
algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors. Instead
write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.  This
   system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] didn't
   handle case B properly.  Ours handles it by including
   a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo
   lunar lander, and went all the way to the moon, don't
   you know.  It displayed the following behaviours
   which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you as
the authors.  A reviewer might think it likely that the new paper was
written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been
contracted to solve problem B.

\noindent
FAQ\medskip\\
{\bf Q:} Are acknowledgements OK?\\
{\bf A:} No.  Leave them for the final copy.\medskip\\
{\bf Q:} How do I cite my results reported in open challenges?
{\bf A:} To conform with the double blind review policy, you can report results of other challenge participants together with your results in your paper. For your results, however, you should not identify yourself and should not mention your participation in the challenge. Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a
sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
\verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'',
shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
However, use it only when there are three or more authors.  Thus, the
following is correct: ``
   Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
because reference~\cite{Alpher03} has just two authors.  If you use the
\verb'\etal' macro provided, then you need not worry about double periods
when used at the end of a sentence as in Alpher \etal.

For this citation style, keep multiple citations in numerical (not
chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
\cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}

All text must be in a two-column format. The total allowable width of the
text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
first page) should begin 1.0 inch (2.54 cm) from the top edge of the
page. The second and following pages should begin 1.0 inch (2.54 cm) from
the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is
available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
the first page. The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
adverbs; do not capitalize articles, coordinate conjunctions, or
prepositions (unless the title begins with such a word). Leave two blank
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is to
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a third-order
heading (we discourage it), use 10-point Times, boldface, initially
capitalized, flush left, preceded by one blank line, followed by a period
and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors14}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the ICCV 2019 web page for a discussion
of the use of color in your document.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2019-02-18 latex/egpaper_for_review.tex
Finalize next TODOs;  hide useless sections

@@
 Meanwhile, structures, such as loopy graphs [15,16] or trees [17,18,19], are more often imposed to represent the region merging hierarchy and help transform the superpixel combination search into graph labeling problems.
-To this end, local [17,16] or structured [18,19] learning based methods are developed.} \SOURCE{SSHMT}
+To this end, local [17,16] or structured [18,19] learning based methods are developed.} \SOURCE{SSHMT} \TODO{This clearly need to be extended and reformulated}
 \item \textbf{Cannot-link constraints:} initially introduced as hard-contraints, then relaxed (MWS, Greedy Fixation)
-\item \textbf{Unsigned clustering methods:} Felzenszwalb Efficient Graph-based Image segmentation
+\item \textbf{Unsigned clustering methods:} Felzenszwalb Efficient Graph-based Image segmentation, \TODO{Hierarchical clustering \& Co.}
 \end{itemize}
@@
 \item GALA (learned update rule)
-\item (Felzenszwalb Efficient Graph-based Image segmentation: can be included, but probably better to just mention it in the related work)
+\item Something depending on the node size...?
 \end{itemize}
@@
 
-%-------------------------------------------------------------------------
-\section{ICCV stuff}
-\subsection{Language}
-
-All manuscripts must be in English.
-
-\subsection{Dual submission}
-
-Please refer to the author guidelines on the ICCV 2019 web page for a
-discussion of the policy on dual submissions.
-
-\subsection{Paper length}
-Papers, excluding the references section,
-must be no longer than eight pages in length. The references section
-will not be included in the page count, and there is no limit on the
-length of the references section. For example, a paper of eight pages
-with two pages of references would have a total length of 10 pages.
-
-Overlength papers will simply not be reviewed.  This includes papers
-where the margins and formatting are deemed to have been significantly
-altered from those laid down by this style guide.  Note that this
-\LaTeX\ guide already sets figure captions and references in a smaller font.
-The reason such papers will not be reviewed is that there is no provision for
-supervised revisions of manuscripts.  The reviewing process cannot determine
-the suitability of the paper for presentation in eight pages if it is
-reviewed in eleven.
-
-%-------------------------------------------------------------------------
-\subsection{The ruler}
-The \LaTeX\ style defines a printed ruler which should be present in the
-version submitted for review.  The ruler is provided in order that
-reviewers may comment on particular lines in the paper without
-circumlocution.  If you are preparing a document using a non-\LaTeX\
-document preparation system, please arrange for an equivalent ruler to
-appear on the final output pages.  The presence or absence of the ruler
-should not change the appearance of any other content on the page.  The
-camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
-the \verb'\iccvfinalcopy' command in the document preamble.)  Reviewers:
-note that the ruler measurements do not align well with lines in the paper
---- this turns out to be very difficult to do well when the paper contains
-many figures and equations, and, when done, looks ugly.  Just use fractional
-references (e.g.\ this line is $095.5$), although in most cases one would
-expect that the approximate location will be adequate.
-
-\subsection{Mathematics}
-
-Please number all of your sections and displayed equations.  It is
-important for readers to be able to refer to any particular equation.  Just
-because you didn't refer to it in the text doesn't mean some future reader
-might not need to refer to it.  It is cumbersome to have to use
-circumlocutions like ``the equation second from the top of page 3 column
-1''.  (Note that the ruler will not be present in the final copy, so is not
-an alternative to equation numbers).  All authors will benefit from reading
-Mermin's description of how to write mathematics:
-\url{http://www.pamitc.org/documents/mermin.pdf}.
-
-\subsection{Blind review}
-
-Many authors misunderstand the concept of anonymizing for blind
-review.  Blind review does not mean that one must remove
-citations to one's own work---in fact it is often impossible to
-review a paper unless the previous citations are known and
-available.
-
-Blind review means that you do not use the words ``my'' or ``our''
-when citing previous work.  That is all.  (But see below for
-techreports.)
-
-Saying ``this builds on the work of Lucy Smith [1]'' does not say
-that you are Lucy Smith; it says that you are building on her
-work.  If you are Smith and Jones, do not say ``as we show in
-[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
-paper, include reference 7 as you would any other cited work.
-
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-\begin{center}
-    An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of our
-   previous paper [1], and show it to be inferior to all
-   previously known methods.  Why the previous paper was
-   accepted without this analysis is beyond me.
-
-   [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-
-\begin{quote}
-\begin{center}
-     An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of the
-   paper of Smith \etal [1], and show it to be inferior to
-   all previously known methods.  Why the previous paper
-   was accepted without this analysis is beyond me.
-
-   [1] Smith, L and Jones, C. ``The frobnicatable foo
-   filter, a fundamental contribution to human knowledge''.
-   Nature 381(12), 1-213.
-\end{quote}
-
-If you are making a submission to another conference at the same time,
-which covers similar or overlapping material, you may need to refer to that
-submission in order to explain the differences, just as you would if you
-had previously published related work.  In such cases, include the
-anonymized parallel submission~\cite{Authors14} as additional material and
-cite it as
-\begin{quote}
-[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
-Supplied as additional material {\tt fg324.pdf}.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details can be
-found elsewhere, and refer them to a technical report.  For conference
-submissions, the paper must stand on its own, and not {\em require} the
-reviewer to go to a techreport for further details.  Thus, you may say in
-the body of the paper ``further details may be found
-in~\cite{Authors14b}''.  Then submit the techreport as additional material.
-Again, you may not assume the reviewers will read this material.
-
-Sometimes your paper is about a problem which you tested using a tool which
-is widely known to be restricted to a single institution.  For example,
-let's say it's 1969, you have solved a key problem on the Apollo lander,
-and you believe that the ICCV70 audience would like to hear about your
-solution.  The work is a development of your celebrated 1968 paper entitled
-``Zero-g frobnication: How being the only people in the world with access to
-the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-
-You can handle this paper like any other.  Don't write ``We show how to
-improve our previous work [Anonymous, 1968].  This time we tested the
-algorithm on a lunar lander [name of lander removed for blind review]''.
-That would be silly, and would immediately identify the authors. Instead
-write the following:
-\begin{quotation}
-\noindent
-   We describe a system for zero-g frobnication.  This
-   system is new because it handles the following cases:
-   A, B.  Previous systems [Zeus et al. 1968] didn't
-   handle case B properly.  Ours handles it by including
-   a foo term in the bar integral.
-
-   ...
-
-   The proposed system was integrated with the Apollo
-   lunar lander, and went all the way to the moon, don't
-   you know.  It displayed the following behaviours
-   which show how well we solved cases A and B: ...
-\end{quotation}
-As you can see, the above text follows standard scientific convention,
-reads better than the first version, and does not explicitly name you as
-the authors.  A reviewer might think it likely that the new paper was
-written by Zeus \etal, but cannot make any decision based on that guess.
-He or she would have to be sure that no other authors could have been
-contracted to solve problem B.
-
-\noindent
-FAQ\medskip\\
-{\bf Q:} Are acknowledgements OK?\\
-{\bf A:} No.  Leave them for the final copy.\medskip\\
-{\bf Q:} How do I cite my results reported in open challenges?
-{\bf A:} To conform with the double blind review policy, you can report results of other challenge participants together with your results in your paper.
-For your results, however, you should not identify yourself and should not mention your participation in the challenge.
-Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
-
-\begin{figure}[t]
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-\end{center}
-   \caption{Example of caption.  It is set in Roman so that mathematics
-   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-   ugly clash.}
-\label{fig:long}
-\label{fig:onecol}
-\end{figure}
-
-\subsection{Miscellaneous}
-
-\noindent
-Compare the following:\\
-\begin{tabular}{ll}
- \verb'$conf_a$' &  $conf_a$ \\
- \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-\end{tabular}\\
-See The \TeX book, p165.
-
-The space after \eg, meaning ``for example'', should not be a
-sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
-\verb'\eg' macro takes care of this.
-
-When citing a multi-author paper, you may save space by using ``et alia'',
-shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
-However, use it only when there are three or more authors.  Thus, the
-following is correct: ``
-   Frobnication has been trendy lately.
-   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-
-This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
-because reference~\cite{Alpher03} has just two authors.  If you use the
-\verb'\etal' macro provided, then you need not worry about double periods
-when used at the end of a sentence as in Alpher \etal.
-
-For this citation style, keep multiple citations in numerical (not
-chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-\cite{Alpher02,Alpher03,Authors14}.
-
-\begin{figure*}
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-\end{center}
-   \caption{Example of a short caption, which should be centered.}
-\label{fig:short}
-\end{figure*}
-
-%------------------------------------------------------------------------
-\section{Formatting your paper}
-
-All text must be in a two-column format. The total allowable width of the
-text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
-cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
-$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
-first page) should begin 1.0 inch (2.54 cm) from the top edge of the
-page. The second and following pages should begin 1.0 inch (2.54 cm) from
-the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
-cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
-paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
-page.
-
-%-------------------------------------------------------------------------
-\subsection{Margins and page numbering}
-
-All printed material, including text, illustrations, and charts, must be kept
-within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
-high.
-
-%-------------------------------------------------------------------------
-\subsection{Type-style and fonts}
-
-Wherever Times is specified, Times Roman may also be used. If neither is
-available on your word processor, please use the font closest in
-appearance to Times to which you have access.
-
-MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
-the first page. The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
-adverbs; do not capitalize articles, coordinate conjunctions, or
-prepositions (unless the title begins with such a word). Leave two blank
-lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type. This information is to
-be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
-double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
-inch or 0.422 cm). Make sure your text is fully justified---that is,
-flush left and flush right. Please do not place any additional blank
-lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in
-Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-,
-second-, and third-order headings.
-
-FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
-should be Times 12-point boldface, initially capitalized, flush left,
-with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
-should be Times 11-point boldface, initially capitalized, flush left,
-with one blank line before, and one after. If you require a third-order
-heading (we discourage it), use 10-point Times, boldface, initially
-capitalized, flush left, preceded by one blank line, followed by a period
-and your text on the same line.
-
-%-------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote {This is what a footnote looks like.  It
-often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral
-observations in
-the text (within parentheses, if you prefer, as in this sentence).  If you
-wish to use a footnote, place it at the bottom of the column on the page on
-which it is referenced. Use Times 8-point type, single-spaced.
-
-%-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times,
-single-spaced, at the end of your paper. When referenced in the text,
-enclose the citation number in square brackets, for
-example~\cite{Authors14}.  Where appropriate, include the name(s) of
-editors of referenced books.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|c|}
-\hline
-Method & Frobnability \\
-\hline\hline
-Theirs & Frumpy \\
-Yours & Frobbly \\
-Ours & Makes one's heart Frob\\
-\hline
-\end{tabular}
-\end{center}
-\caption{Results.   Ours is better.}
-\end{table}
-
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.  Please ensure that any point you wish to
-make is resolvable in a printed copy of the paper.  Resize fonts in figures
-to match the font in the body text, and choose line widths which render
-effectively in print.  Many readers (and reviewers), even of an electronic
-copy, will choose to print your paper in order to read it.  You cannot
-insist that they do otherwise, and therefore must not assume that they can
-zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use
-\verb+\includegraphics+, and to specify the  figure width as a multiple of
-the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage[dvips]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.eps}
-\end{verbatim}
-}
-
-%-------------------------------------------------------------------------
-\subsection{Color}
-
-Please refer to the author guidelines on the ICCV 2019 web page for a discussion
-of the use of color in your document.
-
-%------------------------------------------------------------------------
-\section{Final copy}
-
-You must include your signed IEEE copyright release form when you submit
-your finished paper. We MUST have this form before your paper can be
-published in the proceedings.
-
 {\small
@@
 
+\section{Supplementary Material}
+\begin{itemize}
+\item Equivalence Mutex Watershed and Greedy Edge Contraction
+\end{itemize}
+
+%-------------------------------------------------------------------------
+
+% \section{ICCV stuff}
+% \subsection{Language}
+
+% All manuscripts must be in English.
+
+% \subsection{Dual submission}
+
+% Please refer to the author guidelines on the ICCV 2019 web page for a
+% discussion of the policy on dual submissions.
+
+% \subsection{Paper length}
+% Papers, excluding the references section,
+% must be no longer than eight pages in length. The references section
+% will not be included in the page count, and there is no limit on the
+% length of the references section. For example, a paper of eight pages
+% with two pages of references would have a total length of 10 pages.
+
+% Overlength papers will simply not be reviewed.  This includes papers
+% where the margins and formatting are deemed to have been significantly
+% altered from those laid down by this style guide.  Note that this
+% \LaTeX\ guide already sets figure captions and references in a smaller font.
+% The reason such papers will not be reviewed is that there is no provision for
+% supervised revisions of manuscripts.  The reviewing process cannot determine
+% the suitability of the paper for presentation in eight pages if it is
+% reviewed in eleven.
+
+% %-------------------------------------------------------------------------
+% \subsection{The ruler}
+% The \LaTeX\ style defines a printed ruler which should be present in the
+% version submitted for review.  The ruler is provided in order that
+% reviewers may comment on particular lines in the paper without
+% circumlocution.  If you are preparing a document using a non-\LaTeX\
+% document preparation system, please arrange for an equivalent ruler to
+% appear on the final output pages.  The presence or absence of the ruler
+% should not change the appearance of any other content on the page.  The
+% camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
+% the \verb'\iccvfinalcopy' command in the document preamble.)  Reviewers:
+% note that the ruler measurements do not align well with lines in the paper
+% --- this turns out to be very difficult to do well when the paper contains
+% many figures and equations, and, when done, looks ugly.  Just use fractional
+% references (e.g.\ this line is $095.5$), although in most cases one would
+% expect that the approximate location will be adequate.
+
+% \subsection{Mathematics}
+
+% Please number all of your sections and displayed equations.  It is
+% important for readers to be able to refer to any particular equation.  Just
+% because you didn't refer to it in the text doesn't mean some future reader
+% might not need to refer to it.  It is cumbersome to have to use
+% circumlocutions like ``the equation second from the top of page 3 column
+% 1''.  (Note that the ruler will not be present in the final copy, so is not
+% an alternative to equation numbers).  All authors will benefit from reading
+% Mermin's description of how to write mathematics:
+% \url{http://www.pamitc.org/documents/mermin.pdf}.
+
+% \subsection{Blind review}
+
+% Many authors misunderstand the concept of anonymizing for blind
+% review.  Blind review does not mean that one must remove
+% citations to one's own work---in fact it is often impossible to
+% review a paper unless the previous citations are known and
+% available.
+
+% Blind review means that you do not use the words ``my'' or ``our''
+% when citing previous work.  That is all.  (But see below for
+% techreports.)
+
+% Saying ``this builds on the work of Lucy Smith [1]'' does not say
+% that you are Lucy Smith; it says that you are building on her
+% work.  If you are Smith and Jones, do not say ``as we show in
+% [7]'', say ``as Smith and Jones show in [7]'' and at the end of the
+% paper, include reference 7 as you would any other cited work.
+
+% An example of a bad paper just asking to be rejected:
+% \begin{quote}
+% \begin{center}
+%     An analysis of the frobnicatable foo filter.
+% \end{center}
+
+%   In this paper we present a performance analysis of our
+%   previous paper [1], and show it to be inferior to all
+%   previously known methods.  Why the previous paper was
+%   accepted without this analysis is beyond me.
+
+%   [1] Removed for blind review
+% \end{quote}
+
+% An example of an acceptable paper:
+
+% \begin{quote}
+% \begin{center}
+%      An analysis of the frobnicatable foo filter.
+% \end{center}
+
+%   In this paper we present a performance analysis of the
+%   paper of Smith \etal [1], and show it to be inferior to
+%   all previously known methods.  Why the previous paper
+%   was accepted without this analysis is beyond me.
+
+%   [1] Smith, L and Jones, C. ``The frobnicatable foo
+%   filter, a fundamental contribution to human knowledge''.
+%   Nature 381(12), 1-213.
+% \end{quote}
+
+% If you are making a submission to another conference at the same time,
+% which covers similar or overlapping material, you may need to refer to that
+% submission in order to explain the differences, just as you would if you
+% had previously published related work.  In such cases, include the
+% anonymized parallel submission~\cite{Authors14} as additional material and
+% cite it as
+% \begin{quote}
+% [1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
+% Supplied as additional material {\tt fg324.pdf}.
+% \end{quote}
+
+% Finally, you may feel you need to tell the reader that more details can be
+% found elsewhere, and refer them to a technical report.  For conference
+% submissions, the paper must stand on its own, and not {\em require} the
+% reviewer to go to a techreport for further details.  Thus, you may say in
+% the body of the paper ``further details may be found
+% in~\cite{Authors14b}''.  Then submit the techreport as additional material.
+% Again, you may not assume the reviewers will read this material.
+
+% Sometimes your paper is about a problem which you tested using a tool which
+% is widely known to be restricted to a single institution.  For example,
+% let's say it's 1969, you have solved a key problem on the Apollo lander,
+% and you believe that the ICCV70 audience would like to hear about your
+% solution.  The work is a development of your celebrated 1968 paper entitled
+% ``Zero-g frobnication: How being the only people in the world with access to
+% the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
+
+% You can handle this paper like any other.  Don't write ``We show how to
+% improve our previous work [Anonymous, 1968].  This time we tested the
+% algorithm on a lunar lander [name of lander removed for blind review]''.
+% That would be silly, and would immediately identify the authors. Instead
+% write the following:
+% \begin{quotation}
+% \noindent
+%   We describe a system for zero-g frobnication.  This
+%   system is new because it handles the following cases:
+%   A, B.  Previous systems [Zeus et al. 1968] didn't
+%   handle case B properly.  Ours handles it by including
+%   a foo term in the bar integral.
+
+%   ...
+
+%   The proposed system was integrated with the Apollo
+%   lunar lander, and went all the way to the moon, don't
+%   you know.  It displayed the following behaviours
+%   which show how well we solved cases A and B: ...
+% \end{quotation}
+% As you can see, the above text follows standard scientific convention,
+% reads better than the first version, and does not explicitly name you as
+% the authors.  A reviewer might think it likely that the new paper was
+% written by Zeus \etal, but cannot make any decision based on that guess.
+% He or she would have to be sure that no other authors could have been
+% contracted to solve problem B.
+
+% \noindent
+% FAQ\medskip\\
+% {\bf Q:} Are acknowledgements OK?\\
+% {\bf A:} No.  Leave them for the final copy.\medskip\\
+% {\bf Q:} How do I cite my results reported in open challenges?
+% {\bf A:} To conform with the double blind review policy, you can report results of other challenge participants together with your results in your paper.
+For your results, however, you should not identify yourself and should not mention your participation in the challenge.
+Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
+
+% \begin{figure}[t]
+% \begin{center}
+% \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+%   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
+% \end{center}
+%   \caption{Example of caption.  It is set in Roman so that mathematics
+%   (always set in Roman: $B \sin A = A \sin B$) may be included without an
+%   ugly clash.}
+% \label{fig:long}
+% \label{fig:onecol}
+% \end{figure}
+
+% \subsection{Miscellaneous}
+
+% \noindent
+% Compare the following:\\
+% \begin{tabular}{ll}
+%  \verb'$conf_a$' &  $conf_a$ \\
+%  \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
+% \end{tabular}\\
+% See The \TeX book, p165.
+
+% The space after \eg, meaning ``for example'', should not be a
+% sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
+% \verb'\eg' macro takes care of this.
+
+% When citing a multi-author paper, you may save space by using ``et alia'',
+% shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
+% However, use it only when there are three or more authors.  Thus, the
+% following is correct: ``
+%   Frobnication has been trendy lately.
+%   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
+%   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
+
+% This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
+% because reference~\cite{Alpher03} has just two authors.  If you use the
+% \verb'\etal' macro provided, then you need not worry about double periods
+% when used at the end of a sentence as in Alpher \etal.
+
+% For this citation style, keep multiple citations in numerical (not
+% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
+% \cite{Alpher02,Alpher03,Authors14}.
+
+% \begin{figure*}
+% \begin{center}
+% \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+% \end{center}
+%   \caption{Example of a short caption, which should be centered.}
+% \label{fig:short}
+% \end{figure*}
+
+% %------------------------------------------------------------------------
+% \section{Formatting your paper}
+
+% All text must be in a two-column format. The total allowable width of the
+% text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
+% cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
+% $\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
+% first page) should begin 1.0 inch (2.54 cm) from the top edge of the
+% page. The second and following pages should begin 1.0 inch (2.54 cm) from
+% the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
+% cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
+% paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
+% page.
+
+% %-------------------------------------------------------------------------
+% \subsection{Margins and page numbering}
+
+% All printed material, including text, illustrations, and charts, must be kept
+% within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
+% high.
+
+% %-------------------------------------------------------------------------
+% \subsection{Type-style and fonts}
+
+% Wherever Times is specified, Times Roman may also be used. If neither is
+% available on your word processor, please use the font closest in
+% appearance to Times to which you have access.
+
+% MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
+% the first page. The title should be in Times 14-point, boldface type.
+% Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
+% adverbs; do not capitalize articles, coordinate conjunctions, or
+% prepositions (unless the title begins with such a word). Leave two blank
+% lines after the title.
+
+% AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
+% and printed in Times 12-point, non-boldface type. This information is to
+% be followed by two blank lines.
+
+% The ABSTRACT and MAIN TEXT are to be in a two-column format.
+
+% MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
+% double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
+% inch or 0.422 cm). Make sure your text is fully justified---that is,
+% flush left and flush right. Please do not place any additional blank
+% lines between paragraphs.
+
+% Figure and table captions should be 9-point Roman type as in
+% Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.
+
+% \noindent Callouts should be 9-point Helvetica, non-boldface type.
+% Initially capitalize only the first word of section titles and first-,
+% second-, and third-order headings.
+
+% FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
+% should be Times 12-point boldface, initially capitalized, flush left,
+% with one blank line before, and one blank line after.
+
+% SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
+% should be Times 11-point boldface, initially capitalized, flush left,
+% with one blank line before, and one after. If you require a third-order
+% heading (we discourage it), use 10-point Times, boldface, initially
+% capitalized, flush left, preceded by one blank line, followed by a period
+% and your text on the same line.
+
+% %-------------------------------------------------------------------------
+% \subsection{Footnotes}
+
+% Please use footnotes\footnote {This is what a footnote looks like.  It
+% often distracts the reader from the main flow of the argument.} sparingly.
+% Indeed, try to avoid footnotes altogether and include necessary peripheral
+% observations in
+% the text (within parentheses, if you prefer, as in this sentence).  If you
+% wish to use a footnote, place it at the bottom of the column on the page on
+% which it is referenced. Use Times 8-point type, single-spaced.
+
+% %-------------------------------------------------------------------------
+% \subsection{References}
+
+% List and number all bibliographical references in 9-point Times,
+% single-spaced, at the end of your paper. When referenced in the text,
+% enclose the citation number in square brackets, for
+% example~\cite{Authors14}.  Where appropriate, include the name(s) of
+% editors of referenced books.
+
+% \begin{table}
+% \begin{center}
+% \begin{tabular}{|l|c|}
+% \hline
+% Method & Frobnability \\
+% \hline\hline
+% Theirs & Frumpy \\
+% Yours & Frobbly \\
+% Ours & Makes one's heart Frob\\
+% \hline
+% \end{tabular}
+% \end{center}
+% \caption{Results.   Ours is better.}
+% \end{table}
+
+% %-------------------------------------------------------------------------
+% \subsection{Illustrations, graphs, and photographs}
+
+% All graphics should be centered.  Please ensure that any point you wish to
+% make is resolvable in a printed copy of the paper.  Resize fonts in figures
+% to match the font in the body text, and choose line widths which render
+% effectively in print.  Many readers (and reviewers), even of an electronic
+% copy, will choose to print your paper in order to read it.  You cannot
+% insist that they do otherwise, and therefore must not assume that they can
+% zoom in to see tiny details on a graphic.
+
+% When placing figures in \LaTeX, it's almost always best to use
+% \verb+\includegraphics+, and to specify the  figure width as a multiple of
+% the line width as in the example below
+% {\small\begin{verbatim}
+%   \usepackage[dvips]{graphicx} ...
+%   \includegraphics[width=0.8\linewidth]
+%                   {myfile.eps}
+% \end{verbatim}
+% }
+
+% %-------------------------------------------------------------------------
+% \subsection{Color}
+
+% Please refer to the author guidelines on the ICCV 2019 web page for a discussion
+% of the use of color in your document.
+
+% %------------------------------------------------------------------------
+% \section{Final copy}
+
+% You must include your signed IEEE copyright release form when you submit
+% your finished paper. We MUST have this form before your paper can be
+% published in the proceedings.
+
 \end{document}

### 2019-02-20 latex/egpaper_for_review.tex
Restructure related work and introduction

@@
 \end{itemize}
-\item More intro about proposal-free instance segmentation? Perhaps not needed
 
-\item One common method: \textbf{predict pixel embedding vectors.} For each pixel in the image, a CNN predicts an embedding vector, such that pixels in the same instance are represented by the same vector.
+\item Briefly mention methods for proposal free (pixel embedding vectors, recurrent, more in related work)
+
+\item Among successful methods: \textbf{predict short and long-range affinities}
+\begin{itemize}
+\item for each pixel we fix a set of neighboring pixels (not necessarily limited to the direct neighbors);  a CNN predicts then affinities, that represent how likely it is for each pair of neighboring pixels to be in the same instance.
+\item The final segmentation is obtained by using some kind of graph clustering algorithm
+\item \textbf{Motivation to use this method:} GMIS achieved comparable results to methods based on object proposal like Mask-R-CNN on natural images (Cityscapes);  MWS achieved SOA results on a biological images (ISBI)
+\end{itemize}
+\item It was shown that it is good to describe the problem in terms of a signed graph clustering problem (see MWS and others): directly train CNN to predict \textbf{repulsion and attraction}; no need to define seeds or to fix a threshold given an hierarchy of clusters, etc...
+
+\item \textit{\textbf{Multicut} has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region.
+Its great drawback is that its optimization is NP-hard.} \SOURCE{MWS}.
+\item Problem: this specific application is too expensive even for recently proposed multicut heuristics/ approximations
+\item Efficient alternatives proposed independently (leave details to the related work), but: missing comparison on this type of problem/graph
+\item our contributions:
+\begin{itemize}
+\item we propose a unified and simple formalization of Signed Graph Edge Contraction Clustering and show how many of the recently proposed methods can be seen as special cases
+\item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and energy) 
+\item we propose a new a constrained version of average agglomerative clustering that proved to be quite robust in most of our experiments
+\end{itemize}
+\item on other datasets (connectomics) many methods are based on multi-step pipelines first predicting superpixels
+\item \textit{if we get decent scores on CREMI}: we show that also on neuro-data it is worth to skip the hand-crafted superpixel step and compute the final segmentation directly from the CNN predictions (MWS already showed it on ISBI)
+
+\end{itemize}
+
+\section{Related work}
+\begin{itemize}
+\item \textit{Optional:} more about \textbf{Mask R-CNN}? (we actually already explain in the introduction why we do not care about it)
+\item \textbf{Proposal-free instance segmentation} methods:
+\begin{itemize}
+\item \textbf{Predict pixel embedding vectors:} 
+\begin{itemize}
+\item For each pixel in the image, a CNN predicts an embedding vector, such that pixels in the same instance are represented by the same vector.
 (\textit{by training a model that labels pixels with unit-length vectors that live in some ﬁxed dimension embedding space} \SOURCE{Rec.
@@
 Parsing the image embedding space involves some sort of clustering algorithm.} \SOURCE{online}
-\item use clustering algorithms like DBSCAN, mean-shift or similar ones working directly in the embedding space. \UPDATE{More clustering options..?}
-\item Other methods directly \textbf{Predict short and long-range affinities}: for each pixel we fix a set of neighboring pixels (not necessarily limited to the direct neighbors);  a CNN predicts then affinities, that represent how likely it is for each pair of neighboring pixels to be in the same instance.
-\item Even with pixel embedding vectors we can deduce affinities or signed costs
-\item It was shown that it is good to describe the problem in terms of a signed graph, or better: pixel-grid graph with short- and long-range connections; segmentation given by (signed) graph partitioning algorithm
-\item makes sense to use repulsion/attraction; directly predicted by CNN; no need to fix threshold/number of seeds/etc...
-\item \textit{Multicut has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region.
-Its great drawback is that its optimization is NP-hard.} \SOURCE{MWS}.
-(too big even for multicut approximations)
-\item Efficient alternatives proposed independently: local-search approximations, MWS, graph-merge with average \TODO{Expand this part (add more items to the list) and highlight the fact that so far a clear comparison was missing and everyone was using something kind of random}
-\item To summarize our contributions:
-\begin{itemize}
-\item we propose a unified and simple formalization of Signed Graph Edge Contraction Clustering and show how many of the recently proposed methods can be seen as special cases
-\item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and energy) 
-\item we propose a new a constrained version of average agglomerative clustering that proved to be quite robust in most of our experiments
+\item unsupervised or supervised; different types of loss \TODO{Find good summary}
+\item clustering algorithms like DBSCAN, mean-shift or similar ones working directly in the embedding space  \TODO{Add refs, discuss with Roman}
+\item \textit{Side comment}: Even with pixel embedding vectors we can deduce affinities or signed costs
 \end{itemize}
+\item \textbf{Other methods}: recurrent CNN, deep watershed, InstanceCut \TODO{Add more, discuss with Roman}
+\item \textbf{Predicting long-range affinities:} superhuman, MWS, graph-merge on cityscapes, holistically edge detection (see MWS paper for a good review) \TODO{Add more}
 \end{itemize}
 
-\section{Related work}
+\item So we need a \textbf{graph clustering algorithm}:
 \begin{itemize}
-\item \textbf{Pixel embedding vectors:} unsupervised or supervised; different types of loss \TODO{Find good summary}
-\item clustering algorithms like DBSCAN, mean-shift orsimilar ones working directly in the embedding space  \TODO{Add refs, discuss with Roman}
-\item \textbf{Predicting affinities (and long-range):} superhuman, MWS, graph-merge on cityscapes, holistically edge detection (see MWS paper for a good review) \TODO{Add more}
-\item \textbf{Pipelines in connectomics (or better: merge trees):} \textit{Similar to the boundary detection/region segmentation pipeline for natural image segmentation [6,7,8,9], most recent EM image segmentation methods use a membrane detection/cell segmentation pipeline.
+\item Mention some seeded method?
+\item \textit{Unsigned clustering methods:} Felzenszwalb Efficient Graph-based Image segmentation, (spectral clustering, graph cuts, not sure...)  \TODO{Here I need some input about recent stuff}
+\item \textit{Merge-tree methods:} 
+\begin{itemize}
+\item Hierarchical clustering, ultra-metric contour map...? \TODO{This needs more research}
+\item Only one from pixels I know: GMIS, hierarchical-Felzenszwalb (??) 
+\item most of the others from superpixels
+\item In connectomics: GALA, merge-mistakes (another section for splitting option?)
+\item \textit{Similar to the boundary detection/region segmentation pipeline for natural image segmentation [6,7,8,9], most recent EM image segmentation methods use a membrane detection/cell segmentation pipeline.
 First, a membrane detector generates pixel-wise conﬁdence maps of membrane predictions using local image cues [10,11,12].
@@
 Meanwhile, structures, such as loopy graphs [15,16] or trees [17,18,19], are more often imposed to represent the region merging hierarchy and help transform the superpixel combination search into graph labeling problems.
-To this end, local [17,16] or structured [18,19] learning based methods are developed.} \SOURCE{SSHMT} \TODO{This clearly need to be extended and reformulated}
-\item \textbf{Cannot-link constraints:} initially introduced as hard-contraints, then relaxed (MWS, Greedy Fixation)
-\item \textbf{Unsigned clustering methods:} Felzenszwalb Efficient Graph-based Image segmentation, \TODO{Hierarchical clustering \& Co.}
+To this end, local [17,16] or structured [18,19] learning based methods are developed.} \SOURCE{SSHMT} \SOURCE{Jan Funke Multicut proposals}
+\end{itemize}
+\item \textbf{Signed graph}
+\begin{itemize}
+\item Multicut pipiline and heuristics
+\item Jan Funke proposals
+\item \textit{Cannot-link constraints:} initially introduced as hard-contraints, then relaxed (MWS, Greedy Fixation)
+\item Local-search approximations of MC: GAEC, GreedyFixation
+\end{itemize}
+\end{itemize}
+
 \end{itemize}
@@
 \begin{itemize}
+\item Define graph formalism
 \item Rows in the table:

### 2019-02-21 latex/egpaper_for_review.tex
Add first pseudocode

@@
 \usepackage{amssymb}
+
+\usepackage{algorithm}% http://ctan.org/pkg/algorithm
+\PassOptionsToPackage{noend}{algpseudocode}% comment out if want end's to show
+\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
+
+% \newcommand*{\algrule}[1][\algorithmicindent]{\makebox[#1][l]{\hspace*{.5em}\vrule height .75\baselineskip depth .25\baselineskip}}%
+
+% \newcount\ALG@printindent@tempcnta
+% \def\ALG@printindent{%
+%     \ifnum \theALG@nested>0% is there anything to print
+%         \ifx\ALG@text\ALG@x@notext% is this an end group without any text?
+%             % do nothing
+%             \addvspace{-3pt}% FUDGE for cases where no text is shown, to make the rules line up
+%         \else
+%             \unskip
+%             % draw a rule for each indent level
+%             \ALG@printindent@tempcnta=1
+%             \loop
+%                 \algrule[\csname ALG@ind@\the\ALG@printindent@tempcnta\endcsname]%
+%                 \advance \ALG@printindent@tempcnta 1
+%             \ifnum \ALG@printindent@tempcnta<\numexpr\theALG@nested+1\relax% can't do <=, so add one to RHS and use < instead
+%             \repeat
+%         \fi
+%     \fi
+%     }%
+\usepackage{etoolbox}
+% the following line injects our new indent handling code in place of the default spacing
+% \patchcmd{\ALG@doentity}{\noindent\hskip\ALG@tlm}{\ALG@printindent}{}{\errmessage{failed to patch}}
+% \makeatother
+% end vertical rule patch for algorithmicx
 
@@
 % \newcommand\CHANGED[2]{{{\color{blue}{#1}}\color{green}{#2}}}
+
+\usepackage[dvipsnames]{xcolor}
+\usepackage{enumitem}
 
@@
 \end{itemize}
-\item \textbf{Other methods}: recurrent CNN, deep watershed, InstanceCut \TODO{Add more, discuss with Roman}
+\item \textbf{Other methods}: recurrent CNN, deep watershed, InstanceCut, Deep Coloring 2018 \TODO{Add more, discuss with Roman}
 \item \textbf{Predicting long-range affinities:} superhuman, MWS, graph-merge on cityscapes, holistically edge detection (see MWS paper for a good review) \TODO{Add more}
@@
 \end{itemize}
+
+\begin{algorithm}
+  \caption{Graph Agglomerative Clustering}
+\setlength{\parindent}{\algorithmicindent} \textbf{Inputs:}
+     \begin{itemize}[leftmargin=1.3cm,topsep=0.1pt,itemsep=-1.ex]
+    %  \setlength\itemsep{0.em}
+   \item $\mathcal{G}(V,E)$ with $|V|=N$, $|E|=M$
+   \item signed edge weights $w:\,E\rightarrow\mathbb{R}$
+   \item {\color{blue}addMustNotLink} $\in \{ True, False\}$
+   \end{itemize}
+   \vspace{0.4em}
+
+\setlength{\parindent}{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$
+
+%   \hspace*{\algorithmicindent} \textbf{Inputs:} $\mathcal{G}(V,E)$ with signed costs $w:\,E\rightarrow\mathbb{R}$. \\
+%   Prova \\
+%   \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$\\
+
+  \hspace*{\algorithmicindent} 
+  \begin{algorithmic}[1]
+
+    % \Procedure{GraphEdgeContr}{{\color{blue}bool \emph{addConstraints}}}
+      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
+      \State $\mathcal{G}'(V', E') \gets \mathcal{G}(V, E)$  \Comment{Contracted graph}
+    %   \State PQ $\gets$ Sort $e\in E$ in descending order of $|w_e|$
+        \State PQ.push$(|w_e|, w_e, e) \quad \forall e \in E $  \Comment{Sort edges by $|w_e|$}
+
+      \State $\Pi \gets \{ \{v_1\}, ..., \{v_N\} \}$ \Comment{Initial clustering}
+      \State $E_\dagger \gets \{\}$ \Comment{Set of must-not-link edges}
+    %   \State PQ.push$(e,  ) \quad \forall e \in E $  
+    \State
+      \While{PQ is \textbf{not} empty}
+        \State $|\tilde{w}|, \tilde{w}, e_{uv} \gets $ PQ.popHighest()
+        \If{ $e_{uv} \notin E' $} 
+            \State \textbf{continue}
+        \EndIf
+        \If{({\color{ForestGreen}\textbf{$\tilde{w} > 0$}}) \textbf{and} ($e_{uv} \notin E_\dagger$)}
+        %   \State $u,v \gets u,v \in V' : $
+        %   \State $S_u \gets S \in \Pi$ : $ u \in S$
+        %   \State $S_v \gets S \in \Pi$ : $ v \in S$
+          \State PQ, $\,E_\dagger,\,\, E' \gets$ \textsc{deleteDoubleEdges}($u,v$)
+        %   \State mergeDoubleEdges($u,v$) \Comment{Update PQ, $E_\dagger, \mathcal{G}'$}
+
+        %   \State Update costs of double edges;
+        %   \State Propagate constrained flags of double edges;
+          \State $V' \gets V' \setminus \{ v\}$, $\quad E' \gets E' \setminus \{ e_{uv}\}$
+        %   \State $ S_u \gets S_u \cup S_v$
+          \State $\Pi \gets \Pi \cup \{ S_u^\Pi \cup S_v^\Pi \} \setminus \{ S_u^\Pi, S_v^\Pi \}$
+          % \For{every new double edge}
+          %   \State Delete double edges
+          %   \State Insert new one with updated cost
+          % \EndFor
+        \EndIf
+        \If{({\color{red}\textbf{$\tilde{w} \leq 0$}}) \textbf{and} {\color{blue}addMustNotLink}}
+          \State $ E_\dagger \gets E_\dagger \cup \{e_{uv} \} $
+        \EndIf
+      \EndWhile
+      \State
+    %   \State
+      \Return $\Pi$
+      % \State
+    % \EndProcedure
+
+  \end{algorithmic}
+  \hspace*{2cm} 
+    \begin{algorithmic}[1]
+
+    \Function{DeleteDoubleEdges}{$u,v$}
+      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
+      \State $\mathcal{N}_u = \{ t \in V' | e_{ut}\in E'  \}$
+      \State $\mathcal{N}_v = \{ t \in V' | e_{vt}\in E'  \}$
+      \For{$t \in \mathcal{N}_u  \cap \mathcal{N}_v$ }
+        \State $|\tilde{w}_1|, \tilde{w}_1, e_1 \gets $ PQ.pop($e_{ut}$)
+        \State $|\tilde{w}_2|, \tilde{w}_2, e_2 \gets $ PQ.pop($e_{vt}$)
+        % \State $e_1, e_2 \gets e_{ut}, e_{vt}$
+        \State $E' \gets E' \setminus \{ e_2\}$ %\Comment{Delete double edge}
+        \If{$e_2 \in E_\dagger $} \Comment{Propagate must-not-link}
+            \State $ E_\dagger \gets E_\dagger \cup \{e_1 \} $
+        \EndIf
+        % \State $\tilde{w}_1, \tilde{w}_2 \gets $ PQ.pop($e_1$), PQ.pop($e_2$)
+        \State $\tilde{w}_{\mathrm{new}} \gets$ \textsc{linkageCriteria}$(\tilde{w}_1, \tilde{w}_2)$
+        \State PQ.push($|\tilde{w}_{\mathrm{new}}|$, $\tilde{w}_{\mathrm{new}}$,  $e_1$)
+
+      \EndFor
+
+      \State
+    %   \State
+      \Return PQ, $E_\dagger, E'$
+    %   % \State
+
+    \EndFunction
+
+  \end{algorithmic}
+
+\end{algorithm}
 
@@
 
-%-------------------------------------------------------------------------
-
-% \section{ICCV stuff}
-% \subsection{Language}
-
-% All manuscripts must be in English.
-
-% \subsection{Dual submission}
-
-% Please refer to the author guidelines on the ICCV 2019 web page for a
-% discussion of the policy on dual submissions.
-
-% \subsection{Paper length}
-% Papers, excluding the references section,
-% must be no longer than eight pages in length. The references section
-% will not be included in the page count, and there is no limit on the
-% length of the references section. For example, a paper of eight pages
-% with two pages of references would have a total length of 10 pages.
-
-% Overlength papers will simply not be reviewed.  This includes papers
-% where the margins and formatting are deemed to have been significantly
-% altered from those laid down by this style guide.  Note that this
-% \LaTeX\ guide already sets figure captions and references in a smaller font.
-% The reason such papers will not be reviewed is that there is no provision for
-% supervised revisions of manuscripts.  The reviewing process cannot determine
-% the suitability of the paper for presentation in eight pages if it is
-% reviewed in eleven.
-
-% %-------------------------------------------------------------------------
-% \subsection{The ruler}
-% The \LaTeX\ style defines a printed ruler which should be present in the
-% version submitted for review.  The ruler is provided in order that
-% reviewers may comment on particular lines in the paper without
-% circumlocution.  If you are preparing a document using a non-\LaTeX\
-% document preparation system, please arrange for an equivalent ruler to
-% appear on the final output pages.  The presence or absence of the ruler
-% should not change the appearance of any other content on the page.  The
-% camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
-% the \verb'\iccvfinalcopy' command in the document preamble.)  Reviewers:
-% note that the ruler measurements do not align well with lines in the paper
-% --- this turns out to be very difficult to do well when the paper contains
-% many figures and equations, and, when done, looks ugly.  Just use fractional
-% references (e.g.\ this line is $095.5$), although in most cases one would
-% expect that the approximate location will be adequate.
-
-% \subsection{Mathematics}
-
-% Please number all of your sections and displayed equations.  It is
-% important for readers to be able to refer to any particular equation.  Just
-% because you didn't refer to it in the text doesn't mean some future reader
-% might not need to refer to it.  It is cumbersome to have to use
-% circumlocutions like ``the equation second from the top of page 3 column
-% 1''.  (Note that the ruler will not be present in the final copy, so is not
-% an alternative to equation numbers).  All authors will benefit from reading
-% Mermin's description of how to write mathematics:
-% \url{http://www.pamitc.org/documents/mermin.pdf}.
-
-% \subsection{Blind review}
-
-% Many authors misunderstand the concept of anonymizing for blind
-% review.  Blind review does not mean that one must remove
-% citations to one's own work---in fact it is often impossible to
-% review a paper unless the previous citations are known and
-% available.
-
-% Blind review means that you do not use the words ``my'' or ``our''
-% when citing previous work.  That is all.  (But see below for
-% techreports.)
-
-% Saying ``this builds on the work of Lucy Smith [1]'' does not say
-% that you are Lucy Smith; it says that you are building on her
-% work.  If you are Smith and Jones, do not say ``as we show in
-% [7]'', say ``as Smith and Jones show in [7]'' and at the end of the
-% paper, include reference 7 as you would any other cited work.
-
-% An example of a bad paper just asking to be rejected:
-% \begin{quote}
-% \begin{center}
-%     An analysis of the frobnicatable foo filter.
-% \end{center}
-
-%   In this paper we present a performance analysis of our
-%   previous paper [1], and show it to be inferior to all
-%   previously known methods.  Why the previous paper was
-%   accepted without this analysis is beyond me.
-
-%   [1] Removed for blind review
-% \end{quote}
-
-% An example of an acceptable paper:
-
-% \begin{quote}
-% \begin{center}
-%      An analysis of the frobnicatable foo filter.
-% \end{center}
-
-%   In this paper we present a performance analysis of the
-%   paper of Smith \etal [1], and show it to be inferior to
-%   all previously known methods.  Why the previous paper
-%   was accepted without this analysis is beyond me.
-
-%   [1] Smith, L and Jones, C. ``The frobnicatable foo
-%   filter, a fundamental contribution to human knowledge''.
-%   Nature 381(12), 1-213.
-% \end{quote}
-
-% If you are making a submission to another conference at the same time,
-% which covers similar or overlapping material, you may need to refer to that
-% submission in order to explain the differences, just as you would if you
-% had previously published related work.  In such cases, include the
-% anonymized parallel submission~\cite{Authors14} as additional material and
-% cite it as
-% \begin{quote}
-% [1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
-% Supplied as additional material {\tt fg324.pdf}.
-% \end{quote}
-
-% Finally, you may feel you need to tell the reader that more details can be
-% found elsewhere, and refer them to a technical report.  For conference
-% submissions, the paper must stand on its own, and not {\em require} the
-% reviewer to go to a techreport for further details.  Thus, you may say in
-% the body of the paper ``further details may be found
-% in~\cite{Authors14b}''.  Then submit the techreport as additional material.
-% Again, you may not assume the reviewers will read this material.
-
-% Sometimes your paper is about a problem which you tested using a tool which
-% is widely known to be restricted to a single institution.  For example,
-% let's say it's 1969, you have solved a key problem on the Apollo lander,
-% and you believe that the ICCV70 audience would like to hear about your
-% solution.  The work is a development of your celebrated 1968 paper entitled
-% ``Zero-g frobnication: How being the only people in the world with access to
-% the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-
-% You can handle this paper like any other.  Don't write ``We show how to
-% improve our previous work [Anonymous, 1968].  This time we tested the
-% algorithm on a lunar lander [name of lander removed for blind review]''.
-% That would be silly, and would immediately identify the authors. Instead
-% write the following:
-% \begin{quotation}
-% \noindent
-%   We describe a system for zero-g frobnication.  This
-%   system is new because it handles the following cases:
-%   A, B.  Previous systems [Zeus et al. 1968] didn't
-%   handle case B properly.  Ours handles it by including
-%   a foo term in the bar integral.
-
-%   ...
-
-%   The proposed system was integrated with the Apollo
-%   lunar lander, and went all the way to the moon, don't
-%   you know.  It displayed the following behaviours
-%   which show how well we solved cases A and B: ...
-% \end{quotation}
-% As you can see, the above text follows standard scientific convention,
-% reads better than the first version, and does not explicitly name you as
-% the authors.  A reviewer might think it likely that the new paper was
-% written by Zeus \etal, but cannot make any decision based on that guess.
-% He or she would have to be sure that no other authors could have been
-% contracted to solve problem B.
-
-% \noindent
-% FAQ\medskip\\
-% {\bf Q:} Are acknowledgements OK?\\
-% {\bf A:} No.  Leave them for the final copy.\medskip\\
-% {\bf Q:} How do I cite my results reported in open challenges?
-% {\bf A:} To conform with the double blind review policy, you can report results of other challenge participants together with your results in your paper.
-For your results, however, you should not identify yourself and should not mention your participation in the challenge.
-Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
-
-% \begin{figure}[t]
-% \begin{center}
-% \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-%   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-% \end{center}
-%   \caption{Example of caption.  It is set in Roman so that mathematics
-%   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-%   ugly clash.}
-% \label{fig:long}
-% \label{fig:onecol}
-% \end{figure}
-
-% \subsection{Miscellaneous}
-
-% \noindent
-% Compare the following:\\
-% \begin{tabular}{ll}
-%  \verb'$conf_a$' &  $conf_a$ \\
-%  \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-% \end{tabular}\\
-% See The \TeX book, p165.
-
-% The space after \eg, meaning ``for example'', should not be a
-% sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
-% \verb'\eg' macro takes care of this.
-
-% When citing a multi-author paper, you may save space by using ``et alia'',
-% shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
-% However, use it only when there are three or more authors.  Thus, the
-% following is correct: ``
-%   Frobnication has been trendy lately.
-%   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-%   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-
-% This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
-% because reference~\cite{Alpher03} has just two authors.  If you use the
-% \verb'\etal' macro provided, then you need not worry about double periods
-% when used at the end of a sentence as in Alpher \etal.
-
-% For this citation style, keep multiple citations in numerical (not
-% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-% \cite{Alpher02,Alpher03,Authors14}.
-
-% \begin{figure*}
-% \begin{center}
-% \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-% \end{center}
-%   \caption{Example of a short caption, which should be centered.}
-% \label{fig:short}
-% \end{figure*}
-
-% %------------------------------------------------------------------------
-% \section{Formatting your paper}
-
-% All text must be in a two-column format. The total allowable width of the
-% text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
-% cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
-% $\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
-% first page) should begin 1.0 inch (2.54 cm) from the top edge of the
-% page. The second and following pages should begin 1.0 inch (2.54 cm) from
-% the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
-% cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
-% paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
-% page.
-
-% %-------------------------------------------------------------------------
-% \subsection{Margins and page numbering}
-
-% All printed material, including text, illustrations, and charts, must be kept
-% within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
-% high.
-
-% %-------------------------------------------------------------------------
-% \subsection{Type-style and fonts}
-
-% Wherever Times is specified, Times Roman may also be used. If neither is
-% available on your word processor, please use the font closest in
-% appearance to Times to which you have access.
-
-% MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
-% the first page. The title should be in Times 14-point, boldface type.
-% Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
-% adverbs; do not capitalize articles, coordinate conjunctions, or
-% prepositions (unless the title begins with such a word). Leave two blank
-% lines after the title.
-
-% AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-% and printed in Times 12-point, non-boldface type. This information is to
-% be followed by two blank lines.
-
-% The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-% MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
-% double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
-% inch or 0.422 cm). Make sure your text is fully justified---that is,
-% flush left and flush right. Please do not place any additional blank
-% lines between paragraphs.
-
-% Figure and table captions should be 9-point Roman type as in
-% Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.
-
-% \noindent Callouts should be 9-point Helvetica, non-boldface type.
-% Initially capitalize only the first word of section titles and first-,
-% second-, and third-order headings.
-
-% FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
-% should be Times 12-point boldface, initially capitalized, flush left,
-% with one blank line before, and one blank line after.
-
-% SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
-% should be Times 11-point boldface, initially capitalized, flush left,
-% with one blank line before, and one after. If you require a third-order
-% heading (we discourage it), use 10-point Times, boldface, initially
-% capitalized, flush left, preceded by one blank line, followed by a period
-% and your text on the same line.
-
-% %-------------------------------------------------------------------------
-% \subsection{Footnotes}
-
-% Please use footnotes\footnote {This is what a footnote looks like.  It
-% often distracts the reader from the main flow of the argument.} sparingly.
-% Indeed, try to avoid footnotes altogether and include necessary peripheral
-% observations in
-% the text (within parentheses, if you prefer, as in this sentence).  If you
-% wish to use a footnote, place it at the bottom of the column on the page on
-% which it is referenced. Use Times 8-point type, single-spaced.
-
-% %-------------------------------------------------------------------------
-% \subsection{References}
-
-% List and number all bibliographical references in 9-point Times,
-% single-spaced, at the end of your paper. When referenced in the text,
-% enclose the citation number in square brackets, for
-% example~\cite{Authors14}.  Where appropriate, include the name(s) of
-% editors of referenced books.
-
-% \begin{table}
-% \begin{center}
-% \begin{tabular}{|l|c|}
-% \hline
-% Method & Frobnability \\
-% \hline\hline
-% Theirs & Frumpy \\
-% Yours & Frobbly \\
-% Ours & Makes one's heart Frob\\
-% \hline
-% \end{tabular}
-% \end{center}
-% \caption{Results.   Ours is better.}
-% \end{table}
-
-% %-------------------------------------------------------------------------
-% \subsection{Illustrations, graphs, and photographs}
-
-% All graphics should be centered.  Please ensure that any point you wish to
-% make is resolvable in a printed copy of the paper.  Resize fonts in figures
-% to match the font in the body text, and choose line widths which render
-% effectively in print.  Many readers (and reviewers), even of an electronic
-% copy, will choose to print your paper in order to read it.  You cannot
-% insist that they do otherwise, and therefore must not assume that they can
-% zoom in to see tiny details on a graphic.
-
-% When placing figures in \LaTeX, it's almost always best to use
-% \verb+\includegraphics+, and to specify the  figure width as a multiple of
-% the line width as in the example below
-% {\small\begin{verbatim}
-%   \usepackage[dvips]{graphicx} ...
-%   \includegraphics[width=0.8\linewidth]
-%                   {myfile.eps}
-% \end{verbatim}
-% }
-
-% %-------------------------------------------------------------------------
-% \subsection{Color}
-
-% Please refer to the author guidelines on the ICCV 2019 web page for a discussion
-% of the use of color in your document.
-
-% %------------------------------------------------------------------------
-% \section{Final copy}
-
-% You must include your signed IEEE copyright release form when you submit
-% your finished paper. We MUST have this form before your paper can be
-% published in the proceedings.
-
 \end{document}

### 2019-02-22 latex/egpaper_for_review.tex
Small changes algorithm part

@@
 
-\section{Grand Unified Edge Contraction Algorithm}
+\section{Grand Unified Whatever Clustering}
 \begin{itemize}
-\item Define graph formalism
-\item Rows in the table:
+\item Define graph formalism and clustering $\Pi$
+\item \TODO{Description of the algorithm}
+\item Linkage criteria and table:
 \begin{itemize}
@@
 \end{itemize}
+\item Pseudocode does not (exactly) include more general options: size of the nodes, features for CNN, histogram for median \TODO{But I think I should keep it simple}
+\item Comment about must-not-link relations: they give high proprity to the most confident repulsive edges \item I don't think I need to mention the merge tree (although it could be easily deduced from the code, as a sequence of clustering)
+\item Define multicut energy (or move to following section)
 \end{itemize}

### 2019-02-22 latex/agglo_clust_review.tex
Restructure repo

--- 2019-02-22 latex/egpaper_for_review.tex
@@
 
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-   The ABSTRACT is to be in fully-justified italicized text, at the top
-   of the left-hand column, below the author and affiliation
-   information. Use the word ``Abstract'' as the title, in 12-point
-   Times, boldface type, centered relative to the column, initially
-   capitalized. The abstract is to be in 10-point, single-spaced type.
-   Leave two blank lines after the Abstract, then begin the main text.
-   Look at previous ICCV abstracts to get a feel for style and length.
-\end{abstract}
+\input{chapters/abstract.tex}
 
-%%%%%%%%% BODY TEXT
-\section{Introduction}
+\input{chapters/intro.tex}
 
-\begin{itemize}
-\item \textbf{Intro about CNN:} \textit{The successes of deep convolutional neural nets (CNNs) at image classiﬁcation has spawned a ﬂurry of work in computer vision on adapting these models to pixel-level image understanding tasks, such as boundary detection [1, 90, 64], semantic segmentation [60, 10, 46], optical ﬂow [87, 20], and pose estimation [85, 7].} \SOURCE{Rec.
-embeddings}
-\item Intro about instance segmentation
-\item \textbf{Mask R-CNN:} why we do not like it 
-\begin{itemize}
-\item \textit{most recent successful approaches to instance segmentation have adopted more heuristic approaches that first use an object detector to enumerate candidate instances and then perform pixel-level segmentation of each instance [57, 17, 55, 56, 2].
-Alternately one can generate generic proposal segments and then label each one with a semantic detector [31, 12, 32, 16, 82, 34].
-In either case the detection and segmentation steps can both be mapped to standard binary classiﬁcation losses.
-While effective, these approaches are somewhat unsatisfying since: (1) they rely on the object detector and non-maximum suppression heuristics to accurately “count” the number of instances, (2) they are difﬁcult to train in an end-to-end manner since the interface between instance segmentation and detection is non-differentiable, and (3) they underperform in cluttered scenes as the assignment of pixels to detections is carried out independently for each detection 1.} \SOURCE{Rec.
-embeddings}
-\item elongated segments
-\item \textit{There are three fundamental flaws in a proposal-based instance segmentation architecture.
-First, two objects may share the same bounding box, or a very similar boxes.
-In this case, the mask head, has no way of telling which object to pick in the box.
-This is a serious problem with stringy like object that have low fill rate in their bounding box (e.g.
-bicycles and chairs).
-Second, there is nothing in the architecture preventing a pixel to be shared between two instance.
-Third, the number of instances is limited by the number of proposals processed by the network (usually hundreds).
-More over, the architecture is complex and hard to tune and “debug”.
-In object detection, a precursor to this problem, there are already successes being made to use a simpler, single-stage, architectures e.g.
-RetinaNet.}
-\end{itemize}
-
-\item Briefly mention methods for proposal free (pixel embedding vectors, recurrent, more in related work)
-
-\item Among successful methods: \textbf{predict short and long-range affinities}
-\begin{itemize}
-\item for each pixel we fix a set of neighboring pixels (not necessarily limited to the direct neighbors);  a CNN predicts then affinities, that represent how likely it is for each pair of neighboring pixels to be in the same instance.
-\item The final segmentation is obtained by using some kind of graph clustering algorithm
-\item \textbf{Motivation to use this method:} GMIS achieved comparable results to methods based on object proposal like Mask-R-CNN on natural images (Cityscapes);  MWS achieved SOA results on a biological images (ISBI)
-\end{itemize}
-\item It was shown that it is good to describe the problem in terms of a signed graph clustering problem (see MWS and others): directly train CNN to predict \textbf{repulsion and attraction}; no need to define seeds or to fix a threshold given an hierarchy of clusters, etc...
-
-\item \textit{\textbf{Multicut} has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region.
-Its great drawback is that its optimization is NP-hard.} \SOURCE{MWS}.
-\item Problem: this specific application is too expensive even for recently proposed multicut heuristics/ approximations
-\item Efficient alternatives proposed independently (leave details to the related work), but: missing comparison on this type of problem/graph
-\item our contributions:
-\begin{itemize}
-\item we propose a unified and simple formalization of Signed Graph Edge Contraction Clustering and show how many of the recently proposed methods can be seen as special cases
-\item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and energy) 
-\item we propose a new a constrained version of average agglomerative clustering that proved to be quite robust in most of our experiments
-\end{itemize}
-\item on other datasets (connectomics) many methods are based on multi-step pipelines first predicting superpixels
-\item \textit{if we get decent scores on CREMI}: we show that also on neuro-data it is worth to skip the hand-crafted superpixel step and compute the final segmentation directly from the CNN predictions (MWS already showed it on ISBI)
-
-\end{itemize}
-
-\section{Related work}
-\begin{itemize}
-\item \textit{Optional:} more about \textbf{Mask R-CNN}? (we actually already explain in the introduction why we do not care about it)
-\item \textbf{Proposal-free instance segmentation} methods:
-\begin{itemize}
-\item \textbf{Predict pixel embedding vectors:} 
-\begin{itemize}
-\item For each pixel in the image, a CNN predicts an embedding vector, such that pixels in the same instance are represented by the same vector.
-(\textit{by training a model that labels pixels with unit-length vectors that live in some ﬁxed dimension embedding space} \SOURCE{Rec.
-embeddings} ).
-\textit{With instance embedding, each object is assigned a “color” in a n-dimensional space.
-The network processes the image and produces a dense output, same size as the input image.
-Each pixel in the output of the network is a point in the embedding space.
-Pixels that belong to the same object are close in the embedding space while pixels that belong to different objects are distant in the embedding space.
-Parsing the image embedding space involves some sort of clustering algorithm.} \SOURCE{online}
-\item unsupervised or supervised; different types of loss \TODO{Find good summary}
-\item clustering algorithms like DBSCAN, mean-shift or similar ones working directly in the embedding space  \TODO{Add refs, discuss with Roman}
-\item \textit{Side comment}: Even with pixel embedding vectors we can deduce affinities or signed costs
-\end{itemize}
-\item \textbf{Other methods}: recurrent CNN, deep watershed, InstanceCut, Deep Coloring 2018 \TODO{Add more, discuss with Roman}
-\item \textbf{Predicting long-range affinities:} superhuman, MWS, graph-merge on cityscapes, holistically edge detection (see MWS paper for a good review) \TODO{Add more}
-\end{itemize}
-
-\item So we need a \textbf{graph clustering algorithm}:
-\begin{itemize}
-\item Mention some seeded method?
-\item \textit{Unsigned clustering methods:} Felzenszwalb Efficient Graph-based Image segmentation, (spectral clustering, graph cuts, not sure...)  \TODO{Here I need some input about recent stuff}
-\item \textit{Merge-tree methods:} 
-\begin{itemize}
-\item Hierarchical clustering, ultra-metric contour map...? \TODO{This needs more research}
-\item Only one from pixels I know: GMIS, hierarchical-Felzenszwalb (??) 
-\item most of the others from superpixels
-\item In connectomics: GALA, merge-mistakes (another section for splitting option?)
-\item \textit{Similar to the boundary detection/region segmentation pipeline for natural image segmentation [6,7,8,9], most recent EM image segmentation methods use a membrane detection/cell segmentation pipeline.
-First, a membrane detector generates pixel-wise conﬁdence maps of membrane predictions using local image cues [10,11,12].
-Next, region-based methods are applied to transforming the membrane conﬁdence maps into cell segments.
-It has been shown that region-based methods are necessary for improving the segmentation accuracy from membrane detections for EM images [13].
-A common approach to region-based segmentation is to transform a membrane conﬁdence map into over-segmenting superpixels and use them as “building blocks” for ﬁnal segmentation.
-To correctly combine superpixels, greedy region agglomeration based on certain boundary saliency has been shown to work [14].
-Meanwhile, structures, such as loopy graphs [15,16] or trees [17,18,19], are more often imposed to represent the region merging hierarchy and help transform the superpixel combination search into graph labeling problems.
-To this end, local [17,16] or structured [18,19] learning based methods are developed.} \SOURCE{SSHMT} \SOURCE{Jan Funke Multicut proposals}
-\end{itemize}
-\item \textbf{Signed graph}
-\begin{itemize}
-\item Multicut pipiline and heuristics
-\item Jan Funke proposals
-\item \textit{Cannot-link constraints:} initially introduced as hard-contraints, then relaxed (MWS, Greedy Fixation)
-\item Local-search approximations of MC: GAEC, GreedyFixation
-\end{itemize}
-\end{itemize}
-
-\end{itemize}
+\input{chapters/rel_work.tex}
 
@@
 \bibliographystyle{ieee}
-\bibliography{egbib}
+\bibliography{agglo_clust}
 }

### 2019-02-22 latex/chapters/abstract.tex
Restructure repo

--- 2019-02-21 latex/egpaper_for_review.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{iccv}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-
-\usepackage{algorithm}% http://ctan.org/pkg/algorithm
-\PassOptionsToPackage{noend}{algpseudocode}% comment out if want end's to show
-\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
-
-% \newcommand*{\algrule}[1][\algorithmicindent]{\makebox[#1][l]{\hspace*{.5em}\vrule height .75\baselineskip depth .25\baselineskip}}%
-
-% \newcount\ALG@printindent@tempcnta
-% \def\ALG@printindent{%
-%     \ifnum \theALG@nested>0% is there anything to print
-%         \ifx\ALG@text\ALG@x@notext% is this an end group without any text?
-%             % do nothing
-%             \addvspace{-3pt}% FUDGE for cases where no text is shown, to make the rules line up
-%         \else
-%             \unskip
-%             % draw a rule for each indent level
-%             \ALG@printindent@tempcnta=1
-%             \loop
-%                 \algrule[\csname ALG@ind@\the\ALG@printindent@tempcnta\endcsname]%
-%                 \advance \ALG@printindent@tempcnta 1
-%             \ifnum \ALG@printindent@tempcnta<\numexpr\theALG@nested+1\relax% can't do <=, so add one to RHS and use < instead
-%             \repeat
-%         \fi
-%     \fi
-%     }%
-\usepackage{etoolbox}
-% the following line injects our new indent handling code in place of the default spacing
-% \patchcmd{\ALG@doentity}{\noindent\hskip\ALG@tlm}{\ALG@printindent}{}{\errmessage{failed to patch}}
-% \makeatother
-% end vertical rule patch for algorithmicx
-
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-% \iccvfinalcopy % *** Uncomment this line for the final submission
-
-\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\usepackage{mathrsfs}
-\newcommand{\RED}[1]{#1}
-
-\newcommand\TODO[1]{{\color{red}{TODO: #1}}}
-\newcommand\UPDATE[1]{{\color{blue}{#1}}}
-\newcommand\SOURCE[1]{{\color{green}{(from: #1)}}}
-% \newcommand\CHANGED[2]{{{\color{blue}{#1}}\color{green}{#2}}}
-
-\usepackage[dvipsnames]{xcolor}
-\usepackage{enumitem}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ificcvfinal\pagestyle{empty}\fi
-\begin{document}
-
-%%%%%%%%% TITLE
-\title{\LaTeX\ Author Guidelines for ICCV Proceedings}
-
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
-}
-
-\maketitle
-%\thispagestyle{empty}
-
 %%%%%%%%% ABSTRACT
@@
 \end{abstract}
-
-%%%%%%%%% BODY TEXT
-\section{Introduction}
-
-\begin{itemize}
-\item \textbf{Intro about CNN:} \textit{The successes of deep convolutional neural nets (CNNs) at image classiﬁcation has spawned a ﬂurry of work in computer vision on adapting these models to pixel-level image understanding tasks, such as boundary detection [1, 90, 64], semantic segmentation [60, 10, 46], optical ﬂow [87, 20], and pose estimation [85, 7].} \SOURCE{Rec.
-embeddings}
-\item Intro about instance segmentation
-\item \textbf{Mask R-CNN:} why we do not like it 
-\begin{itemize}
-\item \textit{most recent successful approaches to instance segmentation have adopted more heuristic approaches that first use an object detector to enumerate candidate instances and then perform pixel-level segmentation of each instance [57, 17, 55, 56, 2].
-Alternately one can generate generic proposal segments and then label each one with a semantic detector [31, 12, 32, 16, 82, 34].
-In either case the detection and segmentation steps can both be mapped to standard binary classiﬁcation losses.
-While effective, these approaches are somewhat unsatisfying since: (1) they rely on the object detector and non-maximum suppression heuristics to accurately “count” the number of instances, (2) they are difﬁcult to train in an end-to-end manner since the interface between instance segmentation and detection is non-differentiable, and (3) they underperform in cluttered scenes as the assignment of pixels to detections is carried out independently for each detection 1.} \SOURCE{Rec.
-embeddings}
-\item elongated segments
-\item \textit{There are three fundamental flaws in a proposal-based instance segmentation architecture.
-First, two objects may share the same bounding box, or a very similar boxes.
-In this case, the mask head, has no way of telling which object to pick in the box.
-This is a serious problem with stringy like object that have low fill rate in their bounding box (e.g.
-bicycles and chairs).
-Second, there is nothing in the architecture preventing a pixel to be shared between two instance.
-Third, the number of instances is limited by the number of proposals processed by the network (usually hundreds).
-More over, the architecture is complex and hard to tune and “debug”.
-In object detection, a precursor to this problem, there are already successes being made to use a simpler, single-stage, architectures e.g.
-RetinaNet.}
-\end{itemize}
-
-\item Briefly mention methods for proposal free (pixel embedding vectors, recurrent, more in related work)
-
-\item Among successful methods: \textbf{predict short and long-range affinities}
-\begin{itemize}
-\item for each pixel we fix a set of neighboring pixels (not necessarily limited to the direct neighbors);  a CNN predicts then affinities, that represent how likely it is for each pair of neighboring pixels to be in the same instance.
-\item The final segmentation is obtained by using some kind of graph clustering algorithm
-\item \textbf{Motivation to use this method:} GMIS achieved comparable results to methods based on object proposal like Mask-R-CNN on natural images (Cityscapes);  MWS achieved SOA results on a biological images (ISBI)
-\end{itemize}
-\item It was shown that it is good to describe the problem in terms of a signed graph clustering problem (see MWS and others): directly train CNN to predict \textbf{repulsion and attraction}; no need to define seeds or to fix a threshold given an hierarchy of clusters, etc...
-
-\item \textit{\textbf{Multicut} has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region.
-Its great drawback is that its optimization is NP-hard.} \SOURCE{MWS}.
-\item Problem: this specific application is too expensive even for recently proposed multicut heuristics/ approximations
-\item Efficient alternatives proposed independently (leave details to the related work), but: missing comparison on this type of problem/graph
-\item our contributions:
-\begin{itemize}
-\item we propose a unified and simple formalization of Signed Graph Edge Contraction Clustering and show how many of the recently proposed methods can be seen as special cases
-\item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and energy) 
-\item we propose a new a constrained version of average agglomerative clustering that proved to be quite robust in most of our experiments
-\end{itemize}
-\item on other datasets (connectomics) many methods are based on multi-step pipelines first predicting superpixels
-\item \textit{if we get decent scores on CREMI}: we show that also on neuro-data it is worth to skip the hand-crafted superpixel step and compute the final segmentation directly from the CNN predictions (MWS already showed it on ISBI)
-
-\end{itemize}
-
-\section{Related work}
-\begin{itemize}
-\item \textit{Optional:} more about \textbf{Mask R-CNN}? (we actually already explain in the introduction why we do not care about it)
-\item \textbf{Proposal-free instance segmentation} methods:
-\begin{itemize}
-\item \textbf{Predict pixel embedding vectors:} 
-\begin{itemize}
-\item For each pixel in the image, a CNN predicts an embedding vector, such that pixels in the same instance are represented by the same vector.
-(\textit{by training a model that labels pixels with unit-length vectors that live in some ﬁxed dimension embedding space} \SOURCE{Rec.
-embeddings} ).
-\textit{With instance embedding, each object is assigned a “color” in a n-dimensional space.
-The network processes the image and produces a dense output, same size as the input image.
-Each pixel in the output of the network is a point in the embedding space.
-Pixels that belong to the same object are close in the embedding space while pixels that belong to different objects are distant in the embedding space.
-Parsing the image embedding space involves some sort of clustering algorithm.} \SOURCE{online}
-\item unsupervised or supervised; different types of loss \TODO{Find good summary}
-\item clustering algorithms like DBSCAN, mean-shift or similar ones working directly in the embedding space  \TODO{Add refs, discuss with Roman}
-\item \textit{Side comment}: Even with pixel embedding vectors we can deduce affinities or signed costs
-\end{itemize}
-\item \textbf{Other methods}: recurrent CNN, deep watershed, InstanceCut, Deep Coloring 2018 \TODO{Add more, discuss with Roman}
-\item \textbf{Predicting long-range affinities:} superhuman, MWS, graph-merge on cityscapes, holistically edge detection (see MWS paper for a good review) \TODO{Add more}
-\end{itemize}
-
-\item So we need a \textbf{graph clustering algorithm}:
-\begin{itemize}
-\item Mention some seeded method?
-\item \textit{Unsigned clustering methods:} Felzenszwalb Efficient Graph-based Image segmentation, (spectral clustering, graph cuts, not sure...)  \TODO{Here I need some input about recent stuff}
-\item \textit{Merge-tree methods:} 
-\begin{itemize}
-\item Hierarchical clustering, ultra-metric contour map...? \TODO{This needs more research}
-\item Only one from pixels I know: GMIS, hierarchical-Felzenszwalb (??) 
-\item most of the others from superpixels
-\item In connectomics: GALA, merge-mistakes (another section for splitting option?)
-\item \textit{Similar to the boundary detection/region segmentation pipeline for natural image segmentation [6,7,8,9], most recent EM image segmentation methods use a membrane detection/cell segmentation pipeline.
-First, a membrane detector generates pixel-wise conﬁdence maps of membrane predictions using local image cues [10,11,12].
-Next, region-based methods are applied to transforming the membrane conﬁdence maps into cell segments.
-It has been shown that region-based methods are necessary for improving the segmentation accuracy from membrane detections for EM images [13].
-A common approach to region-based segmentation is to transform a membrane conﬁdence map into over-segmenting superpixels and use them as “building blocks” for ﬁnal segmentation.
-To correctly combine superpixels, greedy region agglomeration based on certain boundary saliency has been shown to work [14].
-Meanwhile, structures, such as loopy graphs [15,16] or trees [17,18,19], are more often imposed to represent the region merging hierarchy and help transform the superpixel combination search into graph labeling problems.
-To this end, local [17,16] or structured [18,19] learning based methods are developed.} \SOURCE{SSHMT} \SOURCE{Jan Funke Multicut proposals}
-\end{itemize}
-\item \textbf{Signed graph}
-\begin{itemize}
-\item Multicut pipiline and heuristics
-\item Jan Funke proposals
-\item \textit{Cannot-link constraints:} initially introduced as hard-contraints, then relaxed (MWS, Greedy Fixation)
-\item Local-search approximations of MC: GAEC, GreedyFixation
-\end{itemize}
-\end{itemize}
-
-\end{itemize}
-
-\begin{algorithm}
-  \caption{Graph Agglomerative Clustering}
-\setlength{\parindent}{\algorithmicindent} \textbf{Inputs:}
-     \begin{itemize}[leftmargin=1.3cm,topsep=0.1pt,itemsep=-1.ex]
-    %  \setlength\itemsep{0.em}
-   \item $\mathcal{G}(V,E)$ with $|V|=N$, $|E|=M$
-   \item signed edge weights $w:\,E\rightarrow\mathbb{R}$
-   \item {\color{blue}addMustNotLink} $\in \{ True, False\}$
-   \end{itemize}
-   \vspace{0.4em}
-
-\setlength{\parindent}{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$
-
-%   \hspace*{\algorithmicindent} \textbf{Inputs:} $\mathcal{G}(V,E)$ with signed costs $w:\,E\rightarrow\mathbb{R}$. \\
-%   Prova \\
-%   \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$\\
-
-  \hspace*{\algorithmicindent} 
-  \begin{algorithmic}[1]
-
-    % \Procedure{GraphEdgeContr}{{\color{blue}bool \emph{addConstraints}}}
-      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
-      \State $\mathcal{G}'(V', E') \gets \mathcal{G}(V, E)$  \Comment{Contracted graph}
-    %   \State PQ $\gets$ Sort $e\in E$ in descending order of $|w_e|$
-        \State PQ.push$(|w_e|, w_e, e) \quad \forall e \in E $  \Comment{Sort edges by $|w_e|$}
-
-      \State $\Pi \gets \{ \{v_1\}, ..., \{v_N\} \}$ \Comment{Initial clustering}
-      \State $E_\dagger \gets \{\}$ \Comment{Set of must-not-link edges}
-    %   \State PQ.push$(e,  ) \quad \forall e \in E $  
-    \State
-      \While{PQ is \textbf{not} empty}
-        \State $|\tilde{w}|, \tilde{w}, e_{uv} \gets $ PQ.popHighest()
-        \If{ $e_{uv} \notin E' $} 
-            \State \textbf{continue}
-        \EndIf
-        \If{({\color{ForestGreen}\textbf{$\tilde{w} > 0$}}) \textbf{and} ($e_{uv} \notin E_\dagger$)}
-        %   \State $u,v \gets u,v \in V' : $
-        %   \State $S_u \gets S \in \Pi$ : $ u \in S$
-        %   \State $S_v \gets S \in \Pi$ : $ v \in S$
-          \State PQ, $\,E_\dagger,\,\, E' \gets$ \textsc{deleteDoubleEdges}($u,v$)
-        %   \State mergeDoubleEdges($u,v$) \Comment{Update PQ, $E_\dagger, \mathcal{G}'$}
-
-        %   \State Update costs of double edges;
-        %   \State Propagate constrained flags of double edges;
-          \State $V' \gets V' \setminus \{ v\}$, $\quad E' \gets E' \setminus \{ e_{uv}\}$
-        %   \State $ S_u \gets S_u \cup S_v$
-          \State $\Pi \gets \Pi \cup \{ S_u^\Pi \cup S_v^\Pi \} \setminus \{ S_u^\Pi, S_v^\Pi \}$
-          % \For{every new double edge}
-          %   \State Delete double edges
-          %   \State Insert new one with updated cost
-          % \EndFor
-        \EndIf
-        \If{({\color{red}\textbf{$\tilde{w} \leq 0$}}) \textbf{and} {\color{blue}addMustNotLink}}
-          \State $ E_\dagger \gets E_\dagger \cup \{e_{uv} \} $
-        \EndIf
-      \EndWhile
-      \State
-    %   \State
-      \Return $\Pi$
-      % \State
-    % \EndProcedure
-
-  \end{algorithmic}
-  \hspace*{2cm} 
-    \begin{algorithmic}[1]
-
-    \Function{DeleteDoubleEdges}{$u,v$}
-      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
-      \State $\mathcal{N}_u = \{ t \in V' | e_{ut}\in E'  \}$
-      \State $\mathcal{N}_v = \{ t \in V' | e_{vt}\in E'  \}$
-      \For{$t \in \mathcal{N}_u  \cap \mathcal{N}_v$ }
-        \State $|\tilde{w}_1|, \tilde{w}_1, e_1 \gets $ PQ.pop($e_{ut}$)
-        \State $|\tilde{w}_2|, \tilde{w}_2, e_2 \gets $ PQ.pop($e_{vt}$)
-        % \State $e_1, e_2 \gets e_{ut}, e_{vt}$
-        \State $E' \gets E' \setminus \{ e_2\}$ %\Comment{Delete double edge}
-        \If{$e_2 \in E_\dagger $} \Comment{Propagate must-not-link}
-            \State $ E_\dagger \gets E_\dagger \cup \{e_1 \} $
-        \EndIf
-        % \State $\tilde{w}_1, \tilde{w}_2 \gets $ PQ.pop($e_1$), PQ.pop($e_2$)
-        \State $\tilde{w}_{\mathrm{new}} \gets$ \textsc{linkageCriteria}$(\tilde{w}_1, \tilde{w}_2)$
-        \State PQ.push($|\tilde{w}_{\mathrm{new}}|$, $\tilde{w}_{\mathrm{new}}$,  $e_1$)
-
-      \EndFor
-
-      \State
-    %   \State
-      \Return PQ, $E_\dagger, E'$
-    %   % \State
-
-    \EndFunction
-
-  \end{algorithmic}
-
-\end{algorithm}
-
-\section{Grand Unified Edge Contraction Algorithm}
-\begin{itemize}
-\item Define graph formalism
-\item Rows in the table:
-\begin{itemize}
-\item Mutex Watershed (MWS), [proof of equivalence included in Appendix]
-\item Greedy Additive Edge Contraction (GAEC), 
-\item Greedy Fixation (GF), 
-\item Hierarchical Agglomerative Clustering with single, complete, average (UPGMA) and weighted average (WPGMA) linkage criteria
-\item GALA (learned update rule)
-\item Something depending on the node size...?
-\end{itemize}
-\end{itemize}
-
-\section{Experiments}
-\begin{itemize}
-\item Nevertheless, in both approaches we can define a grid graph (each vertex representing a pixel) with signed weights and find the final instance segmentation by using a graph partitioning algorithm:
-\begin{itemize}
-\item In Method 1, the graph is complete and the edge weights represent similarities between pairs of pixel embedding vectors.
-In most proposed approaches, embedding vectors representing distinct instances should be "distant enough" in the embedding space (a minimum distance is usually used during the training of the CNN).
-Thus, this threshold distance can be used to define signed affinities, representing attraction or repulsion between pairs of pixels;
-\item  In Method 2, the short- and long-range affinities predicted by the CNN are directly used as signed edge weights in the grid graph
-\end{itemize}
-\end{itemize}
-
-\subsection{Results summary}
-\begin{itemize}
-\item in the proposed simple formalism for Signed Graph Edge Contraction Clustering, we also include a modified version of Hierarchical agglomerative clustering with cannot-link constraints that was not mentioned in literature so far and in our experiments proved to be quite robust to noise and outliers
-\item we compare different types of Signed Graph Edge Contraction Clustering, showing in which situations is preferable to use one or the other and which one can make a better use of the long-range CNN predictions;
-\item we focus our comparison on efficiency and robustness to mistakes in the CNN predictions 
-\item in general, our experiments show that long-range predictions should be used not only during the CNN training, but also as an input of the clustering algorithm
-
-\end{itemize}
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{egbib}
-}
-
-\section{Supplementary Material}
-\begin{itemize}
-\item Equivalence Mutex Watershed and Greedy Edge Contraction
-\end{itemize}
-
-\end{document}

### 2019-02-22 latex/chapters/intro.tex
Restructure repo

--- 2019-02-21 latex/egpaper_for_review.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{iccv}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-
-\usepackage{algorithm}% http://ctan.org/pkg/algorithm
-\PassOptionsToPackage{noend}{algpseudocode}% comment out if want end's to show
-\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
-
-% \newcommand*{\algrule}[1][\algorithmicindent]{\makebox[#1][l]{\hspace*{.5em}\vrule height .75\baselineskip depth .25\baselineskip}}%
-
-% \newcount\ALG@printindent@tempcnta
-% \def\ALG@printindent{%
-%     \ifnum \theALG@nested>0% is there anything to print
-%         \ifx\ALG@text\ALG@x@notext% is this an end group without any text?
-%             % do nothing
-%             \addvspace{-3pt}% FUDGE for cases where no text is shown, to make the rules line up
-%         \else
-%             \unskip
-%             % draw a rule for each indent level
-%             \ALG@printindent@tempcnta=1
-%             \loop
-%                 \algrule[\csname ALG@ind@\the\ALG@printindent@tempcnta\endcsname]%
-%                 \advance \ALG@printindent@tempcnta 1
-%             \ifnum \ALG@printindent@tempcnta<\numexpr\theALG@nested+1\relax% can't do <=, so add one to RHS and use < instead
-%             \repeat
-%         \fi
-%     \fi
-%     }%
-\usepackage{etoolbox}
-% the following line injects our new indent handling code in place of the default spacing
-% \patchcmd{\ALG@doentity}{\noindent\hskip\ALG@tlm}{\ALG@printindent}{}{\errmessage{failed to patch}}
-% \makeatother
-% end vertical rule patch for algorithmicx
-
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-% \iccvfinalcopy % *** Uncomment this line for the final submission
-
-\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\usepackage{mathrsfs}
-\newcommand{\RED}[1]{#1}
-
-\newcommand\TODO[1]{{\color{red}{TODO: #1}}}
-\newcommand\UPDATE[1]{{\color{blue}{#1}}}
-\newcommand\SOURCE[1]{{\color{green}{(from: #1)}}}
-% \newcommand\CHANGED[2]{{{\color{blue}{#1}}\color{green}{#2}}}
-
-\usepackage[dvipsnames]{xcolor}
-\usepackage{enumitem}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ificcvfinal\pagestyle{empty}\fi
-\begin{document}
-
-%%%%%%%%% TITLE
-\title{\LaTeX\ Author Guidelines for ICCV Proceedings}
-
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
-}
-
-\maketitle
-%\thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-   The ABSTRACT is to be in fully-justified italicized text, at the top
-   of the left-hand column, below the author and affiliation
-   information. Use the word ``Abstract'' as the title, in 12-point
-   Times, boldface type, centered relative to the column, initially
-   capitalized. The abstract is to be in 10-point, single-spaced type.
-   Leave two blank lines after the Abstract, then begin the main text.
-   Look at previous ICCV abstracts to get a feel for style and length.
-\end{abstract}
-
-%%%%%%%%% BODY TEXT
 \section{Introduction}
@@
 \end{itemize}
-
-\section{Related work}
-\begin{itemize}
-\item \textit{Optional:} more about \textbf{Mask R-CNN}? (we actually already explain in the introduction why we do not care about it)
-\item \textbf{Proposal-free instance segmentation} methods:
-\begin{itemize}
-\item \textbf{Predict pixel embedding vectors:} 
-\begin{itemize}
-\item For each pixel in the image, a CNN predicts an embedding vector, such that pixels in the same instance are represented by the same vector.
-(\textit{by training a model that labels pixels with unit-length vectors that live in some ﬁxed dimension embedding space} \SOURCE{Rec.
-embeddings} ).
-\textit{With instance embedding, each object is assigned a “color” in a n-dimensional space.
-The network processes the image and produces a dense output, same size as the input image.
-Each pixel in the output of the network is a point in the embedding space.
-Pixels that belong to the same object are close in the embedding space while pixels that belong to different objects are distant in the embedding space.
-Parsing the image embedding space involves some sort of clustering algorithm.} \SOURCE{online}
-\item unsupervised or supervised; different types of loss \TODO{Find good summary}
-\item clustering algorithms like DBSCAN, mean-shift or similar ones working directly in the embedding space  \TODO{Add refs, discuss with Roman}
-\item \textit{Side comment}: Even with pixel embedding vectors we can deduce affinities or signed costs
-\end{itemize}
-\item \textbf{Other methods}: recurrent CNN, deep watershed, InstanceCut, Deep Coloring 2018 \TODO{Add more, discuss with Roman}
-\item \textbf{Predicting long-range affinities:} superhuman, MWS, graph-merge on cityscapes, holistically edge detection (see MWS paper for a good review) \TODO{Add more}
-\end{itemize}
-
-\item So we need a \textbf{graph clustering algorithm}:
-\begin{itemize}
-\item Mention some seeded method?
-\item \textit{Unsigned clustering methods:} Felzenszwalb Efficient Graph-based Image segmentation, (spectral clustering, graph cuts, not sure...)  \TODO{Here I need some input about recent stuff}
-\item \textit{Merge-tree methods:} 
-\begin{itemize}
-\item Hierarchical clustering, ultra-metric contour map...? \TODO{This needs more research}
-\item Only one from pixels I know: GMIS, hierarchical-Felzenszwalb (??) 
-\item most of the others from superpixels
-\item In connectomics: GALA, merge-mistakes (another section for splitting option?)
-\item \textit{Similar to the boundary detection/region segmentation pipeline for natural image segmentation [6,7,8,9], most recent EM image segmentation methods use a membrane detection/cell segmentation pipeline.
-First, a membrane detector generates pixel-wise conﬁdence maps of membrane predictions using local image cues [10,11,12].
-Next, region-based methods are applied to transforming the membrane conﬁdence maps into cell segments.
-It has been shown that region-based methods are necessary for improving the segmentation accuracy from membrane detections for EM images [13].
-A common approach to region-based segmentation is to transform a membrane conﬁdence map into over-segmenting superpixels and use them as “building blocks” for ﬁnal segmentation.
-To correctly combine superpixels, greedy region agglomeration based on certain boundary saliency has been shown to work [14].
-Meanwhile, structures, such as loopy graphs [15,16] or trees [17,18,19], are more often imposed to represent the region merging hierarchy and help transform the superpixel combination search into graph labeling problems.
-To this end, local [17,16] or structured [18,19] learning based methods are developed.} \SOURCE{SSHMT} \SOURCE{Jan Funke Multicut proposals}
-\end{itemize}
-\item \textbf{Signed graph}
-\begin{itemize}
-\item Multicut pipiline and heuristics
-\item Jan Funke proposals
-\item \textit{Cannot-link constraints:} initially introduced as hard-contraints, then relaxed (MWS, Greedy Fixation)
-\item Local-search approximations of MC: GAEC, GreedyFixation
-\end{itemize}
-\end{itemize}
-
-\end{itemize}
-
-\begin{algorithm}
-  \caption{Graph Agglomerative Clustering}
-\setlength{\parindent}{\algorithmicindent} \textbf{Inputs:}
-     \begin{itemize}[leftmargin=1.3cm,topsep=0.1pt,itemsep=-1.ex]
-    %  \setlength\itemsep{0.em}
-   \item $\mathcal{G}(V,E)$ with $|V|=N$, $|E|=M$
-   \item signed edge weights $w:\,E\rightarrow\mathbb{R}$
-   \item {\color{blue}addMustNotLink} $\in \{ True, False\}$
-   \end{itemize}
-   \vspace{0.4em}
-
-\setlength{\parindent}{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$
-
-%   \hspace*{\algorithmicindent} \textbf{Inputs:} $\mathcal{G}(V,E)$ with signed costs $w:\,E\rightarrow\mathbb{R}$. \\
-%   Prova \\
-%   \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$\\
-
-  \hspace*{\algorithmicindent} 
-  \begin{algorithmic}[1]
-
-    % \Procedure{GraphEdgeContr}{{\color{blue}bool \emph{addConstraints}}}
-      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
-      \State $\mathcal{G}'(V', E') \gets \mathcal{G}(V, E)$  \Comment{Contracted graph}
-    %   \State PQ $\gets$ Sort $e\in E$ in descending order of $|w_e|$
-        \State PQ.push$(|w_e|, w_e, e) \quad \forall e \in E $  \Comment{Sort edges by $|w_e|$}
-
-      \State $\Pi \gets \{ \{v_1\}, ..., \{v_N\} \}$ \Comment{Initial clustering}
-      \State $E_\dagger \gets \{\}$ \Comment{Set of must-not-link edges}
-    %   \State PQ.push$(e,  ) \quad \forall e \in E $  
-    \State
-      \While{PQ is \textbf{not} empty}
-        \State $|\tilde{w}|, \tilde{w}, e_{uv} \gets $ PQ.popHighest()
-        \If{ $e_{uv} \notin E' $} 
-            \State \textbf{continue}
-        \EndIf
-        \If{({\color{ForestGreen}\textbf{$\tilde{w} > 0$}}) \textbf{and} ($e_{uv} \notin E_\dagger$)}
-        %   \State $u,v \gets u,v \in V' : $
-        %   \State $S_u \gets S \in \Pi$ : $ u \in S$
-        %   \State $S_v \gets S \in \Pi$ : $ v \in S$
-          \State PQ, $\,E_\dagger,\,\, E' \gets$ \textsc{deleteDoubleEdges}($u,v$)
-        %   \State mergeDoubleEdges($u,v$) \Comment{Update PQ, $E_\dagger, \mathcal{G}'$}
-
-        %   \State Update costs of double edges;
-        %   \State Propagate constrained flags of double edges;
-          \State $V' \gets V' \setminus \{ v\}$, $\quad E' \gets E' \setminus \{ e_{uv}\}$
-        %   \State $ S_u \gets S_u \cup S_v$
-          \State $\Pi \gets \Pi \cup \{ S_u^\Pi \cup S_v^\Pi \} \setminus \{ S_u^\Pi, S_v^\Pi \}$
-          % \For{every new double edge}
-          %   \State Delete double edges
-          %   \State Insert new one with updated cost
-          % \EndFor
-        \EndIf
-        \If{({\color{red}\textbf{$\tilde{w} \leq 0$}}) \textbf{and} {\color{blue}addMustNotLink}}
-          \State $ E_\dagger \gets E_\dagger \cup \{e_{uv} \} $
-        \EndIf
-      \EndWhile
-      \State
-    %   \State
-      \Return $\Pi$
-      % \State
-    % \EndProcedure
-
-  \end{algorithmic}
-  \hspace*{2cm} 
-    \begin{algorithmic}[1]
-
-    \Function{DeleteDoubleEdges}{$u,v$}
-      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
-      \State $\mathcal{N}_u = \{ t \in V' | e_{ut}\in E'  \}$
-      \State $\mathcal{N}_v = \{ t \in V' | e_{vt}\in E'  \}$
-      \For{$t \in \mathcal{N}_u  \cap \mathcal{N}_v$ }
-        \State $|\tilde{w}_1|, \tilde{w}_1, e_1 \gets $ PQ.pop($e_{ut}$)
-        \State $|\tilde{w}_2|, \tilde{w}_2, e_2 \gets $ PQ.pop($e_{vt}$)
-        % \State $e_1, e_2 \gets e_{ut}, e_{vt}$
-        \State $E' \gets E' \setminus \{ e_2\}$ %\Comment{Delete double edge}
-        \If{$e_2 \in E_\dagger $} \Comment{Propagate must-not-link}
-            \State $ E_\dagger \gets E_\dagger \cup \{e_1 \} $
-        \EndIf
-        % \State $\tilde{w}_1, \tilde{w}_2 \gets $ PQ.pop($e_1$), PQ.pop($e_2$)
-        \State $\tilde{w}_{\mathrm{new}} \gets$ \textsc{linkageCriteria}$(\tilde{w}_1, \tilde{w}_2)$
-        \State PQ.push($|\tilde{w}_{\mathrm{new}}|$, $\tilde{w}_{\mathrm{new}}$,  $e_1$)
-
-      \EndFor
-
-      \State
-    %   \State
-      \Return PQ, $E_\dagger, E'$
-    %   % \State
-
-    \EndFunction
-
-  \end{algorithmic}
-
-\end{algorithm}
-
-\section{Grand Unified Edge Contraction Algorithm}
-\begin{itemize}
-\item Define graph formalism
-\item Rows in the table:
-\begin{itemize}
-\item Mutex Watershed (MWS), [proof of equivalence included in Appendix]
-\item Greedy Additive Edge Contraction (GAEC), 
-\item Greedy Fixation (GF), 
-\item Hierarchical Agglomerative Clustering with single, complete, average (UPGMA) and weighted average (WPGMA) linkage criteria
-\item GALA (learned update rule)
-\item Something depending on the node size...?
-\end{itemize}
-\end{itemize}
-
-\section{Experiments}
-\begin{itemize}
-\item Nevertheless, in both approaches we can define a grid graph (each vertex representing a pixel) with signed weights and find the final instance segmentation by using a graph partitioning algorithm:
-\begin{itemize}
-\item In Method 1, the graph is complete and the edge weights represent similarities between pairs of pixel embedding vectors.
-In most proposed approaches, embedding vectors representing distinct instances should be "distant enough" in the embedding space (a minimum distance is usually used during the training of the CNN).
-Thus, this threshold distance can be used to define signed affinities, representing attraction or repulsion between pairs of pixels;
-\item  In Method 2, the short- and long-range affinities predicted by the CNN are directly used as signed edge weights in the grid graph
-\end{itemize}
-\end{itemize}
-
-\subsection{Results summary}
-\begin{itemize}
-\item in the proposed simple formalism for Signed Graph Edge Contraction Clustering, we also include a modified version of Hierarchical agglomerative clustering with cannot-link constraints that was not mentioned in literature so far and in our experiments proved to be quite robust to noise and outliers
-\item we compare different types of Signed Graph Edge Contraction Clustering, showing in which situations is preferable to use one or the other and which one can make a better use of the long-range CNN predictions;
-\item we focus our comparison on efficiency and robustness to mistakes in the CNN predictions 
-\item in general, our experiments show that long-range predictions should be used not only during the CNN training, but also as an input of the clustering algorithm
-
-\end{itemize}
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{egbib}
-}
-
-\section{Supplementary Material}
-\begin{itemize}
-\item Equivalence Mutex Watershed and Greedy Edge Contraction
-\end{itemize}
-
-\end{document}

### 2019-02-22 latex/chapters/rel_work.tex
Restructure repo

--- 2019-02-21 latex/egpaper_for_review.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{iccv}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-
-\usepackage{algorithm}% http://ctan.org/pkg/algorithm
-\PassOptionsToPackage{noend}{algpseudocode}% comment out if want end's to show
-\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
-
-% \newcommand*{\algrule}[1][\algorithmicindent]{\makebox[#1][l]{\hspace*{.5em}\vrule height .75\baselineskip depth .25\baselineskip}}%
-
-% \newcount\ALG@printindent@tempcnta
-% \def\ALG@printindent{%
-%     \ifnum \theALG@nested>0% is there anything to print
-%         \ifx\ALG@text\ALG@x@notext% is this an end group without any text?
-%             % do nothing
-%             \addvspace{-3pt}% FUDGE for cases where no text is shown, to make the rules line up
-%         \else
-%             \unskip
-%             % draw a rule for each indent level
-%             \ALG@printindent@tempcnta=1
-%             \loop
-%                 \algrule[\csname ALG@ind@\the\ALG@printindent@tempcnta\endcsname]%
-%                 \advance \ALG@printindent@tempcnta 1
-%             \ifnum \ALG@printindent@tempcnta<\numexpr\theALG@nested+1\relax% can't do <=, so add one to RHS and use < instead
-%             \repeat
-%         \fi
-%     \fi
-%     }%
-\usepackage{etoolbox}
-% the following line injects our new indent handling code in place of the default spacing
-% \patchcmd{\ALG@doentity}{\noindent\hskip\ALG@tlm}{\ALG@printindent}{}{\errmessage{failed to patch}}
-% \makeatother
-% end vertical rule patch for algorithmicx
-
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-% \iccvfinalcopy % *** Uncomment this line for the final submission
-
-\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\usepackage{mathrsfs}
-\newcommand{\RED}[1]{#1}
-
-\newcommand\TODO[1]{{\color{red}{TODO: #1}}}
-\newcommand\UPDATE[1]{{\color{blue}{#1}}}
-\newcommand\SOURCE[1]{{\color{green}{(from: #1)}}}
-% \newcommand\CHANGED[2]{{{\color{blue}{#1}}\color{green}{#2}}}
-
-\usepackage[dvipsnames]{xcolor}
-\usepackage{enumitem}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ificcvfinal\pagestyle{empty}\fi
-\begin{document}
-
-%%%%%%%%% TITLE
-\title{\LaTeX\ Author Guidelines for ICCV Proceedings}
-
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
-}
-
-\maketitle
-%\thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-   The ABSTRACT is to be in fully-justified italicized text, at the top
-   of the left-hand column, below the author and affiliation
-   information. Use the word ``Abstract'' as the title, in 12-point
-   Times, boldface type, centered relative to the column, initially
-   capitalized. The abstract is to be in 10-point, single-spaced type.
-   Leave two blank lines after the Abstract, then begin the main text.
-   Look at previous ICCV abstracts to get a feel for style and length.
-\end{abstract}
-
-%%%%%%%%% BODY TEXT
-\section{Introduction}
-
-\begin{itemize}
-\item \textbf{Intro about CNN:} \textit{The successes of deep convolutional neural nets (CNNs) at image classiﬁcation has spawned a ﬂurry of work in computer vision on adapting these models to pixel-level image understanding tasks, such as boundary detection [1, 90, 64], semantic segmentation [60, 10, 46], optical ﬂow [87, 20], and pose estimation [85, 7].} \SOURCE{Rec.
-embeddings}
-\item Intro about instance segmentation
-\item \textbf{Mask R-CNN:} why we do not like it 
-\begin{itemize}
-\item \textit{most recent successful approaches to instance segmentation have adopted more heuristic approaches that first use an object detector to enumerate candidate instances and then perform pixel-level segmentation of each instance [57, 17, 55, 56, 2].
-Alternately one can generate generic proposal segments and then label each one with a semantic detector [31, 12, 32, 16, 82, 34].
-In either case the detection and segmentation steps can both be mapped to standard binary classiﬁcation losses.
-While effective, these approaches are somewhat unsatisfying since: (1) they rely on the object detector and non-maximum suppression heuristics to accurately “count” the number of instances, (2) they are difﬁcult to train in an end-to-end manner since the interface between instance segmentation and detection is non-differentiable, and (3) they underperform in cluttered scenes as the assignment of pixels to detections is carried out independently for each detection 1.} \SOURCE{Rec.
-embeddings}
-\item elongated segments
-\item \textit{There are three fundamental flaws in a proposal-based instance segmentation architecture.
-First, two objects may share the same bounding box, or a very similar boxes.
-In this case, the mask head, has no way of telling which object to pick in the box.
-This is a serious problem with stringy like object that have low fill rate in their bounding box (e.g.
-bicycles and chairs).
-Second, there is nothing in the architecture preventing a pixel to be shared between two instance.
-Third, the number of instances is limited by the number of proposals processed by the network (usually hundreds).
-More over, the architecture is complex and hard to tune and “debug”.
-In object detection, a precursor to this problem, there are already successes being made to use a simpler, single-stage, architectures e.g.
-RetinaNet.}
-\end{itemize}
-
-\item Briefly mention methods for proposal free (pixel embedding vectors, recurrent, more in related work)
-
-\item Among successful methods: \textbf{predict short and long-range affinities}
-\begin{itemize}
-\item for each pixel we fix a set of neighboring pixels (not necessarily limited to the direct neighbors);  a CNN predicts then affinities, that represent how likely it is for each pair of neighboring pixels to be in the same instance.
-\item The final segmentation is obtained by using some kind of graph clustering algorithm
-\item \textbf{Motivation to use this method:} GMIS achieved comparable results to methods based on object proposal like Mask-R-CNN on natural images (Cityscapes);  MWS achieved SOA results on a biological images (ISBI)
-\end{itemize}
-\item It was shown that it is good to describe the problem in terms of a signed graph clustering problem (see MWS and others): directly train CNN to predict \textbf{repulsion and attraction}; no need to define seeds or to fix a threshold given an hierarchy of clusters, etc...
-
-\item \textit{\textbf{Multicut} has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region.
-Its great drawback is that its optimization is NP-hard.} \SOURCE{MWS}.
-\item Problem: this specific application is too expensive even for recently proposed multicut heuristics/ approximations
-\item Efficient alternatives proposed independently (leave details to the related work), but: missing comparison on this type of problem/graph
-\item our contributions:
-\begin{itemize}
-\item we propose a unified and simple formalization of Signed Graph Edge Contraction Clustering and show how many of the recently proposed methods can be seen as special cases
-\item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and energy) 
-\item we propose a new a constrained version of average agglomerative clustering that proved to be quite robust in most of our experiments
-\end{itemize}
-\item on other datasets (connectomics) many methods are based on multi-step pipelines first predicting superpixels
-\item \textit{if we get decent scores on CREMI}: we show that also on neuro-data it is worth to skip the hand-crafted superpixel step and compute the final segmentation directly from the CNN predictions (MWS already showed it on ISBI)
-
-\end{itemize}
-
 \section{Related work}
@@
 \end{itemize}
-
-\begin{algorithm}
-  \caption{Graph Agglomerative Clustering}
-\setlength{\parindent}{\algorithmicindent} \textbf{Inputs:}
-     \begin{itemize}[leftmargin=1.3cm,topsep=0.1pt,itemsep=-1.ex]
-    %  \setlength\itemsep{0.em}
-   \item $\mathcal{G}(V,E)$ with $|V|=N$, $|E|=M$
-   \item signed edge weights $w:\,E\rightarrow\mathbb{R}$
-   \item {\color{blue}addMustNotLink} $\in \{ True, False\}$
-   \end{itemize}
-   \vspace{0.4em}
-
-\setlength{\parindent}{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$
-
-%   \hspace*{\algorithmicindent} \textbf{Inputs:} $\mathcal{G}(V,E)$ with signed costs $w:\,E\rightarrow\mathbb{R}$. \\
-%   Prova \\
-%   \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$\\
-
-  \hspace*{\algorithmicindent} 
-  \begin{algorithmic}[1]
-
-    % \Procedure{GraphEdgeContr}{{\color{blue}bool \emph{addConstraints}}}
-      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
-      \State $\mathcal{G}'(V', E') \gets \mathcal{G}(V, E)$  \Comment{Contracted graph}
-    %   \State PQ $\gets$ Sort $e\in E$ in descending order of $|w_e|$
-        \State PQ.push$(|w_e|, w_e, e) \quad \forall e \in E $  \Comment{Sort edges by $|w_e|$}
-
-      \State $\Pi \gets \{ \{v_1\}, ..., \{v_N\} \}$ \Comment{Initial clustering}
-      \State $E_\dagger \gets \{\}$ \Comment{Set of must-not-link edges}
-    %   \State PQ.push$(e,  ) \quad \forall e \in E $  
-    \State
-      \While{PQ is \textbf{not} empty}
-        \State $|\tilde{w}|, \tilde{w}, e_{uv} \gets $ PQ.popHighest()
-        \If{ $e_{uv} \notin E' $} 
-            \State \textbf{continue}
-        \EndIf
-        \If{({\color{ForestGreen}\textbf{$\tilde{w} > 0$}}) \textbf{and} ($e_{uv} \notin E_\dagger$)}
-        %   \State $u,v \gets u,v \in V' : $
-        %   \State $S_u \gets S \in \Pi$ : $ u \in S$
-        %   \State $S_v \gets S \in \Pi$ : $ v \in S$
-          \State PQ, $\,E_\dagger,\,\, E' \gets$ \textsc{deleteDoubleEdges}($u,v$)
-        %   \State mergeDoubleEdges($u,v$) \Comment{Update PQ, $E_\dagger, \mathcal{G}'$}
-
-        %   \State Update costs of double edges;
-        %   \State Propagate constrained flags of double edges;
-          \State $V' \gets V' \setminus \{ v\}$, $\quad E' \gets E' \setminus \{ e_{uv}\}$
-        %   \State $ S_u \gets S_u \cup S_v$
-          \State $\Pi \gets \Pi \cup \{ S_u^\Pi \cup S_v^\Pi \} \setminus \{ S_u^\Pi, S_v^\Pi \}$
-          % \For{every new double edge}
-          %   \State Delete double edges
-          %   \State Insert new one with updated cost
-          % \EndFor
-        \EndIf
-        \If{({\color{red}\textbf{$\tilde{w} \leq 0$}}) \textbf{and} {\color{blue}addMustNotLink}}
-          \State $ E_\dagger \gets E_\dagger \cup \{e_{uv} \} $
-        \EndIf
-      \EndWhile
-      \State
-    %   \State
-      \Return $\Pi$
-      % \State
-    % \EndProcedure
-
-  \end{algorithmic}
-  \hspace*{2cm} 
-    \begin{algorithmic}[1]
-
-    \Function{DeleteDoubleEdges}{$u,v$}
-      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
-      \State $\mathcal{N}_u = \{ t \in V' | e_{ut}\in E'  \}$
-      \State $\mathcal{N}_v = \{ t \in V' | e_{vt}\in E'  \}$
-      \For{$t \in \mathcal{N}_u  \cap \mathcal{N}_v$ }
-        \State $|\tilde{w}_1|, \tilde{w}_1, e_1 \gets $ PQ.pop($e_{ut}$)
-        \State $|\tilde{w}_2|, \tilde{w}_2, e_2 \gets $ PQ.pop($e_{vt}$)
-        % \State $e_1, e_2 \gets e_{ut}, e_{vt}$
-        \State $E' \gets E' \setminus \{ e_2\}$ %\Comment{Delete double edge}
-        \If{$e_2 \in E_\dagger $} \Comment{Propagate must-not-link}
-            \State $ E_\dagger \gets E_\dagger \cup \{e_1 \} $
-        \EndIf
-        % \State $\tilde{w}_1, \tilde{w}_2 \gets $ PQ.pop($e_1$), PQ.pop($e_2$)
-        \State $\tilde{w}_{\mathrm{new}} \gets$ \textsc{linkageCriteria}$(\tilde{w}_1, \tilde{w}_2)$
-        \State PQ.push($|\tilde{w}_{\mathrm{new}}|$, $\tilde{w}_{\mathrm{new}}$,  $e_1$)
-
-      \EndFor
-
-      \State
-    %   \State
-      \Return PQ, $E_\dagger, E'$
-    %   % \State
-
-    \EndFunction
-
-  \end{algorithmic}
-
-\end{algorithm}
-
-\section{Grand Unified Edge Contraction Algorithm}
-\begin{itemize}
-\item Define graph formalism
-\item Rows in the table:
-\begin{itemize}
-\item Mutex Watershed (MWS), [proof of equivalence included in Appendix]
-\item Greedy Additive Edge Contraction (GAEC), 
-\item Greedy Fixation (GF), 
-\item Hierarchical Agglomerative Clustering with single, complete, average (UPGMA) and weighted average (WPGMA) linkage criteria
-\item GALA (learned update rule)
-\item Something depending on the node size...?
-\end{itemize}
-\end{itemize}
-
-\section{Experiments}
-\begin{itemize}
-\item Nevertheless, in both approaches we can define a grid graph (each vertex representing a pixel) with signed weights and find the final instance segmentation by using a graph partitioning algorithm:
-\begin{itemize}
-\item In Method 1, the graph is complete and the edge weights represent similarities between pairs of pixel embedding vectors.
-In most proposed approaches, embedding vectors representing distinct instances should be "distant enough" in the embedding space (a minimum distance is usually used during the training of the CNN).
-Thus, this threshold distance can be used to define signed affinities, representing attraction or repulsion between pairs of pixels;
-\item  In Method 2, the short- and long-range affinities predicted by the CNN are directly used as signed edge weights in the grid graph
-\end{itemize}
-\end{itemize}
-
-\subsection{Results summary}
-\begin{itemize}
-\item in the proposed simple formalism for Signed Graph Edge Contraction Clustering, we also include a modified version of Hierarchical agglomerative clustering with cannot-link constraints that was not mentioned in literature so far and in our experiments proved to be quite robust to noise and outliers
-\item we compare different types of Signed Graph Edge Contraction Clustering, showing in which situations is preferable to use one or the other and which one can make a better use of the long-range CNN predictions;
-\item we focus our comparison on efficiency and robustness to mistakes in the CNN predictions 
-\item in general, our experiments show that long-range predictions should be used not only during the CNN training, but also as an input of the clustering algorithm
-
-\end{itemize}
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{egbib}
-}
-
-\section{Supplementary Material}
-\begin{itemize}
-\item Equivalence Mutex Watershed and Greedy Edge Contraction
-\end{itemize}
-
-\end{document}

### 2019-02-22 latex/chapters/intro.tex
Start adding citations

@@
+% !TEX root = ../agglo_clust_review.tex
+
 \section{Introduction}
@@
 \begin{itemize}
-\item \textbf{Intro about CNN:} \textit{The successes of deep convolutional neural nets (CNNs) at image classiﬁcation has spawned a ﬂurry of work in computer vision on adapting these models to pixel-level image understanding tasks, such as boundary detection [1, 90, 64], semantic segmentation [60, 10, 46], optical ﬂow [87, 20], and pose estimation [85, 7].} \SOURCE{Rec.
-embeddings}
-\item Intro about instance segmentation
-\item \textbf{Mask R-CNN:} why we do not like it 
+\item \textbf{General intro about CNN:} big success in pixel-level image understanding tasks: boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, semantic segmentation \cite{long2015fully,chen2018deeplab,kong2018recurrent}, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet}, and pose estimation \cite{wei2016convolutional,cao2017realtime}
+% \SOURCE{\cite{kong2018recurrent}}
+\item Many recent successful methods generate \textbf{region proposals} and classify the objects in the bounding box \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}
+\item \emph{Why we do not like them}:
 \begin{itemize}
-\item \textit{most recent successful approaches to instance segmentation have adopted more heuristic approaches that first use an object detector to enumerate candidate instances and then perform pixel-level segmentation of each instance [57, 17, 55, 56, 2].
-Alternately one can generate generic proposal segments and then label each one with a semantic detector [31, 12, 32, 16, 82, 34].
-In either case the detection and segmentation steps can both be mapped to standard binary classiﬁcation losses.
-While effective, these approaches are somewhat unsatisfying since: (1) they rely on the object detector and non-maximum suppression heuristics to accurately “count” the number of instances, (2) they are difﬁcult to train in an end-to-end manner since the interface between instance segmentation and detection is non-differentiable, and (3) they underperform in cluttered scenes as the assignment of pixels to detections is carried out independently for each detection 1.} \SOURCE{Rec.
-embeddings}
-\item elongated segments
-\item \textit{There are three fundamental flaws in a proposal-based instance segmentation architecture.
-First, two objects may share the same bounding box, or a very similar boxes.
-In this case, the mask head, has no way of telling which object to pick in the box.
-This is a serious problem with stringy like object that have low fill rate in their bounding box (e.g.
-bicycles and chairs).
-Second, there is nothing in the architecture preventing a pixel to be shared between two instance.
-Third, the number of instances is limited by the number of proposals processed by the network (usually hundreds).
-More over, the architecture is complex and hard to tune and “debug”.
-In object detection, a precursor to this problem, there are already successes being made to use a simpler, single-stage, architectures e.g.
-RetinaNet.}
+\item rely on the object detector and non-maximum suppression heuristics to accurately “count” nb. of instances, 
+\item difficult to train in an end-to-end manner: interface between instance segmentation and detection is non-differentiable
+\item underperform in cluttered scenes (assignment carried out independently for each detection) 
+\item not usable for wiry or articulated segments/objects 
+\item nothing in the architecture preventing a pixel to be shared between two instances
+\item number of instances is limited by nb. proposals processed by CNN (usually hundreds). 
+% \item (architecture is complex and hard to tune and “debug”...?)
 \end{itemize}
 
-\item Briefly mention methods for proposal free (pixel embedding vectors, recurrent, more in related work)
+\item Among successful \textbf{proposal-free methods} there are: predict pixel embedding vectors \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; predict short- and long-range affinities \cite{liu2018affinity,wolf2018mutex,xie2015holistically}
 
-\item Among successful methods: \textbf{predict short and long-range affinities}
-\begin{itemize}
-\item for each pixel we fix a set of neighboring pixels (not necessarily limited to the direct neighbors);  a CNN predicts then affinities, that represent how likely it is for each pair of neighboring pixels to be in the same instance.
-\item The final segmentation is obtained by using some kind of graph clustering algorithm
-\item \textbf{Motivation to use this method:} GMIS achieved comparable results to methods based on object proposal like Mask-R-CNN on natural images (Cityscapes);  MWS achieved SOA results on a biological images (ISBI)
-\end{itemize}
-\item It was shown that it is good to describe the problem in terms of a signed graph clustering problem (see MWS and others): directly train CNN to predict \textbf{repulsion and attraction}; no need to define seeds or to fix a threshold given an hierarchy of clusters, etc...
-
-\item \textit{\textbf{Multicut} has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region.
-Its great drawback is that its optimization is NP-hard.} \SOURCE{MWS}.
-\item Problem: this specific application is too expensive even for recently proposed multicut heuristics/ approximations
-\item Efficient alternatives proposed independently (leave details to the related work), but: missing comparison on this type of problem/graph
+\item In both approaches we can obtain the final segmentation by using a \textbf{graph clustering algorithm}
+\item Recent work (\cite{wolf2018mutex}, more?) shows that it is better to use \textbf{repulsion and attraction} (directly predict it with the classifier, no need to define seeds or to fix a threshold given an hierarchy of clusters)
+\item solving correlation clustering problem (multicut) is too expensive for this application (even using recently proposed heuristics)
 \item our contributions:
 \begin{itemize}
-\item we propose a unified and simple formalization of Signed Graph Edge Contraction Clustering and show how many of the recently proposed methods can be seen as special cases
+\item we propose a unified and simple formalization of Agglomerative Clustering and show how many of the recently proposed methods can be seen as special cases
+\item we propose several new clustering algorithms, among which one proved to be robust in our experiments (average linkage with must-not-link-edges)
 \item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and energy)
-\item we propose a new a constrained version of average agglomerative clustering that proved to be quite robust in most of our experiments
+
 \end{itemize}

### 2019-02-22 latex/chapters/rel_work.tex
Start adding citations

@@
+% !TEX root = ../agglo_clust_review.tex
+
 \section{Related work}
 \begin{itemize}
-\item \textit{Optional:} more about \textbf{Mask R-CNN}? (we actually already explain in the introduction why we do not care about it)
-\item \textbf{Proposal-free instance segmentation} methods:
+\item \textbf{Proposal based methods} 
 \begin{itemize}
-\item \textbf{Predict pixel embedding vectors:} 
+\item Generate region proposals or bounding boxes and classify the objects in the bounding box \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}; fully convolutional  box proposals \cite{li2017fully}.
+\item \emph{More references:} use an object detector to enumerate candidate instances and then perform pixel-level segmentation of each instance \cite{liang2018proposal,dai2016instance,li2017fully,liang2016reversible,arnab2017pixelwise} or generate generic proposal segments and then label each one with a semantic detector \cite{hariharan2014simultaneous,chen2015multi,hariharan2015hypercolumns,dai2015convolutional,uhrig2016pixel,he2017mask}.
+% \SOURCE{\cite{kong2018recurrent}
+\end{itemize}
+
+\item \textbf{Other proposal-free methods:} 
 \begin{itemize}
-\item For each pixel in the image, a CNN predicts an embedding vector, such that pixels in the same instance are represented by the same vector.
+\item box-free \cite{pinheiro2015learning,pinheiro2016learning,liang2018proposal,hu2017fastmask}; joint segmentation and instance labeling jointly in a combinatorial framework \cite{kirillov2017instancecut}; recurrent models \cite{romera2016recurrent,ren2017end}
+\item \textbf{Pixel embedding vectors}: supervised vectors \cite{bai2017deep,liu2017sgn}, unsupervised vectors  \cite{fathi2017semantic,newell2017associative,de2017semantic}, end-to-end training \cite{kong2018recurrent}, embedding depending on scene depth \cite{uhrig2016pixel}, TO CHECK: \cite{sironi2014multiscale}; \TODO{more on pose estimation, vector distance transform, deep coloring?, ECCV semi-convolutions}
+% different types of loss
+% \item For each pixel in the image, a CNN predicts an embedding vector, such that pixels in the same instance are represented by the same vector.
 (\textit{by training a model that labels pixels with unit-length vectors that live in some ﬁxed dimension embedding space} \SOURCE{Rec.
@@
 Parsing the image embedding space involves some sort of clustering algorithm.} \SOURCE{online}
-\item unsupervised or supervised; different types of loss \TODO{Find good summary}
-\item clustering algorithms like DBSCAN, mean-shift or similar ones working directly in the embedding space  \TODO{Add refs, discuss with Roman}
-\item \textit{Side comment}: Even with pixel embedding vectors we can deduce affinities or signed costs
-\end{itemize}
-\item \textbf{Other methods}: recurrent CNN, deep watershed, InstanceCut, Deep Coloring 2018 \TODO{Add more, discuss with Roman}
-\item \textbf{Predicting long-range affinities:} superhuman, MWS, graph-merge on cityscapes, holistically edge detection (see MWS paper for a good review) \TODO{Add more}
+
+% \item Clustering methods: DBSCAN, more
+
+\item \textbf{Most related: predict short- and long-range affinities}.
+For each pixel we fix a set of neighboring pixels (not necessarily limited to the direct neighbors) and CNN predicts how likely it is for each pixel pair to be in the same instance \cite{liu2018affinity,wolf2018mutex,lee2017superhuman,xie2015holistically,Maire_2016_CVPR}
+% \item \cite{liu2018affinity} achieved comparable results to methods based on object proposal like Mask-R-CNN on natural images (Cityscapes); \cite{wolf2018mutex} achieved SOA results on a biological images (ISBI)
+% \item Side comment: Even with pixel embedding vectors we can deduce affinities or signed costs
+% (see MWS paper for a good review)
+
 \end{itemize}
 
-\item So we need a \textbf{graph clustering algorithm}:
+\item \textbf{Graph clustering related work}:
 \begin{itemize}
-\item Mention some seeded method?
-\item \textit{Unsigned clustering methods:} Felzenszwalb Efficient Graph-based Image segmentation, (spectral clustering, graph cuts, not sure...)  \TODO{Here I need some input about recent stuff}
+\item Some seeded methods?
+\item \textit{Unsigned clustering methods:} Efficient Graph-based Image segmentation \cite{felzenszwalb2004efficient}, old graph cut stuff: \cite{shi2000normalized} \TODO{More} 
+ % (spectral clustering, graph cuts...)} 
 \item \textit{Merge-tree methods:} 
 \begin{itemize}
-\item Hierarchical clustering, ultra-metric contour map...? \TODO{This needs more research}
-\item Only one from pixels I know: GMIS, hierarchical-Felzenszwalb (??) 
+\item Hierarchical clustering, ultra-metric contour map \TODO{more}
+\item Methods starting from pixels: \cite{liu2018affinity}, % check HIerarchical Felzenswalb
 \item most of the others from superpixels
@@
 \item Multicut pipiline and heuristics
+% \item \textit{\textbf{Multicut} has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region.
+Its great drawback is that its optimization is NP-hard.} \SOURCE{MWS}.
+
 \item Jan Funke proposals
-\item \textit{Cannot-link constraints:} initially introduced as hard-contraints, then relaxed (MWS, Greedy Fixation)
-\item Local-search approximations of MC: GAEC, GreedyFixation
+\item \textit{Must-not-link edges:} initially introduced as hard-constraints \cite{malmberg2011generalized}, then relaxed \cite{wolf2018mutex,levinkov2017comparative}
+\item Local-search approximations of MC: greeedy fixation and greedy additive edge contraction \cite{levinkov2017comparative}
 \end{itemize}

### 2019-02-24 latex/agglo_clust_review.tex
Start adding citations
Add related work and section 4

@@
 
+% \section{Algorithm}
 \section{Grand Unified Whatever Clustering}
@@
 \item Define graph formalism and clustering $\Pi$
-\item \TODO{Description of the algorithm}
-\item Linkage criteria and table:
+\item Description and pseudo-code
+\item Linkage criteria in the table:
 \begin{itemize}
-\item Mutex Watershed (MWS), [proof of equivalence included in Appendix]
-\item Greedy Additive Edge Contraction (GAEC), 
-\item Greedy Fixation (GF), 
-\item Hierarchical Agglomerative Clustering with single, complete, average (UPGMA) and weighted average (WPGMA) linkage criteria
-\item GALA (learned update rule)
-\item Something depending on the node size...?
+\item Mutex Watershed \cite{wolf2018mutex}, [proof of equivalence included in Appendix]
+\item Greedy Additive Edge Contraction \cite{levinkov2017comparative}, 
+\item Greedy Fixation \cite{levinkov2017comparative}, 
+\item Hierarchical Agglomerative Clustering with single, complete, average (UPGMA) linkage criteria
 \end{itemize}
-\item Pseudocode does not (exactly) include more general options: size of the nodes, features for CNN, histogram for median \TODO{But I think I should keep it simple}
-\item Comment about must-not-link relations: they give high proprity to the most confident repulsive edges \item I don't think I need to mention the merge tree (although it could be easily deduced from the code, as a sequence of clustering)
-\item Define multicut energy (or move to following section)
+\item Easily generalizable for: learned linkage criteria \cite{nunez2013machine}, something depending on node size \cite{felzenszwalb2004efficient}, quantiles, weighted average (WPGMA) and weighted sum
+
+\item Comment about must-not-link relations: they give high priority to the most confident repulsive edges 
+\item I don't think I need to mention the merge tree (although it could be easily deduced from the code, as a sequence of clustering)
+\item comment about complexity (depends on the linkage criteria) and how dense is the graph (check PQ update)
 \end{itemize}
@@
 \begin{itemize}
-\item Nevertheless, in both approaches we can define a grid graph (each vertex representing a pixel) with signed weights and find the final instance segmentation by using a graph partitioning algorithm:
+\item define pixel grid graph and long range connections
+\item probability of long-range connections
+\end{itemize}
+\subsection{Qualitative comparison}
 \begin{itemize}
-\item In Method 1, the graph is complete and the edge weights represent similarities between pairs of pixel embedding vectors.
-In most proposed approaches, embedding vectors representing distinct instances should be "distant enough" in the embedding space (a minimum distance is usually used during the training of the CNN).
-Thus, this threshold distance can be used to define signed affinities, representing attraction or repulsion between pairs of pixels;
-\item  In Method 2, the short- and long-range affinities predicted by the CNN are directly used as signed edge weights in the grid graph
+\item find good way to represent agglomeration order
+\item can we display the must-not-link edges...?
 \end{itemize}
-\end{itemize}
+\subsection{Noise experiments}
 
-\subsection{Results summary}
-\begin{itemize}
-\item in the proposed simple formalism for Signed Graph Edge Contraction Clustering, we also include a modified version of Hierarchical agglomerative clustering with cannot-link constraints that was not mentioned in literature so far and in our experiments proved to be quite robust to noise and outliers
-\item we compare different types of Signed Graph Edge Contraction Clustering, showing in which situations is preferable to use one or the other and which one can make a better use of the long-range CNN predictions;
-\item we focus our comparison on efficiency and robustness to mistakes in the CNN predictions 
-\item in general, our experiments show that long-range predictions should be used not only during the CNN training, but also as an input of the clustering algorithm
+\subsection{Comparison on CREMI and cityscapes}
 
-\end{itemize}
+\section{Conclusions}
 

### 2019-02-24 latex/chapters/intro.tex
Add related work and section 4

@@
 \begin{itemize}
-\item \textbf{General intro about CNN:} big success in pixel-level image understanding tasks: boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, semantic segmentation \cite{long2015fully,chen2018deeplab,kong2018recurrent}, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet}, and pose estimation \cite{wei2016convolutional,cao2017realtime}
+\item \textbf{General intro about CNN:} big success in pixel-level image understanding tasks: boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, semantic segmentation \cite{long2015fully,chen2018deeplab,kong2018recurrent}, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet}, pose estimation \cite{wei2016convolutional,cao2017realtime}...
 % \SOURCE{\cite{kong2018recurrent}}
@@
 \item rely on the object detector and non-maximum suppression heuristics to accurately “count” nb. of instances, 
-\item difficult to train in an end-to-end manner: interface between instance segmentation and detection is non-differentiable
 \item underperform in cluttered scenes (assignment carried out independently for each detection) 
@@
 \item number of instances is limited by nb. proposals processed by CNN (usually hundreds). 
+\item (difficult to train in an end-to-end manner: interface between instance segmentation and detection is non-differentiable)
 % \item (architecture is complex and hard to tune and “debug”...?)
@@
 
-\item Among successful \textbf{proposal-free methods} there are: predict pixel embedding vectors \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; predict short- and long-range affinities \cite{liu2018affinity,wolf2018mutex,xie2015holistically}
+\item Among successful \textbf{proposal-free methods} there are: predict pixel embedding vectors \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; predict short- and long-range affinities \cite{liu2018affinity,wolf2018mutex,xie2015holistically} (more details in related work)
 
@@
 \item on other datasets (connectomics) many methods are based on multi-step pipelines first predicting superpixels
-\item \textit{if we get decent scores on CREMI}: we show that also on neuro-data it is worth to skip the hand-crafted superpixel step and compute the final segmentation directly from the CNN predictions (MWS already showed it on ISBI)
+\item \textit{if we get good scores on CREMI}: we show that also on neuro-data it is worth to skip the hand-crafted superpixel step and compute the final segmentation directly from the CNN affinities (MWS already showed it on the ISBI dataset)
 

### 2019-03-07 latex/chapters/intro.tex
Add more details to exp. sect

@@
 \section{Introduction}
+On possible selling story could be: currently many of the successful proposal-free instance segmentation methods rely on a final clustering step on a grid-graph with both short and long-range connections.
+So it is worth to study this problem in more details.
 
@@
 \item In both approaches we can obtain the final segmentation by using a \textbf{graph clustering algorithm}
-\item Recent work (\cite{wolf2018mutex}, more?) shows that it is better to use \textbf{repulsion and attraction} (directly predict it with the classifier, no need to define seeds or to fix a threshold given an hierarchy of clusters)
+\item Recent work (\cite{wolf2018mutex}, more...) shows that it is better to use \textbf{repulsion and attraction} (directly predict it with the classifier, no need to define seeds or to fix a threshold given an hierarchy of clusters)
 \item solving correlation clustering problem (multicut) is too expensive for this application (even using recently proposed heuristics)
@@
 \begin{itemize}
-\item we propose a unified and simple formalization of Agglomerative Clustering and show how many of the recently proposed methods can be seen as special cases
+\item we propose a unified and simple formalization of Agglomerative Clustering and show how many of the recently proposed methods can be seen as special cases (focusing in particular on signed graphs) (\textbf{review and comparison paper})
 \item we propose several new clustering algorithms, among which one proved to be robust in our experiments (average linkage with must-not-link-edges)
-\item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and energy)
+\item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and MC energy)
 

### 2019-03-14 latex/chapters/3_algorithm.tex
Restructure algorithm section; add chapter files

% !TEX root = ../agglo_clust_review.tex

\begin{figure}
\centering
\includegraphics[width=0.50\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/edge_contraction.png}
\caption{\small 
Example of edge contraction: the edge $e_{uv}$ is selected from priority queue; after nodes $u$ and $v$ are merged and $e_{uv}$ is deleted, there are two double edges $e_1$ and $e_2$ left in the graph.  \TODO{Rotate drawings to optimize space}
\label{fig:example_non_unique_weights_1}}
\end{figure}

\begin{algorithm}
  \caption{General Unified Agglomerative Clustering}
   \hspace*{\algorithmicindent} \textbf{Inputs:} graph $\mathcal{G}(V,E,W)$; bool {\color{blue}\texttt{addCannotLink}}  \\
  \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering and contracted graph $\mathcal{G}'$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]

    % \Procedure{SignedGraphEdgeContr}{{\color{blue}bool \emph{addConstraints}}}
      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
      \State Initialize contracted graph $\mathcal{G}'(V',E')$ from $\mathcal{G}$
      \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
      \State Sort edges in priority queue (PQ) in desc. order of $|W_e|$ 
      \State
      \While{PQ is \textbf{not} empty}
        \State Pop edge $e_{uv}\in E'$ with highest abs. priority $|\tilde{w}|$
        \State
        \If{({\color{ForestGreen}\textbf{$\tilde{w} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}

          % \State PQ, $\,E_\dagger,\,\, E' \gets$ \textsc{deleteDoubleEdges}($u,v$)

        %   \State Update costs of double edges;
        %   \State Propagate constrained flags of double edges;
          \State Contract $e_{uv}$ in $\mathcal{G}'$
          \For{every new pair of double edges $(e_1,e_2)$}
            \State Get priorities $\tilde{w}_1, \tilde{w}_2$ of $e_1,e_2$
            \State Use update rule $f(\tilde{w}_1,\tilde{w}_2)$ (see Table 1) to 
            \Statex \hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent} update priority of $e_1$
            \State Delete $e_2$ from $\mathcal{G}'$
          \EndFor
          % \State  Replace double edges in $\mathcal{G}'$ with single edges
          % \Statex \hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent} and update priorities
        \EndIf
        \State
        \If{({\color{red}\textbf{$\tilde{w} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
          % \State Flag $e_{uv}$ as MustNotLink
          \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
        \EndIf
      \EndWhile

      % \For{$e  \in E$ in descending order of absolute costs $|W(e)|$}
      %   \If{({\color{ForestGreen}\textbf{$W(e) > 0$}}) \textbf{AND} (edge is not constrained)}
      %     \State Contract edge $e$ in the graph $\mathcal{G}'$;
      %     \State Update costs of double edges;
      %     \State Propagate constrained flags of double edges;
      %     % \For{every new double edge}
      %     %   \State Delete double edges
      %     %   \State Insert new one with updated cost
      %     % \EndFor
      %   \EndIf
      %   \If{({\color{red}\textbf{$W(e) \leq 0$}}) \textbf{AND} ({\color{blue}\emph{addConstraints}})}
      %     \State Flag edge $e$ as constrained
      %   \EndIf
      % \EndFor
      \State
      \State
      \Return $\mathcal{G}'$
      % \State

    % \EndProcedure

  \end{algorithmic}
  \label{main_alg}
\end{algorithm}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/aggl_clust.png}
\caption{\small 
Example of agglomerative clustering on signed graph with sum update rule and without Cannot-Link-Constraints. The final clustering is given by one single cluster.
\label{fig:example_non_unique_weights_1}}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.50\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/aggl_clust_with_nonlink.png}
\caption{\small 
Example of agglomerative clustering on signed graph with sum update rule and using Cannot-Link-Constraints. Edges flagged with \texttt{canBeMerged} = \texttt{False} are highlighted in pink. 
\label{fig:example_non_unique_weights_2}}
\end{figure}

\begin{table*}[h]
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{r l || c | c | c}
            % \toprule\toprule
             & &  \multirow{3}{*}{\textbf{Unsigned graphs}}  & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
            % \cmidrule(l{.15em}){4-5}
            % \cline{4-5}
            & & &  \multicolumn{2}{c}{\thead{Use Cannot-Link-Constraints:}} \\

            & & &  \thead{NO} & \thead{YES} \\        
            % \cmidrule[0.3em]{3-5}
            % \midrule[0.15em]
            \midrule\midrule
            Sum: & $f(\tilde{w}_1,\tilde{w}_2) = \tilde{w}_1+\tilde{w}_2$ & \thead{Sum Linkage\\Hierarchical Clustering} & \thead{Greedy Additive \\ Edge Contraction \cite{levinkov2017comparative}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} \\ \midrule

            \makecell[r]{Absolute \\ maximum:} & \makecell[l]{$f(\tilde{w}_1,\tilde{w}_2) =\argmax_{\tilde{w}\in\{\tilde{w}_{1},\tilde{w}_{2}\}} \big|\tilde{w} \big| $}   & \thead{Single Linkage\\Hierarchical Clustering\\ \cite{lance1967general}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Mutex Watershed \cite{wolf2018mutex}} \\ \midrule

            \makecell[r]{Arithmetic \\mean:} & $f(\tilde{w}_1,\tilde{w}_2) = \mathrm{weightedAvg}\{ \tilde{w}_1, \tilde{w}_2 \} $                                 & \thead{ Average Linkage\\ Hierarchical Clustering \\(UPGMA) \cite{lance1967general}} & \thead{Signed Agglomerative Clust. \\ with Average Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule

            Maximum: & $f(\tilde{w}_1,\tilde{w}_2) = \max \{ \tilde{w}_1, \tilde{w}_2 \}  $                                 & \thead{Single Linkage\\Hierarchical Clustering\\ \cite{lance1967general}} & \thead{Signed Agglomerative Clust. \\ with Single Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule

            Minimum:& $f(\tilde{w}_1,\tilde{w}_2) = \min \{ \tilde{w}_1, \tilde{w}_2 \}  $                                 & \thead{Complete Linkage\\ Hierarchical Clustering \\ \cite{lance1967general}}  & \thead{Signed Agglomerative Clust. \\ with Complete Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{The table lists all the algorithms that can be seen as special cases of the Generic Agglomerative Clustering \ref{main_alg} given a specific update rule $f(e_1,e_2)$ and a type of graph...}
    \label{tab:linkage-criteria}
\end{table*}

\section{General Unified Agglomerative Clustering Algorithm (GUACA)}
In this section we introduce a unified agglomerative clustering algorithm that represents a simple generalized formalization of many agglomerative graph clustering algorithms. It can be used to describe both unsigned clustering algorithms ingesting positive similarities between clusters and signed clustering algorithms using attractive and repulsive cues.\\
First, we define the graph notation and the concept of cannot-link constraints. Then, we introduce the generalized algorithm and show \UPDATE{how it can be used to introduce several new agglomerative clustering algorithms for graphs with signed weights.}

\subsection{Graph notation and cannot-link constraints}

\begin{itemize}
\item Define graph formalism and clustering $\Pi$. Make comment about special case of unsigned graph!
\item Introduce concept of cannot-link-constraints
\item From wiki: \emph{Both a must-link and a cannot-link constraint define a relationship between two data instances. A must-link constraint is used to specify that the two instances in the must-link relation should be associated with the same cluster. A cannot-link constraint is used to specify that the two instances in the cannot-link relation should not be associated with the same cluster. These sets of constraints acts as a guide for which a constrained clustering algorithm will attempt to find clusters in a data set which satisfy the specified must-link and cannot-link constraints. Some constrained clustering algorithms will abort if no such clustering exists which satisfies the specified constraints. Others will try to minimize the amount of constraint violation should it be impossible to find a clustering which satisfies the constraints.}

\end{itemize}
\subsection{The algorithm}
\begin{itemize}
\item First give intuitive idea of agglomerative clustering
\item enforce the fact that the cannot-link relations are introduced \textbf{dynamically}

\item \textbf{Specific description:} The algorithm proceeds as follows: it initializes a contracted graph $\mathcal{G}'$ from the original graph $\mathcal{G}$ and it sorts the edges $e\in E$ in a priority queue (PQ) in descending order of absolute value  of the weight, so that the most attractive and the most repulsive edges are analyzed first. The algorithm has two variants: the first one a

At each iteration, one edge is popped from PQ and it is processed only if it belongs to the contracted graph $\mathcal{G}'$. The algorithm terminates when all edges have been processed. and it has two variants: one adding cannot link constraints and one not using them.
\item Comment about must-not-link relations: they give high priority to the most confident repulsive edges 
% \item I don't think I need to mention the merge tree (although it could be easily deduced from the code, as a sequence of clustering)
\item comment about complexity (depends on the linkage criteria) and how dense is the graph (check PQ update)

\end{itemize}

\subsection{Update rules and associated algorithms}
\begin{itemize}
\item Linkage criteria in the table:
\begin{itemize}
\item Mutex Watershed \cite{wolf2018mutex}, [proof of equivalence included in Appendix, also showing that adding or not CLC does not change anything]
\item Greedy Additive Edge Contraction \cite{levinkov2017comparative}, 
\item Greedy Fixation \cite{levinkov2017comparative}, 
\item Hierarchical Agglomerative Clustering with single, complete, average (UPGMA) linkage criteria
\end{itemize}
\item comment about the fact that sum is not an ultra-metric (say better)
\item In this article we analyze only the simplest (and cheapest) types of update rules, but... Easily generalizable for: learned linkage criteria \cite{nunez2013machine}, something depending on node size \cite{felzenszwalb2004efficient}, quantiles, weighted average (WPGMA) and weighted sum (and related work by Paul)

% \begin{table*}[t]
%     \centering
%     \begin{subtable}[t!]{0.98\textwidth}\centering
%         \begin{tabular}{c | c }
%             \toprule\toprule
%             \makecell{Algorithm name} & \makecell{Algorithm description and \\linkage criteria}    \\
%             \midrule\midrule

%             Weighted Arithmetic Mean (WPGMA) & \thead{Assign a weighting $\alpha_e \in \mathbb{R}^+$, $\forall e \in E$ \\ \\ Linkage criteria: $w_{\mathrm{new}} = \frac{\alpha_1 w_1 +\alpha_2 w_2}{\alpha_1 + \alpha_2} $}  \\ \midrule

%             \makecell{Felzenszwalb Efficient \\Graph-based Image Segmentation \cite{felzenszwalb2004efficient}}  & \thead{Initially all edges have positive weights }  \\ \midrule

%             \makecell{Quantile Agglomeration Clustering (...?)}  & \thead{...}  \\ \midrule

%             \makecell{Graph-based active learning \\of agglomeration (GALA) \cite{nunez2013machine}}  & \thead{Assign set of edge features $\phi^{\mathrm{I}}_e$ and \\node features $\phi^{\mathrm{II}}_u$, $\forall u \in V$, $\forall e \in E$. \\ \\ A classifier $f$ with parameters $\theta$ predicts and updates\\ the cost of an edge: $w_e = f(\phi^{\mathrm{I}}_e, \phi^{\mathrm{II}}_u, \phi^{\mathrm{II}}_v; \theta)$, $\forall e_{uv} \in E$} \\ \midrule

%             % \makecell{$w_{\mathrm{new}}=w_{\tilde{e}}$,$\,
%             % \,$ where $\tilde{e}=\mathrm{arg}\max_{e\in \{e_{1},e_{2}\}} \left|w_e\right|$  }  & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Mutex Watershed \cite{wolf2018mutex}} \\ \midrule

%             % Arithmetic mean: $w_{\mathrm{new}} = (w_1+w_2) / 2 $                                 & \thead{Hierarchical Clustering \\ with Average Linkage (UPGMA)} & \thead{\textbf{NEW}}\\ \midrule

%             % Maximum: $w_{\mathrm{new}} = \max \{ w_1, w_2 \}  $                                 & \thead{Hierarchical Clustering \\ with Single Linkage} & \thead{\textbf{NEW}}\\ \midrule

%             % Minimum: $w_{\mathrm{new}} = \min \{ w_1, w_2 \}  $                                 & \thead{Hierarchical Clustering \\ with Complete Linkage} & \thead{\textbf{NEW}}

%         \end{tabular}
%         % \caption{Linkage criteria}
%         \label{tab:linkage-criteria}
%     \end{subtable} 
%     \caption{Linkage criteria 2}
% \end{table*}

\end{itemize}

### 2019-03-14 latex/chapters/4_long_range_graph_def.tex
Restructure algorithm section; add chapter files

% !TEX root = ../agglo_clust_review.tex

\section{Long-range pixel grid graph}
\begin{itemize}
\item Define predictions of the classifier (pseudo probabilities) for edge weights
\item Define possible mappings to signed costs
\item Define long-range grid graph
\item Introduce "Poisson" random graph with a given probability of long-range connections
\item Comment about the short- and long-range distinction in the MWS paper: it does not work that well in practice (applying post-processing to remove small segments is easier and better solution)
\end{itemize}

### 2019-03-14 chapters/2_rel_work.tex
Move to the main repository folder

% !TEX root = ../agglo_clust_review.tex

\section{Related work}
\begin{itemize}
\item \textbf{Proposal based methods} 
\begin{itemize}
\item Generate region proposals or bounding boxes and classify the objects in the bounding box \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}; fully convolutional  box proposals \cite{li2017fully}. 
\item \emph{More references:} use an object detector to enumerate candidate instances and then perform pixel-level segmentation of each instance \cite{liang2018proposal,dai2016instance,li2017fully,liang2016reversible,arnab2017pixelwise} or generate generic proposal segments and then label each one with a semantic detector \cite{hariharan2014simultaneous,chen2015multi,hariharan2015hypercolumns,dai2015convolutional,uhrig2016pixel,he2017mask}.
% \SOURCE{\cite{kong2018recurrent}
\end{itemize}

\item \textbf{Proposal-free methods:} 
\begin{itemize}
\item box-free \cite{pinheiro2015learning,pinheiro2016learning,hu2017fastmask}; joint segmentation and instance labeling in a combinatorial framework \cite{kirillov2017instancecut}; recurrent models \cite{romera2016recurrent,ren2017end}; encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; sequential framework to gradually group from points to lines and then instances \cite{liu2017sgn}
\item \textbf{Pixel embedding vectors}: 
\begin{itemize}
\item supervised vectors \cite{bai2017deep}, unsupervised vectors  \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic} of which \cite{kong2018recurrent} is trained end-to-end;  using scene depth information \cite{uhrig2016pixel}, \TODO{check \cite{sironi2014multiscale}} 
%    \TODO{more on pose estimation, vector distance transform, deep coloring?, ECCV semi-convolutions}

% different types of loss
% \item For each pixel in the image, a CNN predicts an embedding vector, such that pixels in the same instance are represented by the same vector. (\textit{by training a model that labels pixels with unit-length vectors that live in some ﬁxed dimension embedding space} \SOURCE{Rec. embeddings} ). \textit{With instance embedding, each object is assigned a “color” in a n-dimensional space. The network processes the image and produces a dense output, same size as the input image. Each pixel in the output of the network is a point in the embedding space. Pixels that belong to the same object are close in the embedding space while pixels that belong to different objects are distant in the embedding space. Parsing the image embedding space involves some sort of clustering algorithm.} \SOURCE{online}

% \item Clustering methods: DBSCAN, more

\item \emph{Division by used clustering methods}: spectral clustering \cite{liang2018proposal}; mean-shift \cite{kong2018recurrent}; HDBSCAN \cite{}; seeds \cite{fathi2017semantic} \TODO{incomplete}
\end{itemize}

% \item Nevertheless, in both approaches we can define a grid graph (each vertex representing a pixel) with signed weights and find the final instance segmentation by using a graph partitioning algorithm:
% \begin{itemize}
% \item In Method 1, the graph is complete and the edge weights represent similarities between pairs of pixel embedding vectors. In most proposed approaches, embedding vectors representing distinct instances should be "distant enough" in the embedding space (a minimum distance is usually used during the training of the CNN). Thus, this threshold distance can be used to define signed affinities, representing attraction or repulsion between pairs of pixels;
% \item  In Method 2, the short- and long-range affinities predicted by the CNN are directly used as signed edge weights in the grid graph
% \end{itemize}

\item \textbf{Most related: predict short- and long-range affinities}. For each pixel we fix a set of neighboring pixels (not necessarily limited to the direct neighbors) and CNN predicts how likely it is for each pixel pair to be in the same instance \cite{liu2018affinity,wolf2018mutex,lee2017superhuman,xie2015holistically,Maire_2016_CVPR}. Mention that  \cite{liu2018affinity} is SoA on cityscapes for proposal-free methods and \cite{wolf2018mutex} is SoA on ISBI
% \item \cite{liu2018affinity} achieved comparable results to methods based on object proposal like Mask-R-CNN on natural images (Cityscapes); \cite{wolf2018mutex} achieved SOA results on a biological images (ISBI)
% \item Side comment: Even with pixel embedding vectors we can deduce affinities or signed costs
% (see MWS paper for a good review)

\end{itemize}

\item \textbf{Graph clustering related work}:
\begin{itemize}
    \item popular in image segmentation: \textbf{agglomerative clustering}.
    \item Why: more efficient than divisive approaches and graph cuts; does not usually require to specify the final number of clusters (e.g. spectral clustering) or seed nodes (e.g. watershed, random walker) 
    % old graph cut paper: \cite{shi2000normalized}
    % \item \emph{[other clustering methods working in an euclidean embedding space like mean-shift, K-means, Mixture models, BIRCH... can most probably be omitted]}
    \item many segmentation pipelines used to start the agglomeration from superpixels (SLIC, \cite{felzenszwalb2004efficient}, watershed) to reduce size of the problem 
    \item usually we build an hierarchy of clusters (or a \emph{merge-tree}): \TODO{find meaningful order}

% \item \textit{Some reference (atm in random order, to be continued)} 
\begin{itemize}

\item examples on natural images \cite{ren2013image,liu2016image}; ultra-metric contour map \cite{arbelaez2011contour};
\item \emph{Linkage criteria}: arithmetic average \cite{liu2018affinity,lee2017superhuman}; 
quantiles (median) \cite{funke2018large}; % and structured training 
   learned linkage criteria \cite{nunez2013machine}; 
\item An optimization perspective is taken in \cite{kiran2014global} %, which introduces h-increasing energy functions and builds the hierarchy incrementally such that merge decisions greedily minimize the energy
% Check MWS for description and more details
\item normalized cuts and combinatorial grouping \cite{arbelaez2014multiscale}
\item In \emph{connectomics}: \cite{liu2016sshmt}. Use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy. Using local \cite{liu2014modular,krasowski2015improving} or structured \cite{funke2015learning,uzunbas2016efficient} learning based methods % \SOURCE{SSHMT} Check Funke proposals
\end{itemize}
\item Methods finding a flat clustering (no hierarchy): efficient Graph-based Image segmentation \cite{felzenszwalb2004efficient} % defines a measure of quality for the current regions and stops when the merge costs would exceed this measure
\item \textbf{Signed graphs} \TODO{more}
\begin{itemize}
    % \item problem with hierarchical merge-trees is how to choose one single threshold. Choose one single fixed density level. Ideally we want to be able to cut the tree at different places to select our clusters. In density space, \cite{campello2013density}
    \item Multicut pipiline and heuristics \cite{beier2017multicut}... 
    % \item \textit{\textbf{Multicut} has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region. Its great drawback is that its optimization is NP-hard.} \SOURCE{MWS}.

\item hierarchy and multicut proposals \cite{funke2018candidate}
\item \textit{Must-not-link edges:} initially introduced as hard-constraints \cite{malmberg2011generalized}, then introduced dynamically \cite{wolf2018mutex,levinkov2017comparative}. 
\item Local-search approximations of MC: greeedy fixation and greedy additive edge contraction \cite{levinkov2017comparative}
\end{itemize}
\end{itemize}

\end{itemize}

### 2019-03-14 chapters/5_experiments_cityscapes.tex
Move to the main repository folder

% !TEX root = ../agglo_clust_review.tex
\subsection{Results on Cityscapes}

\begin{table*}
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{c| c| c | c}
        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
\textbf{mean} & False & {\color{ForestGreen} 0.3429 } & {\color{ForestGreen} 0.5516 } \\
% MEAN finetuned affs avg thresh035 use log costs & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
mean & True & {\color{Orange} 0.3154 } & {\color{Orange} 0.5269 } \\
% MEAN constr finetuned affs avg thresh035 use log costs & {\color{Red} 0.3000 } & {\color{Orange} 0.5140 } \\
sum & False & {\color{Red} 0.2590 } & {\color{Red} 0.4450 } \\
% GAEC finetuned affs avg thresh035 dont use log costs & {\color{Red} 0.2371 } & {\color{Red} 0.4187 } \\

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Results on cityscapes validation set (with finetuned affinities)}
    \label{tab:linkage-criteria}
\end{table*}

\begin{table*}
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{c| c| c | c}
        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
mean & False & {\color{Orange} 0.3359 } & {\color{ForestGreen} 0.5416 } \\
mean & True & {\color{Orange} 0.3315 } & {\color{ForestGreen} 0.5331 } \\
MutexWatershed & True & {\color{Red} 0.2123 } & {\color{Red} 0.3848 } \\
SingleLinkage & False & {\color{Red} 0.1935 } & {\color{Red} 0.3615 } \\
CompleteLinkage & False & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Scores on cityscapes validation set (original affinities trained by GMIS)}
    \label{tab:linkage-criteria}
\end{table*}

% \begin{table*}
%     \centering
%     \begin{subtable}[t!]{0.98\textwidth}\centering
%         \begin{tabular}{c| c | c | c}
% Update rule & \makecell{Use Cannot-Link\\Constraints} & \makecell{Multicut objective} & Runtime (s)\\ \midrule\midrule
% sum & false & \textbf{-150873} & 99 (??) \\
% sum & true & -150873 & 249 \\
% MutexWatershed & false & -150854 & 100 \\
% mean & false & -150850 & 105 \\
% mean & true & -150848 & 244 \\
% max & true & -149441 & 459 \\
% min & true & -147663 & 186 \\
% min & false & -147663 & 82 \\
% max & false & -103614 & \textbf{16} \\
%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Compare update-rules on fruit-fly large graph}
%     \label{tab:linkage-criteria}
% \end{table*}

### 2019-03-14 chapters/6_conclusions.tex
Move to the main repository folder

--- 2019-03-14 chapters/5_experiments_cityscapes.tex
@@
 % !TEX root = ../agglo_clust_review.tex
-\subsection{Results on Cityscapes}
-
-\begin{table*}
-    \centering
-    \begin{subtable}[t!]{0.98\textwidth}\centering
-        \begin{tabular}{c| c| c | c}
-        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
-\textbf{mean} & False & {\color{ForestGreen} 0.3429 } & {\color{ForestGreen} 0.5516 } \\
-% MEAN finetuned affs avg thresh035 use log costs & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
-GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
-mean & True & {\color{Orange} 0.3154 } & {\color{Orange} 0.5269 } \\
-% MEAN constr finetuned affs avg thresh035 use log costs & {\color{Red} 0.3000 } & {\color{Orange} 0.5140 } \\
-sum & False & {\color{Red} 0.2590 } & {\color{Red} 0.4450 } \\
-% GAEC finetuned affs avg thresh035 dont use log costs & {\color{Red} 0.2371 } & {\color{Red} 0.4187 } \\
-
-        \end{tabular}
-        % \caption{Linkage criteria}
-    \end{subtable} 
-    \caption{Results on cityscapes validation set (with finetuned affinities)}
-    \label{tab:linkage-criteria}
-\end{table*}
-
-\begin{table*}
-    \centering
-    \begin{subtable}[t!]{0.98\textwidth}\centering
-        \begin{tabular}{c| c| c | c}
-        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
-GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
-mean & False & {\color{Orange} 0.3359 } & {\color{ForestGreen} 0.5416 } \\
-mean & True & {\color{Orange} 0.3315 } & {\color{ForestGreen} 0.5331 } \\
-MutexWatershed & True & {\color{Red} 0.2123 } & {\color{Red} 0.3848 } \\
-SingleLinkage & False & {\color{Red} 0.1935 } & {\color{Red} 0.3615 } \\
-CompleteLinkage & False & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\
-
-        \end{tabular}
-        % \caption{Linkage criteria}
-    \end{subtable} 
-    \caption{Scores on cityscapes validation set (original affinities trained by GMIS)}
-    \label{tab:linkage-criteria}
-\end{table*}
-
-% \begin{table*}
-%     \centering
-%     \begin{subtable}[t!]{0.98\textwidth}\centering
-%         \begin{tabular}{c| c | c | c}
-% Update rule & \makecell{Use Cannot-Link\\Constraints} & \makecell{Multicut objective} & Runtime (s)\\ \midrule\midrule
-% sum & false & \textbf{-150873} & 99 (??) \\
-% sum & true & -150873 & 249 \\
-% MutexWatershed & false & -150854 & 100 \\
-% mean & false & -150850 & 105 \\
-% mean & true & -150848 & 244 \\
-% max & true & -149441 & 459 \\
-% min & true & -147663 & 186 \\
-% min & false & -147663 & 82 \\
-% max & false & -103614 & \textbf{16} \\
-%         \end{tabular}
-%         % \caption{Linkage criteria}
-%     \end{subtable} 
-%     \caption{Compare update-rules on fruit-fly large graph}
-%     \label{tab:linkage-criteria}
-% \end{table*}
+\section{Conclusions}

### 2019-03-14 agglo_clust_final.tex
Update title and minor things

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{iccv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\iccvfinalcopy % *** Uncomment this line for the final submission

\def\iccvPaperID{368} % *** Enter the ICCV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ificcvfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Author Guidelines for ICCV Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous ICCV abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

Please follow the steps outlined below when submitting your manuscript to
the IEEE Computer Society Press.  This style guide now has several
important modifications (for example, you are no longer warned against the
use of sticky tape to attach your artwork to the paper), so all authors
should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

Please refer to the author guidelines on the ICCV 2019 web page for a
discussion of the policy on dual submissions.

\subsection{Paper length}
Papers, excluding the references section,
must be no longer than eight pages in length. The references section
will not be included in the page count, and there is no limit on the
length of the references section. For example, a paper of eight pages
with two pages of references would have a total length of 10 pages.

Overlength papers will simply not be reviewed.  This includes papers
where the margins and formatting are deemed to have been significantly
altered from those laid down by this style guide.  Note that this
\LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for
supervised revisions of manuscripts.  The reviewing process cannot determine
the suitability of the paper for presentation in eight pages if it is
reviewed in eleven.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the \verb'\iccvfinalcopy' command in the document preamble.)  Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g.\ this line is $095.5$), although in most cases one would
expect that the approximate location will be adequate.

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove
citations to one's own work---in fact it is often impossible to
review a paper unless the previous citations are known and
available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say
that you are Lucy Smith; it says that you are building on her
work.  If you are Smith and Jones, do not say ``as we show in
[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our
   previous paper [1], and show it to be inferior to all
   previously known methods.  Why the previous paper was
   accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the
   paper of Smith \etal [1], and show it to be inferior to
   all previously known methods.  Why the previous paper
   was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo
   filter, a fundamental contribution to human knowledge''.
   Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to that
submission in order to explain the differences, just as you would if you
had previously published related work.  In such cases, include the
anonymized parallel submission~\cite{Authors14} as additional material and
cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be
found elsewhere, and refer them to a technical report.  For conference
submissions, the paper must stand on its own, and not {\em require} the
reviewer to go to a techreport for further details.  Thus, you may say in
the body of the paper ``further details may be found
in~\cite{Authors14b}''.  Then submit the techreport as additional material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the ICCV70 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how to
improve our previous work [Anonymous, 1968].  This time we tested the
algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors. Instead
write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.  This
   system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] didn't
   handle case B properly.  Ours handles it by including
   a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo
   lunar lander, and went all the way to the moon, don't
   you know.  It displayed the following behaviours
   which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you as
the authors.  A reviewer might think it likely that the new paper was
written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been
contracted to solve problem B.

\noindent
FAQ\medskip\\
{\bf Q:} Are acknowledgements OK?\\
{\bf A:} No.  Leave them for the final copy.\medskip\\
{\bf Q:} How do I cite my results reported in open challenges?
{\bf A:} To conform with the double blind review policy, you can report results of other challenge participants together with your results in your paper. For your results, however, you should not identify yourself and should not mention your participation in the challenge. Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a
sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
\verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'',
shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
However, use it only when there are three or more authors.  Thus, the
following is correct: ``
   Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
because reference~\cite{Alpher03} has just two authors.  If you use the
\verb'\etal' macro provided, then you need not worry about double periods
when used at the end of a sentence as in Alpher \etal.

For this citation style, keep multiple citations in numerical (not
chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
\cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}

All text must be in a two-column format. The total allowable width of the
text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
first page) should begin 1.0 inch (2.54 cm) from the top edge of the
page. The second and following pages should begin 1.0 inch (2.54 cm) from
the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.
Page numbers should be in footer with page numbers, centered and .75
inches from the bottom of the page and make it start at the correct page
number rather than the 4321 in the example.  To do this fine the line (around
line 23)
\begin{verbatim}
%\ificcvfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\end{verbatim}
where the number 4321 is your assigned starting page.

Make sure the first page is numbered by commenting out the first page being
empty on line 46
\begin{verbatim}
%\thispagestyle{empty}
\end{verbatim}

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is
available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
the first page. The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
adverbs; do not capitalize articles, coordinate conjunctions, or
prepositions (unless the title begins with such a word). Leave two blank
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is to
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a third-order
heading (we discourage it), use 10-point Times, boldface, initially
capitalized, flush left, preceded by one blank line, followed by a period
and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors14}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the ICCV 2019 web page for a discussion
of the use of color in your document.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2019-03-14 chapters/2_rel_work.tex
Update title and minor things

@@
 \item box-free \cite{pinheiro2015learning,pinheiro2016learning,hu2017fastmask}; joint segmentation and instance labeling in a combinatorial framework \cite{kirillov2017instancecut}; recurrent models \cite{romera2016recurrent,ren2017end}; encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; sequential framework to gradually group from points to lines and then instances \cite{liu2017sgn}
+\item From end-to-end recurrent attention: \textit{Other approaches us- ing FCNs are proposal-free, but rely on a \textbf{bottom-up merging process}\textbf{}.
+Liang et al.
+[26] predict dense pixel prediction of ob- ject location and size, using clustering as a post-processing step.
+Uhrig et al.
+[41] present another approach based on FCNs, which is trained to produces a semantic segmen- tation as well as an instance-aware angle map, encoding the instance centroids.
+Post-processing based on template matching and instance fusion produces the instance identi- ties.
+Importantly, they also used ground-truth depth labels in training.
+Concurrent work [2, 19, 22] also explores a similar idea of using FCNs to output instance-sensitive embeddings.}
 \item \textbf{Pixel embedding vectors}: 

### 2019-03-14 chapters/3_algorithm.tex
Update title and minor things

--- 2019-03-14 latex/chapters/3_algorithm.tex
@@
 \begin{algorithm}
-  \caption{General Unified Agglomerative Clustering}
+  \caption{Unified Graph Agglomerative Clustering}
    \hspace*{\algorithmicindent} \textbf{Inputs:} graph $\mathcal{G}(V,E,W)$; bool {\color{blue}\texttt{addCannotLink}}  \\
@@
 
-\section{General Unified Agglomerative Clustering Algorithm (GUACA)}
+\section{Unified Graph Agglomerative Clustering \\Algorithm}
 In this section we introduce a unified agglomerative clustering algorithm that represents a simple generalized formalization of many agglomerative graph clustering algorithms.

### 2019-03-15 chapters/3_algorithm.tex
Partial algorithm description; add new figs/tables

@@
 % !TEX root = ../agglo_clust_review.tex
-
-\begin{figure}
-\centering
-\includegraphics[width=0.50\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/edge_contraction.png}
-\caption{\small 
-Example of edge contraction: the edge $e_{uv}$ is selected from priority queue; after nodes $u$ and $v$ are merged and $e_{uv}$ is deleted, there are two double edges $e_1$ and $e_2$ left in the graph.
-\TODO{Rotate drawings to optimize space}
-\label{fig:example_non_unique_weights_1}}
-\end{figure}
 
@@
       % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
-      \State Initialize contracted graph $\mathcal{G}'(V',E')$ from $\mathcal{G}$
+      \State Initialize contracted graph $\mathcal{G}'$ from $\mathcal{G}$
       \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
@@
       \While{PQ is \textbf{not} empty}
-        \State Pop edge $e_{uv}\in E'$ with highest abs. priority $|\tilde{w}|$
+        \State Pop edge $e_{uv}$ in $\mathcal{G}'$ with highest priority $|\tilde{w}|$
         \State
@@
 \centering
-\includegraphics[width=0.45\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/aggl_clust.png}
+\includegraphics[width=0.50\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/edge_contraction.png}
 \caption{\small 
-Example of agglomerative clustering on signed graph with sum update rule and without Cannot-Link-Constraints. The final clustering is given by one single cluster.
+Example of edge contraction: the edge $e_{uv}$ is selected from priority queue; after nodes $u$ and $v$ are merged and $e_{uv}$ is deleted, there are two double edges $e_1$ and $e_2$ left in the graph.
+\TODO{Rotate drawings to optimize space}
 \label{fig:example_non_unique_weights_1}}
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.50\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/aggl_clust_with_nonlink.png}
-\caption{\small 
-Example of agglomerative clustering on signed graph with sum update rule and using Cannot-Link-Constraints. Edges flagged with \texttt{canBeMerged} = \texttt{False} are highlighted in pink. 
-\label{fig:example_non_unique_weights_2}}
-\end{figure}
-
-\begin{table*}[h]
-    \centering
-    \begin{subtable}[t!]{0.98\textwidth}\centering
-        \begin{tabular}{r l || c | c | c}
-            % \toprule\toprule
-             & &  \multirow{3}{*}{\textbf{Unsigned graphs}}  & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
-            % \cmidrule(l{.15em}){4-5}
-            % \cline{4-5}
-            & & &  \multicolumn{2}{c}{\thead{Use Cannot-Link-Constraints:}} \\
-
-            & & &  \thead{NO} & \thead{YES} \\        
-            % \cmidrule[0.3em]{3-5}
-            % \midrule[0.15em]
-            \midrule\midrule
-            Sum: & $f(\tilde{w}_1,\tilde{w}_2) = \tilde{w}_1+\tilde{w}_2$ & \thead{Sum Linkage\\Hierarchical Clustering} & \thead{Greedy Additive \\ Edge Contraction \cite{levinkov2017comparative}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} \\ \midrule
-
-            \makecell[r]{Absolute \\ maximum:} & \makecell[l]{$f(\tilde{w}_1,\tilde{w}_2) =\argmax_{\tilde{w}\in\{\tilde{w}_{1},\tilde{w}_{2}\}} \big|\tilde{w} \big| $}   & \thead{Single Linkage\\Hierarchical Clustering\\ \cite{lance1967general}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Mutex Watershed \cite{wolf2018mutex}} \\ \midrule
-
-            \makecell[r]{Arithmetic \\mean:} & $f(\tilde{w}_1,\tilde{w}_2) = \mathrm{weightedAvg}\{ \tilde{w}_1, \tilde{w}_2 \} $                                 & \thead{ Average Linkage\\ Hierarchical Clustering \\(UPGMA) \cite{lance1967general}} & \thead{Signed Agglomerative Clust.
-\\ with Average Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
-
-            Maximum: & $f(\tilde{w}_1,\tilde{w}_2) = \max \{ \tilde{w}_1, \tilde{w}_2 \}  $                                 & \thead{Single Linkage\\Hierarchical Clustering\\ \cite{lance1967general}} & \thead{Signed Agglomerative Clust.
-\\ with Single Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
-
-            Minimum:& $f(\tilde{w}_1,\tilde{w}_2) = \min \{ \tilde{w}_1, \tilde{w}_2 \}  $                                 & \thead{Complete Linkage\\ Hierarchical Clustering \\ \cite{lance1967general}}  & \thead{Signed Agglomerative Clust.
-\\ with Complete Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}
-
-        \end{tabular}
-        % \caption{Linkage criteria}
-    \end{subtable} 
-    \caption{The table lists all the algorithms that can be seen as special cases of the Generic Agglomerative Clustering \ref{main_alg} given a specific update rule $f(e_1,e_2)$ and a type of graph...}
-    \label{tab:linkage-criteria}
-\end{table*}
-
-\section{Unified Graph Agglomerative Clustering \\Algorithm}
+\section{Unified Graph Agglomerative Clustering}
 In this section we introduce a unified agglomerative clustering algorithm that represents a simple generalized formalization of many agglomerative graph clustering algorithms.
-It can be used to describe both unsigned clustering algorithms ingesting positive similarities between clusters and signed clustering algorithms using attractive and repulsive cues.\\
+It can be used to describe both unsigned clustering algorithms ingesting positive cluster similarities and signed clustering algorithms using attractive and repulsive cues.\\
 First, we define the graph notation and the concept of cannot-link constraints.
@@
 \begin{itemize}
-\item Define graph formalism and clustering $\Pi$. Make comment about special case of unsigned graph!
-\item Introduce concept of cannot-link-constraints
-\item From wiki: \emph{Both a must-link and a cannot-link constraint define a relationship between two data instances.
-A must-link constraint is used to specify that the two instances in the must-link relation should be associated with the same cluster.
-A cannot-link constraint is used to specify that the two instances in the cannot-link relation should not be associated with the same cluster.
-These sets of constraints acts as a guide for which a constrained clustering algorithm will attempt to find clusters in a data set which satisfy the specified must-link and cannot-link constraints.
-Some constrained clustering algorithms will abort if no such clustering exists which satisfies the specified constraints.
-Others will try to minimize the amount of constraint violation should it be impossible to find a clustering which satisfies the constraints.}
+\item Define graph formalism and clustering $\Pi$. Make comment about special case of unsigned graph
+\item Define multicut and associated energy
+\item A cannot-link-constraint defines a mutual exclusion relationship between two nodes in the graph and is used to specify that the these two nodes should not be associated with the same cluster.
+(the alg.
+will introduce them dynamically...)
+\item Given a clustering $\Pi$ and a graph $\mathcal{G}(V,E,W)$, the interaction between two clusters $S_1, S_2 \in \Pi$ is usually defined in terms of a \emph{linkage criterion}, i.e.
+a function of all the edge weights connecting the two clusters:
+\begin{equation} \label{eq:linkage_criterion_def}
+\begin{gathered}
+\mathcal{L}(S_1,S_2) = \mathcal{L}(\mathcal{W})\quad \\
+   \text{where} \quad \mathcal{W} = \{ W(e_{uv})| u\in S_1, v\in S_2 \}.
+\end{gathered}
+\end{equation}
 
 \end{itemize}
+
 \subsection{The algorithm}
 \begin{itemize}
-\item First give intuitive idea of agglomerative clustering
-\item enforce the fact that the cannot-link relations are introduced \textbf{dynamically}
+  \item We now present our first contribution: a unified algorithm for agglomerative graph clustering that can describe in a simple general form many graph partitioning algorithms previously introduced in the literature \UPDATE{and highlights the existence of totally new algorithms}.
+\item We consider a graph $\mathcal{G}(V,E,W)$ with associated signed edge weights, where each node initially represents one cluster.
+\item The proposed graph partitioning algorithm is a general form of agglomerative clustering that outputs a final graph clustering $\Pi$ by progressively merging pairs of neighboring clusters.
+The algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
+\ref{fig:general_idea}b and \ref{fig:general_idea}c).
+
+\item A second variant of the proposed algorithm also introduces cannot-link constraints between clusters during the agglomeration and stops when all the remaining clusters have been previously constrained.
+
+\item During the agglomerative process, the interaction between neighboring clusters is defined by the linkage criterion defined in Equation \ref{eq:linkage_criterion_def} and has to be properly recomputed.
+
+ \item An efficient way of doing this is presented in Algorithm \ref{main_alg}, which proceeds as follows. \UPDATE{TO BE CONTINUED}
+\item The so called contracted graph is initialized from the original graph $\mathcal{G}$ and will represent the clustering $\Pi$ at each iteration of the
 
@@
 % \item I don't think I need to mention the merge tree (although it could be easily deduced from the code, as a sequence of clustering)
+\item Mention precise version in the Appendix
 \item comment about complexity (depends on the linkage criteria) and how dense is the graph (check PQ update)
+
+\item In the special case of an unsigned graph %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
+ representing strictly positive similarities between nodes, the algorithm then returns only one single cluster as an output (see Fig.
+\ref{fig:general_idea}a), \UPDATE{together with a merging tree representing the merging order and defining an hierarchy of clusters}.
 
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.png}
+\caption{\small 
+Example of agglomerative clustering on signed graph with and without cannot-link constraints. The final clustering is given by one single cluster.
+\label{fig:example_cannot_link_constraints}}
+\end{figure}
+
 \subsection{Update rules and associated algorithms}
 \begin{itemize}
-\item Linkage criteria in the table:
-\begin{itemize}
-\item Mutex Watershed \cite{wolf2018mutex}, [proof of equivalence included in Appendix, also showing that adding or not CLC does not change anything]
-\item Greedy Additive Edge Contraction \cite{levinkov2017comparative}, 
-\item Greedy Fixation \cite{levinkov2017comparative}, 
-\item Hierarchical Agglomerative Clustering with single, complete, average (UPGMA) linkage criteria
+\item In this section we will list \UPDATE{ALL} (...) algorithms that can be described using the generalized algorithm we presented and define some new ones
+\item In Table 1 we collected the update rules we tested and compared in this article (correspond to the simplest and cheapest ones to compute). Later we will mention more of them
+\item First unsigned graphs: the merging tree defined by the algorithm (\textbf{define merge tree somewhere..?}) is equivalent to the hierarchical dendrogram (but careful with the sum...) that we have in HC
+\item Then mention CLC and who started using them recently for this type of problem: fixed, then greedyFixation introduced exactly this algorithm as a greedy approx of MC, together with Greedy Additive Edge Contraction
+\item MWS: proposes an efficient implementation of this update rule (briefly mention the idea).
+In the Supplementary material we show that the algorithm they present can be seen as a special case of Unified Graph Agglomerative Clustering with absolute maximum update rule and that adding or not CLC does not change anything
+\item Then new versions of avg/complete and single linkage clustering 
+\item In this article we analyze only the simplest (and cheapest) types of update rules, but...
+Easily generalizable for: learned linkage criteria \cite{nunez2013machine}, something depending on node size \cite{felzenszwalb2004efficient}, quantiles, weighted average (WPGMA) and weighted sum (and related work by Paul), size rule by Thorsten
+\item comment about the fact that sum is not an ultra-metric (say better)
 \end{itemize}
-\item comment about the fact that sum is not an ultra-metric (say better)
-\item In this article we analyze only the simplest (and cheapest) types of update rules, but...
-Easily generalizable for: learned linkage criteria \cite{nunez2013machine}, something depending on node size \cite{felzenszwalb2004efficient}, quantiles, weighted average (WPGMA) and weighted sum (and related work by Paul)
 
@@
 
-\end{itemize}
+\begin{table*}
+    \centering
+    \begin{subtable}[t!]{0.98\textwidth}\centering
+        \begin{tabular}{r l || c | c | c}
+            % \toprule\toprule
+             & &  \multirow{3}{*}{\textbf{Unsigned graphs}}  & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
+            % \cmidrule(l{.15em}){4-5}
+            % \cline{4-5}
+            & & &  \multicolumn{2}{c}{\thead{Add Cannot-Link-Constraints:}} \\
+
+            & & &  \thead{NO} & \thead{YES} \\        
+            % \cmidrule[0.3em]{3-5}
+            % \midrule[0.15em]
+            \midrule\midrule
+            Sum: & $f(\tilde{w}_1,\tilde{w}_2) = \tilde{w}_1+\tilde{w}_2$ & \thead{Sum Linkage\\Hierarchical Clustering} & \thead{Greedy Additive \\ Edge Contraction \cite{levinkov2017comparative}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} \\ \midrule
+
+            \makecell[r]{Absolute \\ maximum:} & \makecell[l]{$f(\tilde{w}_1,\tilde{w}_2) =\argmax_{\tilde{w}\in\{\tilde{w}_{1},\tilde{w}_{2}\}} \big|\tilde{w} \big| $}   & \thead{Single Linkage\\Hierarchical Clustering\\ \cite{lance1967general}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Mutex Watershed \cite{wolf2018mutex}} \\ \midrule
+
+            \makecell[r]{Arithmetic \\mean:} & $f(\tilde{w}_1,\tilde{w}_2) = \mathrm{weightedAvg}\{ \tilde{w}_1, \tilde{w}_2 \} $                                 & \thead{ Average Linkage\\ Hierarchical Clustering \\(UPGMA) \cite{lance1967general}} & \thead{Signed Agglomerative Clust.
+\\ with Average Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
+
+            Maximum: & $f(\tilde{w}_1,\tilde{w}_2) = \max \{ \tilde{w}_1, \tilde{w}_2 \}  $                                 & \thead{Single Linkage\\Hierarchical Clustering\\ \cite{lance1967general}} & \thead{Signed Agglomerative Clust.
+\\ with Single Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
+
+            Minimum:& $f(\tilde{w}_1,\tilde{w}_2) = \min \{ \tilde{w}_1, \tilde{w}_2 \}  $                                 & \thead{Complete Linkage\\ Hierarchical Clustering \\ \cite{lance1967general}}  & \thead{Signed Agglomerative Clust.
+\\ with Complete Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}
+
+        \end{tabular}
+        % \caption{Linkage criteria}
+    \end{subtable} 
+    \caption{The table lists all the algorithms that can be seen as special cases of the Generic Agglomerative Clustering \ref{main_alg} given a specific update rule $f(e_1,e_2)$ and a type of graph...}
+    \label{tab:linkage-criteria}
+\end{table*}

### 2019-03-15 chapters/5_experiments_cityscapes.tex
Partial algorithm description; add new figs/tables

@@
     \begin{subtable}[t!]{0.98\textwidth}\centering
-        \begin{tabular}{c| c| c | c}
-        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
-\textbf{mean} & False & {\color{ForestGreen} 0.3429 } & {\color{ForestGreen} 0.5516 } \\
-% MEAN finetuned affs avg thresh035 use log costs & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
-GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
-mean & True & {\color{Orange} 0.3154 } & {\color{Orange} 0.5269 } \\
-% MEAN constr finetuned affs avg thresh035 use log costs & {\color{Red} 0.3000 } & {\color{Orange} 0.5140 } \\
-sum & False & {\color{Red} 0.2590 } & {\color{Red} 0.4450 } \\
-% GAEC finetuned affs avg thresh035 dont use log costs & {\color{Red} 0.2371 } & {\color{Red} 0.4187 } \\
+        \begin{tabular}{c| c| c | c | c}
+        Update rule & \makecell{Bias factor $\beta$} & AP & AP 50\%\\ \midrule\midrule
+MEAN & thresh035  & {\color{ForestGreen} 0.3429 } & {\color{ForestGreen} 0.5516 } \\
+% MEAN & thresh035 & True & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
+% MEAN & thresh030 & False & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5457 } \\
+ORIGINAL \cite{liu2018affinity} & -  & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
+% MEAN & thresh040 & - & {\color{ForestGreen} 0.3402 } & {\color{ForestGreen} 0.5502 } \\
+MEANconstr & thresh025  & {\color{Orange} 0.3390 } & {\color{ForestGreen} 0.5481 } \\
+% MEANconstr & thresh030 & False & {\color{Orange} 0.3344 } & {\color{ForestGreen} 0.5469 } \\
+% MEAN & thresh045 & - & {\color{Orange} 0.3333 } & {\color{ForestGreen} 0.5438 } \\
+% MEAN & thresh050 & - & {\color{Orange} 0.3255 } & {\color{ForestGreen} 0.5341 } \\
+SingleLinkagePlusCLC & thresh050  & {\color{Orange} 0.3252 } & {\color{ForestGreen} 0.5304 } \\
+MutexWatershed & thresh045  & {\color{Orange} 0.3214 } & {\color{ForestGreen} 0.5306 } \\
+greedyFixation & thresh055  & {\color{Orange} 0.3188 } & {\color{Orange} 0.5271 } \\
+% greedyFixation & thresh050 & - & {\color{Orange} 0.3180 } & {\color{Orange} 0.5155 } \\
+% MEANconstr & thresh020 & False & {\color{Orange} 0.3161 } & {\color{Orange} 0.5136 } \\
+% MutexWatershed & thresh050 & - & {\color{Orange} 0.3158 } & {\color{Orange} 0.5246 } \\
+% MEANconstr & thresh035 & False & {\color{Orange} 0.3154 } & {\color{Orange} 0.5269 } \\
+% greedyFixation & thresh060 & - & {\color{Orange} 0.3135 } & {\color{Orange} 0.5196 } \\
+GAEC & thresh055  & {\color{Orange} 0.3127 } & {\color{Orange} 0.5114 } \\
+% GAEC & thresh050 & - & {\color{Orange} 0.3112 } & {\color{Orange} 0.5085 } \\
+% SingleLinkagePlusCLC & thresh045 & - & {\color{Orange} 0.3109 } & {\color{Orange} 0.5134 } \\
+% GAEC & thresh060 & - & {\color{Orange} 0.3100 } & {\color{Orange} 0.5120 } \\
+% greedyFixation & thresh065 & - & {\color{Orange} 0.3056 } & {\color{Orange} 0.5063 } \\
+% greedyFixation & thresh045 & - & {\color{Orange} 0.3045 } & {\color{Red} 0.4989 } \\
+% GAEC & thresh065 & - & {\color{Orange} 0.3035 } & {\color{Orange} 0.5072 } \\
+% GAEC & thresh045 & - & {\color{Orange} 0.3008 } & {\color{Red} 0.4956 } \\
+% MEANconstr & thresh035 & True & {\color{Red} 0.3000 } & {\color{Orange} 0.5140 } \\
+% MEANconstr & thresh040 & False & {\color{Red} 0.2983 } & {\color{Orange} 0.5076 } \\
+% GAEC & thresh070 & - & {\color{Red} 0.2943 } & {\color{Red} 0.4989 } \\
+% SingleLinkagePlusCLC & thresh055 & - & {\color{Red} 0.2942 } & {\color{Orange} 0.5074 } \\
+% greedyFixation & thresh070 & - & {\color{Red} 0.2919 } & {\color{Red} 0.4906 } \\
+% GAEC & thresh075 & - & {\color{Red} 0.2793 } & {\color{Red} 0.4784 } \\
+% greedyFixation & thresh075 & - & {\color{Red} 0.2750 } & {\color{Red} 0.4707 } \\
+% SingleLinkagePlusCLC & thresh060 & - & {\color{Red} 0.2681 } & {\color{Red} 0.4744 } \\
+% GAEC & thresh035 & True & {\color{Red} 0.2590 } & {\color{Red} 0.4450 } \\
+% greedyFixation & thresh035 & - & {\color{Red} 0.2587 } & {\color{Red} 0.4484 } \\
+% MutexWatershed & thresh040 & - & {\color{Red} 0.2562 } & {\color{Red} 0.4505 } \\
+% MEANconstr & thresh050 & - & {\color{Red} 0.2507 } & {\color{Red} 0.4443 } \\
+% SingleLinkagePlusCLC & thresh040 & - & {\color{Red} 0.2490 } & {\color{Red} 0.4411 } \\
+% SingleLinkagePlusCLC & thresh065 & - & {\color{Red} 0.2489 } & {\color{Red} 0.4401 } \\
+% greedyFixation & thresh035 & - & {\color{Red} 0.2438 } & {\color{Red} 0.4297 } \\
+SingleLinkage & thresh085 & {\color{Red} 0.2433 } & {\color{Red} 0.4436 } \\
+% GAEC & thresh035 & False & {\color{Red} 0.2371 } & {\color{Red} 0.4187 } \\
+% SingleLinkage & thresh080 & - & {\color{Red} 0.2336 } & {\color{Red} 0.4265 } \\
+% SingleLinkagePlusCLC & thresh070 & - & {\color{Red} 0.2285 } & {\color{Red} 0.4045 } \\
+% SingleLinkage & thresh075 & - & {\color{Red} 0.2265 } & {\color{Red} 0.4065 } \\
+% MutexWatershed & thresh035 & - & {\color{Red} 0.2253 } & {\color{Red} 0.4004 } \\
+% SingleLinkage & thresh070 & - & {\color{Red} 0.2213 } & {\color{Red} 0.3947 } \\
+% SingleLinkagePlusCLC & thresh035 & - & {\color{Red} 0.2213 } & {\color{Red} 0.3954 } \\
+% SingleLinkage & thresh065 & - & {\color{Red} 0.2177 } & {\color{Red} 0.3889 } \\
+% SingleLinkage & thresh060 & - & {\color{Red} 0.2116 } & {\color{Red} 0.3842 } \\
+% SingleLinkagePlusCLC & thresh075 & - & {\color{Red} 0.2093 } & {\color{Red} 0.3785 } \\
+% SingleLinkage & thresh055 & - & {\color{Red} 0.1987 } & {\color{Red} 0.3700 } \\
+% SingleLinkage & thresh050 & - & {\color{Red} 0.1952 } & {\color{Red} 0.3659 } \\
+% SingleLinkage & thresh035 & - & {\color{Red} 0.1852 } & {\color{Red} 0.3463 } \\
+CompleteLinkagePlusCLC & thresh035  & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\
+CompleteLinkage & thresh035  & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\
 
@@
 
-\begin{table*}
-    \centering
-    \begin{subtable}[t!]{0.98\textwidth}\centering
-        \begin{tabular}{c| c| c | c}
-        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
-GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
-mean & False & {\color{Orange} 0.3359 } & {\color{ForestGreen} 0.5416 } \\
-mean & True & {\color{Orange} 0.3315 } & {\color{ForestGreen} 0.5331 } \\
-MutexWatershed & True & {\color{Red} 0.2123 } & {\color{Red} 0.3848 } \\
-SingleLinkage & False & {\color{Red} 0.1935 } & {\color{Red} 0.3615 } \\
-CompleteLinkage & False & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\
-
-        \end{tabular}
-        % \caption{Linkage criteria}
-    \end{subtable} 
-    \caption{Scores on cityscapes validation set (original affinities trained by GMIS)}
-    \label{tab:linkage-criteria}
-\end{table*}
-
 % \begin{table*}
@@
 %     \begin{subtable}[t!]{0.98\textwidth}\centering
-%         \begin{tabular}{c| c | c | c}
-% Update rule & \makecell{Use Cannot-Link\\Constraints} & \makecell{Multicut objective} & Runtime (s)\\ \midrule\midrule
-% sum & false & \textbf{-150873} & 99 (??) \\
-% sum & true & -150873 & 249 \\
-% MutexWatershed & false & -150854 & 100 \\
-% mean & false & -150850 & 105 \\
-% mean & true & -150848 & 244 \\
-% max & true & -149441 & 459 \\
-% min & true & -147663 & 186 \\
-% min & false & -147663 & 82 \\
-% max & false & -103614 & \textbf{16} \\
+%         \begin{tabular}{c| c| c | c}
+%         Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
+% GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
+% mean & False & {\color{Orange} 0.3359 } & {\color{ForestGreen} 0.5416 } \\
+% mean & True & {\color{Orange} 0.3315 } & {\color{ForestGreen} 0.5331 } \\
+% MutexWatershed & True & {\color{Red} 0.2123 } & {\color{Red} 0.3848 } \\
+% SingleLinkage & False & {\color{Red} 0.1935 } & {\color{Red} 0.3615 } \\
+% CompleteLinkage & False & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\
+
 %         \end{tabular}
@@
 %     \end{subtable} 
-%     \caption{Compare update-rules on fruit-fly large graph}
+%     \caption{Scores on cityscapes validation set (original affinities trained by GMIS)}
 %     \label{tab:linkage-criteria}

### 2019-03-15 chapters/5_experiments_intro.tex
Partial algorithm description; add new figs/tables

% !TEX root = ../agglo_clust_review.tex

\subsection{Experimental setup and tested datasets}
\begin{itemize}
    \item Define long-range grid graph. (Mention the fact of enforcing local merge)
\item Introduce "Poisson" random graph with a given probability of long-range connections
\item Comment about the short- and long-range distinction in the MWS paper? It does not work that well in practice (applying post-processing to remove small segments is easier and better solution)
\item Define offset patterns (link to supplementary material), trained networks (loss, etc...) and setups on cremi and cityscapes 
\end{itemize}

### 2019-03-15 chapters/5_experiments_noise.tex
Partial algorithm description; add new figs/tables

% !TEX root = ../agglo_clust_review.tex
\begin{figure}
\centering
\includegraphics[width=0.50\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}
\caption{Plot illustrating results with merge-biased noise...}
\end{figure}

\subsection{Noise experiments}
\begin{itemize}
\item Define Perlin/opensimplex noise
\item Present plots
\item Comment about MC energy
\end{itemize}

\begin{figure}
\centering
\includegraphics[width=0.50\textwidth,trim=0.27in 0.27in 0.27in 0.27in,clip]{./figs/split_noise.pdf}
\caption{Plot illustrating results with split-biased noise...}
\end{figure}

### 2019-03-15 chapters/supplementary.tex
Partial algorithm description; add new figs/tables

--- 2019-02-24 latex/agglo_clust_review.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+% !TEX root = ../agglo_clust_review.tex
 
-\usepackage{iccv}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-
-\usepackage{algorithm}% http://ctan.org/pkg/algorithm
-\PassOptionsToPackage{noend}{algpseudocode}% comment out if want end's to show
-\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
-
-% \newcommand*{\algrule}[1][\algorithmicindent]{\makebox[#1][l]{\hspace*{.5em}\vrule height .75\baselineskip depth .25\baselineskip}}%
-
-% \newcount\ALG@printindent@tempcnta
-% \def\ALG@printindent{%
-%     \ifnum \theALG@nested>0% is there anything to print
-%         \ifx\ALG@text\ALG@x@notext% is this an end group without any text?
-%             % do nothing
-%             \addvspace{-3pt}% FUDGE for cases where no text is shown, to make the rules line up
-%         \else
-%             \unskip
-%             % draw a rule for each indent level
-%             \ALG@printindent@tempcnta=1
-%             \loop
-%                 \algrule[\csname ALG@ind@\the\ALG@printindent@tempcnta\endcsname]%
-%                 \advance \ALG@printindent@tempcnta 1
-%             \ifnum \ALG@printindent@tempcnta<\numexpr\theALG@nested+1\relax% can't do <=, so add one to RHS and use < instead
-%             \repeat
-%         \fi
-%     \fi
-%     }%
-\usepackage{etoolbox}
-% the following line injects our new indent handling code in place of the default spacing
-% \patchcmd{\ALG@doentity}{\noindent\hskip\ALG@tlm}{\ALG@printindent}{}{\errmessage{failed to patch}}
-% \makeatother
-% end vertical rule patch for algorithmicx
-
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-% \iccvfinalcopy % *** Uncomment this line for the final submission
-
-\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\usepackage{mathrsfs}
-\newcommand{\RED}[1]{#1}
-
-\newcommand\TODO[1]{{\color{red}{TODO: #1}}}
-\newcommand\UPDATE[1]{{\color{blue}{#1}}}
-\newcommand\SOURCE[1]{{\color{green}{(from: #1)}}}
-% \newcommand\CHANGED[2]{{{\color{blue}{#1}}\color{green}{#2}}}
-
-\usepackage[dvipsnames]{xcolor}
-\usepackage{enumitem}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ificcvfinal\pagestyle{empty}\fi
-\begin{document}
-
-%%%%%%%%% TITLE
-\title{\LaTeX\ Author Guidelines for ICCV Proceedings}
-
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
-}
-
-\maketitle
-%\thispagestyle{empty}
-
-\input{chapters/abstract.tex}
-
-\input{chapters/intro.tex}
-
-\input{chapters/rel_work.tex}
+\section{Supplementary Material}
+\begin{itemize}
+\item Equivalence Mutex Watershed and Greedy Edge Contraction
+\item Complexity: plain agglo., addition of the cannot-link constraints and then comment about efficient implementation of MWS and of single-linkage (what about single linkage+CLC...?)
+\end{itemize}
 
@@
 \end{algorithm}
-
-% \section{Algorithm}
-\section{Grand Unified Whatever Clustering}
-\begin{itemize}
-\item Define graph formalism and clustering $\Pi$
-\item Description and pseudo-code
-\item Linkage criteria in the table:
-\begin{itemize}
-\item Mutex Watershed \cite{wolf2018mutex}, [proof of equivalence included in Appendix]
-\item Greedy Additive Edge Contraction \cite{levinkov2017comparative}, 
-\item Greedy Fixation \cite{levinkov2017comparative}, 
-\item Hierarchical Agglomerative Clustering with single, complete, average (UPGMA) linkage criteria
-\end{itemize}
-\item Easily generalizable for: learned linkage criteria \cite{nunez2013machine}, something depending on node size \cite{felzenszwalb2004efficient}, quantiles, weighted average (WPGMA) and weighted sum
-
-\item Comment about must-not-link relations: they give high priority to the most confident repulsive edges 
-\item I don't think I need to mention the merge tree (although it could be easily deduced from the code, as a sequence of clustering)
-\item comment about complexity (depends on the linkage criteria) and how dense is the graph (check PQ update)
-\end{itemize}
-
-\section{Experiments}
-\begin{itemize}
-\item define pixel grid graph and long range connections
-\item probability of long-range connections
-\end{itemize}
-\subsection{Qualitative comparison}
-\begin{itemize}
-\item find good way to represent agglomeration order
-\item can we display the must-not-link edges...?
-\end{itemize}
-\subsection{Noise experiments}
-
-\subsection{Comparison on CREMI and cityscapes}
-
-\section{Conclusions}
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{agglo_clust}
-}
-
-\section{Supplementary Material}
-\begin{itemize}
-\item Equivalence Mutex Watershed and Greedy Edge Contraction
-\end{itemize}
-
-\end{document}

### 2019-03-16 chapters/3_algorithm.tex
Complete description of the algorithm

@@
 % !TEX root = ../agglo_clust_review.tex
+
+\begin{figure}
+\centering
+\includegraphics[width=0.50\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/edge_contraction.png}
+\caption{\small 
+Example of edge contraction: the edge $e_{uv}$ is selected from priority queue; after nodes $u$ and $v$ are merged and $e_{uv}$ is deleted, there are two double edges $e_1$ and $e_2$ left in the graph.
+\TODO{Rotate drawings to optimize space} \TODO{Add some cannot-link constraints to explain their propagation}
+\label{fig:edge_contraction_and_contr_graph} }
+\end{figure}
+
+\section{Unified Graph Agglomerative Clustering}
+In this section we introduce a unified agglomerative clustering algorithm that represents a simple generalized formalization of many agglomerative graph clustering algorithms.
+It can be used to describe both unsigned clustering algorithms ingesting positive cluster similarities and signed clustering algorithms using attractive and repulsive cues.\\
+First, we define the graph notation and the concept of cannot-link constraints.
+Then, we introduce the generalized algorithm and show \UPDATE{how it can be used to introduce several new agglomerative clustering algorithms for graphs with signed weights.}
+
+\subsection{Contracted graph and cannot-link constraints} \label{sec:contr_graph_and_CLC}
+
+\begin{itemize}
+\item Define graph formalism and clustering $\Pi$. Make comment about special case of unsigned graph
+\item Define multicut and associated energy
+\item A cannot-link-constraint defines a mutual exclusion relationship between two nodes in the graph and is used to specify that the these two nodes should not be associated with the same cluster.
+(the alg.
+will introduce them dynamically...)
+\item Given a clustering $\Pi$ and a graph $\mathcal{G}(V,E,W)$, the interaction between two clusters $S_1, S_2 \in \Pi$ is usually defined in terms of a \emph{linkage criterion}, i.e.
+a function of all the edge weights connecting the two clusters:
+\begin{equation} \label{eq:linkage_criterion_def}
+\begin{gathered}
+\mathcal{L}(S_1,S_2) = \mathcal{L}(\mathcal{W})\quad \\
+   \text{where} \quad \mathcal{W} = \{ W(e_{uv})| u\in S_1, v\in S_2 \}.
+\end{gathered}
+\end{equation}
+
+\end{itemize}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.50\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/edge_contraction.png}
-\caption{\small 
-Example of edge contraction: the edge $e_{uv}$ is selected from priority queue; after nodes $u$ and $v$ are merged and $e_{uv}$ is deleted, there are two double edges $e_1$ and $e_2$ left in the graph.
-\TODO{Rotate drawings to optimize space}
-\label{fig:example_non_unique_weights_1}}
-\end{figure}
+\subsection{The algorithm}
 
-\section{Unified Graph Agglomerative Clustering}
-In this section we introduce a unified agglomerative clustering algorithm that represents a simple generalized formalization of many agglomerative graph clustering algorithms.
-It can be used to describe both unsigned clustering algorithms ingesting positive cluster similarities and signed clustering algorithms using attractive and repulsive cues.\\
-First, we define the graph notation and the concept of cannot-link constraints.
-Then, we introduce the generalized algorithm and show \UPDATE{how it can be used to introduce several new agglomerative clustering algorithms for graphs with signed weights.}
+We now present our first contribution: a unified algorithm for agglomerative graph clustering that can describe in a simple general form many graph partitioning algorithms previously introduced in the literature \UPDATE{and highlights the existence of totally new algorithms}.
 
-\subsection{Graph notation and cannot-link constraints}
-
-\begin{itemize}
-\item Define graph formalism and clustering $\Pi$. Make comment about special case of unsigned graph
-\item Define multicut and associated energy
-\item A cannot-link-constraint defines a mutual exclusion relationship between two nodes in the graph and is used to specify that the these two nodes should not be associated with the same cluster.
-(the alg.
-will introduce them dynamically...)
-\item Given a clustering $\Pi$ and a graph $\mathcal{G}(V,E,W)$, the interaction between two clusters $S_1, S_2 \in \Pi$ is usually defined in terms of a \emph{linkage criterion}, i.e.
-a function of all the edge weights connecting the two clusters:
-\begin{equation} \label{eq:linkage_criterion_def}
-\begin{gathered}
-\mathcal{L}(S_1,S_2) = \mathcal{L}(\mathcal{W})\quad \\
-   \text{where} \quad \mathcal{W} = \{ W(e_{uv})| u\in S_1, v\in S_2 \}.
-\end{gathered}
-\end{equation}
-
-\end{itemize}
-
-\subsection{The algorithm}
-\begin{itemize}
-  \item We now present our first contribution: a unified algorithm for agglomerative graph clustering that can describe in a simple general form many graph partitioning algorithms previously introduced in the literature \UPDATE{and highlights the existence of totally new algorithms}.
-\item We consider a graph $\mathcal{G}(V,E,W)$ with associated signed edge weights, where each node initially represents one cluster.
-\item The proposed graph partitioning algorithm is a general form of agglomerative clustering that outputs a final graph clustering $\Pi$ by progressively merging pairs of neighboring clusters.
+We consider a graph $\mathcal{G}(V,E,W)$ with associated signed edge weights, where each node initially represents one cluster.
+The proposed graph partitioning algorithm is a general form of agglomerative clustering that outputs a final graph clustering $\Pi$ by progressively merging pairs of neighboring clusters.
 The algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
@@
 
-\item A second variant of the proposed algorithm also introduces cannot-link constraints between clusters during the agglomeration and stops when all the remaining clusters have been previously constrained.
+A second variant of the proposed algorithm also introduces cannot-link constraints between clusters during the agglomeration and stops when all the remaining clusters have been previously constrained (option \texttt{addCannotLink} in Algorithm \ref{main_alg}).
 
-\item During the agglomerative process, the interaction between neighboring clusters is defined by the linkage criterion defined in Equation \ref{eq:linkage_criterion_def} and has to be properly recomputed.
+During the agglomerative process, the interaction between neighboring clusters is defined by the linkage criterion defined in Equation \ref{eq:linkage_criterion_def} and has to be properly recomputed.
+One possible efficient way of doing this is to use an edge contraction algorithm like the one presented in Algorithm \ref{main_alg}, which proceeds as follows.
 
- \item An efficient way of doing this is presented in Algorithm \ref{main_alg}, which proceeds as follows. \UPDATE{TO BE CONTINUED}
-\item The so called contracted graph is initialized from the original graph $\mathcal{G}$ and will represent the clustering $\Pi$ at each iteration of the
+Given an initial clustering $\Pi$ where each node of the original graph $\mathcal{G}$ represents its own cluster, the algorithm starts by initializing a contracted graph $\mathcal{G}'$ (see Definition \ref{def:contr_graph}) that will represent the clustering $\Pi$ at each iteration of the agglomeration.
+The algorithm then sorts all edges $e\in E$ by their absolute weight $|W(e)|$ in descending order in a priority queue, so that the most attractive and the most repulsive edges are processed first.
+It iteratively pops one edge $e_{uv}$ from priority queue and, depending on the value of the priority $\tilde{w}$ associated to $e_{uv}$, does the following.
+If the edge is attractive and $\tilde{w}>0$, then perform an edge contraction of $e_{uv}$ in $\mathcal{G}'$ (see Sec.
+\ref{sec:contr_graph_and_CLC} and Fig.
+\ref{fig:edge_contraction_and_contr_graph}), provided that $e_{uv}$ was not previously flagged as a cannot-link constraint; for every new pair of double edges in $\mathcal{G}'$ update \UPDATE{their priorities} according to one of the update rules listed in Table \ref{tab:linkage-criteria} and update cannot-link relationships (see example in Fig.
+\ref{fig:algorithm_with_without_CLC}b from step 3 to 4).
+If, on the other hand, the edge $e_{uv}$ is repulsive and $\tilde{w}\leq 0$, then flag it as a cannot-link constraint if and only if the algorithm input-option \texttt{addCannotLink} is true and mutual exclusion relationships should be enforced.
 
-\item \textbf{Specific description:}  The algorithm proceeds as follows: it initializes a contracted graph $\mathcal{G}'$ from the original graph $\mathcal{G}$ and it sorts the edges $e\in E$ in a priority queue (PQ) in descending order of absolute value  of the weight, so that the most attractive and the most repulsive edges are analyzed first.
-The algorithm has two variants: the first one a
+In the Supplementary material we provide a more detailed version of the algorithm implementation (Sec.
+\ref{sec:detailed_algorithm}) and we also comment on its theoretical complexity (Sec.
+\ref{sec:complexity}).
 
-At each iteration, one edge is popped from PQ and it is processed only if it belongs to the contracted graph $\mathcal{G}'$.
-The algorithm terminates when all edges have been processed.
-and it has two variants: one adding cannot link constraints and one not using them.
-\item Comment about must-not-link relations: they give high priority to the most confident repulsive edges 
-% \item I don't think I need to mention the merge tree (although it could be easily deduced from the code, as a sequence of clustering)
-\item Mention precise version in the Appendix
-\item comment about complexity (depends on the linkage criteria) and how dense is the graph (check PQ update)
+ In the special case of an unsigned graph %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
+ presenting strictly positive similarities between nodes, the algorithm then returns only one single cluster as an output (see Fig.
+\ref{fig:intro_figure}a), \UPDATE{together with a merging tree representing the merging order and defining an hierarchy of clusters} \TODO{use def of merging process of contracted graph to define merging tree}.
 
-\item In the special case of an unsigned graph %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
- representing strictly positive similarities between nodes, the algorithm then returns only one single cluster as an output (see Fig.
-\ref{fig:general_idea}a), \UPDATE{together with a merging tree representing the merging order and defining an hierarchy of clusters}.
-
-\end{itemize}
+% \item Comment about must-not-link relations: they give high priority to the most confident repulsive edges {}
 
@@
 \caption{\small 
-Example of agglomerative clustering on signed graph with and without cannot-link constraints. The final clustering is given by one single cluster.
-\label{fig:example_cannot_link_constraints}}
+Example of agglomerative clustering on signed graph with and without cannot-link constraints...
+\label{fig:algorithm_with_without_CLC}}
 \end{figure}
@@
 Easily generalizable for: learned linkage criteria \cite{nunez2013machine}, something depending on node size \cite{felzenszwalb2004efficient}, quantiles, weighted average (WPGMA) and weighted sum (and related work by Paul), size rule by Thorsten
-\item comment about the fact that sum is not an ultra-metric (say better)
+\item comment about the fact that sum is not really an ultra-metric-distance
 \end{itemize}

### 2019-03-17 chapters/1_intro.tex
Partial algorithm description; add new figs/tables
Add and update graphics

--- 2019-03-07 latex/chapters/intro.tex
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.50\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.pdf} % left bottom right top
+\caption{\small 
+Intro image: explain algorithm, main ideas and contributions
+\label{fig:intro_figure}}
+\end{figure}
+
 \section{Introduction}
-On possible selling story could be: currently many of the successful proposal-free instance segmentation methods rely on a final clustering step on a grid-graph with both short and long-range connections.
+%On possible selling story could be: currently many of the successful proposal-free instance segmentation methods rely on a final clustering step on a grid-graph with both short and long-range connections.
 So it is worth to study this problem in more details.

### 2019-03-17 chapters/3_algorithm.tex
Add and update graphics

@@
 \centering
-\includegraphics[width=0.50\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/edge_contraction.png}
+\includegraphics[width=0.50\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
 \caption{\small 
-Example of edge contraction: the edge $e_{uv}$ is selected from priority queue; after nodes $u$ and $v$ are merged and $e_{uv}$ is deleted, there are two double edges $e_1$ and $e_2$ left in the graph.
-\TODO{Rotate drawings to optimize space} \TODO{Add some cannot-link constraints to explain their propagation}
+Example of edge contraction: the edge $e_{uv}$ is selected from priority queue; after nodes $u$ and $v$ are merged and $e_{uv}$ is deleted, there are two double edges $e_1$ and $e_2$ left in the graph...
 \label{fig:edge_contraction_and_contr_graph} }
@@
 \item Define multicut and associated energy
+
 \item A cannot-link-constraint defines a mutual exclusion relationship between two nodes in the graph and is used to specify that the these two nodes should not be associated with the same cluster.
@@
 will introduce them dynamically...)
+\item Define contracted graph and edge contraction (explain Fig. 2)
 \item Given a clustering $\Pi$ and a graph $\mathcal{G}(V,E,W)$, the interaction between two clusters $S_1, S_2 \in \Pi$ is usually defined in terms of a \emph{linkage criterion}, i.e.
@@
 
+\begin{table*}
+    \centering
+    \begin{subtable}[t!]{0.98\textwidth}\centering
+        \begin{tabular}{r l || c | c | c}
+            % \toprule\toprule
+             & &  \multirow{3}{*}{\textbf{Unsigned graphs}}  & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
+            % \cmidrule(l{.15em}){4-5}
+            % \cline{4-5}
+            & & &  \multicolumn{2}{c}{\thead{Add Cannot-Link-Constraints:}} \\
+
+            & & &  \thead{NO} & \thead{YES} \\        
+            % \cmidrule[0.3em]{3-5}
+            % \midrule[0.15em]
+            \midrule\midrule
+            Sum: & $f(\tilde{w}_1,\tilde{w}_2) = \tilde{w}_1+\tilde{w}_2$ & \thead{Sum Linkage\\Hierarchical Clustering} & \thead{Greedy Additive \\ Edge Contraction \cite{levinkov2017comparative}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} \\ \midrule
+
+            \makecell[r]{Absolute \\ maximum:} & \makecell[l]{$f(\tilde{w}_1,\tilde{w}_2) =\argmax_{\tilde{w}\in\{\tilde{w}_{1},\tilde{w}_{2}\}} \big|\tilde{w} \big| $}   & \thead{Single Linkage\\Hierarchical Clustering\\ \cite{lance1967general}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Mutex Watershed \cite{wolf2018mutex}} \\ \midrule
+
+            \makecell[r]{Arithmetic \\mean:} & $f(\tilde{w}_1,\tilde{w}_2) = \mathrm{weightedAvg}\{ \tilde{w}_1, \tilde{w}_2 \} $                                 & \thead{ Average Linkage\\ Hierarchical Clustering \\(UPGMA) \cite{lance1967general}} & \thead{Signed Agglomerative Clust.
+\\ with Average Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
+
+            Maximum: & $f(\tilde{w}_1,\tilde{w}_2) = \max \{ \tilde{w}_1, \tilde{w}_2 \}  $                                 & \thead{Single Linkage\\Hierarchical Clustering\\ \cite{lance1967general}} & \thead{Signed Agglomerative Clust.
+\\ with Single Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
+
+            Minimum:& $f(\tilde{w}_1,\tilde{w}_2) = \min \{ \tilde{w}_1, \tilde{w}_2 \}  $                                 & \thead{Complete Linkage\\ Hierarchical Clustering \\ \cite{lance1967general}}  & \thead{Signed Agglomerative Clust.
+\\ with Complete Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}
+
+        \end{tabular}
+        % \caption{Linkage criteria}
+    \end{subtable} 
+    \caption{The table lists all the algorithms that can be seen as special cases of the Generic Agglomerative Clustering \ref{main_alg} given a specific update rule $f(e_1,e_2)$ and a type of graph...}
+    \label{tab:linkage-criteria}
+\end{table*}
+
 \subsection{Update rules and associated algorithms}
@@
 % \end{table*}
-
-\begin{table*}
-    \centering
-    \begin{subtable}[t!]{0.98\textwidth}\centering
-        \begin{tabular}{r l || c | c | c}
-            % \toprule\toprule
-             & &  \multirow{3}{*}{\textbf{Unsigned graphs}}  & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
-            % \cmidrule(l{.15em}){4-5}
-            % \cline{4-5}
-            & & &  \multicolumn{2}{c}{\thead{Add Cannot-Link-Constraints:}} \\
-
-            & & &  \thead{NO} & \thead{YES} \\        
-            % \cmidrule[0.3em]{3-5}
-            % \midrule[0.15em]
-            \midrule\midrule
-            Sum: & $f(\tilde{w}_1,\tilde{w}_2) = \tilde{w}_1+\tilde{w}_2$ & \thead{Sum Linkage\\Hierarchical Clustering} & \thead{Greedy Additive \\ Edge Contraction \cite{levinkov2017comparative}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} \\ \midrule
-
-            \makecell[r]{Absolute \\ maximum:} & \makecell[l]{$f(\tilde{w}_1,\tilde{w}_2) =\argmax_{\tilde{w}\in\{\tilde{w}_{1},\tilde{w}_{2}\}} \big|\tilde{w} \big| $}   & \thead{Single Linkage\\Hierarchical Clustering\\ \cite{lance1967general}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Mutex Watershed \cite{wolf2018mutex}} \\ \midrule
-
-            \makecell[r]{Arithmetic \\mean:} & $f(\tilde{w}_1,\tilde{w}_2) = \mathrm{weightedAvg}\{ \tilde{w}_1, \tilde{w}_2 \} $                                 & \thead{ Average Linkage\\ Hierarchical Clustering \\(UPGMA) \cite{lance1967general}} & \thead{Signed Agglomerative Clust.
-\\ with Average Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
-
-            Maximum: & $f(\tilde{w}_1,\tilde{w}_2) = \max \{ \tilde{w}_1, \tilde{w}_2 \}  $                                 & \thead{Single Linkage\\Hierarchical Clustering\\ \cite{lance1967general}} & \thead{Signed Agglomerative Clust.
-\\ with Single Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
-
-            Minimum:& $f(\tilde{w}_1,\tilde{w}_2) = \min \{ \tilde{w}_1, \tilde{w}_2 \}  $                                 & \thead{Complete Linkage\\ Hierarchical Clustering \\ \cite{lance1967general}}  & \thead{Signed Agglomerative Clust.
-\\ with Complete Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}
-
-        \end{tabular}
-        % \caption{Linkage criteria}
-    \end{subtable} 
-    \caption{The table lists all the algorithms that can be seen as special cases of the Generic Agglomerative Clustering \ref{main_alg} given a specific update rule $f(e_1,e_2)$ and a type of graph...}
-    \label{tab:linkage-criteria}
-\end{table*}

### 2019-03-17 chapters/5_experiments_cityscapes.tex
Complete description of the algorithm
Add and update graphics

--- 2019-03-14 chapters/5_experiments_cityscapes.tex
@@
 
-\begin{table*}
+\begin{table}
     \centering
-    \begin{subtable}[t!]{0.98\textwidth}\centering
-        \begin{tabular}{c| c| c | c}
-        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
-\textbf{mean} & False & {\color{ForestGreen} 0.3429 } & {\color{ForestGreen} 0.5516 } \\
-% MEAN finetuned affs avg thresh035 use log costs & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
-GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
-mean & True & {\color{Orange} 0.3154 } & {\color{Orange} 0.5269 } \\
-% MEAN constr finetuned affs avg thresh035 use log costs & {\color{Red} 0.3000 } & {\color{Orange} 0.5140 } \\
-sum & False & {\color{Red} 0.2590 } & {\color{Red} 0.4450 } \\
-% GAEC finetuned affs avg thresh035 dont use log costs & {\color{Red} 0.2371 } & {\color{Red} 0.4187 } \\
+    \begin{subtable}[t!]{0.5\textwidth}\centering
+        \begin{tabular}{c| c| c | c }
+        \makecell{Update rule \\ and CLC} & \makecell{Bias \\factor $\beta$} & AP & AP 50\%\\ \midrule\midrule
+mean F & 0.35  & {\color{ForestGreen} 0.3429 } & {\color{ForestGreen} 0.5516 } \\
+% MEAN & 0.35 & True & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
+% MEAN & 0.30 & False & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5457 } \\
+\cite{liu2018affinity} & -  & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
+% MEAN & 0.40 & - & {\color{ForestGreen} 0.3402 } & {\color{ForestGreen} 0.5502 } \\
+mean T & 0.25  & {\color{Orange} 0.3390 } & {\color{ForestGreen} 0.5481 } \\
+% MEANconstr & 0.30 & False & {\color{Orange} 0.3344 } & {\color{ForestGreen} 0.5469 } \\
+% MEAN & 0.45 & - & {\color{Orange} 0.3333 } & {\color{ForestGreen} 0.5438 } \\
+% MEAN & 0.50 & - & {\color{Orange} 0.3255 } & {\color{ForestGreen} 0.5341 } \\
+max T & 0.50  & {\color{Orange} 0.3252 } & {\color{ForestGreen} 0.5304 } \\
+MWS & 0.45  & {\color{Orange} 0.3214 } & {\color{ForestGreen} 0.5306 } \\
+sum T & 0.55  & {\color{Orange} 0.3188 } & {\color{Orange} 0.5271 } \\
+% greedyFixation & 0.50 & - & {\color{Orange} 0.3180 } & {\color{Orange} 0.5155 } \\
+% MEANconstr & 0.20 & False & {\color{Orange} 0.3161 } & {\color{Orange} 0.5136 } \\
+% MutexWatershed & 0.50 & - & {\color{Orange} 0.3158 } & {\color{Orange} 0.5246 } \\
+% MEANconstr & 0.35 & False & {\color{Orange} 0.3154 } & {\color{Orange} 0.5269 } \\
+% greedyFixation & 0.60 & - & {\color{Orange} 0.3135 } & {\color{Orange} 0.5196 } \\
+sum T & 0.55  & {\color{Orange} 0.3127 } & {\color{Orange} 0.5114 } \\
+% GAEC & 0.50 & - & {\color{Orange} 0.3112 } & {\color{Orange} 0.5085 } \\
+% SingleLinkagePlusCLC & 0.45 & - & {\color{Orange} 0.3109 } & {\color{Orange} 0.5134 } \\
+% GAEC & 0.60 & - & {\color{Orange} 0.3100 } & {\color{Orange} 0.5120 } \\
+% greedyFixation & 0.65 & - & {\color{Orange} 0.3056 } & {\color{Orange} 0.5063 } \\
+% greedyFixation & 0.45 & - & {\color{Orange} 0.3045 } & {\color{Red} 0.4989 } \\
+% GAEC & 0.65 & - & {\color{Orange} 0.3035 } & {\color{Orange} 0.5072 } \\
+% GAEC & 0.45 & - & {\color{Orange} 0.3008 } & {\color{Red} 0.4956 } \\
+% MEANconstr & 0.35 & True & {\color{Red} 0.3000 } & {\color{Orange} 0.5140 } \\
+% MEANconstr & 0.40 & False & {\color{Red} 0.2983 } & {\color{Orange} 0.5076 } \\
+% GAEC & 0.70 & - & {\color{Red} 0.2943 } & {\color{Red} 0.4989 } \\
+% SingleLinkagePlusCLC & 0.55 & - & {\color{Red} 0.2942 } & {\color{Orange} 0.5074 } \\
+% greedyFixation & 0.70 & - & {\color{Red} 0.2919 } & {\color{Red} 0.4906 } \\
+% GAEC & 0.75 & - & {\color{Red} 0.2793 } & {\color{Red} 0.4784 } \\
+% greedyFixation & 0.75 & - & {\color{Red} 0.2750 } & {\color{Red} 0.4707 } \\
+% SingleLinkagePlusCLC & 0.60 & - & {\color{Red} 0.2681 } & {\color{Red} 0.4744 } \\
+% GAEC & 0.35 & True & {\color{Red} 0.2590 } & {\color{Red} 0.4450 } \\
+% greedyFixation & 0.35 & - & {\color{Red} 0.2587 } & {\color{Red} 0.4484 } \\
+% MutexWatershed & 0.40 & - & {\color{Red} 0.2562 } & {\color{Red} 0.4505 } \\
+% MEANconstr & 0.50 & - & {\color{Red} 0.2507 } & {\color{Red} 0.4443 } \\
+% SingleLinkagePlusCLC & 0.40 & - & {\color{Red} 0.2490 } & {\color{Red} 0.4411 } \\
+% SingleLinkagePlusCLC & 0.65 & - & {\color{Red} 0.2489 } & {\color{Red} 0.4401 } \\
+% greedyFixation & 0.35 & - & {\color{Red} 0.2438 } & {\color{Red} 0.4297 } \\
+max F & 0.85 & {\color{Red} 0.2433 } & {\color{Red} 0.4436 } \\
+% GAEC & 0.35 & False & {\color{Red} 0.2371 } & {\color{Red} 0.4187 } \\
+% SingleLinkage & 0.80 & - & {\color{Red} 0.2336 } & {\color{Red} 0.4265 } \\
+% SingleLinkagePlusCLC & 0.70 & - & {\color{Red} 0.2285 } & {\color{Red} 0.4045 } \\
+% SingleLinkage & 0.75 & - & {\color{Red} 0.2265 } & {\color{Red} 0.4065 } \\
+% MutexWatershed & 0.35 & - & {\color{Red} 0.2253 } & {\color{Red} 0.4004 } \\
+% SingleLinkage & 0.70 & - & {\color{Red} 0.2213 } & {\color{Red} 0.3947 } \\
+% SingleLinkagePlusCLC & 0.35 & - & {\color{Red} 0.2213 } & {\color{Red} 0.3954 } \\
+% SingleLinkage & 0.65 & - & {\color{Red} 0.2177 } & {\color{Red} 0.3889 } \\
+% SingleLinkage & 0.60 & - & {\color{Red} 0.2116 } & {\color{Red} 0.3842 } \\
+% SingleLinkagePlusCLC & 0.75 & - & {\color{Red} 0.2093 } & {\color{Red} 0.3785 } \\
+% SingleLinkage & 0.55 & - & {\color{Red} 0.1987 } & {\color{Red} 0.3700 } \\
+% SingleLinkage & 0.50 & - & {\color{Red} 0.1952 } & {\color{Red} 0.3659 } \\
+% SingleLinkage & 0.35 & - & {\color{Red} 0.1852 } & {\color{Red} 0.3463 } \\
+min T & 0.35  & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\
+min F & 0.35  & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\
 
@@
     \end{subtable} 
-    \caption{Results on cityscapes validation set (with finetuned affinities)}
+    \caption{Results on cityscapes validation set (with finetuned affinities). \TODO{Reformat in the usual form, delete colors, less digits}}
     \label{tab:linkage-criteria}
-\end{table*}
-
-\begin{table*}
-    \centering
-    \begin{subtable}[t!]{0.98\textwidth}\centering
-        \begin{tabular}{c| c| c | c}
-        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
-GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
-mean & False & {\color{Orange} 0.3359 } & {\color{ForestGreen} 0.5416 } \\
-mean & True & {\color{Orange} 0.3315 } & {\color{ForestGreen} 0.5331 } \\
-MutexWatershed & True & {\color{Red} 0.2123 } & {\color{Red} 0.3848 } \\
-SingleLinkage & False & {\color{Red} 0.1935 } & {\color{Red} 0.3615 } \\
-CompleteLinkage & False & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\
-
-        \end{tabular}
-        % \caption{Linkage criteria}
-    \end{subtable} 
-    \caption{Scores on cityscapes validation set (original affinities trained by GMIS)}
-    \label{tab:linkage-criteria}
-\end{table*}
+\end{table}
 

### 2019-03-17 chapters/5_experiments_noise.tex
Add and update graphics

@@
 % !TEX root = ../agglo_clust_review.tex
+% 
 \begin{figure}
 \centering
-\includegraphics[width=0.50\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}
-\caption{Plot illustrating results with merge-biased noise...}
-\end{figure}
+        \begin{subfigure}[t]{0.46 \linewidth}
+        \centering
+        \includegraphics[width=0.98\textwidth,trim=4.4in 1.2in 0.in 0.05in,clip]{figs/noisy_affs_merge.pdf}
+        % \caption{Thresholding of local boundary maps ~(THRESH)} \label{fig:thresh}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.46 \linewidth}
+        \centering
+        \includegraphics[width=0.98\textwidth,trim=4.4in 1.2in 0.in 0.05in,clip]{figs/noisy_affs_split.pdf}
+        % \caption{Watershed, seeded at local minima of the smoothed input map~(WS)} \label{fig:ws}
+    \end{subfigure}\hspace{0.5cm}%
+    \caption{Noisy affinities \TODO{Left: clean affinities. Right: divide image in two triangles and show split and merge simultaneously}}
+    % \label{fig:isbi-examples}
+\end{figure}%
 
@@
 \begin{itemize}
-\item Define Perlin/opensimplex noise
+    \item In this section we will quantitatively test the robustness of the unified agglomerative clustering algorithm by adding noise to the edge weights of the graph and see how different choices of update rules compare.
+    \item Among the update rules listed in Table \ref{tab:linkage-criteria}, we will focus only on \emph{sum}, \emph{arithmetic mean} and \emph{absolute maximum}, since they achieved the best scores in the results presented in Sec.
+\ref{sec:exp_first_comparison}.
+Before to present the results shown in Fig.
+\ref{fig:noise_merge} and \ref{fig:noise_split}, we will first introduce the type of noise that was added to the edge weights.
+\item In the set of analyzed experiments, edge weights are estimated \UPDATE{by using a CNN that predicts pairwise interactions between pixels in the image/volume}.
+Fig.
+\ref{fig:noisy_affinities}a illustrates the predictions of the CNN for neighboring pixels in the horizontal direction of Define Perlin/opensimplex noise
 \item Present plots
@@
 \includegraphics[width=0.50\textwidth,trim=0.27in 0.27in 0.27in 0.27in,clip]{./figs/split_noise.pdf}
-\caption{Plot illustrating results with split-biased noise...}
+\caption{Plot illustrating results with split-biased noise...}\label{fig:noise_split}
 \end{figure}
+
+% \begin{figure}
+% \centering
+% \includegraphics[width=0.50\textwidth,trim=0.27in 0.27in 0.27in 0.27in,clip]{./figs/noisy_affs.pdf}
+% \caption{Illustration of noisy affinities}\label{fig:noisy_affinities}
+% \end{figure}

### 2019-03-17 chapters/supplementary.tex
Add and update graphics

@@
 \end{itemize}
+
+\begin{table*}
+    \centering
+    \begin{subtable}[t!]{0.98\textwidth}\centering
+        \begin{tabular}{c| c | c| c | c | c | c | c}
+Update rule & \makecell{Use Cannot-Link\\Constraints} & Log-costs & \makecell{Multicut objective} & Runtime (s) & ARAND & VI-merge & VI-split\\ \midrule\midrule
+% \textbf{mean} & False & \textbf{-102739991} & {\color{Orange} 3797 } & {\color{ForestGreen} \textbf{0.0708} } & {\color{ForestGreen} 0.286 } & {\color{ForestGreen} 0.428 } \\
+% % mean & False & -102730208 & {\color{Orange} 2562 } & {\color{ForestGreen} 0.0715 } & {\color{ForestGreen} 0.292 } & {\color{ForestGreen} 0.423 } \\
+% MutexWatershed & False & -102313957 & {\color{ForestGreen} 830 } & {\color{ForestGreen} 0.0754 } & {\color{ForestGreen} 0.291 } & {\color{Orange} 0.471 } \\
+% sum & False & -101846418 & {\color{Red} 12681 } & {\color{Orange} 0.1623 } & {\color{Orange} 0.427 } & {\color{ForestGreen} 0.427 } \\
+% % sum & False & -101732952 & {\color{Red} 12287 } & {\color{Orange} 0.1624 } & {\color{Orange} 0.436 } & {\color{ForestGreen} 0.390 } \\
+% sum & True & -101487448 & {\color{Red} 8497 } & {\color{Orange} 0.1626 } & {\color{Orange} 0.428 } & {\color{ForestGreen} 0.414 } \\
+% % sum & True & -100745943 & {\color{Red} 13361 } & {\color{Orange} 0.1574 } & {\color{Orange} 0.410 } & {\color{Orange} 0.451 } \\
+% mean & True & -100279671 & {\color{Orange} 4713 } & {\color{Orange} 0.1353 } & {\color{ForestGreen} 0.265 } & {\color{Red} 0.717 } \\
+% % mean & True & -99416111 & {\color{Orange} 3445 } & {\color{Orange} 0.1761 } & {\color{ForestGreen} 0.260 } & {\color{Red} 0.822 } \\
+% max & True & -98143342 & {\color{Red} 7153 } & {\color{ForestGreen} 0.0792 } & {\color{ForestGreen} 0.292 } & {\color{Orange} 0.496 } \\
+% max & False & -48601637 & {\color{ForestGreen} 102 } & {\color{Red} 0.9389 } & {\color{Red} 5.738 } & {\color{ForestGreen} 0.035 } \\
+% min & False & 210377447 & {\color{ForestGreen} 493 } & {\color{Red} 0.9263 } & {\color{ForestGreen} 0.233 } & {\color{Red} 4.745 } \\
+% min & True & 211183545 & {\color{ForestGreen} 692 } & {\color{Red} 0.9221 } & {\color{ForestGreen} 0.232 } & {\color{Red} 4.714 } \\
+mean & False & True & -93152163 & {\color{Orange} 3666 } & {\color{Orange} 0.1204 } & {\color{ForestGreen} 0.231 } & {\color{Red} 0.641 } \\
+sum & False & True & -93142805 & {\color{Red} 16154 } & {\color{ForestGreen} 0.0893 } & {\color{Orange} 0.301 } & {\color{Orange} 0.514 } \\
+mean & False &  & -93072127 & {\color{Orange} 3168 } & {\color{Orange} 0.1284 } & {\color{ForestGreen} 0.234 } & {\color{Red} 0.642 } \\
+sum & True & True & -92936797 & {\color{Red} 21605 } & {\color{ForestGreen} 0.0910 } & {\color{ForestGreen} 0.293 } & {\color{Orange} 0.532 } \\
+MutexWatershed & False &  & -92704851 & {\color{ForestGreen} 632 } & {\color{Orange} 0.1347 } & {\color{ForestGreen} 0.231 } & {\color{Red} 0.751 } \\
+sum & True & False & -91444880 & {\color{Red} 26842 } & {\color{Red} 0.2085 } & {\color{Red} 0.572 } & {\color{Orange} 0.489 } \\
+mean & True & True & -90660193 & {\color{Orange} 4114 } & {\color{Orange} 0.1655 } & {\color{ForestGreen} 0.213 } & {\color{Red} 1.011 } \\
+mean & True &  & -88260595 & {\color{Orange} 4393 } & {\color{Red} 0.2017 } & {\color{ForestGreen} 0.208 } & {\color{Red} 1.155 } \\
+max & True &  & -81432464 & {\color{Red} 7759 } & {\color{Orange} 0.1653 } & {\color{ForestGreen} 0.236 } & {\color{Red} 0.792 } \\
+max & False &  & -37045939 & {\color{ForestGreen} 134 } & {\color{Red} 0.9150 } & {\color{Red} 5.691 } & {\color{ForestGreen} 0.013 } \\
+min & False &  & 213670839 & {\color{ForestGreen} 600 } & {\color{Red} 0.9330 } & {\color{ForestGreen} 0.207 } & {\color{Red} 4.880 } \\
+min & True &  & 214747429 & {\color{ForestGreen} 852 } & {\color{Red} 0.9314 } & {\color{ForestGreen} 0.202 } & {\color{Red} 4.887 } \\
+
+        \end{tabular}
+        % \caption{Linkage criteria}
+    \end{subtable} 
+    \caption{Comparison of update rules on crop of cremi sample C (sorted by multicut energy) \TODO{Reduce insane amount of numbers.
+Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime} }
+    \label{tab:linkage-criteria}
+\end{table*}
 

### 2019-03-17 chapters/3_algorithm.tex
Update list of update rules and associated algs.

@@
 \section{Unified Graph Agglomerative Clustering}
-In this section we introduce a unified agglomerative clustering algorithm that represents a simple generalized formalization of many agglomerative graph clustering algorithms.
-It can be used to describe both unsigned clustering algorithms ingesting positive cluster similarities and signed clustering algorithms using attractive and repulsive cues.\\
+In this section we introduce the Unified Graph Agglomerative Clustering Algorithm (UGACA) that represents a simple generalized formalization of many agglomerative graph clustering algorithms.
+\UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive cluster similarities and signed clustering algorithms using attractive and repulsive cues.}\\
 First, we define the graph notation and the concept of cannot-link constraints.
@@
 The proposed graph partitioning algorithm is a general form of agglomerative clustering that outputs a final graph clustering $\Pi$ by progressively merging pairs of neighboring clusters.
-The algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
+Intuitively, the algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
 \ref{fig:general_idea}b and \ref{fig:general_idea}c).
@@
 
-During the agglomerative process, the interaction between neighboring clusters is defined by the linkage criterion defined in Equation \ref{eq:linkage_criterion_def} and has to be properly recomputed.
-One possible efficient way of doing this is to use an edge contraction algorithm like the one presented in Algorithm \ref{main_alg}, which proceeds as follows.
+During the agglomerative process, the interaction between neighboring clusters is defined by the linkage criterion defined in Equation \ref{eq:linkage_criterion_def} and has to be properly updated and recomputed.
+An efficient way of implementing these updates can be achieved by using the presented edge contraction Algorithm \ref{main_alg}, which proceeds as follows.
 
@@
  presenting strictly positive similarities between nodes, the algorithm then returns only one single cluster as an output (see Fig.
-\ref{fig:intro_figure}a), \UPDATE{together with a merging tree representing the merging order and defining an hierarchy of clusters} \TODO{use def of merging process of contracted graph to define merging tree}.
+\ref{fig:intro_figure}a), \UPDATE{together with a merging tree representing the merging order and defining an hierarchy of clusters} \TODO{use def of merging process of contracted graph to define merging tree?}.
 
@@
 \begin{itemize}
-\item In this section we will list \UPDATE{ALL} (...) algorithms that can be described using the generalized algorithm we presented and define some new ones
-\item In Table 1 we collected the update rules we tested and compared in this article (correspond to the simplest and cheapest ones to compute). Later we will mention more of them
-\item First unsigned graphs: the merging tree defined by the algorithm (\textbf{define merge tree somewhere..?}) is equivalent to the hierarchical dendrogram (but careful with the sum...) that we have in HC
-\item Then mention CLC and who started using them recently for this type of problem: fixed, then greedyFixation introduced exactly this algorithm as a greedy approx of MC, together with Greedy Additive Edge Contraction
-\item MWS: proposes an efficient implementation of this update rule (briefly mention the idea).
-In the Supplementary material we show that the algorithm they present can be seen as a special case of Unified Graph Agglomerative Clustering with absolute maximum update rule and that adding or not CLC does not change anything
-\item Then new versions of avg/complete and single linkage clustering 
-\item In this article we analyze only the simplest (and cheapest) types of update rules, but...
-Easily generalizable for: learned linkage criteria \cite{nunez2013machine}, something depending on node size \cite{felzenszwalb2004efficient}, quantiles, weighted average (WPGMA) and weighted sum (and related work by Paul), size rule by Thorsten
-\item comment about the fact that sum is not really an ultra-metric-distance
+\item In this section we will list some of the algorithms that can be described using the generalized algorithm we presented and define some new ones
+\item In Table 1 we collected the update rules we tested and compared in this article (correspond to the simplest and cheapest ones to compute).
+Later we will mention more of them that were proposed in the literature.
+\item In the special case of unsigned graphs (Table \ref{tab:linkage-criteria} column 1), the UGAC algorithm becomes simply a version of hierarchical clustering with different linkage criteria depending on the chosen update rule.
+It outputs one single cluster and it also defines an hierarchy of clusters during the merging process that can be associated to \UPDATE{a merging tree/  the hierarchical clustering dendrogram}...
+\TODO{Problem: sum does not trivially define an ultra-metric-distance...}
+\item In the literature there have been already several methods using cannot-link constraints for agglomerative clustering algorithms \TODO{repetition from related work}: for example, \cite{malmberg2011generalized} used initially fixed mutual exclusion relationships, whereas \cite{levinkov2017comparative} introduced them dynamically in an edge contraction algorithm for signed graphs, named Greedy Fixation (Table \ref{tab:linkage-criteria} row 1, \emph{sum}).
+At the same time, they also proposed a version of it without cannot link constraints (Greedy Additive Edge Contraction) and they compared both with other greedy and local-search algorithms for solving the multicut/correlation clustering problem.
+\item Dynamically introduced cannot-link constraints were also proposed by \cite{wolf2018mutex}, that...
+\TODO{brief MWS description as efficient implementation of this update rule}.
+In the Supplementary material we show that the algorithm they present can be seen as a special case of UGACA with absolute maximum update rule (Table \ref{tab:linkage-criteria} row 2 - \emph{absolute maximum}) and that adding or not cannot-link constraints does not change the final clustering.
+\item On the other hand, the signed graph versions of UGACA with update rules \emph{arithmetic mean}, \emph{max} and \emph{min} (rows 3 to 5 in Table \ref{tab:linkage-criteria}) are new algorithms that were never mentioned in the literature, \UPDATE{especially those with cannot-link constraints}.
+\item In this article, we test and run a comparison of the five types of update rule listed in Table \ref{tab:linkage-criteria} (i.e.
+\emph{sum}, \emph{absolute mac}, \emph{arithmetic mean}, \emph{max} and \emph{min}), since \UPDATE{they they are the most commonly used and the cheapest to compute}.
+Nevertheless, UGACA can be easily generalized to include even more complex rules.
+For instance, \cite{nunez2013machine} proposes a learned version of update rule where a neural network updates the edge weights depending on edge and node features; another really common choice is to introduce a weight regularization depending on the size of the linked nodes (\cite{felzenszwalb2004efficient} and \cite{kardoostsolving} (unpublished...??), Thorsten..);
+\cite{funke2018large} on the other hand accumulate statistics for each \UPDATE{boundary between clusters} by keeping a discrete histograms of the edge weights and then computes quantiles from it.
 \end{itemize}

### 2019-03-17 chapters/1_intro.tex
Update list of update rules and associated algs.
Small changes

@@
 \caption{\small 
-Intro image: explain algorithm, main ideas and contributions
+Intro image: explain algorithm, main ideas and contributions \TODO{Update colormap with one with two colors only? Atm it can look like another segmentation}
 \label{fig:intro_figure}}
@@
 \item we propose a unified and simple formalization of Agglomerative Clustering and show how many of the recently proposed methods can be seen as special cases (focusing in particular on signed graphs) (\textbf{review and comparison paper})
-\item we propose several new clustering algorithms, among which one proved to be robust in our experiments (average linkage with must-not-link-edges)
+\item new clustering algorithms on signed graphs
 \item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and MC energy)

### 2019-03-17 chapters/3_algorithm.tex
Small changes

@@
 
-\item A cannot-link-constraint defines a mutual exclusion relationship between two nodes in the graph and is used to specify that the these two nodes should not be associated with the same cluster.
-(the alg.
-will introduce them dynamically...)
-\item Define contracted graph and edge contraction (explain Fig. 2)
 \item Given a clustering $\Pi$ and a graph $\mathcal{G}(V,E,W)$, the interaction between two clusters $S_1, S_2 \in \Pi$ is usually defined in terms of a \emph{linkage criterion}, i.e.
@@
 \end{equation}
+
+\item A cannot-link-constraint defines a mutual exclusion relationship between two nodes in the graph and is used to specify that the these two nodes should not be associated with the same cluster.
+(the alg.
+will introduce them dynamically)
+\item Define contracted graph from given graph  $\mathcal{G}$ and clustering $\Pi$; explain edge contraction shown in Fig. 2
 
@@
 Intuitively, the algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
-\ref{fig:general_idea}b and \ref{fig:general_idea}c).
+\ref{fig:intro_figure}b and \ref{fig:intro_figure}c).
 
@@
 It iteratively pops one edge $e_{uv}$ from priority queue and, depending on the value of the priority $\tilde{w}$ associated to $e_{uv}$, does the following.
-If the edge is attractive and $\tilde{w}>0$, then perform an edge contraction of $e_{uv}$ in $\mathcal{G}'$ (see Sec.
+If the edge is attractive and $\tilde{w}>0$, then merge the connected nodes and perform an edge contraction of $e_{uv}$ in $\mathcal{G}'$ (see Sec.
 \ref{sec:contr_graph_and_CLC} and Fig.
-\ref{fig:edge_contraction_and_contr_graph}), provided that $e_{uv}$ was not previously flagged as a cannot-link constraint; for every new pair of double edges in $\mathcal{G}'$ update \UPDATE{their priorities} according to one of the update rules listed in Table \ref{tab:linkage-criteria} and update cannot-link relationships (see example in Fig.
+\ref{fig:edge_contraction_and_contr_graph}), provided that $e_{uv}$ was not previously flagged as a cannot-link constraint; for every new pair of double edges in $\mathcal{G}'$ update \UPDATE{their priorities} according to one of the update rules listed in Table \ref{tab:linkage-criteria} and update the cannot-link relationships (see example in Fig.
 \ref{fig:algorithm_with_without_CLC}b from step 3 to 4).
@@
 \begin{itemize}
-\item In this section we will list some of the algorithms that can be described using the generalized algorithm we presented and define some new ones
-\item In Table 1 we collected the update rules we tested and compared in this article (correspond to the simplest and cheapest ones to compute).
-Later we will mention more of them that were proposed in the literature.
+\item In this section we will list some of the algorithms that can be described using the generalized algorithm we presented and we will introduce some new ones.
+\item In Table \ref{tab:linkage-criteria} we collected the update rules that we tested and compared in this article. Later we will mention more of them that were proposed in the literature.
 \item In the special case of unsigned graphs (Table \ref{tab:linkage-criteria} column 1), the UGAC algorithm becomes simply a version of hierarchical clustering with different linkage criteria depending on the chosen update rule.

### 2019-03-17 chapters/3_algorithm.tex
Update figs. and cityscapes table; noise exp.

@@
 will introduce them dynamically)
-\item Define contracted graph from given graph  $\mathcal{G}$ and clustering $\Pi$; explain edge contraction shown in Fig. 2
+\item Define contracted graph from given graph  $\mathcal{G}$ and clustering $\Pi$; explain edge contraction shown in Fig. 2 and define \emph{update rule} $f(w_1, w_2)$
 
@@
 \ref{sec:contr_graph_and_CLC} and Fig.
-\ref{fig:edge_contraction_and_contr_graph}), provided that $e_{uv}$ was not previously flagged as a cannot-link constraint; for every new pair of double edges in $\mathcal{G}'$ update \UPDATE{their priorities} according to one of the update rules listed in Table \ref{tab:linkage-criteria} and update the cannot-link relationships (see example in Fig.
+\ref{fig:edge_contraction_and_contr_graph}), provided that $e_{uv}$ was not previously flagged as a cannot-link constraint; for every new pair of double edges in $\mathcal{G}'$ update \UPDATE{their priorities} according to one of the update rules listed in Table \ref{tab:linkage-criteria} and update their cannot-link relationships (see example in Fig.
 \ref{fig:algorithm_with_without_CLC}b from step 3 to 4).
@@
 
-            & & &  \thead{NO} & \thead{YES} \\        
+            & & &  \thead{\textsc{No}} & \thead{\textsc{Yes}} \\        
             % \cmidrule[0.3em]{3-5}

### 2019-03-17 chapters/5_experiments_cityscapes.tex
Update list of update rules and associated algs.
Update figs. and cityscapes table; noise exp.

--- 2019-03-14 chapters/5_experiments_cityscapes.tex
@@
 
-\begin{table*}
+\begin{table}
     \centering
-    \begin{subtable}[t!]{0.98\textwidth}\centering
-        \begin{tabular}{c| c| c | c}
-        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
-\textbf{mean} & False & {\color{ForestGreen} 0.3429 } & {\color{ForestGreen} 0.5516 } \\
-% MEAN finetuned affs avg thresh035 use log costs & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
-GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
-mean & True & {\color{Orange} 0.3154 } & {\color{Orange} 0.5269 } \\
-% MEAN constr finetuned affs avg thresh035 use log costs & {\color{Red} 0.3000 } & {\color{Orange} 0.5140 } \\
-sum & False & {\color{Red} 0.2590 } & {\color{Red} 0.4450 } \\
-% GAEC finetuned affs avg thresh035 dont use log costs & {\color{Red} 0.2371 } & {\color{Red} 0.4187 } \\
-
+    \begin{subtable}[t!]{0.5\textwidth}\centering
+        \begin{tabular}{l M{0.25\textwidth} M{0.25\textwidth}}
+        \toprule
+        & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
+        Update rule: & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
+         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
+\textbf{Mean}& \textbf{0.343}  & 0.339  \\
+GMIS \cite{liu2018affinity} & 0.341 & -  \\
+Max &   0.243  &   0.325  \\
+Abs. Max. \cite{wolf2018mutex}  & -  & 0.321 \\
+Sum \cite{levinkov2017comparative} & 0.313  & 0.319  \\
+Min &  0.000    & 0.000  \\
         \end{tabular}
@@
     \end{subtable} 
-    \caption{Results on cityscapes validation set (with finetuned affinities)}
-    \label{tab:linkage-criteria}
-\end{table*}
+    \caption{AP scores on the cityscapes validation set for UGACA and different types of update rules. \TODO{PROBLEM: all apart from GMIS uses finetuned affinities... Unfair comparison?} }
+    \label{tab:results_cityscapes}
+\end{table}
 
-\begin{table*}
-    \centering
-    \begin{subtable}[t!]{0.98\textwidth}\centering
-        \begin{tabular}{c| c| c | c}
-        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
-GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
-mean & False & {\color{Orange} 0.3359 } & {\color{ForestGreen} 0.5416 } \\
-mean & True & {\color{Orange} 0.3315 } & {\color{ForestGreen} 0.5331 } \\
-MutexWatershed & True & {\color{Red} 0.2123 } & {\color{Red} 0.3848 } \\
-SingleLinkage & False & {\color{Red} 0.1935 } & {\color{Red} 0.3615 } \\
-CompleteLinkage & False & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\
+% \begin{table}
+%     \centering
+%     \begin{subtable}[t!]{0.5\textwidth}\centering
+%         \begin{tabular}{c|| c| c| c |c }
+%         & \multicolumn{4}{c}{\thead{Add Cannot-Link-Constraints:}} \\
+%         & \multicolumn{2}{c}{\thead{\textsc{No}}} & \multicolumn{2}{c}{\thead{\textsc{Yes}}} \\
+%          & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
+% Sum & 0.55  & {\color{Orange} 0.313 } & 0.55  & {\color{Orange} 0.319 } \\\midrule
+% Abs. Max. & 0.45  & {\color{Orange} 0.321 } & & \\\midrule
+% \textbf{Mean}& \textbf{0.35 } & {\color{ForestGreen} \textbf{0.343} } & 0.25  & {\color{Orange} 0.339 } \\\midrule
 
-        \end{tabular}
-        % \caption{Linkage criteria}
-    \end{subtable} 
-    \caption{Scores on cityscapes validation set (original affinities trained by GMIS)}
-    \label{tab:linkage-criteria}
-\end{table*}
+% Max & 0.85 & {\color{Red} 0.243 } & 0.50  & {\color{Orange} 0.325 } \\\midrule
+% Min & 0.50  & {\color{Red} 0.000 } & 0.50  & {\color{Red} 0.000 } \\\midrule
+% \cite{liu2018affinity} & -  & {\color{ForestGreen} 0.341 } & - & - \\
+
+%         \end{tabular}
+%         % \caption{Linkage criteria}
+%     \end{subtable} 
+%     \caption{Results on cityscapes validation set (with finetuned affinities). \TODO{Reformat in the usual form, delete colors, less digits}}
+%     \label{tab:results_cityscapes}
+% \end{table}
 

### 2019-03-17 chapters/5_experiments_noise.tex
Update figs. and cityscapes table; noise exp.

--- 2019-03-15 chapters/5_experiments_noise.tex
@@
 % !TEX root = ../agglo_clust_review.tex
+% 
 \begin{figure}
 \centering
-\includegraphics[width=0.50\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}
-\caption{Plot illustrating results with merge-biased noise...}
-\end{figure}
+
+        \includegraphics[width=0.48\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
+
+    \caption{The two figures represent the predictions of the CNN a) without added noise, b) with the addition of the merge-biased noise defined in Eq.
+\ref{eq:opensimplex_noise_def} and c) with split-biased noise.
+The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones).
+Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries \TODO{Add colorbar?}}
+    % \label{fig:isbi-examples}
+\end{figure}%
+
+\begin{figure*}
+\centering
+        \begin{subfigure}[t]{0.48 \textwidth}
+        \centering
+        \includegraphics[width=0.98\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}
+
+        \caption{Merge-biased opensimplex noise} \label{fig:thresh}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.48 \textwidth}
+        \centering
+        \includegraphics[width=0.98\textwidth,trim=0.29in 0.31in 0.31in 0.31in,clip]{./figs/split_noise.pdf}
+        \caption{Split-biased opensimplex noise} \label{fig:ws}
+    \end{subfigure}
+
+\caption{Plot illustrating Adapted RAND scores achieved by UGACA and different update rules when noise is added to the edge weights...
+\TODO{Label which uses only local-neighbors and which uses long-range connections}}\label{fig:noise_merge}
+\end{figure*}
 
@@
 \begin{itemize}
-\item Define Perlin/opensimplex noise
+    \item In this section we will quantitatively test the robustness of UGACA by adding noise to the edge weights of the graph and see how different choices of update rules compare.
+    \item Among the update rules listed in Table \ref{tab:linkage-criteria}, we will focus only on \emph{sum}, \emph{arithmetic mean} and \emph{absolute maximum}, since they achieved the best scores in the results presented in Sec.
+\ref{sec:exp_first_comparison}.
+Before to present the results shown in Fig.
+\ref{fig:noise_merge}, we will first introduce the type of noise that was added to the edge weights.
+\item In the set of experiments presented in this article, edge weights are estimated \UPDATE{by using a CNN that predicts how likely two neighboring pixels are to be part of the same cluster}.
+Fig.
+\ref{fig:noisy_affinities}a illustrates the predictions of the CNN.
+In image processing there are several ways of adding noise to an image, among which the most common are probably  for neighboring pixels in the horizontal direction of Define Perlin/opensimplex noise
 \item Present plots
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.50\textwidth,trim=0.27in 0.27in 0.27in 0.27in,clip]{./figs/split_noise.pdf}
-\caption{Plot illustrating results with split-biased noise...}
-\end{figure}
+% \begin{figure}
+% \centering
+% \includegraphics[width=0.50\textwidth,trim=0.27in 0.27in 0.27in 0.27in,clip]{./figs/noisy_affs.pdf}
+% \caption{Illustration of noisy affinities}\label{fig:noisy_affinities}
+% \end{figure}

### 2019-03-17 chapters/supplementary.tex
Update list of update rules and associated algs.
Update figs. and cityscapes table; noise exp.

@@
     \caption{Comparison of update rules on crop of cremi sample C (sorted by multicut energy) \TODO{Reduce insane amount of numbers.
-Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime} }
-    \label{tab:linkage-criteria}
+Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime.
+Invert ARAND to make it consistent with the plots} }
+    \label{tab:results_cremi_crop_C}
 \end{table*}
+
+\begin{table}
+    \centering
+    \begin{subtable}[t!]{0.5\textwidth}\centering
+        \begin{tabular}{M{0.1\textwidth}| c| c| c | c }
+        \thead{Update \\rule} & \thead{Use Cannot-Link\\ Constraints} & \thead{Bias \\factor $\beta$} & \thead{AP} & \thead{AP 50\%} \\ \midrule\midrule
+\multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
+ &Yes & 0.55  & {\color{Orange} 0.319 } & {\color{Orange} 0.527 } \\\midrule
+Abs. max. &- & 0.45  & {\color{Orange} 0.321 } & {\color{ForestGreen} 0.531 } \\\midrule
+\multirow{2}{*}{Mean} &No & 0.35  & {\color{ForestGreen} 0.343 } & {\color{ForestGreen} 0.552 } \\
+ &Yes & 0.25  & {\color{Orange} 0.339 } & {\color{ForestGreen} 0.548 } \\\midrule
+\multirow{2}{*}{Max} &No & 0.85 & {\color{Red} 0.243 } & {\color{Red} 0.444 } \\
+ &Yes & 0.50  & {\color{Orange} 0.325 } & {\color{ForestGreen} 0.530 } \\\midrule
+\multirow{2}{*}{Min} &No & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\
+ &Yes & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\\midrule
+\cite{liu2018affinity} &-  & -  & {\color{ForestGreen} 0.341 } & {\color{ForestGreen} 0.547 } \\
+% MEAN & 0.35 & True & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
+% MEAN & 0.30 & False & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5457 } \\
+% MEAN & 0.40 & - & {\color{ForestGreen} 0.3402 } & {\color{ForestGreen} 0.5502 } \\
+% MEANconstr & 0.30 & False & {\color{Orange} 0.3344 } & {\color{ForestGreen} 0.5469 } \\
+% MEAN & 0.45 & - & {\color{Orange} 0.3333 } & {\color{ForestGreen} 0.5438 } \\
+% MEAN & 0.50 & - & {\color{Orange} 0.3255 } & {\color{ForestGreen} 0.5341 } \\
+% greedyFixation & 0.50 & - & {\color{Orange} 0.3180 } & {\color{Orange} 0.5155 } \\
+% MEANconstr & 0.20 & False & {\color{Orange} 0.3161 } & {\color{Orange} 0.5136 } \\
+% MutexWatershed & 0.50 & - & {\color{Orange} 0.3158 } & {\color{Orange} 0.5246 } \\
+% MEANconstr & 0.35 & False & {\color{Orange} 0.3154 } & {\color{Orange} 0.5269 } \\
+% greedyFixation & 0.60 & - & {\color{Orange} 0.3135 } & {\color{Orange} 0.5196 } \\
+% GAEC & 0.50 & - & {\color{Orange} 0.3112 } & {\color{Orange} 0.5085 } \\
+% SingleLinkagePlusCLC & 0.45 & - & {\color{Orange} 0.3109 } & {\color{Orange} 0.5134 } \\
+% GAEC & 0.60 & - & {\color{Orange} 0.3100 } & {\color{Orange} 0.5120 } \\
+% greedyFixation & 0.65 & - & {\color{Orange} 0.3056 } & {\color{Orange} 0.5063 } \\
+% greedyFixation & 0.45 & - & {\color{Orange} 0.3045 } & {\color{Red} 0.4989 } \\
+% GAEC & 0.65 & - & {\color{Orange} 0.3035 } & {\color{Orange} 0.5072 } \\
+% GAEC & 0.45 & - & {\color{Orange} 0.3008 } & {\color{Red} 0.4956 } \\
+% MEANconstr & 0.35 & True & {\color{Red} 0.3000 } & {\color{Orange} 0.5140 } \\
+% MEANconstr & 0.40 & False & {\color{Red} 0.2983 } & {\color{Orange} 0.5076 } \\
+% GAEC & 0.70 & - & {\color{Red} 0.2943 } & {\color{Red} 0.4989 } \\
+% SingleLinkagePlusCLC & 0.55 & - & {\color{Red} 0.2942 } & {\color{Orange} 0.5074 } \\
+% greedyFixation & 0.70 & - & {\color{Red} 0.2919 } & {\color{Red} 0.4906 } \\
+% GAEC & 0.75 & - & {\color{Red} 0.2793 } & {\color{Red} 0.4784 } \\
+% greedyFixation & 0.75 & - & {\color{Red} 0.2750 } & {\color{Red} 0.4707 } \\
+% SingleLinkagePlusCLC & 0.60 & - & {\color{Red} 0.2681 } & {\color{Red} 0.4744 } \\
+% GAEC & 0.35 & True & {\color{Red} 0.2590 } & {\color{Red} 0.4450 } \\
+% greedyFixation & 0.35 & - & {\color{Red} 0.2587 } & {\color{Red} 0.4484 } \\
+% MutexWatershed & 0.40 & - & {\color{Red} 0.2562 } & {\color{Red} 0.4505 } \\
+% MEANconstr & 0.50 & - & {\color{Red} 0.2507 } & {\color{Red} 0.4443 } \\
+% SingleLinkagePlusCLC & 0.40 & - & {\color{Red} 0.2490 } & {\color{Red} 0.4411 } \\
+% SingleLinkagePlusCLC & 0.65 & - & {\color{Red} 0.2489 } & {\color{Red} 0.4401 } \\
+% greedyFixation & 0.35 & - & {\color{Red} 0.2438 } & {\color{Red} 0.4297 } \\
+% GAEC & 0.35 & False & {\color{Red} 0.2371 } & {\color{Red} 0.4187 } \\
+% SingleLinkage & 0.80 & - & {\color{Red} 0.2336 } & {\color{Red} 0.4265 } \\
+% SingleLinkagePlusCLC & 0.70 & - & {\color{Red} 0.2285 } & {\color{Red} 0.4045 } \\
+% SingleLinkage & 0.75 & - & {\color{Red} 0.2265 } & {\color{Red} 0.4065 } \\
+% MutexWatershed & 0.35 & - & {\color{Red} 0.2253 } & {\color{Red} 0.4004 } \\
+% SingleLinkage & 0.70 & - & {\color{Red} 0.2213 } & {\color{Red} 0.3947 } \\
+% SingleLinkagePlusCLC & 0.35 & - & {\color{Red} 0.2213 } & {\color{Red} 0.3954 } \\
+% SingleLinkage & 0.65 & - & {\color{Red} 0.2177 } & {\color{Red} 0.3889 } \\
+% SingleLinkage & 0.60 & - & {\color{Red} 0.2116 } & {\color{Red} 0.3842 } \\
+% SingleLinkagePlusCLC & 0.75 & - & {\color{Red} 0.2093 } & {\color{Red} 0.3785 } \\
+% SingleLinkage & 0.55 & - & {\color{Red} 0.1987 } & {\color{Red} 0.3700 } \\
+% SingleLinkage & 0.50 & - & {\color{Red} 0.1952 } & {\color{Red} 0.3659 } \\
+% SingleLinkage & 0.35 & - & {\color{Red} 0.1852 } & {\color{Red} 0.3463 } \\
+
+        \end{tabular}
+        % \caption{Linkage criteria}
+    \end{subtable} 
+    \caption{Results on cityscapes validation set (with finetuned affinities). \TODO{Reformat in the usual form, delete colors, less digits}}
+    \label{tab:results_cityscapes_full}
+\end{table}
 

### 2019-03-18 chapters/3_algorithm.tex
"Finish" draft of noise exp. section

@@
 Intuitively, the algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
-\ref{fig:intro_figure}b and \ref{fig:intro_figure}c).
+\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}b} and \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}c}).
 
@@
  presenting strictly positive similarities between nodes, the algorithm then returns only one single cluster as an output (see Fig.
-\ref{fig:intro_figure}a), \UPDATE{together with a merging tree representing the merging order and defining an hierarchy of clusters} \TODO{use def of merging process of contracted graph to define merging tree?}.
+\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}), \UPDATE{together with a merging tree representing the merging order and defining an hierarchy of clusters} \TODO{use def of merging process of contracted graph to define merging tree?}.
 
@@
             % \cline{4-5}
-            & & &  \multicolumn{2}{c}{\thead{Add Cannot-Link-Constraints:}} \\
+            & & &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
 

### 2019-03-18 chapters/5_experiments_noise.tex
"Finish" draft of noise exp. section

--- 2019-03-15 chapters/5_experiments_noise.tex
@@
 % !TEX root = ../agglo_clust_review.tex
+% 
 \begin{figure}
 \centering
-\includegraphics[width=0.50\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}
-\caption{Plot illustrating results with merge-biased noise...}
-\end{figure}
 
-\subsection{Noise experiments}
+        \includegraphics[width=0.48\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
+
+    \caption{The two figures represent the predictions of the CNN on the CREMI dataset (\UPDATE{REF}) a) without added noise, b) with the addition of the merge-biased noise defined in Eq.
+\ref{eq:opensimplex_noise_def} and c) with split-biased noise.
+The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones).
+Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries \TODO{Add colorbar?
+Adapt to noise defs}}
+    \label{fig:noisy_affs}
+\end{figure}%
+
+\begin{figure*}
+\centering
+        \begin{subfigure}[t]{0.48 \textwidth}
+        \centering
+        \includegraphics[width=0.98\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}
+
+        \caption{Merge-biased opensimplex noise} \label{fig:thresh}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.48 \textwidth}
+        \centering
+        \includegraphics[width=0.98\textwidth,trim=0.29in 0.31in 0.31in 0.31in,clip]{./figs/split_noise.pdf}
+        \caption{Split-biased opensimplex noise} \label{fig:ws}
+    \end{subfigure}
+
+\caption{Plot illustrating Adapted RAND scores achieved by UGACA and different update rules when noise is added to the edge weights...
+\TODO{Label which uses only local-neighbors and which uses long-range connections}}\label{fig:noise_plots}
+\end{figure*}
+
+\subsection{Testing the robustness of the algorithms}
+ In this section we will quantitatively test the robustness of UGACA by adding noise to the edge weights of the graph and see how different choices of update rules compare.
+
+ Among the update rules listed in Table \ref{tab:linkage-criteria}, we will focus only on \emph{sum}, \emph{arithmetic mean} and \emph{absolute maximum}, since they achieved the best scores in the results presented in Sec.
+\ref{sec:exp_first_comparison}.
+Before to present the results shown in Fig.
+\ref{fig:noise_merge}, we will first introduce the type of noise that was added to the edge weights.
+
+ In the set of experiments presented in this article, edge weights are estimated \UPDATE{by using a CNN that predicts how likely two neighboring pixels are to be part of the same cluster}.
+Fig.
+\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}a} illustrates the predictions of the CNN on the CREMI dataset for neuron segmentation.
+We would now like to make these predictions worse by introducing  artifacts, \UPDATE{e.g.
+partially deleted or added boundaries between neurons in the image}.
+In the field of image processing there are several ways of adding noise to an image, among which the most common are Gaussian noise or Poisson shot noise.
+By using these methods, the noise value of each pixel is independent of noise values of neighboring pixels, thus they are not a good choice for our application since the pixelwise predictions of a CNN are usually spatially correlated.
+
+ We then decided to use Perlin noise\footnote{In our experiments, we used opensimplex noise, that is a more recent open-source version of Perlin noise (\UPDATE{REF or link?})}, one of the most common gradient noises used in procedural pattern generation.
+This type of noise generates spatial random patterns that are locally smooth but have large and diverse variations on bigger scales.
+It generates values $n(x)\in[0,1]$ that were mapped to $[-\infty, \infty]$ with the Logit function, $N(x)=\mathrm{Logit}(n(x))$, and then combined with the original CNN predictions $F(x)=\mathrm{Logit}(p(x))$ in the two different following ways:
+\begin{equation}
+% \tilde{F}(x;\theta)=\begin{cases}
+% F(x;\theta)+\mathcal{K}\cdot\max\left(N(x),0\right) & \text{if merge-biased}\\
+% F(x;\theta)+\mathcal{K}\cdot\min\left(N(x),0\right) & \text{if split-biased}
+% \end{cases}
+\tilde{F}_{\pm}(x;\mathcal{K})=F(x)\pm\big|\mathcal{K}\cdot\max\left(\pm N(x),0\right)\big|,
+\end{equation}
+In this equation, $\mathcal{K}\in \mathbb{R}^+$ is a positive factor representing the amount of added noise; $\tilde{F}_{+}(x;\mathcal{K})$ represents a merge-biased modified version of the CNN predictions $F(x)$, such that the probability for two pixels to be in the same cluster is increased only if $N(x)>0$ (see Fig.
+\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b}); on the other hand, $\tilde{F}_{-}(x;\mathcal{K})$ represents a split-biased prediction with decreased probabilities only when $N(x)<0$ (Fig.
+\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}).
+In the Supplementary material we provide a detailed description of the parameters used for the noise generation.
+
+With this strategy, we randomly perturbed the CNN predictions and the edge weights only in some parts of the image.
+The plots in Fig.
+\ref{fig:noise_plots} represent the scores achieved by UGACA with different update rules depending on the amount of noise $\mathcal{K}$ added to the edge weights.
 \begin{itemize}
-\item Define Perlin/opensimplex noise
-\item Present plots
-\item Comment about MC energy
+\item The experiments show that running UGACA on a grid graph with long-range connections always lead to better segmentations/clusterings \TODO{require def.
+of long range graph and long-range probability}
+\item The most robust version of update rule proved to be the arithmetic mean, that achieves similar scores even when a significantly noisy edge weights.
+\item The \emph{absolute maximum} update rule proposed by \cite{wolf2018mutex} provides an efficient and fast option, but it completely fails when too much noise is added.
+\item The \emph{sum} update rule version was the slowest option tested, but it was not as robust as the \emph{mean} version, probably due to its tendency to grow one cluster at the time (see Sec.
+\ref{sec:exp_first_comparison}).
+Comment about MC energy (plots in Suppl.
+Material?)
+\item On the other hand, UGACA with mean update rule and cannot-link constraints never achieves good overall scores, as we have already shown in Sec.
+\ref{sec:exp_first_comparison} and \UPDATE{Figure...?}, because \UPDATE{it tends to introduce too many false splits}.
+%Nevertheless, these additional experiments show that it provides an \UPDATE{almost true over-segmentation of the ground truth segmentation even with strongly merge-biased predictions}.
 \end{itemize}
 
-\begin{figure}
-\centering
-\includegraphics[width=0.50\textwidth,trim=0.27in 0.27in 0.27in 0.27in,clip]{./figs/split_noise.pdf}
-\caption{Plot illustrating results with split-biased noise...}
-\end{figure}
+% \begin{equation}
+% \begin{gathered}
+% \tilde{p}_{\pm}(x;\theta)=\sigma(\tilde{F}_{\pm}(x;\theta))\quad \text{where}\\
+% % \tilde{F}(x;\theta)=\begin{cases}
+% % F(x;\theta)+\mathcal{K}\cdot\max\left(N(x),0\right) & \text{if merge-biased}\\
+% % F(x;\theta)+\mathcal{K}\cdot\min\left(N(x),0\right) & \text{if split-biased}
+% % \end{cases}
+% \tilde{F}_{\pm}(x;\theta)=F(x;\theta)\pm\left|\mathcal{K}\cdot\max\left(\pm N(x),0\right)\right|
+% \end{gathered}
+% \end{equation}

### 2019-03-27 chapters/5_experiments_compare_rules.tex
Update NeurIPS style

% !TEX root = ../agglo_clust_review.tex

% \begin{figure}
% \centering
%         \begin{subfigure}[t]{0.46 \linewidth}
%         \centering
%         \includegraphics[width=0.98\textwidth]{figs/comparison/sum_F.pdf}
%         % \caption{Thresholding of local boundary maps ~(THRESH)} \label{fig:thresh}
%     \end{subfigure}%
%     \begin{subfigure}[t]{0.46 \linewidth}
%         \centering
%         \includegraphics[width=0.98\textwidth]{figs/comparison/sum_T.pdf}
%         % \caption{Watershed, seeded at local minima of the smoothed input map~(WS)} \label{fig:ws}
%     \end{subfigure}\hspace{0.5cm}%

%     % \vspace{0.3cm}
%     \begin{subfigure}[t]{0.92 \linewidth}
%         \centering
%         \includegraphics[width=1.\textwidth]{figs/comparison/MWS.pdf}
%         % \caption{Multicut partitioning based segmentation~(MC-FULL)} \label{fig:mc_full}
%     \end{subfigure}\hspace{0.5cm}

%     \begin{subfigure}[t]{0.46 \linewidth}
%         \centering
%         \includegraphics[width=0.98\textwidth]{figs/comparison/mean_F.pdf}
%         % \caption{Thresholding of local boundary maps ~(THRESH)} \label{fig:thresh}
%     \end{subfigure}%
%     \begin{subfigure}[t]{0.46 \linewidth}
%         \centering
%         \includegraphics[width=0.98\textwidth]{figs/comparison/mean_T.pdf}
%         % \caption{Watershed, seeded at local minima of the smoothed input map~(WS)} \label{fig:ws}
%     \end{subfigure}\hspace{0.5cm}%

% \begin{subfigure}[t]{0.46 \linewidth}
%         \centering
%         \includegraphics[width=0.98\textwidth]{figs/comparison/max_F.pdf}
%         % \caption{Thresholding of local boundary maps ~(THRESH)} \label{fig:thresh}
%     \end{subfigure}%
%     \begin{subfigure}[t]{0.46 \linewidth}
%         \centering
%         \includegraphics[width=0.98\textwidth]{figs/comparison/max_T.pdf}
%         % \caption{Watershed, seeded at local minima of the smoothed input map~(WS)} \label{fig:ws}
%     \end{subfigure}\hspace{0.5cm}%

% \begin{subfigure}[t]{0.46 \linewidth}
%         \centering
%         \includegraphics[width=0.98\textwidth]{figs/comparison/min_F.pdf}
%         % \caption{Thresholding of local boundary maps ~(THRESH)} \label{fig:thresh}
%     \end{subfigure}%
%     \begin{subfigure}[t]{0.46 \linewidth}
%         \centering
%         \includegraphics[width=0.98\textwidth]{figs/comparison/min_T.pdf}
%         % \caption{Watershed, seeded at local minima of the smoothed input map~(WS)} \label{fig:ws}
%     \end{subfigure}\hspace{0.5cm}%

%     % \vspace{-0.4cm}
%     \caption{Comparison of results from different update rules on signed graph with and without cannot-link constraints \TODO{add arrows/circles highlighting merge/split mistakes and correct decisions. Align; add captions}}
%     \label{fig:isbi-examples}
% \end{figure}% \captionsetup[

\subsection{Comparison of update rules} \label{sec:exp_first_comparison}
\begin{itemize}
  \item Highlight difference of the sum in Fig. \ref{fig:intro_figure}
  \item compare different choices of signed-cost-mappings (say which one worked best)
  \item present cremi crop-C table and rule out single and complete linkage
\end{itemize}

### 2019-03-27 chapters/3_algorithm.tex
Minor changes

@@
 In this section we introduce the Unified Graph Agglomerative Clustering Algorithm (UGACA) that represents a simple generalized formalization of many agglomerative graph clustering algorithms.
-\UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive cluster similarities and signed clustering algorithms using attractive and repulsive cues.}\\
-First, we define the graph notation and the concept of cannot-link constraints.
-Then, we introduce the generalized algorithm and show \UPDATE{how it can be used to introduce several new agglomerative clustering algorithms for graphs with signed weights.}
+\UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive node similarities and signed clustering algorithms using attractive and repulsive cues.}\\
+First, we define notation and the concept of cannot-link constraints.
+Then, we introduce the generalized algorithm and show \UPDATE{how it can be used to introduce several new agglomerative clustering algorithms for graphs with signed edge weights.}
 
@@
 The algorithm then sorts all edges $e\in E$ by their absolute weight $|W(e)|$ in descending order in a priority queue, so that the most attractive and the most repulsive edges are processed first.
-It iteratively pops one edge $e_{uv}$ from priority queue and, depending on the value of the priority $\tilde{w}$ associated to $e_{uv}$, does the following.
-If the edge is attractive and $\tilde{w}>0$, then merge the connected nodes and perform an edge contraction of $e_{uv}$ in $\mathcal{G}'$ (see Sec.
+It iteratively pops one edge $e_{uv}$ from priority queue and, depending on the value of the priority $\tilde{w}$ associated with $e_{uv}$, does the following: if the edge is attractive and $\tilde{w}>0$, then merge the connected nodes and perform an edge contraction of $e_{uv}$ in $\mathcal{G}'$ (see Sec.
 \ref{sec:contr_graph_and_CLC} and Fig.
@@
 
-In the Supplementary material we provide a more detailed version of the algorithm implementation (Sec.
-\ref{sec:detailed_algorithm}) and we also comment on its theoretical complexity (Sec.
+In the Supplementary material we provide a more detailed description of the algorithm (Sec.
+\ref{sec:detailed_algorithm}) and we also comment on its computational complexity (Sec.
 \ref{sec:complexity}).
@@
  In the special case of an unsigned graph %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
- presenting strictly positive similarities between nodes, the algorithm then returns only one single cluster as an output (see Fig.
-\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}), \UPDATE{together with a merging tree representing the merging order and defining an hierarchy of clusters} \TODO{use def of merging process of contracted graph to define merging tree?}.
+ presenting strictly positive similarities between nodes, the algorithm returns only one single cluster as an output (see Fig.
+\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}), \UPDATE{together with a merging tree representing the merging order and defining a hierarchy of clusters} \TODO{use def of merging process of contracted graph to define merging tree?}.
 
@@
 \begin{itemize}
-\item In this section we will list some of the algorithms that can be described using the generalized algorithm we presented and we will introduce some new ones.
+\item In this section we will list some of the algorithms that can be described using the generalized Algorithm \ref{main_alg} presented above and we will introduce some new ones.
 \item In Table \ref{tab:linkage-criteria} we collected the update rules that we tested and compared in this article. Later we will mention more of them that were proposed in the literature.
 \item In the special case of unsigned graphs (Table \ref{tab:linkage-criteria} column 1), the UGAC algorithm becomes simply a version of hierarchical clustering with different linkage criteria depending on the chosen update rule.
-It outputs one single cluster and it also defines an hierarchy of clusters during the merging process that can be associated to \UPDATE{a merging tree/  the hierarchical clustering dendrogram}...
+It outputs one single cluster and it also defines a hierarchy of clusters during the merging process that can be associated to \UPDATE{a merging tree/  the hierarchical clustering dendrogram}...
 \TODO{Problem: sum does not trivially define an ultra-metric-distance...}

### 2019-03-27 chapters/5_experiments_cityscapes.tex
"Finish" draft of noise exp. section
Minor changes

@@
 \subsection{Results on Cityscapes}
-
+In the experiments on the cityscapes dataset, we used the pipeline proposed by \cite{liu2018affinity} \UPDATE{that currently represents the method not using any external dataset like MS-COCO}...
 \begin{table}
@@
     \end{subtable} 
-    \caption{AP scores on the cityscapes validation set for UGACA and different types of update rules. \TODO{PROBLEM: all apart from GMIS uses finetuned affinities... Unfair comparison?} }
+    \caption{AP scores on the cityscapes validation set for UGACA and different types of update rules. \TODO{PROBLEM: all apart from GMIS uses finetuned affinities} }
     \label{tab:results_cityscapes}

### 2019-03-27 chapters/5_experiments_noise.tex
Minor changes

@@
 \caption{Plot illustrating Adapted RAND scores achieved by UGACA and different update rules when noise is added to the edge weights...
+Solid lines represent median values, whereas values between the 25th and the 75th percentile are shown in shade areas.
 \TODO{Label which uses only local-neighbors and which uses long-range connections}}\label{fig:noise_plots}
@@
  In this section we will quantitatively test the robustness of UGACA by adding noise to the edge weights of the graph and see how different choices of update rules compare.
-
- Among the update rules listed in Table \ref{tab:linkage-criteria}, we will focus only on \emph{sum}, \emph{arithmetic mean} and \emph{absolute maximum}, since they achieved the best scores in the results presented in Sec.
+ Among the update rules listed in Table \ref{tab:linkage-criteria}, we will only focus on \emph{sum}, \emph{arithmetic mean} and \emph{absolute maximum}, since they achieved the best scores in the results presented in Sec.
 \ref{sec:exp_first_comparison}.
-Before to present the results shown in Fig.
-\ref{fig:noise_merge}, we will first introduce the type of noise that was added to the edge weights.
+%Before to present the results shown in Fig.
+\ref{fig:noise_plots}, we will first introduce the type of noise that was added to the edge weights.
 
@@
 In this equation, $\mathcal{K}\in \mathbb{R}^+$ is a positive factor representing the amount of added noise; $\tilde{F}_{+}(x;\mathcal{K})$ represents a merge-biased modified version of the CNN predictions $F(x)$, such that the probability for two pixels to be in the same cluster is increased only if $N(x)>0$ (see Fig.
-\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b}); on the other hand, $\tilde{F}_{-}(x;\mathcal{K})$ represents a split-biased prediction with decreased probabilities only when $N(x)<0$ (Fig.
+\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b}); on the other hand, $\tilde{F}_{-}(x;\mathcal{K})$ represents a split-biased prediction with decreased probabilities only if $N(x)<0$ (Fig.
 \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}).
@@
 of long range graph and long-range probability}
-\item The most robust version of update rule proved to be the arithmetic mean, that achieves similar scores even when a significantly noisy edge weights.
+\item The most robust version of update rule proved to be the arithmetic mean, that achieves similar scores even with significantly noisy edge weights.
 \item The \emph{absolute maximum} update rule proposed by \cite{wolf2018mutex} provides an efficient and fast option, but it completely fails when too much noise is added.

### 2019-03-27 chapters/3_algorithm.tex
Improve formatting

@@
 
-\begin{figure}
+\begin{minipage}[b]{\textwidth}
         \centering
-\includegraphics[width=0.50\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
-\caption{\small 
+        \begin{minipage}[b]{0.45\textwidth}
+\centering
+        \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
+\captionof{figure}{\small 
 Example of edge contraction: the edge $e_{uv}$ is selected from priority queue; after nodes $u$ and $v$ are merged and $e_{uv}$ is deleted, there are two double edges $e_1$ and $e_2$ left in the graph...
 \label{fig:edge_contraction_and_contr_graph} }
-\end{figure}
+    \end{minipage}\hspace{0.04\textwidth}
+    \begin{minipage}[b]{0.45\textwidth}
+        \centering
+\includegraphics[width=0.8\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.png}
+\captionof{figure}{\small 
+Example of agglomerative clustering on signed graph with and without cannot-link constraints...
+\label{fig:algorithm_with_without_CLC}}
+    \end{minipage}
+\end{minipage}
 
@@
 \begin{algorithm}
-  \caption{Unified Graph Agglomerative Clustering}
+  \caption{Unified Graph Agglomerative Clustering \TODO{adapt to width}}
    \hspace*{\algorithmicindent} \textbf{Inputs:} graph $\mathcal{G}(V,E,W)$; bool {\color{blue}\texttt{addCannotLink}}  \\
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.45\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.png}
-\caption{\small 
-Example of agglomerative clustering on signed graph with and without cannot-link constraints...
-\label{fig:algorithm_with_without_CLC}}
-\end{figure}
-
 \begin{table*}
     \centering
-    \begin{subtable}[t!]{0.98\textwidth}\centering
+    \begin{subtable}[t!]{\textwidth}\centering
         \begin{tabular}{r l || c | c | c}
@@
             \midrule\midrule
-            Sum: & $f(\tilde{w}_1,\tilde{w}_2) = \tilde{w}_1+\tilde{w}_2$ & \thead{Sum Linkage\\Hierarchical Clustering} & \thead{Greedy Additive \\ Edge Contraction \cite{levinkov2017comparative}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} \\ \midrule
+            Sum: & \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \tilde{w}_1+\tilde{w}_2$} & \thead{Sum Linkage\\Hierarchical Clust.} & \thead{Greedy Additive \\ Edge Contraction \\\cite{levinkov2017comparative}} & \thead{Greedy \\Fixation \\\cite{levinkov2017comparative}} \\ \midrule
 
-            \makecell[r]{Absolute \\ maximum:} & \makecell[l]{$f(\tilde{w}_1,\tilde{w}_2) =\argmax_{\tilde{w}\in\{\tilde{w}_{1},\tilde{w}_{2}\}} \big|\tilde{w} \big| $}   & \thead{Single Linkage\\Hierarchical Clustering\\ \cite{lance1967general}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Mutex Watershed \cite{wolf2018mutex}} \\ \midrule
+            \makecell[r]{Abs. \\ max:} & \thead[l]{
+            $
+            f(\tilde{w}_1,\tilde{w}_2) = \begin{cases} 
+            \tilde{w}_1 & \text{if}\,\, |\tilde{w}_1|>|\tilde{w}_2|\\
+            \tilde{w}_2 & \text{otherwise}
+             \end{cases} 
+            $}
+               & \thead{Single Linkage\\Hierarchical Clust.\\ \cite{lance1967general}} & \thead{Mutex \\Watershed \\\cite{wolf2018mutex}} & \thead{Mutex \\Watershed \\\cite{wolf2018mutex}} \\ \midrule
+            \makecell[r]{Mean:} & \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \mathrm{wAvg}\{ \tilde{w}_1, \tilde{w}_2 \} $}                                 & \thead{ Average Linkage\\ Hierarchical Clust.
+\\(UPGMA) \cite{lance1967general}} & \thead{Average Linkage\\Signed Aggl.
+Clust.
+\\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
 
-            \makecell[r]{Arithmetic \\mean:} & $f(\tilde{w}_1,\tilde{w}_2) = \mathrm{weightedAvg}\{ \tilde{w}_1, \tilde{w}_2 \} $                                 & \thead{ Average Linkage\\ Hierarchical Clustering \\(UPGMA) \cite{lance1967general}} & \thead{Signed Agglomerative Clust.
-\\ with Average Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
+            Max: & \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \max \{ \tilde{w}_1, \tilde{w}_2 \}  $}                                 & \thead{Single Linkage\\Hierarchical Clust.\\ \cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl.
+Clust.
+\\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
 
-            Maximum: & $f(\tilde{w}_1,\tilde{w}_2) = \max \{ \tilde{w}_1, \tilde{w}_2 \}  $                                 & \thead{Single Linkage\\Hierarchical Clustering\\ \cite{lance1967general}} & \thead{Signed Agglomerative Clust.
-\\ with Single Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
-
-            Minimum:& $f(\tilde{w}_1,\tilde{w}_2) = \min \{ \tilde{w}_1, \tilde{w}_2 \}  $                                 & \thead{Complete Linkage\\ Hierarchical Clustering \\ \cite{lance1967general}}  & \thead{Signed Agglomerative Clust.
-\\ with Complete Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}
+            Min:& \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \min \{ \tilde{w}_1, \tilde{w}_2 \}  $}                                 & \thead{Complete Linkage\\ Hierarchical Clust.
+\\ \cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl.
+Clust.
+\\ (\textbf{NEW})} & \thead{\textbf{NEW}}
 

### 2019-03-27 chapters/5_experiments_cityscapes.tex
Improve formatting

@@
 In the experiments on the cityscapes dataset, we used the pipeline proposed by \cite{liu2018affinity} \UPDATE{that currently represents the method not using any external dataset like MS-COCO}...
-\begin{table}
-    \centering
-    \begin{subtable}[t!]{0.5\textwidth}\centering
-        \begin{tabular}{l M{0.25\textwidth} M{0.25\textwidth}}
-        \toprule
-        & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
-        Update rule: & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
-         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
-\textbf{Mean}& \textbf{0.343}  & 0.339  \\
-GMIS \cite{liu2018affinity} & 0.341 & -  \\
-Max &   0.243  &   0.325  \\
-Abs. Max. \cite{wolf2018mutex}  & -  & 0.321 \\
-Sum \cite{levinkov2017comparative} & 0.313  & 0.319  \\
-Min &  0.000    & 0.000  \\
-        \end{tabular}
-        % \caption{Linkage criteria}
-    \end{subtable} 
-    \caption{AP scores on the cityscapes validation set for UGACA and different types of update rules. \TODO{PROBLEM: all apart from GMIS uses finetuned affinities} }
-    \label{tab:results_cityscapes}
-\end{table}
 

### 2019-03-27 chapters/5_experiments_noise.tex
Improve formatting

@@
 %
+
 \begin{figure}
-\centering
-
-        \includegraphics[width=0.48\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
-
-    \caption{The two figures represent the predictions of the CNN on the CREMI dataset (\UPDATE{REF}) a) without added noise, b) with the addition of the merge-biased noise defined in Eq.
-\ref{eq:opensimplex_noise_def} and c) with split-biased noise.
-The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones).
-Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries \TODO{Add colorbar?
-Adapt to noise defs}}
-    \label{fig:noisy_affs}
-\end{figure}%
-
-\begin{figure*}
 \centering
@@
 \TODO{Label which uses only local-neighbors and which uses long-range connections}}\label{fig:noise_plots}
-\end{figure*}
+\end{figure}
+
+% \begin{minipage}[b]{0.48\textwidth}
+% % \begin{figure}
+%         % \begin{subfigure}[t]{0.48 \textwidth}
+%         \centering
+%         \includegraphics[width=0.98\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}
+
+%         \captionof{subfigure}{Merge-biased opensimplex noise} \label{fig:thresh}
+%     \end{minipage}\hfil
+% \begin{minipage}[b]{0.48\textwidth}
+%     % \end{subfigure}%
+%     % \begin{subfigure}[t]{0.48 \textwidth}
+%         \centering
+%         \includegraphics[width=0.98\textwidth,trim=0.29in 0.31in 0.31in 0.31in,clip]{./figs/split_noise.pdf}
+%         \captionof{subfigure}{Split-biased opensimplex noise} \label{fig:ws}
+%     % \end{subfigure}
+% \captionof{figure}{Plot illustrating Adapted RAND scores achieved by UGACA and different update rules when noise is added to the edge weights...
+Solid lines represent median values, whereas values between the 25th and the 75th percentile are shown in shade areas.
+\TODO{Label which uses only local-neighbors and which uses long-range connections}}\label{fig:noise_plots}
+% % \end{figure}
 
@@
 
+\begin{minipage}[T!]{\textwidth}
+        \centering
+        \begin{minipage}{0.45\textwidth}
+\centering
+
+        \includegraphics[width=0.85\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
+
+    \captionof{figure}{The two figures represent the predictions of the CNN on the CREMI dataset (\UPDATE{REF}) a) without added noise, b) with the addition of the merge-biased noise defined in Eq.
+\ref{eq:opensimplex_noise_def} and c) with split-biased noise.
+The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones).
+Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries \TODO{Add colorbar?
+Adapt to noise defs}}
+    \label{fig:noisy_affs}
+    \end{minipage}\hspace{0.04\textwidth}
+\begin{minipage}{0.48\textwidth}
+% \begin{table}
+    \centering
+    % \begin{subtable}[t!]{0.5\textwidth}\centering
+        \begin{tabular}{l M{0.25\textwidth} M{0.25\textwidth}}
+        \toprule
+        & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
+        Update rule: & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
+         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
+\textbf{Mean}& \textbf{0.343}  & 0.339  \\
+GMIS \cite{liu2018affinity} & 0.341 & -  \\
+Max &   0.243  &   0.325  \\
+Abs. Max. \cite{wolf2018mutex}  & -  & 0.321 \\
+Sum \cite{levinkov2017comparative} & 0.313  & 0.319  \\
+Min &  0.000    & 0.000  \\
+        \end{tabular}
+        % \caption{Linkage criteria}
+    % \end{subtable} 
+    \captionof{table}{AP scores on the cityscapes validation set for UGACA and different types of update rules. \TODO{PROBLEM: all apart from GMIS uses finetuned affinities} }
+    \label{tab:results_cityscapes}
+\end{minipage}
+\end{minipage}
+
 % \begin{equation}

### 2019-03-28 chapters/1_intro.tex
Update NeurIPS style
Update figures

--- 2019-03-17 chapters/1_intro.tex
@@
 % !TEX root = ../agglo_clust_review.tex
-
-\begin{figure}
-\centering
-\includegraphics[width=0.50\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.pdf} % left bottom right top
-\caption{\small 
-Intro image: explain algorithm, main ideas and contributions
-\label{fig:intro_figure}}
-\end{figure}
 
@@
 \end{itemize}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
+\caption{\small 
+Intro image: explain algorithm, main ideas and contributions
+\label{fig:intro_figure}}
+\end{figure}

### 2019-04-24 chapters/1_intro.tex
Updates to intro and algorithm

@@
 
+Deep convolutional neural nets (CNNs) has been successfully applied to a wide range of tasks of computer vision and pixel-level image understanding, such as \UPDATE{boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, semantic segmentation \cite{long2015fully,chen2018deeplab,kong2018recurrent}, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet}, and pose estimation \cite{wei2016convolutional,cao2017realtime}.}
+
 \begin{itemize}
-\item \textbf{General intro about CNN:} big success in pixel-level image understanding tasks: boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, semantic segmentation \cite{long2015fully,chen2018deeplab,kong2018recurrent}, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet}, pose estimation \cite{wei2016convolutional,cao2017realtime}...
 % \SOURCE{\cite{kong2018recurrent}}
-\item Many recent successful methods generate \textbf{region proposals} and classify the objects in the bounding box \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}
-\item \emph{Why we do not like them}:
+\item \emph{Instance segmentation} is a task of computer vision that involves the detection of all objects in an image by performing pixel-level segmentation of each instance.   
+\item Many recent successful methods for instance segmentation %, usually named \emph{proposal-based methods}, 
+ use heuristic approaches that start from the classical computer vision task of \emph{object detection}, where the goal is to localize each objects using a bounding box, and then predict both a pixel-level mask of each instance and a semantic label (classify the objects in the bounding box).
+\TODO{Is it really general enough as a description...?} \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}
+\item While effective, these approaches are \UPDATE{somewhat unsatisfying (copy/paste, change: present some faults)} because:
 \begin{itemize}
-\item rely on the object detector and non-maximum suppression heuristics to accurately “count” nb. of instances, 
-\item underperform in cluttered scenes (assignment carried out independently for each detection) 
-\item not usable for wiry or articulated segments/objects 
-\item nothing in the architecture preventing a pixel to be shared between two instances
-\item number of instances is limited by nb. proposals processed by CNN (usually hundreds). 
-\item (difficult to train in an end-to-end manner: interface between instance segmentation and detection is non-differentiable)
+\item they rely on the object detector and non-maximum suppression heuristics to count how many instances are present in the image, 
+\item they tend to underperform in cluttered scenes, since instance assignment is often carried out independently for each detection; 
+\item they are not usable for wiry or articulated objects (e.g. in the field of connectomics and neuron segmenation from electron microscopy images) 
+\item their architecture do not usually prevent a pixel to be shared between multiple instances
+\item they do not scale up well since each proposal has to be singularly processed by the CNN. 
+% \item (difficult to train in an end-to-end manner: interface between instance segmentation and detection is non-differentiable)
 % \item (architecture is complex and hard to tune and “debug”...?)
@@
 
-\item Among successful \textbf{proposal-free methods} there are: predict pixel embedding vectors \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; predict short- and long-range affinities \cite{liu2018affinity,wolf2018mutex,xie2015holistically} (more details in related work)
+\item Currently there are two successful approaches used for proposal-free instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likelity it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}
 
-\item In both approaches we can obtain the final segmentation by using a \textbf{graph clustering algorithm}
+\item Both approaches requires a final clustering algorithm to output the final instance segmentation
+
+ and we can define a grid graph, where each vertex represents a pixel, with short- and long-range edge connections
+
+ and find the final instance segmentation by using a graph clustering algorithm.
+
 \item Recent work (\cite{wolf2018mutex}, more...) shows that it is better to use \textbf{repulsion and attraction} (directly predict it with the classifier, no need to define seeds or to fix a threshold given an hierarchy of clusters)

### 2019-04-24 chapters/2_rel_work.tex
Update list of update rules and associated algs.
Update NeurIPS style
Updates to intro and algorithm

--- 2019-03-14 chapters/2_rel_work.tex
@@
 \item Generate region proposals or bounding boxes and classify the objects in the bounding box \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}; fully convolutional  box proposals \cite{li2017fully}.
-\item \emph{More references:} use an object detector to enumerate candidate instances and then perform pixel-level segmentation of each instance \cite{liang2018proposal,dai2016instance,li2017fully,liang2016reversible,arnab2017pixelwise} or generate generic proposal segments and then label each one with a semantic detector \cite{hariharan2014simultaneous,chen2015multi,hariharan2015hypercolumns,dai2015convolutional,uhrig2016pixel,he2017mask}.
+\item \emph{More references:} or generate generic proposal segments and then label each one with a semantic detector \cite{hariharan2014simultaneous,chen2015multi,hariharan2015hypercolumns,dai2015convolutional,uhrig2016pixel,he2017mask}.
+\item these somehow still uses some kind of object detector (at least to find the number of objects), but they do not necessary analyse one proposal at the time: use an object detector to enumerate candidate instances and then perform pixel-level segmentation of each instance \cite{liang2018proposal,dai2016instance,li2017fully,liang2016reversible,arnab2017pixelwise} \TODO{check \cite{dai2016instance}}
 % \SOURCE{\cite{kong2018recurrent}
@@
 \item box-free \cite{pinheiro2015learning,pinheiro2016learning,hu2017fastmask}; joint segmentation and instance labeling in a combinatorial framework \cite{kirillov2017instancecut}; recurrent models \cite{romera2016recurrent,ren2017end}; encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; sequential framework to gradually group from points to lines and then instances \cite{liu2017sgn}
+% \item From end-to-end recurrent attention: \textit{Other approaches us- ing FCNs are proposal-free, but rely on a \textbf{bottom-up merging process}\textbf{}.
+Liang et al.
+[26] predict dense pixel prediction of ob- ject location and size, using clustering as a post-processing step.
+Uhrig et al.
+[41] present another approach based on FCNs, which is trained to produces a semantic segmen- tation as well as an instance-aware angle map, encoding the instance centroids.
+Post-processing based on template matching and instance fusion produces the instance identi- ties.
+Importantly, they also used ground-truth depth labels in training.
+Concurrent work [2, 19, 22] also explores a similar idea of using FCNs to output instance-sensitive embeddings.}
 \item \textbf{Pixel embedding vectors}: 
@@
     \item usually we build an hierarchy of clusters (or a \emph{merge-tree}): \TODO{find meaningful order}
+    \item clustering paper suggested by Roman
 

### 2019-04-24 chapters/3_algorithm.tex
Update figures
Updates to intro and algorithm

@@
 
-\begin{minipage}[b]{\textwidth}
+\begin{minipage}[t]{\textwidth}
         \centering
-        \begin{minipage}[b]{0.45\textwidth}
+        \begin{minipage}[t]{0.45\textwidth}
 \centering
@@
     \end{minipage}\hspace{0.04\textwidth}
-    \begin{minipage}[b]{0.45\textwidth}
+    \begin{minipage}[t]{0.45\textwidth}
         \centering
-\includegraphics[width=0.8\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.png}
+\includegraphics[width=0.8\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.jpg}
 \captionof{figure}{\small 
@@
 
-\subsection{Contracted graph and cannot-link constraints} \label{sec:contr_graph_and_CLC}
+\subsection{Signed graph formalism: edge contraction and cannot-link constraints} \label{sec:contr_graph_and_CLC}
 
 \begin{itemize}
-\item Define graph formalism and clustering $\Pi$. Make comment about special case of unsigned graph
-\item Define multicut and associated energy
+\item \TODO{First define clustering, then weights, costs} We consider the problem of clustering a simple graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes.
+The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+$ to each edge $e \in E$ representing a merge affinity: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that several formalisms defining unsigned weighted graphs associate to each edge a positive scalar that represents a metric or distance on the graph.
+In these formalisms, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+: E \rightarrow \mathbb{R}^+$.}.
+On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^-$ to each edge: the higher this weight, the greater the desire of the incident vertices to be in different clusters.
+Graphs that have only positive weights can be seen as special cases of the previously defined graph $\mathcal{G}(V,E,w^+,w^-)$, when $w^-_e=0$ for every $e \in E$.
 
+\item The set $\Pi$ is defined as a partition of the set of nodes $V$ into $K$ subsets if $V = \cup_{i=1}^K S_i $ and $S_i \cap S_j = \emptyset$ for every $i\neq j \in \{1, ..., K\}$.
+We call a partition $\Pi$ of $V$ a \emph{clustering} if every $S \in \Pi$ induces a connected subgraph (\emph{cluster}) of $\mathcal{G}$.
+\item For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^0_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^1$ the complementary set of edges whose linked nodes belong to distinct clusters:
+
+\begin{align}
+E_\Pi^0 &= \{ uv \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \\
+E^1_\Pi &= E \setminus E^0_\Pi.
+\end{align}
+
+The set of edges $E_\Pi^1$ is known as the \emph{multicut} of $\mathcal{G}$ associated to the clustering $\Pi$. 
+\item Often, graphs with both attractive and repulsive edge attributes are described in terms of a cost function $c: E \rightarrow \mathbb{R}$   The NP-hard multicut graph partition problem also called \emph{correlation clustering} \TODO{cits} amounts to finding a graph multicut $E^1_\Pi$ for which the sum of costs $c_e = w^-_e - w^+_e$
+for every edge e
 \item Given a clustering $\Pi$ and a graph $\mathcal{G}(V,E,W)$, the interaction between two clusters $S_1, S_2 \in \Pi$ is usually defined in terms of a \emph{linkage criterion}, i.e.
@@
 will introduce them dynamically)
-\item Define contracted graph from given graph  $\mathcal{G}$ and clustering $\Pi$; explain edge contraction shown in Fig. 2 and define \emph{update rule} $f(w_1, w_2)$
+\item The algorithm that we will present in the next section iteratively performs a sequence of \emph{edge contractions} on the original graph $\mathcal{G}(V,E,w^+, w^-)$.
+
+\item define \emph{update rule} $f(c_1, c_2)$
 

### 2019-04-24 chapters/1_intro.tex
Restructure introduction

@@
 
-Deep convolutional neural nets (CNNs) has been successfully applied to a wide range of tasks of computer vision and pixel-level image understanding, such as \UPDATE{boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, semantic segmentation \cite{long2015fully,chen2018deeplab,kong2018recurrent}, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet}, and pose estimation \cite{wei2016convolutional,cao2017realtime}.}
+\begin{itemize}
+\item \emph{Possible intro about aggl.
+clustering:} \UPDATE{Hierarchical, agglomerative clustering is an important and well-established technique in unsupervised machine learning.
+Agglomerative clustering schemes start from the partition of the data set into singleton nodes and merge step by step the current pair of mutually closest nodes into a new node until there is one final node left, which comprises the entire data set.
+Various clustering schemes share this procedure as a common definition, but differ in the way in which the measure of inter-cluster dissimilarity is updated after each step.
+} %\cite{mullner2011modern}
+
+\item \emph{Other possible intro:} Many problems in computer vision involve clustering.
+Partitional clustering, such as k-means [1], determines all clusters at once, while agglomerative clustering [1] begins with a large number of small clusters, and iteratively selects two clusters with the largest affinity under some measures to merge, until some stopping condition is reached.
+Ag- glomerative clustering has been studied for more than half a century, and used in many applications [1], because it is conceptually simple and produces an informative hierar- chical structure of clusters.
+% FROM https://arxiv.org/pdf/1208.5092.pdf#page14
+
+\item Get more specific about graph (we do not cluster points in a space, but we cluster vertices with specified neighbors and interactions given by edges).
+
+\item HC is a popular graph partitioning algorithm.
+Why: more efficient than divisive approaches and graph cuts; does not usually require to specify the final number of clusters (e.g.
+spectral clustering) or seed nodes (e.g.
+watershed, random walker).
+\UPDATE{And if the graph is not dense, HC algorithms scale up well with complexity}
+
+\item Motivation 1:
 
 \begin{itemize}
+
+\item all HC methods only talk about positive edge weights, but it is actually easy to generalize them for negative and attractive edges. 
+\item The standard version of HC is good for building hierarchy but problem with hierarchical merge-trees is how to choose one single threshold.
+Choose one single fixed density level.
+Ideally we would like to be able to cut the tree at different places to select our clusters.
+\item An important line of research is based on the observation that superior partitionings are obtained when the graph has both attractive and repulsive edges.
+Solutions that optimally balance attraction and repulsion do not require external stopping criteria such as predefined number of regions or seeds.
+This generalization leads to the NP-hard problem of correlation clustering or (synonymous) multicut (MC) partitioning.
+\emph{Alternative:} multicut / correlation clustering partitions vertices with both attractive and repulsive interactions encoded into the edges of a graph.
+Multicut has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region.
+Its great drawback is that its optimization is NP-hard.
+
+\item Contributions: (and mention introductory Figure)
+\begin{itemize}
+\item We generalize the hierarchical agglomerative clustering framework to graphs with positive and negative edge attributes
+\item We review both standard hierarchical clustering algorithms and signed graph partitioning algorithms by showing how they can be described in this simplified framework (and as special cases of the general algorithm presented in Sec.
+\ref{sec:algorithm})
+\item we introduce and test new variations of these algorithms for signed graphs
+\end{itemize}
+\end{itemize}
+
+\item Motivation 2:
+\begin{itemize}
+\item HC has been always really popular in computer vision: \emph{Instance segmentation} is a task of computer vision that involves the detection of all objects in an image by performing pixel-level segmentation of each instance.
+\item Since conventional unsigned graph agglomerative clustering algorithms, such as the well-known linkage methods [1], usually are quite sensitive to noise and outliers [1] (As their affinities are directly computed using pairwise distances between samples), most methods were based on multi-step pipelines first predicting superpixels (to reduce noise).
+\item These methods are still commonly used for specific instance segmentation applications: connectomics, build merge-tree 
+ %https://arxiv.org/pdf/1208.5092.pdf
+\item still commonly used for building merge-trees, give recent examples in connectomics (Sebastian Seung, etc...) % https://arxiv.org/abs/1608.04051
+\item Graph clustering algorithms recently gained more and more popularity with the advent of deep-learning and its application to instance segmentation
+\item Deep convolutional neural nets (CNNs) has been successfully applied to a wide range of tasks of computer vision and pixel-level image understanding, such as \UPDATE{boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, semantic segmentation \cite{long2015fully,chen2018deeplab,kong2018recurrent}, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet}, and pose estimation \cite{wei2016convolutional,cao2017realtime}.}
 % \SOURCE{\cite{kong2018recurrent}}
-\item \emph{Instance segmentation} is a task of computer vision that involves the detection of all objects in an image by performing pixel-level segmentation of each instance.   
+
+\item Currently there are two successful approaches used for proposal-free bottom-up instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likely it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}
+
+\item Both approaches requires a final clustering algorithm to output the final instance segmentation
+
+ and we can define a grid graph, where each vertex represents a pixel, with short- and long-range edge connections
+
+ and find the final instance segmentation by using a graph clustering algorithm.
+
+\item GMIS achieved 
+comparable results to methods based on object 
+proposal like Mask-R-CNN on natural images 
+(Cityscapes); MWS achieved SOA results on a 
+biological images (ISBI)
+
+\item Out contributions:
+
+\begin{itemize}
+ \item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and quality of the final clustering in terms of multicut energy) \textbf{Comparison paper}
+ \item \textit{if we get good scores on CREMI dataset}: we show that also on neuro-data it is worth to skip the hand-crafted superpixel step and compute the final segmentation directly from the CNN affinities (MWS already showed it on the ISBI dataset): main selling point is again the almost-parameter free feature of the method
+\end{itemize}
+\end{itemize}
+\end{itemize}
+
+More details about instance segmentation (move to related work)
+\begin{itemize}
+
+\item 
 \item Many recent successful methods for instance segmentation %, usually named \emph{proposal-based methods}, 
@@
 
-\item Currently there are two successful approaches used for proposal-free instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likelity it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}
+\item Currently there are two successful approaches used for proposal-free (make brief intro) instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likely it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}
 
@@
 \item new clustering algorithms on signed graphs
-\item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and MC energy)
 
@@
 \item on other datasets (connectomics) many methods are based on multi-step pipelines first predicting superpixels
-\item \textit{if we get good scores on CREMI}: we show that also on neuro-data it is worth to skip the hand-crafted superpixel step and compute the final segmentation directly from the CNN affinities (MWS already showed it on the ISBI dataset)
 

### 2019-04-24 chapters/2_rel_work.tex
Restructure introduction

@@
     \item popular in image segmentation: \textbf{agglomerative clustering}.
+    \item {\small More from \cite{mullner2011modern}: The seven most common methods are termed single, complete, average (UPGMA), weighted (WPGMA, McQuitty), Ward, centroid (UPGMC) and median (WPGMC) linkage (see Everitt et al., 2011, Table 4.1).
+They are implemented in standard numerical and statistical software such as R (R Development Core Team, 2011), MATLAB (The MathWorks, Inc., 2011), Mathematica (Wolfram Research, Inc., 2010), SciPy (Jones et al., 2001).}
     \item Why: more efficient than divisive approaches and graph cuts; does not usually require to specify the final number of clusters (e.g.
@@
     \item usually we build an hierarchy of clusters (or a \emph{merge-tree}): \TODO{find meaningful order}
-    \item clustering paper suggested by Roman
+    \item clustering paper suggested by Roman; Cocoons
 

### 2019-04-24 chapters/3_algorithm.tex
Restructure introduction

@@
 \section{Unified Graph Agglomerative Clustering}
-In this section we introduce the Unified Graph Agglomerative Clustering Algorithm (UGACA) that represents a simple generalized formalization of many agglomerative graph clustering algorithms.
+In this section we introduce the Unified Graph Agglomerative Clustering Algorithm (UGACA) that represents a simple \UPDATE{generalized} formalization of many agglomerative graph clustering algorithms.
 \UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive node similarities and signed clustering algorithms using attractive and repulsive cues.}\\
@@
 \item \TODO{First define clustering, then weights, costs} We consider the problem of clustering a simple graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes.
-The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+$ to each edge $e \in E$ representing a merge affinity: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that several formalisms defining unsigned weighted graphs associate to each edge a positive scalar that represents a metric or distance on the graph.
+The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+$ to each edge $e \in E$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that several formalisms defining unsigned weighted graphs associate to each edge a positive scalar that represents a metric or distance on the graph.
 In these formalisms, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+: E \rightarrow \mathbb{R}^+$.}.
@@
 
-\item The set $\Pi$ is defined as a partition of the set of nodes $V$ into $K$ subsets if $V = \cup_{i=1}^K S_i $ and $S_i \cap S_j = \emptyset$ for every $i\neq j \in \{1, ..., K\}$.
-We call a partition $\Pi$ of $V$ a \emph{clustering} if every $S \in \Pi$ induces a connected subgraph (\emph{cluster}) of $\mathcal{G}$.
+\item We call the set $\Pi$ a \emph{partition of nodes $V$ into $K$ subsets} if $V = \cup_{i=1}^K S_i $ and $S_i \cap S_j = \emptyset$ for every $i\neq j \in \{1, ..., K\}$.
+A partition $\Pi$ of $V$ is a \emph{clustering} if every $S \in \Pi$ induces a connected subgraph (\emph{cluster}) of $\mathcal{G}$.
 \item For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^0_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^1$ the complementary set of edges whose linked nodes belong to distinct clusters:
@@
 \begin{algorithm}
-  \caption{Unified Graph Agglomerative Clustering \TODO{adapt to width}}
+  \caption{Unified Graph Agglomerative Clustering \TODO{make it one-column style}}
    \hspace*{\algorithmicindent} \textbf{Inputs:} graph $\mathcal{G}(V,E,W)$; bool {\color{blue}\texttt{addCannotLink}}  \\
@@
 
-\subsection{The algorithm}
+\subsection{The algorithm} \label{sec:algorithm}
 

### 2019-04-24 chapters/5_experiments_intro.tex
Add and update graphics
"Finish" draft of noise exp. section
Restructure introduction

@@
 \item Introduce "Poisson" random graph with a given probability of long-range connections
-\item Comment about the short- and long-range distinction in the MWS paper? It does not work that well in practice (applying post-processing to remove small segments is easier and better solution)
+\item Comment about the short- and long-range distinction in the MWS paper? It does not work that well in practice (applying post-processing to remove small segments is easier and better solution).
+\item Ad of course we can think about a classifier that separately predict attraction and repulsion
 \item Define offset patterns (link to supplementary material), trained networks (loss, etc...) and setups on cremi and cityscapes 
+\item Mention postprocessing step: get rid of tiny segments; on CREMI we use watershed to fill the deleted parts 
 \end{itemize}

### 2019-04-24 chapters/1_intro.tex
Write introduction

@@
 
+\emph{Instance segmentation} is a task of computer vision consisting in assigning each pixel of an image to an object instance \TODO{REF}.
+The most success in instance segmentation (IS) has been achieved by applying deep learning [REF].
+There are two main types of deep learning approaches to IS: proposal-based and proposal-free methods.
+Proposal-based methods consist of two steps: object detection, for example by finding bounding boxes around the objects, and assigning pixels to the detected objects \TODO{REF}.
+Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example microscopy images of neurons \TODO{cremi, isbi}, where objects are not approximated well by bounding boxes.
+% More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)
+Proposal-free methods perform IS by directly predicting pixel features and then using a clustering algorithm for grouping pixels into object instances \TODO{REF}.
+In this paper, we focus on a proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance.
+Recently, this approach was used in \cite{liu2018affinity} to achieve a performance comparable to the proposal-based methods on the Cityscapes dataset and in \cite{wolf2018mutex} to achieve state-of-the-art results in a competitive neuron segmentation challenge.
+
+The output of the CNN can be represented as a weighted grid graph such that each node represents a pixel of the image and the weights of the edges define interactions between the pixels.
+A graph clustering algorithm is then applied to cluster pixels into instances.
+The majority of clustering methods work with positive edge weights only, representing attractive interactions between the nodes.
+These methods require the user to specify the desired numbers of segments or a termination criterion (as in spectral clustering or iterated normalized cuts) or even a stronger version of supervision in terms of seeds (as in seeded watershed or random walker).
+
+A popular method for graph clustering is hierarchical clustering (HC) which creates an hierarchy of clusters.
+Agglomerative HC is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy REF?.
+This method requires the user to choose a level in the cluster hierarchy defining the desired output clustering.
+
+Other clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between pixels [REF].
+The advantage of using signed graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters.
+For small problems, this can be done optimally by solving the so-called \emph{multicut optimization problem} or \emph{correlation clustering}; however, this problem is NP-hard and thus not scalable [REF].
+Other recently algorithms applicable to signed graphs are greedy approximations of the multicut pro
+
+As to our knowledge, related work applies HC to graphs with positive weights only \TODO{REF}.
+
 \begin{itemize}
+
 \item \emph{Possible intro about aggl.

### 2019-04-25 chapters/1_intro.tex
Finish introduction

--- 2019-04-24 chapters/1_intro.tex
@@
 
-Deep convolutional neural nets (CNNs) has been successfully applied to a wide range of tasks of computer vision and pixel-level image understanding, such as \UPDATE{boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, semantic segmentation \cite{long2015fully,chen2018deeplab,kong2018recurrent}, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet}, and pose estimation \cite{wei2016convolutional,cao2017realtime}.}
+\emph{Instance segmentation} is a task of computer vision consisting in assigning each pixel of an image to an object instance. %, where the number of instances is usually not known in advance. 
+The most success in instance segmentation (IS) has been achieved by applying deep learning \cite{he2017mask,romera2016recurrent,liu2018affinity}.
+There are two main types of successful deep learning approaches to IS: proposal-based and proposal-free methods.
+Proposal-based methods consist of two steps: object detection, for example by finding bounding boxes, and assigning pixels to the detected objects \cite{he2017mask,dai2016instance,li2017fully}.
+Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example microscopy images of neurons \cite{arganda2015crowdsourcing}, where objects are not approximated well by bounding boxes.
+% More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)
+Proposal-free methods perform IS by directly predicting pixel features and then using a clustering algorithm for grouping pixels into object instances \TODO{REFS}.
+In this work, we focus on a proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance.
+Recently, \cite{liu2018affinity} used this approach and achieved performances comparable to proposal-based methods on the Cityscapes dataset; \UPDATE{similarly, the method was used in \cite{wolf2018mutex} to achieve state-of-the-art results in a neuron segmentation challenge.}
 
-\begin{itemize}
-% \SOURCE{\cite{kong2018recurrent}}
-\item \emph{Instance segmentation} is a task of computer vision that involves the detection of all objects in an image by performing pixel-level segmentation of each instance.   
-\item Many recent successful methods for instance segmentation %, usually named \emph{proposal-based methods}, 
- use heuristic approaches that start from the classical computer vision task of \emph{object detection}, where the goal is to localize each objects using a bounding box, and then predict both a pixel-level mask of each instance and a semantic label (classify the objects in the bounding box).
-\TODO{Is it really general enough as a description...?} \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}
-\item While effective, these approaches are \UPDATE{somewhat unsatisfying (copy/paste, change: present some faults)} because:
-\begin{itemize}
-\item they rely on the object detector and non-maximum suppression heuristics to count how many instances are present in the image, 
-\item they tend to underperform in cluttered scenes, since instance assignment is often carried out independently for each detection; 
-\item they are not usable for wiry or articulated objects (e.g. in the field of connectomics and neuron segmenation from electron microscopy images) 
-\item their architecture do not usually prevent a pixel to be shared between multiple instances
-\item they do not scale up well since each proposal has to be singularly processed by the CNN. 
-% \item (difficult to train in an end-to-end manner: interface between instance segmentation and detection is non-differentiable)
-% \item (architecture is complex and hard to tune and “debug”...?)
-\end{itemize}
+In this approach, the output of the CNN can be represented as a weighted grid graph such that each node represents a pixel of the image and the weights of the edges define interactions between the pixels.
+A graph clustering algorithm is then applied to cluster pixels into instances.
+The majority of clustering methods work with positive edge weights only, representing attractive interactions between the nodes.
+These methods require the user to specify the desired numbers of segments or a termination criterion (as in spectral clustering or iterated normalized cuts) or even a stronger version of supervision in terms of seeds (as in seeded watershed or random walker).
 
-\item Currently there are two successful approaches used for proposal-free instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likelity it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}
+A popular method for graph clustering is hierarchical clustering (HC) which creates an hierarchy of clusters.
+Agglomerative HC is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}.
+This method requires the user to choose a level in the cluster hierarchy defining the desired output clustering.
 
-\item Both approaches requires a final clustering algorithm to output the final instance segmentation
+Other clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between pixels \TODO{REFS}.
+The advantage of using signed graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters.
+This can be done optimally by solving the so-called \emph{multicut optimization problem} or \emph{correlation clustering} [REF?]; however, this problem is NP-hard.
+For problems of considerable size, good approximations exist \cite{yarkony2012fast,pape2017solving}, and for even larger problems efficient greedy algorithms were recently proposed \cite{levinkov2017comparative,wolf2018mutex}.
 
- and we can define a grid graph, where each vertex represents a pixel, with short- and long-range edge connections
+Our main contribution is a framework for graph clustering that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract).
+Various existing clustering algorithms, previously introduced in \cite{levinkov2017comparative,wolf2018mutex,lance1967general}, share the general procedure defined in our framework, but differ in the way in which the interaction between clusters is updated after each agglomeration step.
+In this work, we also introduce new variations of these algorithms by allowing the possibility of enforcing mutual-exclusion relationships between clusters during the agglomeration.
 
- and find the final instance segmentation by using a graph clustering algorithm.
+Finally, \UPDATE{we test these different agglomerative clustering algorithms} on the task of instance segmentation both on the CREMI neuron segmentation challenge and the Cityscapes dataset, by comparing achieved scores, efficiency and robustness to noisy edge weights.
 
-\item Recent work (\cite{wolf2018mutex}, more...) shows that it is better to use \textbf{repulsion and attraction} (directly predict it with the classifier, no need to define seeds or to fix a threshold given an hierarchy of clusters)
-\item solving correlation clustering problem (multicut) is too expensive for this application (even using recently proposed heuristics)
-\item our contributions:
-\begin{itemize}
-\item we propose a unified and simple formalization of Agglomerative Clustering and show how many of the recently proposed methods can be seen as special cases (focusing in particular on signed graphs) (\textbf{review and comparison paper})
-\item new clustering algorithms on signed graphs
-\item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and MC energy)
-
-\end{itemize}
-\item on other datasets (connectomics) many methods are based on multi-step pipelines first predicting superpixels
-\item \textit{if we get good scores on CREMI}: we show that also on neuro-data it is worth to skip the hand-crafted superpixel step and compute the final segmentation directly from the CNN affinities (MWS already showed it on the ISBI dataset)
-
-\end{itemize}
+\TODO{Add chapters description}
 

### 2019-04-25 chapters/2_rel_work.tex
Finish introduction

@@
 \section{Related work}
+
 \begin{itemize}
+
+\item Contributions: (and mention introductory Figure)
+\begin{itemize}
+\item We generalize the hierarchical agglomerative clustering framework to graphs with positive and negative edge attributes
+\item We review both standard hierarchical clustering algorithms and signed graph partitioning algorithms by showing how they can be described in this simplified framework (and as special cases of the general algorithm presented in Sec.
+\ref{sec:algorithm})
+\item we introduce and test new variations of these algorithms for signed graphs
+\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+\item Motivation 2:
+\begin{itemize}
+\item HC has been always really popular in computer vision: \emph{Instance segmentation} is a task of computer vision that involves the detection of all objects in an image by performing pixel-level segmentation of each instance.
+\item Since conventional unsigned graph agglomerative clustering algorithms, such as the well-known linkage methods [1], usually are quite sensitive to noise and outliers [1] (As their affinities are directly computed using pairwise distances between samples), most methods were based on multi-step pipelines first predicting superpixels (to reduce noise).
+\item These methods are still commonly used for specific instance segmentation applications: connectomics, build merge-tree 
+ %https://arxiv.org/pdf/1208.5092.pdf
+\item still commonly used for building merge-trees, give recent examples in connectomics (Sebastian Seung, etc...) % https://arxiv.org/abs/1608.04051
+\item Graph clustering algorithms recently gained more and more popularity with the advent of deep-learning and its application to instance segmentation
+\item Deep convolutional neural nets (CNNs) has been successfully applied to a wide range of tasks of computer vision and pixel-level image understanding, such as \UPDATE{boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, semantic segmentation \cite{long2015fully,chen2018deeplab,kong2018recurrent}, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet}, and pose estimation \cite{wei2016convolutional,cao2017realtime}.}
+% \SOURCE{\cite{kong2018recurrent}}
+
+\item Currently there are two successful approaches used for proposal-free bottom-up instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likely it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}
+
+\item Both approaches requires a final clustering algorithm to output the final instance segmentation
+
+ and we can define a grid graph, where each vertex represents a pixel, with short- and long-range edge connections
+
+ and find the final instance segmentation by using a graph clustering algorithm.
+
+\item GMIS achieved 
+comparable results to methods based on object 
+proposal like Mask-R-CNN on natural images 
+(Cityscapes); MWS achieved SOA results on a 
+biological images (ISBI)
+
+\item Out contributions:
+
+\begin{itemize}
+ \item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and quality of the final clustering in terms of multicut energy) \textbf{Comparison paper}
+ \item \textit{if we get good scores on CREMI dataset}: we show that also on neuro-data it is worth to skip the hand-crafted superpixel step and compute the final segmentation directly from the CNN affinities (MWS already showed it on the ISBI dataset): main selling point is again the almost-parameter free feature of the method
+\end{itemize}
+\end{itemize}
+\end{itemize}
+
+More details about instance segmentation (move to related work)
+\begin{itemize}
+
+\item 
+\item Many recent successful methods for instance segmentation %, usually named \emph{proposal-based methods}, 
+ use heuristic approaches that start from the classical computer vision task of \emph{object detection}, where the goal is to localize each objects using a bounding box, and then predict both a pixel-level mask of each instance and a semantic label (classify the objects in the bounding box).
+\TODO{Is it really general enough as a description...?} \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}
+\item While effective, these approaches are \UPDATE{somewhat unsatisfying (copy/paste, change: present some faults)} because:
+\begin{itemize}
+\item they rely on the object detector and non-maximum suppression heuristics to count how many instances are present in the image, 
+\item they tend to underperform in cluttered scenes, since instance assignment is often carried out independently for each detection; 
+\item they are not usable for wiry or articulated objects (e.g. in the field of connectomics and neuron segmenation from electron microscopy images) 
+\item their architecture do not usually prevent a pixel to be shared between multiple instances
+\item they do not scale up well since each proposal has to be singularly processed by the CNN. 
+% \item (difficult to train in an end-to-end manner: interface between instance segmentation and detection is non-differentiable)
+% \item (architecture is complex and hard to tune and “debug”...?)
+\end{itemize}
+
+\item Currently there are two successful approaches used for proposal-free (make brief intro) instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likely it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}
+
+\item Both approaches requires a final clustering algorithm to output the final instance segmentation
+
+ and we can define a grid graph, where each vertex represents a pixel, with short- and long-range edge connections
+
+ and find the final instance segmentation by using a graph clustering algorithm.
+
+\item Recent work (\cite{wolf2018mutex}, more...) shows that it is better to use \textbf{repulsion and attraction} (directly predict it with the classifier, no need to define seeds or to fix a threshold given an hierarchy of clusters)
+\item solving correlation clustering problem (multicut) is too expensive for this application (even using recently proposed heuristics)
+\item our contributions:
+\begin{itemize}
+\item we propose a unified and simple formalization of Agglomerative Clustering and show how many of the recently proposed methods can be seen as special cases (focusing in particular on signed graphs) (\textbf{review and comparison paper})
+\item new clustering algorithms on signed graphs
+
+\end{itemize}
+\item on other datasets (connectomics) many methods are based on multi-step pipelines first predicting superpixels
+
+\end{itemize}
+
+\begin{itemize}
+
+\item \emph{Possible intro about aggl.
+clustering:} \UPDATE{Hierarchical, agglomerative clustering is an important and well-established technique in unsupervised machine learning.
+Agglomerative clustering schemes start from the partition of the data set into singleton nodes and merge step by step the current pair of mutually closest nodes into a new node until there is one final node left, which comprises the entire data set.
+Various clustering schemes share this procedure as a common definition, but differ in the way in which the measure of inter-cluster dissimilarity is updated after each step.
+} %\cite{mullner2011modern}
+
+\item \emph{Other possible intro:} Many problems in computer vision involve clustering.
+Partitional clustering, such as k-means [1], determines all clusters at once, while agglomerative clustering [1] begins with a large number of small clusters, and iteratively selects two clusters with the largest affinity under some measures to merge, until some stopping condition is reached.
+Ag- glomerative clustering has been studied for more than half a century, and used in many applications [1], because it is conceptually simple and produces an informative hierar- chical structure of clusters.
+% FROM https://arxiv.org/pdf/1208.5092.pdf#page14
+
+\item Get more specific about graph (we do not cluster points in a space, but we cluster vertices with specified neighbors and interactions given by edges).
+
+\item HC is a popular graph partitioning algorithm.
+Why: more efficient than divisive approaches and graph cuts; does not usually require to specify the final number of clusters (e.g.
+spectral clustering) or seed nodes (e.g.
+watershed, random walker).
+\UPDATE{And if the graph is not dense, HC algorithms scale up well with complexity}
+
+\item Motivation 1:
+
+\begin{itemize}
+
+\item all HC methods only talk about positive edge weights, but it is actually easy to generalize them for negative and attractive edges. 
+\item The standard version of HC is good for building hierarchy but problem with hierarchical merge-trees is how to choose one single threshold.
+Choose one single fixed density level.
+Ideally we would like to be able to cut the tree at different places to select our clusters.
+\item An important line of research is based on the observation that superior partitionings are obtained when the graph has both attractive and repulsive edges.
+Solutions that optimally balance attraction and repulsion do not require external stopping criteria such as predefined number of regions or seeds.
+This generalization leads to the NP-hard problem of correlation clustering or (synonymous) multicut (MC) partitioning.
+\emph{Alternative:} multicut / correlation clustering partitions vertices with both attractive and repulsive interactions encoded into the edges of a graph.
+Multicut has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region.
+Its great drawback is that its optimization is NP-hard.
+
+\end{itemize}
+
 \item \textbf{Proposal based methods} 

### 2019-04-25 chapters/1_intro.tex
Add algorithm notation

@@
 The advantage of using signed graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters.
-This can be done optimally by solving the so-called \emph{multicut optimization problem} or \emph{correlation clustering} [REF?]; however, this problem is NP-hard.
+This can be done optimally by solving the so-called \emph{multicut optimization problem} or \emph{correlation clustering} \cite{kappes2011globally,chopra1991multiway}; however, this problem is NP-hard.
 For problems of considerable size, good approximations exist \cite{yarkony2012fast,pape2017solving}, and for even larger problems efficient greedy algorithms were recently proposed \cite{levinkov2017comparative,wolf2018mutex}.

### 2019-04-25 chapters/3_algorithm.tex
Add algorithm notation

--- 2019-03-27 chapters/3_algorithm.tex
@@
 
-\begin{minipage}[b]{\textwidth}
+\begin{minipage}[t]{\textwidth}
         \centering
-        \begin{minipage}[b]{0.45\textwidth}
+        \begin{minipage}[t]{0.45\textwidth}
 \centering
         \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
-\captionof{figure}{\small 
-Example of edge contraction: the edge $e_{uv}$ is selected from priority queue; after nodes $u$ and $v$ are merged and $e_{uv}$ is deleted, there are two double edges $e_1$ and $e_2$ left in the graph...
+\captionof{figure}{{\small 
+Example of edge contraction.
+The first row represents the original graph $\mathcal{G}$, the clustering $\Pi$ (purple lines) and the edges not on the cut (highlighted in green) before and after the contraction.
+The second row shows the corresponding contracted graph $\mathcal{G'}$ and cannot-link constraints (edges with red bars).
+In step (b), edge $e_{uv}$ is contracted: nodes $u$ and $v$ are merged and $e_{uv}$ is deleted from $\mathcal{G'}$.
+In (c), the two double edges $e_1$ and $e_2$ left in $\mathcal{G'}$ after the contraction are replaced by a single constrained edge with updated cost $f(c_1, c_2)$, where $f$ is one of the update rules defined in Table \ref{tab:linkage-criteria}.}
 \label{fig:edge_contraction_and_contr_graph} }
     \end{minipage}\hspace{0.04\textwidth}
-    \begin{minipage}[b]{0.45\textwidth}
+    \begin{minipage}[t]{0.45\textwidth}
         \centering
-\includegraphics[width=0.8\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.png}
+\includegraphics[width=0.8\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.jpg}
 \captionof{figure}{\small 
@@
 
-\section{Unified Graph Agglomerative Clustering}
-In this section we introduce the Unified Graph Agglomerative Clustering Algorithm (UGACA) that represents a simple generalized formalization of many agglomerative graph clustering algorithms.
+\section{Generalized framework for Agglomerative Clustering of Signed Graphs}
+In this section we introduce the Unified Graph Agglomerative Clustering Algorithm (UGACA) that represents a simple \UPDATE{generalized} formalization of many agglomerative graph clustering algorithms.
 \UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive node similarities and signed clustering algorithms using attractive and repulsive cues.}\\
@@
 
-\subsection{Contracted graph and cannot-link constraints} \label{sec:contr_graph_and_CLC}
+\subsection{Notation and graph formalism} \label{sec:notation}
 
-\begin{itemize}
-\item Define graph formalism and clustering $\Pi$. Make comment about special case of unsigned graph
-\item Define multicut and associated energy
+Given a simple graph $\mathcal{G}(V,E)$, we call the set $\Pi$ a \emph{clustering} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $S_i \cap S_j = \emptyset$ for every $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
 
-\item Given a clustering $\Pi$ and a graph $\mathcal{G}(V,E,W)$, the interaction between two clusters $S_1, S_2 \in \Pi$ is usually defined in terms of a \emph{linkage criterion}, i.e.
-a function of all the edge weights connecting the two clusters:
-\begin{equation} \label{eq:linkage_criterion_def}
-\begin{gathered}
-\mathcal{L}(S_1,S_2) = \mathcal{L}(\mathcal{W})\quad \\
-   \text{where} \quad \mathcal{W} = \{ W(e_{uv})| u\in S_1, v\in S_2 \}.
-\end{gathered}
+In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes.
+The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+\in \mathbb{R}^+$ to each edge $e \in E$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that several formalisms defining positively weighted graphs associate to each edge a positive scalar that represents a metric or distance on the graph.
+In these formalisms, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+: E \rightarrow \mathbb{R}^+$.}.
+On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^- \in \mathbb{R}^+$ to each edge: the higher this weight, the greater the desire of the incident vertices to be in different clusters.
+Often, graphs with both attractive and repulsive edge attributes are described in terms of a \emph{signed} cost function $\cost: E \rightarrow \mathbb{R}$ that combines both edge weights into one signed scalar number:
+\begin{equation}
+\cost_e = w_e^+ - w_e^- \in \mathbb{R}, \quad \quad \forall e \in E
 \end{equation}
+Graphs that have only positive weights can be clearly seen as special cases of the previously defined graph $\mathcal{G}(V,E,w^+,w^-)$, when $w^-_e=0$ and $c_e \geq 0$ for every $e \in E$.
 
-\item A cannot-link-constraint defines a mutual exclusion relationship between two nodes in the graph and is used to specify that the these two nodes should not be associated with the same cluster.
-(the alg.
-will introduce them dynamically)
-\item Define contracted graph from given graph  $\mathcal{G}$ and clustering $\Pi$; explain edge contraction shown in Fig. 2 and define \emph{update rule} $f(w_1, w_2)$
+\paragraph{Linkage criterion}\label{par:linkage_criterion_def} We call two clusters $S_1,S_2$ \emph{adjacent} if there exists at least one edge $e_{uv}\in E$ in the original graph connecting a node $u\in S_1$ to a node $v\in S_2$:
+\begin{equation}
+ \text{$S_1, S_2 \in \Pi$ are \emph{adjacent}} \quad \Longleftrightarrow  \quad  \mathcal{B}(S_1,S_2) \equiv \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \} \neq \emptyset
+\end{equation}
+where we defined the set of edges connecting two adjacent clusters as \UPDATE{\emph{boundary}} \UPDATE{$\mathcal{B}(S_1,S_2)$}.
+The interaction between two clusters $S_1, S_2$ is usually defined as a function, named \emph{linkage criterion}, depending on the weights of all edges in the boundary $\mathcal{B}(S_1,S_2)$.
+In hierarchical agglomerative clustering and graphs with only positive weights, some examples of linkage criterion statistics are \emph{maximum} (single-linkage clustering), \emph{minimum} (complete-linkage clustering) and arithmetical average (average-linkage clustering).
 
-\end{itemize}
+\paragraph{Multicut and correlation clustering} For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^0_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^1$ the complementary set of edges whose linked nodes belong to distinct clusters:
+\begin{equation}
+E_\Pi^0 \equiv \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \qquad E^1_\Pi \equiv E \setminus E^0_\Pi.
+\end{equation}
+% \begin{align}
+% E_\Pi^0 &= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \\
+% E^1_\Pi &= E \setminus E^0_\Pi.
+% \end{align}
+The set of edges $E_\Pi^1$ is known as the \emph{multicut} of $\mathcal{G}$ associated to the clustering $\Pi$.
+The instance of the NP-hard \emph{weighted correlation clustering} or \emph{minimum cost multicut problem} w.r.t.
+$\mathcal{G}(V,E,w^+, w^-)$ \cite{kappes2011globally,chopra1991multiway,andres2015lifting} is the task of finding a clustering that optimally balance the attraction and repulsion in the graph and is given by the following optimization problem/binary integer program:
+\begin{equation}
+% \min_\Pi \texttt{MC}(\Pi) \equiv
+ \min_\Pi \sum_{e\in E} \cost_e x_e^\Pi,  \qquad \text{where} \quad x^\Pi_e = 
+ \begin{cases} 
+ 1 & \text{if } e\in E^1_\Pi \\
+ 0 & \text{otherwise}.
+ \end{cases}
+\end{equation}
+In the next chapters we will use this objective as a way to measure how balanced is a clustering found by the tested agglomerative clustering algorithms.
 
-\begin{algorithm}
-  \caption{Unified Graph Agglomerative Clustering \TODO{adapt to width}}
-   \hspace*{\algorithmicindent} \textbf{Inputs:} graph $\mathcal{G}(V,E,W)$; bool {\color{blue}\texttt{addCannotLink}}  \\
-  \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering and contracted graph $\mathcal{G}'$\\
+\begin{algorithm}[t]
+  \caption{Generalized Agglomerative Clustering Algorithm for Signed Graphs}
+   \hspace*{\algorithmicindent} \textbf{Inputs:} graph $\mathcal{G}(V,E,W)$; boolean {\color{blue}\texttt{addCannotLink}}  \\
+  \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$ and contracted graph $\mathcal{G}'$\\
   \hspace*{\algorithmicindent} 
   \begin{algorithmic}[1]
-
     % \Procedure{SignedGraphEdgeContr}{{\color{blue}bool \emph{addConstraints}}}
       % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
-      \State Initialize contracted graph $\mathcal{G}'$ from $\mathcal{G}$
+      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ and contracted graph $\mathcal{G}' \gets \mathcal{G}$
       \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
-      \State Sort edges in priority queue (PQ) in desc. order of $|W_e|$ 
+      \State Sort edges in priority queue (PQ) in descending order of absolute costs $|w^+_e - w^-_e|$ 
       \State
       \While{PQ is \textbf{not} empty}
-        \State Pop edge $e_{uv}$ in $\mathcal{G}'$ with highest priority $|\tilde{w}|$
-        \State
-        \If{({\color{ForestGreen}\textbf{$\tilde{w} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
-
+        \State Pop edge $e_{uv}$ in $\mathcal{G}'$ with highest absolute cost $|\cost|$
+        \If{({\color{ForestGreen}\textbf{$\cost > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
           % \State PQ, $\,E_\dagger,\,\, E' \gets$ \textsc{deleteDoubleEdges}($u,v$)
-
         %   \State Update costs of double edges;
         %   \State Propagate constrained flags of double edges;
-          \State Contract $e_{uv}$ in $\mathcal{G}'$
+          \State Contract $e_{uv}$ in $\mathcal{G}'$ and merge clusters in $\Pi$
           \For{every new pair of double edges $(e_1,e_2)$}
-            \State Get priorities $\tilde{w}_1, \tilde{w}_2$ of $e_1,e_2$
-            \State Use update rule $f(\tilde{w}_1,\tilde{w}_2)$ (see Table 1) to 
-            \Statex \hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent} update priority of $e_1$
-            \State Delete $e_2$ from $\mathcal{G}'$
+            % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
+            \State Delete $e_2$ from $\mathcal{G}'$ and update cost of $e_1$ with update rule $f(\cost_{e_1},\cost_{e_2})$ def. in Tab. 1 
+            % \Statex \hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent} update priority of $e_1$
+            % \State Delete $e_2$ from $\mathcal{G}'$
           \EndFor
@@
         \EndIf
-        \State
-        \If{({\color{red}\textbf{$\tilde{w} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
+        % \State
+        \If{({\color{red}\textbf{$\cost \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
           % \State Flag $e_{uv}$ as MustNotLink
@@
       \EndWhile
-
       % \For{$e  \in E$ in descending order of absolute costs $|W(e)|$}
@@
       % \EndFor
+      % \State
       \State
-      \State
-      \Return $\mathcal{G}'$
+      \Return $\Pi$, $\mathcal{G}'$
       % \State
@@
 
-\subsection{The algorithm}
+\subsection{Generalized agglomerative clustering framework} \label{sec:algorithm}
 
-We now present our first contribution: a unified algorithm for agglomerative graph clustering that can describe in a simple general form many graph partitioning algorithms previously introduced in the literature \UPDATE{and highlights the existence of totally new algorithms}.
+We now present our main contribution: a generalized framework for agglomerative graph clustering that can describe in a simple form several graph partitioning algorithms previously introduced in the literature and highlights the existence of new ones.
 
-We consider a graph $\mathcal{G}(V,E,W)$ with associated signed edge weights, where each node initially represents one cluster.
-The proposed graph partitioning algorithm is a general form of agglomerative clustering that outputs a final graph clustering $\Pi$ by progressively merging pairs of neighboring clusters.
+Given a graph $\mathcal{G}(V,E,w^+, w^-)$, the proposed generalized clustering uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merging pairs of adjacent clusters.
 Intuitively, the algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
@@
 
-A second variant of the proposed algorithm also introduces cannot-link constraints between clusters during the agglomeration and stops when all the remaining clusters have been previously constrained (option \texttt{addCannotLink} in Algorithm \ref{main_alg}).
+A second variant of the proposed algorithm also introduces \emph{cannot-link constraints}, representing mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering.
+This variant (Algorithm \ref{main_alg} with \texttt{addCannotLink=True}) stops when all the remaining clusters have been previously constrained.
 
-During the agglomerative process, the interaction between neighboring clusters is defined by the linkage criterion defined in Equation \ref{eq:linkage_criterion_def} and has to be properly updated and recomputed.
-An efficient way of implementing these updates can be achieved by using the presented edge contraction Algorithm \ref{main_alg}, which proceeds as follows.
+% The algorithm that we will present in the next section iteratively performs a sequence of so-called \emph{edge contractions} on the original graph $\mathcal{G}(V,E,w^+, w^-)$.
 
-Given an initial clustering $\Pi$ where each node of the original graph $\mathcal{G}$ represents its own cluster, the algorithm starts by initializing a contracted graph $\mathcal{G}'$ (see Definition \ref{def:contr_graph}) that will represent the clustering $\Pi$ at each iteration of the agglomeration.
+% The graph clustering algorithm we will present in Sec.
+\ref{sec:algorithm} is a bottom-up approach starting with each node assigned to its own cluster and iteratively merging clusters.
+During the agglomeration, the current clustering $\Pi$ is represented by a \emph{contracted graph} $\mathcal{G'}(\mathcal{G}, \Pi)$, such that each of its nodes represents a cluster $S \in \Pi$ and \emph{adjacent} clusters are linked by an edge.
+
+\paragraph{Edge contraction and update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.
+% given by the linkage criterion defined in Sec.
+\ref{sec:notation} and
+An efficient way of implementing these updates can be achieved by representing the clustering $\Pi$ with a \emph{contracted graph} $\mathcal{G'}(\mathcal{G}, \Pi)$, such that each of its nodes is associated to a cluster $S \in \Pi$, edges represent adjacency-relationships between clusters and edge weights inter-cluster interactions.
+\UPDATE{Every time a pair of neighboring clusters is merged, the contracted graph is updated by performing an edge contraction and merging two nodes.
+After the edge contraction, the only cluster interactions that need to be updated are those between nodes connected by double edges in the contracted graph (see Fig.
+\ref{fig:edge_contraction_and_contr_graph}, step b).
+For simple linkage criteria, these updates can be easily computed with an update rule $f$ that depends only on the interactions at the previous step }
+% As a result, the merged node could be linked to some of its neighbors by double edges .
+, representing the fact that their interaction should be updated.
+This update can be easily achieved by using an \emph{update rule} depending only on the weights of the double edges.
+\TODO{such a mess...}
+\UPDATE{In this way we do not need to recompute the interaction by using the linkage criterion over all the edges of the original graph, that would be computationally expensive.}
+
+\paragraph{The algorithm} The proposed Algorithm \ref{main_alg} proceeds as follows.
+Given an initial clustering $\Pi$ where each node of the original graph $\mathcal{G}$ represents its own cluster  \TODO{repetition}, the algorithm starts by initializing a contracted graph $\mathcal{G}'$ (see Definition \ref{def:contr_graph}) that will represent the clustering $\Pi$ at each iteration of the agglomeration.
 The algorithm then sorts all edges $e\in E$ by their absolute weight $|W(e)|$ in descending order in a priority queue, so that the most attractive and the most repulsive edges are processed first.
 It iteratively pops one edge $e_{uv}$ from priority queue and, depending on the value of the priority $\tilde{w}$ associated with $e_{uv}$, does the following: if the edge is attractive and $\tilde{w}>0$, then merge the connected nodes and perform an edge contraction of $e_{uv}$ in $\mathcal{G}'$ (see Sec.
-\ref{sec:contr_graph_and_CLC} and Fig.
+\ref{sec:notation} and Fig.
 \ref{fig:edge_contraction_and_contr_graph}), provided that $e_{uv}$ was not previously flagged as a cannot-link constraint; for every new pair of double edges in $\mathcal{G}'$ update \UPDATE{their priorities} according to one of the update rules listed in Table \ref{tab:linkage-criteria} and update their cannot-link relationships (see example in Fig.
@@
 If, on the other hand, the edge $e_{uv}$ is repulsive and $\tilde{w}\leq 0$, then flag it as a cannot-link constraint if and only if the algorithm input-option \texttt{addCannotLink} is true and mutual exclusion relationships should be enforced.
-
 In the Supplementary material we provide a more detailed description of the algorithm (Sec.
@@
 
- In the special case of an unsigned graph %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
- presenting strictly positive similarities between nodes, the algorithm returns only one single cluster as an output (see Fig.
-\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}), \UPDATE{together with a merging tree representing the merging order and defining a hierarchy of clusters} \TODO{use def of merging process of contracted graph to define merging tree?}.
+ In the special case of a graph with only positive edge interactions, i.e. $w_e^-=0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
+ the algorithm performs a standard agglomerative hierarchical clustering by returning only one single cluster (see Fig.
+\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}) and a hierarchy of clusters defined by the order in which the clusters were merged.
+ %\TODO{use def of merging process of contracted graph to define merging tree?}.
 
 % \item Comment about must-not-link relations: they give high priority to the most confident repulsive edges {}
+
+% Given a clustering $\Pi$ and a graph $\mathcal{G}(V,E,W)$, the interaction between two clusters $S_1, S_2 \in \Pi$ is usually defined in terms of a \emph{linkage criterion}, i.e.
+a function of all the edge weights connecting the two clusters:
+% \begin{equation} 
+% \begin{gathered}
+% \mathcal{L}(S_1,S_2) = \mathcal{L}(\mathcal{W})\quad \\
+%    \text{where} \quad \mathcal{W} = \{ W(e_{uv})| u\in S_1, v\in S_2 \}.
+% \end{gathered}
+% \end{equation}
 
@@
             \midrule\midrule
-            Sum: & \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \tilde{w}_1+\tilde{w}_2$} & \thead{Sum Linkage\\Hierarchical Clust.} & \thead{Greedy Additive \\ Edge Contraction \\\cite{levinkov2017comparative}} & \thead{Greedy \\Fixation \\\cite{levinkov2017comparative}} \\ \midrule
+            Sum: & \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \tilde{w}_1+\tilde{w}_2$} & \thead{Sum Linkage\\Hierarchical Aggl.\\Clustering} & \thead{Greedy Additive \\ Edge Contraction \\\cite{levinkov2017comparative}} & \thead{Greedy \\Fixation \\\cite{levinkov2017comparative}} \\ \midrule
 
@@
             $}
-               & \thead{Single Linkage\\Hierarchical Clust.\\ \cite{lance1967general}} & \thead{Mutex \\Watershed \\\cite{wolf2018mutex}} & \thead{Mutex \\Watershed \\\cite{wolf2018mutex}} \\ \midrule
-            \makecell[r]{Mean:} & \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \mathrm{wAvg}\{ \tilde{w}_1, \tilde{w}_2 \} $}                                 & \thead{ Average Linkage\\ Hierarchical Clust.
+               & \thead{Single Linkage\\Hierarchical Aggl.\\Clustering \cite{lance1967general}} & \thead{Mutex \\Watershed \\\cite{wolf2018mutex}} & \thead{Mutex \\Watershed \\\cite{wolf2018mutex}} \\ \midrule
+            \makecell[r]{Mean:} & \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \mathrm{weightAvg}\{ \tilde{w}_1, \tilde{w}_2 \} $}                                 & \thead{ Average Linkage\\ Hierarchical Clust.
 \\(UPGMA) \cite{lance1967general}} & \thead{Average Linkage\\Signed Aggl.
@@
 
-            Max: & \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \max \{ \tilde{w}_1, \tilde{w}_2 \}  $}                                 & \thead{Single Linkage\\Hierarchical Clust.\\ \cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl.
+            Max: & \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \max \{ \tilde{w}_1, \tilde{w}_2 \}  $}                                 & \thead{Single Linkage\\Hierarchical Aggl.\\Clustering \cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl.
 Clust.
@@
 
-            Min:& \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \min \{ \tilde{w}_1, \tilde{w}_2 \}  $}                                 & \thead{Complete Linkage\\ Hierarchical Clust.
-\\ \cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl.
+            Min:& \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \min \{ \tilde{w}_1, \tilde{w}_2 \}  $}                                 & \thead{Complete Linkage\\ Hierarchical Aggl.\\Clustering \cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl.
 Clust.
@@
 \begin{itemize}
-\item In this section we will list some of the algorithms that can be described using the generalized Algorithm \ref{main_alg} presented above and we will introduce some new ones.
+\item In this section we will list some of the algorithms that can be described using the generalized Algorithm \ref{main_alg} presented above \UPDATE{and we will introduce some new ones}.
 \item In Table \ref{tab:linkage-criteria} we collected the update rules that we tested and compared in this article. Later we will mention more of them that were proposed in the literature.
@@
 \item In this article, we test and run a comparison of the five types of update rule listed in Table \ref{tab:linkage-criteria} (i.e.
-\emph{sum}, \emph{absolute mac}, \emph{arithmetic mean}, \emph{max} and \emph{min}), since \UPDATE{they they are the most commonly used and the cheapest to compute}.
+\emph{sum}, \emph{absolute max}, \emph{arithmetic mean}, \emph{max} and \emph{min}), since \UPDATE{they they are the most commonly used and the cheapest to compute}.
 Nevertheless, UGACA can be easily generalized to include even more complex rules.

### 2019-04-26 chapters/1_intro.tex
Rewrite contr. graph formalism and update exp sec.

@@
 Proposal-based methods consist of two steps: object detection, for example by finding bounding boxes, and assigning pixels to the detected objects \cite{he2017mask,dai2016instance,li2017fully}.
-Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example microscopy images of neurons \cite{arganda2015crowdsourcing}, where objects are not approximated well by bounding boxes.
+Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example electron microscopy image volumes of neurons \cite{arganda2015crowdsourcing}, where objects are not approximated well by bounding boxes.
 % More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)

### 2019-04-26 chapters/3_algorithm.tex
Rewrite contr. graph formalism and update exp sec.

@@
 Given a simple graph $\mathcal{G}(V,E)$, we call the set $\Pi$ a \emph{clustering} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $S_i \cap S_j = \emptyset$ for every $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
+In the following we denote the cluster associated with node $u$ as $S_u$.
+% \begin{equation}
+% S_u \equiv S \in \Pi \,\, \text{s.t.} \,\, u \in S
+% \end{equation}
 
@@
 On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^- \in \mathbb{R}^+$ to each edge: the higher this weight, the greater the desire of the incident vertices to be in different clusters.
-Often, graphs with both attractive and repulsive edge attributes are described in terms of a \emph{signed} cost function $\cost: E \rightarrow \mathbb{R}$ that combines both edge weights into one signed scalar number:
+Often, graphs $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes are also defined as $\mathcal{G}(V,E,\cost)$, where $\cost: E \rightarrow \mathbb{R}$ represents a \emph{signed interaction} that combines both attraction and repulsion into one signed scalar number: % space: make equation in line
 \begin{equation}
@@
 \end{equation}
-Graphs that have only positive weights can be clearly seen as special cases of the previously defined graph $\mathcal{G}(V,E,w^+,w^-)$, when $w^-_e=0$ and $c_e \geq 0$ for every $e \in E$.
+Graphs that have only positive weights can be clearly seen as a special case of the previously defined graph $\mathcal{G}(V,E,w^+,w^-)$, when $w^-_e=0$ and $c_e \geq 0$ for every $e \in E$.
 
-\paragraph{Linkage criterion}\label{par:linkage_criterion_def} We call two clusters $S_1,S_2$ \emph{adjacent} if there exists at least one edge $e_{uv}\in E$ in the original graph connecting a node $u\in S_1$ to a node $v\in S_2$:
-\begin{equation}
- \text{$S_1, S_2 \in \Pi$ are \emph{adjacent}} \quad \Longleftrightarrow  \quad  \mathcal{B}(S_1,S_2) \equiv \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \} \neq \emptyset
+\paragraph{Inter-cluster interaction}\label{par:linkage_criterion_def} We call two clusters $S_1,S_2$ \emph{adjacent} if there exists at least one edge ${e_{uv}\in E}$ connecting a node $u\in S_1$ to a node $v\in S_2$.
+In agglomerative HC, the interaction $\interact_{S_1,S_2}$ between two clusters $S_1, S_2$ is usually defined as a function, named \emph{linkage criterion}, depending on the weights of all edges connecting clusters $S_1$ and $S_2$.
+For example, for a \emph{maximum} linkage criterion statistic (single-linkage), the inter-cluster interaction is given by:
+\begin{equation}\label{eq:max_linkage}
+\mathscr{W}_{S_1,S_2} = \max_{e\in U} \cost(e), \qquad \text{where}\quad U = \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \}.
 \end{equation}
-where we defined the set of edges connecting two adjacent clusters as \UPDATE{\emph{boundary}} \UPDATE{$\mathcal{B}(S_1,S_2)$}.
-The interaction between two clusters $S_1, S_2$ is usually defined as a function, named \emph{linkage criterion}, depending on the weights of all edges in the boundary $\mathcal{B}(S_1,S_2)$.
-In hierarchical agglomerative clustering and graphs with only positive weights, some examples of linkage criterion statistics are \emph{maximum} (single-linkage clustering), \emph{minimum} (complete-linkage clustering) and arithmetical average (average-linkage clustering).
+Other common choices are \emph{minimum} (complete linkage) or \emph{average} (average linkage). %and \emph{sum}.
+% \begin{equation}
+%  \text{$S_1, S_2 \in \Pi$ are \emph{adjacent}} \quad \Longleftrightarrow  \quad  \mathcal{B}(S_1,S_2) \equiv \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \} \neq \emptyset
+% \end{equation}
+% where we defined the set of edges connecting two adjacent clusters as \UPDATE{\emph{boundary}} \UPDATE{$\mathscr{W}(S_1,S_2) , \mathcal{G}'_{\mathcal{G},\Pi}(V',E')$}.
+in the boundary $\mathcal{B}(S_1,S_2)$.
+Some examples of linkage criterion statistics are \emph{maximum} (single-linkage), \emph{minimum} (complete-linkage) and average (average-linkage).
 
@@
 \end{equation}
-In the next chapters we will use this objective as a way to measure how balanced is a clustering found by the tested agglomerative clustering algorithms.
+In the next chapters we will use this objective as a way to measure how much a clustering is balanced.
 
@@
 
-Given a graph $\mathcal{G}(V,E,w^+, w^-)$, the proposed generalized clustering uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merging pairs of adjacent clusters.
+The proposed generalized clustering uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merging pairs of adjacent clusters.
 Intuitively, the algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
@@
 \ref{sec:notation} and
-An efficient way of implementing these updates can be achieved by representing the clustering $\Pi$ with a \emph{contracted graph} $\mathcal{G'}(\mathcal{G}, \Pi)$, such that each of its nodes is associated to a cluster $S \in \Pi$, edges represent adjacency-relationships between clusters and edge weights inter-cluster interactions.
-\UPDATE{Every time a pair of neighboring clusters is merged, the contracted graph is updated by performing an edge contraction and merging two nodes.
-After the edge contraction, the only cluster interactions that need to be updated are those between nodes connected by double edges in the contracted graph (see Fig.
+An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph.
+Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that $\tilde{V} \subseteq V$ and each node $u\in \tilde{V}$ represents the cluster $S_u \in \Pi$, edges in $\tilde{E}$ represent adjacency-relationships between clusters and the signed edge weights are given by inter-cluster interactions, i.e.
+$\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$.
+For the linkage criteria tested in this work, when clusters $S_u,S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$.
+Thus, we can easily express them in terms of a simple \emph{update rule} $f$.
+For instance, in the case of the single-linkage criterion defined in Eq.
+\ref{eq:max_linkage}, we can use the following simple max-update-rule to recompute the interaction between $S_u \cup S_v$ and one of its neighbors $S_t$:
+\begin{equation}
+  \interact_{S_u \cup S_v,S_t} = f( \interact_{S_u,S_t}, \interact_{S_v,S_t}) = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) = \max \{ \tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}) \}
+\end{equation}
+
+\UPDATE{Every time a pair of clusters is merged, the contracted graph is updated by performing an edge contraction and merging the associated nodes.
+The only interactions that then need to be updated are those between nodes that after the edge contraction happen to be connected by double edges (see Fig.
 \ref{fig:edge_contraction_and_contr_graph}, step b).
-For simple linkage criteria, these updates can be easily computed with an update rule $f$ that depends only on the interactions at the previous step }
+For basic linkage criteria, e.g.
+\emph{max} or \emph{min}, the new interaction can be formulated in terms of an \emph{update rule} $f$ depending only on the these updates can be computed with an update rule $f$ that depends only on the interactions at the previous step }
 % As a result, the merged node could be linked to some of its neighbors by double edges .
@@
 This update can be easily achieved by using an \emph{update rule} depending only on the weights of the double edges.
-\TODO{such a mess...}
+\TODO{such a mess...} ...without the need of running a loop over the edges of the original graph.
 \UPDATE{In this way we do not need to recompute the interaction by using the linkage criterion over all the edges of the original graph, that would be computationally expensive.}

### 2019-04-26 chapters/5_experiments_cityscapes.tex
Restructure introduction
Rewrite contr. graph formalism and update exp sec.

@@
 % !TEX root = ../agglo_clust_review.tex
-\subsection{Results on Cityscapes}
+\section{Experiments on Cityscapes}
+A successful proposal-free method was recently presented in \cite{liu2018affinity} and a setup equivalent to the one described in Sec.
+\ref{sec:grid_graph} but uses a more complex pipeline to select region of interests in the image, predict semantic pixel information that is used to improve pixel affinities, etc...
+We used exactly their code and pipeline, but we replaced their final agglomeration clustering step with the algorithms proposed in this paper...
+
 In the experiments on the cityscapes dataset, we used the pipeline proposed by \cite{liu2018affinity} \UPDATE{that currently represents the method not using any external dataset like MS-COCO}...
+
+I should mention the main trick in the loss: ignore background pixels (so focus on boundaries!)
 

### 2019-04-26 chapters/5_experiments_intro.tex
Rewrite contr. graph formalism and update exp sec.

@@
 % !TEX root = ../agglo_clust_review.tex
+\section{Experiments on neuron segmentation}
 
-\subsection{Experimental setup and tested datasets}
+We first evaluate and compare the agglomerative clustering algorithms described in the generalized framework on the task of neuron segmentation in electron microscopy (EM) image volumes.
+This application is of key interest in connectomics, a field of neuro-science with the goal of reconstructing neural wiring diagrams spanning complete central nervous systems.
+While a lot of progress is being made, only proof-reading or manual tracing yields sufficient accuracy for correct circuit reconstruction \cite{schlegel2017learning}.
+\TODO{subsections description}
+
+\subsection{Experimental setup and pixel grid-graph} \label{sec:grid_graph}
+\begin{itemize}
+\item Define predictions of the classifier (pseudo probabilities) for edge weights
+\item Define possible mappings to signed costs
+\item Make comment about which version defines nested segmentations and which does not give hirarchical solutions
+
+\end{itemize}
+
 \begin{itemize}

### 2019-04-26 chapters/3_algorithm.tex
Update algorithm description

@@
         \centering
-        \begin{minipage}[t]{0.45\textwidth}
+        \begin{minipage}[t]{0.49\textwidth}
 \centering
@@
 \captionof{figure}{{\small 
-Example of edge contraction.
-The first row represents the original graph $\mathcal{G}$, the clustering $\Pi$ (purple lines) and the edges not on the cut (highlighted in green) before and after the contraction.
-The second row shows the corresponding contracted graph $\mathcal{G'}$ and cannot-link constraints (edges with red bars).
-In step (b), edge $e_{uv}$ is contracted: nodes $u$ and $v$ are merged and $e_{uv}$ is deleted from $\mathcal{G'}$.
-In (c), the two double edges $e_1$ and $e_2$ left in $\mathcal{G'}$ after the contraction are replaced by a single constrained edge with updated cost $f(c_1, c_2)$, where $f$ is one of the update rules defined in Table \ref{tab:linkage-criteria}.}
+Example of edge contraction of $e_{uv}$.
+The first row represents the original graph $\mathcal{G}$ and the clustering $\Pi$ (purple lines), where green edges are not on the cut.
+Red bars indicate cannot-link constraints, whereas the contracted graph $\tilde{\mathcal{G}}_\Pi$ is shown in the second row.
+In step (ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$.
+In (iii), the two double edges $e_{ut}$ and $e_{vt}$ resulting from the contraction are replaced by a single constrained edge with updated interaction $f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}))$, where $f$ is defined in Table \ref{tab:linkage-criteria}.}
 \label{fig:edge_contraction_and_contr_graph} }
-    \end{minipage}\hspace{0.04\textwidth}
-    \begin{minipage}[t]{0.45\textwidth}
+    \end{minipage}\hspace{0.01\textwidth}
+    \begin{minipage}[t]{0.49\textwidth}
         \centering
@@
 \captionof{figure}{\small 
-Example of agglomerative clustering on signed graph with and without cannot-link constraints...
+\UPDATE{Comparison of \algname{}  with (top) and without (bottom) enforcing cannot-link constraints on a toy graph with positive (green) and repulsive (red) interactions.
+Only contracted graph is represented; every column represent one iteration of the algorithm; the selected edge at each iteration is highlighted in yellow; constrained edges are represented with red bars.
+We note that the two resulting clusterings are different.}
 \label{fig:algorithm_with_without_CLC}}
@@
 
-\section{Generalized framework for Agglomerative Clustering of Signed Graphs}
-In this section we introduce the Unified Graph Agglomerative Clustering Algorithm (UGACA) that represents a simple \UPDATE{generalized} formalization of many agglomerative graph clustering algorithms.
+\section{Generalized framework for Signed Graphs Agglomerative Clustering}
+In this section we introduce the proposed framework for agglomerative clustering of signed graphs. 
+%that represents a simple \UPDATE{generalized} formalization of many agglomerative graph clustering algorithms.
 \UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive node similarities and signed clustering algorithms using attractive and repulsive cues.}\\
-First, we define notation and the concept of cannot-link constraints.
-Then, we introduce the generalized algorithm and show \UPDATE{how it can be used to introduce several new agglomerative clustering algorithms for graphs with signed edge weights.}
+First, we define the graph notation in Sec.
+\ref{sec:notation}, then we introduce the generalized algorithm in Sec.
+\ref{sec:algorithm} and finally we show \UPDATE{how it represents a generalized version of several existing and new graph clustering algorithms (Sec.
+\ref{sec:alg_update_rules}).}
 
@@
 \end{equation}
-Graphs that have only positive weights can be clearly seen as a special case of the previously defined graph $\mathcal{G}(V,E,w^+,w^-)$, when $w^-_e=0$ and $c_e \geq 0$ for every $e \in E$.
+Graphs that have only positive weights can be clearly seen as a special case of the previously defined graph $\mathcal{G}(V,E,w^+,w^-)$, when $w^-_e=0$ and $\cost_e \geq 0$ for every $e \in E$.
 
@@
 \begin{equation}\label{eq:max_linkage}
-\mathscr{W}_{S_1,S_2} = \max_{e\in U} \cost(e), \qquad \text{where}\quad U = \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \}.
+\interact_{S_1,S_2} = \, \max_{e\in U} \cost(e), \qquad \text{where}\quad U = \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \}.
 \end{equation}
@@
 % \end{align}
-The set of edges $E_\Pi^1$ is known as the \emph{multicut} of $\mathcal{G}$ associated to the clustering $\Pi$.
+The set of edges $E_\Pi^1$ is known as the \emph{multicut} of $\mathcal{G}$ w.r.t.
+clustering $\Pi$.
 The instance of the NP-hard \emph{weighted correlation clustering} or \emph{minimum cost multicut problem} w.r.t.
@@
 \begin{algorithm}[t]
-  \caption{Generalized Agglomerative Clustering Algorithm for Signed Graphs}
-   \hspace*{\algorithmicindent} \textbf{Inputs:} graph $\mathcal{G}(V,E,W)$; boolean {\color{blue}\texttt{addCannotLink}}  \\
-  \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$ and contracted graph $\mathcal{G}'$\\
+  \caption{Generalized Algorithm for Signed Graphs Agglomerative Clustering}
+   \hspace*{\algorithmicindent} \textbf{Inputs:} Graph $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes; boolean variable {\color{blue}\texttt{addCannotLink}}  \\
+  \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$\\
   \hspace*{\algorithmicindent} 
@@
       % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
-      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ and contracted graph $\mathcal{G}' \gets \mathcal{G}$
+      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ and contracted graph $\tilde{\mathcal{G}}_\Pi \gets \mathcal{G}$
       \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
-      \State Sort edges in priority queue (PQ) in descending order of absolute costs $|w^+_e - w^-_e|$ 
+      \State Sort edges in priority queue (PQ) in descending order of priority $|\cost_e|=|w^+_e - w^-_e|$ 
       \State
       \While{PQ is \textbf{not} empty}
-        \State Pop edge $e_{uv}$ in $\mathcal{G}'$ with highest absolute cost $|\cost|$
-        \If{({\color{ForestGreen}\textbf{$\cost > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
+        \State Pop edge $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ with highest absolute interaction $|\tilde{\cost}|$
+        \If{({\color{ForestGreen}\textbf{$\tilde{\cost} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
           % \State PQ, $\,E_\dagger,\,\, E' \gets$ \textsc{deleteDoubleEdges}($u,v$)
@@
         %   \State Propagate constrained flags of double edges;
-          \State Contract $e_{uv}$ in $\mathcal{G}'$ and merge clusters in $\Pi$
-          \For{every new pair of double edges $(e_1,e_2)$}
+          \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
+          \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
             % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
-            \State Delete $e_2$ from $\mathcal{G}'$ and update cost of $e_1$ with update rule $f(\cost_{e_1},\cost_{e_2})$ def. in Tab. 1 
+            \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
             % \Statex \hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent} update priority of $e_1$
@@
         % \State
-        \If{({\color{red}\textbf{$\cost \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
+        \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
           % \State Flag $e_{uv}$ as MustNotLink
@@
       \State
-      \Return $\Pi$, $\mathcal{G}'$
+      \Return $\Pi$
       % \State
@@
 
-\subsection{Generalized agglomerative clustering framework} \label{sec:algorithm}
+\subsection{Generalized Algorithm for Signed Graphs Agglomerative Clustering} \label{sec:algorithm}
 
-We now present our main contribution: a generalized framework for agglomerative graph clustering that can describe in a simple form several graph partitioning algorithms previously introduced in the literature and highlights the existence of new ones.
+We now present our main contribution: a Generalized Algorithm for Signed Graphs Agglomerative Clustering (\algname) that can describe in a simple form several graph partitioning algorithms previously introduced in the literature and highlights the existence of new ones.
 
@@
 This variant (Algorithm \ref{main_alg} with \texttt{addCannotLink=True}) stops when all the remaining clusters have been previously constrained.
-
 % The algorithm that we will present in the next section iteratively performs a sequence of so-called \emph{edge contractions} on the original graph $\mathcal{G}(V,E,w^+, w^-)$.
-
 % The graph clustering algorithm we will present in Sec.
@@
 
-\paragraph{Edge contraction and update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.
+\paragraph{Update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.
 % given by the linkage criterion defined in Sec.
 \ref{sec:notation} and
-An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph.
-Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that $\tilde{V} \subseteq V$ and each node $u\in \tilde{V}$ represents the cluster $S_u \in \Pi$, edges in $\tilde{E}$ represent adjacency-relationships between clusters and the signed edge weights are given by inter-cluster interactions, i.e.
+An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph (Fig.
+\ref{fig:edge_contraction_and_contr_graph}).
+Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that $\tilde{V} \subseteq V$ and each node $u\in \tilde{V}$ represents the cluster $S_u \in \Pi$, edges in $\tilde{E}$ represent adjacency-relationships between clusters and the signed edge weights $\tilde{\cost}$ are given by inter-cluster interactions, i.e.
 $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$.
-For the linkage criteria tested in this work, when clusters $S_u,S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$.
-Thus, we can easily express them in terms of a simple \emph{update rule} $f$.
-For instance, in the case of the single-linkage criterion defined in Eq.
-\ref{eq:max_linkage}, we can use the following simple max-update-rule to recompute the interaction between $S_u \cup S_v$ and one of its neighbors $S_t$:
+For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$.
+Thus, we can easily recompute these interactions by using a simple \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$.
+As an example, given the single-linkage criterion defined in Eq.
+\ref{eq:max_linkage}, the interaction between $S_u \cup S_v$ and one of its neighbors $S_t$ is simply given by:
 \begin{equation}
@@
 \end{equation}
-
-\UPDATE{Every time a pair of clusters is merged, the contracted graph is updated by performing an edge contraction and merging the associated nodes.
+All the update rules tested in this article are listed in Table \ref{tab:linkage-criteria}.
+% \UPDATE{Every time a pair of clusters is merged, the contracted graph is updated by performing an edge contraction and merging the associated nodes.
 The only interactions that then need to be updated are those between nodes that after the edge contraction happen to be connected by double edges (see Fig.
@@
 This update can be easily achieved by using an \emph{update rule} depending only on the weights of the double edges.
-\TODO{such a mess...} ...without the need of running a loop over the edges of the original graph.
-\UPDATE{In this way we do not need to recompute the interaction by using the linkage criterion over all the edges of the original graph, that would be computationally expensive.}
+% \TODO{such a mess...} ...without the need of running a loop over the edges of the original graph.
+% \UPDATE{In this way we do not need to recompute the interaction by using the linkage criterion over all the edges of the original graph, that would be computationally expensive.}
 
-\paragraph{The algorithm} The proposed Algorithm \ref{main_alg} proceeds as follows.
-Given an initial clustering $\Pi$ where each node of the original graph $\mathcal{G}$ represents its own cluster  \TODO{repetition}, the algorithm starts by initializing a contracted graph $\mathcal{G}'$ (see Definition \ref{def:contr_graph}) that will represent the clustering $\Pi$ at each iteration of the agglomeration.
-The algorithm then sorts all edges $e\in E$ by their absolute weight $|W(e)|$ in descending order in a priority queue, so that the most attractive and the most repulsive edges are processed first.
-It iteratively pops one edge $e_{uv}$ from priority queue and, depending on the value of the priority $\tilde{w}$ associated with $e_{uv}$, does the following: if the edge is attractive and $\tilde{w}>0$, then merge the connected nodes and perform an edge contraction of $e_{uv}$ in $\mathcal{G}'$ (see Sec.
-\ref{sec:notation} and Fig.
-\ref{fig:edge_contraction_and_contr_graph}), provided that $e_{uv}$ was not previously flagged as a cannot-link constraint; for every new pair of double edges in $\mathcal{G}'$ update \UPDATE{their priorities} according to one of the update rules listed in Table \ref{tab:linkage-criteria} and update their cannot-link relationships (see example in Fig.
-\ref{fig:algorithm_with_without_CLC}b from step 3 to 4).
-If, on the other hand, the edge $e_{uv}$ is repulsive and $\tilde{w}\leq 0$, then flag it as a cannot-link constraint if and only if the algorithm input-option \texttt{addCannotLink} is true and mutual exclusion relationships should be enforced.
-In the Supplementary material we provide a more detailed description of the algorithm (Sec.
-\ref{sec:detailed_algorithm}) and we also comment on its computational complexity (Sec.
-\ref{sec:complexity}).
+\paragraph{The edge contraction algorithm} The proposed generalized Algorithm \ref{main_alg} then proceeds as follows, similarly to the one proposed in \cite{levinkov2017comparative}.
+It starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first.
+It then iteratively pops one edge $e_{uv}$ from PQ and, depending on the priority $\tilde{\cost}$, does the following: in case of attractive interaction $\tilde{\cost}>0$, provided that $e_{uv}$ was not flagged as a cannot-link constraint, then merge the connected clusters, perform an edge contraction of $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and update the priorities of new double edges as explained in Fig.
+\ref{fig:edge_contraction_and_contr_graph}.
+% For every new pair of double edges in $\tilde{\mathcal{G}}_\Pi$, update their priorities according to one of the update rules listed in Table \ref{tab:linkage-criteria} together with their cannot-link relationships.
+If, on the other hand, the interaction is repulsive ($\tilde{\cost}\leq 0$) and the option \texttt{addCannotLink} of Alg.
+\ref{main_alg} is \texttt{True}, then the edge $e_{uv}$ is flagged as cannot-link constraint.
+In the Supplementary material we provide a more detailed description of the algorithm and we also comment on its computational complexity (Sec. \ref{sec:complexity}).
 
- In the special case of a graph with only positive edge interactions, i.e. $w_e^-=0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
- the algorithm performs a standard agglomerative hierarchical clustering by returning only one single cluster (see Fig.
-\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}) and a hierarchy of clusters defined by the order in which the clusters were merged.
  %\TODO{use def of merging process of contracted graph to define merging tree?}.
@@
             \midrule\midrule
-            Sum: & \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \tilde{w}_1+\tilde{w}_2$} & \thead{Sum Linkage\\Hierarchical Aggl.\\Clustering} & \thead{Greedy Additive \\ Edge Contraction \\\cite{levinkov2017comparative}} & \thead{Greedy \\Fixation \\\cite{levinkov2017comparative}} \\ \midrule
+            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} & \thead{Sum Linkage\\Hierarchical Aggl.\\Clustering} & \thead{Greedy Additive \\ Edge Contraction \\\cite{levinkov2017comparative}} & \thead{Greedy \\Fixation \\\cite{levinkov2017comparative}} \\ \midrule
 
@@
             $
-            f(\tilde{w}_1,\tilde{w}_2) = \begin{cases} 
-            \tilde{w}_1 & \text{if}\,\, |\tilde{w}_1|>|\tilde{w}_2|\\
-            \tilde{w}_2 & \text{otherwise}
+            f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
+            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
+            \tilde{\cost}_2 & \text{otherwise}
              \end{cases} 
@@
                & \thead{Single Linkage\\Hierarchical Aggl.\\Clustering \cite{lance1967general}} & \thead{Mutex \\Watershed \\\cite{wolf2018mutex}} & \thead{Mutex \\Watershed \\\cite{wolf2018mutex}} \\ \midrule
-            \makecell[r]{Mean:} & \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \mathrm{weightAvg}\{ \tilde{w}_1, \tilde{w}_2 \} $}                                 & \thead{ Average Linkage\\ Hierarchical Clust.
+            \makecell[r]{Mean:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                                 & \thead{ Average Linkage\\ Hierarchical Clust.
 \\(UPGMA) \cite{lance1967general}} & \thead{Average Linkage\\Signed Aggl.
@@
 
-            Max: & \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \max \{ \tilde{w}_1, \tilde{w}_2 \}  $}                                 & \thead{Single Linkage\\Hierarchical Aggl.\\Clustering \cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl.
+            Max: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Single Linkage\\Hierarchical Aggl.\\Clustering \cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl.
 Clust.
@@
 
-            Min:& \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \min \{ \tilde{w}_1, \tilde{w}_2 \}  $}                                 & \thead{Complete Linkage\\ Hierarchical Aggl.\\Clustering \cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl.
+            Min:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Complete Linkage\\ Hierarchical Aggl.\\Clustering \cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl.
 Clust.
@@
     \end{subtable} 
-    \caption{The table lists all the algorithms that can be seen as special cases of the Generic Agglomerative Clustering \ref{main_alg} given a specific update rule $f(e_1,e_2)$ and a type of graph...}
+    \caption{The table lists the update rules $f$ tested in this article.
+Depending on the type of graph (signed or unsigned) and the use of cannot-link constraints, existing and new algorithms are obtained.}
     \label{tab:linkage-criteria}
@@
 
-\subsection{Update rules and associated algorithms}
+\subsection{Different update rules: new and existing algorithms} \label{sec:alg_update_rules}
 \begin{itemize}
@@
 \item In Table \ref{tab:linkage-criteria} we collected the update rules that we tested and compared in this article. Later we will mention more of them that were proposed in the literature.
+
+\item In the special case of a graph with only positive edge interactions, i.e. $w_e^-=0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
+ the algorithm performs a standard agglomerative hierarchical clustering by returning only one single cluster (see Fig.
+\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}) and a hierarchy of clusters defined by the order in which the clusters were merged.
+
 \item In the special case of unsigned graphs (Table \ref{tab:linkage-criteria} column 1), the UGAC algorithm becomes simply a version of hierarchical clustering with different linkage criteria depending on the chosen update rule.
@@
 \cite{funke2018large} on the other hand accumulate statistics for each \UPDATE{boundary between clusters} by keeping a discrete histograms of the edge weights and then computes quantiles from it.
+
 \end{itemize}
+\TODO{More details on efficient implementations in appendix?}
 

### 2019-04-26 chapters/5_experiments_noise.tex
Update figures
Update algorithm description

@@
 
-\subsection{Testing the robustness of the algorithms}
+\subsection{Different update rules and robustness to noise}
  In this section we will quantitatively test the robustness of UGACA by adding noise to the edge weights of the graph and see how different choices of update rules compare.
@@
 The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones).
-Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries \TODO{Add colorbar?
-Adapt to noise defs}}
+    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
+    \TODO{Add colorbar? Adapt to noise defs}}
     \label{fig:noisy_affs}

### 2019-04-27 chapters/3_algorithm.tex
Polish presentation of different update rules

@@
 \ref{sec:notation}, then we introduce the generalized algorithm in Sec.
-\ref{sec:algorithm} and finally we show \UPDATE{how it represents a generalized version of several existing and new graph clustering algorithms (Sec.
+\ref{sec:algorithm} and finally we show \UPDATE{how it can be seen as a generalization of existing and new graph clustering algorithms (Sec.
 \ref{sec:alg_update_rules}).}
@@
 
-The proposed generalized clustering uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merging pairs of adjacent clusters.
+The proposed algorithm uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merging pairs of adjacent clusters.
 Intuitively, the algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
@@
 \ref{sec:notation} and
-An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph (Fig.
-\ref{fig:edge_contraction_and_contr_graph}).
-Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that $\tilde{V} \subseteq V$ and each node $u\in \tilde{V}$ represents the cluster $S_u \in \Pi$, edges in $\tilde{E}$ represent adjacency-relationships between clusters and the signed edge weights $\tilde{\cost}$ are given by inter-cluster interactions, i.e.
-$\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$.
+An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph.
+Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that $\tilde{V} \subseteq V$ and each node $u\in \tilde{V}$ represents the cluster $S_u \in \Pi$.
+Edges in $\tilde{E}$ represent adjacency-relationships between clusters and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$.
 For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$.
@@
 
-\paragraph{The edge contraction algorithm} The proposed generalized Algorithm \ref{main_alg} then proceeds as follows, similarly to the one proposed in \cite{levinkov2017comparative}.
+\paragraph{The proposed edge contraction algorithm} The proposed generalized Algorithm \ref{main_alg} then proceeds as follows, similarly to the one proposed in \cite{levinkov2017comparative}.
 It starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first.
@@
 \subsection{Different update rules: new and existing algorithms} \label{sec:alg_update_rules}
-\begin{itemize}
-\item In this section we will list some of the algorithms that can be described using the generalized Algorithm \ref{main_alg} presented above \UPDATE{and we will introduce some new ones}.
-\item In Table \ref{tab:linkage-criteria} we collected the update rules that we tested and compared in this article. Later we will mention more of them that were proposed in the literature.
+%In this section, we show how the choice of different update rules for the presented generalized algorithm \algname{} leads to existing and new algorithms (see Table \ref{tab:linkage-criteria}).
 
-\item In the special case of a graph with only positive edge interactions, i.e. $w_e^-=0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
- the algorithm performs a standard agglomerative hierarchical clustering by returning only one single cluster (see Fig.
-\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}) and a hierarchy of clusters defined by the order in which the clusters were merged.
+In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
+ the algorithm performs a standard agglomerative HC by returning only one single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see Fig.
+\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}).
+The choice of update rule determines the type of linkage (Table \ref{tab:linkage-criteria}, column 2, unsigned graphs).
 
-\item In the special case of unsigned graphs (Table \ref{tab:linkage-criteria} column 1), the UGAC algorithm becomes simply a version of hierarchical clustering with different linkage criteria depending on the chosen update rule.
-It outputs one single cluster and it also defines a hierarchy of clusters during the merging process that can be associated to \UPDATE{a merging tree/  the hierarchical clustering dendrogram}...
-\TODO{Problem: sum does not trivially define an ultra-metric-distance...}
-\item In the literature there have been already several methods using cannot-link constraints for agglomerative clustering algorithms \TODO{repetition from related work}: for example, \cite{malmberg2011generalized} used initially fixed mutual exclusion relationships, whereas \cite{levinkov2017comparative} introduced them dynamically in an edge contraction algorithm for signed graphs, named Greedy Fixation (Table \ref{tab:linkage-criteria} row 1, \emph{sum}).
-At the same time, they also proposed a version of it without cannot link constraints (Greedy Additive Edge Contraction) and they compared both with other greedy and local-search algorithms for solving the multicut/correlation clustering problem.
-\item Dynamically introduced cannot-link constraints were also proposed by \cite{wolf2018mutex}, that...
-\TODO{brief MWS description as efficient implementation of this update rule}.
-In the Supplementary material we show that the algorithm they present can be seen as a special case of UGACA with absolute maximum update rule (Table \ref{tab:linkage-criteria} row 2 - \emph{absolute maximum}) and that adding or not cannot-link constraints does not change the final clustering.
-\item On the other hand, the signed graph versions of UGACA with update rules \emph{arithmetic mean}, \emph{max} and \emph{min} (rows 3 to 5 in Table \ref{tab:linkage-criteria}) are new algorithms that were never mentioned in the literature, \UPDATE{especially those with cannot-link constraints}.
-\item In this article, we test and run a comparison of the five types of update rule listed in Table \ref{tab:linkage-criteria} (i.e.
-\emph{sum}, \emph{absolute max}, \emph{arithmetic mean}, \emph{max} and \emph{min}), since \UPDATE{they they are the most commonly used and the cheapest to compute}.
-Nevertheless, UGACA can be easily generalized to include even more complex rules.
-For instance, \cite{nunez2013machine} proposes a learned version of update rule where a neural network updates the edge weights depending on edge and node features; another really common choice is to introduce a weight regularization depending on the size of the linked nodes (\cite{felzenszwalb2004efficient} and \cite{kardoostsolving} (unpublished...??), Thorsten..);
-\cite{funke2018large} on the other hand accumulate statistics for each \UPDATE{boundary between clusters} by keeping a discrete histograms of the edge weights and then computes quantiles from it.
+On the other hand, in the case of graphs with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was already proposed in \cite{levinkov2017comparative} (Table \ref{tab:linkage-criteria}, sum update rule, row 1).
+They present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms solving the multicut optimization problem.
 
-\end{itemize}
-\TODO{More details on efficient implementations in appendix?}
+A clustering algorithm for signed graphs dynamically introducing cannot-link constraints was also proposed in \cite{wolf2018mutex}.
+In the supplementary material (Sec.
+\ref{sec:equivalence_MWS}) we show how this algorithm, named Mutex Watershed, can be seen as an efficient implementation of \algname{} with the \emph{absolute-maximum} update rule defined in Table \ref{tab:linkage-criteria}, row 2.
+Then, we also observe that, for this choice of update rule, \algname{} returns the same clustering with or without cannot-link constraints.
 
-% \begin{table*}[t]
-%     \centering
-%     \begin{subtable}[t!]{0.98\textwidth}\centering
-%         \begin{tabular}{c | c }
-%             \toprule\toprule
-%             \makecell{Algorithm name} & \makecell{Algorithm description and \\linkage criteria}    \\
-%             \midrule\midrule
+New variations of agglomerative clustering on signed graphs that, to our knowledge, were never mentioned in the literature are given by \algname{} with update rules \emph{mean}, \emph{max} and \emph{min} (rows 3 to 5 in Table \ref{tab:linkage-criteria}).
 
-%             Weighted Arithmetic Mean (WPGMA) & \thead{Assign a weighting $\alpha_e \in \mathbb{R}^+$, $\forall e \in E$ \\ \\ Linkage criteria: $w_{\mathrm{new}} = \frac{\alpha_1 w_1 +\alpha_2 w_2}{\alpha_1 + \alpha_2} $}  \\ \midrule
-
-%             \makecell{Felzenszwalb Efficient \\Graph-based Image Segmentation \cite{felzenszwalb2004efficient}}  & \thead{Initially all edges have positive weights }  \\ \midrule
-
-%             \makecell{Quantile Agglomeration Clustering (...?)}  & \thead{...}  \\ \midrule
-
-%             \makecell{Graph-based active learning \\of agglomeration (GALA) \cite{nunez2013machine}}  & \thead{Assign set of edge features $\phi^{\mathrm{I}}_e$ and \\node features $\phi^{\mathrm{II}}_u$, $\forall u \in V$, $\forall e \in E$.
-\\ \\ A classifier $f$ with parameters $\theta$ predicts and updates\\ the cost of an edge: $w_e = f(\phi^{\mathrm{I}}_e, \phi^{\mathrm{II}}_u, \phi^{\mathrm{II}}_v; \theta)$, $\forall e_{uv} \in E$} \\ \midrule
-
-%             % \makecell{$w_{\mathrm{new}}=w_{\tilde{e}}$,$\,
-%             % \,$ where $\tilde{e}=\mathrm{arg}\max_{e\in \{e_{1},e_{2}\}} \left|w_e\right|$  }  & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Mutex Watershed \cite{wolf2018mutex}} \\ \midrule
-
-%             % Arithmetic mean: $w_{\mathrm{new}} = (w_1+w_2) / 2 $                                 & \thead{Hierarchical Clustering \\ with Average Linkage (UPGMA)} & \thead{\textbf{NEW}}\\ \midrule
-
-%             % Maximum: $w_{\mathrm{new}} = \max \{ w_1, w_2 \}  $                                 & \thead{Hierarchical Clustering \\ with Single Linkage} & \thead{\textbf{NEW}}\\ \midrule
-
-%             % Minimum: $w_{\mathrm{new}} = \min \{ w_1, w_2 \}  $                                 & \thead{Hierarchical Clustering \\ with Complete Linkage} & \thead{\textbf{NEW}}
-
-%         \end{tabular}
-%         % \caption{Linkage criteria}
-%         \label{tab:linkage-criteria}
-%     \end{subtable} 
-%     \caption{Linkage criteria 2}
-% \end{table*}
+In this work we test and compare the five update rules listed in Table \ref{tab:linkage-criteria} that represents the most used ones. 
+Apart from these, for instance, \cite{nunez2013machine} proposes a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features.
+Other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}), whereas
+\cite{funke2018large} uses a \emph{quantile} update rule by populating a histogram for each inter-cluster interaction.

### 2019-04-27 chapters/3_algorithm.tex
Add descr. of experimental setup

@@
 \ref{sec:notation}, then we introduce the generalized algorithm in Sec.
-\ref{sec:algorithm} and finally we show \UPDATE{how it can be seen as a generalization of existing and new graph clustering algorithms (Sec.
-\ref{sec:alg_update_rules}).}
+\ref{sec:algorithm} and finally we show \UPDATE{how it can be seen as a generalization of existing and new graph clustering algorithms in Sec.
+\ref{sec:alg_update_rules}.}
 
@@
 The instance of the NP-hard \emph{weighted correlation clustering} or \emph{minimum cost multicut problem} w.r.t.
-$\mathcal{G}(V,E,w^+, w^-)$ \cite{kappes2011globally,chopra1991multiway,andres2015lifting} is the task of finding a clustering that optimally balance the attraction and repulsion in the graph and is given by the following optimization problem/binary integer program:
+$\mathcal{G}(V,E,w^+, w^-)$ \cite{kappes2011globally,chopra1991multiway,andres2015lifting} is the task of finding the clustering that optimally balance the attraction and repulsion in the graph and is given by the following optimization problem/binary integer program:
 \begin{equation}
@@
 % \UPDATE{In this way we do not need to recompute the interaction by using the linkage criterion over all the edges of the original graph, that would be computationally expensive.}
-
 \paragraph{The proposed edge contraction algorithm} The proposed generalized Algorithm \ref{main_alg} then proceeds as follows, similarly to the one proposed in \cite{levinkov2017comparative}.
@@
     \end{subtable} 
-    \caption{The table lists the update rules $f$ tested in this article.
-Depending on the type of graph (signed or unsigned) and the use of cannot-link constraints, existing and new algorithms are obtained.}
+    \caption{The table lists the tested update rules $f$.
+Existing and new algorithms are given by a specific choice of update rule, type of graph (signed or unsigned) and optional use of cannot-link constraints.}
     \label{tab:linkage-criteria}
@@
 
-In this work we test and compare the five update rules listed in Table \ref{tab:linkage-criteria} that represents the most used ones. 
-Apart from these, for instance, \cite{nunez2013machine} proposes a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features.
+In this work we test and compare the five update rules listed in Table \ref{tab:linkage-criteria} that represents the most common options. 
+Apart from these, \cite{nunez2013machine} proposes a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features.
 Other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}), whereas

### 2019-04-27 chapters/5_experiments_intro.tex
Polish presentation of different update rules
Add descr. of experimental setup

@@
 
-\subsection{Experimental setup and pixel grid-graph} \label{sec:grid_graph}
-\begin{itemize}
-\item Define predictions of the classifier (pseudo probabilities) for edge weights
-\item Define possible mappings to signed costs
-\item Make comment about which version defines nested segmentations and which does not give hirarchical solutions
+\subsection{Experimental setup: pixel grid-graph with long-range connections} \label{sec:grid_graph}
+EM segmentation is commonly performed by first predicting which pixels belong to a cell membrane using a CNN.
+As described in Sec.
+\ref{sec:related_work}, different postprocessing methods are then used to obtain a segmentation.
+The CNN can either be trained to predict boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pixel and one of its neighbors to belong to the same neuron segment.
+The affinities do not have to be limited to direct neighboring pixels, in fact, \cite{lee2017superhuman} have shown that using long-range affinities is beneficial for the training of the CNN.
+Similarly to \cite{wolf2018mutex}, we then train a CNN to predict short- and long-range affinities and use them as input weights for \algname{}.
+The output layer of the CNN will then have $m_{\mathrm{direct}}+m_{\mathrm{long}}$ channels, where $m_{\mathrm{direct}}=6$ represents the direct neighbors in 3D and $m_{\mathrm{long}}$ is the number of long-range ones.
+In the Supplementary material (Sec.
+\ref{sec:training_details}) we provide more details on the chosen neighborhood structure, data augmentation and the training with L1 loss of the used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d}.
 
-\end{itemize}
+The output of the CNN can be represented as a \emph{weighted 3D grid graph}, such that each node represents a pixel/voxel of the volume image.
+Each node is connected to its neighbors by $m_{\mathrm{direct}}$ edges ($E_{\mathrm{direct}}$) and $m_{\mathrm{long}}$ long-range ones ($E_{\mathrm{long}}$).
+In our experiments we evaluate how beneficial long-range connections are for the final segmentation and we add them to the graph with a given probability $p_{\mathrm{long}}$ (if $p_{\mathrm{long}}=0$, then $E_{\mathrm{long}}=\emptyset$).
+The post-processing presented in \cite{lee2017superhuman} did not use any predicted long-range connection, whereas \cite{wolf2018mutex} introduced them with strides of 2 in the XY-plane.
 
-\begin{itemize}
-    \item Define long-range grid graph. (Mention the fact of enforcing local merge)
-\item Introduce "Poisson" random graph with a given probability of long-range connections
-\item Comment about the short- and long-range distinction in the MWS paper? It does not work that well in practice (applying post-processing to remove small segments is easier and better solution).
-\item Ad of course we can think about a classifier that separately predict attraction and repulsion
-\item Define offset patterns (link to supplementary material), trained networks (loss, etc...) and setups on cremi and cityscapes 
-\item Mention postprocessing step: get rid of tiny segments; on CREMI we use watershed to fill the deleted parts 
-\end{itemize}
+The trained CNN outputs pseudo-probabilities $p:E \rightarrow [0,1]$ that have to be mapped to positive and negative edge weights\footnote{Note that in general attractive and repulsive interactions $w^+$ and $w^-$ can be independently estimated with different classifiers.}.
+The most common approaches use \emph{additive} \cite{ailon2008aggregating} or \emph{logarithmic} \cite{finkel2008enforcing,andres2012globally} mappings:
+\begin{equation}
+\cost_{e,\mathrm{Add}} = p_e - \beta, \qquad \quad \cost_{e,\mathrm{Log}} = \log \left( \frac{p_e}{1-p_e} \right) + \log \left( \frac{\beta}{1-\beta} \right),
+\end{equation}
+where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation.
+We evaluated both of them empirically with each of the tested update rules and found that the additive mapping is the best option in all cases apart from the sum update rule.

### 2019-04-27 chapters/5_experiments_cityscapes.tex
Polish sec. about noise exps

@@
 % !TEX root = ../agglo_clust_review.tex
-\section{Experiments on Cityscapes}
+\section{Experiments on CityScapes}
 A successful proposal-free method was recently presented in \cite{liu2018affinity} and a setup equivalent to the one described in Sec.

### 2019-04-27 chapters/5_experiments_compare_rules.tex
Add descr. of experimental setup
Polish sec. about noise exps

@@
 
-\subsection{Comparison of update rules} \label{sec:exp_first_comparison}
+\subsection{Evaluating different update rules} \label{sec:exp_first_comparison}
 \begin{itemize}
@@
 \end{itemize}
+
+Among the update rules listed in Table \ref{tab:linkage-criteria}, in the next sections we will only focus on \emph{sum}, \emph{arithmetic mean} and \emph{absolute maximum}, since they performed best in these experiments.

### 2019-04-27 chapters/5_experiments_noise.tex
Add descr. of experimental setup
Polish sec. about noise exps

@@
 
-\caption{Plot illustrating Adapted RAND scores achieved by UGACA and different update rules when noise is added to the edge weights...
-Solid lines represent median values, whereas values between the 25th and the 75th percentile are shown in shade areas.
-\TODO{Label which uses only local-neighbors and which uses long-range connections}}\label{fig:noise_plots}
+\caption{Plot of the Rand-Scores achieved by the generalized algorithm and different update rules when noise is added to the edge weights.
+Solid lines represent median values, whereas values between the 25th and the 75th percentile are shown in shade areas.}\label{fig:noise_plots}
 \end{figure}
@@
 \subsection{Different update rules and robustness to noise}
- In this section we will quantitatively test the robustness of UGACA by adding noise to the edge weights of the graph and see how different choices of update rules compare.
- Among the update rules listed in Table \ref{tab:linkage-criteria}, we will only focus on \emph{sum}, \emph{arithmetic mean} and \emph{absolute maximum}, since they achieved the best scores in the results presented in Sec.
-\ref{sec:exp_first_comparison}.
-%Before to present the results shown in Fig.
-\ref{fig:noise_plots}, we will first introduce the type of noise that was added to the edge weights.
+ In this section we evaluate the robustness of \algname{} with different update rules by adding noise to the edge weights.
+  %Before to present the results shown in Fig. \ref{fig:noise_plots}, we will first introduce the type of noise that was added to the edge weights.
+% In the set of experiments presented in this article, edge weights are estimated \UPDATE{by using a CNN that predicts how likely two neighboring pixels are to be part of the same cluster}. 
+Fig.
+\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}a} shows an example of uncertain CNN predictions on a slice of the neuron segmentation dataset.
+We now present a way of modifying the CNN output to introduce additional artifacts like a missing or false boundary evidence.
 
- In the set of experiments presented in this article, edge weights are estimated \UPDATE{by using a CNN that predicts how likely two neighboring pixels are to be part of the same cluster}.
-Fig.
-\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}a} illustrates the predictions of the CNN on the CREMI dataset for neuron segmentation.
-We would now like to make these predictions worse by introducing  artifacts, \UPDATE{e.g.
-partially deleted or added boundaries between neurons in the image}.
 In the field of image processing there are several ways of adding noise to an image, among which the most common are Gaussian noise or Poisson shot noise. 
-By using these methods, the noise value of each pixel is independent of noise values of neighboring pixels, thus they are not a good choice for our application since the pixelwise predictions of a CNN are usually spatially correlated.
-
- We then decided to use Perlin noise\footnote{In our experiments, we used opensimplex noise, that is a more recent open-source version of Perlin noise (\UPDATE{REF or link?})}, one of the most common gradient noises used in procedural pattern generation.
-This type of noise generates spatial random patterns that are locally smooth but have large and diverse variations on bigger scales.
-It generates values $n(x)\in[0,1]$ that were mapped to $[-\infty, \infty]$ with the Logit function, $N(x)=\mathrm{Logit}(n(x))$, and then combined with the original CNN predictions $F(x)=\mathrm{Logit}(p(x))$ in the two different following ways:
-\begin{equation}
+In these cases, the noise of one pixel does not correlate with its neighboring noise values. On the other hand, predictions of a CNN are known to be spatially correlated. 
+Thus, we used Perlin noise\footnote{In our experiments, we used an open-source version of simplex noise \cite{perlin2001noise}, which is an improved open-source version of Perlin noise \cite{perlin1985image}}, one of the most common gradient noises used in procedural pattern generation.
+This type of noise $n(x)\in[0,1]$ generates spatial random patterns that are locally smooth but have large and diverse variations on bigger scales.
+We then combined it with the CNN predictions $p(x)$ in the two following ways:
+\begin{equation}\label{eq:noise_biased_predictions}
 % \tilde{F}(x;\theta)=\begin{cases}
@@
 \end{equation}
-In this equation, $\mathcal{K}\in \mathbb{R}^+$ is a positive factor representing the amount of added noise; $\tilde{F}_{+}(x;\mathcal{K})$ represents a merge-biased modified version of the CNN predictions $F(x)$, such that the probability for two pixels to be in the same cluster is increased only if $N(x)>0$ (see Fig.
-\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b}); on the other hand, $\tilde{F}_{-}(x;\mathcal{K})$ represents a split-biased prediction with decreased probabilities only if $N(x)<0$ (Fig.
+where  $N(x)=\mathrm{Logit}[n(x)]$; $F(x)=\mathrm{Logit}[p(x)]$ and $\mathcal{K}\in \mathbb{R}^+$ is a positive factor representing the amount of added noise.
+$\tilde{F}_{+}(x;\mathcal{K})$ represents then a merge-biased prediction, such that the probability for two pixels to be in the same cluster is increased only if $N(x)>0$ (see Fig.
+\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b}), whereas $\tilde{F}_{-}(x;\mathcal{K})$ is a split-biased prediction with decreased probabilities when $N(x)<0$ (Fig.
 \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}).
-In the Supplementary material we provide a detailed description of the parameters used for the noise generation.
+In the Supplementary material (Sec.
+\ref{sec:details_perlin}) we provide a more detailed description of the parameters used for the noise generation.
 
-With this strategy, we randomly perturbed the CNN predictions and the edge weights only in some parts of the image.
 The plots in Fig.
-\ref{fig:noise_plots} represent the scores achieved by UGACA with different update rules depending on the amount of noise $\mathcal{K}$ added to the edge weights.
-\begin{itemize}
-\item The experiments show that running UGACA on a grid graph with long-range connections always lead to better segmentations/clusterings \TODO{require def.
-of long range graph and long-range probability}
-\item The most robust version of update rule proved to be the arithmetic mean, that achieves similar scores even with significantly noisy edge weights.
-\item The \emph{absolute maximum} update rule proposed by \cite{wolf2018mutex} provides an efficient and fast option, but it completely fails when too much noise is added.
-\item The \emph{sum} update rule version was the slowest option tested, but it was not as robust as the \emph{mean} version, probably due to its tendency to grow one cluster at the time (see Sec.
+\ref{fig:noise_plots} represent the scores achieved by \algname{} with different update rules depending on the amount of noise $\mathcal{K}$ added to the edge weights and the probability $p_{\mathrm{long}}$ of long-range connections in the graph.
+Results clearly show that adding long-range edges is always beneficial for final segmentation.
+\TODO{What about time?} The most robust version of update rule proved to be the \emph{mean}, that achieves similar scores even with significantly noisy edge weights.
+The \emph{absolute maximum} update rule proposed by \cite{wolf2018mutex} provides an efficient and fast option, but completely fails when too much noise is added.
+The \emph{sum} update rule version was the slowest option tested, but it was not as robust as the \emph{mean} version, probably due to its tendency to grow one cluster at the time (see Sec.
 \ref{sec:exp_first_comparison}).
-Comment about MC energy (plots in Suppl.
-Material?)
-\item On the other hand, UGACA with mean update rule and cannot-link constraints never achieves good overall scores, as we have already shown in Sec.
-\ref{sec:exp_first_comparison} and \UPDATE{Figure...?}, because \UPDATE{it tends to introduce too many false splits}.
+\TODO{Comment about MC energy}
+On the other hand, \algname{} with \emph{mean} update rule and cannot-link constraints did not achieve high scores because of the strong over-segmentation error.
 %Nevertheless, these additional experiments show that it provides an \UPDATE{almost true over-segmentation of the ground truth segmentation even with strongly merge-biased predictions}.
-\end{itemize}
 
@@
 
-    \captionof{figure}{The two figures represent the predictions of the CNN on the CREMI dataset (\UPDATE{REF}) a) without added noise, b) with the addition of the merge-biased noise defined in Eq.
-\ref{eq:opensimplex_noise_def} and c) with split-biased noise.
-The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones).
+    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge}.
+(a) shows the original predictions $F(x)$, (b) the merge-biased version $\tilde{F}_{+}(x;\mathcal{K})$ defined in Eq.
+\ref{eq:noise_biased_predictions} and c) the split-biased version $\tilde{F}_{-}(x;\mathcal{K})$.
+Blue pixels represent boundary evidence.
+    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
     %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
-    \TODO{Add colorbar? Adapt to noise defs}}
+    }
     \label{fig:noisy_affs}
@@
     % \end{subtable} 
-    \captionof{table}{AP scores on the cityscapes validation set for UGACA and different types of update rules. \TODO{PROBLEM: all apart from GMIS uses finetuned affinities} }
+    \captionof{table}{AP scores on the cityscapes validation set for the generalized algorithm and different types of update rules.  }
     \label{tab:results_cityscapes}

### 2019-04-28 chapters/1_intro.tex
Update algorithm description
Start rewriting related work

@@
 There are two main types of successful deep learning approaches to IS: proposal-based and proposal-free methods.
-Proposal-based methods consist of two steps: object detection, for example by finding bounding boxes, and assigning pixels to the detected objects \cite{he2017mask,dai2016instance,li2017fully}.
+Proposal-based methods consist of two steps: detecting objects, for example by finding bounding boxes, and assigning pixels to the detected instances \cite{he2017mask,dai2016instance,li2017fully}.
 Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example electron microscopy image volumes of neurons \cite{arganda2015crowdsourcing}, where objects are not approximated well by bounding boxes.
 % More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)
-Proposal-free methods perform IS by directly predicting pixel features and then using a clustering algorithm for grouping pixels into object instances \TODO{REFS}.
+Thus, there is a growing interest for more efficient proposal-free methods that perform IS by directly predicting pixel features and then grouping pixels into object instances \TODO{REFS}.
 In this work, we focus on a proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance.
-Recently, \cite{liu2018affinity} used this approach and achieved performances comparable to proposal-based methods on the Cityscapes dataset; \UPDATE{similarly, the method was used in \cite{wolf2018mutex} to achieve state-of-the-art results in a neuron segmentation challenge.}
+Recently, \cite{liu2018affinity} used this approach and achieved performances comparable to proposal-based methods on the Cityscapes dataset; \UPDATE{similarly, the method was used in \cite{wolf2018mutex} to achieve state-of-the-art results in a neuron segmentation challenge.} \TODO{Rewrite}
 
@@
 
-A popular method for graph clustering is hierarchical clustering (HC) which creates an hierarchy of clusters.
+Another popular method for graph clustering is hierarchical clustering (HC) which creates an hierarchy of clusters.
 Agglomerative HC is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}.
@@
 Finally, \UPDATE{we test these different agglomerative clustering algorithms} on the task of instance segmentation both on the CREMI neuron segmentation challenge and the Cityscapes dataset, by comparing achieved scores, efficiency and robustness to noisy edge weights.
-
 \TODO{Add chapters description}

### 2019-04-28 chapters/2_rel_work.tex
Update algorithm description
Add descr. of experimental setup
Start rewriting related work

--- 2019-04-24 chapters/2_rel_work.tex
@@
 
-\section{Related work}
-\begin{itemize}
-\item \textbf{Proposal based methods} 
-\begin{itemize}
-\item Generate region proposals or bounding boxes and classify the objects in the bounding box \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}; fully convolutional  box proposals \cite{li2017fully}.
-\item \emph{More references:} or generate generic proposal segments and then label each one with a semantic detector \cite{hariharan2014simultaneous,chen2015multi,hariharan2015hypercolumns,dai2015convolutional,uhrig2016pixel,he2017mask}.
-\item these somehow still uses some kind of object detector (at least to find the number of objects), but they do not necessary analyse one proposal at the time: use an object detector to enumerate candidate instances and then perform pixel-level segmentation of each instance \cite{liang2018proposal,dai2016instance,li2017fully,liang2016reversible,arnab2017pixelwise} \TODO{check \cite{dai2016instance}}
-% \SOURCE{\cite{kong2018recurrent}
-\end{itemize}
+\section{Related work} \label{sec:related_work}
 
-\item \textbf{Proposal-free methods:} 
-\begin{itemize}
-\item box-free \cite{pinheiro2015learning,pinheiro2016learning,hu2017fastmask}; joint segmentation and instance labeling in a combinatorial framework \cite{kirillov2017instancecut}; recurrent models \cite{romera2016recurrent,ren2017end}; encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; sequential framework to gradually group from points to lines and then instances \cite{liu2017sgn}
-% \item From end-to-end recurrent attention: \textit{Other approaches us- ing FCNs are proposal-free, but rely on a \textbf{bottom-up merging process}\textbf{}.
-Liang et al.
-[26] predict dense pixel prediction of ob- ject location and size, using clustering as a post-processing step.
-Uhrig et al.
-[41] present another approach based on FCNs, which is trained to produces a semantic segmen- tation as well as an instance-aware angle map, encoding the instance centroids.
-Post-processing based on template matching and instance fusion produces the instance identi- ties.
-Importantly, they also used ground-truth depth labels in training.
-Concurrent work [2, 19, 22] also explores a similar idea of using FCNs to output instance-sensitive embeddings.}
-\item \textbf{Pixel embedding vectors}: 
-\begin{itemize}
-\item supervised vectors \cite{bai2017deep}, unsupervised vectors  \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic} of which \cite{kong2018recurrent} is trained end-to-end;  using scene depth information \cite{uhrig2016pixel}, \TODO{check \cite{sironi2014multiscale}}
-%    \TODO{more on pose estimation, vector distance transform, deep coloring?, ECCV semi-convolutions}
+% \begin{itemize}
+% \item Motivation 2:
+% \begin{itemize}
+% \item HC has been always really popular in computer vision: \emph{Instance segmentation} is a task of computer vision that involves the detection of all objects in an image by performing pixel-level segmentation of each instance.
+% \item Since conventional unsigned graph agglomerative clustering algorithms, such as the well-known linkage methods [1], usually are quite sensitive to noise and outliers [1] (As their affinities are directly computed using pairwise distances between samples), most methods were based on multi-step pipelines first predicting superpixels (to reduce noise).
+% \item These methods are still commonly used for specific instance segmentation applications: connectomics, build merge-tree 
+%  %https://arxiv.org/pdf/1208.5092.pdf
+% \item still commonly used for building merge-trees, give recent examples in connectomics (Sebastian Seung, etc...) % https://arxiv.org/abs/1608.04051
+% \item Graph clustering algorithms recently gained more and more popularity with the advent of deep-learning and its application to instance segmentation
+% \item Deep convolutional neural nets (CNNs) has been successfully applied to a wide range of tasks of computer vision and pixel-level image understanding, such as \UPDATE{boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, semantic segmentation \cite{long2015fully,chen2018deeplab,kong2018recurrent}, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet}, and pose estimation \cite{wei2016convolutional,cao2017realtime}.}
+% % \SOURCE{\cite{kong2018recurrent}}
 
-% different types of loss
-% \item For each pixel in the image, a CNN predicts an embedding vector, such that pixels in the same instance are represented by the same vector.
-(\textit{by training a model that labels pixels with unit-length vectors that live in some ﬁxed dimension embedding space} \SOURCE{Rec.
-embeddings} ).
-\textit{With instance embedding, each object is assigned a “color” in a n-dimensional space.
-The network processes the image and produces a dense output, same size as the input image.
-Each pixel in the output of the network is a point in the embedding space.
-Pixels that belong to the same object are close in the embedding space while pixels that belong to different objects are distant in the embedding space.
-Parsing the image embedding space involves some sort of clustering algorithm.} \SOURCE{online}
+% \item Currently there are two successful approaches used for proposal-free bottom-up instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likely it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}
 
-% \item Clustering methods: DBSCAN, more
+% \item Both approaches requires a final clustering algorithm to output the final instance segmentation
 
-\item \emph{Division by used clustering methods}: spectral clustering \cite{liang2018proposal}; mean-shift \cite{kong2018recurrent}; HDBSCAN \cite{}; seeds \cite{fathi2017semantic} \TODO{incomplete}
-\end{itemize}
+%  and we can define a grid graph, where each vertex represents a pixel, with short- and long-range edge connections
 
-% \item Nevertheless, in both approaches we can define a grid graph (each vertex representing a pixel) with signed weights and find the final instance segmentation by using a graph partitioning algorithm:
+%  and find the final instance segmentation by using a graph clustering algorithm.
+
+% \item GMIS achieved 
+% comparable results to methods based on object 
+% proposal like Mask-R-CNN on natural images 
+% (Cityscapes); MWS achieved SOA results on a 
+% biological images (ISBI)
+
+% \item Out contributions:
+
 % \begin{itemize}
-% \item In Method 1, the graph is complete and the edge weights represent similarities between pairs of pixel embedding vectors.
-In most proposed approaches, embedding vectors representing distinct instances should be "distant enough" in the embedding space (a minimum distance is usually used during the training of the CNN).
-Thus, this threshold distance can be used to define signed affinities, representing attraction or repulsion between pairs of pixels;
-% \item  In Method 2, the short- and long-range affinities predicted by the CNN are directly used as signed edge weights in the grid graph
+%  \item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and quality of the final clustering in terms of multicut energy) \textbf{Comparison paper}
+%  \item \textit{if we get good scores on CREMI dataset}: we show that also on neuro-data it is worth to skip the hand-crafted superpixel step and compute the final segmentation directly from the CNN affinities (MWS already showed it on the ISBI dataset): main selling point is again the almost-parameter free feature of the method
+% \end{itemize}
+% \end{itemize}
 % \end{itemize}
 
+% More details about instance segmentation (move to related work)
+% \begin{itemize}
+
+% \item 
+% \item Many recent successful methods for instance segmentation %, usually named \emph{proposal-based methods}, 
+%  use heuristic approaches that start from the classical computer vision task of \emph{object detection}, where the goal is to localize each objects using a bounding box, and then predict both a pixel-level mask of each instance and a semantic label (classify the objects in the bounding box).
+\TODO{Is it really general enough as a description...?} \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}
+% \item While effective, these approaches are \UPDATE{somewhat unsatisfying (copy/paste, change: present some faults)} because:
+% \begin{itemize}
+% \item they rely on the object detector and non-maximum suppression heuristics to count how many instances are present in the image, 
+% \item they tend to underperform in cluttered scenes, since instance assignment is often carried out independently for each detection; 
+% \item they are not usable for wiry or articulated objects (e.g. in the field of connectomics and neuron segmenation from electron microscopy images) 
+% \item their architecture do not usually prevent a pixel to be shared between multiple instances
+% \item they do not scale up well since each proposal has to be singularly processed by the CNN. 
+% % \item (difficult to train in an end-to-end manner: interface between instance segmentation and detection is non-differentiable)
+% % \item (architecture is complex and hard to tune and “debug”...?)
+% \end{itemize}
+
+% \item Currently there are two successful approaches used for proposal-free (make brief intro) instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likely it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}
+
+% \item Both approaches requires a final clustering algorithm to output the final instance segmentation
+
+%  and we can define a grid graph, where each vertex represents a pixel, with short- and long-range edge connections
+
+%  and find the final instance segmentation by using a graph clustering algorithm.
+
+% \item Recent work (\cite{wolf2018mutex}, more...) shows that it is better to use \textbf{repulsion and attraction} (directly predict it with the classifier, no need to define seeds or to fix a threshold given an hierarchy of clusters)
+% \item solving correlation clustering problem (multicut) is too expensive for this application (even using recently proposed heuristics)
+% \item our contributions:
+% \begin{itemize}
+% \item we propose a unified and simple formalization of Agglomerative Clustering and show how many of the recently proposed methods can be seen as special cases (focusing in particular on signed graphs) (\textbf{review and comparison paper})
+% \item new clustering algorithms on signed graphs
+
+% \end{itemize}
+% \item on other datasets (connectomics) many methods are based on multi-step pipelines first predicting superpixels
+
+% \end{itemize}
+
+% \item Motivation 1:
+
+% \begin{itemize}
+
+% \item all HC methods only talk about positive edge weights, but it is actually easy to generalize them for negative and attractive edges. 
+% \item The standard version of HC is good for building hierarchy but problem with hierarchical merge-trees is how to choose one single threshold.
+Choose one single fixed density level.
+Ideally we would like to be able to cut the tree at different places to select our clusters.
+% \item An important line of research is based on the observation that superior partitionings are obtained when the graph has both attractive and repulsive edges.
+Solutions that optimally balance attraction and repulsion do not require external stopping criteria such as predefined number of regions or seeds.
+This generalization leads to the NP-hard problem of correlation clustering or (synonymous) multicut (MC) partitioning.
+\emph{Alternative:} multicut / correlation clustering partitions vertices with both attractive and repulsive interactions encoded into the edges of a graph.
+Multicut has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region.
+Its great drawback is that its optimization is NP-hard.
+
+% \end{itemize}
+In recent years there has been considerable progress in pixel-level understanding tasks of computer vision, such as semantic segmentation \cite{long2015fully,kong2018recurrent,chen2018deeplab}, boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, %, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet},
+and pose estimation \cite{wei2016convolutional,cao2017realtime}.
+This progress was mostly associated with new key ideas and architectures of deep convolutional convolutional networks (CNNs), like dilated/``atrous'' convolutions \cite{yu2015multi,chen2018deeplab} or ``hourglass'' architectures with skip connections \cite{ronneberger2015u,paszke2016enet} increasing the receptive field of view of the model.
+
+\textbf{Proposal-based instance segmentation methods} decompose the segmentation task into two steps that consists in generating object proposals or bounding boxes and assigning to each object a class and a binary segmentation mask \cite{he2017mask,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}.
+% Here I could have more: \cite{pinheiro2015learning,pinheiro2016learning,hu2017fastmask} and probably something more in Deep coloring
+% \item \emph{More references:} or generate generic proposal segments and then label each one with a semantic detector \cite{hariharan2014simultaneous,chen2015multi,hariharan2015hypercolumns,dai2015convolutional,uhrig2016pixel,he2017mask}.
+They commonly rely on Faster RCNN \cite{ren2015faster} and can be trained end-to-end using non-maximum suppression.
+Other methods use instead recurrent models to sequentially generate instances one-by-one \cite{romera2016recurrent,ren2017end}.
+
+\textbf{Proposal-free methods} avoid the limitations of box proposals (e.g.
+for wiry objects) by directly grouping pixels into instances.
+For example, some approaches use a combinatorial framework for joint segmentation \cite{kirillov2017instancecut}, whereas others sequentially group pixels into lines and then instances \cite{liu2017sgn}.
+% encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; 
+A watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction and a template matching scheme using scene depth information is proposed in \cite{uhrig2016pixel}.
+Another line of research uses metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,novotny2018semi,kulikov2018instance}
+% \TODO{What about \cite{liang2018proposal} using spectral clustering?}. 
+A clustering algorithm, e.g. HDBSCAN, is then applied to retrieve instances: for example, a model was trained end-to-end in \cite{kong2018recurrent} by using a mean-shift algorithm.
+%  and introducing a ﬁxed number of labels (colors) and then dynamically assigning object instances to those labels during training (coloring) \cite{kulikov2018instance}
+
+\textbf{Boundary prediction} is another task that has seen noticeable progress thanks to deep supervision \cite{xie2015holistically,kokkinos2015pushing}. 
+Our work is based on \cite{liu2018affinity}, where a model is trained to classify whether a pair of pixels (not necessarily given by direct neighbors) belong to the same instance.
+
+\begin{itemize}
+    \item Ciao
+\begin{itemize}
 \item \textbf{Most related: predict short- and long-range affinities}.
@@
 \item \textit{Must-not-link edges:} initially introduced as hard-constraints \cite{malmberg2011generalized}, then introduced dynamically \cite{wolf2018mutex,levinkov2017comparative}. 
-\item Local-search approximations of MC: greeedy fixation and greedy additive edge contraction \cite{levinkov2017comparative}
+\item Local-search approximations of MC: greeedy fixation and greedy additive edge contraction \cite{levinkov2017comparative}, and mention size-depending GAEC
 \end{itemize}
+\item Section 4 requires to related work in connectomics!
+\item Conclusion: we specifically build on top of work by......!! We combine the work of MWS, GMIS, GAEC, GF by defining a simple framework and then compare them!
 \end{itemize}

### 2019-04-28 chapters/3_algorithm.tex
Start rewriting related work

@@
 An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph.
-Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that $\tilde{V} \subseteq V$ and each node $u\in \tilde{V}$ represents the cluster $S_u \in \Pi$.
+Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that $\tilde{V} \subseteq V$ and each node $u\in \tilde{V}$ represents the cluster $S_u \in \Pi$ including $u\in V$.
 Edges in $\tilde{E}$ represent adjacency-relationships between clusters and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$.
@@
 % \UPDATE{In this way we do not need to recompute the interaction by using the linkage criterion over all the edges of the original graph, that would be computationally expensive.}
-\paragraph{The proposed edge contraction algorithm} The proposed generalized Algorithm \ref{main_alg} then proceeds as follows, similarly to the one proposed in \cite{levinkov2017comparative}.
+\paragraph{The proposed edge contraction algorithm} Algorithm \ref{main_alg} then proceeds as follows, similarly to the one presented in \cite{levinkov2017comparative}.
 It starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first.
@@
  the algorithm performs a standard agglomerative HC by returning only one single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see Fig.
-\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}).
-The choice of update rule determines the type of linkage (Table \ref{tab:linkage-criteria}, column 2, unsigned graphs).
+\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}), where the choice of update rule determines the type of linkage (Table \ref{tab:linkage-criteria}, column 2 with unsigned graphs).
 
-On the other hand, in the case of graphs with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was already proposed in \cite{levinkov2017comparative} (Table \ref{tab:linkage-criteria}, sum update rule, row 1).
+Given a graph with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was already proposed in \cite{levinkov2017comparative} (Table \ref{tab:linkage-criteria}, sum update rule, row 1).
 They present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms solving the multicut optimization problem.
 
-A clustering algorithm for signed graphs dynamically introducing cannot-link constraints was also proposed in \cite{wolf2018mutex}.
+Another proposed clustering algorithm for signed graphs, named Mutex Watershed \cite{wolf2018mutex}, also introduces dynamical cannot-link constraints.
 In the supplementary material (Sec.
-\ref{sec:equivalence_MWS}) we show how this algorithm, named Mutex Watershed, can be seen as an efficient implementation of \algname{} with the \emph{absolute-maximum} update rule defined in Table \ref{tab:linkage-criteria}, row 2.
-Then, we also observe that, for this choice of update rule, \algname{} returns the same clustering with or without cannot-link constraints.
+\ref{sec:equivalence_MWS}) we show how it can be seen as an efficient implementation of \algname{} with the \emph{absolute-maximum} update rule defined in Table \ref{tab:linkage-criteria} and we also observe that this case the algorithm returns the same clustering with or without enforcing cannot-link constraints.
 
-New variations of agglomerative clustering on signed graphs that, to our knowledge, were never mentioned in the literature are given by \algname{} with update rules \emph{mean}, \emph{max} and \emph{min} (rows 3 to 5 in Table \ref{tab:linkage-criteria}).
+On the other hand, new variations of agglomerative clustering on signed graphs that, to our knowledge, were never mentioned in the literature are given by \algname{} with update rules \emph{mean}, \emph{max} and \emph{min} (rows 3 to 5 in Table \ref{tab:linkage-criteria}).
 
-In this work we test and compare the five update rules listed in Table \ref{tab:linkage-criteria} that represents the most common options. 
-Apart from these, \cite{nunez2013machine} proposes a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features.
-Other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}), whereas
+In this work we test and compare these algorithms and the five update rules listed in Table \ref{tab:linkage-criteria} that represent the most common options. 
+Nevertheless, more elaborated options exist: \cite{nunez2013machine} proposes a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}), whereas
 \cite{funke2018large} uses a \emph{quantile} update rule by populating a histogram for each inter-cluster interaction.

### 2019-04-28 chapters/5_experiments_noise.tex
Start rewriting related work

@@
 
-    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge}.
-(a) shows the original predictions $F(x)$, (b) the merge-biased version $\tilde{F}_{+}(x;\mathcal{K})$ defined in Eq.
-\ref{eq:noise_biased_predictions} and c) the split-biased version $\tilde{F}_{-}(x;\mathcal{K})$.
+    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise.
 Blue pixels represent boundary evidence.
+Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
     %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 

### 2019-04-29 chapters/2_rel_work.tex
Finish rewriting related work

@@
 A watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction and a template matching scheme using scene depth information is proposed in \cite{uhrig2016pixel}.
-Another line of research uses metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,novotny2018semi,kulikov2018instance}
+Another line of research uses metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,novotny2018semi,kulikov2018instance}.
 % \TODO{What about \cite{liang2018proposal} using spectral clustering?}. 
-A clustering algorithm, e.g. HDBSCAN, is then applied to retrieve instances: for example, a model was trained end-to-end in \cite{kong2018recurrent} by using a mean-shift algorithm.
+Final instances are then retrieved by applying a clustering algorithm, e.g.
+DBSCAN, and the method of \cite{kong2018recurrent} based on the mean-shift algorithm is an example of approach trained end-to-end.
 %  and introducing a ﬁxed number of labels (colors) and then dynamically assigning object instances to those labels during training (coloring) \cite{kulikov2018instance}
 
-\textbf{Boundary prediction} is another task that has seen noticeable progress thanks to deep supervision \cite{xie2015holistically,kokkinos2015pushing}. 
-Our work is based on \cite{liu2018affinity}, where a model is trained to classify whether a pair of pixels (not necessarily given by direct neighbors) belong to the same instance.
+\textbf{Edge detection} is another task that has seen noticeable progress thanks to deep learning \cite{xie2015holistically,kokkinos2015pushing}.
+This is also nicely illustrated by the evolution of neuron segmentation for connectomics, an important field of neuroscience we also address in our experiments.
+CNNs were introduced to this application in \cite{jain2007supervised}, but further progress in model architectures and data augmentation methods lead to much more refined boundary map predictions \cite{lee2017superhuman,meirovitch2016multi,ciresan2012deep} as well as structured loss learning \cite{funke2018large,turaga2009maximin}.
+% or trained an end-to-end watershed region growing algorithm \cite{wolf2017learned}.  
+In all these methods, subsequent postprocessing and superpixel merging outputs the final segmentation.
+Some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy.
+The lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while flood-filling networks \cite{januszewski2018high} eliminate superpixels by training a recurrent CNN to perform region growing one region at the time.
+% \SOURCE{SSHMT} Check Funke proposals
 
-\begin{itemize}
-    \item Ciao
-\begin{itemize}
-\item \textbf{Most related: predict short- and long-range affinities}.
-For each pixel we fix a set of neighboring pixels (not necessarily limited to the direct neighbors) and CNN predicts how likely it is for each pixel pair to be in the same instance \cite{liu2018affinity,wolf2018mutex,lee2017superhuman,xie2015holistically,Maire_2016_CVPR}.
-Mention that  \cite{liu2018affinity} is SoA on cityscapes for proposal-free methods and \cite{wolf2018mutex} is SoA on ISBI
-% \item \cite{liu2018affinity} achieved comparable results to methods based on object proposal like Mask-R-CNN on natural images (Cityscapes); \cite{wolf2018mutex} achieved SOA results on a biological images (ISBI)
-% \item Side comment: Even with pixel embedding vectors we can deduce affinities or signed costs
-% (see MWS paper for a good review)
+\textbf{Agglomerative graph clustering} has often been successfully applied to instance segmentation \cite{ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down/divisive approaches like graph cuts.
+Outside of neuron segmentation, novel termination criteria and merging strategies were proposed: \cite{malmberg2011generalized}, for example, uses fixed sets of merge constraints during the agglomeration, while ultrametric contour maps \cite{arbelaez2011contour} combines an oriented watershed transform with an edge detector and agglomerates superpixels until the ultrametric distance exceeds a learned threshold.
+An optimization approach is considered in \cite{kiran2014global} by performing greedy merge decisions minimizing a certain energy.
+The popular graph-based segmentation proposed in \cite{felzenszwalb2004efficient} then defines a measure of quality for the current clusters and stops when the merge costs would exceed this measure.
+\TODO{Roman's paper, Cocoons}
+On the other hand, several approaches simply use some of the classical hierarchical clustering methods to define inter-cluster dissimilarity, e.g.
+average linkage \cite{liu2018affinity,lee2017superhuman} or median \cite{funke2018large}.
+The GALA algorithm in \cite{nunez2013machine,knowles2016rhoananet} features instead a linkage criterion learned by a neural network.
 
-\end{itemize}
+\textbf{Clustering of signed graphs} is another important line of research with the goal of balancing a graph with both attractive and repulsive interactions between clusters, avoiding the need for external stopping criteria.
+The problem of finding an optimally balanced clustering has a long history in the field of combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}.
+The name \emph{correlation clustering} was coined by \cite{bansal2004correlation} that also showed its NP-hardness, while its connection with graph multicuts was made by \cite{demaine2006correlation}.
+Modern integer linear programming solvers can tackle problem instances of considerable size \cite{andres2012globally}, and for even larger problems some methods use good approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy heuristic algorithms \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient,kardoostsolving} or persistence criteria to reduce the size of the problem \cite{lange2018partial,lange2018combinatorial}.
+\TODO{Cannot-link constraints!}
+% Missing: Funke proposals, discussion about cannot-link constraints!!!
 
-\item \textbf{Graph clustering related work}:
-\begin{itemize}
-    \item popular in image segmentation: \textbf{agglomerative clustering}.
-    \item {\small More from \cite{mullner2011modern}: The seven most common methods are termed single, complete, average (UPGMA), weighted (WPGMA, McQuitty), Ward, centroid (UPGMC) and median (WPGMC) linkage (see Everitt et al., 2011, Table 4.1).
-They are implemented in standard numerical and statistical software such as R (R Development Core Team, 2011), MATLAB (The MathWorks, Inc., 2011), Mathematica (Wolfram Research, Inc., 2010), SciPy (Jones et al., 2001).}
-    \item Why: more efficient than divisive approaches and graph cuts; does not usually require to specify the final number of clusters (e.g.
-spectral clustering) or seed nodes (e.g.
-watershed, random walker)
-    % old graph cut paper: \cite{shi2000normalized}
-    % \item \emph{[other clustering methods working in an euclidean embedding space like mean-shift, K-means, Mixture models, BIRCH... can most probably be omitted]}
-    \item many segmentation pipelines used to start the agglomeration from superpixels (SLIC, \cite{felzenszwalb2004efficient}, watershed) to reduce size of the problem 
-    \item usually we build an hierarchy of clusters (or a \emph{merge-tree}): \TODO{find meaningful order}
-    \item clustering paper suggested by Roman; Cocoons
+This work combines the clustering algorithms proposed in \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a simple generalized framework for agglomerative clustering and \UPDATE{evaluate them on an instance segmentation task by adopting ideas and CNN models from \cite{liu2018affinity,wolf2018mutex,funke2018large} to predict boundary evidence and long-range pixelwise relationships.}
 
-% \item \textit{Some reference (atm in random order, to be continued)} 
-\begin{itemize}
+% \begin{itemize}
 
-\item examples on natural images \cite{ren2013image,liu2016image}; ultra-metric contour map \cite{arbelaez2011contour};
-\item \emph{Linkage criteria}: arithmetic average \cite{liu2018affinity,lee2017superhuman}; 
-quantiles (median) \cite{funke2018large}; % and structured training 
-   learned linkage criteria \cite{nunez2013machine}; 
-\item An optimization perspective is taken in \cite{kiran2014global} %, which introduces h-increasing energy functions and builds the hierarchy incrementally such that merge decisions greedily minimize the energy
-% Check MWS for description and more details
-\item normalized cuts and combinatorial grouping \cite{arbelaez2014multiscale}
-\item In \emph{connectomics}: \cite{liu2016sshmt}.
-Use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy.
-Using local \cite{liu2014modular,krasowski2015improving} or structured \cite{funke2015learning,uzunbas2016efficient} learning based methods % \SOURCE{SSHMT} Check Funke proposals
-\end{itemize}
-\item Methods finding a flat clustering (no hierarchy): efficient Graph-based Image segmentation \cite{felzenszwalb2004efficient} % defines a measure of quality for the current regions and stops when the merge costs would exceed this measure
-\item \textbf{Signed graphs} \TODO{more}
-\begin{itemize}
-    % \item problem with hierarchical merge-trees is how to choose one single threshold.
+% \item \textbf{Graph clustering related work}:
+% \begin{itemize}
+
+%     \item clustering paper suggested by Roman; Cocoons
+
+% % \item \textit{Some reference (atm in random order, to be continued)} 
+% \begin{itemize}
+
+% \item examples on natural images \cite{ren2013image,liu2016image}; ultra-metric contour map \cite{arbelaez2011contour};
+% \item \emph{Linkage criteria}: arithmetic average \cite{liu2018affinity,lee2017superhuman}; 
+% quantiles (median) \cite{funke2018large}; % and structured training 
+%    learned linkage criteria \cite{nunez2013machine}; 
+% \item An optimization perspective is taken in \cite{kiran2014global} %, which introduces h-increasing energy functions and builds the hierarchy incrementally such that merge decisions greedily minimize the energy
+% % Check MWS for description and more details
+% \item normalized cuts and combinatorial grouping 
+% \end{itemize}
+% \item Methods finding a flat clustering (no hierarchy): efficient Graph-based Image segmentation \cite{felzenszwalb2004efficient} % defines a measure of quality for the current regions and stops when the merge costs would exceed this measure
+% \item \textbf{Signed graphs}
+% \begin{itemize}
+%     % \item problem with hierarchical merge-trees is how to choose one single threshold.
 Choose one single fixed density level.
@@
 In density space, \cite{campello2013density}
-    \item Multicut pipiline and heuristics \cite{beier2017multicut}... 
-    % \item \textit{\textbf{Multicut} has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region.
+%     \item Multicut pipiline and heuristics \cite{beier2017multicut}... 
+%     % \item \textit{\textbf{Multicut} has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region.
 Its great drawback is that its optimization is NP-hard.} \SOURCE{MWS}.
 
-\item hierarchy and multicut proposals \cite{funke2018candidate}
-\item \textit{Must-not-link edges:} initially introduced as hard-constraints \cite{malmberg2011generalized}, then introduced dynamically \cite{wolf2018mutex,levinkov2017comparative}. 
-\item Local-search approximations of MC: greeedy fixation and greedy additive edge contraction \cite{levinkov2017comparative}, and mention size-depending GAEC
-\end{itemize}
-\item Section 4 requires to related work in connectomics!
-\item Conclusion: we specifically build on top of work by......!! We combine the work of MWS, GMIS, GAEC, GF by defining a simple framework and then compare them!
-\end{itemize}
+% \item hierarchy and multicut proposals \cite{funke2018candidate}
+% \item \textit{Must-not-link edges:} initially introduced as hard-constraints \cite{malmberg2011generalized}, then introduced dynamically \cite{wolf2018mutex,levinkov2017comparative}. 
+% \item Local-search approximations of MC: greeedy fixation and greedy additive edge contraction \cite{levinkov2017comparative}, and mention size-depending GAEC
+% \end{itemize}
+% \end{itemize}
 
-\end{itemize}
+% \end{itemize}

### 2019-04-29 chapters/3_algorithm.tex
Finish rewriting related work

@@
             \midrule\midrule
-            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} & \thead{Sum Linkage\\Hierarchical Aggl.\\Clustering} & \thead{Greedy Additive \\ Edge Contraction \\\cite{levinkov2017comparative}} & \thead{Greedy \\Fixation \\\cite{levinkov2017comparative}} \\ \midrule
+            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} & \thead{Sum Linkage\\Hierarchical Aggl.\\Clustering} & \thead{Greedy Additive \\ Edge Contraction \\\cite{keuper2015efficient}} & \thead{Greedy \\Fixation \\\cite{levinkov2017comparative}} \\ \midrule
 
@@
 
-Given a graph with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was already proposed in \cite{levinkov2017comparative} (Table \ref{tab:linkage-criteria}, sum update rule, row 1).
+Given a graph with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was already proposed in \cite{levinkov2017comparative,keuper2015efficient} (Table \ref{tab:linkage-criteria}, sum update rule, row 1).
 They present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms solving the multicut optimization problem.

### 2019-04-30 chapters/1_intro.tex
Finish rewriting related work
Update images and update minor details

@@
 Proposal-based methods consist of two steps: detecting objects, for example by finding bounding boxes, and assigning pixels to the detected instances \cite{he2017mask,dai2016instance,li2017fully}.
-Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example electron microscopy image volumes of neurons \cite{arganda2015crowdsourcing}, where objects are not approximated well by bounding boxes.
+Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing}, where objects are not approximated well by bounding boxes.
 % More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)
-Thus, there is a growing interest for more efficient proposal-free methods that perform IS by directly predicting pixel features and then grouping pixels into object instances \TODO{REFS}.
-In this work, we focus on a proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance.
-Recently, \cite{liu2018affinity} used this approach and achieved performances comparable to proposal-based methods on the Cityscapes dataset; \UPDATE{similarly, the method was used in \cite{wolf2018mutex} to achieve state-of-the-art results in a neuron segmentation challenge.} \TODO{Rewrite}
+Thus, there is a growing interest for more efficient proposal-free methods that perform IS by directly predicting pixel features and then grouping pixels into object instances \cite{kong2018recurrent,novotny2018semi,kulikov2018instance,kirillov2017instancecut}.
+In this work, we focus on a common proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance.
+Recently, this approach was successfully applied both to neuron segmentation of 3D EM image stacks \cite{lee2017superhuman,wolf2018mutex} and instance segmentation of 2D urban scenes \cite{liu2018affinity}, where it achieved performances comparable to proposal-based methods.
 
@@
 These methods require the user to specify the desired numbers of segments or a termination criterion (as in spectral clustering or iterated normalized cuts) or even a stronger version of supervision in terms of seeds (as in seeded watershed or random walker).
-
-Another popular method for graph clustering is hierarchical clustering (HC) which creates an hierarchy of clusters.
+Hierarchical clustering (HC) is also a popular method, which creates an hierarchy of clusters.
 Agglomerative HC is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}.
@@
 
-Other clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between pixels \TODO{REFS}.
+Other clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between pixels.
 The advantage of using signed graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters.
-This can be done optimally by solving the so-called \emph{multicut optimization problem} or \emph{correlation clustering} \cite{kappes2011globally,chopra1991multiway}; however, this problem is NP-hard.
-For problems of considerable size, good approximations exist \cite{yarkony2012fast,pape2017solving}, and for even larger problems efficient greedy algorithms were recently proposed \cite{levinkov2017comparative,wolf2018mutex}.
+This can be done optimally by solving the so-called \emph{multicut optimization problem} or \emph{correlation clustering} \cite{kappes2011globally,chopra1991multiway}.
+However, this problem is NP-hard, so good approximations \cite{yarkony2012fast,pape2017solving} and efficient greedy heuristics \cite{levinkov2017comparative,wolf2018mutex} were proposed.
 
-Our main contribution is a framework for graph clustering that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract).
-Various existing clustering algorithms, previously introduced in \cite{levinkov2017comparative,wolf2018mutex,lance1967general}, share the general procedure defined in our framework, but differ in the way in which the interaction between clusters is updated after each agglomeration step.
-In this work, we also introduce new variations of these algorithms by allowing the possibility of enforcing mutual-exclusion relationships between clusters during the agglomeration.
+Our main contribution is a review framework for graph clustering that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract).
+Various existing clustering algorithms, previously introduced in \cite{levinkov2017comparative,wolf2018mutex,kardoostsolving,lance1967general}, share the general procedure defined in our framework, but differ in the way in which the interaction between clusters is updated after each agglomeration step.
+Moreover, we also introduce new variations of these algorithms by allowing the possibility of enforcing mutual-exclusion relationships between clusters.
 
-Finally, \UPDATE{we test these different agglomerative clustering algorithms} on the task of instance segmentation both on the CREMI neuron segmentation challenge and the Cityscapes dataset, by comparing achieved scores, efficiency and robustness to noisy edge weights.
-\TODO{Add chapters description}
+We evaluate the performances of these different agglomerative clustering algorithms on image instance segmentation of 2D urban scenes (CityScapes dataset) and 3D biological image stacks (CREMI neuron segmentation challenge), by comparing achieved scores, efficiency and robustness to noisy edge weights.
+\TODO{Chapters description}
 
@@
 \centering
-\includegraphics[width=\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
+% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
+\includegraphics[width=\textwidth,trim=0.4in 1.3in 0.in 0.2in,clip]{./figs/intro_image.jpg} % left bottom right top
 \caption{\small 

### 2019-04-30 chapters/2_rel_work.tex
Update images and update minor details

@@
 \section{Related work} \label{sec:related_work}
+% In recent years there has been considerable progress in pixel-level understanding tasks of computer vision, such as semantic segmentation \cite{long2015fully,kong2018recurrent,chen2018deeplab}, boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, %, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet},
+Recent progress in semantic segmentation \cite{long2015fully,kong2018recurrent,chen2018deeplab}, boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, %, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet},
+and pose estimation \cite{wei2016convolutional,cao2017realtime} was mostly associated with new key ideas and architectures in deep learning, like dilated convolutions \cite{yu2015multi,chen2018deeplab} or ``hourglass'' architectures with skip connections \cite{ronneberger2015u,paszke2016enet} increasing the receptive field of view of the model.
 
-% \begin{itemize}
-% \item Motivation 2:
-% \begin{itemize}
-% \item HC has been always really popular in computer vision: \emph{Instance segmentation} is a task of computer vision that involves the detection of all objects in an image by performing pixel-level segmentation of each instance.
-% \item Since conventional unsigned graph agglomerative clustering algorithms, such as the well-known linkage methods [1], usually are quite sensitive to noise and outliers [1] (As their affinities are directly computed using pairwise distances between samples), most methods were based on multi-step pipelines first predicting superpixels (to reduce noise).
-% \item These methods are still commonly used for specific instance segmentation applications: connectomics, build merge-tree 
-%  %https://arxiv.org/pdf/1208.5092.pdf
-% \item still commonly used for building merge-trees, give recent examples in connectomics (Sebastian Seung, etc...) % https://arxiv.org/abs/1608.04051
-% \item Graph clustering algorithms recently gained more and more popularity with the advent of deep-learning and its application to instance segmentation
-% \item Deep convolutional neural nets (CNNs) has been successfully applied to a wide range of tasks of computer vision and pixel-level image understanding, such as \UPDATE{boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, semantic segmentation \cite{long2015fully,chen2018deeplab,kong2018recurrent}, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet}, and pose estimation \cite{wei2016convolutional,cao2017realtime}.}
-% % \SOURCE{\cite{kong2018recurrent}}
-
-% \item Currently there are two successful approaches used for proposal-free bottom-up instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likely it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}
-
-% \item Both approaches requires a final clustering algorithm to output the final instance segmentation
-
-%  and we can define a grid graph, where each vertex represents a pixel, with short- and long-range edge connections
-
-%  and find the final instance segmentation by using a graph clustering algorithm.
-
-% \item GMIS achieved 
-% comparable results to methods based on object 
-% proposal like Mask-R-CNN on natural images 
-% (Cityscapes); MWS achieved SOA results on a 
-% biological images (ISBI)
-
-% \item Out contributions:
-
-% \begin{itemize}
-%  \item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and quality of the final clustering in terms of multicut energy) \textbf{Comparison paper}
-%  \item \textit{if we get good scores on CREMI dataset}: we show that also on neuro-data it is worth to skip the hand-crafted superpixel step and compute the final segmentation directly from the CNN affinities (MWS already showed it on the ISBI dataset): main selling point is again the almost-parameter free feature of the method
-% \end{itemize}
-% \end{itemize}
-% \end{itemize}
-
-% More details about instance segmentation (move to related work)
-% \begin{itemize}
-
-% \item 
-% \item Many recent successful methods for instance segmentation %, usually named \emph{proposal-based methods}, 
-%  use heuristic approaches that start from the classical computer vision task of \emph{object detection}, where the goal is to localize each objects using a bounding box, and then predict both a pixel-level mask of each instance and a semantic label (classify the objects in the bounding box).
-\TODO{Is it really general enough as a description...?} \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}
-% \item While effective, these approaches are \UPDATE{somewhat unsatisfying (copy/paste, change: present some faults)} because:
-% \begin{itemize}
-% \item they rely on the object detector and non-maximum suppression heuristics to count how many instances are present in the image, 
-% \item they tend to underperform in cluttered scenes, since instance assignment is often carried out independently for each detection; 
-% \item they are not usable for wiry or articulated objects (e.g. in the field of connectomics and neuron segmenation from electron microscopy images) 
-% \item their architecture do not usually prevent a pixel to be shared between multiple instances
-% \item they do not scale up well since each proposal has to be singularly processed by the CNN. 
-% % \item (difficult to train in an end-to-end manner: interface between instance segmentation and detection is non-differentiable)
-% % \item (architecture is complex and hard to tune and “debug”...?)
-% \end{itemize}
-
-% \item Currently there are two successful approaches used for proposal-free (make brief intro) instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likely it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}
-
-% \item Both approaches requires a final clustering algorithm to output the final instance segmentation
-
-%  and we can define a grid graph, where each vertex represents a pixel, with short- and long-range edge connections
-
-%  and find the final instance segmentation by using a graph clustering algorithm.
-
-% \item Recent work (\cite{wolf2018mutex}, more...) shows that it is better to use \textbf{repulsion and attraction} (directly predict it with the classifier, no need to define seeds or to fix a threshold given an hierarchy of clusters)
-% \item solving correlation clustering problem (multicut) is too expensive for this application (even using recently proposed heuristics)
-% \item our contributions:
-% \begin{itemize}
-% \item we propose a unified and simple formalization of Agglomerative Clustering and show how many of the recently proposed methods can be seen as special cases (focusing in particular on signed graphs) (\textbf{review and comparison paper})
-% \item new clustering algorithms on signed graphs
-
-% \end{itemize}
-% \item on other datasets (connectomics) many methods are based on multi-step pipelines first predicting superpixels
-
-% \end{itemize}
-
-% \item Motivation 1:
-
-% \begin{itemize}
-
-% \item all HC methods only talk about positive edge weights, but it is actually easy to generalize them for negative and attractive edges. 
-% \item The standard version of HC is good for building hierarchy but problem with hierarchical merge-trees is how to choose one single threshold.
-Choose one single fixed density level.
-Ideally we would like to be able to cut the tree at different places to select our clusters.
-% \item An important line of research is based on the observation that superior partitionings are obtained when the graph has both attractive and repulsive edges.
-Solutions that optimally balance attraction and repulsion do not require external stopping criteria such as predefined number of regions or seeds.
-This generalization leads to the NP-hard problem of correlation clustering or (synonymous) multicut (MC) partitioning.
-\emph{Alternative:} multicut / correlation clustering partitions vertices with both attractive and repulsive interactions encoded into the edges of a graph.
-Multicut has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region.
-Its great drawback is that its optimization is NP-hard.
-
-% \end{itemize}
-In recent years there has been considerable progress in pixel-level understanding tasks of computer vision, such as semantic segmentation \cite{long2015fully,kong2018recurrent,chen2018deeplab}, boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, %, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet},
-and pose estimation \cite{wei2016convolutional,cao2017realtime}.
-This progress was mostly associated with new key ideas and architectures of deep convolutional convolutional networks (CNNs), like dilated/``atrous'' convolutions \cite{yu2015multi,chen2018deeplab} or ``hourglass'' architectures with skip connections \cite{ronneberger2015u,paszke2016enet} increasing the receptive field of view of the model.
-
-\textbf{Proposal-based instance segmentation methods} decompose the segmentation task into two steps that consists in generating object proposals or bounding boxes and assigning to each object a class and a binary segmentation mask \cite{he2017mask,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}.
+\textbf{Proposal-based methods} decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}.
 % Here I could have more: \cite{pinheiro2015learning,pinheiro2016learning,hu2017fastmask} and probably something more in Deep coloring
 % \item \emph{More references:} or generate generic proposal segments and then label each one with a semantic detector \cite{hariharan2014simultaneous,chen2015multi,hariharan2015hypercolumns,dai2015convolutional,uhrig2016pixel,he2017mask}.
-They commonly rely on Faster RCNN \cite{ren2015faster} and can be trained end-to-end using non-maximum suppression.
+They commonly rely on {Faster-RCNN}~\cite{ren2015faster} and can be trained end-to-end using non-maximum suppression.
 Other methods use instead recurrent models to sequentially generate instances one-by-one \cite{romera2016recurrent,ren2017end}.
 
-\textbf{Proposal-free methods} avoid the limitations of box proposals (e.g.
-for wiry objects) by directly grouping pixels into instances.
-For example, some approaches use a combinatorial framework for joint segmentation \cite{kirillov2017instancecut}, whereas others sequentially group pixels into lines and then instances \cite{liu2017sgn}.
+\textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances.
+For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for joint segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
 % encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; 
-A watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction and a template matching scheme using scene depth information is proposed in \cite{uhrig2016pixel}.
-Another line of research uses metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,novotny2018semi,kulikov2018instance}.
+a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
+Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,novotny2018semi,kulikov2018instance}.
 % \TODO{What about \cite{liang2018proposal} using spectral clustering?}. 
-Final instances are then retrieved by applying a clustering algorithm, e.g.
-DBSCAN, and the method of \cite{kong2018recurrent} based on the mean-shift algorithm is an example of approach trained end-to-end.
+Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrent}.
 %  and introducing a ﬁxed number of labels (colors) and then dynamically assigning object instances to those labels during training (coloring) \cite{kulikov2018instance}
 
-\textbf{Edge detection} is another task that has seen noticeable progress thanks to deep learning \cite{xie2015holistically,kokkinos2015pushing}.
-This is also nicely illustrated by the evolution of neuron segmentation for connectomics, an important field of neuroscience we also address in our experiments.
-CNNs were introduced to this application in \cite{jain2007supervised}, but further progress in model architectures and data augmentation methods lead to much more refined boundary map predictions \cite{lee2017superhuman,meirovitch2016multi,ciresan2012deep} as well as structured loss learning \cite{funke2018large,turaga2009maximin}.
+\textbf{Edge detection} also experienced recent noticeable progress \cite{xie2015holistically,kokkinos2015pushing}.
+This is nicely illustrated by the evolution of neuron segmentation for connectomics, a field of neuroscience we also address in our experiments.
+CNNs were introduced to this application in \cite{jain2007supervised}, but further progress in deep learning and data augmentation lead to much more refined boundary detection \cite{lee2017superhuman,meirovitch2016multi,ciresan2012deep}.
 % or trained an end-to-end watershed region growing algorithm \cite{wolf2017learned}.  
-In all these methods, subsequent postprocessing and superpixel merging outputs the final segmentation.
+Subsequent postprocessing and superpixel-merging outputs final instances.
 Some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy.
 The lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while flood-filling networks \cite{januszewski2018high} eliminate superpixels by training a recurrent CNN to perform region growing one region at the time.
+A structured learning approach was also proposed in \cite{funke2018large,turaga2009maximin}.
 % \SOURCE{SSHMT} Check Funke proposals
 
-\textbf{Agglomerative graph clustering} has often been successfully applied to instance segmentation \cite{ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down/divisive approaches like graph cuts.
-Outside of neuron segmentation, novel termination criteria and merging strategies were proposed: \cite{malmberg2011generalized}, for example, uses fixed sets of merge constraints during the agglomeration, while ultrametric contour maps \cite{arbelaez2011contour} combines an oriented watershed transform with an edge detector and agglomerates superpixels until the ultrametric distance exceeds a learned threshold.
-An optimization approach is considered in \cite{kiran2014global} by performing greedy merge decisions minimizing a certain energy.
-The popular graph-based segmentation proposed in \cite{felzenszwalb2004efficient} then defines a measure of quality for the current clusters and stops when the merge costs would exceed this measure.
-\TODO{Roman's paper, Cocoons}
-On the other hand, several approaches simply use some of the classical hierarchical clustering methods to define inter-cluster dissimilarity, e.g.
+\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts.
+Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters; whereas the optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy.
+\TODO{Roman, Cocoons, Benjamin}
+On the other hand, several segmentation pipelines use classical HC linkage criteria, e.g.
 average linkage \cite{liu2018affinity,lee2017superhuman} or median \cite{funke2018large}.
-The GALA algorithm in \cite{nunez2013machine,knowles2016rhoananet} features instead a linkage criterion learned by a neural network.
+The GALA algorithm in \cite{nunez2013machine,knowles2016rhoananet} features instead a linkage learned by a neural network.
 
-\textbf{Clustering of signed graphs} is another important line of research with the goal of balancing a graph with both attractive and repulsive interactions between clusters, avoiding the need for external stopping criteria.
-The problem of finding an optimally balanced clustering has a long history in the field of combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}.
+\textbf{Clustering of signed graphs} is another important line of research with the goal of balancing a graph with both attractive and repulsive cues.
+Finding an optimally balanced clustering has a long history in the field of combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}.
+%and can be done without the need to specify a termination criterion.
 The name \emph{correlation clustering} was coined by \cite{bansal2004correlation} that also showed its NP-hardness, while its connection with graph multicuts was made by \cite{demaine2006correlation}.
-Modern integer linear programming solvers can tackle problem instances of considerable size \cite{andres2012globally}, and for even larger problems some methods use good approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy heuristic algorithms \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient,kardoostsolving} or persistence criteria to reduce the size of the problem \cite{lange2018partial,lange2018combinatorial}.
+Modern integer linear programming solvers can tackle problem instances of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy heuristic algorithms \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger problems.
 \TODO{Cannot-link constraints!}
@@
 
-This work combines the clustering algorithms proposed in \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a simple generalized framework for agglomerative clustering and \UPDATE{evaluate them on an instance segmentation task by adopting ideas and CNN models from \cite{liu2018affinity,wolf2018mutex,funke2018large} to predict boundary evidence and long-range pixelwise relationships.}
-
-% \begin{itemize}
-
-% \item \textbf{Graph clustering related work}:
-% \begin{itemize}
-
-%     \item clustering paper suggested by Roman; Cocoons
-
-% % \item \textit{Some reference (atm in random order, to be continued)} 
-% \begin{itemize}
-
-% \item examples on natural images \cite{ren2013image,liu2016image}; ultra-metric contour map \cite{arbelaez2011contour};
-% \item \emph{Linkage criteria}: arithmetic average \cite{liu2018affinity,lee2017superhuman}; 
-% quantiles (median) \cite{funke2018large}; % and structured training 
-%    learned linkage criteria \cite{nunez2013machine}; 
-% \item An optimization perspective is taken in \cite{kiran2014global} %, which introduces h-increasing energy functions and builds the hierarchy incrementally such that merge decisions greedily minimize the energy
-% % Check MWS for description and more details
-% \item normalized cuts and combinatorial grouping 
-% \end{itemize}
-% \item Methods finding a flat clustering (no hierarchy): efficient Graph-based Image segmentation \cite{felzenszwalb2004efficient} % defines a measure of quality for the current regions and stops when the merge costs would exceed this measure
-% \item \textbf{Signed graphs}
-% \begin{itemize}
-%     % \item problem with hierarchical merge-trees is how to choose one single threshold.
-Choose one single fixed density level.
-Ideally we want to be able to cut the tree at different places to select our clusters.
-In density space, \cite{campello2013density}
-%     \item Multicut pipiline and heuristics \cite{beier2017multicut}... 
-%     % \item \textit{\textbf{Multicut} has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region.
-Its great drawback is that its optimization is NP-hard.} \SOURCE{MWS}.
-
-% \item hierarchy and multicut proposals \cite{funke2018candidate}
-% \item \textit{Must-not-link edges:} initially introduced as hard-constraints \cite{malmberg2011generalized}, then introduced dynamically \cite{wolf2018mutex,levinkov2017comparative}. 
-% \item Local-search approximations of MC: greeedy fixation and greedy additive edge contraction \cite{levinkov2017comparative}, and mention size-depending GAEC
-% \end{itemize}
-% \end{itemize}
-
-% \end{itemize}
+\UPDATE{This work combines the clustering algorithms proposed in \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a simple generalized framework for agglomerative clustering and evaluate them on an instance segmentation task by adopting ideas and CNN architectures from \cite{liu2018affinity,wolf2018mutex,funke2018large} to predict long-range relationships between pixels and boundary evidence between instances.}

### 2019-04-30 chapters/3_algorithm.tex
Update images and update minor details

@@
 % !TEX root = ../agglo_clust_review.tex
-
-\begin{minipage}[t]{\textwidth}
-        \centering
-        \begin{minipage}[t]{0.49\textwidth}
-\centering
-        \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
-\captionof{figure}{{\small 
-Example of edge contraction of $e_{uv}$.
-The first row represents the original graph $\mathcal{G}$ and the clustering $\Pi$ (purple lines), where green edges are not on the cut.
-Red bars indicate cannot-link constraints, whereas the contracted graph $\tilde{\mathcal{G}}_\Pi$ is shown in the second row.
-In step (ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$.
-In (iii), the two double edges $e_{ut}$ and $e_{vt}$ resulting from the contraction are replaced by a single constrained edge with updated interaction $f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}))$, where $f$ is defined in Table \ref{tab:linkage-criteria}.}
-\label{fig:edge_contraction_and_contr_graph} }
-    \end{minipage}\hspace{0.01\textwidth}
-    \begin{minipage}[t]{0.49\textwidth}
-        \centering
-\includegraphics[width=0.8\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.jpg}
-\captionof{figure}{\small 
-\UPDATE{Comparison of \algname{}  with (top) and without (bottom) enforcing cannot-link constraints on a toy graph with positive (green) and repulsive (red) interactions.
-Only contracted graph is represented; every column represent one iteration of the algorithm; the selected edge at each iteration is highlighted in yellow; constrained edges are represented with red bars.
-We note that the two resulting clusterings are different.}
-\label{fig:algorithm_with_without_CLC}}
-    \end{minipage}
-\end{minipage}
 
@@
 
-Given a simple graph $\mathcal{G}(V,E)$, we call the set $\Pi$ a \emph{clustering} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $S_i \cap S_j = \emptyset$ for every $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
-In the following we denote the cluster associated with node $u$ as $S_u$.
+We consider an undirected simple graph $\mathcal{G}(V,E)$, in which nodes can represent either pixels, superpixels or voxels.
+We call the set $\Pi$ a \emph{clustering} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $S_i \cap S_j = \emptyset$ for each $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
+In the following we denote as $S_u$ the cluster associated with node $u$.
 % \begin{equation}
@@
 In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes.
-The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+\in \mathbb{R}^+$ to each edge $e \in E$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that several formalisms defining positively weighted graphs associate to each edge a positive scalar that represents a metric or distance on the graph.
-In these formalisms, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+: E \rightarrow \mathbb{R}^+$.}.
-On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^- \in \mathbb{R}^+$ to each edge: the higher this weight, the greater the desire of the incident vertices to be in different clusters.
-Often, graphs $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes are also defined as $\mathcal{G}(V,E,\cost)$, where $\cost: E \rightarrow \mathbb{R}$ represents a \emph{signed interaction} that combines both attraction and repulsion into one signed scalar number: % space: make equation in line
-\begin{equation}
-\cost_e = w_e^+ - w_e^- \in \mathbb{R}, \quad \quad \forall e \in E
-\end{equation}
-Graphs that have only positive weights can be clearly seen as a special case of the previously defined graph $\mathcal{G}(V,E,w^+,w^-)$, when $w^-_e=0$ and $\cost_e \geq 0$ for every $e \in E$.
+The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that several formalisms for positively weighted graphs associate to each edge a positive scalar that represents a metric or distance on the graph, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+: E \rightarrow \mathbb{R}^+$.}.
+On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters.
+Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are also often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring signed edge weights: ${\cost_e = w_e^+ - w_e^- \in \mathbb{R}, \, \forall e \in E}$.
+Graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0$ and $w^-_e=0$ for each $e \in E$.
 
@@
 
+\begin{minipage}{\textwidth}
+        \centering
+        \begin{minipage}{0.49\textwidth}
+\centering
+        % \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
+        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
+\captionof{figure}{ 
+Example of edge contraction.
+First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (red bars).
+Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$.
+In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$.
+In step iii), double edges $e_{ut}$ and $e_{vt}$ resulting from edge contraction are replaced by single edge with updated interaction $f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}))$, see definitions in Tab.~\ref{tab:linkage-criteria}.
+\label{fig:edge_contraction_and_contr_graph} }
+    \end{minipage}\hspace{0.01\textwidth}
+    \begin{minipage}{0.49\textwidth}
+        \centering
+\includegraphics[width=0.8\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.jpg}
+\captionof{figure}{ 
+\UPDATE{Comparison of \algname{}  with (top) and without (bottom) enforcing cannot-link constraints on a toy graph with positive (green) and repulsive (red) interactions.
+Only contracted graph is represented; every column represent one iteration of the algorithm; the selected edge at each iteration is highlighted in yellow; constrained edges are represented with red bars.
+We note that the two resulting clusterings are different.}
+\label{fig:algorithm_with_without_CLC}}
+    \end{minipage}
+\end{minipage}
+
 \subsection{Generalized Algorithm for Signed Graphs Agglomerative Clustering} \label{sec:algorithm}
 
-We now present our main contribution: a Generalized Algorithm for Signed Graphs Agglomerative Clustering (\algname) that can describe in a simple form several graph partitioning algorithms previously introduced in the literature and highlights the existence of new ones.
+We now present a Generalized Algorithm for Signed Graphs Agglomerative Clustering (\algname) that can describe in a simple form several graph partitioning algorithms previously introduced in the literature and highlights the existence of new ones.
 
@@
 \ref{main_alg} is \texttt{True}, then the edge $e_{uv}$ is flagged as cannot-link constraint.
-In the Supplementary material we provide a more detailed description of the algorithm and we also comment on its computational complexity (Sec. \ref{sec:complexity}).
+In the Supplementary material we comment on the algorithm computational complexity (Sec. \ref{sec:complexity}).
 
@@
 
-Another proposed clustering algorithm for signed graphs, named Mutex Watershed \cite{wolf2018mutex}, also introduces dynamical cannot-link constraints.
-In the supplementary material (Sec.
-\ref{sec:equivalence_MWS}) we show how it can be seen as an efficient implementation of \algname{} with the \emph{absolute-maximum} update rule defined in Table \ref{tab:linkage-criteria} and we also observe that this case the algorithm returns the same clustering with or without enforcing cannot-link constraints.
+Mutex Watershed \cite{wolf2018mutex}, another algorithm for signed graphs, also introduces dynamical cannot-link constraints.
+In supplementary material (Sec.
+\ref{sec:equivalence_MWS}) we show how it can be seen as an efficient implementation of \algname{} with the \emph{abs-max} update rule (see Tab.
+\ref{tab:linkage-criteria}) and observe that in this case \algname{} returns the same clustering with or without enforcing cannot-link constraints.
 
-On the other hand, new variations of agglomerative clustering on signed graphs that, to our knowledge, were never mentioned in the literature are given by \algname{} with update rules \emph{mean}, \emph{max} and \emph{min} (rows 3 to 5 in Table \ref{tab:linkage-criteria}).
+On the other hand, new variations of \algname{} that, to our knowledge, were never mentioned in the literature are showed in Tab.
+\ref{tab:linkage-criteria} by using signed graphs and update rules \emph{mean}, \emph{max} or \emph{min}.
 
-In this work we test and compare these algorithms and the five update rules listed in Table \ref{tab:linkage-criteria} that represent the most common options. 
-Nevertheless, more elaborated options exist: \cite{nunez2013machine} proposes a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}), whereas
+In this work we compare the algorithms listed in Table \ref{tab:linkage-criteria}, which represent the most common options. 
+Nevertheless, more elaborated options exist: \cite{nunez2013machine} proposes a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas
 \cite{funke2018large} uses a \emph{quantile} update rule by populating a histogram for each inter-cluster interaction.

### 2019-04-30 chapters/2_rel_work.tex
Small changes

@@
 a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
-Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,novotny2018semi,kulikov2018instance}.
+Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,kulikov2018instance}.
+% Semi-convolutiona: \cite{novotny2018semi}
 % \TODO{What about \cite{liang2018proposal} using spectral clustering?}. 
@@
 Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters; whereas the optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy.
-\TODO{Roman, Cocoons, Benjamin}
+\TODO{Roman, Cocoons, Benjamin?}
 On the other hand, several segmentation pipelines use classical HC linkage criteria, e.g.
@@
 Modern integer linear programming solvers can tackle problem instances of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy heuristic algorithms \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger problems.
-\TODO{Cannot-link constraints!}
+\TODO{Cannot-link constraints?}
 % Missing: Funke proposals, discussion about cannot-link constraints!!!

### 2019-05-05 chapters/1_intro.tex
Small changes
Add vectorized images

@@
 % \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
-\includegraphics[width=\textwidth,trim=0.4in 1.3in 0.in 0.2in,clip]{./figs/intro_image.jpg} % left bottom right top
-\caption{\small 
-Intro image: explain algorithm, main ideas and contributions
+\includegraphics[width=\textwidth]{./figs/intro_image.pdf} % left bottom right top
+\caption{
+\TODO{Intro image caption} % main ideas and contributions
 \label{fig:intro_figure}}

### 2019-05-05 chapters/3_algorithm.tex
Small changes
Add vectorized images

@@
 
-\begin{minipage}{\textwidth}
-        \centering
-        \begin{minipage}{0.49\textwidth}
-\centering
-        % \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
-        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
-\captionof{figure}{ 
-Example of edge contraction.
-First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (red bars).
-Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$.
-In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$.
-In step iii), double edges $e_{ut}$ and $e_{vt}$ resulting from edge contraction are replaced by single edge with updated interaction $f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}))$, see definitions in Tab.~\ref{tab:linkage-criteria}.
-\label{fig:edge_contraction_and_contr_graph} }
-    \end{minipage}\hspace{0.01\textwidth}
-    \begin{minipage}{0.49\textwidth}
-        \centering
-\includegraphics[width=0.8\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.jpg}
-\captionof{figure}{ 
-\UPDATE{Comparison of \algname{}  with (top) and without (bottom) enforcing cannot-link constraints on a toy graph with positive (green) and repulsive (red) interactions.
-Only contracted graph is represented; every column represent one iteration of the algorithm; the selected edge at each iteration is highlighted in yellow; constrained edges are represented with red bars.
-We note that the two resulting clusterings are different.}
-\label{fig:algorithm_with_without_CLC}}
-    \end{minipage}
-\end{minipage}
-
 \subsection{Generalized Algorithm for Signed Graphs Agglomerative Clustering} \label{sec:algorithm}
@@
 During the agglomeration, the current clustering $\Pi$ is represented by a \emph{contracted graph} $\mathcal{G'}(\mathcal{G}, \Pi)$, such that each of its nodes represents a cluster $S \in \Pi$ and \emph{adjacent} clusters are linked by an edge.
+
+\begin{minipage}{\textwidth}
+        \centering
+        \begin{minipage}{0.49\textwidth}
+\centering
+        % \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
+        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
+\captionof{figure}{ 
+Example of edge contraction.
+First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (red bars).
+Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$.
+In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$.
+In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from edge contraction are replaced by single edge with updated interaction $f(\tilde{\cost}(e_{tu}), \tilde{\cost}(e_{tv}))$, see definitions in Tab.~\ref{tab:linkage-criteria}.
+\label{fig:edge_contraction_and_contr_graph}  }
+    \end{minipage}\hspace{0.01\textwidth}
+    \begin{minipage}{0.49\textwidth}
+        \centering
+\includegraphics[width=\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/add_constraints.pdf}
+\captionof{figure}{ 
+\UPDATE{Comparison of \algname{}  with (top) and without (bottom) enforcing cannot-link constraints on a toy graph with positive (green) and repulsive (red) interactions.
+Only contracted graph is represented; every column represent one iteration of the algorithm; the selected edge at each iteration is highlighted in yellow; constrained edges are represented with red bars.
+We note that the two resulting clusterings are different.}
+\label{fig:algorithm_with_without_CLC}}
+    \end{minipage}
+\end{minipage}
 

### 2019-05-06 chapters/1_intro.tex
Update images and reduce sizes

@@
 \caption{
-\TODO{Intro image caption} % main ideas and contributions
+{\small (\textbf{a}) Some iterations of the generalized algorithm on toy graphs with attractive (green) and repulsive (red) interactions.
+(\textbf{b}) Example of CREMI 2016 data \cite{cremiChallenge} overlaid with instance segmentation.
+(\textbf{c}) Agglomeration order, representing which pairs of neighboring pixels were merged first (blue) and later on (red).
+We note how similar update rules, like \emph{Sum} (in the middle) and \emph{Mean} (on the right), lead to strongly different merging orders. 
+% On the left: a single cluster is returned with only attractive interactions.
+}
+ % main ideas and contributions
 \label{fig:intro_figure}}

### 2019-05-06 chapters/2_rel_work.tex
Update images and reduce sizes

@@
 % \TODO{What about \cite{liang2018proposal} using spectral clustering?}. 
-Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrent}.
+Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}.
 %  and introducing a ﬁxed number of labels (colors) and then dynamically assigning object instances to those labels during training (coloring) \cite{kulikov2018instance}

### 2019-05-06 chapters/3_algorithm.tex
Update images and reduce sizes

@@
 In the next chapters we will use this objective as a way to measure how much a clustering is balanced.
+
+\begin{figure}
+        \centering
+        \begin{minipage}{0.49\textwidth}
+\centering
+        % \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
+        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
+\captionof{figure}{ 
+{\small Example of edge contraction.
+First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars).
+Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$.
+In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$.
+In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from edge contraction are replaced by single edge with updated interaction $f(\tilde{\cost}(e_{tu}), \tilde{\cost}(e_{tv}))$, see definitions in Tab.~\ref{tab:linkage-criteria}.
+}
+\label{fig:edge_contraction_and_contr_graph}  }
+    \end{minipage}\hspace{0.01\textwidth}
+    \begin{minipage}{0.49\textwidth}
+        \centering
+\includegraphics[width=0.91\textwidth]{./figs/add_constraints.pdf}
+\captionof{figure}{ 
+{\small Some iterations of the generalized algorithm  with (top) and without (bottom) adding cannot-link constraints.
+The graph has both attractive (green) and repulsive (red) edges; cannot-link constraints are given by violet bars.
+At each iteration, the edge selected by the algorithm is highlighted in yellow.
+When cannot-link constraints are enforced, the final clustering is given by two clusters instead of only one.}
+\label{fig:algorithm_with_without_CLC}}
+    \end{minipage}
+\end{figure}
 
@@
 
-\begin{minipage}{\textwidth}
-        \centering
-        \begin{minipage}{0.49\textwidth}
-\centering
-        % \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
-        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
-\captionof{figure}{ 
-Example of edge contraction.
-First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (red bars).
-Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$.
-In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$.
-In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from edge contraction are replaced by single edge with updated interaction $f(\tilde{\cost}(e_{tu}), \tilde{\cost}(e_{tv}))$, see definitions in Tab.~\ref{tab:linkage-criteria}.
-\label{fig:edge_contraction_and_contr_graph}  }
-    \end{minipage}\hspace{0.01\textwidth}
-    \begin{minipage}{0.49\textwidth}
-        \centering
-\includegraphics[width=\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/add_constraints.pdf}
-\captionof{figure}{ 
-\UPDATE{Comparison of \algname{}  with (top) and without (bottom) enforcing cannot-link constraints on a toy graph with positive (green) and repulsive (red) interactions.
-Only contracted graph is represented; every column represent one iteration of the algorithm; the selected edge at each iteration is highlighted in yellow; constrained edges are represented with red bars.
-We note that the two resulting clusterings are different.}
-\label{fig:algorithm_with_without_CLC}}
-    \end{minipage}
-\end{minipage}
-
 \paragraph{Update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.
@@
     \centering
+    \scriptsize
     \begin{subtable}[t!]{\textwidth}\centering
@@
             % \toprule\toprule
-             & &  \multirow{3}{*}{\textbf{Unsigned graphs}}  & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
+            \multicolumn{2}{c||}{}  &   & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
             % \cmidrule(l{.15em}){4-5}
             % \cline{4-5}
-            & & &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
-
+            \multicolumn{2}{c||}{} & \textbf{Unsigned graphs} &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
              &  &  &  \thead{\textsc{No}} & \thead{\textsc{Yes}} \\        
@@
             \midrule\midrule
-            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} & \thead{Sum Linkage\\Hierarchical Aggl.\\Clustering} & \thead{Greedy Additive \\ Edge Contraction \\\cite{keuper2015efficient}} & \thead{Greedy \\Fixation \\\cite{levinkov2017comparative}} \\ \midrule
+            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} & \thead{Sum Linkage\\Hier.
+Aggl.
+Clust.} & \thead{Greedy Additive \\ Edge Contraction \cite{keuper2015efficient}} & \thead{Greedy Fixation\\\cite{levinkov2017comparative}} \\ \midrule
 
-            \makecell[r]{Abs. \\ max:} & \thead[l]{
+            \makecell[r]{Absolute \\Max:} & \thead[l]{
             $
@@
             $}
-               & \thead{Single Linkage\\Hierarchical Aggl.\\Clustering \cite{lance1967general}} & \thead{Mutex \\Watershed \\\cite{wolf2018mutex}} & \thead{Mutex \\Watershed \\\cite{wolf2018mutex}} \\ \midrule
-            \makecell[r]{Mean:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                                 & \thead{ Average Linkage\\ Hierarchical Clust.
-\\(UPGMA) \cite{lance1967general}} & \thead{Average Linkage\\Signed Aggl.
+               & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Mutex Watershed \\\cite{wolf2018mutex}} & \thead{Mutex Watershed\\\cite{wolf2018mutex}} \\ \midrule
+            \makecell[r]{Mean:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                                 & \thead{ Average Linkage\\ Hier.
+Aggl.
 Clust.
-\\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
+\cite{lance1967general}} & \thead{Average Linkage\\Signed Aggl.
+Clust.
+(\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
 
-            Max: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Single Linkage\\Hierarchical Aggl.\\Clustering \cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl.
+            Max: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Single Linkage\\Hier.
+Aggl.
 Clust.
-\\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
+\cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl.
+Clust.
+(\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
 
-            Min:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Complete Linkage\\ Hierarchical Aggl.\\Clustering \cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl.
+            Min:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Complete Linkage\\ Hier.
+Aggl.
 Clust.
-\\ (\textbf{NEW})} & \thead{\textbf{NEW}}
+\cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl.
+Clust.
+(\textbf{NEW})} & \thead{\textbf{NEW}}
 
@@
     \end{subtable} 
-    \caption{The table lists the tested update rules $f$.
-Existing and new algorithms are given by a specific choice of update rule, type of graph (signed or unsigned) and optional use of cannot-link constraints.}
+    \caption{{\small The table lists the tested update rules $f$.
+Existing and new algorithms are given by a specific choice of update rule, type of graph (signed or unsigned) and optional use of cannot-link constraints.}}
     \label{tab:linkage-criteria}

### 2019-05-06 chapters/5_experiments_noise.tex
Update images and reduce sizes

@@
 \centering
-        \begin{subfigure}[t]{0.48 \textwidth}
+        \begin{subfigure}[t]{0.49 \textwidth}
         \centering
-        \includegraphics[width=0.98\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}
+        \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise.pdf}
 
-        \caption{Merge-biased opensimplex noise} \label{fig:thresh}
+        \caption{Merge-biased noise added to edge weights} \label{fig:thresh}
     \end{subfigure}%
-    \begin{subfigure}[t]{0.48 \textwidth}
+    \begin{subfigure}[t]{0.49 \textwidth}
         \centering
-        \includegraphics[width=0.98\textwidth,trim=0.29in 0.31in 0.31in 0.31in,clip]{./figs/split_noise.pdf}
-        \caption{Split-biased opensimplex noise} \label{fig:ws}
+        \includegraphics[width=\textwidth,trim=0.53in 0.35in 0.65in 0.80in,clip]{./figs/split_noise.pdf}
+        \caption{Split-biased noise added to edge weights} \label{fig:ws}
     \end{subfigure}
 
-\caption{Plot of the Rand-Scores achieved by the generalized algorithm and different update rules when noise is added to the edge weights.
-Solid lines represent median values, whereas values between the 25th and the 75th percentile are shown in shade areas.}\label{fig:noise_plots}
+\caption{{\small Rand-Scores achieved by the generalized algorithm and different update rules when noise is added to the edge weights.
+Solid lines represent median values; values between the 25th and the 75th percentile are shown in shade areas.
+In the plots at the top, long-range connections are not used.}}\label{fig:noise_plots}
 \end{figure}

### 2019-05-07 chapters/1_intro.tex
Steffen comments

@@
 
-\emph{Instance segmentation} is a task of computer vision consisting in assigning each pixel of an image to an object instance. %, where the number of instances is usually not known in advance. 
-The most success in instance segmentation (IS) has been achieved by applying deep learning \cite{he2017mask,romera2016recurrent,liu2018affinity}.
-There are two main types of successful deep learning approaches to IS: proposal-based and proposal-free methods.
-Proposal-based methods consist of two steps: detecting objects, for example by finding bounding boxes, and assigning pixels to the detected instances \cite{he2017mask,dai2016instance,li2017fully}.
+\emph{Instance segmentation} is a computer vision task consisting in assigning each pixel of an image to an object instance. %, where the number of instances is usually not known in advance. 
+Most recently, success in instance segmentation (IS) has been achieved by applying deep learning and there are two main types of successful deep learning approaches to IS: proposal-based \cite{he2017mask,dai2016instance,li2017fully} and proposal-free \cite{kong2018recurrent,novotny2018semi,kulikov2018instance,kirillov2017instancecut} methods.
+Proposal-based methods consist of two steps: detecting objects, for example by finding bounding boxes, and assigning pixels to the detected instances.
 Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing}, where objects are not approximated well by bounding boxes.
 % More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)
-Thus, there is a growing interest for more efficient proposal-free methods that perform IS by directly predicting pixel features and then grouping pixels into object instances \cite{kong2018recurrent,novotny2018semi,kulikov2018instance,kirillov2017instancecut}.
+Thus, there is a growing interest for more efficient proposal-free methods that perform IS by directly predicting pixel features and then grouping pixels into object instances.
 In this work, we focus on a common proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance.

### 2019-05-07 chapters/3_algorithm.tex
Steffen comments

@@
 
-We now present a Generalized Algorithm for Signed Graphs Agglomerative Clustering (\algname) that can describe in a simple form several graph partitioning algorithms previously introduced in the literature and highlights the existence of new ones.
+We now present a Generalized Algorithm for Signed Graphs Agglomerative Clustering (\algname) that describes several graph partitioning algorithms previously introduced in the literature and highlights the existence of new ones.
 
-The proposed algorithm uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merging pairs of adjacent clusters.
+The proposed algorithm \ref{main_alg} uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merges pairs of adjacent clusters.
 Intuitively, the algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.

### 2019-05-07 chapters/1_intro.tex
Update figures; start getting rid of update rules

@@
 We evaluate the performances of these different agglomerative clustering algorithms on image instance segmentation of 2D urban scenes (CityScapes dataset) and 3D biological image stacks (CREMI neuron segmentation challenge), by comparing achieved scores, efficiency and robustness to noisy edge weights.
-\TODO{Chapters description}
+% \TODO{Chapters description}
 
@@
 \caption{
-{\small (\textbf{a}) Some iterations of the generalized algorithm on toy graphs with attractive (green) and repulsive (red) interactions.
-(\textbf{b}) Example of CREMI 2016 data \cite{cremiChallenge} overlaid with instance segmentation.
-(\textbf{c}) Agglomeration order, representing which pairs of neighboring pixels were merged first (blue) and later on (red).
-We note how similar update rules, like \emph{Sum} (in the middle) and \emph{Mean} (on the right), lead to strongly different merging orders. 
+ (\textbf{a}) Some iterations of the generalized algorithm on toy graphs with attractive (green) and repulsive (red) interactions.
+(\textbf{b}) Example of CREMI 2016 neuron-segmentation data \cite{cremiChallenge} overlaid with instance segmentation.
+(\textbf{c}) Agglomeration order, representing which pairs of neighboring pixels were merged first (white), later on (brown) or never (black).
+We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
 % On the left: a single cluster is returned with only attractive interactions.
-}
  % main ideas and contributions

### 2019-05-07 chapters/3_algorithm.tex
Update figures; start getting rid of update rules

@@
 \begin{equation}\label{eq:max_linkage}
-\interact_{S_1,S_2} = \, \max_{e\in U} \cost(e), \qquad \text{where}\quad U = \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \}.
+\interact_{S_1,S_2} = \, \max_{e\in U(S_u,S_v)} \cost(e), \qquad \text{where}\quad E_{12} = \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \}.
 \end{equation}
@@
 \centering
-        \begin{minipage}{0.49\textwidth}
+        \begin{subfigure}[t]{0.46 \textwidth}
         \centering
-        % \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
-        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
-\captionof{figure}{ 
-{\small Example of edge contraction.
-First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars).
-Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$.
-In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$.
-In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from edge contraction are replaced by single edge with updated interaction $f(\tilde{\cost}(e_{tu}), \tilde{\cost}(e_{tv}))$, see definitions in Tab.~\ref{tab:linkage-criteria}.
-}
-\label{fig:edge_contraction_and_contr_graph}  }
-    \end{minipage}\hspace{0.01\textwidth}
-    \begin{minipage}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{./figs/example_no_constr.pdf}
+        \caption{No constraints}
+    \end{subfigure} \hfill
+    \begin{subfigure}[t]{0.46 \textwidth}
         \centering
-\includegraphics[width=0.91\textwidth]{./figs/add_constraints.pdf}
-\captionof{figure}{ 
-{\small Some iterations of the generalized algorithm  with (top) and without (bottom) adding cannot-link constraints.
-The graph has both attractive (green) and repulsive (red) edges; cannot-link constraints are given by violet bars.
-At each iteration, the edge selected by the algorithm is highlighted in yellow.
-When cannot-link constraints are enforced, the final clustering is given by two clusters instead of only one.}
-\label{fig:algorithm_with_without_CLC}}
-    \end{minipage}
+        \includegraphics[width=\textwidth]{./figs/example_with_constr.pdf}
+        \caption{With constraints}
+    \end{subfigure}
+\caption{Some iterations of the generalized algorithm with and without adding cannot-link constraints.
+In this example the \emph{Sum} linkage criteria was used.
+The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges.
+We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
+\label{fig:algorithm_with_without_CLC}
 \end{figure}
-
 \begin{algorithm}[t]
@@
       % \State
-
     % \EndProcedure
-
   \end{algorithmic}
@@
     \begin{subtable}[t!]{\textwidth}\centering
-        \begin{tabular}{r  l || c | c | c}
+        \begin{tabular}{c r  l ?? c | c | c}
             % \toprule\toprule
-            \multicolumn{2}{c||}{}  &   & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
+            \multicolumn{3}{c??}{}  & \multirow{2}{*}[-0.5em]{\textbf{Unsigned Graphs}} & \multicolumn{2}{c}{\textbf{Signed Graphs}}  \\        
             % \cmidrule(l{.15em}){4-5}
             % \cline{4-5}
-            \multicolumn{2}{c||}{} & \textbf{Unsigned graphs} &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
-             &  &  &  \thead{\textsc{No}} & \thead{\textsc{Yes}} \\        
-            % \cmidrule[0.3em]{3-5}
+            % \multicolumn{2}{c||}{} &  &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
+            \multicolumn{3}{c??}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\
+
             % \midrule[0.15em]
-            \midrule\midrule
-            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} & \thead{Sum Linkage\\Hier.
+            \cmidrule[0.15em]{2-6}\morecmidrules \cmidrule[0.15em]{2-6}
+            % \midrule \midrule
+            \multirow{5}{*}[-2.5em]{\begin{turn}{90}\thead{\textbf{Linkage criteria} $\,\,\interact_{S_u ,S_v}$}\end{turn}}  & Sum: & $\displaystyle \sum_{e\in (S_u \times S_v)} \cost_e$ & \thead{Sum Linkage\\Hier.
 Aggl.
-Clust.} & \thead{Greedy Additive \\ Edge Contraction \cite{keuper2015efficient}} & \thead{Greedy Fixation\\\cite{levinkov2017comparative}} \\ \midrule
+Clust.} & \thead{Greedy Additive \\ Edge Contraction \cite{keuper2015efficient}} & \thead{Greedy Fixation\\\cite{levinkov2017comparative}} \\
+            \cmidrule[0.07em]{2-6}
 
-            \makecell[r]{Absolute \\Max:} & \thead[l]{
-            $
-            f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
-            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
-            \tilde{\cost}_2 & \text{otherwise}
-             \end{cases} 
-            $}
-               & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Mutex Watershed \\\cite{wolf2018mutex}} & \thead{Mutex Watershed\\\cite{wolf2018mutex}} \\ \midrule
-            \makecell[r]{Mean:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                                 & \thead{ Average Linkage\\ Hier.
+             &\makecell[r]{Absolute \\Max:} & 
+            $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in (S_u \times S_v)} |\cost_t|$
+               & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Mutex Watershed \\\cite{wolf2018mutex}} & \thead{Mutex Watershed\\\cite{wolf2018mutex}} \\
+              \cmidrule[0.07em]{2-6}
+             & \makecell[r]{Average:} & $\displaystyle \sum_{e\in (S_u \times S_v)} \cost_e \bigg/ \big|S_u \times S_v\big|  $ & \thead{ Average Linkage\\ Hier.
 Aggl.
@@
 Clust.
-(\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
+(\textbf{NEW})} & \thead{\textbf{NEW}}\\
+            \cmidrule[0.07em]{2-6}
+           % \midrule
 
-            Max: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Single Linkage\\Hier.
+            & Max: & $\displaystyle \max_{e\in (S_u \times S_v)} \cost_e$ & \thead{Single Linkage\\Hier.
 Aggl.
@@
 Clust.
-(\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
+(\textbf{NEW})} & \thead{\textbf{NEW}}\\
+            \cmidrule[0.07em]{2-6}
 
-            Min:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Complete Linkage\\ Hier.
+            & Min:& $\displaystyle \min_{e\in (S_u \times S_v)} \cost_e$ & \thead{Complete Linkage\\ Hier.
 Aggl.
@@
     \end{subtable} 
-    \caption{{\small The table lists the tested update rules $f$.
-Existing and new algorithms are given by a specific choice of update rule, type of graph (signed or unsigned) and optional use of cannot-link constraints.}}
+    \caption{{\small The table lists the tested linkage criteria.
+Existing and new algorithms are given by a specific choice of linkage criteria, type of graph (signed or unsigned) and optional use of cannot-link constraints.}}
     \label{tab:linkage-criteria}
 \end{table*}
+
+% \begin{table*}
+%     \centering
+%     \scriptsize
+%     \begin{subtable}[t!]{\textwidth}\centering
+%         \begin{tabular}{r  l || c | c | c}
+%             % \toprule\toprule
+%             \multicolumn{2}{c||}{}  &   & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
+%             % \cmidrule(l{.15em}){4-5}
+%             % \cline{4-5}
+%             \multicolumn{2}{c||}{} & \textbf{Unsigned graphs} &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
+%              &  &  &  \thead{\textsc{No}} & \thead{\textsc{Yes}} \\        
+%             % \cmidrule[0.3em]{3-5}
+%             % \midrule[0.15em]
+%             \midrule\midrule
+%             Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} & \thead{Sum Linkage\\Hier.
+Aggl.
+Clust.} & \thead{Greedy Additive \\ Edge Contraction \cite{keuper2015efficient}} & \thead{Greedy Fixation\\\cite{levinkov2017comparative}} \\ \midrule
+
+%             \makecell[r]{Absolute \\Max:} & \thead[l]{
+%             $
+%             f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
+%             \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
+%             \tilde{\cost}_2 & \text{otherwise}
+%              \end{cases} 
+%             $}
+%                & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Mutex Watershed \\\cite{wolf2018mutex}} & \thead{Mutex Watershed\\\cite{wolf2018mutex}} \\ \midrule
+%             \makecell[r]{Mean:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                                 & \thead{ Average Linkage\\ Hier.
+Aggl.
+Clust.
+\cite{lance1967general}} & \thead{Average Linkage\\Signed Aggl.
+Clust.
+(\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
+
+%             Max: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Single Linkage\\Hier.
+Aggl.
+Clust.
+\cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl.
+Clust.
+(\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
+
+%             Min:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Complete Linkage\\ Hier.
+Aggl.
+Clust.
+\cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl.
+Clust.
+(\textbf{NEW})} & \thead{\textbf{NEW}}
+
+%         \end{tabular}
+%         % \caption{Linkage criteria}
+%     \end{subtable} 
+%     \caption{{\small The table lists the tested update rules $f$.
+Existing and new algorithms are given by a specific choice of update rule, type of graph (signed or unsigned) and optional use of cannot-link constraints.}}
+%     \label{tab:linkage-criteria}
+% \end{table*}
 

### 2019-05-07 chapters/5_experiments_compare_rules.tex
Update figures; start getting rid of update rules

@@
 % !TEX root = ../agglo_clust_review.tex
+
+\begin{figure}[t]
+\centering
+% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
+\includegraphics[width=\textwidth]{./figs/comparison.pdf} % left bottom right top
+\caption{
+{\small Comparison of results from different update rules on signed graph with and without cannot-link constraints 
+}
+ % main ideas and contributions
+\label{fig:cremi_comparison}}
+\end{figure}
+\begin{figure}[b]
+\centering
+% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
+\includegraphics[width=\textwidth]{./figs/cityscapes_compare.pdf} % left bottom right top
+\caption{
+{\small Comparison of results from different update rules on signed graph with and without cannot-link constraints 
+}
+ % main ideas and contributions
+\label{fig:cytiscapes_comparison}}
+\end{figure}
 
@@
   \item Highlight difference of the sum in Fig. \ref{fig:intro_figure}
-  \item compare different choices of signed-cost-mappings (say which one worked best)
+  % \item compare different choices of signed-cost-mappings (say which one worked best)
   \item present cremi crop-C table and rule out single and complete linkage

### 2019-05-07 chapters/5_experiments_noise.tex
Update figures; start getting rid of update rules

@@
     \end{subfigure}
-
 \caption{{\small Rand-Scores achieved by the generalized algorithm and different update rules when noise is added to the edge weights.
@@
 
-\begin{minipage}[T!]{\textwidth}
+\begin{figure}
         \centering
-        \begin{minipage}{0.45\textwidth}
+\begin{minipage}[T]{0.48\textwidth}
+% \begin{table}
     \centering
-
-        \includegraphics[width=0.85\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
-
-    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise.
-Blue pixels represent boundary evidence.
-Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
-    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
-    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
-    }
-    \label{fig:noisy_affs}
-    \end{minipage}\hspace{0.04\textwidth}
-\begin{minipage}{0.48\textwidth}
+    % \begin{subtable}[t!]{0.5\textwidth}\centering
+        \begin{tabular}{l M{0.2\textwidth} M{0.2\textwidth}}
+        \toprule
+        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
+         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
+         & \multicolumn{1}{c}{\thead{No\\Constraints}} & \multicolumn{1}{c}{\thead{With\\constraints}} \\ \midrule
+         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
+\textbf{Mean}& \textbf{0.9292}  & 0.8647  \\
+% Lifted multicut & - & -  \\
+Abs. Max.  & 0.9246 & 0.9246 \\
+Max &   0.0611  &  0.9208  \\
+Sum  & 0.8377  & 0.8426  \\
+Min &  0.0737 & 0.0779  \\
+        \end{tabular}
+        % \caption{Linkage criteria}
+    % \end{subtable} 
+    \captionof{table}{Arand-Scores on CREMI challenge (crop of sample C) \UPDATE{for the generalized algorithm and different types of linkage criteria and the optional use of cannot-link constraints.} }
+    \label{tab:results_cremi_val}
+\end{minipage}\hfill
+\begin{minipage}[T]{0.48\textwidth}
 % \begin{table}
@@
         \toprule
-        & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
-        Update rule: & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
+        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
+         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
+         & \multicolumn{1}{c}{\thead{No\\Constraints}} & \multicolumn{1}{c}{\thead{With\\constraints}} \\ \midrule
          % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
 \textbf{Mean}& \textbf{0.343}  & 0.339  \\
-GMIS \cite{liu2018affinity} & 0.341 & -  \\
+GMIS \cite{liu2018affinity} & 0.330 & -  \\
 Max &   0.243  &   0.325  \\
-Abs. Max. \cite{wolf2018mutex}  & -  & 0.321 \\
-Sum \cite{levinkov2017comparative} & 0.313  & 0.319  \\
+Abs. Max.  & 0.321 & 0.321 \\
+Sum & 0.313  & 0.319  \\
 Min &  0.000    & 0.000  \\
@@
     % \end{subtable} 
-    \captionof{table}{AP scores on the cityscapes validation set for the generalized algorithm and different types of update rules.  }
+    \captionof{table}{AP scores on the cityscapes validation set for the generalized algorithm and different types of linkage criteria.  }
     \label{tab:results_cityscapes}
 \end{minipage}
-\end{minipage}
+\end{figure}
 

### 2019-05-07 chapters/supplementary.tex
"Finish" draft of noise exp. section
Add descr. of experimental setup
Update figures; start getting rid of update rules

@@
 
+\begin{figure}
+        \centering
+\begin{minipage}{0.45\textwidth}
+\centering
+        \includegraphics[width=0.85\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
+
+    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise.
+Blue pixels represent boundary evidence.
+Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
+    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
+    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
+    }
+    \label{fig:noisy_affs}
+    \end{minipage}\hfill
+\begin{minipage}{0.49\textwidth}
+\centering
+        % \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
+        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
+\captionof{figure}{ 
+{\small Example of edge contraction.
+First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars).
+Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$.
+In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$.
+In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from edge contraction are replaced by single edge with updated interaction $f(\tilde{\cost}(e_{tu}), \tilde{\cost}(e_{tv}))$, see definitions in Tab.~\ref{tab:linkage-criteria}.
+}
+\label{fig:edge_contraction_and_contr_graph}  }
+    \end{minipage}
+\end{figure}
+
 \section{Supplementary Material}
+\paragraph{Update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.
+% given by the linkage criterion defined in Sec.
+\ref{sec:notation} and
+An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph.
+Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that $\tilde{V} \subseteq V$ and each node $u\in \tilde{V}$ represents the cluster $S_u \in \Pi$ including $u\in V$.
+Edges in $\tilde{E}$ represent adjacency-relationships between clusters and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$.
+For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$.
+Thus, we can easily recompute these interactions by using a simple \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$.
+As an example, given the single-linkage criterion defined in Eq.
+\ref{eq:max_linkage}, the interaction between $S_u \cup S_v$ and one of its neighbors $S_t$ is simply given by:
+\begin{equation}
+  \interact_{S_u \cup S_v,S_t} = f( \interact_{S_u,S_t}, \interact_{S_v,S_t}) = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) = \max \{ \tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}) \}
+\end{equation}
+All the update rules tested in this article are listed in Table \ref{tab:linkage-criteria}.
+
 \begin{itemize}
@@
 \item Complexity: plain agglo., addition of the cannot-link constraints and then comment about efficient implementation of MWS and of single-linkage (what about single linkage+CLC...?)
+\item Noise: also mention details about plots (fix some long-range edges, fix noise seed and vary K)
+\item exp. setup details: enforcing local merges, MWS distinguish between repulsive-long, post-processing of small segments, loss, architecture, training parameters, offset patterns
+\item
+
 \end{itemize}
@@
 min & True &  & 214747429 & {\color{ForestGreen} 852 } & {\color{Red} 0.9314 } & {\color{ForestGreen} 0.202 } & {\color{Red} 4.887 } \\
+
+        \end{tabular}
+        % \caption{Linkage criteria}
+    \end{subtable} 
+    \caption{Comparison of update rules on crop of cremi sample B (sorted by multicut energy) \TODO{Reduce insane amount of numbers.
+Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime.
+Invert ARAND to make it consistent with the plots} }
+    \label{tab:results_cremi_crop_C}
+\end{table*}
+
+\begin{table*}
+    \centering
+    \begin{subtable}[t!]{0.98\textwidth}\centering
+        \begin{tabular}{c| c | c| c | c | c | c | c}
+Update rule & \makecell{Use Cannot-Link\\Constraints} & Log-costs & \makecell{Multicut objective} & Runtime (s) & ARAND & VI-merge & VI-split\\ \midrule\midrule
+mean & False &  & -102739991 & {\color{Orange} 3797 } & {\color{ForestGreen} 0.9292 } & {\color{ForestGreen} 0.286 } & {\color{ForestGreen} 0.428 } \\
+mean & False &  & -102730208 & {\color{Orange} 2562 } & {\color{ForestGreen} 0.9285 } & {\color{ForestGreen} 0.292 } & {\color{ForestGreen} 0.423 } \\
+MutexWatershed & False &  & -102313957 & {\color{ForestGreen} 830 } & {\color{ForestGreen} 0.9246 } & {\color{ForestGreen} 0.291 } & {\color{Orange} 0.471 } \\
+max & True &  & -98143342 & {\color{Red} 7153 } & {\color{ForestGreen} 0.9208 } & {\color{ForestGreen} 0.292 } & {\color{Orange} 0.496 } \\
+mean & True &  & -100279671 & {\color{Orange} 4713 } & {\color{Orange} 0.8647 } & {\color{ForestGreen} 0.265 } & {\color{Red} 0.717 } \\
+sum & True &  & -100745943 & {\color{Red} 13361 } & {\color{Orange} 0.8426 } & {\color{Orange} 0.410 } & {\color{Orange} 0.451 } \\
+sum & False &  & -101846418 & {\color{Red} 12681 } & {\color{Orange} 0.8377 } & {\color{Orange} 0.427 } & {\color{ForestGreen} 0.427 } \\
+sum & False &  & -101732952 & {\color{Red} 12287 } & {\color{Orange} 0.8376 } & {\color{Orange} 0.436 } & {\color{ForestGreen} 0.390 } \\
+sum & True &  & -101487448 & {\color{Red} 8497 } & {\color{Orange} 0.8374 } & {\color{Orange} 0.428 } & {\color{ForestGreen} 0.414 } \\
+mean & True &  & -99416111 & {\color{Orange} 3445 } & {\color{Orange} 0.8239 } & {\color{ForestGreen} 0.260 } & {\color{Red} 0.822 } \\
+min & True &  & 211183545 & {\color{ForestGreen} 692 } & {\color{Red} 0.0779 } & {\color{ForestGreen} 0.232 } & {\color{Red} 4.714 } \\
+min & False &  & 210377447 & {\color{ForestGreen} 493 } & {\color{Red} 0.0737 } & {\color{ForestGreen} 0.233 } & {\color{Red} 4.745 } \\
+max & False &  & -48601637 & {\color{ForestGreen} 102 } & {\color{Red} 0.0611 } & {\color{Red} 5.738 } & {\color{ForestGreen} 0.035 } \\
 

### 2019-05-08 chapters/1_intro.tex
Rewrite pseudocode and move contr. gr. to Appendix

@@
 
-Our main contribution is a review framework for graph clustering that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract).
-Various existing clustering algorithms, previously introduced in \cite{levinkov2017comparative,wolf2018mutex,kardoostsolving,lance1967general}, share the general procedure defined in our framework, but differ in the way in which the interaction between clusters is updated after each agglomeration step.
-Moreover, we also introduce new variations of these algorithms by allowing the possibility of enforcing mutual-exclusion relationships between clusters.
+Our first contribution is a review framework for graph clustering (Sec.
+\ref{sec:general_framework}) that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract).
+We show that various existing partitioning algorithms \cite{levinkov2017comparative,wolf2018mutex,kardoostsolving,lance1967general} can be reformulated in our framework, so that they share a general procedure but differ in the way inter-cluster interaction is updated after each iteration.
+Moreover, this framework allows us to introduce new variations of these algorithms that also enforce mutual-exclusion relationships between clusters.
 
-We evaluate the performances of these different agglomerative clustering algorithms on image instance segmentation of 2D urban scenes (CityScapes dataset) and 3D biological image stacks (CREMI neuron segmentation challenge), by comparing achieved scores, efficiency and robustness to noisy edge weights.
-% \TODO{Chapters description}
+Finally, the algorithms included in the framework are evaluated on an instance segmentation task, both on 3D biological image stacks (Sec.
+\ref{sec:neuro_segm_exp}) and 2D urban scenes (Sec.
+\ref{sec:cityscapes_exp}).
+Our analysis highlights strengths and weaknesses of each algorithm by comparing their robustness to noise, efficiency and inclination to output a well balanced graph partitioning.
 

### 2019-05-08 chapters/2_rel_work.tex
Update figures; start getting rid of update rules
Rewrite pseudocode and move contr. gr. to Appendix

@@
 
-\textbf{Edge detection} also experienced recent noticeable progress \cite{xie2015holistically,kokkinos2015pushing}.
-This is nicely illustrated by the evolution of neuron segmentation for connectomics, a field of neuroscience we also address in our experiments.
-CNNs were introduced to this application in \cite{jain2007supervised}, but further progress in deep learning and data augmentation lead to much more refined boundary detection \cite{lee2017superhuman,meirovitch2016multi,ciresan2012deep}.
+\textbf{Edge detection} also experienced recent progress thanks to deep learning, both on natural images \cite{xie2015holistically,kokkinos2015pushing} and \UPDATE{biological data \cite{lee2017superhuman,schmidt2018cell,meirovitch2016multi,ciresan2012deep}}.
+In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:
+% CNNs were introduced to this application in \cite{jain2007supervised}, but further progress in deep learning and 
+% the introduction of new architectures lead to a much more refined boundary detection. 
 % or trained an end-to-end watershed region growing algorithm \cite{wolf2017learned}.  
-Subsequent postprocessing and superpixel-merging outputs final instances.
-Some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy.
-The lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while flood-filling networks \cite{januszewski2018high} eliminate superpixels by training a recurrent CNN to perform region growing one region at the time.
+% Subsequent postprocessing and superpixel-merging outputs final instances. 
+some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while flood-filling networks \cite{januszewski2018high} eliminate superpixels by training a recurrent CNN to perform region growing one region at the time.
 A structured learning approach was also proposed in \cite{funke2018large,turaga2009maximin}.
@@
 \textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts.
-Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters; whereas the optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy.
-\TODO{Roman, Cocoons, Benjamin?}
-On the other hand, several segmentation pipelines use classical HC linkage criteria, e.g.
-average linkage \cite{liu2018affinity,lee2017superhuman} or median \cite{funke2018large}.
-The GALA algorithm in \cite{nunez2013machine,knowles2016rhoananet} features instead a linkage learned by a neural network.
+Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters.
+% \TODO{Roman, Cocoons, Benjamin?}
+The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical HC linkage criteria, e.g.
+average linkage \cite{liu2018affinity,lee2017superhuman}, median \cite{funke2018large} or a linkage learned by a neural network \cite{nunez2013machine,knowles2016rhoananet}.
 
-\textbf{Clustering of signed graphs} is another important line of research with the goal of balancing a graph with both attractive and repulsive cues.
-Finding an optimally balanced clustering has a long history in the field of combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}.
+\textbf{Clustering of signed graphs} has the goal of partitioning a graph with both attractive and repulsive cues.
+Finding an optimally balanced partitioning has a long history in combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}.
 %and can be done without the need to specify a termination criterion.
-The name \emph{correlation clustering} was coined by \cite{bansal2004correlation} that also showed its NP-hardness, while its connection with graph multicuts was made by \cite{demaine2006correlation}.
-Modern integer linear programming solvers can tackle problem instances of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy heuristic algorithms \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger problems.
-\TODO{Cannot-link constraints?}
+NP-hardness of the \emph{correlation clustering} problem was shown in \cite{bansal2004correlation}, while the connection with graph multicuts was made by \cite{demaine2006correlation}.
+Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy heuristic algorithms \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
+% \TODO{Cannot-link constraints?}
 % Missing: Funke proposals, discussion about cannot-link constraints!!!
 
-\UPDATE{This work combines the clustering algorithms proposed in \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a simple generalized framework for agglomerative clustering and evaluate them on an instance segmentation task by adopting ideas and CNN architectures from \cite{liu2018affinity,wolf2018mutex,funke2018large} to predict long-range relationships between pixels and boundary evidence between instances.}
+This work reformulates the clustering algorithms of \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a general framework and adopt ideas from the proposal-free methods \cite{liu2018affinity,wolf2018mutex,funke2018large} to predict long-range relationships between pixels.

### 2019-05-08 chapters/3_algorithm.tex
Rewrite pseudocode and move contr. gr. to Appendix

@@
 
-\section{Generalized framework for Signed Graphs Agglomerative Clustering}
-In this section we introduce the proposed framework for agglomerative clustering of signed graphs. 
+\section{Generalized framework for Signed Graphs Agglomerative Clustering} \label{sec:general_framework}
+This section introduces the proposed generalized framework: 
 %that represents a simple \UPDATE{generalized} formalization of many agglomerative graph clustering algorithms.
 \UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive node similarities and signed clustering algorithms using attractive and repulsive cues.}\\
-First, we define the graph notation in Sec.
-\ref{sec:notation}, then we introduce the generalized algorithm in Sec.
-\ref{sec:algorithm} and finally we show \UPDATE{how it can be seen as a generalization of existing and new graph clustering algorithms in Sec.
-\ref{sec:alg_update_rules}.}
+we define the graph notation in Sec.~\ref{sec:notation}, introduce Algorithm \ref{main_alg} in Sec.
+\ref{sec:algorithm} and finally show how it can be seen as a generalization of existing and new graph clustering algorithms in Sec.
+\ref{sec:alg_update_rules}.
 
@@
 We consider an undirected simple graph $\mathcal{G}(V,E)$, in which nodes can represent either pixels, superpixels or voxels.
-We call the set $\Pi$ a \emph{clustering} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $S_i \cap S_j = \emptyset$ for each $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
-In the following we denote as $S_u$ the cluster associated with node $u$.
+We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $S_i \cap S_j = \emptyset$ for each $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
+We also denote as $S_u$ the cluster associated with node $u$.
 % \begin{equation}
@@
 In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes.
-The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that several formalisms for positively weighted graphs associate to each edge a positive scalar that represents a metric or distance on the graph, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+: E \rightarrow \mathbb{R}^+$.}.
+The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms \UPDATE{REFS} for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}.
 On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters.
-Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are also often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring signed edge weights: ${\cost_e = w_e^+ - w_e^- \in \mathbb{R}, \, \forall e \in E}$.
-Graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0$ and $w^-_e=0$ for each $e \in E$.
+Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are also often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring positive and negative edge weights $\cost_e\in \mathbb{R}$.
+Following the theoretical considerations in \cite{lange2018partial}, we define these signed weights as ${\cost_e = w_e^+ - w_e^-}$.
+Some approaches directly compute $\cost_e$, whereas others compute $w_e^+$ and $w_e^-$ separately.
+In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$.
 
-\paragraph{Inter-cluster interaction}\label{par:linkage_criterion_def} We call two clusters $S_1,S_2$ \emph{adjacent} if there exists at least one edge ${e_{uv}\in E}$ connecting a node $u\in S_1$ to a node $v\in S_2$.
-In agglomerative HC, the interaction $\interact_{S_1,S_2}$ between two clusters $S_1, S_2$ is usually defined as a function, named \emph{linkage criterion}, depending on the weights of all edges connecting clusters $S_1$ and $S_2$.
-For example, for a \emph{maximum} linkage criterion statistic (single-linkage), the inter-cluster interaction is given by:
-\begin{equation}\label{eq:max_linkage}
-\interact_{S_1,S_2} = \, \max_{e\in U(S_u,S_v)} \cost(e), \qquad \text{where}\quad E_{12} = \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \}.
-\end{equation}
-Other common choices are \emph{minimum} (complete linkage) or \emph{average} (average linkage). %and \emph{sum}.
-% \begin{equation}
-%  \text{$S_1, S_2 \in \Pi$ are \emph{adjacent}} \quad \Longleftrightarrow  \quad  \mathcal{B}(S_1,S_2) \equiv \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \} \neq \emptyset
+\textbf{Inter-cluster interaction } We call two clusters $S_1,S_2$ \emph{adjacent} if there exists at least one edge ${e_{uv}\in E}$ connecting a node $u\in S_1$ to a node $v\in S_2$.
+In agglomerative HC, the interaction $\interact(S_1,S_2)$ between the two clusters is usually defined as a function, named \emph{linkage criterion}, depending on the weights of all edges connecting clusters $S_1$ and $S_2$.
+All the linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
+% For example, for a \emph{maximum} linkage criterion statistic (single-linkage), the inter-cluster interaction is given by:
+% \begin{equation}\label{eq:max_linkage}
+% \interact_{S_1,S_2} = \, \max_{e\in U(S_u,S_v)} \cost(e), \qquad \text{where}\quad E_{12} = \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \}.
 % \end{equation}
-% where we defined the set of edges connecting two adjacent clusters as \UPDATE{\emph{boundary}} \UPDATE{$\mathscr{W}(S_1,S_2) , \mathcal{G}'_{\mathcal{G},\Pi}(V',E')$}.
-in the boundary $\mathcal{B}(S_1,S_2)$.
-Some examples of linkage criterion statistics are \emph{maximum} (single-linkage), \emph{minimum} (complete-linkage) and average (average-linkage).
+% Other common choices are \emph{minimum} (complete linkage) or \emph{average} (average linkage). %and \emph{sum}.
 
-\paragraph{Multicut and correlation clustering} For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^0_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^1$ the complementary set of edges whose linked nodes belong to distinct clusters:
+\textbf{Multicut and correlation clustering } For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^{\mathrm{internal}}_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^{\mathrm{external}}$ the complementary set of edges whose linked nodes belong to distinct clusters:
 \begin{equation}
-E_\Pi^0 \equiv \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \qquad E^1_\Pi \equiv E \setminus E^0_\Pi.
+E_\Pi^{\mathrm{internal}} \equiv \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \qquad E^{\mathrm{external}}_\Pi \equiv E \setminus E^{\mathrm{internal}}_\Pi.
 \end{equation}
@@
 % \end{align}
-The set of edges $E_\Pi^1$ is known as the \emph{multicut} of $\mathcal{G}$ w.r.t.
+The set of edges $E_\Pi^{\mathrm{external}}$ is known as the \emph{multicut} of $\mathcal{G}$ w.r.t.
 clustering $\Pi$.
-The instance of the NP-hard \emph{weighted correlation clustering} or \emph{minimum cost multicut problem} w.r.t.
-$\mathcal{G}(V,E,w^+, w^-)$ \cite{kappes2011globally,chopra1991multiway,andres2015lifting} is the task of finding the clustering that optimally balance the attraction and repulsion in the graph and is given by the following optimization problem/binary integer program:
+The instance of the NP-hard \emph{weighted correlation clustering/multicut problem}
+% w.r.t. $\mathcal{G}(V,E,\cost)$ 
+corresponds to finding the partitioning that optimally balance attraction and repulsion in the graph and is given by the following binary integer program \cite{kappes2011globally,chopra1991multiway,andres2015lifting}:
 \begin{equation}
@@
  \begin{cases} 
- 1 & \text{if } e\in E^1_\Pi \\
+ 1 & \text{if } e\in E^{\mathrm{external}}_\Pi \\
  0 & \text{otherwise}.
@@
     \end{subfigure}
-\caption{Some iterations of the generalized algorithm with and without adding cannot-link constraints.
-In this example the \emph{Sum} linkage criteria was used.
+\caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints.
 The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges.
@@
   \caption{Generalized Algorithm for Signed Graphs Agglomerative Clustering}
-   \hspace*{\algorithmicindent} \textbf{Inputs:} Graph $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes; boolean variable {\color{blue}\texttt{addCannotLink}}  \\
+   \hspace*{\algorithmicindent} \textbf{Inputs:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}\texttt{addCannotLinkConstraints}}  \\
   \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$\\
@@
   \begin{algorithmic}[1]
-    % \Procedure{SignedGraphEdgeContr}{{\color{blue}bool \emph{addConstraints}}}
-      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
-      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ and contracted graph $\tilde{\mathcal{G}}_\Pi \gets \mathcal{G}$
-      \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
-      \State Sort edges in priority queue (PQ) in descending order of priority $|\cost_e|=|w^+_e - w^-_e|$ 
+      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ with each node in its own cluster
+      % \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
+      % \State Sort edges in priority queue (PQ) in descending order of absolute weight $|\cost_e|=|w^+_e - w^-_e|$ 
       \State
-      \While{PQ is \textbf{not} empty}
-        \State Pop edge $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ with highest absolute interaction $|\tilde{\cost}|$
-        \If{({\color{ForestGreen}\textbf{$\tilde{\cost} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
-          % \State PQ, $\,E_\dagger,\,\, E' \gets$ \textsc{deleteDoubleEdges}($u,v$)
-        %   \State Update costs of double edges;
-        %   \State Propagate constrained flags of double edges;
-          \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
-          \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
-            % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
-            \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
-            % \Statex \hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent} update priority of $e_1$
-            % \State Delete $e_2$ from $\mathcal{G}'$
-          \EndFor
-          % \State  Replace double edges in $\mathcal{G}'$ with single edges
-          % \Statex \hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent} and update priorities
+      \Repeat
+        \State Select pair of clusters $S_u,S_v\in\Pi$ with highest absolute interaction $|\interact{}(S_u,S_v)|$
+        % \State
+        \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ are \textbf{not} constrained\big]}
+          \State Merge cluster $S_u$ with $S_v$: update interactions and cannot-link constraints with all their neighbors
         \EndIf
         % \State
-        \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
-          % \State Flag $e_{uv}$ as MustNotLink
-          \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
+        \If{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big] \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
+          \State Constrain clusters $S_u$ and $S_v$
         \EndIf
-      \EndWhile
-      % \For{$e  \in E$ in descending order of absolute costs $|W(e)|$}
-      %   \If{({\color{ForestGreen}\textbf{$W(e) > 0$}}) \textbf{AND} (edge is not constrained)}
-      %     \State Contract edge $e$ in the graph $\mathcal{G}'$;
-      %     \State Update costs of double edges;
-      %     \State Propagate constrained flags of double edges;
-      %     % \For{every new double edge}
-      %     %   \State Delete double edges
-      %     %   \State Insert new one with updated cost
-      %     % \EndFor
+      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \big[all adjacent clusters are constrained\big]}
+        % \If{({\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
+        %   \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
+        %   \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
+        %     % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
+        %     \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
+        %   \EndFor
         % \EndIf
-      %   \If{({\color{red}\textbf{$W(e) \leq 0$}}) \textbf{AND} ({\color{blue}\emph{addConstraints}})}
-      %     \State Flag edge $e$ as constrained
+        % \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
+        %   \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
         % \EndIf
-      % \EndFor
-      % \State
+
+      \State
       \State
       \Return $\Pi$
-      % \State
-    % \EndProcedure
   \end{algorithmic}
@@
 A second variant of the proposed algorithm also introduces \emph{cannot-link constraints}, representing mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering.
-This variant (Algorithm \ref{main_alg} with \texttt{addCannotLink=True}) stops when all the remaining clusters have been previously constrained.
+This variant (Algorithm \ref{main_alg} with \texttt{addCannotLinkConstraints=True}) stops when all the remaining clusters have been previously constrained.
 % The algorithm that we will present in the next section iteratively performs a sequence of so-called \emph{edge contractions} on the original graph $\mathcal{G}(V,E,w^+, w^-)$.
@@
 
-\paragraph{Update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.
-% given by the linkage criterion defined in Sec.
-\ref{sec:notation} and
-An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph.
-Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that $\tilde{V} \subseteq V$ and each node $u\in \tilde{V}$ represents the cluster $S_u \in \Pi$ including $u\in V$.
-Edges in $\tilde{E}$ represent adjacency-relationships between clusters and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$.
-For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$.
+% For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$.
 Thus, we can easily recompute these interactions by using a simple \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$.
@@
 \ref{eq:max_linkage}, the interaction between $S_u \cup S_v$ and one of its neighbors $S_t$ is simply given by:
-\begin{equation}
-  \interact_{S_u \cup S_v,S_t} = f( \interact_{S_u,S_t}, \interact_{S_v,S_t}) = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) = \max \{ \tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}) \}
-\end{equation}
-All the update rules tested in this article are listed in Table \ref{tab:linkage-criteria}.
-% \UPDATE{Every time a pair of clusters is merged, the contracted graph is updated by performing an edge contraction and merging the associated nodes.
-The only interactions that then need to be updated are those between nodes that after the edge contraction happen to be connected by double edges (see Fig.
-\ref{fig:edge_contraction_and_contr_graph}, step b).
-For basic linkage criteria, e.g.
-\emph{max} or \emph{min}, the new interaction can be formulated in terms of an \emph{update rule} $f$ depending only on the these updates can be computed with an update rule $f$ that depends only on the interactions at the previous step }
-% As a result, the merged node could be linked to some of its neighbors by double edges .
-, representing the fact that their interaction should be updated.
-This update can be easily achieved by using an \emph{update rule} depending only on the weights of the double edges.
-% \TODO{such a mess...} ...without the need of running a loop over the edges of the original graph.
-% \UPDATE{In this way we do not need to recompute the interaction by using the linkage criterion over all the edges of the original graph, that would be computationally expensive.}
-\paragraph{The proposed edge contraction algorithm} Algorithm \ref{main_alg} then proceeds as follows, similarly to the one presented in \cite{levinkov2017comparative}.
+% \begin{equation}
+%   \interact_{S_u \cup S_v,S_t} = f( \interact_{S_u,S_t}, \interact_{S_v,S_t}) = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) = \max \{ \tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}) \}
+% \end{equation}
+% All the update rules tested in this article are listed in Table \ref{tab:linkage-criteria}.
+
+\UPDATE{\textbf{The proposed edge contraction algorithm } Algorithm \ref{main_alg} then proceeds as follows, similarly to the one presented in \cite{levinkov2017comparative}.
 It starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first.
@@
 \ref{main_alg} is \texttt{True}, then the edge $e_{uv}$ is flagged as cannot-link constraint.
-In the Supplementary material we comment on the algorithm computational complexity (Sec. \ref{sec:complexity}).
+In the Supplementary material we comment on the algorithm computational complexity (Sec. \ref{sec:complexity}).}
 
@@
             % \midrule \midrule
-            \multirow{5}{*}[-2.5em]{\begin{turn}{90}\thead{\textbf{Linkage criteria} $\,\,\interact_{S_u ,S_v}$}\end{turn}}  & Sum: & $\displaystyle \sum_{e\in (S_u \times S_v)} \cost_e$ & \thead{Sum Linkage\\Hier.
+            \multirow{5}{*}[-1.5em]{\begin{turn}{90}\thead{\textbf{Linkage criteria} $\,\,\interact(S_u ,S_v)$}\end{turn}}  & Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
 Aggl.
@@
              &\makecell[r]{Absolute \\Max:} & 
-            $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in (S_u \times S_v)} |\cost_t|$
+            $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
                & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Mutex Watershed \\\cite{wolf2018mutex}} & \thead{Mutex Watershed\\\cite{wolf2018mutex}} \\
               \cmidrule[0.07em]{2-6}
-             & \makecell[r]{Average:} & $\displaystyle \sum_{e\in (S_u \times S_v)} \cost_e \bigg/ \big|S_u \times S_v\big|  $ & \thead{ Average Linkage\\ Hier.
+             & \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier.
 Aggl.
@@
 
-            & Max: & $\displaystyle \max_{e\in (S_u \times S_v)} \cost_e$ & \thead{Single Linkage\\Hier.
+            & Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier.
 Aggl.
@@
 
-            & Min:& $\displaystyle \min_{e\in (S_u \times S_v)} \cost_e$ & \thead{Complete Linkage\\ Hier.
+            & Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier.
 Aggl.
@@
     \end{subtable} 
-    \caption{{\small The table lists the tested linkage criteria.
-Existing and new algorithms are given by a specific choice of linkage criteria, type of graph (signed or unsigned) and optional use of cannot-link constraints.}}
+    \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
+In the listed linkage criteria, we defined the set of all edges connecting cluster $S_u$ to cluster $S_v$ as $E_{uv}=(S_u \times S_v) \cap E$}
     \label{tab:linkage-criteria}
@@
  the algorithm performs a standard agglomerative HC by returning only one single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see Fig.
-\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}), where the choice of update rule determines the type of linkage (Table \ref{tab:linkage-criteria}, column 2 with unsigned graphs).
+\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} - left panel), where the choice of update rule determines the type of linkage (Table \ref{tab:linkage-criteria}, unsigned graphs).
 
-Given a graph with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was already proposed in \cite{levinkov2017comparative,keuper2015efficient} (Table \ref{tab:linkage-criteria}, sum update rule, row 1).
+Given a graph with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was already proposed in \cite{levinkov2017comparative,keuper2015efficient} (Table \ref{tab:linkage-criteria}, \emph{Sum} linkage).
 They present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms solving the multicut optimization problem.
 
-Mutex Watershed \cite{wolf2018mutex}, another algorithm for signed graphs, also introduces dynamical cannot-link constraints.
-In supplementary material (Sec.
-\ref{sec:equivalence_MWS}) we show how it can be seen as an efficient implementation of \algname{} with the \emph{abs-max} update rule (see Tab.
-\ref{tab:linkage-criteria}) and observe that in this case \algname{} returns the same clustering with or without enforcing cannot-link constraints.
+The Mutex Watershed \cite{wolf2018mutex}, another algorithm for signed graph partitioning, also introduces dynamical cannot-link constraints.
+In the supplementary material (Sec.
+\ref{sec:equivalence_MWS}) we show how it can be seen as an efficient implementation of \algname{} with the \emph{Absolute maximum} linkage defined in Table \ref{tab:linkage-criteria} and observe that in this case \algname{} returns the same clustering with or without enforcing cannot-link constraints.
 
-On the other hand, new variations of \algname{} that, to our knowledge, were never mentioned in the literature are showed in Tab.
-\ref{tab:linkage-criteria} by using signed graphs and update rules \emph{mean}, \emph{max} or \emph{min}.
+On the other hand, to our knowledge, the presented agglomerative algorithm with \emph{Average}, \emph{Max} or \emph{Min} linkage was never applied to signed graphs or combined with cannot-link constraints, thus we decided to test all these new variations.
 
-In this work we compare the algorithms listed in Table \ref{tab:linkage-criteria}, which represent the most common options. 
-Nevertheless, more elaborated options exist: \cite{nunez2013machine} proposes a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas
-\cite{funke2018large} uses a \emph{quantile} update rule by populating a histogram for each inter-cluster interaction.
+\UPDATE{Additional types of linkage criteria were proposed in the literature}:
+\cite{nunez2013machine} for example proposed a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas
+\cite{funke2018large} uses a \emph{quantile} linkage criteria by populating a histogram for each inter-cluster interaction.
+\UPDATE{To our knowledge, the linkage criteria listed in Table \ref{tab:linkage-criteria} represent the most used ones, thus we include them in our experimental comparison presented in the next chapters.}

### 2019-05-08 chapters/5_experiments_cityscapes.tex
Rewrite pseudocode and move contr. gr. to Appendix

@@
 % !TEX root = ../agglo_clust_review.tex
-\section{Experiments on CityScapes}
+\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
 A successful proposal-free method was recently presented in \cite{liu2018affinity} and a setup equivalent to the one described in Sec.

### 2019-05-08 chapters/5_experiments_intro.tex
Update images and update minor details
Rewrite pseudocode and move contr. gr. to Appendix

@@
 % !TEX root = ../agglo_clust_review.tex
-\section{Experiments on neuron segmentation}
+\section{Experiments on neuron segmentation}\label{sec:neuro_segm_exp}
 
@@
 
-The output of the CNN can be represented as a \emph{weighted 3D grid graph}, such that each node represents a pixel/voxel of the volume image.
+The output of the CNN can be represented as a weighted 3D grid graph, such that each node represents a pixel/voxel of the volume image.
 Each node is connected to its neighbors by $m_{\mathrm{direct}}$ edges ($E_{\mathrm{direct}}$) and $m_{\mathrm{long}}$ long-range ones ($E_{\mathrm{long}}$).

### 2019-05-08 chapters/supplementary.tex
Rewrite pseudocode and move contr. gr. to Appendix

@@
 \section{Supplementary Material}
+During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.  % given by the linkage criterion defined in Sec. \ref{sec:notation} and
+Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, with $\tilde{V} \subseteq V$ such that node $u\in \tilde{V}$ represents the associated cluster $S_u \in \Pi$.
+Edges in $\tilde{E}$ are defined by adjacency-relationships between clusters and edge weights $\tilde{\cost}_{uv}$ represent inter-cluster interactions $\interact(S_u,S_v)$.
+
 \paragraph{Update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.
@@
 All the update rules tested in this article are listed in Table \ref{tab:linkage-criteria}.
+
+% \UPDATE{Every time a pair of clusters is merged, the contracted graph is updated by performing an edge contraction and merging the associated nodes.
+The only interactions that then need to be updated are those between nodes that after the edge contraction happen to be connected by double edges (see Fig.
+\ref{fig:edge_contraction_and_contr_graph}, step b).
+For basic linkage criteria, e.g.
+\emph{max} or \emph{min}, the new interaction can be formulated in terms of an \emph{update rule} $f$ depending only on the these updates can be computed with an update rule $f$ that depends only on the interactions at the previous step }
+% As a result, the merged node could be linked to some of its neighbors by double edges .
+, representing the fact that their interaction should be updated.
+This update can be easily achieved by using an \emph{update rule} depending only on the weights of the double edges.
+% \TODO{such a mess...} ...without the need of running a loop over the edges of the original graph.
+% \UPDATE{In this way we do not need to recompute the interaction by using the linkage criterion over all the edges of the original graph, that would be computationally expensive.}
+\textbf{The proposed edge contraction algorithm } Algorithm \ref{main_alg} then proceeds as follows, similarly to the one presented in \cite{levinkov2017comparative}.
+It starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first.
+It then iteratively pops one edge $e_{uv}$ from PQ and, depending on the priority $\tilde{\cost}$, does the following: in case of attractive interaction $\tilde{\cost}>0$, provided that $e_{uv}$ was not flagged as a cannot-link constraint, then merge the connected clusters, perform an edge contraction of $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and update the priorities of new double edges as explained in Fig.
+\ref{fig:edge_contraction_and_contr_graph}.
+% For every new pair of double edges in $\tilde{\mathcal{G}}_\Pi$, update their priorities according to one of the update rules listed in Table \ref{tab:linkage-criteria} together with their cannot-link relationships.
+If, on the other hand, the interaction is repulsive ($\tilde{\cost}\leq 0$) and the option \texttt{addCannotLink} of Alg.
+\ref{main_alg} is \texttt{True}, then the edge $e_{uv}$ is flagged as cannot-link constraint.
+In the Supplementary material we comment on the algorithm computational complexity (Sec. \ref{sec:complexity}).
 
@@
 
+\begin{algorithm}[t]
+  \caption{Generalized Algorithm for Signed Graphs Agglomerative Clustering}
+   \hspace*{\algorithmicindent} \textbf{Inputs:} Graph $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes; boolean variable {\color{blue}\texttt{addCannotLink}}  \\
+  \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$\\
+  \hspace*{\algorithmicindent} 
+  \begin{algorithmic}[1]
+      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ and contracted graph $\tilde{\mathcal{G}}_\Pi \gets \mathcal{G}$
+      \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
+      \State Sort edges in priority queue (PQ) in descending order of priority $|\cost_e|=|w^+_e - w^-_e|$ 
+      \State
+      \While{PQ is \textbf{not} empty}
+        \State Pop edge $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ with highest absolute interaction $|\tilde{\cost}|$
+        \If{({\color{ForestGreen}\textbf{$\tilde{\cost} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
+          \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
+          \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
+            % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
+            \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
+          \EndFor
+        \EndIf
+        \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
+          \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
+        \EndIf
+      \EndWhile
+      \State
+      \Return $\Pi$
+  \end{algorithmic}
+  \label{main_alg_suppl}
+\end{algorithm}
+
 \begin{algorithm}

### 2019-05-08 chapters/3_algorithm.tex
Adapt algorithm description to new pseudocode

@@
         \includegraphics[width=\textwidth]{./figs/example_no_constr.pdf}
-        \caption{No constraints}
+        \caption{No constraints}\label{subfig:no_constraints}
     \end{subfigure} \hfill
@@
         \includegraphics[width=\textwidth]{./figs/example_with_constr.pdf}
-        \caption{With constraints}
+        \caption{With constraints}\label{subfig:with_constraints}
     \end{subfigure}
@@
       \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ with each node in its own cluster
+      \State Initial interactions between nodes given by $\cost_e = w^+_e - w^-_e$
       % \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
@@
 
-\subsection{Generalized Algorithm for Signed Graphs Agglomerative Clustering} \label{sec:algorithm}
+\subsection{Generalized Algorithm for Signed Graphs Agglomerative Clustering (\algname)} \label{sec:algorithm}
 
-We now present a Generalized Algorithm for Signed Graphs Agglomerative Clustering (\algname) that describes several graph partitioning algorithms previously introduced in the literature and highlights the existence of new ones.
+The proposed Algorithm \ref{main_alg} uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merges pairs of adjacent clusters.
+It starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
+\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}).
+After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.
 
-The proposed algorithm \ref{main_alg} uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merges pairs of adjacent clusters.
-Intuitively, the algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
-\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}b} and \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}c}).
-
-A second variant of the proposed algorithm also introduces \emph{cannot-link constraints}, representing mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering.
-This variant (Algorithm \ref{main_alg} with \texttt{addCannotLinkConstraints=True}) stops when all the remaining clusters have been previously constrained.
+A second variant of Algorithm \ref{main_alg}, with option \texttt{addCannotLinkConstraints=True}, introduces \emph{cannot-link constraints}, which represent mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering.
+This variant
+select the pair of clusters with the highest absolute interaction $|\interact(S_u, S_v)|$, so that the most attractive and the most repulsive pairs are analyzed first (see example in Fig.
+\ref{subfig:with_constraints}).
+If the interaction is repulsive, then the two clusters are constrained.
+If it is attractive, then they are merged, provided that they were not already previously constrained.
+The algorithm stops when all the remaining clusters are constrained.
 % The algorithm that we will present in the next section iteratively performs a sequence of so-called \emph{edge contractions} on the original graph $\mathcal{G}(V,E,w^+, w^-)$.
@@
 During the agglomeration, the current clustering $\Pi$ is represented by a \emph{contracted graph} $\mathcal{G'}(\mathcal{G}, \Pi)$, such that each of its nodes represents a cluster $S \in \Pi$ and \emph{adjacent} clusters are linked by an edge.
-
 % For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$.
@@
 
-\UPDATE{\textbf{The proposed edge contraction algorithm } Algorithm \ref{main_alg} then proceeds as follows, similarly to the one presented in \cite{levinkov2017comparative}.
+In the Supplementary material we comment on the algorithm \UPDATE{computational complexity $\mathcal{O}(?)$} and present an efficient implementation based on an edge contraction algorithm combined with a priority queue (Sec.
+\ref{sec:complexity}).
+
+% \UPDATE{\textbf{The proposed edge contraction algorithm } Algorithm \ref{main_alg} then proceeds as follows, similarly to the one presented in \cite{levinkov2017comparative}.
 It starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first.
@@
 \ref{fig:edge_contraction_and_contr_graph}.
-% For every new pair of double edges in $\tilde{\mathcal{G}}_\Pi$, update their priorities according to one of the update rules listed in Table \ref{tab:linkage-criteria} together with their cannot-link relationships.
-If, on the other hand, the interaction is repulsive ($\tilde{\cost}\leq 0$) and the option \texttt{addCannotLink} of Alg.
+% % For every new pair of double edges in $\tilde{\mathcal{G}}_\Pi$, update their priorities according to one of the update rules listed in Table \ref{tab:linkage-criteria} together with their cannot-link relationships.
+% If, on the other hand, the interaction is repulsive ($\tilde{\cost}\leq 0$) and the option \texttt{addCannotLink} of Alg.
 \ref{main_alg} is \texttt{True}, then the edge $e_{uv}$ is flagged as cannot-link constraint.
-In the Supplementary material we comment on the algorithm computational complexity (Sec. \ref{sec:complexity}).}
+% In the Supplementary material we comment on the algorithm computational complexity (Sec. \ref{sec:complexity}).}
 
@@
     \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
-In the listed linkage criteria, we defined the set of all edges connecting cluster $S_u$ to cluster $S_v$ as $E_{uv}=(S_u \times S_v) \cap E$}
+The set $E_{uv}$ of all edges connecting cluster $S_u$ to cluster $S_v$ is defined as $E_{uv}=(S_u \times S_v) \cap E$.}
     \label{tab:linkage-criteria}
@@
 
-\UPDATE{Additional types of linkage criteria were proposed in the literature}:
+Apart from the linkage criteria defined in Table \ref{tab:linkage-criteria}, additional ones were proposed in the literature:
 \cite{nunez2013machine} for example proposed a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas
 \cite{funke2018large} uses a \emph{quantile} linkage criteria by populating a histogram for each inter-cluster interaction.
-\UPDATE{To our knowledge, the linkage criteria listed in Table \ref{tab:linkage-criteria} represent the most used ones, thus we include them in our experimental comparison presented in the next chapters.}
+In the next chapters, our experiments focus on the linkage criteria listed in Table \ref{tab:linkage-criteria}, since they represent the most used ones.

### 2019-05-08 chapters/5_experiments_intro.tex
Adapt algorithm description to new pseudocode

@@
 In our experiments we evaluate how beneficial long-range connections are for the final segmentation and we add them to the graph with a given probability $p_{\mathrm{long}}$ (if $p_{\mathrm{long}}=0$, then $E_{\mathrm{long}}=\emptyset$).
-The post-processing presented in \cite{lee2017superhuman} did not use any predicted long-range connection, whereas \cite{wolf2018mutex} introduced them with strides of 2 in the XY-plane.
+We note that the post-processing presented in \cite{lee2017superhuman} did not use any predicted long-range connection, whereas \cite{wolf2018mutex} introduced them with strides of 2 in the XY-plane.
 
@@
 where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation.
-We evaluated both of them empirically with each of the tested update rules and found that the additive mapping is the best option in all cases apart from the sum update rule.
+We evaluated both of them empirically with each of the tested update rules and found that the additive mapping is the best option in all cases apart from the \emph{Sum} linkage.

### 2019-05-09 chapters/3_algorithm.tex
Update noise plots

@@
 
-\section{Generalized framework for Signed Graphs Agglomerative Clustering} \label{sec:general_framework}
+\section{Generalized framework for Signed Graph Agglomerative Clustering} \label{sec:general_framework}
 This section introduces the proposed generalized framework: 
@@
 \begin{algorithm}[t]
-  \caption{Generalized Algorithm for Signed Graphs Agglomerative Clustering}
-   \hspace*{\algorithmicindent} \textbf{Inputs:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}\texttt{addCannotLinkConstraints}}  \\
-  \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$\\
+  \caption{\algname{}: Generalized Algorithm for Signed Graph Agglomerative Clustering}
+   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}\texttt{addCannotLinkConstraints}}  \\
+  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
   \hspace*{\algorithmicindent} 
@@
       % \State Sort edges in priority queue (PQ) in descending order of absolute weight $|\cost_e|=|w^+_e - w^-_e|$ 
-      \State
+      % \State
       \Repeat
@@
         \If{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big] \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
-          \State Constrain clusters $S_u$ and $S_v$
+          \State Add CannotLink Constraint between clusters $S_u$ and $S_v$
         \EndIf
@@
 
-      \State
+      % \State
       \State
@@
 
-\subsection{Generalized Algorithm for Signed Graphs Agglomerative Clustering (\algname)} \label{sec:algorithm}
+\subsection{\algname{}: Generalized Algorithm for Signed Graph Agglomerative Clustering} \label{sec:algorithm}
 
-The proposed Algorithm \ref{main_alg} uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merges pairs of adjacent clusters.
+The proposed \algname{} Algorithm \ref{main_alg} uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merges pairs of adjacent clusters.
 It starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
@@
     \end{subtable} 
-    \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
+    \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm \algname{}, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
 The set $E_{uv}$ of all edges connecting cluster $S_u$ to cluster $S_v$ is defined as $E_{uv}=(S_u \times S_v) \cap E$.}
@@
 
-\subsection{Different update rules: new and existing algorithms} \label{sec:alg_update_rules}
+\subsection{\algname{} with different linkage criteria: new and existing algorithms} \label{sec:alg_update_rules}
 %In this section, we show how the choice of different update rules for the presented generalized algorithm \algname{} leads to existing and new algorithms (see Table \ref{tab:linkage-criteria}).
@@
 
-On the other hand, to our knowledge, the presented agglomerative algorithm with \emph{Average}, \emph{Max} or \emph{Min} linkage was never applied to signed graphs or combined with cannot-link constraints, thus we decided to test all these new variations.
+On the other hand, to our knowledge, the presented agglomerative algorithm with \emph{Average}, \emph{Max} or \emph{Min} linkage was never applied to signed graphs or combined with cannot-link constraints, \UPDATE{thus we decided to test all these new variations.}
 

### 2019-05-09 chapters/5_experiments_intro.tex
Update noise plots

@@
 where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation.
-We evaluated both of them empirically with each of the tested update rules and found that the additive mapping is the best option in all cases apart from the \emph{Sum} linkage.
+We evaluated both of them empirically with each of the tested linkage and found that the additive mapping is the best option in all cases apart from the \emph{Sum} linkage.

### 2019-05-09 chapters/5_experiments_noise.tex
Adapt algorithm description to new pseudocode
Update noise plots

@@
         \centering
-        \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise.pdf}
+        \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}
 
-        \caption{Merge-biased noise added to edge weights} \label{fig:thresh}
-    \end{subfigure}%
+        \caption{Direct neighbor connections ($p_{\mathrm{long}}=0$)} \label{fig:merge_noise_only_direct}
+    \end{subfigure} \hfill
     \begin{subfigure}[t]{0.49 \textwidth}
         \centering
-        \includegraphics[width=\textwidth,trim=0.53in 0.35in 0.65in 0.80in,clip]{./figs/split_noise.pdf}
-        \caption{Split-biased noise added to edge weights} \label{fig:ws}
+        \includegraphics[width=\textwidth,trim=0.53in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_long_range.pdf}
+        \caption{With long-range connections ($p_{\mathrm{long}}=0.1$)} \label{fig:merge_noise_with_long_range}
     \end{subfigure}
-\caption{{\small Rand-Scores achieved by the generalized algorithm and different update rules when noise is added to the edge weights.
+\caption{\UPDATE{Rand-Scores achieved by the generalized algorithm and different update rules when noise is added to the edge weights.
 Solid lines represent median values; values between the 25th and the 75th percentile are shown in shade areas.
@@
 \subsection{Different update rules and robustness to noise}
- In this section we evaluate the robustness of \algname{} with different update rules by adding noise to the edge weights.
+ In this section we evaluate the robustness of \algname{} with different linkage criteria by adding noise to the edge weights.
   %Before to present the results shown in Fig. \ref{fig:noise_plots}, we will first introduce the type of noise that was added to the edge weights.
@@
 \ref{fig:noise_plots} represent the scores achieved by \algname{} with different update rules depending on the amount of noise $\mathcal{K}$ added to the edge weights and the probability $p_{\mathrm{long}}$ of long-range connections in the graph.
-Results clearly show that adding long-range edges is always beneficial for final segmentation.
+Results clearly show that adding long-range edges is always beneficial for the final segmentation \TODO{Not True!}.
 \TODO{What about time?} The most robust version of update rule proved to be the \emph{mean}, that achieves similar scores even with significantly noisy edge weights.

### 2019-05-09 chapters/5_experiments_noise.tex
Update and move figures

@@
 
-The plots in Fig.
+\UPDATE{The plots in Fig.
 \ref{fig:noise_plots} represent the scores achieved by \algname{} with different update rules depending on the amount of noise $\mathcal{K}$ added to the edge weights and the probability $p_{\mathrm{long}}$ of long-range connections in the graph.
@@
 \TODO{Comment about MC energy}
-On the other hand, \algname{} with \emph{mean} update rule and cannot-link constraints did not achieve high scores because of the strong over-segmentation error.
+On the other hand, \algname{} with \emph{mean} update rule and cannot-link constraints did not achieve high scores because of the strong over-segmentation error.}
 %Nevertheless, these additional experiments show that it provides an \UPDATE{almost true over-segmentation of the ground truth segmentation even with strongly merge-biased predictions}.
@@
 \end{figure}
+\begin{figure}[b]
+\centering
+% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
+\includegraphics[width=\textwidth]{./figs/cityscapes_compare.pdf} % left bottom right top
+\caption{
+\UPDATE{Comparison of results from different update rules on signed graph with and without cannot-link constraints}
+ \label{fig:cytiscapes_comparison}}
+\end{figure}
 

### 2019-05-10 chapters/1_intro.tex
Update exp. sec. and NeurIPS 2019

@@
 % More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)
-Thus, there is a growing interest for more efficient proposal-free methods that perform IS by directly predicting pixel features and then grouping pixels into object instances.
+Thus, there is a growing interest for more efficient proposal-free methods that perform IS by directly predicting \UPDATE{pixel features} and then grouping pixels into object instances.
 In this work, we focus on a common proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance.
-Recently, this approach was successfully applied both to neuron segmentation of 3D EM image stacks \cite{lee2017superhuman,wolf2018mutex} and instance segmentation of 2D urban scenes \cite{liu2018affinity}, where it achieved performances comparable to proposal-based methods.
+Recently, this approach was successfully applied both to neuron segmentation of 3D EM image stacks \cite{lee2017superhuman,wolf2018mutex} and instance segmentation of 2D urban scenes \cite{liu2018affinity}, where it achieved performances superior and comparable, respectively, to proposal-based methods.
 
@@
 These methods require the user to specify the desired numbers of segments or a termination criterion (as in spectral clustering or iterated normalized cuts) or even a stronger version of supervision in terms of seeds (as in seeded watershed or random walker).
-Hierarchical clustering (HC) is also a popular method, which creates an hierarchy of clusters.
+Hierarchical clustering (HC) is also a popular method, which creates a hierarchy of clusters.
 Agglomerative HC is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}.

### 2019-05-10 chapters/3_algorithm.tex
Update exp. sec. and NeurIPS 2019

@@
 
-We consider an undirected simple graph $\mathcal{G}(V,E)$, in which nodes can represent either pixels, superpixels or voxels.
+We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$, in which nodes can represent either pixels, superpixels or voxels.
 We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $S_i \cap S_j = \emptyset$ for each $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
@@
 % \end{equation}
-
-In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes.
+% In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. 
 The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms \UPDATE{REFS} for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}.
@@
 \textbf{Inter-cluster interaction } We call two clusters $S_1,S_2$ \emph{adjacent} if there exists at least one edge ${e_{uv}\in E}$ connecting a node $u\in S_1$ to a node $v\in S_2$.
-In agglomerative HC, the interaction $\interact(S_1,S_2)$ between the two clusters is usually defined as a function, named \emph{linkage criterion}, depending on the weights of all edges connecting clusters $S_1$ and $S_2$.
+In agglomerative HC, the interaction $\interact(S_1,S_2)$ between the two clusters is usually defined as a function, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S_1$ and $S_2$.
 All the linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
@@
 
-\textbf{Multicut and correlation clustering } For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^{\mathrm{internal}}_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^{\mathrm{external}}$ the complementary set of edges whose linked nodes belong to distinct clusters:
+\textbf{Multicut and correlation clustering } For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^{\mathrm{internal}}_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^{\mathrm{external}}$ the complementary set of edges whose incident nodes belong to distinct clusters:
 \begin{equation}
@@
 \end{equation}
-In the next chapters we will use this objective as a way to measure how much a clustering is balanced.
+In the next chapters we will use this objective as measure of how balanced a clustering is.
 

### 2019-05-10 chapters/5_experiments_compare_rules.tex
Rewrite pseudocode and move contr. gr. to Appendix
Update and move figures
Update exp. sec. and NeurIPS 2019

--- 2019-03-27 chapters/5_experiments_compare_rules.tex
@@
 
-% \begin{figure}
-% \centering
-%         \begin{subfigure}[t]{0.46 \linewidth}
-%         \centering
-%         \includegraphics[width=0.98\textwidth]{figs/comparison/sum_F.pdf}
-%         % \caption{Thresholding of local boundary maps ~(THRESH)} \label{fig:thresh}
-%     \end{subfigure}%
-%     \begin{subfigure}[t]{0.46 \linewidth}
-%         \centering
-%         \includegraphics[width=0.98\textwidth]{figs/comparison/sum_T.pdf}
-%         % \caption{Watershed, seeded at local minima of the smoothed input map~(WS)} \label{fig:ws}
-%     \end{subfigure}\hspace{0.5cm}%
+\begin{figure}[t]
+\centering
+% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
+\includegraphics[width=\textwidth]{./figs/comparison.pdf} % left bottom right top
+\caption{\algname{} with different linkage criteria on some difficult parts of the CREMI Challenge \cite{cremiChallenge} training data.
+Red arrows point to wrongly split regions.
+Yellow arrows point out merge errors.
+Green arrows indicate challenging, but correctly segmented regions.
+% Only the involved segments are colored.
+ % main ideas and contributions
+\label{fig:cremi_comparison}}
+\end{figure}
+\begin{figure}
+        \centering
+\begin{minipage}[T]{0.48\textwidth}
+% \begin{table}
+    \centering
+    \scriptsize
+    % \begin{subtable}[t!]{0.5\textwidth}\centering
+        \begin{tabular}{l|l|c|c}
+        % \toprule
+        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
+         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
+         & \algname{} Linkage & \makecell{Arand\\Score} & VI-Score \\ \midrule
+         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
+DTWS + LMC \cite{beier2016efficient}& -& & \\
+DTWS + avgHC &-& & \\
+DTWS  & -& & \\
+THRESH &-& & \\ \hline
+\algname{} & Average& & \\
+Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & & \\
+GAEC \cite{keuper2015efficient} & Sum & & \\
+Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr.  & & \\
+        \end{tabular}
+    \captionof{table}{Arand-Scores and VI-Scores on CREMI challenge training data}
+    \label{tab:results_cremi_train}
+\end{minipage}\hfill
+\begin{minipage}[T]{0.48\textwidth}
+    \centering
+    \scriptsize
+        \begin{tabular}{l|c|c}
+         & \makecell{CREMI \\Score} & \makecell{Arand\\Score} \\ \midrule
+Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
+PNI-UNet & 0.228 & 0.116 \\
+Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
+MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
+CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
+LFC \cite{parag2017anisotropic} & 0.616 & \\
+        \end{tabular}
+    \captionof{table}{\UPDATE{TBD:} Scores on test data}
+    \label{tab:results_cremi_test}
+\end{minipage}
+\end{figure}
 
-%     % \vspace{0.3cm}
-%     \begin{subfigure}[t]{0.92 \linewidth}
-%         \centering
-%         \includegraphics[width=1.\textwidth]{figs/comparison/MWS.pdf}
-%         % \caption{Multicut partitioning based segmentation~(MC-FULL)} \label{fig:mc_full}
-%     \end{subfigure}\hspace{0.5cm}
+\subsection{CREMI Challenge} \label{sec:exp_first_comparison}
+We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available.
+The dataset comes from a serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present available training ground truth.
+The results submitted to the leaderboard are evaluated using the CREMI score\footnote{\url{https://cremi.org/leaderboard/}}, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score\cite{arganda2015crowdsourcing}.
+The data is highly anisotropic and contains artifacts like missing sections, staining precipitations and support film folds.
 
-%     \begin{subfigure}[t]{0.46 \linewidth}
-%         \centering
-%         \includegraphics[width=0.98\textwidth]{figs/comparison/mean_F.pdf}
-%         % \caption{Thresholding of local boundary maps ~(THRESH)} \label{fig:thresh}
-%     \end{subfigure}%
-%     \begin{subfigure}[t]{0.46 \linewidth}
-%         \centering
-%         \includegraphics[width=0.98\textwidth]{figs/comparison/mean_T.pdf}
-%         % \caption{Watershed, seeded at local minima of the smoothed input map~(WS)} \label{fig:ws}
-%     \end{subfigure}\hspace{0.5cm}%
+\textbf{Training } We pre-aligned the training and test data with an elastic alignment method \cite{saalfeld2012elastic}.
+We further simulated low contrast sections...
+and missing sections by setting their intensity value to zero...
+We used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d} trained with L1 loss (Adam optimizer with learning rate...).
 
-% \begin{subfigure}[t]{0.46 \linewidth}
-%         \centering
-%         \includegraphics[width=0.98\textwidth]{figs/comparison/max_F.pdf}
-%         % \caption{Thresholding of local boundary maps ~(THRESH)} \label{fig:thresh}
-%     \end{subfigure}%
-%     \begin{subfigure}[t]{0.46 \linewidth}
-%         \centering
-%         \includegraphics[width=0.98\textwidth]{figs/comparison/max_T.pdf}
-%         % \caption{Watershed, seeded at local minima of the smoothed input map~(WS)} \label{fig:ws}
-%     \end{subfigure}\hspace{0.5cm}%
+\textbf{Additional methods tested }  We compare the performances of the algorithms in our framework with other basic and state-of-the-art post-processing methods.
+To ensure a fair comparison, we test all methods on the same predictions of our CNN model.
+As baseline methods, we consider a simple thresholding (THRESH) and a watershed algorithm seeded at the maxima of a boundary distance transform (WSDT).
+For these baselines, affinities are converted to a boundary map \UPDATE{by taking a weighted average over short- and long-range edge connections}.
+Other state-of-the-art neuron-segmentation multi-step-pipelines first find 2D superpixels using WSDT and then apply a graph partitioning algorithm: in our comparison, we include one pipeline using agglomerative HC with average linkage (avgHC) and one using an approximation of the Lifted Multicut Problem (LMC) \cite{beier2016efficient}.
 
-% \begin{subfigure}[t]{0.46 \linewidth}
-%         \centering
-%         \includegraphics[width=0.98\textwidth]{figs/comparison/min_F.pdf}
-%         % \caption{Thresholding of local boundary maps ~(THRESH)} \label{fig:thresh}
-%     \end{subfigure}%
-%     \begin{subfigure}[t]{0.46 \linewidth}
-%         \centering
-%         \includegraphics[width=0.98\textwidth]{figs/comparison/min_T.pdf}
-%         % \caption{Watershed, seeded at local minima of the smoothed input map~(WS)} \label{fig:ws}
-%     \end{subfigure}\hspace{0.5cm}%
-
-%     % \vspace{-0.4cm}
-%     \caption{Comparison of results from different update rules on signed graph with and without cannot-link constraints \TODO{add arrows/circles highlighting merge/split mistakes and correct decisions.
-Align; add captions}}
-%     \label{fig:isbi-examples}
-% \end{figure}% \captionsetup[
-
-\subsection{Comparison of update rules} \label{sec:exp_first_comparison}
-\begin{itemize}
-  \item Highlight difference of the sum in Fig. \ref{fig:intro_figure}
-  \item compare different choices of signed-cost-mappings (say which one worked best)
-  \item present cremi crop-C table and rule out single and complete linkage
-\end{itemize}
+\textbf{Comparison results } Among all the signed graph algorithms included in our generalized framework, the less-known one with \emph{Average} linkage consistently outperformed all other previously proposed linkage like \emph{Sum} or \emph{Absolute Max}
+(see Table \ref{tab:results_cremi_train}).
+This method also achieved \UPDATE{comparable} scores to other complex multi-step pipelines that usually require the user to tune several hyper-parameters.
+The performances of all linkage criteria listed in Table \ref{tab:linkage-criteria} are summarized in Table \ref{tab:cremi_train_full} in Appendix and in Fig.
+\ref{fig:cremi_comparison}, where we highlight some of the major mistakes...

### 2019-05-10 chapters/5_experiments_intro.tex
Update and move figures
Update exp. sec. and NeurIPS 2019

@@
 % !TEX root = ../agglo_clust_review.tex
+
 \section{Experiments on neuron segmentation}\label{sec:neuro_segm_exp}
@@
 \subsection{Experimental setup: pixel grid-graph with long-range connections} \label{sec:grid_graph}
-EM segmentation is commonly performed by first predicting which pixels belong to a cell membrane using a CNN.
+EM segmentation is commonly performed by first predicting 
+% which pixels belong to a cell membrane using a CNN.
 As described in Sec.
 \ref{sec:related_work}, different postprocessing methods are then used to obtain a segmentation.
-The CNN can either be trained to predict boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pixel and one of its neighbors to belong to the same neuron segment.
+The CNN can either be trained to predict
+boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment.
 The affinities do not have to be limited to direct neighboring pixels, in fact, \cite{lee2017superhuman} have shown that using long-range affinities is beneficial for the training of the CNN. 
-Similarly to \cite{wolf2018mutex}, we then train a CNN to predict short- and long-range affinities and use them as input weights for \algname{}.
-The output layer of the CNN will then have $m_{\mathrm{direct}}+m_{\mathrm{long}}$ channels, where $m_{\mathrm{direct}}=6$ represents the direct neighbors in 3D and $m_{\mathrm{long}}$ is the number of long-range ones.
-In the Supplementary material (Sec.
-\ref{sec:training_details}) we provide more details on the chosen neighborhood structure, data augmentation and the training with L1 loss of the used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d}.
+Thus, we train a CNN to predict both short- and long-range affinities
+and use them as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image. 
+% In our experiments, we divided the set of edges $E$ in $E_{\mathrm{direct}}$ connecting direct neighboring voxels and $E_{\mathrm{long}}$. 
+In the Supplementary material (Sec. \ref{sec:training_details}) we provide more details on the chosen neighborhood structure.
+% , data augmentation and the training with L1 loss of the used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d}.
+% We evaluate how beneficial long-range connections are by adding 
+% The output layer of the CNN will then have $m_{\mathrm{direct}}+m_{\mathrm{long}}$ channels, where $m_{\mathrm{direct}}=6$ represents the direct neighbors in 3D and $m_{\mathrm{long}}$ is the number of long-range ones.
+% The output of the CNN can be represented as a weighted 3D grid graph, such that each node represents a pixel/voxel of the volume image.
+Each node is connected to its neighbors by $m_{\mathrm{direct}}$ edges ($E_{\mathrm{direct}}$) and $m_{\mathrm{long}}$ long-range ones ($E_{\mathrm{long}}$).
+% In our experiments we evaluate how beneficial long-range connections are for the final segmentation and we add them to the graph with a given probability $p_{\mathrm{long}}$ (if $p_{\mathrm{long}}=0$, then $E_{\mathrm{long}}=\emptyset$).
+% We note that the post-processing presented in \cite{lee2017superhuman} did not use any predicted long-range connection, whereas \cite{wolf2018mutex} introduced them with strides of 2 in the XY-plane.
 
-The output of the CNN can be represented as a weighted 3D grid graph, such that each node represents a pixel/voxel of the volume image.
-Each node is connected to its neighbors by $m_{\mathrm{direct}}$ edges ($E_{\mathrm{direct}}$) and $m_{\mathrm{long}}$ long-range ones ($E_{\mathrm{long}}$).
-In our experiments we evaluate how beneficial long-range connections are for the final segmentation and we add them to the graph with a given probability $p_{\mathrm{long}}$ (if $p_{\mathrm{long}}=0$, then $E_{\mathrm{long}}=\emptyset$).
-We note that the post-processing presented in \cite{lee2017superhuman} did not use any predicted long-range connection, whereas \cite{wolf2018mutex} introduced them with strides of 2 in the XY-plane.
-
-The trained CNN outputs pseudo-probabilities $p:E \rightarrow [0,1]$ that have to be mapped to positive and negative edge weights\footnote{Note that in general attractive and repulsive interactions $w^+$ and $w^-$ can be independently estimated with different classifiers.}.
+Our CNN model outputs affinities in the form of pseudo-probabilities $p:E \rightarrow [0,1]$, where $p=0$ represents a boundary evidence.
+In order to use them as input of the algorithms in our framework, we mapped them to positive and negative values\footnote{Note that in general attractive and repulsive interactions $w^+$ and $w^-$ can be independently estimated with different classifiers.}.
 The most common approaches use \emph{additive} \cite{ailon2008aggregating} or \emph{logarithmic} \cite{finkel2008enforcing,andres2012globally} mappings:
-\begin{equation}
+\begin{equation} \label{eq:mappings}
 \cost_{e,\mathrm{Add}} = p_e - \beta, \qquad \quad \cost_{e,\mathrm{Log}} = \log \left( \frac{p_e}{1-p_e} \right) + \log \left( \frac{\beta}{1-\beta} \right),
@@
 We evaluated both of them empirically with each of the tested linkage and found that the additive mapping is the best option in all cases apart from the \emph{Sum} linkage.
+\TODO{Comment about HC threshold}

### 2019-05-10 chapters/5_experiments_noise.tex
Update exp. sec. and NeurIPS 2019

--- 2019-05-09 chapters/5_experiments_noise.tex
@@
 
-        \caption{Direct neighbor connections ($p_{\mathrm{long}}=0$)} \label{fig:merge_noise_only_direct}
+        \caption{Without long-range edges: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
     \end{subfigure} \hfill
@@
         \includegraphics[width=\textwidth,trim=0.53in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_long_range.pdf}
-        \caption{With long-range connections ($p_{\mathrm{long}}=0.1$)} \label{fig:merge_noise_with_long_range}
+        \caption{With long-range edges: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
     \end{subfigure}
-\caption{\UPDATE{Rand-Scores achieved by the generalized algorithm and different update rules when noise is added to the edge weights.
-Solid lines represent median values; values between the 25th and the 75th percentile are shown in shade areas.
-In the plots at the top, long-range connections are not used.}}\label{fig:noise_plots}
+\caption{Performances of \algname{} with different linkage criteria on a crop of CREMI training data, depending on the amount of noise (x-axis) added to the CNN predictions.
+\textbf{Top}: Accuracies given by Rand-Score (higher is better).
+\textbf{Bottom}: Relative difference in multicut objective (lower is better) measuring how balanced the final clusterings are.
+Solid lines represent median values. Values between the 25th and the 75th percentile are shown in shade areas.}\label{fig:noise_plots}
 \end{figure}
@@
 
-\subsection{Different update rules and robustness to noise}
+\subsection{In-depth comparison of different linkage criteria for \algname{}}
+Highlight difference of the sum in Fig. \ref{fig:intro_figure}.
+% \begin{itemize}
+%   % \item compare different choices of signed-cost-mappings (say which one worked best)
+%   % \item present cremi crop-C table and rule out single and complete linkage
+% \end{itemize}
+Among the update rules listed in Table \ref{tab:linkage-criteria}, in the next sections we will only focus on \emph{sum}, \emph{arithmetic mean} and \emph{absolute maximum}, since they performed best in these experiments.
+
  In this section we evaluate the robustness of \algname{} with different linkage criteria by adding noise to the edge weights.
@@
 \ref{sec:details_perlin}) we provide a more detailed description of the parameters used for the noise generation.
-
-The plots in Fig.
+% \UPDATE{The plots in Fig.
 \ref{fig:noise_plots} represent the scores achieved by \algname{} with different update rules depending on the amount of noise $\mathcal{K}$ added to the edge weights and the probability $p_{\mathrm{long}}$ of long-range connections in the graph.
@@
 The \emph{absolute maximum} update rule proposed by \cite{wolf2018mutex} provides an efficient and fast option, but completely fails when too much noise is added.
-The \emph{sum} update rule version was the slowest option tested, but it was not as robust as the \emph{mean} version, probably due to its tendency to grow one cluster at the time (see Sec.
+% The \emph{sum} update rule version was the slowest option tested, but it was not as robust as the \emph{mean} version, probably due to its tendency to grow one cluster at the time (see Sec.
 \ref{sec:exp_first_comparison}).
 \TODO{Comment about MC energy}
-On the other hand, \algname{} with \emph{mean} update rule and cannot-link constraints did not achieve high scores because of the strong over-segmentation error.
-%Nevertheless, these additional experiments show that it provides an \UPDATE{almost true over-segmentation of the ground truth segmentation even with strongly merge-biased predictions}.
+% On the other hand, \algname{} with \emph{mean} update rule and cannot-link constraints did not achieve high scores because of the strong over-segmentation error.}
 
-\begin{figure}
+\begin{figure}[b]
 \centering
-\begin{minipage}[T]{0.48\textwidth}
-% \begin{table}
+\begin{minipage}[T]{0.54\textwidth}
     \centering
-    % \begin{subtable}[t!]{0.5\textwidth}\centering
-        \begin{tabular}{l M{0.2\textwidth} M{0.2\textwidth}}
-        \toprule
-        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
-         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
-         & \multicolumn{1}{c}{\thead{No\\Constraints}} & \multicolumn{1}{c}{\thead{With\\constraints}} \\ \midrule
-         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
-\textbf{Mean}& \textbf{0.9292}  & 0.8647  \\
-% Lifted multicut & - & -  \\
-Abs. Max.  & 0.9246 & 0.9246 \\
-Max &   0.0611  &  0.9208  \\
-Sum  & 0.8377  & 0.8426  \\
-Min &  0.0737 & 0.0779  \\
+    \footnotesize
+        \begin{tabular}{l|l|cc}
+           & \algname{}  &  \multicolumn{2}{c}{Use constraints:} \\
+           & Linkage & \textsc{No} & \textsc{Yes} \\ \midrule
+DWT \cite{bai2017deep} & - & 21.2 & - \\
+SGN \cite{liu2017sgn} & - & 29.2 & - \\
+Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
+ & Min &  0    & 0  \\
+ & Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
+\multirow{2}{*}{GMIS Pipeline \cite{liu2018affinity}} & Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
+ & Max &   24.3  &   32.5  \\
+ & GMIS \cite{liu2018affinity} & 33.0 & -  \\
+ & \textbf{Average}& \textbf{34.3}  & 33.9  \\
         \end{tabular}
-        % \caption{Linkage criteria}
-    % \end{subtable} 
-    \captionof{table}{Arand-Scores on CREMI challenge (crop of sample C) \UPDATE{for the generalized algorithm and different types of linkage criteria and the optional use of cannot-link constraints.} }
-    \label{tab:results_cremi_val}
+    \captionof{table}{AP scores on the cityscapes validation set for the generalized algorithm and different types of linkage criteria.  }
+    \label{tab:results_cityscapes_val}
 \end{minipage}\hfill
-\begin{minipage}[T]{0.48\textwidth}
-% \begin{table}
+\begin{minipage}[T]{0.43\textwidth}
     \centering
-    % \begin{subtable}[t!]{0.5\textwidth}\centering
-        \begin{tabular}{l M{0.25\textwidth} M{0.25\textwidth}}
-        \toprule
-        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
-         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
-         & \multicolumn{1}{c}{\thead{No\\Constraints}} & \multicolumn{1}{c}{\thead{With\\constraints}} \\ \midrule
-         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
-\textbf{Mean}& \textbf{0.343}  & 0.339  \\
-GMIS \cite{liu2018affinity} & 0.330 & -  \\
-Max &   0.243  &   0.325  \\
-Abs. Max.  & 0.321 & 0.321 \\
-Sum & 0.313  & 0.319  \\
-Min &  0.000    & 0.000  \\
-        \end{tabular}
-        % \caption{Linkage criteria}
-    % \end{subtable} 
-    \captionof{table}{AP scores on the cityscapes validation set for the generalized algorithm and different types of linkage criteria.  }
-    \label{tab:results_cityscapes}
+    \centering
+\includegraphics[width=\textwidth]{./figs/cityscapes_compare_2.pdf} % left bottom right top
 \end{minipage}

### 2019-05-12 chapters/2_rel_work.tex
Update and rewrite exps. sections

@@
 
-This work reformulates the clustering algorithms of \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a general framework and adopt ideas from the proposal-free methods \cite{liu2018affinity,wolf2018mutex,funke2018large} to predict long-range relationships between pixels.
+This work reformulates the clustering algorithms of \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a generalized framework and adopt ideas from the proposal-free methods \cite{liu2018affinity,wolf2018mutex,funke2018large} to predict long-range relationships between pixels.

### 2019-05-12 chapters/3_algorithm.tex
Update and rewrite exps. sections

@@
 \section{Generalized framework for Signed Graph Agglomerative Clustering} \label{sec:general_framework}
-This section introduces the proposed generalized framework: 
+In this section, we first define the graph notation (Sec.~\ref{sec:notation}) and then introduce one of our main contributions: a signed graph partitioning algorithm (Sec.
+\ref{sec:algorithm}) that can be seen as a generalization of several existing and new clustering algorithms (Sec.
+\ref{sec:alg_update_rules}).
+ % introduces the proposed generalized framework: 
 %that represents a simple \UPDATE{generalized} formalization of many agglomerative graph clustering algorithms.
 \UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive node similarities and signed clustering algorithms using attractive and repulsive cues.}\\
-we define the graph notation in Sec.~\ref{sec:notation}, introduce Algorithm \ref{main_alg} in Sec.
-\ref{sec:algorithm} and finally show how it can be seen as a generalization of existing and new graph clustering algorithms in Sec.
-\ref{sec:alg_update_rules}.
+% we  in Sec.~\ref{sec:notation}, introduce Algorithm \ref{main_alg} in  and finally show how it can be seen as a generalization of existing and new graph clustering algorithms in .
 
@@
 
-We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$, in which nodes can represent either pixels, superpixels or voxels.
-We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $S_i \cap S_j = \emptyset$ for each $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
+We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes, in which nodes can represent either pixels, superpixels or voxels.
+We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $\,S_i \cap S_j = \emptyset$ for each $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
 We also denote as $S_u$ the cluster associated with node $u$.
@@
 corresponds to finding the partitioning that optimally balance attraction and repulsion in the graph and is given by the following binary integer program \cite{kappes2011globally,chopra1991multiway,andres2015lifting}:
-\begin{equation}
+\begin{equation}\label{eq:multicut_obj}
 % \min_\Pi \texttt{MC}(\Pi) \equiv
@@
     \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm \algname{}, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
-The set $E_{uv}$ of all edges connecting cluster $S_u$ to cluster $S_v$ is defined as $E_{uv}=(S_u \times S_v) \cap E$.}
+The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e.
+$E_{uv}=(S_u \times S_v) \cap E$.}
     \label{tab:linkage-criteria}
@@
 In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
- the algorithm performs a standard agglomerative HC by returning only one single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see Fig.
-\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} - left panel), where the choice of update rule determines the type of linkage (Table \ref{tab:linkage-criteria}, unsigned graphs).
+ the algorithm performs a standard agglomerative HC by returning only one single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see left panel of Fig.
+\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} and Table \ref{tab:linkage-criteria}, unsigned graphs).
 
@@
 They present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms solving the multicut optimization problem.
-
-The Mutex Watershed \cite{wolf2018mutex}, another algorithm for signed graph partitioning, also introduces dynamical cannot-link constraints.
-In the supplementary material (Sec.
-\ref{sec:equivalence_MWS}) we show how it can be seen as an efficient implementation of \algname{} with the \emph{Absolute maximum} linkage defined in Table \ref{tab:linkage-criteria} and observe that in this case \algname{} returns the same clustering with or without enforcing cannot-link constraints.
-
-On the other hand, to our knowledge, the presented agglomerative algorithm with \emph{Average}, \emph{Max} or \emph{Min} linkage was never applied to signed graphs or combined with cannot-link constraints, \UPDATE{thus we decided to test all these new variations.}
+The Mutex Watershed \cite{wolf2018mutex} is another signed graph partitioning algorithm that introduces dynamical cannot-link constraints.
+In Appendix \ref{sec:equivalence_MWS} we prove that it can be seen as an efficient implementation of \algname{} with \emph{Absolute maximum} linkage (see def.
+in Table \ref{tab:linkage-criteria}) and observe that in this case \algname{} returns the same clustering with or without enforcing cannot-link constraints.
+\UPDATE{Less-known options: \emph{Average}, \emph{Max} or \emph{Min} linkage applied to signed graphs or never combined with cannot-link constraints.}
 
 Apart from the linkage criteria defined in Table \ref{tab:linkage-criteria}, additional ones were proposed in the literature:
-\cite{nunez2013machine} for example proposed a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas
+\cite{nunez2013machine} for example uses a learned approach where a neural network updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas
 \cite{funke2018large} uses a \emph{quantile} linkage criteria by populating a histogram for each inter-cluster interaction.
-In the next chapters, our experiments focus on the linkage criteria listed in Table \ref{tab:linkage-criteria}, since they represent the most used ones.
+In our experiments, we decided to focus on the linkage criteria listed in Table \ref{tab:linkage-criteria}, since they represent the most common options.

### 2019-05-12 chapters/5_experiments_cityscapes.tex
Update exp. sec. and NeurIPS 2019
Update and rewrite exps. sections

--- 2019-04-27 chapters/5_experiments_cityscapes.tex
@@
 % !TEX root = ../agglo_clust_review.tex
-\section{Experiments on CityScapes}
-A successful proposal-free method was recently presented in \cite{liu2018affinity} and a setup equivalent to the one described in Sec.
-\ref{sec:grid_graph} but uses a more complex pipeline to select region of interests in the image, predict semantic pixel information that is used to improve pixel affinities, etc...
-We used exactly their code and pipeline, but we replaced their final agglomeration clustering step with the algorithms proposed in this paper...
+\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
+We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing.
+Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle.
+For our experiments, we used the state-of-the-art proposal-free pipeline proposed in \cite{liu2018affinity} (GMIS) that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
+Their trained model was publicly available, so we simply replaced their final graph-merging algorithm (GMIS-Agglo) with \algname{}.
+See Appendix \ref{sec:cityscapes_appendix} for more details on how we fine-tuned their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
 
-In the experiments on the cityscapes dataset, we used the pipeline proposed by \cite{liu2018affinity} \UPDATE{that currently represents the method not using any external dataset like MS-COCO}...
-
-I should mention the main trick in the loss: ignore background pixels (so focus on boundaries!)
+Results are summarized in Table \ref{tab:results_cityscapes_val} and confirm our findings on neuron-segmentation: \algname{} with average linkage achieves the best scores, whereas other linkage tend to introduce more false region-splits, like \emph{Abs.
+Max.}, or false region-merge, like \emph{Sum}.
+GMIS-Agglo requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 in \cite{liu2018affinity}.
 

### 2019-05-12 chapters/5_experiments_compare_rules.tex
Update and rewrite exps. sections

@@
 \includegraphics[width=\textwidth]{./figs/comparison.pdf} % left bottom right top
-\caption{\algname{} with different linkage criteria on some difficult parts of the CREMI Challenge \cite{cremiChallenge} training data.
+\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge \cite{cremiChallenge} training data.
+Only the few wrongly segmented regions are highlighted in colors.
 Red arrows point to wrongly split regions.
@@
          % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
-         & \algname{} Linkage & \makecell{Arand\\Score} & VI-Score \\ \midrule
+         & \algname{} Linkage & \makecell{Arand} & \makecell{VI-Merge} \\ \midrule
          % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
@@
 THRESH &-& & \\ \hline
-\algname{} & Average& & \\
-Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & & \\
-GAEC \cite{keuper2015efficient} & Sum & & \\
-Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr.  & & \\
+\algname{} & Average& 0.936 & 0.685 \\
+Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 & 0.642 \\
+Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 & 0.714 \\
+GAEC \cite{keuper2015efficient} & Sum & 0.872 & 0.539 \\
         \end{tabular}
@@
 
-\subsection{CREMI Challenge} \label{sec:exp_first_comparison}
+\subsection{CREMI Challenge} \label{sec:cremi_challenge}
 We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available.
-The dataset comes from a serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present available training ground truth.
+The dataset comes from a serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth.
 The results submitted to the leaderboard are evaluated using the CREMI score\footnote{\url{https://cremi.org/leaderboard/}}, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score\cite{arganda2015crowdsourcing}.
@@
 
-\textbf{Training } We pre-aligned the training and test data with an elastic alignment method \cite{saalfeld2012elastic}.
+\textbf{Training details} \UPDATE{We pre-aligned the training and test data with an elastic alignment method \cite{saalfeld2012elastic}.
 We further simulated low contrast sections...
 and missing sections by setting their intensity value to zero...
-We used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d} trained with L1 loss (Adam optimizer with learning rate...).
+We used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d} trained with L1 loss (Adam optimizer with learning rate...).}
 
@@
 For these baselines, affinities are converted to a boundary map \UPDATE{by taking a weighted average over short- and long-range edge connections}.
-Other state-of-the-art neuron-segmentation multi-step-pipelines first find 2D superpixels using WSDT and then apply a graph partitioning algorithm: in our comparison, we include one pipeline using agglomerative HC with average linkage (avgHC) and one using an approximation of the Lifted Multicut Problem (LMC) \cite{beier2016efficient}.
-
-\textbf{Comparison results } Among all the signed graph algorithms included in our generalized framework, the less-known one with \emph{Average} linkage consistently outperformed all other previously proposed linkage like \emph{Sum} or \emph{Absolute Max}
-(see Table \ref{tab:results_cremi_train}).
-This method also achieved \UPDATE{comparable} scores to other complex multi-step pipelines that usually require the user to tune several hyper-parameters.
-The performances of all linkage criteria listed in Table \ref{tab:linkage-criteria} are summarized in Table \ref{tab:cremi_train_full} in Appendix and in Fig.
-\ref{fig:cremi_comparison}, where we highlight some of the major mistakes...
+Other state-of-the-art multi-step-pipelines for neuron-segmentation first find 2D superpixels using WSDT and then apply a graph partitioning algorithm: in our comparison, we include one pipeline using agglomerative HC with average linkage (avgHC) and one using an approximation of the Lifted Multicut Problem (LMC) \cite{beier2016efficient}.

### 2019-05-12 chapters/5_experiments_intro.tex
Update and rewrite exps. sections

@@
 This application is of key interest in connectomics, a field of neuro-science with the goal of reconstructing neural wiring diagrams spanning complete central nervous systems.
-While a lot of progress is being made, only proof-reading or manual tracing yields sufficient accuracy for correct circuit reconstruction \cite{schlegel2017learning}.
-\TODO{subsections description}
+Currently, only proof-reading or manual tracing yields sufficient accuracy for correct circuit reconstruction \cite{schlegel2017learning}, thus further progress is required in automated reconstruction methods.
+In Sec.
+\ref{sec:grid_graph}, we present how we predicted signed edge weights with a CNN.
+Then we introduce the CREMI challenge and our tested methods in Sec.
+\ref{sec:cremi_challenge} and present our results in Sec.
+\ref{sec:comparison_exps}.
 
@@
 % In our experiments, we divided the set of edges $E$ in $E_{\mathrm{direct}}$ connecting direct neighboring voxels and $E_{\mathrm{long}}$. 
-In the Supplementary material (Sec. \ref{sec:training_details}) we provide more details on the chosen neighborhood structure.
+See Appendix \ref{sec:training_details} for more details on the chosen neighborhood structure.
 % , data augmentation and the training with L1 loss of the used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d}.
@@
 We evaluated both of them empirically with each of the tested linkage and found that the additive mapping is the best option in all cases apart from the \emph{Sum} linkage.
-\TODO{Comment about HC threshold}
+\TODO{HC threshold}

### 2019-05-12 chapters/5_experiments_noise.tex
Update and rewrite exps. sections

@@
     \end{subfigure}
-\caption{Performances of \algname{} with different linkage criteria on a crop of CREMI training data, depending on the amount of noise (x-axis) added to the CNN predictions.
-\textbf{Top}: Accuracies given by Rand-Score (higher is better).
-\textbf{Bottom}: Relative difference in multicut objective (lower is better) measuring how balanced the final clusterings are.
-Solid lines represent median values. Values between the 25th and the 75th percentile are shown in shade areas.}\label{fig:noise_plots}
+\caption{Performances of \algname{} with different linkage criteria on a crop of CREMI training data sample B, depending on the amount of noise (x-axis) added to the CNN predictions.
+\textbf{Top}: Accuracy given by Rand-Score (higher is better).
+Solid lines represent median values.
+Values between the 25th and the 75th percentile are shown in shade areas.
+\textbf{Bottom}: Multicut objective (Eq.
+\ref{eq:multicut_obj}), measuring how balanced the final clusterings are (lower is better); for a clearer comparison, an offset is added to the energy values, so that the method achieving the lowest energy is always assigned to value 1.
+\UPDATE{CLC}
+}\label{fig:noise_plots}
 \end{figure}
@@
 
-\subsection{In-depth comparison of different linkage criteria for \algname{}}
-Highlight difference of the sum in Fig. \ref{fig:intro_figure}.
-% \begin{itemize}
-%   % \item compare different choices of signed-cost-mappings (say which one worked best)
-%   % \item present cremi crop-C table and rule out single and complete linkage
-% \end{itemize}
-Among the update rules listed in Table \ref{tab:linkage-criteria}, in the next sections we will only focus on \emph{sum}, \emph{arithmetic mean} and \emph{absolute maximum}, since they performed best in these experiments.
+\subsection{In-depth comparison of different linkage criteria for \algname{}} \label{sec:comparison_exps}
+As shown in Table \ref{tab:results_cremi_train}, among all the signed graph algorithms included in our generalized framework, the less-known one with \emph{Average} linkage consistently outperformed all other previously proposed linkage like \emph{Sum} or \emph{Absolute Max}.
+This method also achieved \UPDATE{comparable} scores to other complex multi-step pipelines that usually require the user to tune several hyper-parameters, like LMC.
+In Fig.
+\ref{fig:cremi_comparison}, we highlight some failure cases of \algname{} and in Appendix we provide an extended version of Table \ref{tab:results_cremi_train} including all linkage tested with \algname{} on the full CREMI training data.
 
- In this section we evaluate the robustness of \algname{} with different linkage criteria by adding noise to the edge weights.
-  %Before to present the results shown in Fig. \ref{fig:noise_plots}, we will first introduce the type of noise that was added to the edge weights.
-% In the set of experiments presented in this article, edge weights are estimated \UPDATE{by using a CNN that predicts how likely two neighboring pixels are to be part of the same cluster}. 
-Fig.
-\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}a} shows an example of uncertain CNN predictions on a slice of the neuron segmentation dataset.
-We now present a way of modifying the CNN output to introduce additional artifacts like a missing or false boundary evidence.
+In order to highlight the properties and the strengths of each linkage criteria and  perform an in-depth comparison that is as quantitative as possible, we run an additional set of experiments where we perturbed the CNN predictions with noise.
+In Appendix, we provide all the details about the used type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false boundary evidences (see visual example in Fig.
+\ref{fig:noisy_affs}).
 
-In the field of image processing there are several ways of adding noise to an image, among which the most common are Gaussian noise or Poisson shot noise. 
-In these cases, the noise of one pixel does not correlate with its neighboring noise values. On the other hand, predictions of a CNN are known to be spatially correlated. 
-Thus, we used Perlin noise\footnote{In our experiments, we used an open-source version of simplex noise \cite{perlin2001noise}, which is an improved open-source version of Perlin noise \cite{perlin1985image}}, one of the most common gradient noises used in procedural pattern generation.
-This type of noise $n(x)\in[0,1]$ generates spatial random patterns that are locally smooth but have large and diverse variations on bigger scales.
-We then combined it with the CNN predictions $p(x)$ in the two following ways:
-\begin{equation}\label{eq:noise_biased_predictions}
-% \tilde{F}(x;\theta)=\begin{cases}
-% F(x;\theta)+\mathcal{K}\cdot\max\left(N(x),0\right) & \text{if merge-biased}\\
-% F(x;\theta)+\mathcal{K}\cdot\min\left(N(x),0\right) & \text{if split-biased}
-% \end{cases}
-\tilde{F}_{\pm}(x;\mathcal{K})=F(x)\pm\big|\mathcal{K}\cdot\max\left(\pm N(x),0\right)\big|,
-\end{equation}
-where  $N(x)=\mathrm{Logit}[n(x)]$; $F(x)=\mathrm{Logit}[p(x)]$ and $\mathcal{K}\in \mathbb{R}^+$ is a positive factor representing the amount of added noise.
-$\tilde{F}_{+}(x;\mathcal{K})$ represents then a merge-biased prediction, such that the probability for two pixels to be in the same cluster is increased only if $N(x)>0$ (see Fig.
-\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b}), whereas $\tilde{F}_{-}(x;\mathcal{K})$ is a split-biased prediction with decreased probabilities when $N(x)<0$ (Fig.
-\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}).
-In the Supplementary material (Sec.
-\ref{sec:details_perlin}) we provide a more detailed description of the parameters used for the noise generation.
+Plots in Fig.
+\ref{fig:noise_plots} summarize 6000 experiments: we focused on the best performing linkage criteria, i.e.
+\emph{Average}, \emph{Sum} and \emph{Abs Max}, and tested them with different values of noise, both with and without use of long-range connections in the grid-graph\footnote{We tested 20 values of noise and, for each setup, we averaged the scores over 30 runs.}.
+In Fig.
+\ref{fig:noise_plots}, we used a merge-biased noise decreasing boundary evidence.
+See Fig.
+\ref{fig:noise_split} in Appendix for a split-biased version.
+Our findings confirm that \algname{} with \emph{Average} linkage criterion represents the most robust algorithm tested and that is the one benefiting more from additional long-range edge connections.
+Other versions using cannot-link constraints generally lead to an over-segmentation, but are robust to ``leaks through holes'' given by missing boundary evidence.
+The greedy \emph{absolute maximum} linkage proposed by \cite{wolf2018mutex} is the least robust to noise, but, as we show in Table \ref{tab:full_cremi_results}, it represents an efficient and considerably faster option.
+The \emph{Sum} linkage generally outputs the most balanced graph partitioning according to the objective defined in Eq.
+\ref{eq:multicut_obj} and is then confirmed to be a good choice for initializing more complex approximations of the multicut optimization problem like \cite{beier2016efficient}.
+Nevertheless, in more challenging parts of the data (see Fig.
+\ref{fig:cremi_comparison}) or in the presence of noise, it often incorrectly merge regions together, leading to more unbalanced graph partitioning.
+In these cases, the use of cannot-link constraints or a more robust average linkage are preferable.
 % \UPDATE{The plots in Fig.
-\ref{fig:noise_plots} represent the scores achieved by \algname{} with different update rules depending on the amount of noise $\mathcal{K}$ added to the edge weights and the probability $p_{\mathrm{long}}$ of long-range connections in the graph.
+\ref{fig:noise_plots} represent the scores achieved by \algname{} with different update rules depending on the amount of noise $\m{}athcal{K}$ added to the edge weights and the probability $p_{\mathrm{long}}$ of long-range connections in the graph.
 Results clearly show that adding long-range edges is always beneficial for the final segmentation \TODO{Not True!}.
@@
 % On the other hand, \algname{} with \emph{mean} update rule and cannot-link constraints did not achieve high scores because of the strong over-segmentation error.}
+
+% Highlight difference of the sum in Fig. \ref{fig:intro_figure}.
+% \begin{itemize}
+%   % \item compare different choices of signed-cost-mappings (say which one worked best)
+%   % \item present cremi crop-C table and rule out single and complete linkage
+% \end{itemize}
 
@@
 Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
+ & \textbf{Average}& \textbf{34.3}  & 33.9  \\
+ & GMIS-Agglo \cite{liu2018affinity} & \UPDATE{33.0} & -  \\
+\multirow{2}{*}{GMIS Pipeline} & Max &   24.3  &   32.5  \\
+ & Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
+ & Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
  & Min &  0    & 0  \\
- & Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
-\multirow{2}{*}{GMIS Pipeline \cite{liu2018affinity}} & Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
- & Max &   24.3  &   32.5  \\
- & GMIS \cite{liu2018affinity} & 33.0 & -  \\
- & \textbf{Average}& \textbf{34.3}  & 33.9  \\
         \end{tabular}

### 2019-05-12 chapters/supplementary.tex
Update and rewrite exps. sections

@@
 \end{itemize}
+
+\subsection{Noise exps}
+ % In this section we evaluate the robustness of \algname{} with different linkage criteria by adding noise to the edge weights.
+  %Before to present the results shown in Fig. \ref{fig:noise_plots}, we will first introduce the type of noise that was added to the edge weights.
+% In the set of experiments presented in this article, edge weights are estimated \UPDATE{by using a CNN that predicts how likely two neighboring pixels are to be part of the same cluster}. 
+Fig.
+\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}a} shows an example of uncertain CNN predictions on a slice of the neuron segmentation dataset.
+We now present a way of modifying the CNN output to introduce additional artifacts like a missing or false boundary evidence.
+
+In the field of image processing there are several ways of adding noise to an image, among which the most common are Gaussian noise or Poisson shot noise. 
+In these cases, the noise of one pixel does not correlate with its neighboring noise values. On the other hand, predictions of a CNN are known to be spatially correlated. 
+Thus, we used Perlin noise\footnote{In our experiments, we used an open-source version of simplex noise \cite{perlin2001noise}, which is an improved open-source version of Perlin noise \cite{perlin1985image}}, one of the most common gradient noises used in procedural pattern generation.
+This type of noise $n(x)\in[0,1]$ generates spatial random patterns that are locally smooth but have large and diverse variations on bigger scales.
+We then combined it with the CNN predictions $p(x)$ in the two following ways:
+\begin{equation}\label{eq:noise_biased_predictions}
+% \tilde{F}(x;\theta)=\begin{cases}
+% F(x;\theta)+\mathcal{K}\cdot\max\left(N(x),0\right) & \text{if merge-biased}\\
+% F(x;\theta)+\mathcal{K}\cdot\min\left(N(x),0\right) & \text{if split-biased}
+% \end{cases}
+\tilde{F}_{\pm}(x;\mathcal{K})=F(x)\pm\big|\mathcal{K}\cdot\max\left(\pm N(x),0\right)\big|,
+\end{equation}
+where  $N(x)=\mathrm{Logit}[n(x)]$; $F(x)=\mathrm{Logit}[p(x)]$ and $\mathcal{K}\in \mathbb{R}^+$ is a positive factor representing the amount of added noise.
+$\tilde{F}_{+}(x;\mathcal{K})$ represents then a merge-biased prediction, such that the probability for two pixels to be in the same cluster is increased only if $N(x)>0$ (see Fig.
+\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b}), whereas $\tilde{F}_{-}(x;\mathcal{K})$ is a split-biased prediction with decreased probabilities when $N(x)<0$ (Fig.
+\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}).
+In the Supplementary material (Sec.
+\ref{sec:details_perlin}) we provide a more detailed description of the parameters used for the noise generation.
+
+\subsection{Cityscapes exps}
+Mention the main trick in the loss: ignore background pixels (so focus on boundaries). Same mapping defined in \ref{eq:mappings}
 

### 2019-05-13 chapters/1_intro.tex
Update intro

@@
 \section{Introduction}
-%On possible selling story could be: currently many of the successful proposal-free instance segmentation methods rely on a final clustering step on a grid-graph with both short and long-range connections.
-So it is worth to study this problem in more details.
+The majority of clustering methods work with positive edge weights only, representing for example attractive interactions between the nodes.
+These methods require the user to specify the desired numbers of clusters or a termination criterion (as in spectral clustering or iterated normalized cuts) or even a stronger version of supervision in terms of seeds (as in seeded watershed or random walker).
+Hierarchical clustering (HC) is also a popular method, which creates a hierarchy of clusters.
+Agglomerative HC is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}.
+This method usually requires the user to choose a level in the cluster hierarchy defining the desired output clustering.
 
-\emph{Instance segmentation} is a computer vision task consisting in assigning each pixel of an image to an object instance. %, where the number of instances is usually not known in advance. 
-Most recently, success in instance segmentation (IS) has been achieved by applying deep learning and there are two main types of successful deep learning approaches to IS: proposal-based \cite{he2017mask,dai2016instance,li2017fully} and proposal-free \cite{kong2018recurrent,novotny2018semi,kulikov2018instance,kirillov2017instancecut} methods.
+Other partitioning methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between nodes.
+The advantage of using signed graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters.
+This can be done optimally by solving the so-called \emph{multicut optimization problem} or \emph{correlation clustering} \cite{kappes2011globally,chopra1991multiway}.
+However, this problem is NP-hard, so heuristic approximated methods were proposed \cite{yarkony2012fast,pape2017solving}.
+For even larger problems, greedy agglomerative partitioning algorithms are usually employed \cite{kardoostsolving,keuper2015efficient}.
+Some of these approaches \cite{levinkov2017comparative,wolf2018mutex} also dynamically introduce cannot-link constraints, representing mutual exclusion relationships between clusters.
+Despite their similarity to agglomerative HC algorithms for unsigned graphs with only positive weights, neither an explicit connection nor a clear experimental comparison was proposed so far.
+
+As a first contribution, we reformulate several of these recently proposed graph agglomerative algorithms in a simple review framework (Sec.
+\ref{sec:general_framework}) that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract).
+From this new point of view, agglomerative HC and algorithms proposed in \cite{levinkov2017comparative,wolf2018mutex,lance1967general,kardoostsolving} all share a general procedure but differ in the way inter-cluster interaction is updated after each iteration (Table \ref{tab:linkage-criteria}).
+At the same time, we also show that this framework allows us to introduce totally new variations of these algorithms.
+Ultimately, by presenting this simple general approach, our hope is to motivate a deeper understanding of the connection between algorithms for unsigned and signed graphs.
+
+We then evaluate and compare these algorithms on \emph{instance segmentation}, which is a computer vision task consisting in assigning each pixel of an image to an object instance.
+%, where the number of instances is usually not known in advance.
+For our experiments, we focus on a \emph{proposal-free} deep learning method that does not involve object detection but directly group pixels into object instances.
+Recently, there has been a growing interest for proposal-free methods, since in certain types of data, for example electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing}, objects are not approximated well by bounding boxes.
+We then use a CNN to predict the edge weights of a grid-graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms of our framework.
+By applying this method both to 2D urban scenes from the CityScapes dataset and a challenging neuron-segmentation task of 3D EM image stacks, we show how... \UPDATE{Summarize results}
+
+% Most recently, success in instance segmentation (IS) has been achieved by applying deep learning and there are two main types of successful deep learning approaches to IS: proposal-based \cite{he2017mask,dai2016instance,li2017fully} and proposal-free \cite{kong2018recurrent,novotny2018semi,kulikov2018instance,kirillov2017instancecut} methods.
 Proposal-based methods consist of two steps: detecting objects, for example by finding bounding boxes, and assigning pixels to the detected instances.
@@
 % More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)
-Thus, there is a growing interest for more efficient proposal-free methods that perform IS by directly predicting \UPDATE{pixel features} and then grouping pixels into object instances.
+% Thus, there is a growing interest for more efficient proposal-free methods that perform IS by directly predicting \UPDATE{pixel features} and then grouping pixels into object instances.
 In this work, we focus on a common proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance.
 Recently, this approach was successfully applied both to neuron segmentation of 3D EM image stacks \cite{lee2017superhuman,wolf2018mutex} and instance segmentation of 2D urban scenes \cite{liu2018affinity}, where it achieved performances superior and comparable, respectively, to proposal-based methods.
-
-In this approach, the output of the CNN can be represented as a weighted grid graph such that each node represents a pixel of the image and the weights of the edges define interactions between the pixels.
+% In this approach, the output of the CNN can be represented as a weighted grid graph such that each node represents a pixel of the image and the weights of the edges define interactions between the pixels.
 A graph clustering algorithm is then applied to cluster pixels into instances.
-The majority of clustering methods work with positive edge weights only, representing attractive interactions between the nodes.
-These methods require the user to specify the desired numbers of segments or a termination criterion (as in spectral clustering or iterated normalized cuts) or even a stronger version of supervision in terms of seeds (as in seeded watershed or random walker).
-Hierarchical clustering (HC) is also a popular method, which creates a hierarchy of clusters.
-Agglomerative HC is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}.
-This method requires the user to choose a level in the cluster hierarchy defining the desired output clustering.
-
-Other clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between pixels.
-The advantage of using signed graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters.
-This can be done optimally by solving the so-called \emph{multicut optimization problem} or \emph{correlation clustering} \cite{kappes2011globally,chopra1991multiway}.
-However, this problem is NP-hard, so good approximations \cite{yarkony2012fast,pape2017solving} and efficient greedy heuristics \cite{levinkov2017comparative,wolf2018mutex} were proposed.
-
-Our first contribution is a review framework for graph clustering (Sec.
-\ref{sec:general_framework}) that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract).
-We show that various existing partitioning algorithms \cite{levinkov2017comparative,wolf2018mutex,kardoostsolving,lance1967general} can be reformulated in our framework, so that they share a general procedure but differ in the way inter-cluster interaction is updated after each iteration.
-Moreover, this framework allows us to introduce new variations of these algorithms that also enforce mutual-exclusion relationships between clusters.
-
-Finally, the algorithms included in the framework are evaluated on an instance segmentation task, both on 3D biological image stacks (Sec.
+% Finally, the algorithms included in the framework are evaluated on an instance segmentation task, both on 3D biological image stacks (Sec.
 \ref{sec:neuro_segm_exp}) and 2D urban scenes (Sec.

### 2019-05-13 chapters/3_algorithm.tex
Update intro

@@
 \section{Generalized framework for Signed Graph Agglomerative Clustering} \label{sec:general_framework}
-In this section, we first define the graph notation (Sec.~\ref{sec:notation}) and then introduce one of our main contributions: a signed graph partitioning algorithm (Sec.
+In this section, we first define the graph notation in Sec.~\ref{sec:notation} and then introduce one of our main contributions: a signed graph partitioning algorithm (Sec.
 \ref{sec:algorithm}) that can be seen as a generalization of several existing and new clustering algorithms (Sec.

### 2019-05-13 chapters/5_experiments_compare_rules.tex

@@
 
-\textbf{Training details} \UPDATE{We pre-aligned the training and test data with an elastic alignment method \cite{saalfeld2012elastic}.
+\textbf{Training details}
+To alleviate difficulties in segmentation, we use a version of the data that was elastically aligned by the challenge organizers with the method \cite{saalfeld2012elastic}.
+We train a 3D U-Net \cite{ronneberger2015u, cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
+as described in \cite{lee2017superhuman}. In addition to the standard data augmentation techniques of random rotations, random flips and elastic deformations, we simulate data artifacts.
+In more detail, we randomly zero-out slices, decrease the contrast of slices, simulate tears, introduce alignment jitter and paste artifacts extracted from the training data.
+Both \cite{funke2018large} and \cite{lee2017superhuman} have shown
+that these kinds of augmentations can help to alleviate issues caused by EM-imaging artifacts.
+We use L2 loss and Adam optimizer to train the network.
+%\UPDATE{We pre-aligned the training and test data with an elastic alignment method \cite{saalfeld2012elastic}.
 We further simulated low contrast sections...

### 2019-05-13 chapters/3_algorithm.tex
Update training methods

@@
 This variant
-select the pair of clusters with the highest absolute interaction $|\interact(S_u, S_v)|$, so that the most attractive and the most repulsive pairs are analyzed first (see example in Fig.
+selects the pair of clusters with the highest absolute interaction $|\interact(S_u, S_v)|$, so that the most attractive and the most repulsive pairs are analyzed first (see example in Fig.
 \ref{subfig:with_constraints}).
@@
 In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
- the algorithm performs a standard agglomerative HC by returning only one single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see left panel of Fig.
+ the algorithm performs a standard agglomerative HC by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see left panel of Fig.
 \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} and Table \ref{tab:linkage-criteria}, unsigned graphs).

### 2019-05-13 chapters/5_experiments_compare_rules.tex
Update training methods

@@
 \textbf{Training details}
-To alleviate difficulties in segmentation, we use a version of the data that was elastically aligned by the challenge organizers with the method \cite{saalfeld2012elastic}.
+To alleviate difficulties stemming from misalignment, we use a version of the data that was elastically realigned by the challenge organizers with the method of \cite{saalfeld2012elastic}.
 We train a 3D U-Net \cite{ronneberger2015u, cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 

### 2019-05-14 chapters/0_abstract.tex
Update intro and abstract

% !TEX root = ../agglo_clust_review.tex
%%%%%%%%% ABSTRACT
\begin{abstract}
We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and cannot-link constraints, i.e. mutual exclusion between clusters. These different combinations then correspond to existing clustering methods as well as new algorithms that we introduce and analyze. We evaluate these different algorithms on instance segmentation, which is the task of partitioning an image into distinct segments, by predicting edge weights with a CNN. \UPDATE{Summarize results} 
\end{abstract}

### 2019-05-14 chapters/1_intro.tex
Update intro and abstract

@@
 \section{Introduction}
-The majority of clustering methods work with positive edge weights only, representing for example attractive interactions between the nodes.
-These methods require the user to specify the desired numbers of clusters or a termination criterion (as in spectral clustering or iterated normalized cuts) or even a stronger version of supervision in terms of seeds (as in seeded watershed or random walker).
-Hierarchical clustering (HC) is also a popular method, which creates a hierarchy of clusters.
+The clustering of weighted graphs has been successfully applied to such tasks as image segmentation, tracking... \UPDATE{REFS}
+Most graph clustering methods work with positive edge weights only, representing similarities or distances between the nodes.
+These methods are parameter-based and require users to specify the desired numbers of clusters or a termination criterion (e.g.
+spectral clustering or iterated normalized cuts) or even a stronger version of supervision in terms of seeds (e.g.
+seeded watershed or random walker).
+Hierarchical clustering (HC) is a popular graph clustering method, which creates a hierarchy of clusters.
 Agglomerative HC is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}.
@@
 
-Other partitioning methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between nodes.
-The advantage of using signed graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters.
-This can be done optimally by solving the so-called \emph{multicut optimization problem} or \emph{correlation clustering} \cite{kappes2011globally,chopra1991multiway}.
-However, this problem is NP-hard, so heuristic approximated methods were proposed \cite{yarkony2012fast,pape2017solving}.
-For even larger problems, greedy agglomerative partitioning algorithms are usually employed \cite{kardoostsolving,keuper2015efficient}.
-Some of these approaches \cite{levinkov2017comparative,wolf2018mutex} also dynamically introduce cannot-link constraints, representing mutual exclusion relationships between clusters.
-Despite their similarity to agglomerative HC algorithms for unsigned graphs with only positive weights, neither an explicit connection nor a clear experimental comparison was proposed so far.
+Other graph clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between nodes.
+The advantage of using signed graphs over positive-weight graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters.
+This can be done optimally by solving the so-called \emph{multicut optimization} or \emph{correlation clustering} problem \cite{kappes2011globally,chopra1991multiway}.
+However, this problem is NP-hard, so instead of finding optimal solutions, most of the methods perform approximations.
+Greedy agglomerative clustering algorithms are among the most efficient methods \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}.
+% Some of these methods \cite{levinkov2017comparative,wolf2018mutex} dynamically introduce cannot-link constraints, representing mutual exclusion relationships between clusters.
 
-As a first contribution, we reformulate several of these recently proposed graph agglomerative algorithms in a simple review framework (Sec.
+Thus, greedy agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter free and efficient.
+Despite the fact that there exist a variety of these algorithms, there has been no overarching studies comparing them and making it possible to choose the most appropriate algorithm for particular applications and assess their properties, e.g.
+robustness and efficiency.
+
+%Despite their similarity to agglomerative HC algorithms for unsigned graphs with only positive weights, neither an explicit connection nor a clear experimental comparison was proposed so far.
+
+In this paper, we propose a novel theoretical framework for generalizing over the greedy agglomerative clustering algorithms for signed graphs by linking these algorithms to the agglomerative HC.
+This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}, i.e.
+mutual exclusion between clusters, in a consistent way.
+These different combinations then correspond to existing clustering algorithms as well as allows us to introduce and explore new algorithms.
+The framework can also be easily expended to accommodate additional linkage criteria.
+
+%As a first contribution, we reformulate several of these recently proposed graph agglomerative algorithms in a simple review framework (Sec.
 \ref{sec:general_framework}) that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract).
@@
 At the same time, we also show that this framework allows us to introduce totally new variations of these algorithms.
-Ultimately, by presenting this simple general approach, our hope is to motivate a deeper understanding of the connection between algorithms for unsigned and signed graphs.
+%Ultimately, by presenting this simple general approach, our hope is to motivate a deeper understanding of the connection between algorithms for unsigned and signed graphs.
 
@@
 %, where the number of instances is usually not known in advance.
-For our experiments, we focus on a \emph{proposal-free} deep learning method that does not involve object detection but directly group pixels into object instances.
-Recently, there has been a growing interest for proposal-free methods, since in certain types of data, for example electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing}, objects are not approximated well by bounding boxes.
-We then use a CNN to predict the edge weights of a grid-graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms of our framework.
-By applying this method both to 2D urban scenes from the CityScapes dataset and a challenging neuron-segmentation task of 3D EM image stacks, we show how... \UPDATE{Summarize results}
+We use a CNN to predict the edge weights of a graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms in our framework.
+% For our experiments, we focus on a \emph{proposal-free} deep learning method that does not involve object detection but directly group pixels into object instances. 
+Recently, there has been a growing interest for such \emph{proposal-free} methods that do not involve object detection, since in certain types of data objects cannot be approximated by bounding boxes.
+%  (for example in electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing})
 
+By applying this method both to 2D urban scenes from the CityScapes dataset and the challenging neuron-segmentation task of 3D EM image stacks, \UPDATE{we show how one of the less-known algorithms included in our framework consistently outperformed all other previously proposed signed graph clustering methods and achieved comparable/superior scores to other complex multi-step pipelines...}
 % Most recently, success in instance segmentation (IS) has been achieved by applying deep learning and there are two main types of successful deep learning approaches to IS: proposal-based \cite{he2017mask,dai2016instance,li2017fully} and proposal-free \cite{kong2018recurrent,novotny2018semi,kulikov2018instance,kirillov2017instancecut} methods.
@@
 \caption{
- (\textbf{a}) Some iterations of the generalized algorithm on toy graphs with attractive (green) and repulsive (red) interactions.
+ (\textbf{a}) Iterations of three different algorithms in the generalized framework on  toy graph examples with attractive (green) and repulsive (red) interactions.
 (\textbf{b}) Example of CREMI 2016 neuron-segmentation data \cite{cremiChallenge} overlaid with instance segmentation.
-(\textbf{c}) Agglomeration order, representing which pairs of neighboring pixels were merged first (white), later on (brown) or never (black).
-We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
+(\textbf{c}) Agglomeration order, representing which pairs of neighboring pixels were merged first (white), later on (brown), or never (black).
+%We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
 % On the left: a single cluster is returned with only attractive interactions.

### 2019-05-15 chapters/0_abstract.tex
Update supplementaries

@@
 \begin{abstract}
+\today,\currenttime - 
 We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes.

### 2019-05-15 chapters/3_algorithm.tex
Update supplementaries

@@
           \State Merge cluster $S_u$ with $S_v$: update interactions and cannot-link constraints with all their neighbors
-        \EndIf
         % \State
-        \If{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big] \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
+        \ElsIf{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big] \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
           \State Add CannotLink Constraint between clusters $S_u$ and $S_v$
@@
 \end{table*}
+\begin{figure}
+\centering
+% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
+\includegraphics[width=\textwidth]{./figs/comparison.pdf} % left bottom right top
+\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge \cite{cremiChallenge} training data.
+Only the few wrongly segmented regions are highlighted in colors.
+Red arrows point to wrongly split regions.
+Yellow arrows point out merge errors.
+Green arrows indicate challenging, but correctly segmented regions.
+% Only the involved segments are colored.
+ % main ideas and contributions
+\label{fig:cremi_comparison}}
+\end{figure}
 

### 2019-05-15 chapters/5_experiments_compare_rules.tex
Update supplementaries

@@
 
-\begin{figure}[t]
-\centering
-% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
-\includegraphics[width=\textwidth]{./figs/comparison.pdf} % left bottom right top
-\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge \cite{cremiChallenge} training data.
-Only the few wrongly segmented regions are highlighted in colors.
-Red arrows point to wrongly split regions.
-Yellow arrows point out merge errors.
-Green arrows indicate challenging, but correctly segmented regions.
-% Only the involved segments are colored.
- % main ideas and contributions
-\label{fig:cremi_comparison}}
-\end{figure}
 \begin{figure}
@@
     % \begin{subtable}[t!]{0.5\textwidth}\centering
-        \begin{tabular}{l|l|c|c}
+        \begin{tabular}{l|l|c}
         % \toprule
@@
          % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
-         & \algname{} Linkage & \makecell{Arand} & \makecell{VI-Merge} \\ \midrule
+         & \algname{} Linkage & \makecell{Arand-Score}  \\ \midrule \midrule
          % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
-DTWS + LMC \cite{beier2016efficient}& -& & \\
-DTWS + avgHC &-& & \\
-DTWS  & -& & \\
-THRESH &-& & \\ \hline
-\algname{} & Average& 0.936 & 0.685 \\
-Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 & 0.642 \\
-Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 & 0.714 \\
-GAEC \cite{keuper2015efficient} & Sum & 0.872 & 0.539 \\
+\textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
+Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
+DTWS + LMC (LR)& -& 0.903 $\pm$ 0.016 \\
+DTWS + MC (LR)& -& 0.903 $\pm$ 0.017 \\
+% DTWS + avgHC &-& \\
+DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
+DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
+Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
+GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
+THRESH &-& 0.221  $\pm$ 0.067 \\ 
+DTWS  & -& 0.010 $\pm$ 0.003\\
         \end{tabular}

### 2019-05-15 chapters/5_experiments_noise.tex
Update supplementaries

@@
 \textbf{Bottom}: Multicut objective (Eq.
-\ref{eq:multicut_obj}), measuring how balanced the final clusterings are (lower is better); for a clearer comparison, an offset is added to the energy values, so that the method achieving the lowest energy is always assigned to value 1.
-\UPDATE{CLC}
+\ref{eq:multicut_obj}), measuring how balanced the final clusterings are (lower is better); for a clearer comparison, an offset is added to the energy values, so that the method achieving the lowest energy is always assigned to value zero.
 }\label{fig:noise_plots}
@@
 
-\subsection{In-depth comparison of different linkage criteria for \algname{}} \label{sec:comparison_exps}
+\subsection{Results}
+% \subsection{In-depth comparison of different linkage criteria for \algname{}} \label{sec:comparison_exps}
 As shown in Table \ref{tab:results_cremi_train}, among all the signed graph algorithms included in our generalized framework, the less-known one with \emph{Average} linkage consistently outperformed all other previously proposed linkage like \emph{Sum} or \emph{Absolute Max}.
@@
 In order to highlight the properties and the strengths of each linkage criteria and  perform an in-depth comparison that is as quantitative as possible, we run an additional set of experiments where we perturbed the CNN predictions with noise.
-In Appendix, we provide all the details about the used type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false boundary evidences (see visual example in Fig.
+In Appendix, we provide all the details about the used type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false boundary evidences (see example in Fig.
 \ref{fig:noisy_affs}).

### 2019-05-15 chapters/supplementary.tex
Update intro and abstract
Update supplementaries

@@
 
+\begin{algorithm}
+  \caption{\algname{} as a generalized edge contraction algorithm for signed graphs}
+\hspace*{\algorithmicindent} \textbf{Input:} $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes and $M$ edges; boolean \texttt{{\color{blue}addCannotLinkConstraints}} \\
+\hspace*{\algorithmicindent} \textbf{Output:} Final clustering given by union-find data structure \\
+  \hspace*{\algorithmicindent} 
+  \begin{algorithmic}[1]
+    % \Procedure{GraphEdgeContr}{{\color{blue}bool \emph{addConstraints}}}
+      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
+      \State $\tilde{\mathcal{G}}(\tilde{V},\tilde{E}) \gets \mathcal{G}(V,E,w^+,w^-)$  \Comment{Init. contracted graph}
+      \State \texttt{UF} $\gets$ initUnionFind($V$) \Comment{Init. data structure representing clustering}
+    %   \State PQ $\gets$ Sort $e\in E$ in descending order of $|w_e|$
+        \State PQ.push$(|w_e|, e) \quad \forall e \in E $  \Comment{Init. priority queue in desc. order of $|w_e|=|w_e^+ - w_e^-|$, $\mathcal{O}(M)$}
+        \State \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$ \Comment{Init. cannot-link constraints}
+      % \State $E_\dagger \gets \{\}$ \Comment{Set of must-not-link edges}
+    %   \State PQ.push$(e,  ) \quad \forall e \in E $  
+    \State
+      \While{PQ is \textbf{not} empty}
+        \State $\tilde{w}, e_{uv} \gets $ PQ.popHighest() \Comment{$\mathcal{O}(\log M)$}
+        \State \textbf{assert} \texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$) \Comment{Edges in PQ always link nodes in different clusters}
+        % \If{ $e_{uv} \notin E' $} 
+        %     \State \textbf{continue}
+        % \EndIf
+        \If{({\color{ForestGreen}\textbf{$\tilde{w} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
+        %   \State $u,v \gets u,v \in V' : $
+        %   \State $S_u \gets S \in \Pi$ : $ u \in S$
+        %   \State $S_v \gets S \in \Pi$ : $ v \in S$
+          \State PQ, \texttt{canBeMerged}, $\tilde{E}$ $\gets$ \textsc{UpdateNeighbors}($u,v$)
+        %   \State mergeDoubleEdges($u,v$) \Comment{Update PQ, $E_\dagger, \mathcal{G}'$}
+
+        %   \State Update costs of double edges;
+        %   \State Propagate constrained flags of double edges;
+          \State $\tilde{V} \gets \tilde{V} \setminus \{ v\}$, $\quad \tilde{E} \gets \tilde{E} \setminus \{ e_{uv}\}$ \Comment{Update contracted graph}
+        %   \State $ S_u \gets S_u \cup S_v$
+          \State \texttt{UF}.merge($u,v$) \Comment{Merge clusters, $\mathcal{O}(\alpha(M))$}
+          % \For{every new double edge}
+          %   \State Delete double edges
+          %   \State Insert new one with updated cost
+          % \EndFor
+        \ElsIf{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
+          \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False} \Comment{Constrain the two clusters}
+        \EndIf
+      \EndWhile
+      \State
+    %   \State
+      \Return Union-find structure \texttt{UF}
+      % \State
+    % \EndProcedure
+  \end{algorithmic}
+  \hspace*{1.5cm} 
+    \begin{algorithmic}[1]
+    \Function{UpdateNeighbors}{$u,v$}
+      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
+      % \State $\mathcal{N}_u = \{ t \in V' | e_{ut}\in E'  \}$; $\mathcal{N}_v = \{ t \in V' | e_{vt}\in E'  \}$ 
+      \For{$t \in \mathcal{N}_v$ } \Comment{Loop over neighbors in $\tilde{\mathcal{G}}$ of deleted node $v$}
+        \State $\tilde{E} \gets \tilde{E} \setminus \{e_{vt}\}$
+        \State $\tilde{w}_{vt} \gets$ PQ.delete($e_{vt}$) \Comment{$\mathcal{O}(\log M)$}
+        \State \texttt{canBeMerged}$[e_{ut}] \gets$ \texttt{canBeMerged}$[e_{ut}]$ \textbf{and} \texttt{canBeMerged}$[e_{vt}]$
+        \If{$t \in \mathcal{N}_u$ }\Comment{$t$ is a common neighbor of $u$ and $v$}
+          \State $\tilde{w}_{ut} \gets$ PQ.delete($e_{ut}$)  \Comment{$\mathcal{O}(\log M)$}
+          \State PQ.push($ |f(\tilde{w}_{ut}, \tilde{w}_{vt})|, e_{ut}$) \Comment{$\mathcal{O}(\log M)$  }
+        % \EndIf
+        \Else
+          \State $\tilde{E} \gets \tilde{E} \cup \{e_{ut}\}$
+          \State PQ.push($ |\tilde{w}_{vt}|, e_{ut}$) \Comment{$\mathcal{O}(\log M)$}
+        \EndIf
+      \EndFor
+      \State
+    %   \State
+      \Return PQ, \texttt{canBeMerged}, $\tilde{E}$
+    %   % \State
+    \EndFunction
+  \end{algorithmic}
+  \label{detailed_alg}
+\end{algorithm}
 \begin{figure}
         \centering
-\begin{minipage}{0.45\textwidth}
-\centering
-        \includegraphics[width=0.85\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
-
-    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise.
-Blue pixels represent boundary evidence.
-Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
-    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
-    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
-    }
-    \label{fig:noisy_affs}
-    \end{minipage}\hfill
 \begin{minipage}{0.49\textwidth}
@@
         \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
-\captionof{figure}{ 
-{\small Example of edge contraction.
+% \captionof{figure}{ 
+% {\small Example of edge contraction.
 First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars).
@@
 }
-\label{fig:edge_contraction_and_contr_graph}  }
+% \label{fig:edge_contraction_and_contr_graph}  }
+    \end{minipage} \hfill
+\begin{minipage}[T]{0.48\textwidth}
+    \centering
+    \scriptsize
+                \begin{tabular}[b]{r | l }
+            \toprule
+            % \multicolumn{2}{c||}{}  &   & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
+            % \cmidrule(l{.15em}){4-5}
+            % \cline{4-5}
+            % \multicolumn{2}{c||}{} & \textbf{Unsigned graphs} &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
+            Linkage criteria & Update rule $f$ \\        
+            \midrule
+            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} \\ 
+            \makecell[r]{Absolute \\Maximum:} & \thead[l]{
+            $
+            f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
+            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
+            \tilde{\cost}_2 & \text{otherwise}
+             \end{cases} 
+            $}
+               \\ 
+            \makecell[r]{Average:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                 \\ 
+            Maximum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} \\
+            Minimum:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} 
+        \end{tabular}
+    % \captionof{table}{}
+    \label{tab:linkage_and_update_rules}
 \end{minipage}
+\caption{ 
+\textbf{Left:} Example of edge contraction.
+First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars).
+Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$.
+In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$.
+In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from the edge contraction are replaced by a single edge with updated interaction.
+\textbf{Right:} The table lists the update rules $f(\tilde{\cost}_1, \tilde{\cost}_2)$ associated to the linkage criteria of Table \ref{tab:linkage-criteria} and that are used to efficiently update the interactions between clusters.
+\TODO{Update figure}}
+\label{fig:edge_contraction_and_contr_graph}  
 \end{figure}
@@
 \section{Supplementary Material}
-During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.  % given by the linkage criterion defined in Sec. \ref{sec:notation} and
-Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, with $\tilde{V} \subseteq V$ such that node $u\in \tilde{V}$ represents the associated cluster $S_u \in \Pi$.
+\subsection{Implementation details and complexity of \algname{}}
+
+% During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.  % given by the linkage criterion defined in Sec. \ref{sec:notation} and
+% Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, with $\tilde{V} \subseteq V$ such that node $u\in \tilde{V}$ represents the associated cluster $S_u \in \Pi$.
 Edges in $\tilde{E}$ are defined by adjacency-relationships between clusters and edge weights $\tilde{\cost}_{uv}$ represent inter-cluster interactions $\interact(S_u,S_v)$.
@@
 
+\subsection{Equivalence between Mutex Watershed and \emph{Absolute Maximum} linkage}
+
 \begin{itemize}
@@
 \end{itemize}
+
+\begin{figure}
+\centering
+        \includegraphics[width=0.45\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
+
+    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise.
+Blue pixels represent boundary evidence.
+Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
+    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
+    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
+    }
+    \label{fig:noisy_affs}
+\end{figure}
 
@@
 
-\begin{table*}
-    \centering
-    \begin{subtable}[t!]{0.98\textwidth}\centering
-        \begin{tabular}{c| c | c| c | c | c | c | c}
-Update rule & \makecell{Use Cannot-Link\\Constraints} & Log-costs & \makecell{Multicut objective} & Runtime (s) & ARAND & VI-merge & VI-split\\ \midrule\midrule
-% \textbf{mean} & False & \textbf{-102739991} & {\color{Orange} 3797 } & {\color{ForestGreen} \textbf{0.0708} } & {\color{ForestGreen} 0.286 } & {\color{ForestGreen} 0.428 } \\
-% % mean & False & -102730208 & {\color{Orange} 2562 } & {\color{ForestGreen} 0.0715 } & {\color{ForestGreen} 0.292 } & {\color{ForestGreen} 0.423 } \\
-% MutexWatershed & False & -102313957 & {\color{ForestGreen} 830 } & {\color{ForestGreen} 0.0754 } & {\color{ForestGreen} 0.291 } & {\color{Orange} 0.471 } \\
-% sum & False & -101846418 & {\color{Red} 12681 } & {\color{Orange} 0.1623 } & {\color{Orange} 0.427 } & {\color{ForestGreen} 0.427 } \\
-% % sum & False & -101732952 & {\color{Red} 12287 } & {\color{Orange} 0.1624 } & {\color{Orange} 0.436 } & {\color{ForestGreen} 0.390 } \\
-% sum & True & -101487448 & {\color{Red} 8497 } & {\color{Orange} 0.1626 } & {\color{Orange} 0.428 } & {\color{ForestGreen} 0.414 } \\
-% % sum & True & -100745943 & {\color{Red} 13361 } & {\color{Orange} 0.1574 } & {\color{Orange} 0.410 } & {\color{Orange} 0.451 } \\
-% mean & True & -100279671 & {\color{Orange} 4713 } & {\color{Orange} 0.1353 } & {\color{ForestGreen} 0.265 } & {\color{Red} 0.717 } \\
-% % mean & True & -99416111 & {\color{Orange} 3445 } & {\color{Orange} 0.1761 } & {\color{ForestGreen} 0.260 } & {\color{Red} 0.822 } \\
-% max & True & -98143342 & {\color{Red} 7153 } & {\color{ForestGreen} 0.0792 } & {\color{ForestGreen} 0.292 } & {\color{Orange} 0.496 } \\
-% max & False & -48601637 & {\color{ForestGreen} 102 } & {\color{Red} 0.9389 } & {\color{Red} 5.738 } & {\color{ForestGreen} 0.035 } \\
-% min & False & 210377447 & {\color{ForestGreen} 493 } & {\color{Red} 0.9263 } & {\color{ForestGreen} 0.233 } & {\color{Red} 4.745 } \\
-% min & True & 211183545 & {\color{ForestGreen} 692 } & {\color{Red} 0.9221 } & {\color{ForestGreen} 0.232 } & {\color{Red} 4.714 } \\
-mean & False & True & -93152163 & {\color{Orange} 3666 } & {\color{Orange} 0.1204 } & {\color{ForestGreen} 0.231 } & {\color{Red} 0.641 } \\
-sum & False & True & -93142805 & {\color{Red} 16154 } & {\color{ForestGreen} 0.0893 } & {\color{Orange} 0.301 } & {\color{Orange} 0.514 } \\
-mean & False &  & -93072127 & {\color{Orange} 3168 } & {\color{Orange} 0.1284 } & {\color{ForestGreen} 0.234 } & {\color{Red} 0.642 } \\
-sum & True & True & -92936797 & {\color{Red} 21605 } & {\color{ForestGreen} 0.0910 } & {\color{ForestGreen} 0.293 } & {\color{Orange} 0.532 } \\
-MutexWatershed & False &  & -92704851 & {\color{ForestGreen} 632 } & {\color{Orange} 0.1347 } & {\color{ForestGreen} 0.231 } & {\color{Red} 0.751 } \\
-sum & True & False & -91444880 & {\color{Red} 26842 } & {\color{Red} 0.2085 } & {\color{Red} 0.572 } & {\color{Orange} 0.489 } \\
-mean & True & True & -90660193 & {\color{Orange} 4114 } & {\color{Orange} 0.1655 } & {\color{ForestGreen} 0.213 } & {\color{Red} 1.011 } \\
-mean & True &  & -88260595 & {\color{Orange} 4393 } & {\color{Red} 0.2017 } & {\color{ForestGreen} 0.208 } & {\color{Red} 1.155 } \\
-max & True &  & -81432464 & {\color{Red} 7759 } & {\color{Orange} 0.1653 } & {\color{ForestGreen} 0.236 } & {\color{Red} 0.792 } \\
-max & False &  & -37045939 & {\color{ForestGreen} 134 } & {\color{Red} 0.9150 } & {\color{Red} 5.691 } & {\color{ForestGreen} 0.013 } \\
-min & False &  & 213670839 & {\color{ForestGreen} 600 } & {\color{Red} 0.9330 } & {\color{ForestGreen} 0.207 } & {\color{Red} 4.880 } \\
-min & True &  & 214747429 & {\color{ForestGreen} 852 } & {\color{Red} 0.9314 } & {\color{ForestGreen} 0.202 } & {\color{Red} 4.887 } \\
+% \begin{table*}
+%     \centering
+%     \begin{subtable}[t!]{0.98\textwidth}\centering
+%         \begin{tabular}{c| c | c| c | c | c | c | c}
+% Update rule & \makecell{Use Cannot-Link\\Constraints} & Log-costs & \makecell{Multicut objective} & Runtime (s) & ARAND & VI-merge & VI-split\\ \midrule\midrule
+% mean & False & True & -93152163 & {\color{Orange} 3666 } & {\color{Orange} 0.1204 } & {\color{ForestGreen} 0.231 } & {\color{Red} 0.641 } \\
+% sum & False & True & -93142805 & {\color{Red} 16154 } & {\color{ForestGreen} 0.0893 } & {\color{Orange} 0.301 } & {\color{Orange} 0.514 } \\
+% mean & False &  & -93072127 & {\color{Orange} 3168 } & {\color{Orange} 0.1284 } & {\color{ForestGreen} 0.234 } & {\color{Red} 0.642 } \\
+% sum & True & True & -92936797 & {\color{Red} 21605 } & {\color{ForestGreen} 0.0910 } & {\color{ForestGreen} 0.293 } & {\color{Orange} 0.532 } \\
+% MutexWatershed & False &  & -92704851 & {\color{ForestGreen} 632 } & {\color{Orange} 0.1347 } & {\color{ForestGreen} 0.231 } & {\color{Red} 0.751 } \\
+% sum & True & False & -91444880 & {\color{Red} 26842 } & {\color{Red} 0.2085 } & {\color{Red} 0.572 } & {\color{Orange} 0.489 } \\
+% mean & True & True & -90660193 & {\color{Orange} 4114 } & {\color{Orange} 0.1655 } & {\color{ForestGreen} 0.213 } & {\color{Red} 1.011 } \\
+% mean & True &  & -88260595 & {\color{Orange} 4393 } & {\color{Red} 0.2017 } & {\color{ForestGreen} 0.208 } & {\color{Red} 1.155 } \\
+% max & True &  & -81432464 & {\color{Red} 7759 } & {\color{Orange} 0.1653 } & {\color{ForestGreen} 0.236 } & {\color{Red} 0.792 } \\
+% max & False &  & -37045939 & {\color{ForestGreen} 134 } & {\color{Red} 0.9150 } & {\color{Red} 5.691 } & {\color{ForestGreen} 0.013 } \\
+% min & False &  & 213670839 & {\color{ForestGreen} 600 } & {\color{Red} 0.9330 } & {\color{ForestGreen} 0.207 } & {\color{Red} 4.880 } \\
+% min & True &  & 214747429 & {\color{ForestGreen} 852 } & {\color{Red} 0.9314 } & {\color{ForestGreen} 0.202 } & {\color{Red} 4.887 } \\
 
-        \end{tabular}
-        % \caption{Linkage criteria}
-    \end{subtable} 
-    \caption{Comparison of update rules on crop of cremi sample B (sorted by multicut energy) \TODO{Reduce insane amount of numbers.
+%         \end{tabular}
+%         % \caption{Linkage criteria}
+%     \end{subtable} 
+%     \caption{Comparison of update rules on crop of cremi sample B (sorted by multicut energy) \TODO{Reduce insane amount of numbers.
 Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime.
 Invert ARAND to make it consistent with the plots} }
-    \label{tab:results_cremi_crop_C}
-\end{table*}
+%     \label{tab:results_cremi_crop_C}
+% \end{table*}
 
-\begin{table*}
-    \centering
-    \begin{subtable}[t!]{0.98\textwidth}\centering
-        \begin{tabular}{c| c | c| c | c | c | c | c}
-Update rule & \makecell{Use Cannot-Link\\Constraints} & Log-costs & \makecell{Multicut objective} & Runtime (s) & ARAND & VI-merge & VI-split\\ \midrule\midrule
-mean & False &  & -102739991 & {\color{Orange} 3797 } & {\color{ForestGreen} 0.9292 } & {\color{ForestGreen} 0.286 } & {\color{ForestGreen} 0.428 } \\
-mean & False &  & -102730208 & {\color{Orange} 2562 } & {\color{ForestGreen} 0.9285 } & {\color{ForestGreen} 0.292 } & {\color{ForestGreen} 0.423 } \\
-MutexWatershed & False &  & -102313957 & {\color{ForestGreen} 830 } & {\color{ForestGreen} 0.9246 } & {\color{ForestGreen} 0.291 } & {\color{Orange} 0.471 } \\
-max & True &  & -98143342 & {\color{Red} 7153 } & {\color{ForestGreen} 0.9208 } & {\color{ForestGreen} 0.292 } & {\color{Orange} 0.496 } \\
-mean & True &  & -100279671 & {\color{Orange} 4713 } & {\color{Orange} 0.8647 } & {\color{ForestGreen} 0.265 } & {\color{Red} 0.717 } \\
-sum & True &  & -100745943 & {\color{Red} 13361 } & {\color{Orange} 0.8426 } & {\color{Orange} 0.410 } & {\color{Orange} 0.451 } \\
-sum & False &  & -101846418 & {\color{Red} 12681 } & {\color{Orange} 0.8377 } & {\color{Orange} 0.427 } & {\color{ForestGreen} 0.427 } \\
-sum & False &  & -101732952 & {\color{Red} 12287 } & {\color{Orange} 0.8376 } & {\color{Orange} 0.436 } & {\color{ForestGreen} 0.390 } \\
-sum & True &  & -101487448 & {\color{Red} 8497 } & {\color{Orange} 0.8374 } & {\color{Orange} 0.428 } & {\color{ForestGreen} 0.414 } \\
-mean & True &  & -99416111 & {\color{Orange} 3445 } & {\color{Orange} 0.8239 } & {\color{ForestGreen} 0.260 } & {\color{Red} 0.822 } \\
-min & True &  & 211183545 & {\color{ForestGreen} 692 } & {\color{Red} 0.0779 } & {\color{ForestGreen} 0.232 } & {\color{Red} 4.714 } \\
-min & False &  & 210377447 & {\color{ForestGreen} 493 } & {\color{Red} 0.0737 } & {\color{ForestGreen} 0.233 } & {\color{Red} 4.745 } \\
-max & False &  & -48601637 & {\color{ForestGreen} 102 } & {\color{Red} 0.0611 } & {\color{Red} 5.738 } & {\color{ForestGreen} 0.035 } \\
+% \begin{table*}
+%     \centering
+%     \begin{subtable}[t!]{0.98\textwidth}\centering
+%         \begin{tabular}{c| c | c| c | c | c | c | c}
+% Update rule & \makecell{Use Cannot-Link\\Constraints} & Log-costs & \makecell{Multicut objective} & Runtime (s) & ARAND & VI-merge & VI-split\\ \midrule\midrule
+% mean & False &  & -102739991 & {\color{Orange} 3797 } & {\color{ForestGreen} 0.9292 } & {\color{ForestGreen} 0.286 } & {\color{ForestGreen} 0.428 } \\
+% mean & False &  & -102730208 & {\color{Orange} 2562 } & {\color{ForestGreen} 0.9285 } & {\color{ForestGreen} 0.292 } & {\color{ForestGreen} 0.423 } \\
+% MutexWatershed & False &  & -102313957 & {\color{ForestGreen} 830 } & {\color{ForestGreen} 0.9246 } & {\color{ForestGreen} 0.291 } & {\color{Orange} 0.471 } \\
+% max & True &  & -98143342 & {\color{Red} 7153 } & {\color{ForestGreen} 0.9208 } & {\color{ForestGreen} 0.292 } & {\color{Orange} 0.496 } \\
+% mean & True &  & -100279671 & {\color{Orange} 4713 } & {\color{Orange} 0.8647 } & {\color{ForestGreen} 0.265 } & {\color{Red} 0.717 } \\
+% sum & True &  & -100745943 & {\color{Red} 13361 } & {\color{Orange} 0.8426 } & {\color{Orange} 0.410 } & {\color{Orange} 0.451 } \\
+% sum & False &  & -101846418 & {\color{Red} 12681 } & {\color{Orange} 0.8377 } & {\color{Orange} 0.427 } & {\color{ForestGreen} 0.427 } \\
+% sum & False &  & -101732952 & {\color{Red} 12287 } & {\color{Orange} 0.8376 } & {\color{Orange} 0.436 } & {\color{ForestGreen} 0.390 } \\
+% sum & True &  & -101487448 & {\color{Red} 8497 } & {\color{Orange} 0.8374 } & {\color{Orange} 0.428 } & {\color{ForestGreen} 0.414 } \\
+% mean & True &  & -99416111 & {\color{Orange} 3445 } & {\color{Orange} 0.8239 } & {\color{ForestGreen} 0.260 } & {\color{Red} 0.822 } \\
+% min & True &  & 211183545 & {\color{ForestGreen} 692 } & {\color{Red} 0.0779 } & {\color{ForestGreen} 0.232 } & {\color{Red} 4.714 } \\
+% min & False &  & 210377447 & {\color{ForestGreen} 493 } & {\color{Red} 0.0737 } & {\color{ForestGreen} 0.233 } & {\color{Red} 4.745 } \\
+% max & False &  & -48601637 & {\color{ForestGreen} 102 } & {\color{Red} 0.0611 } & {\color{Red} 5.738 } & {\color{ForestGreen} 0.035 } \\
 
-        \end{tabular}
-        % \caption{Linkage criteria}
-    \end{subtable} 
-    \caption{Comparison of update rules on crop of cremi sample C (sorted by multicut energy) \TODO{Reduce insane amount of numbers.
+%         \end{tabular}
+%         % \caption{Linkage criteria}
+%     \end{subtable} 
+%     \caption{Comparison of update rules on crop of cremi sample C (sorted by multicut energy) \TODO{Reduce insane amount of numbers.
 Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime.
 Invert ARAND to make it consistent with the plots} }
-    \label{tab:results_cremi_crop_C}
-\end{table*}
+%     \label{tab:results_cremi_crop_C}
+% \end{table*}
 
-\begin{table}
-    \centering
-    \begin{subtable}[t!]{0.5\textwidth}\centering
-        \begin{tabular}{M{0.1\textwidth}| c| c| c | c }
-        \thead{Update \\rule} & \thead{Use Cannot-Link\\ Constraints} & \thead{Bias \\factor $\beta$} & \thead{AP} & \thead{AP 50\%} \\ \midrule\midrule
-\multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
- &Yes & 0.55  & {\color{Orange} 0.319 } & {\color{Orange} 0.527 } \\\midrule
-Abs. max. &- & 0.45  & {\color{Orange} 0.321 } & {\color{ForestGreen} 0.531 } \\\midrule
-\multirow{2}{*}{Mean} &No & 0.35  & {\color{ForestGreen} 0.343 } & {\color{ForestGreen} 0.552 } \\
- &Yes & 0.25  & {\color{Orange} 0.339 } & {\color{ForestGreen} 0.548 } \\\midrule
-\multirow{2}{*}{Max} &No & 0.85 & {\color{Red} 0.243 } & {\color{Red} 0.444 } \\
- &Yes & 0.50  & {\color{Orange} 0.325 } & {\color{ForestGreen} 0.530 } \\\midrule
-\multirow{2}{*}{Min} &No & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\
- &Yes & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\\midrule
-\cite{liu2018affinity} &-  & -  & {\color{ForestGreen} 0.341 } & {\color{ForestGreen} 0.547 } \\
-% MEAN & 0.35 & True & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
-% MEAN & 0.30 & False & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5457 } \\
-% MEAN & 0.40 & - & {\color{ForestGreen} 0.3402 } & {\color{ForestGreen} 0.5502 } \\
-% MEANconstr & 0.30 & False & {\color{Orange} 0.3344 } & {\color{ForestGreen} 0.5469 } \\
-% MEAN & 0.45 & - & {\color{Orange} 0.3333 } & {\color{ForestGreen} 0.5438 } \\
-% MEAN & 0.50 & - & {\color{Orange} 0.3255 } & {\color{ForestGreen} 0.5341 } \\
-% greedyFixation & 0.50 & - & {\color{Orange} 0.3180 } & {\color{Orange} 0.5155 } \\
-% MEANconstr & 0.20 & False & {\color{Orange} 0.3161 } & {\color{Orange} 0.5136 } \\
-% MutexWatershed & 0.50 & - & {\color{Orange} 0.3158 } & {\color{Orange} 0.5246 } \\
-% MEANconstr & 0.35 & False & {\color{Orange} 0.3154 } & {\color{Orange} 0.5269 } \\
-% greedyFixation & 0.60 & - & {\color{Orange} 0.3135 } & {\color{Orange} 0.5196 } \\
-% GAEC & 0.50 & - & {\color{Orange} 0.3112 } & {\color{Orange} 0.5085 } \\
-% SingleLinkagePlusCLC & 0.45 & - & {\color{Orange} 0.3109 } & {\color{Orange} 0.5134 } \\
-% GAEC & 0.60 & - & {\color{Orange} 0.3100 } & {\color{Orange} 0.5120 } \\
-% greedyFixation & 0.65 & - & {\color{Orange} 0.3056 } & {\color{Orange} 0.5063 } \\
-% greedyFixation & 0.45 & - & {\color{Orange} 0.3045 } & {\color{Red} 0.4989 } \\
-% GAEC & 0.65 & - & {\color{Orange} 0.3035 } & {\color{Orange} 0.5072 } \\
-% GAEC & 0.45 & - & {\color{Orange} 0.3008 } & {\color{Red} 0.4956 } \\
-% MEANconstr & 0.35 & True & {\color{Red} 0.3000 } & {\color{Orange} 0.5140 } \\
-% MEANconstr & 0.40 & False & {\color{Red} 0.2983 } & {\color{Orange} 0.5076 } \\
-% GAEC & 0.70 & - & {\color{Red} 0.2943 } & {\color{Red} 0.4989 } \\
-% SingleLinkagePlusCLC & 0.55 & - & {\color{Red} 0.2942 } & {\color{Orange} 0.5074 } \\
-% greedyFixation & 0.70 & - & {\color{Red} 0.2919 } & {\color{Red} 0.4906 } \\
-% GAEC & 0.75 & - & {\color{Red} 0.2793 } & {\color{Red} 0.4784 } \\
-% greedyFixation & 0.75 & - & {\color{Red} 0.2750 } & {\color{Red} 0.4707 } \\
-% SingleLinkagePlusCLC & 0.60 & - & {\color{Red} 0.2681 } & {\color{Red} 0.4744 } \\
-% GAEC & 0.35 & True & {\color{Red} 0.2590 } & {\color{Red} 0.4450 } \\
-% greedyFixation & 0.35 & - & {\color{Red} 0.2587 } & {\color{Red} 0.4484 } \\
-% MutexWatershed & 0.40 & - & {\color{Red} 0.2562 } & {\color{Red} 0.4505 } \\
-% MEANconstr & 0.50 & - & {\color{Red} 0.2507 } & {\color{Red} 0.4443 } \\
-% SingleLinkagePlusCLC & 0.40 & - & {\color{Red} 0.2490 } & {\color{Red} 0.4411 } \\
-% SingleLinkagePlusCLC & 0.65 & - & {\color{Red} 0.2489 } & {\color{Red} 0.4401 } \\
-% greedyFixation & 0.35 & - & {\color{Red} 0.2438 } & {\color{Red} 0.4297 } \\
-% GAEC & 0.35 & False & {\color{Red} 0.2371 } & {\color{Red} 0.4187 } \\
-% SingleLinkage & 0.80 & - & {\color{Red} 0.2336 } & {\color{Red} 0.4265 } \\
-% SingleLinkagePlusCLC & 0.70 & - & {\color{Red} 0.2285 } & {\color{Red} 0.4045 } \\
-% SingleLinkage & 0.75 & - & {\color{Red} 0.2265 } & {\color{Red} 0.4065 } \\
-% MutexWatershed & 0.35 & - & {\color{Red} 0.2253 } & {\color{Red} 0.4004 } \\
-% SingleLinkage & 0.70 & - & {\color{Red} 0.2213 } & {\color{Red} 0.3947 } \\
-% SingleLinkagePlusCLC & 0.35 & - & {\color{Red} 0.2213 } & {\color{Red} 0.3954 } \\
-% SingleLinkage & 0.65 & - & {\color{Red} 0.2177 } & {\color{Red} 0.3889 } \\
-% SingleLinkage & 0.60 & - & {\color{Red} 0.2116 } & {\color{Red} 0.3842 } \\
-% SingleLinkagePlusCLC & 0.75 & - & {\color{Red} 0.2093 } & {\color{Red} 0.3785 } \\
-% SingleLinkage & 0.55 & - & {\color{Red} 0.1987 } & {\color{Red} 0.3700 } \\
-% SingleLinkage & 0.50 & - & {\color{Red} 0.1952 } & {\color{Red} 0.3659 } \\
-% SingleLinkage & 0.35 & - & {\color{Red} 0.1852 } & {\color{Red} 0.3463 } \\
+% \begin{table}
+%     \centering
+%     \begin{subtable}[t!]{0.5\textwidth}\centering
+%         \begin{tabular}{M{0.1\textwidth}| c| c| c | c }
+%         \thead{Update \\rule} & \thead{Use Cannot-Link\\ Constraints} & \thead{Bias \\factor $\beta$} & \thead{AP} & \thead{AP 50\%} \\ \midrule\midrule
+% \multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
+%  &Yes & 0.55  & {\color{Orange} 0.319 } & {\color{Orange} 0.527 } \\\midrule
+% Abs. max. &- & 0.45  & {\color{Orange} 0.321 } & {\color{ForestGreen} 0.531 } \\\midrule
+% \multirow{2}{*}{Mean} &No & 0.35  & {\color{ForestGreen} 0.343 } & {\color{ForestGreen} 0.552 } \\
+%  &Yes & 0.25  & {\color{Orange} 0.339 } & {\color{ForestGreen} 0.548 } \\\midrule
+% \multirow{2}{*}{Max} &No & 0.85 & {\color{Red} 0.243 } & {\color{Red} 0.444 } \\
+%  &Yes & 0.50  & {\color{Orange} 0.325 } & {\color{ForestGreen} 0.530 } \\\midrule
+% \multirow{2}{*}{Min} &No & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\
+%  &Yes & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\\midrule
+% \cite{liu2018affinity} &-  & -  & {\color{ForestGreen} 0.341 } & {\color{ForestGreen} 0.547 } \\
+%         \end{tabular}
+%         % \caption{Linkage criteria}
+%     \end{subtable} 
+%     \caption{Results on cityscapes validation set (with finetuned affinities). \TODO{Reformat in the usual form, delete colors, less digits}}
+%     \label{tab:results_cityscapes_full}
+% \end{table}
 
-        \end{tabular}
-        % \caption{Linkage criteria}
-    \end{subtable} 
-    \caption{Results on cityscapes validation set (with finetuned affinities). \TODO{Reformat in the usual form, delete colors, less digits}}
-    \label{tab:results_cityscapes_full}
-\end{table}
+% \begin{algorithm}[t]
+%   \caption{Generalized Algorithm for Signed Graphs Agglomerative Clustering}
+%    \hspace*{\algorithmicindent} \textbf{Inputs:} Graph $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes; boolean variable {\color{blue}\texttt{addCannotLink}}  \\
+%   \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$\\
+%   \hspace*{\algorithmicindent} 
+%   \begin{algorithmic}[1]
 
-\begin{algorithm}[t]
-  \caption{Generalized Algorithm for Signed Graphs Agglomerative Clustering}
-   \hspace*{\algorithmicindent} \textbf{Inputs:} Graph $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes; boolean variable {\color{blue}\texttt{addCannotLink}}  \\
-  \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$\\
-  \hspace*{\algorithmicindent} 
-  \begin{algorithmic}[1]
-      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ and contracted graph $\tilde{\mathcal{G}}_\Pi \gets \mathcal{G}$
-      \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
-      \State Sort edges in priority queue (PQ) in descending order of priority $|\cost_e|=|w^+_e - w^-_e|$ 
-      \State
-      \While{PQ is \textbf{not} empty}
-        \State Pop edge $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ with highest absolute interaction $|\tilde{\cost}|$
-        \If{({\color{ForestGreen}\textbf{$\tilde{\cost} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
-          \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
-          \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
-            % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
-            \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
-          \EndFor
-        \EndIf
-        \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
-          \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
-        \EndIf
-      \EndWhile
-      \State
-      \Return $\Pi$
-  \end{algorithmic}
-  \label{main_alg_suppl}
-\end{algorithm}
-
-\begin{algorithm}
-  \caption{Graph Agglomerative Clustering}
-\setlength{\parindent}{\algorithmicindent} \textbf{Inputs:}
-     \begin{itemize}[leftmargin=1.3cm,topsep=0.1pt,itemsep=-1.ex]
-    %  \setlength\itemsep{0.em}
-   \item $\mathcal{G}(V,E)$ with $|V|=N$, $|E|=M$
-   \item signed edge weights $w:\,E\rightarrow\mathbb{R}$
-   \item {\color{blue}addMustNotLink} $\in \{ True, False\}$
-   \end{itemize}
-   \vspace{0.4em}
-
-\setlength{\parindent}{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$
-
-%   \hspace*{\algorithmicindent} \textbf{Inputs:} $\mathcal{G}(V,E)$ with signed costs $w:\,E\rightarrow\mathbb{R}$. \\
-%   Prova \\
-%   \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$\\
-
-  \hspace*{\algorithmicindent} 
-  \begin{algorithmic}[1]
-
-    % \Procedure{GraphEdgeContr}{{\color{blue}bool \emph{addConstraints}}}
-      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
-      \State $\mathcal{G}'(V', E') \gets \mathcal{G}(V, E)$  \Comment{Contracted graph}
-    %   \State PQ $\gets$ Sort $e\in E$ in descending order of $|w_e|$
-        \State PQ.push$(|w_e|, w_e, e) \quad \forall e \in E $  \Comment{Sort edges by $|w_e|$}
-
-      \State $\Pi \gets \{ \{v_1\}, ..., \{v_N\} \}$ \Comment{Initial clustering}
-      \State $E_\dagger \gets \{\}$ \Comment{Set of must-not-link edges}
-    %   \State PQ.push$(e,  ) \quad \forall e \in E $  
-    \State
-      \While{PQ is \textbf{not} empty}
-        \State $|\tilde{w}|, \tilde{w}, e_{uv} \gets $ PQ.popHighest()
-        \If{ $e_{uv} \notin E' $} 
-            \State \textbf{continue}
-        \EndIf
-        \If{({\color{ForestGreen}\textbf{$\tilde{w} > 0$}}) \textbf{and} ($e_{uv} \notin E_\dagger$)}
-        %   \State $u,v \gets u,v \in V' : $
-        %   \State $S_u \gets S \in \Pi$ : $ u \in S$
-        %   \State $S_v \gets S \in \Pi$ : $ v \in S$
-          \State PQ, $\,E_\dagger,\,\, E' \gets$ \textsc{deleteDoubleEdges}($u,v$)
-        %   \State mergeDoubleEdges($u,v$) \Comment{Update PQ, $E_\dagger, \mathcal{G}'$}
-
-        %   \State Update costs of double edges;
-        %   \State Propagate constrained flags of double edges;
-          \State $V' \gets V' \setminus \{ v\}$, $\quad E' \gets E' \setminus \{ e_{uv}\}$
-        %   \State $ S_u \gets S_u \cup S_v$
-          \State $\Pi \gets \Pi \cup \{ S_u^\Pi \cup S_v^\Pi \} \setminus \{ S_u^\Pi, S_v^\Pi \}$
-          % \For{every new double edge}
-          %   \State Delete double edges
-          %   \State Insert new one with updated cost
+%       \State Init. clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ and contracted graph $\tilde{\mathcal{G}}_\Pi \gets \mathcal{G}$
+%       \State Init. \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
+%       \State Sort edges in priority queue (PQ) in descending order of priority $|\cost_e|=|w^+_e - w^-_e|$ 
+%       \State
+%       \While{PQ is \textbf{not} empty}
+%         \State Pop edge $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ with highest absolute interaction $|\tilde{\cost}|$
+%         \If{({\color{ForestGreen}\textbf{$\tilde{\cost} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
+%           \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
+%           \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
+%             % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
+%             \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
 %           \EndFor
-        \EndIf
-        \If{({\color{red}\textbf{$\tilde{w} \leq 0$}}) \textbf{and} {\color{blue}addMustNotLink}}
-          \State $ E_\dagger \gets E_\dagger \cup \{e_{uv} \} $
-        \EndIf
-      \EndWhile
-      \State
+%         \EndIf
+%         \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
+%           \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
+%         \EndIf
+%       \EndWhile
 %       \State
-      \Return $\Pi$
-      % \State
-    % \EndProcedure
-
-  \end{algorithmic}
-  \hspace*{2cm} 
-    \begin{algorithmic}[1]
-
-    \Function{DeleteDoubleEdges}{$u,v$}
-      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
-      \State $\mathcal{N}_u = \{ t \in V' | e_{ut}\in E'  \}$
-      \State $\mathcal{N}_v = \{ t \in V' | e_{vt}\in E'  \}$
-      \For{$t \in \mathcal{N}_u  \cap \mathcal{N}_v$ }
-        \State $|\tilde{w}_1|, \tilde{w}_1, e_1 \gets $ PQ.pop($e_{ut}$)
-        \State $|\tilde{w}_2|, \tilde{w}_2, e_2 \gets $ PQ.pop($e_{vt}$)
-        % \State $e_1, e_2 \gets e_{ut}, e_{vt}$
-        \State $E' \gets E' \setminus \{ e_2\}$ %\Comment{Delete double edge}
-        \If{$e_2 \in E_\dagger $} \Comment{Propagate must-not-link}
-            \State $ E_\dagger \gets E_\dagger \cup \{e_1 \} $
-        \EndIf
-        % \State $\tilde{w}_1, \tilde{w}_2 \gets $ PQ.pop($e_1$), PQ.pop($e_2$)
-        \State $\tilde{w}_{\mathrm{new}} \gets$ \textsc{linkageCriteria}$(\tilde{w}_1, \tilde{w}_2)$
-        \State PQ.push($|\tilde{w}_{\mathrm{new}}|$, $\tilde{w}_{\mathrm{new}}$,  $e_1$)
-
-      \EndFor
-
-      \State
-    %   \State
-      \Return PQ, $E_\dagger, E'$
-    %   % \State
-
-    \EndFunction
-
-  \end{algorithmic}
-
-\end{algorithm}
+%       \Return $\Pi$
+%   \end{algorithmic}
+%   \label{main_alg_suppl}
+% \end{algorithm}

### 2019-05-15 chapters/supplementary.tex
Update impl. and complexity section

@@
 % !TEX root = ../agglo_clust_review.tex
+
+\section{Supplementary Material}
 
@@
   \label{detailed_alg}
+  % \caption{where $\alpha$ is the slowly growing inverse Ackerman function}
 \end{algorithm}
@@
     % \captionof{table}{}
-    \label{tab:linkage_and_update_rules}
+    % \label{tab:linkage_and_update_rules}
 \end{minipage}
@@
 \textbf{Right:} The table lists the update rules $f(\tilde{\cost}_1, \tilde{\cost}_2)$ associated to the linkage criteria of Table \ref{tab:linkage-criteria} and that are used to efficiently update the interactions between clusters.
-\TODO{Update figure}}
+\TODO{Update notation figure}}
 \label{fig:edge_contraction_and_contr_graph}  
@@
 
-\section{Supplementary Material}
 \subsection{Implementation details and complexity of \algname{}}
@@
 Edges in $\tilde{E}$ are defined by adjacency-relationships between clusters and edge weights $\tilde{\cost}_{uv}$ represent inter-cluster interactions $\interact(S_u,S_v)$.
-
-\paragraph{Update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.
+\paragraph*{Update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed, as shown in Algorithm \ref{main_alg}.
 % given by the linkage criterion defined in Sec.
@@
 Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that $\tilde{V} \subseteq V$ and each node $u\in \tilde{V}$ represents the cluster $S_u \in \Pi$ including $u\in V$.
-Edges in $\tilde{E}$ represent adjacency-relationships between clusters and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$.
+Edges in $\tilde{E}$ represent adjacency-relationships between clusters
+and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$. 
 For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$.
-Thus, we can easily recompute these interactions by using a simple \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$.
-As an example, given the single-linkage criterion defined in Eq.
-\ref{eq:max_linkage}, the interaction between $S_u \cup S_v$ and one of its neighbors $S_t$ is simply given by:
+Thus, we can recompute these interactions by using an \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$:
 \begin{equation}
-  \interact_{S_u \cup S_v,S_t} = f( \interact_{S_u,S_t}, \interact_{S_v,S_t}) = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) = \max \{ \tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}) \}
+  \interact(S_u \cup S_v,S_t) = f\Big[ \interact(S_u,S_t), \interact(S_v,S_t) \Big] = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) %= \max \{ \tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}) \}
 \end{equation}
-All the update rules tested in this article are listed in Table \ref{tab:linkage-criteria}.
+In Fig.
+\ref{fig:edge_contraction_and_contr_graph} we show an example of edge contraction and we list the update rules associated to the linkage criteria we introduced in Table \ref{tab:linkage-criteria}.
+  % As an example, given the single-linkage criterion defined in Table , the interaction between $S_u \cup S_v$ and one of its neighbors $S_t$ is simply given by:
+% All the update rules tested in this article are listed in Table \ref{tab:linkage-criteria}.
 
-% \UPDATE{Every time a pair of clusters is merged, the contracted graph is updated by performing an edge contraction and merging the associated nodes.
-The only interactions that then need to be updated are those between nodes that after the edge contraction happen to be connected by double edges (see Fig.
-\ref{fig:edge_contraction_and_contr_graph}, step b).
-For basic linkage criteria, e.g.
-\emph{max} or \emph{min}, the new interaction can be formulated in terms of an \emph{update rule} $f$ depending only on the these updates can be computed with an update rule $f$ that depends only on the interactions at the previous step }
-% As a result, the merged node could be linked to some of its neighbors by double edges .
-, representing the fact that their interaction should be updated.
-This update can be easily achieved by using an \emph{update rule} depending only on the weights of the double edges.
-% \TODO{such a mess...} ...without the need of running a loop over the edges of the original graph.
-% \UPDATE{In this way we do not need to recompute the interaction by using the linkage criterion over all the edges of the original graph, that would be computationally expensive.}
-\textbf{The proposed edge contraction algorithm } Algorithm \ref{main_alg} then proceeds as follows, similarly to the one presented in \cite{levinkov2017comparative}.
-It starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first.
-It then iteratively pops one edge $e_{uv}$ from PQ and, depending on the priority $\tilde{\cost}$, does the following: in case of attractive interaction $\tilde{\cost}>0$, provided that $e_{uv}$ was not flagged as a cannot-link constraint, then merge the connected clusters, perform an edge contraction of $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and update the priorities of new double edges as explained in Fig.
+% \algname{} was implemented by using a standard agglomerative clustering algorithm based on a priority queue and a union
+\paragraph{Implementation} As we show in Algorithm \ref{detailed_alg}, our implementation of \algname{} is based on a heap and a union-find data structure.
+The algorithm starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first.
+It then iteratively pops one edge $e_{uv}$ from PQ and, depending on the priority $\tilde{\cost}_{uv}$, does the following: in case of attractive interaction $\tilde{\cost}_{uv}>0$, provided that $e_{uv}$ was not flagged as a cannot-link constraint, then merge the connected clusters, perform an edge contraction of $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and update the priorities of new double edges as explained in Fig.
 \ref{fig:edge_contraction_and_contr_graph}.
 % For every new pair of double edges in $\tilde{\mathcal{G}}_\Pi$, update their priorities according to one of the update rules listed in Table \ref{tab:linkage-criteria} together with their cannot-link relationships.
-If, on the other hand, the interaction is repulsive ($\tilde{\cost}\leq 0$) and the option \texttt{addCannotLink} of Alg.
-\ref{main_alg} is \texttt{True}, then the edge $e_{uv}$ is flagged as cannot-link constraint.
-In the Supplementary material we comment on the algorithm computational complexity (Sec. \ref{sec:complexity}).
+If, on the other hand, the interaction is repulsive ($\tilde{\cost}_{uv}\leq 0$) and the option \texttt{addCannotLinkContraints} of Alg.
+\ref{detailed_alg} is \texttt{True}, then the edge $e_{uv}$ is flagged as cannot-link constraint.
+
+\paragraph*{Complexity} In the main loop, the algorithm iterates over all edges, but the only iterations presenting a complexity different from $\mathcal{O}(1)$ are the ones involving a merge of two clusters, which are at most $N-1$.
+By using a union-find data structure (with path compression and union by rank) the time complexity of \texttt{merge}$(u, v)$ and \texttt{find}($u$) operations is $\mathcal{O}(\alpha(N))$, where $\alpha$ is the slowly growing inverse Ackerman function.
+The algorithm then iterates over the neighbors of the merged cluster (at most $N$) and updates/deletes values in the priority queue ($\mathcal{O}(\log |E|)$).
+Therefore, similarly to a heap-based implementation of hierarchical agglomerative clustering, our implementation of \algname{} has a complexity of $\mathcal{O}(N^2 \log N)$.
+In the worst case, when the graph is dense and $|E|=N^2$, the algorithm requires $\mathcal{O}(N^2)$ memory and does not scale up well.
+Nevertheless, in our practical applications the graph is much sparser, so $\mathcal{O}(|E|)=\mathcal{O}(N)$ and \UPDATE{in Fig.
+\ref{fig:runtime_plot} we show how the empirical runtime of \algname{} is much closer to $\mathcal{O}(N \log N)$ than $\mathcal{O}(N^2 \log N)$.} With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$.
 
@@
 \begin{itemize}
-\item Equivalence Mutex Watershed and Greedy Edge Contraction
-\item Complexity: plain agglo., addition of the cannot-link constraints and then comment about efficient implementation of MWS and of single-linkage (what about single linkage+CLC...?)
+% \item Equivalence Mutex Watershed and Greedy Edge Contraction
+% \item Complexity: plain agglo., addition of the cannot-link constraints and then comment about efficient implementation of MWS and of single-linkage (what about single linkage+CLC...?)
 \item Noise: also mention details about plots (fix some long-range edges, fix noise seed and vary K)
@@
 \end{itemize}
-
-\begin{figure}
-\centering
-        \includegraphics[width=0.45\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
-
-    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise.
-Blue pixels represent boundary evidence.
-Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
-    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
-    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
-    }
-    \label{fig:noisy_affs}
-\end{figure}
 
@@
 \ref{sec:details_perlin}) we provide a more detailed description of the parameters used for the noise generation.
+
+\begin{figure}[b]
+\centering
+        \includegraphics[width=0.45\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
+
+    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise.
+Blue pixels represent boundary evidence.
+Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
+    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
+    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
+    }
+    \label{fig:noisy_affs}
+\end{figure}
 

### 2019-05-16 chapters/supplementary.tex
Add MWS equivalence proof

@@
 \hspace*{\algorithmicindent} \textbf{Input:} $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes and $M$ edges; boolean \texttt{{\color{blue}addCannotLinkConstraints}} \\
-\hspace*{\algorithmicindent} \textbf{Output:} Final clustering given by union-find data structure \\
+\hspace*{\algorithmicindent} \textbf{Output:} Final clustering \\
   \hspace*{\algorithmicindent} 
@@
     %   \State PQ $\gets$ Sort $e\in E$ in descending order of $|w_e|$
-        \State PQ.push$(|w_e|, e) \quad \forall e \in E $  \Comment{Init. priority queue in desc. order of $|w_e|=|w_e^+ - w_e^-|$, $\mathcal{O}(M)$}
+        \State PQ.push$(|w_e|, e) \quad \forall e \in E $  \Comment{Init. priority queue in desc. order of $|w_e|=|w_e^+ - w_e^-|$, $\mathcal{O}(|E|)$}
         \State \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$ \Comment{Init. cannot-link constraints}
@@
       \While{PQ is \textbf{not} empty}
-        \State $\tilde{w}, e_{uv} \gets $ PQ.popHighest() \Comment{$\mathcal{O}(\log M)$}
+        \State $\tilde{w}, e_{uv} \gets $ PQ.popHighest() \Comment{$\mathcal{O}(\log |E|)$}
         \State \textbf{assert} \texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$) \Comment{Edges in PQ always link nodes in different clusters}
@@
         %   \State $ S_u \gets S_u \cup S_v$
-          \State \texttt{UF}.merge($u,v$) \Comment{Merge clusters, $\mathcal{O}(\alpha(M))$}
+          \State \texttt{UF}.merge($u,v$) \Comment{Merge clusters, $\mathcal{O}(\alpha(|E|))$}
           % \For{every new double edge}
@@
     %   \State
-      \Return Union-find structure \texttt{UF}
+      \Return Final clustering given by union-find data structure  \texttt{UF}
       % \State
@@
         \State $\tilde{E} \gets \tilde{E} \setminus \{e_{vt}\}$
-        \State $\tilde{w}_{vt} \gets$ PQ.delete($e_{vt}$) \Comment{$\mathcal{O}(\log M)$}
+        \State $\tilde{w}_{vt} \gets$ PQ.delete($e_{vt}$) \Comment{$\mathcal{O}(\log |E|)$}
         \State \texttt{canBeMerged}$[e_{ut}] \gets$ \texttt{canBeMerged}$[e_{ut}]$ \textbf{and} \texttt{canBeMerged}$[e_{vt}]$
         \If{$t \in \mathcal{N}_u$ }\Comment{$t$ is a common neighbor of $u$ and $v$}
-          \State $\tilde{w}_{ut} \gets$ PQ.delete($e_{ut}$)  \Comment{$\mathcal{O}(\log M)$}
-          \State PQ.push($ |f(\tilde{w}_{ut}, \tilde{w}_{vt})|, e_{ut}$) \Comment{$\mathcal{O}(\log M)$  }
+          \State $\tilde{w}_{ut} \gets$ PQ.delete($e_{ut}$)  \Comment{$\mathcal{O}(\log |E|)$}
+          \State PQ.push($ |f(\tilde{w}_{ut}, \tilde{w}_{vt})|, e_{ut}$) \Comment{$\mathcal{O}(\log |E|)$  }
         % \EndIf
@@
           \State $\tilde{E} \gets \tilde{E} \cup \{e_{ut}\}$
-          \State PQ.push($ |\tilde{w}_{vt}|, e_{ut}$) \Comment{$\mathcal{O}(\log M)$}
+          \State PQ.push($ |\tilde{w}_{vt}|, e_{ut}$) \Comment{$\mathcal{O}(\log |E|)$}
         \EndIf
@@
 % \algname{} was implemented by using a standard agglomerative clustering algorithm based on a priority queue and a union
-\paragraph{Implementation} As we show in Algorithm \ref{detailed_alg}, our implementation of \algname{} is based on a heap and a union-find data structure.
-The algorithm starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first.
+\paragraph{Implementation} As we show in Algorithm \ref{detailed_alg}, our implementation of \algname{} is based on an union-find data structure and a heap allowing deletion of its elements.
+The algorithm starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a heap/priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first.
 It then iteratively pops one edge $e_{uv}$ from PQ and, depending on the priority $\tilde{\cost}_{uv}$, does the following: in case of attractive interaction $\tilde{\cost}_{uv}>0$, provided that $e_{uv}$ was not flagged as a cannot-link constraint, then merge the connected clusters, perform an edge contraction of $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and update the priorities of new double edges as explained in Fig.
@@
 In the worst case, when the graph is dense and $|E|=N^2$, the algorithm requires $\mathcal{O}(N^2)$ memory and does not scale up well.
-Nevertheless, in our practical applications the graph is much sparser, so $\mathcal{O}(|E|)=\mathcal{O}(N)$ and \UPDATE{in Fig.
-\ref{fig:runtime_plot} we show how the empirical runtime of \algname{} is much closer to $\mathcal{O}(N \log N)$ than $\mathcal{O}(N^2 \log N)$.} With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$.
+Nevertheless, in our practical applications the graph is much sparser, so $\mathcal{O}(|E|)=\mathcal{O}(N)$.
+% and \UPDATE{in Fig. \ref{fig:runtime_plot} we show how the empirical runtime of \algname{} is much closer to $\mathcal{O}(N \log N)$ than $\mathcal{O}(N^2 \log N)$.} 
+With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$.
+Moreover, in the next section, we present an efficient implementation of \algname{} with \emph{Absolute Maximum} update rule with empirical $\mathcal{O}(N \log N)$ complexity.
 
-\subsection{Equivalence between Mutex Watershed and \emph{Absolute Maximum} linkage}
+\begin{algorithm}
+  \caption{Mutex Watershed Algorithm proposed by \cite{wolf2018mutex}}
+\hspace*{\algorithmicindent} \textbf{Input:} $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes and $M$ edges \\
+\hspace*{\algorithmicindent} \textbf{Output:} Final clustering \\
+  \hspace*{\algorithmicindent} 
+  \begin{algorithmic}[1]
+      \State \texttt{UF} $\gets$ initUnionFind($V$) 
+      % \State
+      \For{$(u,v)=e\in E$ in descending order of $|w_e|=|w_e^+ - w_e^-|$}
+        \If{\texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$)} \Comment{Check if $u,v$ are already in the same cluster}
+          \If{({\color{ForestGreen}\textbf{$w_e > 0$}}) \textbf{and} \texttt{canBeMerged}($u,v$)}  \Comment{Check for cannot-link constraints}
+            \State \texttt{UF}.merge($u,v$) and inherit constraints of parent clusters
+          \ElsIf{({\color{red}\textbf{$w_e \leq 0$}})}
+            \State Add cannot-link constraints between parent clusters of $u,v$
+          \EndIf
+        \EndIf
+      \EndFor
+      \State
+    %   \State
+      \Return Final clustering given by union-find data structure \texttt{UF}
+      % \State
+    % \EndProcedure
+  \end{algorithmic}
+  \label{alg:mutex_watershed}
+  % \caption{where $\alpha$ is the slowly growing inverse Ackerman function}
+\end{algorithm}
+
+\subsection{Properties of \algname{} with \emph{Absolute Maximum} linkage}
+\paragraph{Remark on graph notation} The definition of a graph proposed by \cite{wolf2018mutex} makes a distinction between a set of positive edges $E^+$, associated with a set $W^+$ of positive scalar attributes representing merge affinities, and a set of negative edges $E^-$, associated with a set $W^-$ of positive scalar attributes representing split tendencies.
+On the other hand, in our definition $\mathcal{G}(V,E,w^+,w^-)$ each edge have both an attractive $w_e^+$ and a repulsive $w_e^-$ attribute, so we can make them equivalent by defining:
+\begin{align}
+E^+ = \{ e \in E \,\,\text{s.t.} \,\,w_e = w_e^+ - w_e^- > 0\},& \qquad E^- = \{ e \in E \,\,\text{s.t.}\,\, w_e = w_e^+ - w_e^- \leq 0\} \\
+W^+ = \{ |w_e| \,\,\text{s.t.}\,\, e \in E^+\},& \qquad W^- = \{ |w_e| \,\,\text{s.t.}\,\, e \in E^-\}
+\end{align}
+
+\begin{prop} \label{prop:equiv_MWS}
+The Mutex Watershed Algorithm \ref{alg:mutex_watershed} (MWS) with empirical $\mathcal{O}(N \log N)$ complexity introduced by \cite{wolf2018mutex} returns the same final clustering given by the \algname{} Algorithm \ref{detailed_alg} with the use of cannot-link constraints and an Absolute Maximum update rule:
+\begin{equation}\label{eq:def_abs_max}
+f_{\mathrm{Abs.Max.}}(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
+            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
+            \tilde{\cost}_2 & \text{otherwise}
+             \end{cases} 
+\end{equation}
+\end{prop}
+\begin{proof}
+Both algorithms sort edges in descending order of the absolute interactions $|w_e|$ and then iterate over all of them.
+The only difference is that MWS, after merging two clusters, does not update the interactions between the new cluster and its neighbors.
+However, since with an Abs.
+Max.
+linkage the interaction between clusters is simply given by the edge with highest absolute weight $|w_e|$, the order by which edges are iterated over in \algname{} is never updated.
+Thus, both algorithms perform precisely the same steps and return the same clustering.
+\end{proof}
+\begin{prop}
+The \algname{} Algorithm \ref{detailed_alg} with the Absolute Maximum linkage defined in Eq.
+\ref{eq:def_abs_max} returns the same final clustering whether or not cannot-link constraints are enforced.
+\end{prop}
+\begin{proof}
+% In Proposition \ref{prop:equiv_MWS} we observed that \algname{} with Abs. Max. linkage never updates the order by which edges are iterated over
+In the \algname{} Algorithm \ref{detailed_alg}, the clustering is updated only when two clusters are merged and the condition at line 9 is satisfied. 
+We also observe that, in the unconstrained version of \algname{}, the predicate \texttt{canBeMerged} at line 9 can never be false.
+Let us now contradict the initial hypothesis and assume by absurd that the constrained version of \algname{} introduces a cannot-link constraints between two clusters sharing a positive interaction $\tilde{w}>0$ and outputs a different clustering as compared to the unconstrained version.
+This can happen only in the situation shown in Fig.
+\ref{fig:contradiction_case}, when two clusters $u$ and $v$ are merged together and share a common neighboring node $t$ having the following two properties: a) $u$ and $t$ are already constrained and share a repulsive interaction $w_{ut}\leq0$, b) $v$ and $t$ share an attractive interaction $w_{vt}>0$ that is higher in absolute value $|w_{vt}|>|w_{ut}|$.
+Then, according to Eq. \ref{eq:def_abs_max}, the new merged cluster $uv$ and $t$ are constrained and share a positive interaction. 
+But this case can never happen, since if $|w_{vt}|>|w_{ut}|$ then clusters $v$ and $t$ are merged before clusters $u$ and $t$ are constrained.  
+\end{proof}
+
+\subsection{CREMI challenge and compared methods}
+
+\subsection{Noise exps}
 
@@
 \item 
-
 \end{itemize}
 
-\subsection{Noise exps}
  % In this section we evaluate the robustness of \algname{} with different linkage criteria by adding noise to the edge weights.

### 2019-05-16 chapters/1_intro.tex
Add comparison details to suppl.

@@
 seeded watershed or random walker).
-Hierarchical clustering (HC) is a popular graph clustering method, which creates a hierarchy of clusters.
-Agglomerative HC is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}.
+Hierarchical clustering is a popular graph clustering method, which creates a hierarchy of clusters.
+Hierarchical agglomerative clustering (HAC) is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}.
 This method usually requires the user to choose a level in the cluster hierarchy defining the desired output clustering.
@@
 
-In this paper, we propose a novel theoretical framework for generalizing over the greedy agglomerative clustering algorithms for signed graphs by linking these algorithms to the agglomerative HC.
+In this paper, we propose a novel theoretical framework for generalizing over the greedy agglomerative clustering algorithms for signed graphs by linking these algorithms to HAC.
 This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}, i.e.

### 2019-05-16 chapters/5_experiments_compare_rules.tex
Add comparison details to suppl.

@@
 Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
-DTWS + LMC (LR)& -& 0.903 $\pm$ 0.016 \\
-DTWS + MC (LR)& -& 0.903 $\pm$ 0.017 \\
+DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
+DTWS + MC & -& 0.903 $\pm$ 0.017 \\
 % DTWS + avgHC &-& \\
-DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
-DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
+% DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
+% DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
 Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
@@
 THRESH &-& 0.221  $\pm$ 0.067 \\ 
-DTWS  & -& 0.010 $\pm$ 0.003\\
+% DTWS  & -& 0.010 $\pm$ 0.003\\
         \end{tabular}
-    \captionof{table}{Arand-Scores and VI-Scores on CREMI challenge training data}
+    \captionof{table}{Arand-Scores on CREMI challenge training data}
     \label{tab:results_cremi_train}
@@
 The results submitted to the leaderboard are evaluated using the CREMI score\footnote{\url{https://cremi.org/leaderboard/}}, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score\cite{arganda2015crowdsourcing}.
-The data is highly anisotropic and contains artifacts like missing sections, staining precipitations and support film folds.
+In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.
 
-\textbf{Training details}
-To alleviate difficulties stemming from misalignment, we use a version of the data that was elastically realigned by the challenge organizers with the method of \cite{saalfeld2012elastic}.
-We train a 3D U-Net \cite{ronneberger2015u, cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
-as described in \cite{lee2017superhuman}. In addition to the standard data augmentation techniques of random rotations, random flips and  elastic deformations, we simulate data artifacts.
-In more detail, we randomly zero-out slices, decrease the contrast of slices, simulate tears, introduce alignment jitter and paste artifacts extracted from the training data.
-Both \cite{funke2018large} and \cite{lee2017superhuman} have shown
-that these kinds of augmentations can help to alleviate issues caused by EM-imaging artifacts.
-We use L2 loss and Adam optimizer to train the network.
-%\UPDATE{We pre-aligned the training and test data with an elastic alignment method \cite{saalfeld2012elastic}.
-We further simulated low contrast sections...
-and missing sections by setting their intensity value to zero...
-We used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d} trained with L1 loss (Adam optimizer with learning rate...).}
-
-\textbf{Additional methods tested }  We compare the performances of the algorithms in our framework with other basic and state-of-the-art post-processing methods.
+\textbf{Additional methods tested } We compare the performances of \algname{} with other basic and state-of-the-art post-processing methods.
 To ensure a fair comparison, we test all methods on the same predictions of our CNN model.
-As baseline methods, we consider a simple thresholding (THRESH) and a watershed algorithm seeded at the maxima of a boundary distance transform (WSDT).
-For these baselines, affinities are converted to a boundary map \UPDATE{by taking a weighted average over short- and long-range edge connections}.
-Other state-of-the-art multi-step-pipelines for neuron-segmentation first find 2D superpixels using WSDT and then apply a graph partitioning algorithm: in our comparison, we include one pipeline using agglomerative HC with average linkage (avgHC) and one using an approximation of the Lifted Multicut Problem (LMC) \cite{beier2016efficient}.
+As basic method, we perform a simple thresholding (THRESH) by running connected components on a boundary map generated from the CNN affinities (see Appendix \ref{sec:cremi_details} for all details on this and the following methods).
+On the other hand, almost all state-of-the-art methods for neuron-segmentation first generates 2D superpixels and then apply a graph partitioning algorithm, as we showed in the related work section.
+Superpixels are usually computed with a watershed algorithm seeded at the maxima of a distance transform generated from a boundary map (WSDT).
+In our comparison we use approximated methods of the multicut (MC) and lifted multicut problem (LMC).

### 2019-05-16 chapters/5_experiments_intro.tex
Add comparison details to suppl.

@@
 Currently, only proof-reading or manual tracing yields sufficient accuracy for correct circuit reconstruction \cite{schlegel2017learning}, thus further progress is required in automated reconstruction methods.
-In Sec.
-\ref{sec:grid_graph}, we present how we predicted signed edge weights with a CNN.
+First, we present how we predicted signed edge weights with a CNN.
 Then we introduce the CREMI challenge and our tested methods in Sec.
-\ref{sec:cremi_challenge} and present our results in Sec.
-\ref{sec:comparison_exps}.
+\ref{sec:cremi_challenge} and finally we present our results in Sec.
+\ref{sec:results}.
 
-\subsection{Experimental setup: pixel grid-graph with long-range connections} \label{sec:grid_graph}
+% \subsection{Experimental setup: pixel grid-graph with long-range connections} \label{sec:grid_graph}
 EM segmentation is commonly performed by first predicting 
@@
 % In our experiments, we divided the set of edges $E$ in $E_{\mathrm{direct}}$ connecting direct neighboring voxels and $E_{\mathrm{long}}$. 
-See Appendix \ref{sec:training_details} for more details on the chosen neighborhood structure.
+% See Appendix \ref{sec:training_details} for more details on the chosen neighborhood structure.
 % , data augmentation and the training with L1 loss of the used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d}.
@@
 \begin{equation} \label{eq:mappings}
-\cost_{e,\mathrm{Add}} = p_e - \beta, \qquad \quad \cost_{e,\mathrm{Log}} = \log \left( \frac{p_e}{1-p_e} \right) + \log \left( \frac{\beta}{1-\beta} \right),
+\cost_{e,\mathrm{Add}} = p_e - \beta, \qquad \quad \cost_{e,\mathrm{Log}} = \log \left( \frac{p_e}{1-p_e} \right) - \log \left( \frac{\beta}{1-\beta} \right),
 \end{equation}
@@
 We evaluated both of them empirically with each of the tested linkage and found that the additive mapping is the best option in all cases apart from the \emph{Sum} linkage.
-\TODO{HC threshold}
+Note that varying the parameter $\beta$ does not usually define a hierarchy of nested clusterings, thus it is not equivalent to varying a threshold parameter in HAC.
+This hierarchical property is only valid for \algname{} without constraints and with \emph{Average}, \emph{Max} or \emph{Min} linkage.

### 2019-05-16 chapters/5_experiments_noise.tex
Add comparison details to suppl.

@@
 
-\subsection{Results}
-% \subsection{In-depth comparison of different linkage criteria for \algname{}} \label{sec:comparison_exps}
-As shown in Table \ref{tab:results_cremi_train}, among all the signed graph algorithms included in our generalized framework, the less-known one with \emph{Average} linkage consistently outperformed all other previously proposed linkage like \emph{Sum} or \emph{Absolute Max}.
-This method also achieved \UPDATE{comparable} scores to other complex multi-step pipelines that usually require the user to tune several hyper-parameters, like LMC.
+\subsection{Results}\label{sec:results}
+% \subsection{In-depth comparison of different linkage criteria for \algname{}} 
+The difficulty of the dataset is highlighted by the poor scores achieved by THRESH in Table \ref{tab:results_cremi_train}.
+Among all the signed graph algorithms included in our generalized framework, the less-known one with \emph{Average} linkage consistently outperformed all other previously proposed linkage like \emph{Sum} or \emph{Absolute Max}.
+This simple method also achieved remarkably superior scores to other state-of-the-art multi-step methods.
+\TODO{Wait for new test-scores}
 In Fig.
-\ref{fig:cremi_comparison}, we highlight some failure cases of \algname{} and in Appendix we provide an extended version of Table \ref{tab:results_cremi_train} including all linkage tested with \algname{} on the full CREMI training data.
+\ref{fig:cremi_comparison}, we highlight some failure cases of the different agglomerative algorithms included in our framework.
+In Appendix we provide an extended version of Table \ref{tab:results_cremi_train} including all scores linkage tested with \algname{} on the full CREMI training data.
 
@@
 
-Plots in Fig.
+\UPDATE{Plots in Fig.
 \ref{fig:noise_plots} summarize 6000 experiments: we focused on the best performing linkage criteria, i.e.
@@
 In these cases, the use of cannot-link constraints or a more robust average linkage are preferable.
-% \UPDATE{The plots in Fig.
-\ref{fig:noise_plots} represent the scores achieved by \algname{} with different update rules depending on the amount of noise $\m{}athcal{K}$ added to the edge weights and the probability $p_{\mathrm{long}}$ of long-range connections in the graph.
-Results clearly show that adding long-range edges is always beneficial for the final segmentation \TODO{Not True!}.
-\TODO{What about time?} The most robust version of update rule proved to be the \emph{mean}, that achieves similar scores even with significantly noisy edge weights.
-The \emph{absolute maximum} update rule proposed by \cite{wolf2018mutex} provides an efficient and fast option, but completely fails when too much noise is added.
-% The \emph{sum} update rule version was the slowest option tested, but it was not as robust as the \emph{mean} version, probably due to its tendency to grow one cluster at the time (see Sec.
-\ref{sec:exp_first_comparison}).
-\TODO{Comment about MC energy}
-% On the other hand, \algname{} with \emph{mean} update rule and cannot-link constraints did not achieve high scores because of the strong over-segmentation error.}
-
-% Highlight difference of the sum in Fig. \ref{fig:intro_figure}.
-% \begin{itemize}
-%   % \item compare different choices of signed-cost-mappings (say which one worked best)
-%   % \item present cremi crop-C table and rule out single and complete linkage
-% \end{itemize}
-
+}
 \begin{figure}[b]
@@
 \end{figure}
-
-% \begin{equation}
-% \begin{gathered}
-% \tilde{p}_{\pm}(x;\theta)=\sigma(\tilde{F}_{\pm}(x;\theta))\quad \text{where}\\
-% % \tilde{F}(x;\theta)=\begin{cases}
-% % F(x;\theta)+\mathcal{K}\cdot\max\left(N(x),0\right) & \text{if merge-biased}\\
-% % F(x;\theta)+\mathcal{K}\cdot\min\left(N(x),0\right) & \text{if split-biased}
-% % \end{cases}
-% \tilde{F}_{\pm}(x;\theta)=F(x;\theta)\pm\left|\mathcal{K}\cdot\max\left(\pm N(x),0\right)\right|
-% \end{gathered}
-% \end{equation}

### 2019-05-16 chapters/supplementary.tex
Add comparison details to suppl.

@@
 With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$.
-Moreover, in the next section, we present an efficient implementation of \algname{} with \emph{Absolute Maximum} update rule with empirical $\mathcal{O}(N \log N)$ complexity.
+Moreover, in the next section, we present an efficient implementation of \algname{} with \emph{Absolute Maximum} linkage that has empirical $\mathcal{O}(N \log N)$ complexity.
 
@@
 \subsection{Properties of \algname{} with \emph{Absolute Maximum} linkage}
-\paragraph{Remark on graph notation} The definition of a graph proposed by \cite{wolf2018mutex} makes a distinction between a set of positive edges $E^+$, associated with a set $W^+$ of positive scalar attributes representing merge affinities, and a set of negative edges $E^-$, associated with a set $W^-$ of positive scalar attributes representing split tendencies.
+\paragraph{Remark on graph notation} The definition of a graph proposed by \cite{wolf2018mutex} makes a distinction between a set of positive edges $E^+$, associated with a set $W^+$ of positive scalar attributes representing merge affinities, and a set of negative edges $E^-$, associated with a set $W^-$ of positive attributes representing split tendencies.
 On the other hand, in our definition $\mathcal{G}(V,E,w^+,w^-)$ each edge have both an attractive $w_e^+$ and a repulsive $w_e^-$ attribute, so we can make them equivalent by defining:
@@
 
-\subsection{CREMI challenge and compared methods}
+\subsection{CREMI challenge and compared methods}\label{sec:cremi_details}
+\paragraph{Training details} The data from the CREMI challenge is highly anisotropic and contains artifacts like missing sections, staining precipitations and support film folds. 
+To alleviate difficulties stemming from misalignment, we use a version of the data that was elastically realigned by the challenge organizers with the method of \cite{saalfeld2012elastic}.
+We train a 3D U-Net \cite{ronneberger2015u, cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
+as described in \cite{lee2017superhuman}. In addition to the standard data augmentation techniques of random rotations, random flips and  elastic deformations, we simulate data artifacts.
+In more detail, we randomly zero-out slices, decrease the contrast of slices, simulate tears, introduce alignment jitter and paste artifacts extracted from the training data.
+Both \cite{funke2018large} and \cite{lee2017superhuman} have shown
+that these kinds of augmentations can help to alleviate issues caused by EM-imaging artifacts.
+We use L2 loss and Adam optimizer to train the network.
 
-\subsection{Noise exps}
+\paragraph{THRESH and WSDT} The basic post-processing methods we consider cannot take long-range affinities into account, so we only consider direct neighbors affinities and generate a boundary map by taking an average over the 3 directions.
+Based on this boundary map, we run connected components (THRESH) and we also introduce seeds at the maxima of the smoothed distance transform (WSDT).
+For WSDT, the degree of smoothing was optimized such that each region receives as few seeds as possible, without however causing severe under-segmentation.
+Due to the anisotropy of the data, we generate 2D WSDT superpixels by considering each 2D image in the stack singularly.
+
+\paragraph{Multi-step pipelines} Given the 2D WSDT superpixels, we build a 3D region-adjacency graph such that each node represents a superpixel.
+The weights of the edges connecting neighboring superpixels are computed by taking an average over both short- and long-range affinities connecting the two regions.
+We then convert the edge probabilities to signed weights using the logarithmic mapping defined in Eq.
+\ref{eq:mappings} and solve the multicut problem on this graph.
+For our experiments, we use the approximate Kernighan-Lin solver \cite{keuper2015efficient,kernighan1970efficient} (MC).
+In some cases, the long-range affinities predicted by the CNN can connect two superpixels that are not direct-neighbors.
+Thus, in these cases we introduce additional \emph{lifted} edges in the graph and an instance of the lifted multicut problem (LMC).
+This time, similarly to the methods mentioned in \cite{beier2016efficient}, we used a combination of approximate solvers consisting in GAEC and Kernighan-Lin.
+and      Other state-of-the-art multi-step-pipelines for neuron-segmentation first find 2D superpixels using WSDT and then apply a graph partitioning algorithm: in our comparison, we include one pipeline using agglomerative HC with average linkage (avgHC) and one using an approximation of the Lifted Multicut Problem (LMC) \cite{beier2016efficient}.
+
+ \paragraph{Scaling up \algname{} to the full CREMI dataset} Describe all tricks and then present extended Table
+
+\subsection{Use of gradient noise on the CNN predictions} \label{sec:appendix_noise_gen}
 
@@
 \item Noise: also mention details about plots (fix some long-range edges, fix noise seed and vary K)
-\item exp. setup details: enforcing local merges, MWS distinguish between repulsive-long, post-processing of small segments, loss, architecture, training parameters, offset patterns
+\item exp. setup details: enforcing local merges, MWS distinguish between repulsive-long, post-processing of small segments
 \item 
@@
 
-\subsection{Cityscapes exps}
+\subsection{Fine-tuning the GMIS pipeline on CityScapes} \label{sec:appendix_cityscapes}
 Mention the main trick in the loss: ignore background pixels (so focus on boundaries). Same mapping defined in \ref{eq:mappings}

### 2019-05-17 chapters/supplementary.tex
Update details about full cremi exps

@@
 
-\subsection{CREMI challenge and compared methods}\label{sec:cremi_details}
+\subsection{Neuron segmentation and compared methods}\label{sec:cremi_details}
 \paragraph{Training details} The data from the CREMI challenge is highly anisotropic and contains artifacts like missing sections, staining precipitations and support film folds. 
@@
 that these kinds of augmentations can help to alleviate issues caused by EM-imaging artifacts.
-We use L2 loss and Adam optimizer to train the network.
+We use L2 loss and Adam optimizer to train the network. \TODO{Field of view?}
 
@@
 
- \paragraph{Scaling up \algname{} to the full CREMI dataset} Describe all tricks and then present extended Table
+\subsection{\algname{} on the full CREMI dataset}
+ \paragraph{Pre-merge processing} For the predictions on the full dataset from the CREMI challenge, we used  the padded volumes provided by the challenge.
+The crops on which we performed a prediction have a size of $1500\times1500\times127=2.86\cdot 10^8$ voxels or larger.
+Building a graph with $10^8$ nodes can easily incur a large use of memory, so we decided to perform a preprocessing step by initially merging some nodes together.
+Simply down-sampling the predictions of the CNN would have led to a loss of resolution and performances in the most difficult parts of the dataset.
+Thus, we decided to pre-merge the most connected components of the graph that would be anyway clustered during the first iterations of \algname{}.
+To do this, we used a simple approach: we generated a boundary probability map by taking for each voxel an average over affinities in all directions (both short- and long-range ones) and we run THRESH to find the connected components.
+With this approach, pixels are pre-clustered only when they are far away (in all directions) from all predicted boundaries.
+ To make sure that in this preprocessing step different neurons are never merged together by mistake, we intersected these segments given by the conservative THRESH with the segments given by WSDT \TODO{show figure?}.
+By using this method, we initialized \algname{} with a reduced graph that represents a true over-segmentation.
+In our experiments, the use of this preprocessing method did not impact the final scores achieved by \algname{} and significantly reduced its runtime.
 
-\subsection{Use of gradient noise on the CNN predictions} \label{sec:appendix_noise_gen}
+ \paragraph{Removing small segments} After running \algname{}, we use a simple post-processing step to delete small segments on the boundaries, most of which are given by single-pixel clusters.
+We deleted all regions with less than 200 pixels and used a seeded watershed algorithm to expand the bigger segments.
 
-\begin{itemize}
-% \item Equivalence Mutex Watershed and Greedy Edge Contraction
-% \item Complexity: plain agglo., addition of the cannot-link constraints and then comment about efficient implementation of MWS and of single-linkage (what about single linkage+CLC...?)
-\item Noise: also mention details about plots (fix some long-range edges, fix noise seed and vary K)
-\item exp. setup details: enforcing local merges, MWS distinguish between repulsive-long, post-processing of small segments
-\item 
-\end{itemize}
+ \paragraph{Enforcing local merge} In 2D images of urban-scenes, due to partial occlusion, one object instance can be given by multiple components that are not directly connected in the image plane.
+This is not the case in neuron-segmentation, where each neuron should be given by a single 3D connected component in the volume.
+To enforce this, we modified the implementation of \algname{} so that two clusters are merged only when they represent two adjacent supervoxels in the 3D volume and if this condition is not satisfied, the merge is postponed.
+This then avoids the introduction of ``air-bridges'' between segments due to attractive long-range connections in the voxel-graph.
+ This approach achieved superior performances to the one proposed in \cite{wolf2018mutex}, where all long-range connections in the voxel-graph are associated to a negative repulsive edge weight.
+
+\paragraph{Extended results} \TODO{present extended table}
+
+\subsection{Experiments on neuron segmentation adding noise to CNN predictions} \label{sec:appendix_noise_gen}
+
+\TODO{Also mention details about plots (fix some long-range edges, fix noise seed and vary K)}
 
@@
 \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}).
-In the Supplementary material (Sec.
-\ref{sec:details_perlin}) we provide a more detailed description of the parameters used for the noise generation.
+\TODO{Add more details}
 

### 2019-05-17 chapters/5_experiments_cityscapes.tex
Add comparison details to suppl.
Add more details about CS exps

@@
 Their trained model was publicly available, so we simply replaced their final graph-merging algorithm (GMIS-Agglo) with \algname{}.
-See Appendix \ref{sec:cityscapes_appendix} for more details on how we fine-tuned their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
+See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
 
@@
 Max.}, or false region-merge, like \emph{Sum}.
-GMIS-Agglo requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 in \cite{liu2018affinity}.
-
-% \begin{table}
-%     \centering
-%     \begin{subtable}[t!]{0.5\textwidth}\centering
-%         \begin{tabular}{c|| c| c| c |c }
-%         & \multicolumn{4}{c}{\thead{Add Cannot-Link-Constraints:}} \\
-%         & \multicolumn{2}{c}{\thead{\textsc{No}}} & \multicolumn{2}{c}{\thead{\textsc{Yes}}} \\
-%          & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
-% Sum & 0.55  & {\color{Orange} 0.313 } & 0.55  & {\color{Orange} 0.319 } \\\midrule
-% Abs. Max. & 0.45  & {\color{Orange} 0.321 } & & \\\midrule
-% \textbf{Mean}& \textbf{0.35 } & {\color{ForestGreen} \textbf{0.343} } & 0.25  & {\color{Orange} 0.339 } \\\midrule
-
-% Max & 0.85 & {\color{Red} 0.243 } & 0.50  & {\color{Orange} 0.325 } \\\midrule
-% Min & 0.50  & {\color{Red} 0.000 } & 0.50  & {\color{Red} 0.000 } \\\midrule
-% \cite{liu2018affinity} & -  & {\color{ForestGreen} 0.341 } & - & - \\
-
-%         \end{tabular}
-%         % \caption{Linkage criteria}
-%     \end{subtable} 
-%     \caption{Results on cityscapes validation set (with finetuned affinities). \TODO{Reformat in the usual form, delete colors, less digits}}
-%     \label{tab:results_cityscapes}
-% \end{table}
-
-% \begin{table*}
-%     \centering
-%     \begin{subtable}[t!]{0.98\textwidth}\centering
-%         \begin{tabular}{c| c| c | c}
-%         Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
-% GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
-% mean & False & {\color{Orange} 0.3359 } & {\color{ForestGreen} 0.5416 } \\
-% mean & True & {\color{Orange} 0.3315 } & {\color{ForestGreen} 0.5331 } \\
-% MutexWatershed & True & {\color{Red} 0.2123 } & {\color{Red} 0.3848 } \\
-% SingleLinkage & False & {\color{Red} 0.1935 } & {\color{Red} 0.3615 } \\
-% CompleteLinkage & False & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\
-
-%         \end{tabular}
-%         % \caption{Linkage criteria}
-%     \end{subtable} 
-%     \caption{Scores on cityscapes validation set (original affinities trained by GMIS)}
-%     \label{tab:linkage-criteria}
-% \end{table*}
+GMIS-Agglo requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.

### 2019-05-17 chapters/5_experiments_noise.tex
Add more details about CS exps

@@
 % \subsection{In-depth comparison of different linkage criteria for \algname{}} 
-The difficulty of the dataset is highlighted by the poor scores achieved by THRESH in Table \ref{tab:results_cremi_train}.
+\TODO{Mention Appendix} The difficulty of the dataset is highlighted by the poor scores achieved by THRESH in Table \ref{tab:results_cremi_train}.
 Among all the signed graph algorithms included in our generalized framework, the less-known one with \emph{Average} linkage consistently outperformed all other previously proposed linkage like \emph{Sum} or \emph{Absolute Max}.
@@
 \centering
-\begin{minipage}[T]{0.54\textwidth}
+\begin{minipage}[T]{0.59\textwidth}
     \centering
@@
         \begin{tabular}{l|l|cc}
-           & \algname{}  &  \multicolumn{2}{c}{Use constraints:} \\
-           & Linkage & \textsc{No} & \textsc{Yes} \\ \midrule
+           & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
+          Pipeline & method & \textsc{No} & \textsc{Yes} \\ \midrule
 DWT \cite{bai2017deep} & - & 21.2 & - \\
@@
 Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
- & \textbf{Average}& \textbf{34.3}  & 33.9  \\
- & GMIS-Agglo \cite{liu2018affinity} & \UPDATE{33.0} & -  \\
-\multirow{2}{*}{GMIS Pipeline} & Max &   24.3  &   32.5  \\
- & Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
- & Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
- & Min &  0    & 0  \\
+ & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
+ & MultiStepHAC \cite{liu2018affinity} & \UPDATE{33.0} & -  \\
+\multirow{2}{*}{GMIS \cite{liu2018affinity}} & \algname{} Max &   24.3  &   32.5  \\
+ & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
+ & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
+ & \algname{} Min &  0    & 0  \\
         \end{tabular}
@@
 \end{minipage}\hfill
-\begin{minipage}[T]{0.43\textwidth}
-    \centering
+\begin{minipage}[T]{0.37\textwidth}
     \centering

### 2019-05-17 chapters/supplementary.tex
Add more details about CS exps

@@
 \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}).
-\TODO{Add more details}
+\TODO{Add impl.
+details}
 
@@
 \subsection{Fine-tuning the GMIS pipeline on CityScapes} \label{sec:appendix_cityscapes}
-Mention the main trick in the loss: ignore background pixels (so focus on boundaries). Same mapping defined in \ref{eq:mappings}
+For our experiments, we used the model from GMIS \cite{liu2018affinity} that is publicly available.
+The instance-branch of the model was trained with a Binary Cross-Entropy loss, but we noticed how the short-range affinities were biased towards high probabilities, so that a strong short-range boundary evidence was never predicted by the model.
+In \cite{liu2018affinity}, they handle this problem by proposing a modified version of HAC that is done in stages (GMIS-Agglo): initially only short-range affinities are used to run HAC and a low threshold in the hierarchy is chosen to define a first clustering; a new HAC problem including long-range affinities is then initialized with the first clustering; in the method proposed by \cite{liu2018affinity}, these steps are repeated three times.
 
-% \begin{table*}
-%     \centering
-%     \begin{subtable}[t!]{0.98\textwidth}\centering
-%         \begin{tabular}{c| c | c| c | c | c | c | c}
-% Update rule & \makecell{Use Cannot-Link\\Constraints} & Log-costs & \makecell{Multicut objective} & Runtime (s) & ARAND & VI-merge & VI-split\\ \midrule\midrule
-% mean & False & True & -93152163 & {\color{Orange} 3666 } & {\color{Orange} 0.1204 } & {\color{ForestGreen} 0.231 } & {\color{Red} 0.641 } \\
-% sum & False & True & -93142805 & {\color{Red} 16154 } & {\color{ForestGreen} 0.0893 } & {\color{Orange} 0.301 } & {\color{Orange} 0.514 } \\
-% mean & False &  & -93072127 & {\color{Orange} 3168 } & {\color{Orange} 0.1284 } & {\color{ForestGreen} 0.234 } & {\color{Red} 0.642 } \\
-% sum & True & True & -92936797 & {\color{Red} 21605 } & {\color{ForestGreen} 0.0910 } & {\color{ForestGreen} 0.293 } & {\color{Orange} 0.532 } \\
-% MutexWatershed & False &  & -92704851 & {\color{ForestGreen} 632 } & {\color{Orange} 0.1347 } & {\color{ForestGreen} 0.231 } & {\color{Red} 0.751 } \\
-% sum & True & False & -91444880 & {\color{Red} 26842 } & {\color{Red} 0.2085 } & {\color{Red} 0.572 } & {\color{Orange} 0.489 } \\
-% mean & True & True & -90660193 & {\color{Orange} 4114 } & {\color{Orange} 0.1655 } & {\color{ForestGreen} 0.213 } & {\color{Red} 1.011 } \\
-% mean & True &  & -88260595 & {\color{Orange} 4393 } & {\color{Red} 0.2017 } & {\color{ForestGreen} 0.208 } & {\color{Red} 1.155 } \\
-% max & True &  & -81432464 & {\color{Red} 7759 } & {\color{Orange} 0.1653 } & {\color{ForestGreen} 0.236 } & {\color{Red} 0.792 } \\
-% max & False &  & -37045939 & {\color{ForestGreen} 134 } & {\color{Red} 0.9150 } & {\color{Red} 5.691 } & {\color{ForestGreen} 0.013 } \\
-% min & False &  & 213670839 & {\color{ForestGreen} 600 } & {\color{Red} 0.9330 } & {\color{ForestGreen} 0.207 } & {\color{Red} 4.880 } \\
-% min & True &  & 214747429 & {\color{ForestGreen} 852 } & {\color{Red} 0.9314 } & {\color{ForestGreen} 0.202 } & {\color{Red} 4.887 } \\
+Since GMIS-Agglo is a rather complex post-processing method that requires to tune several hyper-parameters, we opted for a different approach.
+We added two 1x1 convolutional layers to the instance-branch model and trained them by using a
 
-%         \end{tabular}
-%         % \caption{Linkage criteria}
-%     \end{subtable} 
-%     \caption{Comparison of update rules on crop of cremi sample B (sorted by multicut energy) \TODO{Reduce insane amount of numbers.
-Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime.
-Invert ARAND to make it consistent with the plots} }
-%     \label{tab:results_cremi_crop_C}
-% \end{table*}
+% Mention the main trick in the loss: ignore background pixels (so focus on boundaries).
 
-% \begin{table*}
-%     \centering
-%     \begin{subtable}[t!]{0.98\textwidth}\centering
-%         \begin{tabular}{c| c | c| c | c | c | c | c}
-% Update rule & \makecell{Use Cannot-Link\\Constraints} & Log-costs & \makecell{Multicut objective} & Runtime (s) & ARAND & VI-merge & VI-split\\ \midrule\midrule
-% mean & False &  & -102739991 & {\color{Orange} 3797 } & {\color{ForestGreen} 0.9292 } & {\color{ForestGreen} 0.286 } & {\color{ForestGreen} 0.428 } \\
-% mean & False &  & -102730208 & {\color{Orange} 2562 } & {\color{ForestGreen} 0.9285 } & {\color{ForestGreen} 0.292 } & {\color{ForestGreen} 0.423 } \\
-% MutexWatershed & False &  & -102313957 & {\color{ForestGreen} 830 } & {\color{ForestGreen} 0.9246 } & {\color{ForestGreen} 0.291 } & {\color{Orange} 0.471 } \\
-% max & True &  & -98143342 & {\color{Red} 7153 } & {\color{ForestGreen} 0.9208 } & {\color{ForestGreen} 0.292 } & {\color{Orange} 0.496 } \\
-% mean & True &  & -100279671 & {\color{Orange} 4713 } & {\color{Orange} 0.8647 } & {\color{ForestGreen} 0.265 } & {\color{Red} 0.717 } \\
-% sum & True &  & -100745943 & {\color{Red} 13361 } & {\color{Orange} 0.8426 } & {\color{Orange} 0.410 } & {\color{Orange} 0.451 } \\
-% sum & False &  & -101846418 & {\color{Red} 12681 } & {\color{Orange} 0.8377 } & {\color{Orange} 0.427 } & {\color{ForestGreen} 0.427 } \\
-% sum & False &  & -101732952 & {\color{Red} 12287 } & {\color{Orange} 0.8376 } & {\color{Orange} 0.436 } & {\color{ForestGreen} 0.390 } \\
-% sum & True &  & -101487448 & {\color{Red} 8497 } & {\color{Orange} 0.8374 } & {\color{Orange} 0.428 } & {\color{ForestGreen} 0.414 } \\
-% mean & True &  & -99416111 & {\color{Orange} 3445 } & {\color{Orange} 0.8239 } & {\color{ForestGreen} 0.260 } & {\color{Red} 0.822 } \\
-% min & True &  & 211183545 & {\color{ForestGreen} 692 } & {\color{Red} 0.0779 } & {\color{ForestGreen} 0.232 } & {\color{Red} 4.714 } \\
-% min & False &  & 210377447 & {\color{ForestGreen} 493 } & {\color{Red} 0.0737 } & {\color{ForestGreen} 0.233 } & {\color{Red} 4.745 } \\
-% max & False &  & -48601637 & {\color{ForestGreen} 102 } & {\color{Red} 0.0611 } & {\color{Red} 5.738 } & {\color{ForestGreen} 0.035 } \\
+% Same mapping defined in \ref{eq:mappings}
 
-%         \end{tabular}
-%         % \caption{Linkage criteria}
-%     \end{subtable} 
-%     \caption{Comparison of update rules on crop of cremi sample C (sorted by multicut energy) \TODO{Reduce insane amount of numbers.
-Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime.
-Invert ARAND to make it consistent with the plots} }
-%     \label{tab:results_cremi_crop_C}
-% \end{table*}
-
-% \begin{table}
-%     \centering
-%     \begin{subtable}[t!]{0.5\textwidth}\centering
-%         \begin{tabular}{M{0.1\textwidth}| c| c| c | c }
-%         \thead{Update \\rule} & \thead{Use Cannot-Link\\ Constraints} & \thead{Bias \\factor $\beta$} & \thead{AP} & \thead{AP 50\%} \\ \midrule\midrule
-% \multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
-%  &Yes & 0.55  & {\color{Orange} 0.319 } & {\color{Orange} 0.527 } \\\midrule
-% Abs. max. &- & 0.45  & {\color{Orange} 0.321 } & {\color{ForestGreen} 0.531 } \\\midrule
-% \multirow{2}{*}{Mean} &No & 0.35  & {\color{ForestGreen} 0.343 } & {\color{ForestGreen} 0.552 } \\
-%  &Yes & 0.25  & {\color{Orange} 0.339 } & {\color{ForestGreen} 0.548 } \\\midrule
-% \multirow{2}{*}{Max} &No & 0.85 & {\color{Red} 0.243 } & {\color{Red} 0.444 } \\
-%  &Yes & 0.50  & {\color{Orange} 0.325 } & {\color{ForestGreen} 0.530 } \\\midrule
-% \multirow{2}{*}{Min} &No & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\
-%  &Yes & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\\midrule
-% \cite{liu2018affinity} &-  & -  & {\color{ForestGreen} 0.341 } & {\color{ForestGreen} 0.547 } \\
-%         \end{tabular}
-%         % \caption{Linkage criteria}
-%     \end{subtable} 
-%     \caption{Results on cityscapes validation set (with finetuned affinities). \TODO{Reformat in the usual form, delete colors, less digits}}
-%     \label{tab:results_cityscapes_full}
-% \end{table}
-
-% \begin{algorithm}[t]
-%   \caption{Generalized Algorithm for Signed Graphs Agglomerative Clustering}
-%    \hspace*{\algorithmicindent} \textbf{Inputs:} Graph $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes; boolean variable {\color{blue}\texttt{addCannotLink}}  \\
-%   \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$\\
-%   \hspace*{\algorithmicindent} 
-%   \begin{algorithmic}[1]
-
-%       \State Init. clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ and contracted graph $\tilde{\mathcal{G}}_\Pi \gets \mathcal{G}$
-%       \State Init. \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
-%       \State Sort edges in priority queue (PQ) in descending order of priority $|\cost_e|=|w^+_e - w^-_e|$ 
-%       \State
-%       \While{PQ is \textbf{not} empty}
-%         \State Pop edge $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ with highest absolute interaction $|\tilde{\cost}|$
-%         \If{({\color{ForestGreen}\textbf{$\tilde{\cost} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
-%           \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
-%           \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
-%             % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
-%             \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
-%           \EndFor
-%         \EndIf
-%         \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
-%           \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
-%         \EndIf
-%       \EndWhile
-%       \State
-%       \Return $\Pi$
-%   \end{algorithmic}
-%   \label{main_alg_suppl}
-% \end{algorithm}
+% Due to the unbalanced nature of the original affinities, we had to perform a parameter-search of the $\beta$ hyper-parameter.
+Since with a certain value of $\beta$ could be optimal for some versions of \algname{} but not others, we decide to perform a parameter search for each version of \algname{} and Table \ref{tab:results_cityscapes_val} lists the best-case performances for each of the methods.

### 2019-05-18 chapters/1_intro.tex
Start finalizing result section

@@
 By applying this method both to 2D urban scenes from the CityScapes dataset and the challenging neuron-segmentation task of 3D EM image stacks, \UPDATE{we show how one of the less-known algorithms included in our framework consistently outperformed all other previously proposed signed graph clustering methods and achieved comparable/superior scores to other complex multi-step pipelines...}
+
+Contributions: generalized framework given by simple algorithm; proof of equivalence with previously proposed methods; new algorithms included; on instance image segmentation, one of the less-known methods in our methods achieved remarkable scores compared to previously aggl.
+methods proposed; comparable scores to much more complex multi-step pipelines; extensive set of experiments with noise, highlighting the properties of different agglomerative methods; over-clustering and under-clustering
+
 % Most recently, success in instance segmentation (IS) has been achieved by applying deep learning and there are two main types of successful deep learning approaches to IS: proposal-based \cite{he2017mask,dai2016instance,li2017fully} and proposal-free \cite{kong2018recurrent,novotny2018semi,kulikov2018instance,kirillov2017instancecut} methods.
@@
 (\textbf{c}) Agglomeration order, representing which pairs of neighboring pixels were merged first (white), later on (brown), or never (black).
+ \TODO{show nice segmentations, affinities and replace unsigned case}
 %We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 

### 2019-05-18 chapters/2_rel_work.tex
Start finalizing result section

@@
 \section{Related work} \label{sec:related_work}
-% In recent years there has been considerable progress in pixel-level understanding tasks of computer vision, such as semantic segmentation \cite{long2015fully,kong2018recurrent,chen2018deeplab}, boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, %, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet},
-Recent progress in semantic segmentation \cite{long2015fully,kong2018recurrent,chen2018deeplab}, boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, %, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet},
-and pose estimation \cite{wei2016convolutional,cao2017realtime} was mostly associated with new key ideas and architectures in deep learning, like dilated convolutions \cite{yu2015multi,chen2018deeplab} or ``hourglass'' architectures with skip connections \cite{ronneberger2015u,paszke2016enet} increasing the receptive field of view of the model.
-
-\textbf{Proposal-based methods} decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}.
+% Recent progress in semantic segmentation \cite{long2015fully,kong2018recurrent,chen2018deeplab}, boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, %, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet},
+% and pose estimation \cite{wei2016convolutional,cao2017realtime} was mostly associated with new key ideas and architectures in deep learning, like dilated convolutions \cite{yu2015multi,chen2018deeplab} or ``hourglass'' architectures with skip connections \cite{ronneberger2015u,paszke2016enet} increasing the receptive field of view of the model.
+\textbf{Proposal-based methods} have been highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}.
+They decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}.
 % Here I could have more: \cite{pinheiro2015learning,pinheiro2016learning,hu2017fastmask} and probably something more in Deep coloring

### 2019-05-18 chapters/3_algorithm.tex
Update impl. and complexity section
Add comparison details to suppl.
Start finalizing result section

@@
 % Other common choices are \emph{minimum} (complete linkage) or \emph{average} (average linkage). %and \emph{sum}.
-
-\textbf{Multicut and correlation clustering } For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^{\mathrm{internal}}_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^{\mathrm{external}}$ the complementary set of edges whose incident nodes belong to distinct clusters:
-\begin{equation}
-E_\Pi^{\mathrm{internal}} \equiv \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \qquad E^{\mathrm{external}}_\Pi \equiv E \setminus E^{\mathrm{internal}}_\Pi.
-\end{equation}
-% \begin{align}
-% E_\Pi^0 &= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \\
-% E^1_\Pi &= E \setminus E^0_\Pi.
-% \end{align}
-The set of edges $E_\Pi^{\mathrm{external}}$ is known as the \emph{multicut} of $\mathcal{G}$ w.r.t.
-clustering $\Pi$.
-The instance of the NP-hard \emph{weighted correlation clustering/multicut problem}
-% w.r.t. $\mathcal{G}(V,E,\cost)$ 
-corresponds to finding the partitioning that optimally balance attraction and repulsion in the graph and is given by the following binary integer program \cite{kappes2011globally,chopra1991multiway,andres2015lifting}:
-\begin{equation}\label{eq:multicut_obj}
-% \min_\Pi \texttt{MC}(\Pi) \equiv
- \min_\Pi \sum_{e\in E} \cost_e x_e^\Pi,  \qquad \text{where} \quad x^\Pi_e = 
- \begin{cases} 
- 1 & \text{if } e\in E^{\mathrm{external}}_\Pi \\
- 0 & \text{otherwise}.
- \end{cases}
-\end{equation}
-In the next chapters we will use this objective as measure of how balanced a clustering is.
 
@@
 
-The proposed \algname{} Algorithm \ref{main_alg} uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merges pairs of adjacent clusters.
+\TODO{mention detailed pseudocode} The proposed \algname{} Algorithm \ref{main_alg} uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merges pairs of adjacent clusters.
 It starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
@@
 
-In the Supplementary material we comment on the algorithm \UPDATE{computational complexity $\mathcal{O}(?)$} and present an efficient implementation based on an edge contraction algorithm combined with a priority queue (Sec.
-\ref{sec:complexity}).
+In Appendix \ref{sec:detailed_impl} we comment on the algorithm \UPDATE{computational complexity $\mathcal{O}(N^2 \log N)$} and present an efficient implementation based on an edge contraction algorithm combined with a priority queue.
 
@@
     \begin{subtable}[t!]{\textwidth}\centering
-        \begin{tabular}{c r  l ?? c | c | c}
+        \begin{tabular}{c r  l ? c | c | c}
             % \toprule\toprule
-            \multicolumn{3}{c??}{}  & \multirow{2}{*}[-0.5em]{\textbf{Unsigned Graphs}} & \multicolumn{2}{c}{\textbf{Signed Graphs}}  \\        
+            \multicolumn{3}{c?}{\multirow{2}{*}[-0.5em]{\thead{\textbf{}}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
             % \cmidrule(l{.15em}){4-5}
@@
             % \multicolumn{2}{c||}{} &  &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
-            \multicolumn{3}{c??}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\
+            \multicolumn{3}{c?}{} &  &  \multicolumn{1}{c|}{\thead{No Constraints}} & \thead{With Constraints} \\
 
-            % \midrule[0.15em]
-            \cmidrule[0.15em]{2-6}\morecmidrules \cmidrule[0.15em]{2-6}
+            \midrule[0.3em]
+            % \cmidrule[0.3em]{2-6}
+            % \morecmidrules \cmidrule[0.15em]{2-6}
             % \midrule \midrule
-            \multirow{5}{*}[-1.5em]{\begin{turn}{90}\thead{\textbf{Linkage criteria} $\,\,\interact(S_u ,S_v)$}\end{turn}}  & Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
+            \multirow{5}{*}[-0.5em]{\begin{turn}{90}\thead{\textbf{Linkage criteria} $\,\,\interact(S_u ,S_v)$}\end{turn}}  & Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
 Aggl.
-Clust.} & \thead{Greedy Additive \\ Edge Contraction \cite{keuper2015efficient}} & \thead{Greedy Fixation\\\cite{levinkov2017comparative}} \\
-            \cmidrule[0.07em]{2-6}
+Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} \\
+            % \cmidrule[0.07em]{2-6}
 
-             &\makecell[r]{Absolute \\Max:} & 
+             &\makecell[r]{Absolute Max:} & 
             $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
-               & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Mutex Watershed \\\cite{wolf2018mutex}} & \thead{Mutex Watershed\\\cite{wolf2018mutex}} \\
-              \cmidrule[0.07em]{2-6}
+               & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Mutex Watershed \cite{wolf2018mutex}} \\
+              % \cmidrule[0.07em]{2-6}
              & \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier.
 Aggl.
-Clust.
-\cite{lance1967general}} & \thead{Average Linkage\\Signed Aggl.
-Clust.
-(\textbf{NEW})} & \thead{\textbf{NEW}}\\
-            \cmidrule[0.07em]{2-6}
+Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
+            % \cmidrule[0.07em]{2-6}
            % \midrule
 
-            & Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier.
-Aggl.
-Clust.
-\cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl.
-Clust.
-(\textbf{NEW})} & \thead{\textbf{NEW}}\\
-            \cmidrule[0.07em]{2-6}
+            & Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\ 
+            % \cmidrule[0.07em]{2-6}
 
-            & Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier.
-Aggl.
-Clust.
-\cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl.
-Clust.
-(\textbf{NEW})} & \thead{\textbf{NEW}}
+            & Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}
 

### 2019-05-18 chapters/5_experiments_cityscapes.tex
Start finalizing result section

@@
 \section{Experiments on CityScapes}\label{sec:cityscapes_exp}
-We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing.
+We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
+% recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing.
 Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle.
-For our experiments, we used the state-of-the-art proposal-free pipeline proposed in \cite{liu2018affinity} (GMIS) that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
-Their trained model was publicly available, so we simply replaced their final graph-merging algorithm (GMIS-Agglo) with \algname{}.
+For our experiments, we used the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
+Their trained model was made publicly available, so we simply replaced their final graph-merging algorithm (MultiStepHAC) with \algname{}.
 See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
@@
 Max.}, or false region-merge, like \emph{Sum}.
-GMIS-Agglo requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.
+\UPDATE{In Appendix, Table \ref{tab:extended_results_cityscapes} includes all other tested linkage}.
+MultiStepHAC requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.

### 2019-05-18 chapters/5_experiments_compare_rules.tex
Add more details about CS exps
Start finalizing result section

@@
          % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
-         & \algname{} Linkage & \makecell{Arand-Score}  \\ \midrule \midrule
+         & \algname{} Linkage & \makecell{Arand-Score}  \\ \midrule 
          % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
@@
 DTWS + MC & -& 0.903 $\pm$ 0.017 \\
+DTWS + \algname{} & Average& \TODO{} \\
 % DTWS + avgHC &-& \\
@@
         \end{tabular}
-    \captionof{table}{Arand-Scores on CREMI challenge training data}
+    \captionof{table}{Arand-Scores achieved by Different post-processing methods on CREMI challenge training predictions}
     \label{tab:results_cremi_train}
@@
         \end{tabular}
-    \captionof{table}{\UPDATE{TBD:} Scores on test data}
+    \captionof{table}{Current leaderboard of the CREMI challenge \TODO{Update refs}}
     \label{tab:results_cremi_test}
@@
 The dataset comes from a serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth.
-The results submitted to the leaderboard are evaluated using the CREMI score\footnote{\url{https://cremi.org/leaderboard/}}, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score\cite{arganda2015crowdsourcing}.
+The results submitted to the leaderboard are evaluated using the CREMI score\footnote{\url{https://cremi.org/leaderboard/}}, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}.
 In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.
@@
 To ensure a fair comparison, we test all methods on the same predictions of our CNN model.
-As basic method, we perform a simple thresholding (THRESH) by running connected components on a boundary map generated from the CNN affinities (see Appendix \ref{sec:cremi_details} for all details on this and the following methods).
-On the other hand, almost all state-of-the-art methods for neuron-segmentation first generates 2D superpixels and then apply a graph partitioning algorithm, as we showed in the related work section.
-Superpixels are usually computed with a watershed algorithm seeded at the maxima of a distance transform generated from a boundary map (WSDT).
-In our comparison we use approximated methods of the multicut (MC) and lifted multicut problem (LMC).
+As basic method, we perform a simple thresholding (THRESH) by running connected components on a boundary map generated from the CNN affinities (see Appendix \ref{sec:cremi_details} for more details on this and the following methods).
+On the other hand, most of state-of-the-art methods for neuron-segmentation first generates 2D superpixels and then apply a graph partitioning algorithm, since this approach so far proved to be the most reliable that could scale up to the size of the problem.
+Superpixels are usually computed with a watershed algorithm seeded at the maxima of a boundary distance transform (WSDT).
+The algorithms employed in our comparison to partition the superpixel graph were given by \TODO{\algname{}} (WSDT+\algname{}) or approximations of the multicut (WSDT+MC) and lifted multicut (WSDT+LMC) problems.

### 2019-05-18 chapters/5_experiments_intro.tex
Start finalizing result section

@@
 % We note that the post-processing presented in \cite{lee2017superhuman} did not use any predicted long-range connection, whereas \cite{wolf2018mutex} introduced them with strides of 2 in the XY-plane.
-
-Our CNN model outputs affinities in the form of pseudo-probabilities $p:E \rightarrow [0,1]$, where $p=0$ represents a boundary evidence.
-In order to use them as input of the algorithms in our framework, we mapped them to positive and negative values\footnote{Note that in general attractive and repulsive interactions $w^+$ and $w^-$ can be independently estimated with different classifiers.}.
-The most common approaches use \emph{additive} \cite{ailon2008aggregating} or \emph{logarithmic} \cite{finkel2008enforcing,andres2012globally} mappings:
-\begin{equation} \label{eq:mappings}
-\cost_{e,\mathrm{Add}} = p_e - \beta, \qquad \quad \cost_{e,\mathrm{Log}} = \log \left( \frac{p_e}{1-p_e} \right) - \log \left( \frac{\beta}{1-\beta} \right),
-\end{equation}
-where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation.
-We evaluated both of them empirically with each of the tested linkage and found that the additive mapping is the best option in all cases apart from the \emph{Sum} linkage.
-Note that varying the parameter $\beta$ does not usually define a hierarchy of nested clusterings, thus it is not equivalent to varying a threshold parameter in HAC.
-This hierarchical property is only valid for \algname{} without constraints and with \emph{Average}, \emph{Max} or \emph{Min} linkage.

### 2019-05-18 chapters/5_experiments_noise.tex
Start finalizing result section

@@
 \textbf{Top}: Accuracy given by Rand-Score (higher is better).
-Solid lines represent median values.
+Solid lines represent median values over 30 experiments.
 Values between the 25th and the 75th percentile are shown in shade areas.
-\textbf{Bottom}: Multicut objective (Eq.
+\TODO{Def long-range edges}
+%\textbf{Bottom}: Multicut objective (Eq.
 \ref{eq:multicut_obj}), measuring how balanced the final clusterings are (lower is better); for a clearer comparison, an offset is added to the energy values, so that the method achieving the lowest energy is always assigned to value zero.
@@
 
-\subsection{Results}\label{sec:results}
+\subsection{Results and discussion}\label{sec:results}
 % \subsection{In-depth comparison of different linkage criteria for \algname{}} 
-\TODO{Mention Appendix} The difficulty of the dataset is highlighted by the poor scores achieved by THRESH in Table \ref{tab:results_cremi_train}.
-Among all the signed graph algorithms included in our generalized framework, the less-known one with \emph{Average} linkage consistently outperformed all other previously proposed linkage like \emph{Sum} or \emph{Absolute Max}.
-This simple method also achieved remarkably superior scores to other state-of-the-art multi-step methods.
-\TODO{Wait for new test-scores}
-In Fig.
-\ref{fig:cremi_comparison}, we highlight some failure cases of the different agglomerative algorithms included in our framework.
-In Appendix we provide an extended version of Table \ref{tab:results_cremi_train} including all scores linkage tested with \algname{} on the full CREMI training data.
+\textbf{Comparison results } Table \ref{tab:results_cremi_train} shows how \algname{} compares to other tested methods on the predictions of our CNN. 
+The poor scores achieved by THRESH highlight the difficulty of the task.
+On the other hand, \algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage).
+The remarkably competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem.
+In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with Average linkage even achieved significantly superior scores compared to other methods based on WSDT superpixels.
+Our hypothesis to explain this superior performances it that, currently, there are not good ways of generating superpixels that can take the long-range predictions of the CNN into account.
+It is of course possible to make use of long-range predictions to compute the edge weights of the superpixel graph, but, in our experience, this process usually involves a lot of parameter tuning and trial and error.
+In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets and present an extended version of Table \ref{tab:results_cremi_train} including all tested \algname{} algorithms.
 
-In order to highlight the properties and the strengths of each linkage criteria and  perform an in-depth comparison that is as quantitative as possible, we run an additional set of experiments where we perturbed the CNN predictions with noise.
-In Appendix, we provide all the details about the used type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false boundary evidences (see example in Fig.
-\ref{fig:noisy_affs}).
-
-\UPDATE{Plots in Fig.
-\ref{fig:noise_plots} summarize 6000 experiments: we focused on the best performing linkage criteria, i.e.
-\emph{Average}, \emph{Sum} and \emph{Abs Max}, and tested them with different values of noise, both with and without use of long-range connections in the grid-graph\footnote{We tested 20 values of noise and, for each setup, we averaged the scores over 30 runs.}.
-In Fig.
+\textbf{Noise experiments } In order to highlight the properties of each \algname{} algorithm and  perform an in-depth comparison that is as quantitative as possible, we run an additional set of experiments where we perturbed the CNN predictions with noise.
+Appendix \ref{sec:appendix_noise_gen} introduces the type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false boundary evidences.
+Fig.
+\ref{fig:noise_plots} summarize our 12000 noise experiments: we focused on the best performing linkage criteria, i.e.
+\emph{Average}, \emph{Sum} and \emph{Abs Max}, and tested them with different values of noise, both with and without use of long-range connections in the grid-graph.
+% In Fig.
 \ref{fig:noise_plots}, we used a merge-biased noise decreasing boundary evidence.
@@
 \ref{fig:noise_split} in Appendix for a split-biased version.
-Our findings confirm that \algname{} with \emph{Average} linkage criterion represents the most robust algorithm tested and that is the one benefiting more from additional long-range edge connections.
+
+\textbf{Average and Abs Max linkage } Our findings confirm that \algname{} with \emph{Average} linkage criterion represents the most robust algorithm tested and that is the one benefiting more from additional long-range edge connections.
 Other versions using cannot-link constraints generally lead to an over-segmentation, but are robust to ``leaks through holes'' given by missing boundary evidence.
 The greedy \emph{absolute maximum} linkage proposed by \cite{wolf2018mutex} is the least robust to noise, but, as we show in Table \ref{tab:full_cremi_results}, it represents an efficient and considerably faster option.
-The \emph{Sum} linkage generally outputs the most balanced graph partitioning according to the objective defined in Eq.
+
+\textbf{Sum linkage } The \emph{Sum} linkage generally outputs the most balanced graph partitioning according to the objective defined in Eq.
 \ref{eq:multicut_obj} and is then confirmed to be a good choice for initializing more complex approximations of the multicut optimization problem like \cite{beier2016efficient}.
@@
 In these cases, the use of cannot-link constraints or a more robust average linkage are preferable.
-}
+In Fig. \ref{fig:cremi_comparison}, we highlight some failure cases of the different agglomerative algorithms included in our framework.
+
 \begin{figure}[b]
@@
  & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
- & MultiStepHAC \cite{liu2018affinity} & \UPDATE{33.0} & -  \\
-\multirow{2}{*}{GMIS \cite{liu2018affinity}} & \algname{} Max &   24.3  &   32.5  \\
+\multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & \UPDATE{33.0} & -  \\
+ % & \algname{} Max &   24.3  &   32.5  \\
  & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
  & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
- & \algname{} Min &  0    & 0  \\
+ % & \algname{} Min &  0    & 0  \\
         \end{tabular}
-    \captionof{table}{AP scores on the cityscapes validation set for the generalized algorithm and different types of linkage criteria.  }
+    \captionof{table}{Average Precision (AP) scores on the cityscapes validation set achieved by the tested pipelines}
     \label{tab:results_cityscapes_val}

### 2019-05-18 chapters/6_conclusions.tex
Start finalizing result section

@@
 % !TEX root = ../agglo_clust_review.tex
-\section{Conclusions}
+\section{Conclusion}
+We presented both a theoretical and experimental contribution: ; why average is so cool?
+
+We presented a generalized framework and showed how one of the new algorithms included in it, \algname{} with average linkage, represent a simple agglomerative method that does not require the user to tune parameters or generate superpixels and showed extremely competitive performances in biological images, even on the challenging and competitive task of neuron segmentation.
+(good-quality superpixels are strongly dataset-dependent)
+Compared to previously proposed agglomerative clustering methods for signed graphs, it proved to be the one making best use of the long-range predictions of the CNN; the fact that average is superior to abs max is not surprising, given the literature about HAC with single and average linkage (due to the greediness of the maximum linkage); and enforcing cannot-link constraints, we have also seen that introducing too many long-range mainly repulsive predictions can cause strong over-clustering; tendency to under-clustering of the sum linkage can be explained with the chain-reaction effect and its tendency to grow one cluster at the time that does not allow to build good statistics between adjacent clusters.
+This is partially fixed by constraints, but not really...

### 2019-05-18 chapters/supplementary.tex
Start finalizing result section

@@
       % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
-      % \State $\mathcal{N}_u = \{ t \in V' | e_{ut}\in E'  \}$; $\mathcal{N}_v = \{ t \in V' | e_{vt}\in E'  \}$ 
+      \State $\mathcal{N}_u = \{ t \in \tilde{V} | e_{ut}\in \tilde{E}  \}$
+      \State $\mathcal{N}_v = \{ t \in \tilde{V} | e_{vt}\in \tilde{E}  \}$ 
       \For{$t \in \mathcal{N}_v$ } \Comment{Loop over neighbors in $\tilde{\mathcal{G}}$ of deleted node $v$}
@@
 
-\subsection{Implementation details and complexity of \algname{}}
+\subsection{Implementation details and complexity of \algname{}} \label{sec:detailed_impl}
 
@@
 Moreover, in the next section, we present an efficient implementation of \algname{} with \emph{Absolute Maximum} linkage that has empirical $\mathcal{O}(N \log N)$ complexity.
+\TODO{Empirical complexity plot?}
 
@@
 Let us now contradict the initial hypothesis and assume by absurd that the constrained version of \algname{} introduces a cannot-link constraints between two clusters sharing a positive interaction $\tilde{w}>0$ and outputs a different clustering as compared to the unconstrained version.
-This can happen only in the situation shown in Fig.
-\ref{fig:contradiction_case}, when two clusters $u$ and $v$ are merged together and share a common neighboring node $t$ having the following two properties: a) $u$ and $t$ are already constrained and share a repulsive interaction $w_{ut}\leq0$, b) $v$ and $t$ share an attractive interaction $w_{vt}>0$ that is higher in absolute value $|w_{vt}|>|w_{ut}|$.
+This can happen only in the situation \TODO{shown in Fig.
+\ref{fig:contradiction_case}}, when two clusters $u$ and $v$ are merged together and share a common neighboring node $t$ having the following two properties: a) $u$ and $t$ are already constrained and share a repulsive interaction $w_{ut}\leq0$, b) $v$ and $t$ share an attractive interaction $w_{vt}>0$ that is higher in absolute value $|w_{vt}|>|w_{ut}|$.
 Then, according to Eq. \ref{eq:def_abs_max}, the new merged cluster $uv$ and $t$ are constrained and share a positive interaction. 
@@
 \end{proof}
+
+\subsection{Multicut and correlation clustering } 
+\TODO{Omit completely?} For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^{\mathrm{internal}}_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^{\mathrm{external}}$ the complementary set of edges whose incident nodes belong to distinct clusters:
+\begin{equation}
+E_\Pi^{\mathrm{internal}} \equiv \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \qquad E^{\mathrm{external}}_\Pi \equiv E \setminus E^{\mathrm{internal}}_\Pi.
+\end{equation}
+% \begin{align}
+% E_\Pi^0 &= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \\
+% E^1_\Pi &= E \setminus E^0_\Pi.
+% \end{align}
+The set of edges $E_\Pi^{\mathrm{external}}$ is known as the \emph{multicut} of $\mathcal{G}$ w.r.t.
+clustering $\Pi$.
+The instance of the NP-hard \emph{weighted correlation clustering/multicut problem}
+% w.r.t. $\mathcal{G}(V,E,\cost)$ 
+corresponds to finding the partitioning that optimally balance attraction and repulsion in the graph and is given by the following binary integer program \cite{kappes2011globally,chopra1991multiway,andres2015lifting}:
+\begin{equation}\label{eq:multicut_obj}
+% \min_\Pi \texttt{MC}(\Pi) \equiv
+ \min_\Pi \sum_{e\in E} \cost_e x_e^\Pi,  \qquad \text{where} \quad x^\Pi_e = 
+ \begin{cases} 
+ 1 & \text{if } e\in E^{\mathrm{external}}_\Pi \\
+ 0 & \text{otherwise}.
+ \end{cases}
+\end{equation}
+In the next chapters we will use this objective as measure of how balanced a clustering is.
+
+\subsection{Predicting signed edge weights with a CNN}
+Our CNN model outputs affinities in the form of pseudo-probabilities $p:E \rightarrow [0,1]$, where $p=0$ represents a boundary evidence.
+In order to use them as input of the algorithms in our framework, we mapped them to positive and negative values\footnote{Note that in general attractive and repulsive interactions $w^+$ and $w^-$ can be independently estimated with different classifiers.}.
+The most common approaches use \emph{additive} \cite{ailon2008aggregating} or \emph{logarithmic} \cite{finkel2008enforcing,andres2012globally} mappings:
+\begin{equation} \label{eq:mappings}
+\cost_{e,\mathrm{Add}} = p_e - \beta, \qquad \quad \cost_{e,\mathrm{Log}} = \log \left( \frac{p_e}{1-p_e} \right) - \log \left( \frac{\beta}{1-\beta} \right),
+\end{equation}
+where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation.
+We evaluated both of them empirically with each of the tested linkage and found that the additive mapping is the best option in all cases apart from the \emph{Sum} linkage.
+Note that varying the parameter $\beta$ does not usually define a hierarchy of nested clusterings, thus it is not equivalent to varying a threshold parameter in HAC.
+This hierarchical property is only valid for \algname{} without constraints and with \emph{Average}, \emph{Max} or \emph{Min} linkage.
 
@@
 
-\subsection{\algname{} on the full CREMI dataset}
+\subsection{\algname{} on the full CREMI dataset} \label{sec:appendix_exps_full_cremi}
  \paragraph{Pre-merge processing} For the predictions on the full dataset from the CREMI challenge, we used  the padded volumes provided by the challenge.
@@
 In our experiments, the use of this preprocessing method did not impact the final scores achieved by \algname{} and significantly reduced its runtime.
+On the full datasets, we used only 10 \% of the long-range connections in the pixel-graph, since adding all of them did not improve the scores and only made the simulations much slower and memory inefficient.
 
- \paragraph{Removing small segments} After running \algname{}, we use a simple post-processing step to delete small segments on the boundaries, most of which are given by single-pixel clusters.
-We deleted all regions with less than 200 pixels and used a seeded watershed algorithm to expand the bigger segments.
+ \paragraph{Removing small segments} After running \algname{}, we use a simple post-processing step to delete small segments on the boundaries, most of which are given by single-voxel clusters.
+On the neuron segmentation predictions, we deleted all regions with less than 200 voxels and used a seeded watershed algorithm to expand the bigger segments.
 
@@
 This is not the case in neuron-segmentation, where each neuron should be given by a single 3D connected component in the volume.
-To enforce this, we modified the implementation of \algname{} so that two clusters are merged only when they represent two adjacent supervoxels in the 3D volume and if this condition is not satisfied, the merge is postponed.
-This then avoids the introduction of ``air-bridges'' between segments due to attractive long-range connections in the voxel-graph.
- This approach achieved superior performances to the one proposed in \cite{wolf2018mutex}, where all long-range connections in the voxel-graph are associated to a negative repulsive edge weight.
+In order to enforce it, we modified the implementation of \algname{} so that two clusters are merged only when they represent two adjacent supervoxels in the 3D volume and if this condition is not satisfied, the merge is postponed until there is a direct connection.
+This then avoids the introduction of ``air-bridges'' between segments due to attractive long-range connections in the initial voxel grid-graph.
+ This approach achieved superior performances to the one proposed in \cite{wolf2018mutex}, where all long-range connections in the grid-graph are associated to a negative repulsive edge weight.
 
@@
   %Before to present the results shown in Fig. \ref{fig:noise_plots}, we will first introduce the type of noise that was added to the edge weights.
-% In the set of experiments presented in this article, edge weights are estimated \UPDATE{by using a CNN that predicts how likely two neighboring pixels are to be part of the same cluster}. 
+% In our experiments, edge weights are estimated \UPDATE{by using a CNN that predicts how likely two neighboring pixels are to be part of the same cluster}. 
 Fig.
-\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}a} shows an example of uncertain CNN predictions on a slice of the neuron segmentation dataset.
+\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}a} shows an example of uncertain CNN predictions on a part of the neuron segmentation CREMI dataset.
 We now present a way of modifying the CNN output to introduce additional artifacts like a missing or false boundary evidence.
@@
 Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
+\TODO{Add raw-data (and GT)}
     %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
@@
 The instance-branch of the model was trained with a Binary Cross-Entropy loss, but we noticed how the short-range affinities were biased towards high probabilities, so that a strong short-range boundary evidence was never predicted by the model.
-In \cite{liu2018affinity}, they handle this problem by proposing a modified version of HAC that is done in stages (GMIS-Agglo): initially only short-range affinities are used to run HAC and a low threshold in the hierarchy is chosen to define a first clustering; a new HAC problem including long-range affinities is then initialized with the first clustering; in the method proposed by \cite{liu2018affinity}, these steps are repeated three times.
+In \cite{liu2018affinity}, they handle this problem by proposing a modified version of HAC that is done in stages (MultiStepHAC): initially only short-range affinities are used to run HAC and a low threshold in the hierarchy is chosen to define a first clustering; then a new HAC problem including long-range affinities is  initialized with the first clustering; in the method proposed by \cite{liu2018affinity}, these steps are repeated three times.
 
-Since GMIS-Agglo is a rather complex post-processing method that requires to tune several hyper-parameters, we opted for a different approach.
-We added two 1x1 convolutional layers to the instance-branch model and trained them by using a
+Since MultiStepHAC is a rather complex post-processing method that requires to tune several hyper-parameters, we opted for a different approach to solve the problem of the unbalanced affinities.
+We added two 1x1 convolutional layers to the instance-branch model and trained them by using the same loss used for example by \cite{wolf2018mutex} and is based on the S\o resen-Dice coefficient \cite{dice1945measures,sorensen1948method}.
+Compared to Hamming-distance based loss like Binary Cross-Entropy or Mean Squared Error, the advantage of this loss is its being robust against prediction and / or target sparsity, that is a desirable quality in this application since boundaries between instances can be sparse.
+During training, all the affinities involving at least one pixel belonging to the background were ignored in the loss.
+In this way, these last two layers specialized in improving the predictions of boundary evidence between adjacent instances (especially those belonging to the same class).
+We then considered an average of these new fine-tuned affinities with the original unbalanced ones predicted by the model.
+During the fine-tuning process, only the parameters in the last two layers were updated.
 
-% Mention the main trick in the loss: ignore background pixels (so focus on boundaries).
-
-% Same mapping defined in \ref{eq:mappings}
-
-% Due to the unbalanced nature of the original affinities, we had to perform a parameter-search of the $\beta$ hyper-parameter.
-Since with a certain value of $\beta$ could be optimal for some versions of \algname{} but not others, we decide to perform a parameter search for each version of \algname{} and Table \ref{tab:results_cityscapes_val} lists the best-case performances for each of the methods.
+Before to apply \algname{}, we performed a parameter-search for the bias $\beta$ defined in \ref{eq:mappings}.
+Table \ref{tab:results_cityscapes_val_expanded} lists the best-case performances for each of the methods with the chosen bias $\beta$: note that depending on the version of \algname{}, it was necessary to bias more or less the predicted edge weights.
+\TODO{Add extended table (explain what $\beta=0$ means)}

### 2019-05-19 chapters/supplementary.tex
Updates from Overleaf

--- 2019-05-17 chapters/supplementary.tex
@@
 An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph.
-Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that $\tilde{V} \subseteq V$ and each node $u\in \tilde{V}$ represents the cluster $S_u \in \Pi$ including $u\in V$.
+Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that there exists exactly one representative $|\tilde{V} \cap S| = 1$ for every cluster $S \in \Pi$ .
 Edges in $\tilde{E}$ represent adjacency-relationships between clusters
@@
 Therefore, similarly to a heap-based implementation of hierarchical agglomerative clustering, our implementation of \algname{} has a complexity of $\mathcal{O}(N^2 \log N)$.
-In the worst case, when the graph is dense and $|E|=N^2$, the algorithm requires $\mathcal{O}(N^2)$ memory and does not scale up well.
+In the worst case, when the graph is dense and $|E|=N^2$, the algorithm requires $\mathcal{O}(N^2)$ memory.
 Nevertheless, in our practical applications the graph is much sparser, so $\mathcal{O}(|E|)=\mathcal{O}(N)$.
@@
 With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$.
-Moreover, in the next section, we present an efficient implementation of \algname{} with \emph{Absolute Maximum} linkage that has empirical $\mathcal{O}(N \log N)$ complexity.
+Moreover, in the next section, we present an efficient implementation of \algname{} with \emph{Absolute Maximum} linkage that has empirical $\mathcal{O}(N \log N)$ complexity~\cite{wolf2018mutex}.
 
@@
 We also observe that, in the unconstrained version of \algname{}, the predicate \texttt{canBeMerged} at line 9 can never be false.
-Let us now contradict the initial hypothesis and assume by absurd that the constrained version of \algname{} introduces a cannot-link constraints between two clusters sharing a positive interaction $\tilde{w}>0$ and outputs a different clustering as compared to the unconstrained version.
-This can happen only in the situation shown in Fig.
-\ref{fig:contradiction_case}, when two clusters $u$ and $v$ are merged together and share a common neighboring node $t$ having the following two properties: a) $u$ and $t$ are already constrained and share a repulsive interaction $w_{ut}\leq0$, b) $v$ and $t$ share an attractive interaction $w_{vt}>0$ that is higher in absolute value $|w_{vt}|>|w_{ut}|$.
-Then, according to Eq. \ref{eq:def_abs_max}, the new merged cluster $uv$ and $t$ are constrained and share a positive interaction. 
-But this case can never happen, since if $|w_{vt}|>|w_{ut}|$ then clusters $v$ and $t$ are merged before clusters $u$ and $t$ are constrained.  
+Let us now contradict the initial hypothesis and assume the opposite that the constrained version of \algname{} introduces a cannot-link constraints between two clusters sharing a positive interaction $\tilde{w}>0$ and outputs a different clustering as compared to the unconstrained version.
+This can only happen when two clusters $u$ and $v$ are merged together and share a common neighboring node $t$ having the following two properties: a) $u$ and $t$ are already constrained and share a repulsive interaction $w_{ut}\leq0$, b) $v$ and $t$ share an attractive interaction $w_{vt}>0$ that is higher in absolute value $|w_{vt}|>|w_{ut}|$.
+We have illustrated this event in Fig.
+\ref{fig:contradiction_case}.
+According to Eq. \ref{eq:def_abs_max}, the new merged cluster $uv$ and $t$ are constrained and share a positive interaction. 
+However, this case is impossible, since $|w_{vt}|>|w_{ut}|$ implies that clusters $v$ and $t$ are merged \emph{before} clusters $u$ and $t$ are constrained. 
 \end{proof}

### 2019-05-19 chapters/2_rel_work.tex
Merge comments from Constantin and Steffen

@@
 \textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances.
-For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for joint segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
+For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
 % encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; 
@@
 The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical HC linkage criteria, e.g.
-average linkage \cite{liu2018affinity,lee2017superhuman}, median \cite{funke2018large} or a linkage learned by a neural network \cite{nunez2013machine,knowles2016rhoananet}.
+average linkage \cite{liu2018affinity,lee2017superhuman}, median \cite{funke2018large} or a linkage learned by a random forest classifier \cite{nunez2013machine,knowles2016rhoananet}.
 
@@
 NP-hardness of the \emph{correlation clustering} problem was shown in \cite{bansal2004correlation}, while the connection with graph multicuts was made by \cite{demaine2006correlation}.
-Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy heuristic algorithms \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
+Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
 % \TODO{Cannot-link constraints?}
@@
 
-This work reformulates the clustering algorithms of \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a generalized framework and adopt ideas from the proposal-free methods \cite{liu2018affinity,wolf2018mutex,funke2018large} to predict long-range relationships between pixels.
+This work reformulates the clustering algorithms of \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a generalized framework and adopt ideas from the proposal-free methods \cite{liu2018affinity,wolf2018mutex,lee2017superhuman} to predict long-range relationships between pixels.

### 2019-05-19 chapters/3_algorithm.tex
Merge comments from Constantin and Steffen

@@
 Apart from the linkage criteria defined in Table \ref{tab:linkage-criteria}, additional ones were proposed in the literature:
-\cite{nunez2013machine} for example uses a learned approach where a neural network updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas
+\cite{nunez2013machine} for example uses a learned approach where a random forest classifier updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas
 \cite{funke2018large} uses a \emph{quantile} linkage criteria by populating a histogram for each inter-cluster interaction.

### 2019-05-19 chapters/supplementary.tex
Merge comments from Constantin and Steffen

--- 2019-05-18 chapters/supplementary.tex
@@
 In the \algname{} Algorithm \ref{detailed_alg}, the clustering is updated only when two clusters are merged and the condition at line 9 is satisfied. 
-We also observe that, in the unconstrained version of \algname{}, the predicate \texttt{canBeMerged} at line 9 can never be false.
+We also observe that, in the unconstrained version of \algname{}, the predicate \texttt{canBeMerged} at line 9 can never be false because cannot-link constraints are never introduced at line 14.
 Let us now contradict the initial hypothesis and assume by absurd that the constrained version of \algname{} introduces a cannot-link constraints between two clusters sharing a positive interaction $\tilde{w}>0$ and outputs a different clustering as compared to the unconstrained version.

### 2019-05-19 chapters/3_algorithm.tex
Finalize cremi results section

@@
 \begin{algorithm}[t]
-  \caption{\algname{}: Generalized Algorithm for Signed Graph Agglomerative Clustering}
+  \caption{\algname{}: Generalized Algorithm for Agglomerative Signed Graph Partitioning}
    \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}\texttt{addCannotLinkConstraints}}  \\
@@
 
-\subsection{\algname{}: Generalized Algorithm for Signed Graph Agglomerative Clustering} \label{sec:algorithm}
+\subsection{\algname{}: Generalized Algorithm for Agglomerative Signed Graph Partitioning} \label{sec:algorithm}
 
-\TODO{mention detailed pseudocode} The proposed \algname{} Algorithm \ref{main_alg} uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merges pairs of adjacent clusters.
+In Algorithm \ref{main_alg}, we provide a simplified pseudo-code for the proposed \algname{} algorithm that is based on a bottom-up approach starting with each node assigned to its own cluster and iteratively merges pairs of adjacent clusters.
 It starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
@@
 
-In Appendix \ref{sec:detailed_impl} we comment on the algorithm \UPDATE{computational complexity $\mathcal{O}(N^2 \log N)$} and present an efficient implementation based on an edge contraction algorithm combined with a priority queue.
+In Appendix \ref{sec:detailed_impl}, we comment on the algorithm computational complexity $\mathcal{O}(N^2 \log N)$ and present our efficient implementation given by the edge contraction Algorithm \ref{detailed_alg} using a priority queue.
 

### 2019-05-19 chapters/5_experiments_noise.tex
Finalize cremi results section

@@
 % \subsection{In-depth comparison of different linkage criteria for \algname{}} 
-\textbf{Comparison results } Table \ref{tab:results_cremi_train} shows how \algname{} compares to other tested methods on the predictions of our CNN. 
-The poor scores achieved by THRESH highlight the difficulty of the task.
-On the other hand, \algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage).
+\textbf{Comparison results } Table \ref{tab:results_cremi_train} shows how \algname{} compares to other tested post-processing methods applied to the predictions of our model. 
+% The poor scores achieved by THRESH highlight the difficulty of the task. 
+\algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage).
 The remarkably competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem.
@@
 
-\textbf{Noise experiments } In order to highlight the properties of each \algname{} algorithm and  perform an in-depth comparison that is as quantitative as possible, we run an additional set of experiments where we perturbed the CNN predictions with noise.
+\textbf{Noise experiments } Fig.
+\ref{fig:cremi_comparison} highlights some failure cases of the different agglomerative algorithms included in our framework.
+Additionally, we run a set of experiments where the CNN predictions are perturbed by noise, in order to highlight the properties of each \algname{} algorithm and perform an in-depth comparison that is as quantitative as possible.
 Appendix \ref{sec:appendix_noise_gen} introduces the type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false boundary evidences.
@@
 
-\textbf{Average and Abs Max linkage } Our findings confirm that \algname{} with \emph{Average} linkage criterion represents the most robust algorithm tested and that is the one benefiting more from additional long-range edge connections.
-Other versions using cannot-link constraints generally lead to an over-segmentation, but are robust to ``leaks through holes'' given by missing boundary evidence.
-The greedy \emph{absolute maximum} linkage proposed by \cite{wolf2018mutex} is the least robust to noise, but, as we show in Table \ref{tab:full_cremi_results}, it represents an efficient and considerably faster option.
+\textbf{Average and Abs Max linkage } Our findings confirm that \algname{} with \emph{Average} linkage criterion represents the most robust algorithm tested and the one that benefits the most from using the long-range CNN predictions.
+On the other hand, it is not a surprise that the \emph{Abs Max} statistic proposed by \cite{wolf2018mutex} is less robust to noise than the \emph{Average} linkage, but, as we show in the Appendix \TODO{Table \ref{tab:full_cremi_results}}, \emph{Abs Max} represents a valid and considerably faster option.
+Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights, then \algname{} with cannot-link constraints shows a clear tendency to over-cluster.
 
-\textbf{Sum linkage } The \emph{Sum} linkage generally outputs the most balanced graph partitioning according to the objective defined in Eq.
+\textbf{Sum linkage } 
+% The \emph{Sum} linkage generally outputs the most balanced graph partitioning according to the objective defined in Eq.
 \ref{eq:multicut_obj} and is then confirmed to be a good choice for initializing more complex approximations of the multicut optimization problem like \cite{beier2016efficient}.
-Nevertheless, in more challenging parts of the data (see Fig.
-\ref{fig:cremi_comparison}) or in the presence of noise, it often incorrectly merge regions together, leading to more unbalanced graph partitioning.
-In these cases, the use of cannot-link constraints or a more robust average linkage are preferable.
-In Fig. \ref{fig:cremi_comparison}, we highlight some failure cases of the different agglomerative algorithms included in our framework.
+All our experiments, as well as the examples in Fig.
+\ref{fig:cremi_comparison}, show that \algname{} with \emph{Sum} linkage is the algorithm with the highest probability of under-clustering and incorrectly merging segments.
+This is strongly related to the  empirical observation highlighted in Fig.
+\ref{fig:intro_figure}, where it is shown that the agglomeration order given by \algname{} with \emph{Sum} linkage is clearly different as compared to those given by other linkage criteria like \emph{Average} or \emph{Abs Max}.
+Particularly, a \emph{Sum} statistic tends to grow clusters one after the other.
+The intuitive explanation behind this is the following: initially, most of the infra-cluster nodes present similar attractive interactions between each others; when the two nodes sharing the most attractive interaction are merged, there is a high chance that they both share an attractive interaction with a common neighboring node, so the new interaction with this common neighbor will be immediately assigned to a high priority in the agglomeration, given by the sum of two high weights; this usually starts a ``chain reaction'', where only a single cluster is agglomerated at the beginning.
+On the other hand, other linkage criteria grow clusters of similar sizes in parallel and accumulate more valuable statistics between the clusters.
 

### 2019-05-19 chapters/0_abstract.tex
Finish polishing intro, abstract, conclusions

--- 2019-05-14 chapters/0_abstract.tex
@@
 mutual exclusion between clusters.
-These different combinations then correspond to existing clustering methods as well as new algorithms that we introduce and analyze.
-We evaluate these different algorithms on instance segmentation, which is the task of partitioning an image into distinct segments, by predicting edge weights with a CNN.
-\UPDATE{Summarize results}
+We then prove how these different combinations correspond to existing clustering methods as well as new algorithms that we introduce and analyze.
+An extensive comparison study is performed to evaluate properties of the clustering algorithms, e.g.
+robustness and efficiency, by applying them to instance segmentation, which is the task of partitioning an image into distinct segments.
+% and by predicting edge weights with a CNN. 
+We then show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and the CityScapes dataset.
 \end{abstract}

### 2019-05-19 chapters/1_intro.tex
Finish polishing intro, abstract, conclusions

--- 2019-05-14 chapters/1_intro.tex
@@
 \section{Introduction}
-The clustering of weighted graphs has been successfully applied to such tasks as image segmentation, tracking... \UPDATE{REFS}
-Most graph clustering methods work with positive edge weights only, representing similarities or distances between the nodes.
+\UPDATE{\today,\currenttime} -  In computer vision, the clustering of weighted graphs has been successfully applied to such tasks as image segmentation, object tracking and pose estimation.
+%image segmentation, object tracking, stereo matching, etc.), to high-level tasks (e.g.
+image classification, object recognition, image parsing
+% to model many types of re- lations and processes in physical, biological, social and information systems
+Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes.
 These methods are parameter-based and require users to specify the desired numbers of clusters or a termination criterion (e.g.
-spectral clustering or iterated normalized cuts) or even a stronger version of supervision in terms of seeds (e.g.
+spectral clustering or iterated normalized cuts) or even a supervision in terms of seeds (e.g.
 seeded watershed or random walker).
-Hierarchical clustering (HC) is a popular graph clustering method, which creates a hierarchy of clusters.
-Agglomerative HC is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}.
+%Hierarchical clustering is a popular graph clustering method, which creates a hierarchy of clusters.
+Hierarchical agglomerative clustering (HAC) is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}.
 This method usually requires the user to choose a level in the cluster hierarchy defining the desired output clustering.
@@
 Other graph clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between nodes.
-The advantage of using signed graphs over positive-weight graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters.
+The advantage of using signed graphs over positive-weighted graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters.
 This can be done optimally by solving the so-called \emph{multicut optimization} or \emph{correlation clustering} problem \cite{kappes2011globally,chopra1991multiway}.
-However, this problem is NP-hard, so instead of finding optimal solutions, most of the methods perform approximations.
-Greedy agglomerative clustering algorithms are among the most efficient methods \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}.
+However, this problem is NP-hard, so instead of finding optimal solutions, several greedy agglomerative clustering algorithms were proposed.
 % Some of these methods \cite{levinkov2017comparative,wolf2018mutex} dynamically introduce cannot-link constraints, representing mutual exclusion relationships between clusters.
 
-Thus, greedy agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter free and efficient.
-Despite the fact that there exist a variety of these algorithms, there has been no overarching studies comparing them and making it possible to choose the most appropriate algorithm for particular applications and assess their properties, e.g.
+Thus, agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter free and efficient.
+Despite the fact that there exist a variety of these algorithms \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}, there has been no overarching studies comparing them and making it possible to choose the most appropriate algorithm for particular applications and assess their properties, e.g.
 robustness and efficiency.
@@
 
-In this paper, we propose a novel theoretical framework for generalizing over the greedy agglomerative clustering algorithms for signed graphs by linking these algorithms to the agglomerative HC.
-This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}, i.e.
-mutual exclusion between clusters, in a consistent way.
-These different combinations then correspond to existing clustering algorithms as well as allows us to introduce and explore new algorithms.
-The framework can also be easily expended to accommodate additional linkage criteria.
-
+In this paper, we propose a novel theoretical framework for generalizing over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering, which is a popular bottom-up approach defining an hierarchy of clusters on positive-weighted graphs \cite{lance1967general}.
+This framework defines an underlying basic algorithm and allows us to explore in a consistent way its combinations with different linkage criteria and \emph{cannot-link constraints}, i.e.
+mutual exclusion between clusters.
+We then theoretically prove that different combinations correspond to existing clustering algorithms as well as new algorithms that we introduce and explore.
+% The framework can also be easily expended to accommodate additional linkage criteria.
 %As a first contribution, we reformulate several of these recently proposed graph agglomerative algorithms in a simple review framework (Sec.
@@
 
-We then evaluate and compare these algorithms on \emph{instance segmentation}, which is a computer vision task consisting in assigning each pixel of an image to an object instance.
+We evaluate and compare these algorithms on \emph{instance segmentation}, which is a computer vision task consisting in assigning each pixel of an image to an object instance.
 %, where the number of instances is usually not known in advance.
@@
 % For our experiments, we focus on a \emph{proposal-free} deep learning method that does not involve object detection but directly group pixels into object instances. 
-Recently, there has been a growing interest for such \emph{proposal-free} methods that do not involve object detection, since in certain types of data objects cannot be approximated by bounding boxes.
 %  (for example in electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing})
 
-By applying this method both to 2D urban scenes from the CityScapes dataset and the challenging neuron-segmentation task of 3D EM image stacks, \UPDATE{we show how one of the less-known algorithms included in our framework consistently outperformed all other previously proposed signed graph clustering methods and achieved comparable/superior scores to other complex multi-step pipelines...}
-% Most recently, success in instance segmentation (IS) has been achieved by applying deep learning and there are two main types of successful deep learning approaches to IS: proposal-based \cite{he2017mask,dai2016instance,li2017fully} and proposal-free \cite{kong2018recurrent,novotny2018semi,kulikov2018instance,kirillov2017instancecut} methods.
-Proposal-based methods consist of two steps: detecting objects, for example by finding bounding boxes, and assigning pixels to the detected instances.
-Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing}, where objects are not approximated well by bounding boxes.
-% More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)
-% Thus, there is a growing interest for more efficient proposal-free methods that perform IS by directly predicting \UPDATE{pixel features} and then grouping pixels into object instances.
-In this work, we focus on a common proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance.
-Recently, this approach was successfully applied both to neuron segmentation of 3D EM image stacks \cite{lee2017superhuman,wolf2018mutex} and instance segmentation of 2D urban scenes \cite{liu2018affinity}, where it achieved performances superior and comparable, respectively, to proposal-based methods.
-% In this approach, the output of the CNN can be represented as a weighted grid graph such that each node represents a pixel of the image and the weights of the edges define interactions between the pixels.
-A graph clustering algorithm is then applied to cluster pixels into instances.
-% Finally, the algorithms included in the framework are evaluated on an instance segmentation task, both on 3D biological image stacks (Sec.
-\ref{sec:neuro_segm_exp}) and 2D urban scenes (Sec.
-\ref{sec:cityscapes_exp}).
-Our analysis highlights strengths and weaknesses of each algorithm by comparing their robustness to noise, efficiency and inclination to output a well balanced graph partitioning.
+With our comparison experiments, performed both on 2D urban scenes and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
+Our findings show that one of the new agglomerative algorithms introduced by our generalized framework, based on an average linkage criterion, consistently outperforms all other previously known agglomerative algorithms for signed graphs and achieves competitive scores on the challenging CREMI 2016 segmentation benchmark.
+% This simple agglomerative algorithm also achieves competitive scores on the challenging CREMI 2016 segmentation benchmark, similarly to other approaches that rely on complex multi-step pipelines.
 
@@
 (\textbf{c}) Agglomeration order, representing which pairs of neighboring pixels were merged first (white), later on (brown), or never (black).
+ \TODO{re-arrange, show affinities and replace unsigned case with Abs Max}
 %We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 

### 2019-05-19 chapters/3_algorithm.tex
Finish polishing intro, abstract, conclusions

@@
 
-\section{Generalized framework for Signed Graph Agglomerative Clustering} \label{sec:general_framework}
-In this section, we first define the graph notation in Sec.~\ref{sec:notation} and then introduce one of our main contributions: a signed graph partitioning algorithm (Sec.
+\section{Generalized Framework for Agglomerative Clustering of Signed Graphs} \label{sec:general_framework}
+In this section, we first define notation and then introduce one of our main contributions: a signed graph partitioning algorithm (Sec.
 \ref{sec:algorithm}) that can be seen as a generalization of several existing and new clustering algorithms (Sec.
@@
 
-We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes, in which nodes can represent either pixels, superpixels or voxels.
+We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes.
+In computer vision applications, the nodes can represent either pixels, superpixels or voxels.
 We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $\,S_i \cap S_j = \emptyset$ for each $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
@@
 
-\textbf{Inter-cluster interaction } We call two clusters $S_1,S_2$ \emph{adjacent} if there exists at least one edge ${e_{uv}\in E}$ connecting a node $u\in S_1$ to a node $v\in S_2$.
-In agglomerative HC, the interaction $\interact(S_1,S_2)$ between the two clusters is usually defined as a function, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S_1$ and $S_2$.
+\textbf{Inter-cluster interaction } We call two clusters $S_i,S_j$ \emph{adjacent} if there exists at least one edge ${e_{uv}\in E}$ connecting a node $u\in S_i$ to a node $v\in S_j$.
+In agglomerative HC, the interaction $\interact(S_i,S_j)$ between the two clusters is usually defined as a function, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S_i$ and $S_j$.
 All the linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
@@
         \includegraphics[width=\textwidth]{./figs/example_with_constr.pdf}
-        \caption{With constraints}\label{subfig:with_constraints}
+        \caption{With cannot-link constraints}\label{subfig:with_constraints}
     \end{subfigure}
@@
         \EndIf
-      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \big[all adjacent clusters are constrained\big]}
+      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \big[all adjacent clusters have cannot-link constraints\big]}
         % \If{({\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
@@
 \caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge \cite{cremiChallenge} training data.
-Only the few wrongly segmented regions are highlighted in colors.
+Only the few \emph{wrongly} segmented regions are highlighted in colors.
+Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.
 Red arrows point to wrongly split regions.
@@
 The Mutex Watershed \cite{wolf2018mutex} is another signed graph partitioning algorithm that introduces dynamical cannot-link constraints.
-In Appendix \ref{sec:equivalence_MWS} we prove that it can be seen as an efficient implementation of \algname{} with \emph{Absolute maximum} linkage (see def.
+In Appendix \ref{sec:appendix_abs_max} we prove that it can be seen as an efficient implementation of \algname{} with \emph{Absolute maximum} linkage (see def.
 in Table \ref{tab:linkage-criteria}) and observe that in this case \algname{} returns the same clustering with or without enforcing cannot-link constraints.
-\UPDATE{Less-known options: \emph{Average}, \emph{Max} or \emph{Min} linkage applied to signed graphs or never combined with cannot-link constraints.}
+On the other hand, to our knowledge, \emph{Average}, \emph{Max} or \emph{Min} linkage criteria have never been used for signed graphs agglomerative algorithms or been combined with cannot-link constraints.
 

### 2019-05-19 chapters/5_experiments_compare_rules.tex
Finish polishing intro, abstract, conclusions

@@
 DTWS + MC & -& 0.903 $\pm$ 0.017 \\
-DTWS + \algname{} & Average& \TODO{} \\
 % DTWS + avgHC &-& \\
@@
 THRESH &-& 0.221  $\pm$ 0.067 \\ 
+DTWS + \algname{} & Average& \TODO{} \\
 % DTWS  & -& 0.010 $\pm$ 0.003\\
         \end{tabular}
-    \captionof{table}{Arand-Scores achieved by Different post-processing methods on CREMI challenge training predictions}
+    \captionof{table}{Arand-Scores achieved by different post-processing methods on CREMI challenge training predictions}
     \label{tab:results_cremi_train}
@@
 
-\subsection{CREMI Challenge} \label{sec:cremi_challenge}
+\subsection{Data: CREMI Challenge} \label{sec:cremi_challenge}
 We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available.
@@
 Superpixels are usually computed with a watershed algorithm seeded at the maxima of a boundary distance transform (WSDT).
-The algorithms employed in our comparison to partition the superpixel graph were given by \TODO{\algname{}} (WSDT+\algname{}) or approximations of the multicut (WSDT+MC) and lifted multicut (WSDT+LMC) problems.
+The algorithms employed in our comparison to partition the superpixel graph were given by \algname{} (WSDT+\algname{}) or approximations of the multicut (WSDT+MC) and lifted multicut (WSDT+LMC) problems.

### 2019-05-19 chapters/5_experiments_noise.tex
Finish polishing intro, abstract, conclusions

@@
 \ref{eq:multicut_obj} and is then confirmed to be a good choice for initializing more complex approximations of the multicut optimization problem like \cite{beier2016efficient}.
-All our experiments, as well as the examples in Fig.
-\ref{fig:cremi_comparison}, show that \algname{} with \emph{Sum} linkage is the algorithm with the highest probability of under-clustering and incorrectly merging segments.
-This is strongly related to the  empirical observation highlighted in Fig.
-\ref{fig:intro_figure}, where it is shown that the agglomeration order given by \algname{} with \emph{Sum} linkage is clearly different as compared to those given by other linkage criteria like \emph{Average} or \emph{Abs Max}.
-Particularly, a \emph{Sum} statistic tends to grow clusters one after the other.
-The intuitive explanation behind this is the following: initially, most of the infra-cluster nodes present similar attractive interactions between each others; when the two nodes sharing the most attractive interaction are merged, there is a high chance that they both share an attractive interaction with a common neighboring node, so the new interaction with this common neighbor will be immediately assigned to a high priority in the agglomeration, given by the sum of two high weights; this usually starts a ``chain reaction'', where only a single cluster is agglomerated at the beginning.
-On the other hand, other linkage criteria grow clusters of similar sizes in parallel and accumulate more valuable statistics between the clusters.
+All our experiments show that \algname{} with \emph{Sum} linkage is the algorithm with the highest tendency to under-cluster and incorrectly merge segments (see Fig.
+\ref{fig:cremi_comparison} for an example).
+This property is related to the empirical observation that a \emph{Sum} statistic tends to grow clusters one after the other, as shown in Fig.
+\ref{fig:intro_figure} by the quite unique agglomeration order of the \emph{Sum} statistic.
+An intuitive explanation of this fact is the following: initially, most of the infra-cluster nodes present similar attractive interactions between each others; when the two nodes sharing the most attractive interaction are merged, there is a high chance that they both share an attractive interaction with a common neighboring node, so the new interaction with this common neighbor will be immediately assigned to a high priority in the agglomeration, given by the sum of two high weights; this usually starts a ``chain reaction'', where only a single cluster is agglomerated at the beginning.
+On the other hand, as we also see in Fig.
+\ref{fig:intro_figure}, other linkage criteria like \emph{Average} or \emph{Abs Max} grow clusters of similar sizes in parallel and accumulate in this way much more reliable inter-cluster statistics.
 

### 2019-05-19 chapters/6_conclusions.tex
Finish polishing intro, abstract, conclusions

--- 2019-03-14 chapters/6_conclusions.tex
@@
 % !TEX root = ../agglo_clust_review.tex
-\section{Conclusions}
+\section{Conclusion}
+We have presented a novel theoretical framework for agglomerative clustering of graphs with both positive and negative weights and we have shown that several existing clustering algorithms, like the Mutex Watershed, can be reformulated as special cases of one underlying agglomerative algorithm.
+This framework also allowed us to introduce new algorithms, one of which (based on an average linkage) outperformed all the others and proved to be a simple and remarkably robust approach to process short- and long-range predictions of a CNN applied to an instance segmentation task.
+On biological images, this simple average agglomeration algorithm can represent a valuable choice for an user that is not willing to spend a lot of time tuning complex task-dependent pipelines.
+% or test several dataset-dependent
+
+In future work we plan to extend the comparison to other types of graphs and explore common theoretical properties of the algorithms included in the framework.
+% We presented a generalized framework and showed how one of the new algorithms included in it, \algname{} with average linkage, represent a simple agglomerative method that does not require the user to tune parameters or generate superpixels and showed extremely competitive performances in biological images, even on the challenging and competitive task of neuron segmentation.
+(good-quality superpixels are strongly dataset-dependent)
+% Compared to previously proposed agglomerative clustering methods for signed graphs, it proved to be the one making best use of the long-range predictions of the CNN; the fact that average is superior to abs max is not surprising, given the literature about HAC with single and average linkage (due to the greediness of the maximum linkage); and enforcing cannot-link constraints, we have also seen that introducing too many long-range mainly repulsive predictions can cause strong over-clustering; tendency to under-clustering of the sum linkage can be explained with the chain-reaction effect and its tendency to grow one cluster at the time that does not allow to build good statistics between adjacent clusters.
+This is partially fixed by constraints, but not really...

### 2019-05-20 chapters/3_algorithm.tex
Update figs and re-arrange

@@
 
-We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes.
+\TODO{Update inconsistent notation}We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes.
 In computer vision applications, the nodes can represent either pixels, superpixels or voxels.
@@
 \includegraphics[width=\textwidth]{./figs/comparison.pdf} % left bottom right top
-\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge \cite{cremiChallenge} training data.
+\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data.
 Only the few \emph{wrongly} segmented regions are highlighted in colors.
@@
 Green arrows indicate challenging, but correctly segmented regions.
+The average linkage without cannot-link constraints achieved an almost error-free segmentation.
 % Only the involved segments are colored.

### 2019-05-20 chapters/5_experiments_cityscapes.tex
Finalize cremi results section
Update figs and re-arrange

@@
 Max.}, or false region-merge, like \emph{Sum}.
-\UPDATE{In Appendix, Table \ref{tab:extended_results_cityscapes} includes all other tested linkage}.
+In Appendix, \TODO{Table \ref{tab:extended_results_cityscapes}} includes all other tested linkage.
 MultiStepHAC requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.
+
+\begin{figure}[t]
+\centering
+\begin{minipage}[T]{0.59\textwidth}
+    \centering
+    \footnotesize
+        \begin{tabular}{l|l|cc}
+           & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
+          Pipeline & method & \textsc{No} & \textsc{Yes} \\ \midrule
+DWT \cite{bai2017deep} & - & 21.2 & - \\
+SGN \cite{liu2017sgn} & - & 29.2 & - \\
+Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
+ & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
+\multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & \UPDATE{33.0} & -  \\
+ % & \algname{} Max &   24.3  &   32.5  \\
+ & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
+ & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
+ % & \algname{} Min &  0    & 0  \\
+        \end{tabular}
+    \captionof{table}{Average Precision (AP) scores on the cityscapes validation set achieved by the tested pipelines}
+    \label{tab:results_cityscapes_val}
+\end{minipage}\hfill
+\begin{minipage}[T]{0.37\textwidth}
+    \centering
+\includegraphics[width=\textwidth]{./figs/cityscapes_compare_2.pdf} % left bottom right top
+\end{minipage}
+\end{figure}

### 2019-05-20 chapters/5_experiments_compare_rules.tex
Update figs and re-arrange

@@
 % !TEX root = ../agglo_clust_review.tex
-
-\begin{figure}
-        \centering
-\begin{minipage}[T]{0.48\textwidth}
-% \begin{table}
-    \centering
-    \scriptsize
-    % \begin{subtable}[t!]{0.5\textwidth}\centering
-        \begin{tabular}{l|l|c}
-        % \toprule
-        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
-         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
-         & \algname{} Linkage & \makecell{Arand-Score}  \\ \midrule 
-         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
-\textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
-Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
-DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
-DTWS + MC & -& 0.903 $\pm$ 0.017 \\
-% DTWS + avgHC &-& \\
-% DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
-% DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
-Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
-GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
-THRESH &-& 0.221  $\pm$ 0.067 \\ 
-DTWS + \algname{} & Average& \TODO{} \\
-% DTWS  & -& 0.010 $\pm$ 0.003\\
-        \end{tabular}
-    \captionof{table}{Arand-Scores achieved by different post-processing methods on CREMI challenge training predictions}
-    \label{tab:results_cremi_train}
-\end{minipage}\hfill
-\begin{minipage}[T]{0.48\textwidth}
-    \centering
-    \scriptsize
-        \begin{tabular}{l|c|c}
-         & \makecell{CREMI \\Score} & \makecell{Arand\\Score} \\ \midrule
-Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
-PNI-UNet & 0.228 & 0.116 \\
-Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
-MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
-CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
-LFC \cite{parag2017anisotropic} & 0.616 & \\
-        \end{tabular}
-    \captionof{table}{Current leaderboard of the CREMI challenge \TODO{Update refs}}
-    \label{tab:results_cremi_test}
-\end{minipage}
-\end{figure}
 

### 2019-05-20 chapters/5_experiments_noise.tex
Update figs and re-arrange

@@
 % !TEX root = ../agglo_clust_review.tex
-%
 
+\subsection{Results and discussion}\label{sec:results}
+% \subsection{In-depth comparison of different linkage criteria for \algname{}} 
+\textbf{Comparison results } Table \ref{tab:results_cremi_train} shows how \algname{} compares to other tested post-processing methods applied to the predictions of our model. 
+% The poor scores achieved by THRESH highlight the difficulty of the task. 
+\algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage).
+The remarkably competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem.
+In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with Average linkage even achieved significantly superior scores compared to other methods based on WSDT superpixels.
+Our hypothesis to explain this superior performances it that, currently, there are not good ways of generating superpixels that can take the long-range predictions of the CNN into account.
+It is of course possible to make use of long-range predictions to compute the edge weights of the superpixel graph, but, in our experience, this process usually involves a lot of parameter tuning and trial and error.
+In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets and present an extended version of Table \ref{tab:results_cremi_train} including all tested \algname{} algorithms.
+
+\begin{figure}[t]
+        \centering
+\begin{minipage}[t]{0.48\textwidth}
+% \begin{table}
+    \centering
+    \scriptsize
+    % \begin{subtable}[t!]{0.5\textwidth}\centering
+        \begin{tabular}[t]{l|l|c}
+        % \toprule
+        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
+         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
+         & \makecell[l]{\algname{}\\ Linkage} & \makecell{Arand-Score \\(higher is better)} \\ \midrule 
+         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
+\textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
+Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
+DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
+DTWS + MC & -& 0.903 $\pm$ 0.017 \\
+% DTWS + avgHC &-& \\
+% DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
+% DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
+Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
+GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
+THRESH &-& 0.221  $\pm$ 0.067 \\ 
+DTWS + \algname{} & Average& \TODO{} \\
+% DTWS  & -& 0.010 $\pm$ 0.003\\
+        \end{tabular}
+    \captionof{table}{Arand-Scores achieved by different post-processing methods on CREMI challenge training predictions}
+    \label{tab:results_cremi_train}
+\end{minipage}\hfill
+\begin{minipage}[t]{0.48\textwidth}
+    \centering
+    \scriptsize
+        \begin{tabular}[t]{l|c}
+         & \makecell{CREMI Score \\(lower is better)}  \\ \midrule
+Our UNet + DTWS + LMC &  \textbf{0.221}\\
+PNI-UNet & 0.228 \\
+Our UNet + \algname{} Avg-Linkage & 0.244 \\
+MALA-UNet + MC \cite{funke2018large} & 0.276 \\
+CRUNet \cite{zeng2017deepem3d} & 0.566  \\
+LFC \cite{parag2017anisotropic} & 0.616  \\
+% Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
+% PNI-UNet & 0.228 & 0.116 \\
+% Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
+% MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
+% CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
+% LFC \cite{parag2017anisotropic} & 0.616 & \\
+        \end{tabular}
+        \vspace*{2.3em}
+    \captionof{table}{Current leaderboard of the CREMI challenge \TODO{Update refs and check}}
+    \label{tab:results_cremi_test}
+\end{minipage}
+\end{figure}
+\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
 \begin{figure}
 \centering
+    %     \begin{subfigure}[t]{0.49 \textwidth}
+    %     \centering
+    %     \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}
+
+    %     \caption{Without long-range edges: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
+    % \end{subfigure} \hfill
+    % \begin{subfigure}[t]{0.49 \textwidth}
+    %     \centering
+    %     \includegraphics[width=\textwidth,trim=0.53in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_long_range.pdf}
+    %     \caption{With long-range edges: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
+    % \end{subfigure}
     \begin{subfigure}[t]{0.49 \textwidth}
         \centering
-        \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}
-
-        \caption{Without long-range edges: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
+        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_0.pdf}
+        % \caption{Without long-range edges: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
     \end{subfigure} \hfill
@@
         \centering
-        \includegraphics[width=\textwidth,trim=0.53in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_long_range.pdf}
-        \caption{With long-range edges: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
+        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
+        % \caption{With long-range edges: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
     \end{subfigure}
-\caption{Performances of \algname{} with different linkage criteria on a crop of CREMI training data sample B, depending on the amount of noise (x-axis) added to the CNN predictions.
-\textbf{Top}: Accuracy given by Rand-Score (higher is better).
+
+        \begin{subfigure}[t]{0.49 \textwidth}
+        \centering
+        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.2in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
+        \caption{Without long-range edges} \label{fig:merge_noise_only_direct}
+    \end{subfigure} \hfill
+    \begin{subfigure}[t]{0.49 \textwidth}
+        \centering
+        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.20in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
+        \caption{With 10\% long-range edges} \label{fig:merge_noise_with_long_range}
+    \end{subfigure}
+\caption{\algname{} sensitivity to noise: performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions.
+In all experiments the average linkage proved to be the most robust.
 Solid lines represent median values over 30 experiments.
 Values between the 25th and the 75th percentile are shown in shade areas.
-\TODO{Def long-range edges}
+The two set of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details).
+On the right, 10\% of the long-range CNN predictions were randomly added to the grid-graph.
 %\textbf{Bottom}: Multicut objective (Eq.
@@
 \end{figure}
-
 % \begin{minipage}[b]{0.48\textwidth}
@@
 %         \includegraphics[width=0.98\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}
-
 %         \captionof{subfigure}{Merge-biased opensimplex noise} \label{fig:thresh}
@@
 % % \end{figure}
-
-\subsection{Results and discussion}\label{sec:results}
-% \subsection{In-depth comparison of different linkage criteria for \algname{}} 
-\textbf{Comparison results } Table \ref{tab:results_cremi_train} shows how \algname{} compares to other tested post-processing methods applied to the predictions of our model. 
-% The poor scores achieved by THRESH highlight the difficulty of the task. 
-\algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage).
-The remarkably competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem.
-In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with Average linkage even achieved significantly superior scores compared to other methods based on WSDT superpixels.
-Our hypothesis to explain this superior performances it that, currently, there are not good ways of generating superpixels that can take the long-range predictions of the CNN into account.
-It is of course possible to make use of long-range predictions to compute the edge weights of the superpixel graph, but, in our experience, this process usually involves a lot of parameter tuning and trial and error.
-In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets and present an extended version of Table \ref{tab:results_cremi_train} including all tested \algname{} algorithms.
 
@@
 \ref{fig:intro_figure}, other linkage criteria like \emph{Average} or \emph{Abs Max} grow clusters of similar sizes in parallel and accumulate in this way much more reliable inter-cluster statistics.
-
-\begin{figure}[b]
-\centering
-\begin{minipage}[T]{0.59\textwidth}
-    \centering
-    \footnotesize
-        \begin{tabular}{l|l|cc}
-           & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
-          Pipeline & method & \textsc{No} & \textsc{Yes} \\ \midrule
-DWT \cite{bai2017deep} & - & 21.2 & - \\
-SGN \cite{liu2017sgn} & - & 29.2 & - \\
-Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
- & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
-\multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & \UPDATE{33.0} & -  \\
- % & \algname{} Max &   24.3  &   32.5  \\
- & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
- & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
- % & \algname{} Min &  0    & 0  \\
-        \end{tabular}
-    \captionof{table}{Average Precision (AP) scores on the cityscapes validation set achieved by the tested pipelines}
-    \label{tab:results_cityscapes_val}
-\end{minipage}\hfill
-\begin{minipage}[T]{0.37\textwidth}
-    \centering
-\includegraphics[width=\textwidth]{./figs/cityscapes_compare_2.pdf} % left bottom right top
-\end{minipage}
-\end{figure}

### 2019-05-20 chapters/3_algorithm.tex
Update formalism and minor changes

@@
 
-\TODO{Update inconsistent notation}We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes.
+We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes.
 In computer vision applications, the nodes can represent either pixels, superpixels or voxels.
-We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $\,S_i \cap S_j = \emptyset$ for each $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
+We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{S\in\Pi} S $, $\,S \cap \tilde{S} = \emptyset$ for different clusters $S, \tilde{S}\in \Pi$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
 We also denote as $S_u$ the cluster associated with node $u$.
@@
 % In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. 
-The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms \UPDATE{REFS} for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}.
-On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters.
+The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates to every edge a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms \UPDATE{REFS} for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}.
+On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates to each edge a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters.
 Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are also often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring positive and negative edge weights $\cost_e\in \mathbb{R}$.
@@
 
-\textbf{Inter-cluster interaction } We call two clusters $S_i,S_j$ \emph{adjacent} if there exists at least one edge ${e_{uv}\in E}$ connecting a node $u\in S_i$ to a node $v\in S_j$.
-In agglomerative HC, the interaction $\interact(S_i,S_j)$ between the two clusters is usually defined as a function, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S_i$ and $S_j$.
+\textbf{Inter-cluster interaction } We call two clusters $S_u,S_v$ \emph{adjacent} if there exists at least one edge ${e_{ts}\in E}$ connecting a node $t\in S_u$ to a node $s\in S_v$.
+In hierarchical agglomerative clustering, the interaction $\interact(S_u,S_v)$ between the two clusters is usually defined as a function $\interact{}:\Pi \times \Pi \rightarrow \mathbb{R}$, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S_u$ and $S_v$, i.e.
+$E_{uv}=(S_u \times S_v) \cap E$.
 All the linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
@@
 In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
- the algorithm performs a standard agglomerative HC by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see left panel of Fig.
+ the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see left panel of Fig.
 \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} and Table \ref{tab:linkage-criteria}, unsigned graphs).

### 2019-05-20 chapters/supplementary.tex
Finish polishing intro, abstract, conclusions
Update figs and re-arrange
Update formalism and minor changes

@@
 
-\subsection{Properties of \algname{} with \emph{Absolute Maximum} linkage}
+\subsection{Properties of \algname{} with \emph{Absolute Maximum} linkage}\label{sec:appendix_abs_max}
 \paragraph{Remark on graph notation} The definition of a graph proposed by \cite{wolf2018mutex} makes a distinction between a set of positive edges $E^+$, associated with a set $W^+$ of positive scalar attributes representing merge affinities, and a set of negative edges $E^-$, associated with a set $W^-$ of positive attributes representing split tendencies.
@@
 \ref{eq:mappings} and solve the multicut problem on this graph.
-For our experiments, we use the approximate Kernighan-Lin solver \cite{keuper2015efficient,kernighan1970efficient} (MC).
+For our experiments, we use the approximate Kernighan-Lin solver \cite{keuper2015efficient,kernighan1970efficient} (WSDT+MC).
 In some cases, the long-range affinities predicted by the CNN can connect two superpixels that are not direct-neighbors.
-Thus, in these cases we introduce additional \emph{lifted} edges in the graph and an instance of the lifted multicut problem (LMC).
+Thus, in these cases we introduce additional \emph{lifted} edges in the graph and an instance of the lifted multicut problem (WSDT+LMC).
 This time, similarly to the methods mentioned in \cite{beier2016efficient}, we used a combination of approximate solvers consisting in GAEC and Kernighan-Lin.
-and      Other state-of-the-art multi-step-pipelines for neuron-segmentation first find 2D superpixels using WSDT and then apply a graph partitioning algorithm: in our comparison, we include one pipeline using agglomerative HC with average linkage (avgHC) and one using an approximation of the Lifted Multicut Problem (LMC) \cite{beier2016efficient}.
+%and      Other state-of-the-art multi-step-pipelines for neuron-segmentation first find 2D superpixels using WSDT and then apply a graph partitioning algorithm: in our comparison, we include one pipeline using hierarchical agglomerative clustering with average linkage (avgHC) and one using an approximation of the Lifted Multicut Problem (LMC) \cite{beier2016efficient}.
 
@@
 % In our experiments, edge weights are estimated \UPDATE{by using a CNN that predicts how likely two neighboring pixels are to be part of the same cluster}. 
+A crop of CREMI training data sample B was used.
+
 Fig.

### 2019-05-20 chapters/5_experiments_compare_rules.tex

@@
 We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available.
-The dataset comes from a serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth.
+The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth.
 The results submitted to the leaderboard are evaluated using the CREMI score\footnote{\url{https://cremi.org/leaderboard/}}, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}.

### 2019-05-20 chapters/1_intro.tex
Add Constantin comments

@@
 Thus, agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter free and efficient.
-Despite the fact that there exist a variety of these algorithms \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}, there has been no overarching studies comparing them and making it possible to choose the most appropriate algorithm for particular applications and assess their properties, e.g.
+Despite the fact that there exist a variety of these algorithms \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}, there have been no overarching studies comparing them and making it possible to choose the most appropriate algorithm for particular applications and assess their properties, e.g.
 robustness and efficiency.
@@
 In this paper, we propose a novel theoretical framework for generalizing over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering, which is a popular bottom-up approach defining an hierarchy of clusters on positive-weighted graphs \cite{lance1967general}.
-This framework defines an underlying basic algorithm and allows us to explore in a consistent way its combinations with different linkage criteria and \emph{cannot-link constraints}, i.e.
+This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}, i.e.
 mutual exclusion between clusters.

### 2019-05-20 chapters/5_experiments_noise.tex
Add Constantin comments

@@
 In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with Average linkage even achieved significantly superior scores compared to other methods based on WSDT superpixels.
-Our hypothesis to explain this superior performances it that, currently, there are not good ways of generating superpixels that can take the long-range predictions of the CNN into account.
-It is of course possible to make use of long-range predictions to compute the edge weights of the superpixel graph, but, in our experience, this process usually involves a lot of parameter tuning and trial and error.
+Thus, this method offers a simple and successful approach that grow the clusters starting directly from pixels and had the advantage of avoiding potential errors in the superpixel generation.
+In fact, generating for example good quality WSDT superpixels requires to tune several parameters.
+%Our hypothesis to explain this superior performances is that, currently, there are not good ways of generating superpixels that can take the long-range predictions of the CNN into account. 
+%It is of course possible to make use of long-range predictions to compute the edge weights of the superpixel graph, but, in our experience, this process usually involves a lot of parameter tuning and trial and error.
 In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets and present an extended version of Table \ref{tab:results_cremi_train} including all tested \algname{} algorithms.
+Fig. \ref{fig:cremi_comparison} highlights some failure cases of the different agglomerative algorithms included in our framework.
 
@@
 THRESH &-& 0.221  $\pm$ 0.067 \\ 
-DTWS + \algname{} & Average& \TODO{} \\
+% DTWS + \algname{} & Average& \TODO{} \\
 % DTWS  & -& 0.010 $\pm$ 0.003\\
@@
 PNI-UNet & 0.228 \\
-Our UNet + \algname{} Avg-Linkage & 0.244 \\
+Our UNet + \algname{} Avg-Linkage & 0.241 \\
 MALA-UNet + MC \cite{funke2018large} & 0.276 \\
@@
         \end{tabular}
-        \vspace*{2.3em}
-    \captionof{table}{Current leaderboard of the CREMI challenge \TODO{Update refs and check}}
+        \vspace*{1.5em}
+    \captionof{table}{Current leaderboard of the CREMI challenge}
     \label{tab:results_cremi_test}
@@
 
-\textbf{Noise experiments } Fig.
-\ref{fig:cremi_comparison} highlights some failure cases of the different agglomerative algorithms included in our framework.
-Additionally, we run a set of experiments where the CNN predictions are perturbed by noise, in order to highlight the properties of each \algname{} algorithm and perform an in-depth comparison that is as quantitative as possible.
+\textbf{Noise experiments }  Additionally, we run a set of experiments where the CNN predictions are perturbed by noise, in order to highlight the properties of each \algname{} algorithm and perform an in-depth comparison that is as quantitative as possible.
 Appendix \ref{sec:appendix_noise_gen} introduces the type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false boundary evidences.
@@
 \ref{fig:noise_plots} summarize our 12000 noise experiments: we focused on the best performing linkage criteria, i.e.
-\emph{Average}, \emph{Sum} and \emph{Abs Max}, and tested them with different values of noise, both with and without use of long-range connections in the grid-graph.
+\emph{Average}, \emph{Sum} and \emph{Abs Max}, and tested them with different values of noise.
+%, both with and without use of long-range connections in the grid-graph.
 % In Fig.

### 2019-05-20 chapters/1_intro.tex
Update figs; add extended CS results

@@
 % \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
-\includegraphics[width=\textwidth]{./figs/intro_image.pdf} % left bottom right top
-\caption{
- (\textbf{a}) Iterations of three different algorithms in the generalized framework on  toy graph examples with attractive (green) and repulsive (red) interactions.
-(\textbf{b}) Example of CREMI 2016 neuron-segmentation data \cite{cremiChallenge} overlaid with instance segmentation.
-(\textbf{c}) Agglomeration order, representing which pairs of neighboring pixels were merged first (white), later on (brown), or never (black).
- \TODO{re-arrange, show affinities and replace unsigned case with Abs Max}
+\includegraphics[width=0.9\textwidth]{./figs/intro_image_v2.pdf} % left bottom right top
+\caption{ \textbf{Left:} raw data from the CREMI 2016 neuron-segmentation challenge and short- / long-range predictions of a CNN.
+\textbf{Right:} Outputs of three different agglomerative algorithms included in the proposed generalized framework.
+The  agglomeration order in (a) shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black).
+When signed graphs are used, the final clustering / instance segmentation is shown in (b).
+We also illustrate some iterations of the algorithms on toy graph examples with attractive (green) and repulsive (red) interactions.
 %We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 

### 2019-05-20 chapters/2_rel_work.tex
Finish polishing intro, abstract, conclusions
Update figs; add extended CS results

@@
 \textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances.
+Recently, there has been a growing interest for such  methods that do not involve object detection, since, in certain types of data, object instances cannot be approximated by bounding boxes.
 For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
@@
 NP-hardness of the \emph{correlation clustering} problem was shown in \cite{bansal2004correlation}, while the connection with graph multicuts was made by \cite{demaine2006correlation}.
-Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
+Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2019mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
 % \TODO{Cannot-link constraints?}

### 2019-05-20 chapters/3_algorithm.tex
Update figs; add extended CS results

@@
 In computer vision applications, the nodes can represent either pixels, superpixels or voxels.
-We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{S\in\Pi} S $, $\,S \cap \tilde{S} = \emptyset$ for different clusters $S, \tilde{S}\in \Pi$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
+We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{S\in\Pi} S $, $\,S \cap S' = \emptyset$ for different clusters $S, S'\in \Pi$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
 We also denote as $S_u$ the cluster associated with node $u$.
@@
 In hierarchical agglomerative clustering, the interaction $\interact(S_u,S_v)$ between the two clusters is usually defined as a function $\interact{}:\Pi \times \Pi \rightarrow \mathbb{R}$, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S_u$ and $S_v$, i.e.
-$E_{uv}=(S_u \times S_v) \cap E$.
+$(S_u \times S_v) \cap E$.
 All the linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
@@
 % \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
-\includegraphics[width=\textwidth]{./figs/comparison.pdf} % left bottom right top
+\includegraphics[width=\textwidth]{./figs/comparison_new.pdf} % left bottom right top
 \caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data.
-Only the few \emph{wrongly} segmented regions are highlighted in colors.
+The main \emph{wrongly} segmented regions are highlighted in warm colors.
 Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.
@@
 Yellow arrows point out merge errors.
-Green arrows indicate challenging, but correctly segmented regions.
 The average linkage without cannot-link constraints achieved an almost error-free segmentation.
@@
 In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
- the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see left panel of Fig.
+ the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see \UPDATE{left panel} of Fig.
 \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} and Table \ref{tab:linkage-criteria}, unsigned graphs).

### 2019-05-20 chapters/5_experiments_noise.tex
Update figs; add extended CS results

@@
          % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
-         & \makecell[l]{\algname{}\\ Linkage} & \makecell{Arand-Score \\(higher is better)} \\ \midrule 
+         & \makecell[l]{\algname{}\\ Linkage} & \makecell{Rand-Score \\(higher is better)} \\ \midrule 
          % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
@@
         \end{tabular}
-    \captionof{table}{Arand-Scores achieved by different post-processing methods on CREMI challenge training predictions}
+    \captionof{table}{Rand-Scores achieved by different post-processing methods on CREMI challenge training predictions}
     \label{tab:results_cremi_train}
@@
         \end{tabular}
-        \vspace*{1.5em}
+        \vspace*{1.1em}
     \captionof{table}{Current leaderboard of the CREMI challenge}

### 2019-05-20 chapters/supplementary.tex
Update figs; add extended CS results

@@
 In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from the edge contraction are replaced by a single edge with updated interaction.
-\textbf{Right:} The table lists the update rules $f(\tilde{\cost}_1, \tilde{\cost}_2)$ associated to the linkage criteria of Table \ref{tab:linkage-criteria} and that are used to efficiently update the interactions between clusters.
-\TODO{Update notation figure}}
+\textbf{Right:} The table lists the update rules $f(\tilde{\cost}_1, \tilde{\cost}_2)$ associated to the linkage criteria of Table \ref{tab:linkage-criteria} and that are used to efficiently update the interactions between clusters.}
 \label{fig:edge_contraction_and_contr_graph}  
@@
 Moreover, in the next section, we present an efficient implementation of \algname{} with \emph{Absolute Maximum} linkage that has empirical $\mathcal{O}(N \log N)$ complexity.
-\TODO{Empirical complexity plot?}
+%\TODO{Empirical complexity plot?}
 
@@
 that these kinds of augmentations can help to alleviate issues caused by EM-imaging artifacts.
-We use L2 loss and Adam optimizer to train the network. \TODO{Field of view?}
+We use L2 loss and Adam optimizer to train the network. % \TODO{Field of view?}
 
@@
 With this approach, pixels are pre-clustered only when they are far away (in all directions) from all predicted boundaries.
- To make sure that in this preprocessing step different neurons are never merged together by mistake, we intersected these segments given by the conservative THRESH with the segments given by WSDT \TODO{show figure?}.
+ To make sure that in this preprocessing step different neurons are never merged together by mistake, we intersected these segments given by the conservative THRESH with the segments given by WSDT.
+%\TODO{show figure?}
  By using this method, we initialized \algname{} with a reduced graph that represents a true over-segmentation.
@@
 \begin{figure}[b]
+\end{figure}
+
+% \multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
+%  &Yes & 0.55  & {\color{Orange} 0.319 } & {\color{Orange} 0.527 } \\\midrule
+% % Abs. max. &- & 0.45  & {\color{Orange} 0.321 } & {\color{ForestGreen} 0.531 } \\\midrule
+% % \multirow{2}{*}{Mean} &No & 0.35  & {\color{ForestGreen} 0.343 } & {\color{ForestGreen} 0.552 } \\
+%  % &Yes & 0.25  & {\color{Orange} 0.339 } & {\color{ForestGreen} 0.548 } \\\midrule
+% \multirow{2}{*}{Max} &No & 0.85 & {\color{Red} 0.243 } & {\color{Red} 0.444 } \\
+%  &Yes & 0.50  & {\color{Orange} 0.325 } & {\color{ForestGreen} 0.530 } \\\midrule
+% \multirow{2}{*}{Min} &No & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\
+%  &Yes & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\\midrule
+% \cite{liu2018affinity} &-  & -  & {\color{ForestGreen} 0.341 } & {\color{ForestGreen} 0.547 } \\
+\begin{figure}[t]
 \centering
-        \includegraphics[width=0.45\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
-
+\begin{minipage}[T]{0.35\textwidth}
+    \centering
+    \footnotesize
+        \begin{tabular}{l|c|c}
+          \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
+          % Pipeline & method & \textsc{No} & \textsc{Yes} \\ 
+          Average & 34.3 & 0.35 \\
+          Average + CLC & 33.9 & 0.25\\
+          Max + CLC & 32.5 & 0.50 \\
+          Abs Max & 32.1 & 0.45\\
+          Sum + CLC & 31.9 & 0.55 \\
+          Sum & 31.3 & 0.55 \\
+          Max & 24.3 & 0.85 \\
+          Min & 0.00 & 0.50 \\
+          Min + CLC & 0.00 & 0.50 \\
+        \end{tabular}
+    \captionof{table}{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set.
+A bias value $\beta=0$ returns one single cluster.}
+    \label{tab:extended_results_cityscapes_val}
+\end{minipage}\hfill
+\begin{minipage}[T]{0.6\textwidth}
+\centering
+        \includegraphics[width=0.88\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
     \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise.
@@
 Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
-\TODO{Add raw-data (and GT)}
+\TODO{Overlay raw-data}
     %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
@@
     \label{fig:noisy_affs}
+\end{minipage}
 \end{figure}
@@
 Before to apply \algname{}, we performed a parameter-search for the bias $\beta$ defined in \ref{eq:mappings}.
-Table \ref{tab:results_cityscapes_val_expanded} lists the best-case performances for each of the methods with the chosen bias $\beta$: note that depending on the version of \algname{}, it was necessary to bias more or less the predicted edge weights.
-\TODO{Add extended table (explain what $\beta=0$ means)}
+Table \ref{tab:extended_results_cityscapes_val} lists the best-case performances for each of the methods with the chosen bias $\beta$: note that depending on the version of \algname{}, it was necessary to bias more or less the predicted edge weights.

### 2019-05-21 chapters/3_algorithm.tex
Update scores and add extended tables

@@
 \caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data.
-The main \emph{wrongly} segmented regions are highlighted in warm colors.
+The main \emph{wrongly} segmented regions are highlighted in different warm colors.
 Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.
@@
 Yellow arrows point out merge errors.
-The average linkage without cannot-link constraints achieved an almost error-free segmentation.
+The average linkage without cannot-link constraints returned the best segmentation.
 % Only the involved segments are colored.

### 2019-05-21 chapters/5_experiments_noise.tex
Update scores and add extended tables

@@
          % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
-         & \makecell[l]{\algname{}\\ Linkage} & \makecell{Rand-Score \\(higher is better)} \\ \midrule 
+         & \makecell[l]{\algname{}\\ Linkage} & \makecell{Cremi-Score \\(lower is better)} \\ \midrule 
          % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
-\textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
-Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
-DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
-DTWS + MC & -& 0.903 $\pm$ 0.017 \\
-% DTWS + avgHC &-& \\
-% DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
-% DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
-Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
-GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
-THRESH &-& 0.221  $\pm$ 0.067 \\ 
-% DTWS + \algname{} & Average& \TODO{} \\
-% DTWS  & -& 0.010 $\pm$ 0.003\\
+\textbf{\algname{}} & \textbf{Average}& \textbf{0.226}  \\
+Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.282 \\
+DTWS + MC & -& 0.310 \\
+DTWS + LMC & -& 0.317 \\
+Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.322 \\
+GAEC \cite{keuper2015efficient} & Sum & 0.334 \\
+THRESH &-& 1.521 \\ 
+% \textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
+% Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
+% DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
+% DTWS + MC & -& 0.903 $\pm$ 0.017 \\
+% % DTWS + avgHC &-& \\
+% % DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
+% % DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
+% Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
+% GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
+% THRESH &-& 0.221  $\pm$ 0.067 \\ 
+% % DTWS + \algname{} & Average& \TODO{} \\
+% % DTWS  & -& 0.010 $\pm$ 0.003\\
         \end{tabular}
-    \captionof{table}{Rand-Scores achieved by different post-processing methods on CREMI challenge training predictions}
+    \captionof{table}{Cremi-Scores achieved by different post-processing methods. Scores are averaged over the three CREMI training samples}
     \label{tab:results_cremi_train}
@@
         \begin{tabular}[t]{l|c}
-         & \makecell{CREMI Score \\(lower is better)}  \\ \midrule
+         & \makecell{Cremi-Score \\(lower is better)}  \\ \midrule
 Our UNet + DTWS + LMC &  \textbf{0.221}\\
@@
         \vspace*{1.1em}
-    \captionof{table}{Current leaderboard of the CREMI challenge}
+    \captionof{table}{Current leaderboard of the CREMI challenge with the Cremi-Scores averaged over the three test samples}
     \label{tab:results_cremi_test}
@@
 \textbf{Average and Abs Max linkage } Our findings confirm that \algname{} with \emph{Average} linkage criterion represents the most robust algorithm tested and the one that benefits the most from using the long-range CNN predictions.
-On the other hand, it is not a surprise that the \emph{Abs Max} statistic proposed by \cite{wolf2018mutex} is less robust to noise than the \emph{Average} linkage, but, as we show in the Appendix \TODO{Table \ref{tab:full_cremi_results}}, \emph{Abs Max} represents a valid and considerably faster option.
+On the other hand, it is not a surprise that the \emph{Abs Max} statistic proposed by \cite{wolf2018mutex} is less robust to noise than the \emph{Average} linkage, but, as we show in the Appendix Table \ref{tab:extended_results_cremi}, \emph{Abs Max} represents a valid and considerably faster option.
 Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights, then \algname{} with cannot-link constraints shows a clear tendency to over-cluster.

### 2019-05-21 chapters/supplementary.tex
Update scores and add extended tables

@@
 
-\paragraph{Extended results} \TODO{present extended table}
+\paragraph{Extended results} For all algorithms, the chosen value of bias parameter was $\beta = 0$. \TODO{Finish}
+
+\begin{table}[t]
+\centering
+    \footnotesize
+% \begin{minipage}[T]{0.85\textwidth}
+%     \centering
+        \begin{tabular}{l|c|c|c|c}
+          \algname{} linkage & \makecell{Cremi-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
+          % Pipeline & method & \textsc{No} & \textsc{Yes} \\ 
+Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 3.49 $\cdot$ 10$^4$ \\
+Sum + CLC & 0.282 & 0.906 & 0.358 & 4.64 $\cdot$ 10$^4$ \\
+Abs Max & 0.322 & 0.897 & 0.286 & 1.24 $\cdot$ 10$^4$ \\
+Max + CLC & 0.324 & 0.893 & 0.292 & 6.31 $\cdot$ 10$^4$ \\
+Sum & 0.334 & 0.872 & 0.461 & 4.74 $\cdot$ 10$^4$ \\
+Average + CLC & 0.563 & 0.772 & 0.259 & 2.95 $\cdot$ 10$^4$ \\
+Min & 2.522 & 0.030 & 0.197 & 2.97 $\cdot$ 10$^3$ \\
+Min + CLC & 2.522 & 0.030 & 0.197 & 4.77 $\cdot$ 10$^3$ \\
+Max & 2.626 & 0.028 & 7.069 & \textbf{6.04 $\cdot$ 10$^\mathbf{2}$} \\
+        \end{tabular}
+        \vspace*{1.1em}
+    \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set. CLC stands for cannot-link constraints}
+    \label{tab:extended_results_cremi}
+\end{table}
+% \hfill
+% \begin{minipage}[T]{0.6\textwidth}
+% \centering
+%         \includegraphics[width=0.88\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
+%     \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise.
+Blue pixels represent boundary evidence.
+Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
+\TODO{Overlay raw-data}
+%     %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
+%     %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
+%     }
+%     \label{fig:noisy_affs}
+% \end{minipage}
+% \end{figure}
 
@@
 details}
-
-\begin{figure}[b]
-\end{figure}
-
 % \multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
@@
 \centering
+\begin{minipage}[T]{0.6\textwidth}
+\centering
+        \includegraphics[width=0.88\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
+    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise.
+Blue pixels represent boundary evidence.
+Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
+\TODO{Overlay raw-data}
+    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
+    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
+    }
+    \label{fig:noisy_affs}
+\end{minipage}\hfill
 \begin{minipage}[T]{0.35\textwidth}
@@
     \captionof{table}{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set.
-A bias value $\beta=0$ returns one single cluster.}
+A bias value $\beta=0$ returns one single cluster.
+CLC stands for cannot-link constraints}
     \label{tab:extended_results_cityscapes_val}
-\end{minipage}\hfill
-\begin{minipage}[T]{0.6\textwidth}
-\centering
-        \includegraphics[width=0.88\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
-    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise.
-Blue pixels represent boundary evidence.
-Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
-\TODO{Overlay raw-data}
-    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
-    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
-    }
-    \label{fig:noisy_affs}
 \end{minipage}

### 2019-05-21 chapters/5_experiments_noise.tex
Polish details about noise experiments

@@
 In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with Average linkage even achieved significantly superior scores compared to other methods based on WSDT superpixels.
-Thus, this method offers a simple and successful approach that grow the clusters starting directly from pixels and had the advantage of avoiding potential errors in the superpixel generation.
+This shows that this method offers a simple and successful approach that grow the clusters starting directly from pixels and had the advantage of avoiding potential errors in the superpixel generation.
 In fact, generating for example good quality WSDT superpixels requires to tune several parameters.
@@
 %It is of course possible to make use of long-range predictions to compute the edge weights of the superpixel graph, but, in our experience, this process usually involves a lot of parameter tuning and trial and error.
+Moreover, superpixel generation does not usually make use of the long-range predictions of the CNN and, in our experiments, using them to compute the weights of the edges in the superpixel graph did not make a big difference.
 In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets and present an extended version of Table \ref{tab:results_cremi_train} including all tested \algname{} algorithms.

### 2019-05-21 chapters/supplementary.tex
Polish details about noise experiments

@@
 \subsection{Experiments on neuron segmentation adding noise to CNN predictions} \label{sec:appendix_noise_gen}
-
-\TODO{Also mention details about plots (fix some long-range edges, fix noise seed and vary K)}
-
- % In this section we evaluate the robustness of \algname{} with different linkage criteria by adding noise to the edge weights.
-  %Before to present the results shown in Fig. \ref{fig:noise_plots}, we will first introduce the type of noise that was added to the edge weights.
-% In our experiments, edge weights are estimated \UPDATE{by using a CNN that predicts how likely two neighboring pixels are to be part of the same cluster}. 
-A crop of CREMI training data sample B was used.
-
-Fig.
+Additionally to the comparison on the full training dataset, we performed additional experiments on a crop of the dataset\footnote{We chose a challenging part of CREMI training sample B}, where we perturbed the predictions of the CNN with noise and we introduced additional artifacts like missing or fictitious boundary evidences.
+% Fig.
 \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}a} shows an example of uncertain CNN predictions on a part of the neuron segmentation CREMI dataset.
@@
 In these cases, the noise of one pixel does not correlate with its neighboring noise values. On the other hand, predictions of a CNN are known to be spatially correlated. 
-Thus, we used Perlin noise\footnote{In our experiments, we used an open-source version of simplex noise \cite{perlin2001noise}, which is an improved open-source version of Perlin noise \cite{perlin1985image}}, one of the most common gradient noises used in procedural pattern generation.
+Thus, we used Perlin noise\footnote{In our experiments, we used an open-source implementation of simplex noise \cite{perlin2001noise}, which is an improved version of Perlin noise \cite{perlin1985image}}, one of the most common gradient noises used in procedural pattern generation.
 This type of noise $n(x)\in[0,1]$ generates spatial random patterns that are locally smooth but have large and diverse variations on bigger scales.
@@
 where  $N(x)=\mathrm{Logit}[n(x)]$; $F(x)=\mathrm{Logit}[p(x)]$ and $\mathcal{K}\in \mathbb{R}^+$ is a positive factor representing the amount of added noise.
-$\tilde{F}_{+}(x;\mathcal{K})$ represents then a merge-biased prediction, such that the probability for two pixels to be in the same cluster is increased only if $N(x)>0$ (see Fig.
-\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b}), whereas $\tilde{F}_{-}(x;\mathcal{K})$ is a split-biased prediction with decreased probabilities when $N(x)<0$ (Fig.
+$\tilde{F}_{+}(x;\mathcal{K})$ represents then a under-clustering biased prediction, such that the probability for two pixels to be in the same cluster is increased only if $N(x)>0$ (see Fig.
+\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b}), whereas $\tilde{F}_{-}(x;\mathcal{K})$ is a over-clustering biased prediction with decreased probabilities when $N(x)<0$ (Fig.
 \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}).
-\TODO{Add impl.
-details}
+In the implementation we used, the noise can be generated in an arbitrary number of dimensions and a smoothing factor can be specified for each direction independently.
+In our experiments, each pixel is represented by a node in the grid-graph and it is linked to $K$ other nodes by short- and long-range edges.
+Thus, the output of our CNN model has $K$ channels: for each pixel / voxel, it outputs $K$ values representing the weights of different edge connections.
+We then generated a 4-dimensional noise that matches the dimension of the CNN output.
+The data is highly anisotropic, i.e.
+it has a lower resolution in one of the dimensions.
+Due to this fact, we chose different smoothing parameters to generate the noise in different directions.
+% one of the dimensions has a lower resolution,   such that three dimensions represent the spatial ones a
 % \multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
@@
 Blue pixels represent boundary evidence.
-Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
+Image a) shows the original CNN predictions, b) the under-clustering biased version $\tilde{F}_{+}$ and c) the over-clustering biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
 \TODO{Overlay raw-data}

### 2019-05-21 chapters/3_algorithm.tex
Update figs and minor changes

@@
 
-In Algorithm \ref{main_alg}, we provide a simplified pseudo-code for the proposed \algname{} algorithm that is based on a bottom-up approach starting with each node assigned to its own cluster and iteratively merges pairs of adjacent clusters.
-It starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
+In Algorithm \ref{main_alg}, we provide a simplified pseudo-code for the proposed \algname{} algorithm that is based on a bottom-up approach starting with each node assigned to its own cluster and iteratively merging pairs of adjacent clusters.
+The algorithm has two variants, depending on the boolean value of the input option \texttt{addCannotLinkConstraints}.
+The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
 \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}).
@@
 
-A second variant of Algorithm \ref{main_alg}, with option \texttt{addCannotLinkConstraints=True}, introduces \emph{cannot-link constraints}, which represent mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering.
+In the second variant, when \texttt{addCannotLinkConstraints=True}, Algorithm \ref{main_alg} also introduces \emph{cannot-link constraints}, which represent mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering.
 This variant
@@
 In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
- the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see \UPDATE{left panel} of Fig.
+ the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see bottom panel of Fig.
 \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} and Table \ref{tab:linkage-criteria}, unsigned graphs).

### 2019-05-21 chapters/5_experiments_cityscapes.tex
Update figs; add extended CS results
Update figs and minor changes

@@
 Max.}, or false region-merge, like \emph{Sum}.
-In Appendix, \TODO{Table \ref{tab:extended_results_cityscapes}} includes all other tested linkage.
+In Appendix, Table \ref{tab:extended_results_cityscapes_val} includes all other tested linkage.
 MultiStepHAC requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.
@@
  & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
-\multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & \UPDATE{33.0} & -  \\
+\multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 & -  \\
  % & \algname{} Max &   24.3  &   32.5  \\

### 2019-05-21 chapters/5_experiments_compare_rules.tex
Update figs and minor changes

@@
 Superpixels are usually computed with a watershed algorithm seeded at the maxima of a boundary distance transform (WSDT).
-The algorithms employed in our comparison to partition the superpixel graph were given by \algname{} (WSDT+\algname{}) or approximations of the multicut (WSDT+MC) and lifted multicut (WSDT+LMC) problems.
+The algorithms employed in our comparison to partition the superpixel graph were given by approximations of the multicut (WSDT+MC) and lifted multicut (WSDT+LMC) problems.

### 2019-05-21 chapters/5_experiments_noise.tex
Update figs and minor changes

--- 2019-05-21 chapters/5_experiments_noise.tex
@@
 The remarkably competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem.
-In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with Average linkage even achieved significantly superior scores compared to other methods based on WSDT superpixels.
-Thus, this method offers a simple and successful approach that grow the clusters starting directly from pixels and had the advantage of avoiding potential errors in the superpixel generation.
+In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with \emph{Average} linkage even achieved significantly superior scores compared to other methods based on WSDT superpixels.
+This shows that this method offers a simple and successful approach growing clusters starting directly from pixels and had the advantage of avoiding potential errors in the superpixel generation.
 In fact, generating for example good quality WSDT superpixels requires to tune several parameters.
@@
 %It is of course possible to make use of long-range predictions to compute the edge weights of the superpixel graph, but, in our experience, this process usually involves a lot of parameter tuning and trial and error.
-In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets and present an extended version of Table \ref{tab:results_cremi_train} including all tested \algname{} algorithms.
+Moreover, superpixel generation does not usually make use of the long-range predictions of the CNN and, in our experiments, using them to compute the weights of the edges in the superpixel graph did not change the final scores.
+In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets and present an extended version of Table \ref{tab:results_cremi_train} including all tested \algname{} linkage.
 Fig. \ref{fig:cremi_comparison} highlights some failure cases of the different agglomerative algorithms included in our framework.
@@
          & \makecell{Cremi-Score \\(lower is better)}  \\ \midrule
-Our UNet + DTWS + LMC &  \textbf{0.221}\\
-PNI-UNet & 0.228 \\
+\textbf{Our UNet + DTWS + LMC} &  \textbf{0.221}\\
+PNI-UNet \UPDATE{[REF?]} & 0.228 \\
 Our UNet + \algname{} Avg-Linkage & 0.241 \\
@@
         \centering
-        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.2in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
-        \caption{Without long-range edges} \label{fig:merge_noise_only_direct}
+        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.2in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
+        \caption{No long-range predictions: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
     \end{subfigure} \hfill
@@
         \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.20in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
-        \caption{With 10\% long-range edges} \label{fig:merge_noise_with_long_range}
+        \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
     \end{subfigure}
-\caption{\algname{} sensitivity to noise: performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions.
-In all experiments the average linkage proved to be the most robust.
+\caption{\algname{} sensitivity to noise:  average linkage proved to be the most robust.
+Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions.
 Solid lines represent median values over 30 experiments.
@@
 The two set of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details).
-On the right, 10\% of the long-range CNN predictions were randomly added to the grid-graph.
+For each experiment, some of the long-range CNN predictions were randomly selected and added them to pixel grid-graph with probability $p_{\mathrm{long}}$.
 %\textbf{Bottom}: Multicut objective (Eq.
@@
 \ref{fig:intro_figure} by the quite unique agglomeration order of the \emph{Sum} statistic.
-An intuitive explanation of this fact is the following: initially, most of the infra-cluster nodes present similar attractive interactions between each others; when the two nodes sharing the most attractive interaction are merged, there is a high chance that they both share an attractive interaction with a common neighboring node, so the new interaction with this common neighbor will be immediately assigned to a high priority in the agglomeration, given by the sum of two high weights; this usually starts a ``chain reaction'', where only a single cluster is agglomerated at the beginning.
+An intuitive explanation of this fact is the following: initially, most of the intra-cluster nodes present similar attractive interactions between each others; when the two nodes sharing the most attractive interaction are merged, there is a high chance that they both share an attractive interaction with a common neighboring node, so the new interaction with this common neighbor will be immediately assigned to a high priority in the agglomeration, given by the sum of two high weights; this usually starts a ``chain reaction'', where only a single cluster is agglomerated at the beginning.
 On the other hand, as we also see in Fig.

### 2019-05-21 chapters/6_conclusions.tex
Update figs and minor changes

@@
 \section{Conclusion}
-We have presented a novel theoretical framework for agglomerative clustering of graphs with both positive and negative weights and we have shown that several existing clustering algorithms, like the Mutex Watershed, can be reformulated as special cases of one underlying agglomerative algorithm.
-This framework also allowed us to introduce new algorithms, one of which (based on an average linkage) outperformed all the others and proved to be a simple and remarkably robust approach to process short- and long-range predictions of a CNN applied to an instance segmentation task.
-On biological images, this simple average agglomeration algorithm can represent a valuable choice for an user that is not willing to spend a lot of time tuning complex task-dependent pipelines.
+We have presented a novel theoretical framework for agglomerative clustering of graphs with both positive and negative weights and we have shown that several existing clustering algorithms, e.g.
+the Mutex Watershed \cite{wolf2018mutex}, can be reformulated as special cases of one underlying agglomerative algorithm.
+This framework also allowed us to introduce new algorithms, one of which, based on an average linkage, outperformed all the others and proved to be a simple and remarkably robust approach to process short- and long-range predictions of a CNN applied to an instance segmentation task.
+On biological images, this simple average agglomeration algorithm can represent a valuable choice for an user that is not willing to spend much time tuning complex task-dependent pipelines based on superpixels.
 % or test several dataset-dependent

### 2019-05-21 chapters/supplementary.tex
Update figs and minor changes

@@
 In the implementation we used, the noise can be generated in an arbitrary number of dimensions and a smoothing factor can be specified for each direction independently.
-In our experiments, each pixel is represented by a node in the grid-graph and it is linked to $K$ other nodes by short- and long-range edges.
-Thus, the output of our CNN model has $K$ channels: for each pixel / voxel, it outputs $K$ values representing the weights of different edge connections.
+In our experiments, each pixel is represented by a node in the grid-graph and it is linked to $n_{\mathrm{nb}}$ other nodes by short- and long-range edges.
+Thus, the output of our CNN model has $n_{\mathrm{nb}}$ channels: for each pixel / voxel, it outputs $n_{\mathrm{nb}}$ values representing the weights of different edge connections.
 We then generated a 4-dimensional noise that matches the dimension of the CNN output.
@@
 Due to this fact, we chose different smoothing parameters to generate the noise in different directions.
+
+The experiments summarized in Fig.
+\ref{fig:noise_plots} were performed in the following way: for each value $\mathcal{K}$, 30 random noise samples were drawn, from which median and percentiles statistics were computed for each different linkage criteria.
+For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
 % one of the dimensions has a lower resolution,   such that three dimensions represent the spatial ones a

### 2019-05-21 chapters/1_intro.tex
Update figs; squeeze text

@@
 \section{Introduction}
-\UPDATE{\today,\currenttime} -  In computer vision, the clustering of weighted graphs has been successfully applied to such tasks as image segmentation, object tracking and pose estimation.
+In computer vision, the clustering of weighted graphs has been successfully applied to such tasks as image segmentation, object tracking and pose estimation.
 %image segmentation, object tracking, stereo matching, etc.), to high-level tasks (e.g.
@@
 In this paper, we propose a novel theoretical framework for generalizing over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering, which is a popular bottom-up approach defining an hierarchy of clusters on positive-weighted graphs \cite{lance1967general}.
-This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}, i.e.
+This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}.
+%, i.e.
 mutual exclusion between clusters.
@@
 % \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
-\includegraphics[width=0.9\textwidth]{./figs/intro_image_v2.pdf} % left bottom right top
-\caption{ \textbf{Left:} raw data from the CREMI 2016 neuron-segmentation challenge and short- / long-range predictions of a CNN.
+\includegraphics[width=\textwidth]{./figs/intro_image_v2.pdf} % left bottom right top
+\caption{ \textbf{Left:} Raw data from the CREMI 2016 neuron-segmentation challenge.
+\textbf{Middle:} Short- and long-range predictions of our UNet model.
 \textbf{Right:} Outputs of three different agglomerative algorithms included in the proposed generalized framework.
 The  agglomeration order in (a) shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black).
-When signed graphs are used, the final clustering / instance segmentation is shown in (b).
+The final clustering / instance segmentation is shown in (b).
 We also illustrate some iterations of the algorithms on toy graph examples with attractive (green) and repulsive (red) interactions.

### 2019-05-21 chapters/2_rel_work.tex
Update figs; squeeze text

@@
 
-\textbf{Edge detection} also experienced recent progress thanks to deep learning, both on natural images \cite{xie2015holistically,kokkinos2015pushing} and \UPDATE{biological data \cite{lee2017superhuman,schmidt2018cell,meirovitch2016multi,ciresan2012deep}}.
+\textbf{Edge detection} also experienced recent progress thanks to deep learning, both on natural images \cite{xie2015holistically,kokkinos2015pushing} and biological data \cite{lee2017superhuman,schmidt2018cell,meirovitch2016multi,ciresan2012deep}.
 In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:

### 2019-05-21 chapters/5_experiments_cityscapes.tex
Update figs; squeeze text

@@
 Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle.
-For our experiments, we used the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
-Their trained model was made publicly available, so we simply replaced their final graph-merging algorithm (MultiStepHAC) with \algname{}.
-See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
-
+See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.
+%that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
+% Their trained model was made publicly available, so we simply replaced their final graph-merging algorithm (MultiStepHAC) with \algname{}.
+their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
 Results are summarized in Table \ref{tab:results_cityscapes_val} and confirm our findings on neuron-segmentation: \algname{} with average linkage achieves the best scores, whereas other linkage tend to introduce more false region-splits, like \emph{Abs.
@@
 In Appendix, Table \ref{tab:extended_results_cityscapes_val} includes all other tested linkage.
-MultiStepHAC requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.
-
+The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.
 \begin{figure}[t]
 \centering
-\begin{minipage}[T]{0.59\textwidth}
+\begin{minipage}[T]{0.6\textwidth}
     \centering
-    \footnotesize
+    \scriptsize
         \begin{tabular}{l|l|cc}
@@
         \end{tabular}
-    \captionof{table}{Average Precision (AP) scores on the cityscapes validation set achieved by the tested pipelines}
+    \captionof{table}{Average Precision (AP) scores (higher is better) on the cityscapes validation set achieved by the tested pipelines.}
     \label{tab:results_cityscapes_val}
@@
     \centering
-\includegraphics[width=\textwidth]{./figs/cityscapes_compare_2.pdf} % left bottom right top
+\includegraphics[width=0.95\textwidth]{./figs/cityscapes_compare_2.pdf} % left bottom right top
 \end{minipage}

### 2019-05-21 chapters/5_experiments_intro.tex
Update figs; squeeze text

@@
 Currently, only proof-reading or manual tracing yields sufficient accuracy for correct circuit reconstruction \cite{schlegel2017learning}, thus further progress is required in automated reconstruction methods.
-First, we present how we predicted signed edge weights with a CNN.
+%First, we present how we predicted signed edge weights with a CNN.
 Then we introduce the CREMI challenge and our tested methods in Sec.
@@
 boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment.
-The affinities do not have to be limited to direct neighboring pixels, in fact, \cite{lee2017superhuman} have shown that using long-range affinities is beneficial for the training of the CNN. 
-Thus, we train a CNN to predict both short- and long-range affinities
+The affinities do not have to be limited to direct neighboring pixels
+Thus, similarly to \cite{lee2017superhuman}, we train a CNN to predict both short- and long-range affinities
 and use them as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image. 

### 2019-05-21 chapters/5_experiments_noise.tex
Update figs; squeeze text

@@
 \algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage).
-The remarkably competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem.
-In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with \emph{Average} linkage even achieved significantly superior scores compared to other methods based on WSDT superpixels.
+The competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem.
+In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with \emph{Average} linkage even achieved superior scores compared to other methods based on WSDT superpixels.
 This shows that this method offers a simple and successful approach growing clusters starting directly from pixels and had the advantage of avoiding potential errors in the superpixel generation.
@@
 Moreover, superpixel generation does not usually make use of the long-range predictions of the CNN and, in our experiments, using them to compute the weights of the edges in the superpixel graph did not change the final scores.
-In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets and present an extended version of Table \ref{tab:results_cremi_train} including all tested \algname{} linkage.
 Fig. \ref{fig:cremi_comparison} highlights some failure cases of the different agglomerative algorithms included in our framework.
+In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets.
+Appendix Table \ref{tab:extended_results_cremi} lists the performances and the run-times for all tested \algname{} linkage.
 
@@
         \centering
-\begin{minipage}[t]{0.48\textwidth}
+\begin{minipage}[t]{0.56\textwidth}
 % \begin{table}
@@
          % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
-\textbf{\algname{}} & \textbf{Average}& \textbf{0.226}  \\
-Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.282 \\
-DTWS + MC & -& 0.310 \\
-DTWS + LMC & -& 0.317 \\
-Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.322 \\
-GAEC \cite{keuper2015efficient} & Sum & 0.334 \\
-THRESH &-& 1.521 \\ 
+\textbf{Our UNet + \algname{} Avg-Link} & \textbf{Average}& \textbf{0.226}  \\
+Our UNet + Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.282 \\
+Our UNet + DTWS + MC & -& 0.310 \\
+Our UNet + DTWS + LMC & -& 0.317 \\
+Our UNet + Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.322 \\
+Our UNet + GAEC \cite{keuper2015efficient} & Sum & 0.334 \\
+Our UNet + THRESH &-& 1.521 \\ 
 % \textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
@@
         \end{tabular}
-    \captionof{table}{Cremi-Scores achieved by different post-processing methods. Scores are averaged over the three CREMI training samples}
+    \captionof{table}{Cremi-Scores achieved by different post-processing methods. Scores are averaged over the three CREMI training datasets}
     \label{tab:results_cremi_train}
 \end{minipage}\hfill
-\begin{minipage}[t]{0.48\textwidth}
+\begin{minipage}[t]{0.4\textwidth}
     \centering
@@
          & \makecell{Cremi-Score \\(lower is better)}  \\ \midrule
-\textbf{Our UNet + DTWS + LMC} &  \textbf{0.221}\\
-PNI-UNet \UPDATE{[REF?]} & 0.228 \\
-Our UNet + \algname{} Avg-Linkage & 0.241 \\
+Our UNet + DTWS + LMC &  0.221\\
+PNI-UNet \cite{lee2017superhuman} & 0.228 \\
+\textbf{Our UNet + \algname{} Avg-Link} & \textbf{0.241} \\
 MALA-UNet + MC \cite{funke2018large} & 0.276 \\
@@
         \vspace*{1.1em}
-    \captionof{table}{Current leaderboard of the CREMI challenge with the Cremi-Scores averaged over the three test samples}
+    \captionof{table}{Current published entries of the CREMI challenge \cite{cremiChallenge} leaderboard on the three test datasets}
     \label{tab:results_cremi_test}
@@
 \emph{Average}, \emph{Sum} and \emph{Abs Max}, and tested them with different values of noise.
+In these experiments, we also want to test how beneficial it is to use long-range CNN predictions in the agglomeration.
+Thus, we perform a set of simulations without adding long-range connections to the grid-graph and another set where we introduce them with a 10\% probability\footnote{We also performed simulations adding all the long-range predictions given by CNN, but we did not note major differences with the case with only 10\% of them.
+Adding this small portion is usually sufficient to improve the scores.}.
 %, both with and without use of long-range connections in the grid-graph.

### 2019-05-21 chapters/supplementary.tex
Update figs; squeeze text

@@
 
-\subsection{Multicut and correlation clustering } 
-\TODO{Omit completely?} For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^{\mathrm{internal}}_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^{\mathrm{external}}$ the complementary set of edges whose incident nodes belong to distinct clusters:
-\begin{equation}
-E_\Pi^{\mathrm{internal}} \equiv \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \qquad E^{\mathrm{external}}_\Pi \equiv E \setminus E^{\mathrm{internal}}_\Pi.
-\end{equation}
-% \begin{align}
-% E_\Pi^0 &= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \\
-% E^1_\Pi &= E \setminus E^0_\Pi.
-% \end{align}
-The set of edges $E_\Pi^{\mathrm{external}}$ is known as the \emph{multicut} of $\mathcal{G}$ w.r.t.
+% \subsection{Multicut and correlation clustering } 
+% \TODO{Omit completely?} For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^{\mathrm{internal}}_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^{\mathrm{external}}$ the complementary set of edges whose incident nodes belong to distinct clusters:
+% \begin{equation}
+% E_\Pi^{\mathrm{internal}} \equiv \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \qquad E^{\mathrm{external}}_\Pi \equiv E \setminus E^{\mathrm{internal}}_\Pi.
+% \end{equation}
+% % \begin{align}
+% % E_\Pi^0 &= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \\
+% % E^1_\Pi &= E \setminus E^0_\Pi.
+% % \end{align}
+% The set of edges $E_\Pi^{\mathrm{external}}$ is known as the \emph{multicut} of $\mathcal{G}$ w.r.t.
 clustering $\Pi$.
 The instance of the NP-hard \emph{weighted correlation clustering/multicut problem}
-% w.r.t. $\mathcal{G}(V,E,\cost)$ 
-corresponds to finding the partitioning that optimally balance attraction and repulsion in the graph and is given by the following binary integer program \cite{kappes2011globally,chopra1991multiway,andres2015lifting}:
-\begin{equation}\label{eq:multicut_obj}
-% \min_\Pi \texttt{MC}(\Pi) \equiv
- \min_\Pi \sum_{e\in E} \cost_e x_e^\Pi,  \qquad \text{where} \quad x^\Pi_e = 
- \begin{cases} 
- 1 & \text{if } e\in E^{\mathrm{external}}_\Pi \\
- 0 & \text{otherwise}.
- \end{cases}
-\end{equation}
-In the next chapters we will use this objective as measure of how balanced a clustering is.
+% % w.r.t. $\mathcal{G}(V,E,\cost)$ 
+% corresponds to finding the partitioning that optimally balance attraction and repulsion in the graph and is given by the following binary integer program \cite{kappes2011globally,chopra1991multiway,andres2015lifting}:
+% \begin{equation}\label{eq:multicut_obj}
+% % \min_\Pi \texttt{MC}(\Pi) \equiv
+%  \min_\Pi \sum_{e\in E} \cost_e x_e^\Pi,  \qquad \text{where} \quad x^\Pi_e = 
+%  \begin{cases} 
+%  1 & \text{if } e\in E^{\mathrm{external}}_\Pi \\
+%  0 & \text{otherwise}.
+%  \end{cases}
+% \end{equation}
+% In the next chapters we will use this objective as measure of how balanced a clustering is.
 
@@
 
-\paragraph{Extended results} For all algorithms, the chosen value of bias parameter was $\beta = 0$. \TODO{Finish}
-
 \begin{table}[t]
@@
 %     \centering
-        \begin{tabular}{l|c|c|c|c}
-          \algname{} linkage & \makecell{Cremi-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
+        \begin{tabular}{l|c|c|c|c|c}
+          \algname{} linkage & \makecell{Cremi-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
           % Pipeline & method & \textsc{No} & \textsc{Yes} \\
-Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 3.49 $\cdot$ 10$^4$ \\
-Sum + CLC & 0.282 & 0.906 & 0.358 & 4.64 $\cdot$ 10$^4$ \\
-Abs Max & 0.322 & 0.897 & 0.286 & 1.24 $\cdot$ 10$^4$ \\
-Max + CLC & 0.324 & 0.893 & 0.292 & 6.31 $\cdot$ 10$^4$ \\
-Sum & 0.334 & 0.872 & 0.461 & 4.74 $\cdot$ 10$^4$ \\
-Average + CLC & 0.563 & 0.772 & 0.259 & 2.95 $\cdot$ 10$^4$ \\
-Min & 2.522 & 0.030 & 0.197 & 2.97 $\cdot$ 10$^3$ \\
-Min + CLC & 2.522 & 0.030 & 0.197 & 4.77 $\cdot$ 10$^3$ \\
-Max & 2.626 & 0.028 & 7.069 & \textbf{6.04 $\cdot$ 10$^\mathbf{2}$} \\
+
+% Average & 0.226 & 0.936 & 0.315 & 0.494 & 
+% Sum + CLC & 0.282 & 0.906 & 0.358 & 0.510 & 
+% Abs Max & 0.322 & 0.897 & 0.286 & 0.735 & 
+% Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 
+% Sum & 0.334 & 0.872 & 0.461 & 0.444 & 
+% Average + CLC & 0.563 & 0.772 & 0.259 & 1.142 & 
+% Min & 2.522 & 0.030 & 0.197 & 6.365 & 
+% Min + CLC & 2.522 & 0.030 & 0.197 & 6.365 & 
+% Max & 2.626 & 0.028 & 7.069 & 0.026 & 
+Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 0.494 & 3.49 $\cdot$ 10$^4$ \\
+Sum + CLC \cite{levinkov2017comparative} & 0.282 & 0.906 & 0.358 & 0.510 & 4.64 $\cdot$ 10$^4$ \\
+Abs Max \cite{wolf2018mutex} & 0.322 & 0.897 & 0.286 & 0.735 & 1.24 $\cdot$ 10$^4$ \\
+Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 6.31 $\cdot$ 10$^4$ \\
+Sum \cite{keuper2015efficient} & 0.334 & 0.872 & 0.461 & 0.444 & 4.74 $\cdot$ 10$^4$ \\
+Average + CLC & 0.563 & 0.772 & 0.259  & 1.142 & 2.95 $\cdot$ 10$^4$ \\
+Min & 2.522 & 0.030 & \textbf{0.197} & 6.365 & 2.97 $\cdot$ 10$^3$ \\
+Min + CLC & 2.522 & 0.030 & \textbf{0.197}  & 6.365 & 4.77 $\cdot$ 10$^3$ \\
+Max & 2.626 & 0.028 & 7.069 & \textbf{0.026} & \textbf{6.04 $\cdot$ 10$^\mathbf{2}$} \\
         \end{tabular}
         \vspace*{1.1em}
-    \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set. CLC stands for cannot-link constraints}
+    \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set.
+CLC stands for cannot-link constraints.
+For all algorithms, the chosen value of bias parameter was $\beta = 0$.}
     \label{tab:extended_results_cremi}
@@
 Image a) shows the original CNN predictions, b) the under-clustering biased version $\tilde{F}_{+}$ and c) the over-clustering biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
-\TODO{Overlay raw-data}
     %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 

### 2019-05-21 chapters/5_experiments_noise.tex
Updates from Overleaf

--- 2019-05-21 chapters/5_experiments_noise.tex
@@
 \textbf{Our UNet + DTWS + LMC} &  \textbf{0.221}\\
-PNI-UNet \UPDATE{[REF?]} & 0.228 \\
+PNI-UNet \cite{lee2017superhuman} & 0.228 \\
 Our UNet + \algname{} Avg-Linkage & 0.241 \\

### 2019-05-22 chapters/1_intro.tex
Update final details

@@
 % \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
-\includegraphics[width=\textwidth]{./figs/intro_image_v2.pdf} % left bottom right top
-\caption{ \textbf{Left:} Raw data from the CREMI 2016 neuron-segmentation challenge.
-\textbf{Middle:} Short- and long-range predictions of our UNet model.
-\textbf{Right:} Outputs of three different agglomerative algorithms included in the proposed generalized framework.
+\includegraphics[width=0.95\textwidth]{./figs/intro_image_v2.pdf} % left bottom right top
+\caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge.
+\textbf{(2)} Some short- and long-range predictions of our UNet model.
+\textbf{(3)} Outputs of three different agglomerative algorithms included in the proposed generalized framework.
 The  agglomeration order in (a) shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black).

### 2019-05-22 chapters/2_rel_work.tex
Update final details

@@
 % \TODO{Roman, Cocoons, Benjamin?}
-The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical HC linkage criteria, e.g.
+The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical HAC linkage criteria, e.g.
 average linkage \cite{liu2018affinity,lee2017superhuman}, median \cite{funke2018large} or a linkage learned by a random forest classifier \cite{nunez2013machine,knowles2016rhoananet}.

### 2019-05-22 chapters/5_experiments_cityscapes.tex
Update final details

@@
 their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
-Results are summarized in Table \ref{tab:results_cityscapes_val} and confirm our findings on neuron-segmentation: \algname{} with average linkage achieves the best scores, whereas other linkage tend to introduce more false region-splits, like \emph{Abs.
-Max.}, or false region-merge, like \emph{Sum}.
-In Appendix, Table \ref{tab:extended_results_cityscapes_val} includes all other tested linkage.
-The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.
+Results are summarized in Table \ref{tab:results_cityscapes_val} and confirm our findings on neuron-segmentation: \algname{} with average linkage achieves the best scores, whereas other linkage tend to over-cluster, like \emph{Abs.
+Max.}, or under-cluster and merge instances, like \emph{Sum}.
+In Appendix, Table \ref{tab:extended_results_cityscapes_val} includes the scores of all other tested \algname{} algorithms.
+The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by them, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.
 \begin{figure}[t]

### 2019-05-22 chapters/5_experiments_noise.tex
Update final details

--- 2019-05-21 chapters/5_experiments_noise.tex
@@
         \vspace*{1.1em}
-    \captionof{table}{Current published entries of the CREMI challenge \cite{cremiChallenge} leaderboard on the three test datasets}
+    \captionof{table}{Current published entries of the CREMI challenge leaderboard \cite{cremiChallenge} on the three test datasets}
     \label{tab:results_cremi_test}
@@
 The two set of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details).
-For each experiment, some of the long-range CNN predictions were randomly selected and added them to pixel grid-graph with probability $p_{\mathrm{long}}$.
+For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges in the pixel grid-graph.
 %\textbf{Bottom}: Multicut objective (Eq.
@@
 Fig.
-\ref{fig:noise_plots} summarize our 12000 noise experiments: we focused on the best performing linkage criteria, i.e.
-\emph{Average}, \emph{Sum} and \emph{Abs Max}, and tested them with different values of noise.
-In these experiments, we also want to test how beneficial it is to use long-range CNN predictions in the agglomeration.
-Thus, we perform a set of simulations without adding long-range connections to the grid-graph and another set where we introduce them with a 10\% probability\footnote{We also performed simulations adding all the long-range predictions given by CNN, but we did not note major differences with the case with only 10\% of them.
+\ref{fig:noise_plots} summarize our 12000 noise experiments: we focus on the best performing linkage criteria, i.e.
+\emph{Average}, \emph{Sum} and \emph{Abs Max}, and test them with different values of noise.
+In these experiments, we also want to assess how beneficial it is to use long-range CNN predictions in the agglomeration.
+Thus, we perform a set of simulations without adding long-range connections to the grid-graph and another set where we introduce them with a 10\% probability\footnote{We also performed simulations adding all the long-range predictions given by the CNN model, but we did not note major differences with the case using only 10\% of them.
 Adding this small portion is usually sufficient to improve the scores.}.

### 2019-05-22 chapters/supplementary.tex
Update final details

@@
 Let us now contradict the initial hypothesis and assume by absurd that the constrained version of \algname{} introduces a cannot-link constraints between two clusters sharing a positive interaction $\tilde{w}>0$ and outputs a different clustering as compared to the unconstrained version.
-This can happen only in the situation \TODO{shown in Fig.
-\ref{fig:contradiction_case}}, when two clusters $u$ and $v$ are merged together and share a common neighboring node $t$ having the following two properties: a) $u$ and $t$ are already constrained and share a repulsive interaction $w_{ut}\leq0$, b) $v$ and $t$ share an attractive interaction $w_{vt}>0$ that is higher in absolute value $|w_{vt}|>|w_{ut}|$.
+This can happen only in the situation shown in Fig.
+\ref{fig:abs_max_proof_example}, when two clusters $u$ and $v$ are merged together and share a common neighboring node $t$ having the following two properties: a) $u$ and $t$ are already constrained and share a repulsive interaction $w_{ut}\leq0$, b) $v$ and $t$ share an attractive interaction $w_{vt}>0$ that is higher in absolute value $|w_{vt}|>|w_{ut}|$.
 Then, according to Eq. \ref{eq:def_abs_max}, the new merged cluster $uv$ and $t$ are constrained and share a positive interaction. 
@@
 \end{proof}
+
+\begin{figure}
+        \centering
+
+        \includegraphics[width=0.7\textwidth]{./figs/proof_abs_max_example.pdf} % left bottom right top
+\caption{\algname{} with \emph{AbsMax} linkage: Example representing the only case of edge contraction $e_{uv}$ that would introduce a positive attractive interaction between two constrained clusters.
+Note this can actually never happen with an \emph{AbsMax} linkage, because edge $e_{ut}$ has a lower absolute priority as compared to $e_{uv}$, so clusters $u$ and $t$ cannot have been constrained before $u$ and $v$ are merged.
+}
+\label{fig:abs_max_proof_example}  
+\end{figure}
 
@@
 Blue pixels represent boundary evidence.
-Image a) shows the original CNN predictions, b) the under-clustering biased version $\tilde{F}_{+}$ and c) the over-clustering biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
+Image a) shows the original CNN predictions, b) the under-clustering biased version $\tilde{F}_{+}$ and c) the over-clustering biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}) \TODO{raw overlay}.
     %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 

### 2019-05-23 chapters/0_abstract.tex
Update final details
Add Elke comments; squeeze for 1st submission

@@
 We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes.
-This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and cannot-link constraints, i.e.
-mutual exclusion between clusters.
-We then prove how these different combinations correspond to existing clustering methods as well as new algorithms that we introduce and analyze.
+This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and cannot-link constraints.
+We prove how these different combinations correspond to existing clustering methods as well as new algorithms that we introduce and analyze.
 An extensive comparison study is performed to evaluate properties of the clustering algorithms, e.g.
 robustness and efficiency, by applying them to instance segmentation, which is the task of partitioning an image into distinct segments.
-% and by predicting edge weights with a CNN. 
-We then show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and the CityScapes dataset.
+We show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and the CityScapes dataset.
 \end{abstract}

### 2019-05-23 chapters/1_intro.tex
Add Elke comments; squeeze for 1st submission

@@
 This can be done optimally by solving the so-called \emph{multicut optimization} or \emph{correlation clustering} problem \cite{kappes2011globally,chopra1991multiway}.
-However, this problem is NP-hard, so instead of finding optimal solutions, several greedy agglomerative clustering algorithms were proposed.
+However, this problem is NP-hard, so instead of finding optimal solutions, several greedy agglomerative clustering algorithms have been proposed.
 % Some of these methods \cite{levinkov2017comparative,wolf2018mutex} dynamically introduce cannot-link constraints, representing mutual exclusion relationships between clusters.
@@
 Thus, agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter free and efficient.
-Despite the fact that there exist a variety of these algorithms \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}, there have been no overarching studies comparing them and making it possible to choose the most appropriate algorithm for particular applications and assess their properties, e.g.
+Despite the fact that there exists a variety of these algorithms \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}, there have been no overarching studies comparing them and making it possible to choose the most appropriate algorithm for particular applications and assess their properties, e.g.
 robustness and efficiency.
@@
 %, where the number of instances is usually not known in advance.
-We use a CNN to predict the edge weights of a graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms in our framework.
+We use a CNN to predict the edge weights of a graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms in our framework (see Fig.
+\ref{fig:intro_figure}).
 % For our experiments, we focus on a \emph{proposal-free} deep learning method that does not involve object detection but directly group pixels into object instances. 
@@
 % \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
-\includegraphics[width=0.95\textwidth]{./figs/intro_image_v2.pdf} % left bottom right top
+\includegraphics[width=0.85\textwidth]{./figs/intro_image_v2.pdf} % left bottom right top
 \caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge.
-\textbf{(2)} Some short- and long-range predictions of our UNet model.
-\textbf{(3)} Outputs of three different agglomerative algorithms included in the proposed generalized framework.
-The  agglomeration order in (a) shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black).
-The final clustering / instance segmentation is shown in (b).
-We also illustrate some iterations of the algorithms on toy graph examples with attractive (green) and repulsive (red) interactions.
+\textbf{(2)} Some short- and long-range predictions of our UNet model, where white pixels represent boundary evidence.
+\textbf{(3)} Outputs of three different agglomerative algorithms included in our proposed generalized clustering framework.
+The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black).
+The final clustering / instance segmentation is shown in 3c, overlaid with the raw image.
+In 3a, we also illustrate some iterations of the algorithms on toy graph examples with attractive (green) and repulsive (red) interactions.
 %We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 

### 2019-05-23 chapters/3_algorithm.tex
Add Elke comments; squeeze for 1st submission

@@
 
-\section{Generalized Framework for Agglomerative Clustering of Signed Graphs} \label{sec:general_framework}
+\section{Generalized framework for agglomerative clustering of signed graphs} \label{sec:general_framework}
 In this section, we first define notation and then introduce one of our main contributions: a signed graph partitioning algorithm (Sec.
@@
 % In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. 
-The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates to every edge a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms \UPDATE{REFS} for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}.
+The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates to every edge a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}.
 On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates to each edge a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters.
@@
 
-\subsection{\algname{}: Generalized Algorithm for Agglomerative Signed Graph Partitioning} \label{sec:algorithm}
+\subsection{\algname{}: Generalized algorithm for agglomerative signed graph partitioning} \label{sec:algorithm}
 
@@
 The algorithm has two variants, depending on the boolean value of the input option \texttt{addCannotLinkConstraints}.
-The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see Fig.
+The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see iterations on toy graphs in block 3 of Fig.
 \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}).
@@
     \begin{subtable}[t!]{\textwidth}\centering
-        \begin{tabular}{c r  l ? c | c | c}
+        \begin{tabular}{c r  l | c | c  c}
             % \toprule\toprule
-            \multicolumn{3}{c?}{\multirow{2}{*}[-0.5em]{\thead{\textbf{}}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
+            \multicolumn{3}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{Linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
             % \cmidrule(l{.15em}){4-5}
@@
             % \multicolumn{2}{c||}{} &  &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
-            \multicolumn{3}{c?}{} &  &  \multicolumn{1}{c|}{\thead{No Constraints}} & \thead{With Constraints} \\
+            \multicolumn{3}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\
 
-            \midrule[0.3em]
+            \midrule
             % \cmidrule[0.3em]{2-6}
@@
             % \midrule \midrule
-            \multirow{5}{*}[-0.5em]{\begin{turn}{90}\thead{\textbf{Linkage criteria} $\,\,\interact(S_u ,S_v)$}\end{turn}}  & Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
+            % \multirow{5}{*}[-0.5em]{\begin{turn}{90}\thead{\textbf{Linkage criteria} $\,\,\interact(S_u ,S_v)$}\end{turn}} 
+             & Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
 Aggl.
@@
 % \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
-\includegraphics[width=\textwidth]{./figs/comparison_new.pdf} % left bottom right top
+\includegraphics[width=0.9\textwidth]{./figs/comparison_new.pdf} % left bottom right top
 \caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data.
@@
 Yellow arrows point out merge errors.
-The average linkage without cannot-link constraints returned the best segmentation.
+The \emph{Average} linkage without cannot-link constraints returned the best segmentation.
 % Only the involved segments are colored.
@@
 In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
- the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see bottom panel of Fig.
-\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} and Table \ref{tab:linkage-criteria}, unsigned graphs).
+ the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see Table \ref{tab:linkage-criteria}, unsigned graphs).
 

### 2019-05-23 chapters/5_experiments_cityscapes.tex
Add Elke comments; squeeze for 1st submission

@@
 their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
-Results are summarized in Table \ref{tab:results_cityscapes_val} and confirm our findings on neuron-segmentation: \algname{} with average linkage achieves the best scores, whereas other linkage tend to over-cluster, like \emph{Abs.
+Results are summarized in Table \ref{tab:results_cityscapes_val} and Fig.
+\ref{fig:cityscapes}: similarly to the previous experiments, \algname{} with \emph{Average} linkage achieves the best scores, whereas other linkage tend to over-cluster, like \emph{Abs.
 Max.}, or under-cluster and merge instances, like \emph{Sum}.
-In Appendix, Table \ref{tab:extended_results_cityscapes_val} includes the scores of all other tested \algname{} algorithms.
 The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by them, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.
+Appendix - Table \ref{tab:extended_results_cityscapes_val} includes the scores of all other tested \algname{} algorithms.
 \begin{figure}[t]
 \centering
-\begin{minipage}[T]{0.6\textwidth}
+\begin{minipage}[b]{0.5\textwidth}
     \centering
@@
 Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
- & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
+ & \textbf{\algname{} Avg-Link}& \textbf{34.3}  & 33.9  \\
 \multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 & -  \\
@@
         \end{tabular}
-    \captionof{table}{Average Precision (AP) scores (higher is better) on the cityscapes validation set achieved by the tested pipelines.}
+    \captionof{table}{Average Precision (AP) scores (higher is better) on the CityScapes validation set.}
     \label{tab:results_cityscapes_val}
 \end{minipage}\hfill
-\begin{minipage}[T]{0.37\textwidth}
+\begin{minipage}[b]{0.46\textwidth}
     \centering
-\includegraphics[width=0.95\textwidth]{./figs/cityscapes_compare_2.pdf} % left bottom right top
+\includegraphics[width=\textwidth]{./figs/cityscapes_compare_3.pdf} % left bottom right top
+\caption{Instance segmentations given by different \algname{} linkage criteria on CityScapes}\label{fig:cityscapes}
 \end{minipage}

### 2019-05-23 chapters/5_experiments_compare_rules.tex
Add Elke comments; squeeze for 1st submission

@@
 
-\subsection{Data: CREMI Challenge} \label{sec:cremi_challenge}
+\subsection{Data and methods} \label{sec:cremi_challenge}
 We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available.
 The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth.
-The results submitted to the leaderboard are evaluated using the CREMI score\footnote{\url{https://cremi.org/leaderboard/}}, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}.
+The results submitted to the leaderboard are evaluated using the CREMI score (\url{https://cremi.org/leaderboard/}), based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}.
 In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.
 
-\textbf{Additional methods tested } We compare the performances of \algname{} with other basic and state-of-the-art post-processing methods.
+\textbf{State-of-the-art methods } We compare the performances of \algname{} with other basic and state-of-the-art post-processing methods.
 To ensure a fair comparison, we test all methods on the same predictions of our CNN model.

### 2019-05-23 chapters/5_experiments_noise.tex
Add Elke comments; squeeze for 1st submission

@@
          % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
-         & \makecell[l]{\algname{}\\ Linkage} & \makecell{Cremi-Score \\(lower is better)} \\ \midrule 
+         & \makecell[l]{\algname{}\\ Linkage} & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
          % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
@@
         \end{tabular}
-    \captionof{table}{Cremi-Scores achieved by different post-processing methods. Scores are averaged over the three CREMI training datasets}
+    \captionof{table}{CREMI-Scores achieved by different post-processing methods. Scores are averaged over the three CREMI training datasets}
     \label{tab:results_cremi_train}
@@
         \begin{tabular}[t]{l|c}
-         & \makecell{Cremi-Score \\(lower is better)}  \\ \midrule
+         & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
 Our UNet + DTWS + LMC &  0.221\\
@@
         \vspace*{1.1em}
-    \captionof{table}{Current published entries of the CREMI challenge leaderboard \cite{cremiChallenge} on the three test datasets}
+    \captionof{table}{Current published entries of the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019) on the three test datasets}
     \label{tab:results_cremi_test}
@@
         \centering
-        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.2in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
+        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
         \caption{No long-range predictions: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
@@
         \centering
-        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.20in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
+        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
         \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
     \end{subfigure}
-\caption{\algname{} sensitivity to noise:  average linkage proved to be the most robust.
+\caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust.
 Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions.
@@
 In these experiments, we also want to assess how beneficial it is to use long-range CNN predictions in the agglomeration.
-Thus, we perform a set of simulations without adding long-range connections to the grid-graph and another set where we introduce them with a 10\% probability\footnote{We also performed simulations adding all the long-range predictions given by the CNN model, but we did not note major differences with the case using only 10\% of them.
+Thus, we perform a set of simulations without adding long-range connections to the grid-graph and another set where we introduce them with a 10\% probability\footnote{We also performed experiments adding all the long-range predictions given by the CNN model, but we did not note major differences with the case using only 10\% of them.
 Adding this small portion is usually sufficient to improve the scores.}.

### 2019-05-23 chapters/6_conclusions.tex
Update figs; squeeze text
Add Elke comments; squeeze for 1st submission

@@
 the Mutex Watershed \cite{wolf2018mutex}, can be reformulated as special cases of one underlying agglomerative algorithm.
-This framework also allowed us to introduce new algorithms, one of which, based on an average linkage, outperformed all the others and proved to be a simple and remarkably robust approach to process short- and long-range predictions of a CNN applied to an instance segmentation task.
+This framework also allowed us to introduce new algorithms, one of which, based on an \emph{Average} linkage, outperformed all the others and proved to be a simple and remarkably robust approach to process short- and long-range predictions of a CNN applied to an instance segmentation task.
 On biological images, this simple average agglomeration algorithm can represent a valuable choice for an user that is not willing to spend much time tuning complex task-dependent pipelines based on superpixels.
 % or test several dataset-dependent
-
 In future work we plan to extend the comparison to other types of graphs and explore common theoretical properties of the algorithms included in the framework.

### 2019-05-23 chapters/supplementary.tex
Add Elke comments; squeeze for 1st submission

@@
 
-\section{Supplementary Material}
+\section{Supplementary material}
 
@@
 that these kinds of augmentations can help to alleviate issues caused by EM-imaging artifacts.
-We use L2 loss and Adam optimizer to train the network. % \TODO{Field of view?}
+We use L2 loss and Adam optimizer to train the network. The model was trained on all the three samples with available ground truth labels.
 
@@
         \begin{tabular}{l|c|c|c|c|c}
-          \algname{} linkage & \makecell{Cremi-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
+          \algname{} linkage & \makecell{CREMI-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
           % Pipeline & method & \textsc{No} & \textsc{Yes} \\
@@
     \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set. 
+    CREMI-Score \cite{cremiChallenge}, is given by a combination of the Adapted Rand-Score (Rand-Score) and the Variation of Information Score for under-clustering (VI-merge) and over-clustering (VI-split) \cite{arganda2015crowdsourcing}.
     CLC stands for cannot-link constraints.
-For all algorithms, the chosen value of bias parameter was $\beta = 0$.}
+For all algorithms, the chosen value of bias parameter was $\beta = 0$.
+We used a machine with CPU Intel(R) Xeon(R) X5650  @ 2.67GHz for our comparison experiments.}
     \label{tab:extended_results_cremi}
@@
 \subsection{Experiments on neuron segmentation adding noise to CNN predictions} \label{sec:appendix_noise_gen}
-Additionally to the comparison on the full training dataset, we performed additional experiments on a crop of the dataset\footnote{We chose a challenging part of CREMI training sample B}, where we perturbed the predictions of the CNN with noise and we introduced additional artifacts like missing or fictitious boundary evidences.
+Additionally to the comparison on the full training dataset, we performed additional experiments on a crop of the more challenging CREMI training sample B, where we perturbed the predictions of the CNN with noise and we introduced additional artifacts like missing or fictitious boundary evidences.
 % Fig.
@@
 Blue pixels represent boundary evidence.
-Image a) shows the original CNN predictions, b) the under-clustering biased version $\tilde{F}_{+}$ and c) the over-clustering biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}) \TODO{raw overlay}.
+Image a) shows the original CNN predictions, b) the under-clustering biased version $\tilde{F}_{+}$ and c) the over-clustering biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
     %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 

### 2019-05-23 chapters/0_abstract.tex
Add Anna's comments on intro

@@
 This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and cannot-link constraints.
-We prove how these different combinations correspond to existing clustering methods as well as new algorithms that we introduce and analyze.
-An extensive comparison study is performed to evaluate properties of the clustering algorithms, e.g.
-robustness and efficiency, by applying them to instance segmentation, which is the task of partitioning an image into distinct segments.
-We show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and the CityScapes dataset.
+We prove the equivalence of the existing clustering methods to some of those combinations and introduce new algorithms for combinations which have not been studied yet.
+An extensive comparison is performed to evaluate properties of the clustering algorithms, e.g.
+robustness and efficiency, by applying them to the problem of instance segmentation in images.
+We show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset.
 \end{abstract}

### 2019-05-23 chapters/1_intro.tex
Add Anna's comments on intro

@@
 These methods are parameter-based and require users to specify the desired numbers of clusters or a termination criterion (e.g.
-spectral clustering or iterated normalized cuts) or even a supervision in terms of seeds (e.g.
+spectral clustering or iterated normalized cuts) or even to add a seed for each object  (e.g.
 seeded watershed or random walker).
@@
 Other graph clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between nodes.
-The advantage of using signed graphs over positive-weighted graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters.
+The advantage of signed graphs over positive-weighted graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters.
 This can be done optimally by solving the so-called \emph{multicut optimization} or \emph{correlation clustering} problem \cite{kappes2011globally,chopra1991multiway}.
-However, this problem is NP-hard, so instead of finding optimal solutions, several greedy agglomerative clustering algorithms have been proposed.
-% Some of these methods \cite{levinkov2017comparative,wolf2018mutex} dynamically introduce cannot-link constraints, representing mutual exclusion relationships between clusters.
+This problem is NP-hard, but approximate solvers have already been proposed \cite{beier2016efficient}.
+Besides, the general problem of graph partitioning can be solved approximately by greedy agglomerative clustering \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}.
 
-Thus, agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter free and efficient.
-Despite the fact that there exists a variety of these algorithms \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}, there have been no overarching studies comparing them and making it possible to choose the most appropriate algorithm for particular applications and assess their properties, e.g.
-robustness and efficiency.
+Agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter-free and efficient.
+Despite the fact that there exists a variety of these algorithms, no overarching study has so far been made to compare their robustness and efficiency or to provide guidelines for matching an algorithm to the partitioning problem at hand.
 
@@
 
-In this paper, we propose a novel theoretical framework for generalizing over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering, which is a popular bottom-up approach defining an hierarchy of clusters on positive-weighted graphs \cite{lance1967general}.
+In this paper, we propose a novel theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering on positive-weighted graphs \cite{lance1967general}.
 This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}.
@@
 mutual exclusion between clusters.
-We then theoretically prove that different combinations correspond to existing clustering algorithms as well as new algorithms that we introduce and explore.
+We then formally prove that some of the combinations correspond to existing clustering algorithms and introduce new algorithms for combinations which have not been explored yet.
 % The framework can also be easily expended to accommodate additional linkage criteria.
@@
 
-We evaluate and compare these algorithms on \emph{instance segmentation}, which is a computer vision task consisting in assigning each pixel of an image to an object instance.
+We evaluate and compare these algorithms on \emph{instance segmentation} - a computer vision task of assigning each pixel of an image to an object instance.
 %, where the number of instances is usually not known in advance.
@@
 
-With our comparison experiments, performed both on 2D urban scenes and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
+With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
 Our findings show that one of the new agglomerative algorithms introduced by our generalized framework, based on an average linkage criterion, consistently outperforms all other previously known agglomerative algorithms for signed graphs and achieves competitive scores on the challenging CREMI 2016 segmentation benchmark.

### 2019-05-23 chapters/1_intro.tex
Update Fig 1

@@
 % \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
-\includegraphics[width=0.85\textwidth]{./figs/intro_image_v2.pdf} % left bottom right top
+\includegraphics[width=0.95\textwidth]{./figs/intro_image_v3.pdf} % left bottom right top
 \caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge.
@@
 \textbf{(3)} Outputs of three different agglomerative algorithms included in our proposed generalized clustering framework.
+The final clustering / instance segmentation is shown in 3a, overlaid with the raw image.
 The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black).
-The final clustering / instance segmentation is shown in 3c, overlaid with the raw image.
-In 3a, we also illustrate some iterations of the algorithms on toy graph examples with attractive (green) and repulsive (red) interactions.
+In 3c, we also illustrate some iterations of the algorithms on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions.
+At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left.
 %We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 

### 2019-05-23 chapters/1_intro.tex
Update tables

@@
 With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
-Our findings show that one of the new agglomerative algorithms introduced by our generalized framework, based on an average linkage criterion, consistently outperforms all other previously known agglomerative algorithms for signed graphs and achieves competitive scores on the challenging CREMI 2016 segmentation benchmark.
+We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework.
+It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark.
 % This simple agglomerative algorithm also achieves competitive scores on the challenging CREMI 2016 segmentation benchmark, similarly to other approaches that rely on complex multi-step pipelines.
@@
 \textbf{(2)} Some short- and long-range predictions of our UNet model, where white pixels represent boundary evidence.
-\textbf{(3)} Outputs of three different agglomerative algorithms included in our proposed generalized clustering framework.
+\textbf{(3)} Outputs of two agglomerative algorithms included in our proposed generalized clustering framework, with \emph{Sum} and \emph{Average} linkage criteria.
 The final clustering / instance segmentation is shown in 3a, overlaid with the raw image.
@@
 In 3c, we also illustrate some iterations of the algorithms on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions.
-At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left.
+At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left in the graph.
 %We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 

### 2019-05-23 chapters/5_experiments_cityscapes.tex
Update tables

@@
 Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
- & \textbf{\algname{} Avg-Link}& \textbf{34.3}  & 33.9  \\
+ & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
 \multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 & -  \\

### 2019-05-23 chapters/5_experiments_compare_rules.tex
Update tables

@@
 
-\subsection{Data and methods} \label{sec:cremi_challenge}
+\subsection{Data: CREMI challenge} \label{sec:cremi_challenge}
 We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available.
@@
 In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.
-
-\textbf{State-of-the-art methods } We compare the performances of \algname{} with other basic and state-of-the-art post-processing methods.
-To ensure a fair comparison, we test all methods on the same predictions of our CNN model.
-As basic method, we perform a simple thresholding (THRESH) by running connected components on a boundary map generated from the CNN affinities (see Appendix \ref{sec:cremi_details} for more details on this and the following methods).
-On the other hand, most of state-of-the-art methods for neuron-segmentation first generates 2D superpixels and then apply a graph partitioning algorithm, since this approach so far proved to be the most reliable that could scale up to the size of the problem.
-Superpixels are usually computed with a watershed algorithm seeded at the maxima of a boundary distance transform (WSDT).
-The algorithms employed in our comparison to partition the superpixel graph were given by approximations of the multicut (WSDT+MC) and lifted multicut (WSDT+LMC) problems.

### 2019-05-23 chapters/5_experiments_noise.tex
Update tables

@@
 % \subsection{In-depth comparison of different linkage criteria for \algname{}} 
-\textbf{Comparison results } Table \ref{tab:results_cremi_train} shows how \algname{} compares to other tested post-processing methods applied to the predictions of our model. 
+\textbf{Comparison results } Table \ref{tab:results_cremi_train} shows how the agglomerative algorithms derived from our framework compare to each other.
+For a simple baseline, we also include a segmentation produced by thresholding the affinity predictions (THRESH).
 % The poor scores achieved by THRESH highlight the difficulty of the task. 
 \algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage).
-The competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem.
-In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with \emph{Average} linkage even achieved superior scores compared to other methods based on WSDT superpixels.
-This shows that this method offers a simple and successful approach growing clusters starting directly from pixels and had the advantage of avoiding potential errors in the superpixel generation.
-In fact, generating for example good quality WSDT superpixels requires to tune several parameters.
-%Our hypothesis to explain this superior performances is that, currently, there are not good ways of generating superpixels that can take the long-range predictions of the CNN into account. 
-%It is of course possible to make use of long-range predictions to compute the edge weights of the superpixel graph, but, in our experience, this process usually involves a lot of parameter tuning and trial and error.
-Moreover, superpixel generation does not usually make use of the long-range predictions of the CNN and, in our experiments, using them to compute the weights of the edges in the superpixel graph did not change the final scores.
-Fig. \ref{fig:cremi_comparison} highlights some failure cases of the different agglomerative algorithms included in our framework.
+The competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem of \cite{beier2017multicut} that uses several random forests to predict graph edge weights, relying not only on information derived from affinity maps but also raw data and shape information.
+Note that the test volumes contain several imaging artifacts that make segmentation particularly challenging and might profit from more robust edge statistics of super-pixel based approaches.
+On the other hand, the fact that our algorithm can operate on pixels directly removes the parameter tuning necessary to obtain good super-pixels and can also avoid errors that result from wrong superpixels that cannot be fixed during later agglomeration.
 In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets.
@@
     % \begin{subtable}[t!]{0.5\textwidth}\centering
-        \begin{tabular}[t]{l|l|c}
+        \begin{tabular}[t]{l|c}
         % \toprule
@@
          % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
-         & \makecell[l]{\algname{}\\ Linkage} & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
+          & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
          % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
-\textbf{Our UNet + \algname{} Avg-Link} & \textbf{Average}& \textbf{0.226}  \\
-Our UNet + Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.282 \\
-Our UNet + DTWS + MC & -& 0.310 \\
-Our UNet + DTWS + LMC & -& 0.317 \\
-Our UNet + Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.322 \\
-Our UNet + GAEC \cite{keuper2015efficient} & Sum & 0.334 \\
-Our UNet + THRESH &-& 1.521 \\ 
+\textbf{Our UNet + \algname{}} \textbf{Average}& \textbf{0.226}  \\
+Our UNet + \algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
+% Our UNet + DTWS + MC & -& 0.310 \\
+% Our UNet + DTWS + LMC & -& 0.317 \\
+Our UNet + \algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
+Our UNet + \algname{} Max. + Constraints & 0.324 \\
+Our UNet + \algname{} Sum \cite{keuper2015efficient} & 0.334 \\
+Our UNet + \algname{} Average + Constraints & 0.563 \\
+Our UNet + THRESH & 1.521 \\ 
+Our UNet + \algname{} Min & 2.522 \\
+Our UNet + \algname{} Min + Constraints & 2.522 \\
+Our UNet + \algname{} Max & 2.626 \\
 % \textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
@@
 PNI-UNet \cite{lee2017superhuman} & 0.228 \\
-\textbf{Our UNet + \algname{} Avg-Link} & \textbf{0.241} \\
+\textbf{Our UNet + \algname{} Average} & \textbf{0.241} \\
 MALA-UNet + MC \cite{funke2018large} & 0.276 \\
@@
         \end{tabular}
-        \vspace*{1.1em}
+        % \vspace*{1.1em}
     \captionof{table}{Current published entries of the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019) on the three test datasets}

### 2019-05-23 chapters/0_abstract.tex
Update figs

@@
 We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes.
-This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and cannot-link constraints.
-We prove the equivalence of the existing clustering methods to some of those combinations and introduce new algorithms for combinations which have not been studied yet.
-An extensive comparison is performed to evaluate properties of the clustering algorithms, e.g.
-robustness and efficiency, by applying them to the problem of instance segmentation in images.
+This framework defines \algname{}, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints.
+We prove the equivalence of existing clustering methods to some of those combinations, and introduce new algorithms for combinations which have not been studied.
+An extensive comparison is performed to evaluate properties of the clustering algorithms in the context of instance segmentation in images, including robustness to noise and efficiency.
 We show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset.

### 2019-05-23 chapters/1_intro.tex
Update figs

@@
 \section{Introduction}
-In computer vision, the clustering of weighted graphs has been successfully applied to such tasks as image segmentation, object tracking and pose estimation.
+In computer vision, the partitioning of weighted graphs has been successfully applied to such tasks as image segmentation, object tracking and pose estimation.
 %image segmentation, object tracking, stereo matching, etc.), to high-level tasks (e.g.

### 2019-05-23 chapters/3_algorithm.tex
Update figs

@@
 \begin{algorithm}[t]
-  \caption{\algname{}: Generalized Algorithm for Agglomerative Signed Graph Partitioning}
+  \caption{\algname{}: generalized algorithm for signed graph partitioning}
    \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}\texttt{addCannotLinkConstraints}}  \\
@@
 
-\subsection{\algname{}: Generalized algorithm for agglomerative signed graph partitioning} \label{sec:algorithm}
+\subsection{\algname{}: generalized algorithm for signed graph partitioning} \label{sec:algorithm}
 
@@
             % \toprule\toprule
-            \multicolumn{3}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{Linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
+            \multicolumn{3}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} Linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
             % \cmidrule(l{.15em}){4-5}
@@
 % \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
-\includegraphics[width=0.9\textwidth]{./figs/comparison_new.pdf} % left bottom right top
+\includegraphics[width=\textwidth]{./figs/comparison_new.pdf} % left bottom right top
 \caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data.

### 2019-05-23 chapters/5_experiments_noise.tex
Update figs

@@
 % The poor scores achieved by THRESH highlight the difficulty of the task. 
-\algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage).
+\algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC (\algname{} Sum), Greedy Fixation (\algname{} Sum + Constraints) or Mutex Watershed (\algname{} Abs.
+Max.).
 The competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem of \cite{beier2017multicut} that uses several random forests to predict graph edge weights, relying not only on information derived from affinity maps but also raw data and shape information.
@@
         \end{tabular}
-        % \vspace*{1.1em}
+        \vspace*{4.5em}
     \captionof{table}{Current published entries of the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019) on the three test datasets}

### 2019-05-23 chapters/0_abstract.tex
Last changes

@@
 We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes.
-This framework defines \algname{}, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints.
+This framework defines GASP, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints.
 We prove the equivalence of existing clustering methods to some of those combinations, and introduce new algorithms for combinations which have not been studied.

### 2019-05-23 chapters/3_algorithm.tex
Last changes

@@
   \begin{algorithmic}[1]
-      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ with each node in its own cluster
+      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$ with each node in its own cluster
       \State Initial interactions between nodes given by $\cost_e = w^+_e - w^-_e$
@@
 
-In Algorithm \ref{main_alg}, we provide a simplified pseudo-code for the proposed \algname{} algorithm that is based on a bottom-up approach starting with each node assigned to its own cluster and iteratively merging pairs of adjacent clusters.
-The algorithm has two variants, depending on the boolean value of the input option \texttt{addCannotLinkConstraints}.
-The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see iterations on toy graphs in block 3 of Fig.
+In Algorithm \ref{main_alg}, we provide simplified pseudo-code for the proposed \algname{} algorithm.
+\algname{} implements a bottom-up approach that starts by assigning each node to its own cluster and then iteratively merges pairs of adjacent clusters.
+The algorithm has two variants.
+The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual by repulsive interactions (see iterations on toy graphs in block 3 of Fig.
 \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}).
@@
 \ref{subfig:with_constraints}).
-If the interaction is repulsive, then the two clusters are constrained.
-If it is attractive, then they are merged, provided that they were not already previously constrained.
-The algorithm stops when all the remaining clusters are constrained.
+If the interaction is repulsive, then the two clusters are constrained and its members can never merge in subsequent steps.
+If the interaction is attractive, then the clusters are merged, provided that they were not previously constrained.
+The algorithm terminates when all the remaining clusters are constrained.
 % The algorithm that we will present in the next section iteratively performs a sequence of so-called \emph{edge contractions} on the original graph $\mathcal{G}(V,E,w^+, w^-)$.
@@
 
-In Appendix \ref{sec:detailed_impl}, we comment on the algorithm computational complexity $\mathcal{O}(N^2 \log N)$ and present our efficient implementation given by the edge contraction Algorithm \ref{detailed_alg} using a priority queue.
+In Appendix \ref{sec:detailed_impl}, we comment on the algorithm's computational complexity $\mathcal{O}(N^2 \log N)$ and present our efficient implementation given by the edge contraction Algorithm \ref{detailed_alg} using a priority queue.
 
@@
 
-\begin{table*}
+\begin{table*}[b]
     \centering
@@
             % \toprule\toprule
-            \multicolumn{3}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} Linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
+            \multicolumn{3}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
             % \cmidrule(l{.15em}){4-5}
@@
     \end{subtable} 
-    \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm \algname{}, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
+    \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning \algname{}, given a linkage criterium, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
 The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e.
-$E_{uv}=(S_u \times S_v) \cap E$.}
+$E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
     \label{tab:linkage-criteria}
@@
 
+%TALK ABOUT TABLE 1 and wonderfully it sumarizes 
+Our main contribution is the generalized algorithm for signed graph partitioning, short GASP, that encompasses several known and novel agglomerative algorithms on display in Table \ref{tab:linkage-criteria}.
+In our framework, individual algorithms are differentiated by the linkage criterion employed. We review them in the following paragraphs.
+
 In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
@@
 
-Given a graph with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was already proposed in \cite{levinkov2017comparative,keuper2015efficient} (Table \ref{tab:linkage-criteria}, \emph{Sum} linkage).
-They present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms solving the multicut optimization problem.
+Given a graph with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was pioneered in \cite{levinkov2017comparative,keuper2015efficient} (Table \ref{tab:linkage-criteria}, \emph{Sum} linkage).
+The authors present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms approximating the multicut optimization problem.
 The Mutex Watershed \cite{wolf2018mutex} is another signed graph partitioning algorithm that introduces dynamical cannot-link constraints.
-In Appendix \ref{sec:appendix_abs_max} we prove that it can be seen as an efficient implementation of \algname{} with \emph{Absolute maximum} linkage (see def.
-in Table \ref{tab:linkage-criteria}) and observe that in this case \algname{} returns the same clustering with or without enforcing cannot-link constraints.
-On the other hand, to our knowledge, \emph{Average}, \emph{Max} or \emph{Min} linkage criteria have never been used for signed graphs agglomerative algorithms or been combined with cannot-link constraints.
+In Appendix \ref{sec:appendix_abs_max} we prove that, surprisingly, it can also be seen as an efficient implementation of \algname{} with \emph{Absolute maximum} linkage (see def.
+in Table \ref{tab:linkage-criteria}).
+We observe that in this case \algname{} returns the same clustering with or without enforcing cannot-link constraints.
+On the other hand, to our knowledge, \emph{Average}, \emph{Max} or \emph{Min} linkage criteria have never been used for signed graph agglomerative algorithms or been combined with cannot-link constraints.
 

### 2019-05-23 chapters/5_experiments_cityscapes.tex
Last changes

@@
 Results are summarized in Table \ref{tab:results_cityscapes_val} and Fig.
-\ref{fig:cityscapes}: similarly to the previous experiments, \algname{} with \emph{Average} linkage achieves the best scores, whereas other linkage tend to over-cluster, like \emph{Abs.
-Max.}, or under-cluster and merge instances, like \emph{Sum}.
+\ref{fig:cityscapes}: similarly to the previous experiments, \algname{} with \emph{Average} linkage achieves the best scores, whereas other linkage criteria tend to over-cluster, like \emph{Abs Max}, or under-cluster and merge instances, like \emph{Sum}.
 The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by them, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.

### 2019-05-23 chapters/5_experiments_compare_rules.tex
Last changes

@@
 \subsection{Data: CREMI challenge} \label{sec:cremi_challenge}
-We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available.
+We evaluate all algorithms in the proposed framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available.
 The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth.

### 2019-05-23 chapters/5_experiments_intro.tex
Last changes

@@
 boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment.
-The affinities do not have to be limited to direct neighboring pixels
+The affinities do not have to be limited to immediately adjacent pixels
 Thus, similarly to \cite{lee2017superhuman}, we train a CNN to predict both short- and long-range affinities

### 2019-05-23 chapters/5_experiments_noise.tex
Last changes

--- 2019-05-23 chapters/5_experiments_noise.tex
@@
 % \subsection{In-depth comparison of different linkage criteria for \algname{}} 
-\textbf{Comparison results } Table \ref{tab:results_cremi_train} shows how the agglomerative algorithms derived from our framework compare to each other.
+\textbf{Comparison of linkage criteria} Table \ref{tab:results_cremi_train} shows how the agglomerative algorithms derived from our framework compare to each other.
 For a simple baseline, we also include a segmentation produced by thresholding the affinity predictions (THRESH).
 % The poor scores achieved by THRESH highlight the difficulty of the task. 
-\algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage).
-The competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem of \cite{beier2017multicut} that uses several random forests to predict graph edge weights, relying not only on information derived from affinity maps but also raw data and shape information.
+\algname{} with \emph{Average} linkage, representing one of the new algorithms derived from our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC (\algname{} Sum) \cite{keuper2015efficient}, Greedy Fixation (\algname{} Sum + Constraints) \cite{levinkov2017comparative} or Mutex Watershed (\algname{} Abs.
+Max.) \cite{wolf2018mutex}.
+The competitive performance of this simple parameter-free algorithm is also reported in Table \ref{tab:results_cremi_test}, showing the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the lifted multicut formulation of \cite{beier2017multicut} that uses several random forests to predict graph edge weights, relying not only on information derived from affinity maps but also raw data and shape information.
 Note that the test volumes contain several imaging artifacts that make segmentation particularly challenging and might profit from more robust edge statistics of super-pixel based approaches.
@@
          % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
-\textbf{Our UNet + \algname{}} \textbf{Average}& \textbf{0.226}  \\
-Our UNet + \algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
+\textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
+\algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
 % Our UNet + DTWS + MC & -& 0.310 \\
 % Our UNet + DTWS + LMC & -& 0.317 \\
-Our UNet + \algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
-Our UNet + \algname{} Max. + Constraints & 0.324 \\
-Our UNet + \algname{} Sum \cite{keuper2015efficient} & 0.334 \\
-Our UNet + \algname{} Average + Constraints & 0.563 \\
-Our UNet + THRESH & 1.521 \\ 
-Our UNet + \algname{} Min & 2.522 \\
-Our UNet + \algname{} Min + Constraints & 2.522 \\
-Our UNet + \algname{} Max & 2.626 \\
+\algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
+\algname{} Max. + Constraints & 0.324 \\
+\algname{} Sum \cite{keuper2015efficient} & 0.334 \\
+\algname{} Average + Constraints & 0.563 \\
+THRESH & 1.521 \\ 
 % \textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
@@
         \end{tabular}
-    \captionof{table}{CREMI-Scores achieved by different post-processing methods. Scores are averaged over the three CREMI training datasets}
+    \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding.
+All methods use the affinity predictions from our CNN as input.
+Scores are averages over the three CREMI training datasets.}
     \label{tab:results_cremi_train}
@@
          & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
-Our UNet + DTWS + LMC &  0.221\\
-PNI-UNet \cite{lee2017superhuman} & 0.228 \\
-\textbf{Our UNet + \algname{} Average} & \textbf{0.241} \\
-MALA-UNet + MC \cite{funke2018large} & 0.276 \\
-CRUNet \cite{zeng2017deepem3d} & 0.566  \\
+Our CNN + DTWS + LMC &  0.221\\
+PNI CNN \cite{lee2017superhuman} & 0.228 \\
+\textbf{Our CNN + \algname{} Average} & \textbf{0.241} \\
+MALA CNN + MC \cite{funke2018large} & 0.276 \\
+CRU-Net \cite{zeng2017deepem3d} & 0.566  \\
 LFC \cite{parag2017anisotropic} & 0.616  \\
@@
         \end{tabular}
-        % \vspace*{1.1em}
-    \captionof{table}{Current published entries of the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019) on the three test datasets}
+        \vspace*{1em}
+    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019). The scores are averages of the three test datasets.}
     \label{tab:results_cremi_test}
@@
 Solid lines represent median values over 30 experiments.
-Values between the 25th and the 75th percentile are shown in shade areas.
-The two set of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details).
-For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges in the pixel grid-graph.
+Values between the 25th and the 75th percentile are shown in shaded areas.
+The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details).
+For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph.
 %\textbf{Bottom}: Multicut objective (Eq.
@@
 
-\textbf{Noise experiments }  Additionally, we run a set of experiments where the CNN predictions are perturbed by noise, in order to highlight the properties of each \algname{} algorithm and perform an in-depth comparison that is as quantitative as possible.
-Appendix \ref{sec:appendix_noise_gen} introduces the type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false boundary evidences.
+\textbf{Noise experiments }  Additionally, we conduct a set of experiments where the CNN predictions are perturbed by structured noise, in order to highlight the properties of each \algname{} variant and perform an in-depth comparison that is as quantitative as possible.
+Appendix \ref{sec:appendix_noise_gen} introduces the type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false positive boundary evidence.
 Fig.
-\ref{fig:noise_plots} summarize our 12000 noise experiments: we focus on the best performing linkage criteria, i.e.
-\emph{Average}, \emph{Sum} and \emph{Abs Max}, and test them with different values of noise.
+\ref{fig:noise_plots} summarizes our 12000 noise experiments: we focus on the best performing linkage criteria, i.e.
+\emph{Average}, \emph{Sum} and \emph{Abs Max}, and test them with different amount of noise.
 In these experiments, we also want to assess how beneficial it is to use long-range CNN predictions in the agglomeration.
-Thus, we perform a set of simulations without adding long-range connections to the grid-graph and another set where we introduce them with a 10\% probability\footnote{We also performed experiments adding all the long-range predictions given by the CNN model, but we did not note major differences with the case using only 10\% of them.
-Adding this small portion is usually sufficient to improve the scores.}.
+Thus, we perform a set of simulations without adding long-range connections to the grid-graph and another set where we introduce them with a 10\% probability\footnote{We also performed experiments adding all the long-range predictions given by the CNN model, but we did not note major differences when using only 10\% of them.
+Adding this fraction is usually sufficient to improve the scores.}.
 %, both with and without use of long-range connections in the grid-graph.

### 2019-05-23 chapters/6_conclusions.tex
Last changes

--- 2019-05-21 chapters/6_conclusions.tex
@@
 \section{Conclusion}
-We have presented a novel theoretical framework for agglomerative clustering of graphs with both positive and negative weights and we have shown that several existing clustering algorithms, e.g.
+We have presented a novel unifying framework for agglomerative clustering of graphs with both positive and negative edge weights and we have shown that several existing clustering algorithms, e.g.
 the Mutex Watershed \cite{wolf2018mutex}, can be reformulated as special cases of one underlying agglomerative algorithm.
-This framework also allowed us to introduce new algorithms, one of which, based on an average linkage, outperformed all the others and proved to be a simple and remarkably robust approach to process short- and long-range predictions of a CNN applied to an instance segmentation task.
-On biological images, this simple average agglomeration algorithm can represent a valuable choice for an user that is not willing to spend much time tuning complex task-dependent pipelines based on superpixels.
+This framework also allowed us to introduce new algorithms, one of which, based on an \emph{Average} linkage criterion, outperformed all the others: It proved to be a simple and remarkably robust approach to process short- and long-range predictions of a CNN applied to an instance segmentation task.
+On biological images, this simple average agglomeration algorithm can represent a valuable choice for user who is not willing to spend much time tuning complex task-dependent pipelines based on superpixels.
 % or test several dataset-dependent
-
-In future work we plan to extend the comparison to other types of graphs and explore common theoretical properties of the algorithms included in the framework.
+In future work we plan to extend the comparison to other types of non-image graphs and explore common theoretical properties of the algorithms included in the framework.
 % We presented a generalized framework and showed how one of the new algorithms included in it, \algname{} with average linkage, represent a simple agglomerative method that does not require the user to tune parameters or generate superpixels and showed extremely competitive performances in biological images, even on the challenging and competitive task of neuron segmentation.

### 2019-06-03 chapters/1_intro.tex
Last changes
Prepare arxiv version; update figures

@@
 % \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
-\includegraphics[width=0.95\textwidth]{./figs/intro_image_v3.pdf} % left bottom right top
+\includegraphics[width=\textwidth]{./figs/intro_image_v3.pdf} % left bottom right top
 \caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge.
-\textbf{(2)} Some short- and long-range predictions of our UNet model, where white pixels represent boundary evidence.
+\textbf{(2)} Some short- and long-range predictions of our CNN model, where white pixels represent boundary evidence.
 \textbf{(3)} Outputs of two agglomerative algorithms included in our proposed generalized clustering framework, with \emph{Sum} and \emph{Average} linkage criteria.
@@
 The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black).
-In 3c, we also illustrate some iterations of the algorithms on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions.
+(\textbf{4}) Some iterations of \algname{} on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions.
 At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left in the graph.

### 2019-06-03 chapters/3_algorithm.tex
Prepare arxiv version; update figures

@@
 The algorithm has two variants.
-The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual by repulsive interactions (see iterations on toy graphs in block 3 of Fig.
+The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual by repulsive interactions (see iterations on toy graphs in block 4 of Fig.
 \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}).

### 2019-06-03 chapters/supplementary.tex
Update figs
Prepare arxiv version; update figures

@@
 \begin{algorithm}
-  \caption{\algname{} as a generalized edge contraction algorithm for signed graphs}
+  \caption{Implementation of \algname{}, generalized algorithm for signed graph partitioning}
 \hspace*{\algorithmicindent} \textbf{Input:} $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes and $M$ edges; boolean \texttt{{\color{blue}addCannotLinkConstraints}} \\
@@
 \centering
-        \includegraphics[width=0.88\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
-    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise.
-Blue pixels represent boundary evidence.
-Image a) shows the original CNN predictions, b) the under-clustering biased version $\tilde{F}_{+}$ and c) the over-clustering biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
+        % \includegraphics[width=0.88\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
+        \includegraphics[width=\textwidth,trim=0.0in -0.in -0.0in -0.4in,clip]{figs/noisy_affs_comparison.pdf}
+    \captionof{figure}{CNN predictions on a slice of the CREMI neuron segmentation challenge with and without additional noise.
+(\textbf{a}) Raw data (\textbf{b}) Original CNN predictions $F(x)$, where blue pixels represent boundary evidence (\textbf{c}) Under-clustering biased version $\tilde{F}_{+}(x;\mathcal{K})$ of the predictions defined in Eq.
+\ref{eq:noise_biased_predictions} with $\mathcal{K}=8$ (\textbf{d}) Over-clustering biased version $\tilde{F}_{-}(x;\mathcal{K})$.
+Long-range predictions are not shown.
     %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
@@
 Table \ref{tab:extended_results_cityscapes_val} lists the best-case performances for each of the methods with the chosen bias $\beta$: note that depending on the version of \algname{}, it was necessary to bias more or less the predicted edge weights.
+
+The semantic categories are assigned to each instance in the same way proposed by \cite{liu2018affinity}, i.e.
+with a majority vote based on the semantic output of the model.
+Moreover, we use the same method  proposed by \cite{liu2018affinity} to compute the edge weights of the graph by combining both semantic and instance outputs.

### 2019-06-17 chapters/2_rel_work.tex
Add test results cityscapes

@@
 \textbf{Proposal-based methods} have been highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}.
-They decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}.
+They decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,liu2018path,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}.
 % Here I could have more: \cite{pinheiro2015learning,pinheiro2016learning,hu2017fastmask} and probably something more in Deep coloring

### 2019-06-17 chapters/5_experiments_cityscapes.tex
Add test results cityscapes

--- 2019-05-23 chapters/5_experiments_cityscapes.tex
@@
 their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
-Results are summarized in Table \ref{tab:results_cityscapes_val} and Fig.
-\ref{fig:cityscapes}: similarly to the previous experiments, \algname{} with \emph{Average} linkage achieves the best scores, whereas other linkage tend to over-cluster, like \emph{Abs.
-Max.}, or under-cluster and merge instances, like \emph{Sum}.
+Results are summarized in Table \ref{tab:results_cityscapes_val} and Fig. \ref{fig:cityscapes}: \algname{} with \emph{Average} linkage is the proposal-free method that achieves the best scores.
+ Similarly to the previous experiments, other linkage criteria tend to over-cluster, like \emph{Abs Max}, or under-cluster and merge instances, like \emph{Sum}.
 The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by them, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.
 Appendix - Table \ref{tab:extended_results_cityscapes_val} includes the scores of all other tested \algname{} algorithms.
-\begin{figure}[t]
+\captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
+\renewcommand*{\thesubtable}{(\alph{subtable})}
+\begin{table}[t]
 \centering
-\begin{minipage}[b]{0.5\textwidth}
+\begin{subtable}{0.5 \textwidth}
     \centering
@@
         \begin{tabular}{l|l|cc}
-           & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
-          Pipeline & method & \textsc{No} & \textsc{Yes} \\ \midrule
-DWT \cite{bai2017deep} & - & 21.2 & - \\
-SGN \cite{liu2017sgn} & - & 29.2 & - \\
-Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
- & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
-\multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 & -  \\
+%             & & \multicolumn{2}{c}{AP} \\
+%            & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
+%           Method & method & \textsc{No} & \textsc{Yes} \\ \midrule
+% % DWT \cite{bai2017deep} & - & 21.2 & - \\
+% SGN \cite{liu2017sgn} & - & 29.2 & - \\
+% Mask R-CNN \cite{he2017mask} & - & 31.5 & - \\ \hline
+%  & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
+% \multirow{2}{*}{GMIS Model \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 & -  \\
+%  % & \algname{} Max &   24.3  &   32.5  \\
+%  & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
+%  & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
+
+Method & Agglomeration type & AP \\ \midrule
+% DWT \cite{bai2017deep} & - & 21.2 & - \\
+% SGN \cite{liu2017sgn} & - & 29.2 & - \\
+PANet \cite{liu2018path} & - & \textbf{36.5} \\
+Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
+ & \algname{} Average& 34.3 \\
+ & \algname{} Average + Constraints & 33.9 \\
+\multirow{2}{*}{GMIS Model \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 \\
  % & \algname{} Max &   24.3  &   32.5  \\
- & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
- & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
+ & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
+ & \algname{} Sum + Constraints  \cite{levinkov2017comparative} & 31.9  \\
+ & \algname{} Sum \cite{keuper2015efficient} & 31.3 \\
+
  % & \algname{} Min &  0    & 0  \\
         \end{tabular}
-    \captionof{table}{Average Precision (AP) scores (higher is better) on the CityScapes validation set.}
+    \caption{CityScapes \emph{validation} set}
     \label{tab:results_cityscapes_val}
-\end{minipage}\hfill
-\begin{minipage}[b]{0.46\textwidth}
+\end{subtable}\hfill
+\begin{subtable}{0.46\textwidth}
 \centering
-\includegraphics[width=\textwidth]{./figs/cityscapes_compare_3.pdf} % left bottom right top
-\caption{Instance segmentations given by different \algname{} linkage criteria on CityScapes}\label{fig:cityscapes}
-\end{minipage}
+    \scriptsize
+\begin{tabular}{l|cc}
+           Method & AP  & AP 50\% \\ \midrule
+           PANet \cite{liu2018path} & \textbf{31.8} & \textbf{57.1} \\
+           \textbf{Ours: GMIS Model + \algname{} Average} & 28.3 & 47.0 \\ 
+           GMIS \cite{liu2018affinity} & 27.3 & 45.6 \\
+           Mask R-CNN \cite{he2017mask} & 26.2 & 49.9 \\
+           SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
+           DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
+           DWT \cite{bai2017deep} & 19.4 & 35.3 \\
+           % SIAS\cite{} & 17.4 & 36.7 \\
+           InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
+
+        \end{tabular}
+    \caption{CityScapes \emph{test} set}
+    \label{tab:results_cityscapes_test}
+\end{subtable}
+\caption{Average Precision scores (higher is better) on the CityScapes dataset.
+\algname{} with \emph{Average} linkage combined with the GMIS Model \cite{liu2018affinity} represents the proposal-free method achieving the best results (May 2019).
+We only compare methods that did not use external data (e.g.
+COCO \cite{lin2014microsoft}) for training.}
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{./figs/cityscapes_compare_4.pdf} % left bottom right top
+\caption{Visual results given by different \algname{} linkage criteria on a crop of a CityScapes image}\label{fig:cityscapes}
 \end{figure}

### 2019-06-25 chapters/1_intro.tex
Add test results cityscapes
Delete comments

@@
 In computer vision, the partitioning of weighted graphs has been successfully applied to such tasks as image segmentation, object tracking and pose estimation. 
-%image segmentation, object tracking, stereo matching, etc.), to high-level tasks (e.g.
-image classification, object recognition, image parsing
-% to model many types of re- lations and processes in physical, biological, social and information systems
 Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes.
@@
 seeded watershed or random walker).
-%Hierarchical clustering is a popular graph clustering method, which creates a hierarchy of clusters.
-Hierarchical agglomerative clustering (HAC) is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}.
-This method usually requires the user to choose a level in the cluster hierarchy defining the desired output clustering.
 
@@
 
-%Despite their similarity to agglomerative HC algorithms for unsigned graphs with only positive weights, neither an explicit connection nor a clear experimental comparison was proposed so far.
-
 In this paper, we propose a novel theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering on positive-weighted graphs \cite{lance1967general}.
 This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}.
-%, i.e.
-mutual exclusion between clusters.
 We then formally prove that some of the combinations correspond to existing clustering algorithms and introduce new algorithms for combinations which have not been explored yet.
-% The framework can also be easily expended to accommodate additional linkage criteria.
-%As a first contribution, we reformulate several of these recently proposed graph agglomerative algorithms in a simple review framework (Sec.
-\ref{sec:general_framework}) that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract).
-From this new point of view, agglomerative HC and algorithms proposed in \cite{levinkov2017comparative,wolf2018mutex,lance1967general,kardoostsolving} all share a general procedure but differ in the way inter-cluster interaction is updated after each iteration (Table \ref{tab:linkage-criteria}).
-At the same time, we also show that this framework allows us to introduce totally new variations of these algorithms.
-%Ultimately, by presenting this simple general approach, our hope is to motivate a deeper understanding of the connection between algorithms for unsigned and signed graphs.
 
 We evaluate and compare these algorithms on \emph{instance segmentation} - a computer vision task of assigning each pixel of an image to an object instance. 
-%, where the number of instances is usually not known in advance.
 We use a CNN to predict the edge weights of a graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms in our framework (see Fig.
 \ref{fig:intro_figure}).
-% For our experiments, we focus on a \emph{proposal-free} deep learning method that does not involve object detection but directly group pixels into object instances. 
-%  (for example in electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing})
 
@@
 We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework.
-It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark.
-% This simple agglomerative algorithm also achieves competitive scores on the challenging CREMI 2016 segmentation benchmark, similarly to other approaches that rely on complex multi-step pipelines.
+It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark and is state-of-the-art on CityScapes when compared to other proposal-free methods.
+Our code is available at \url{https://github.com/abailoni/GASP}.
 
@@
 \centering
-% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
 \includegraphics[width=\textwidth]{./figs/intro_image_v3.pdf} % left bottom right top
@@
 At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left in the graph.
-%We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
-% On the left: a single cluster is returned with only attractive interactions.
- % main ideas and contributions
 \label{fig:intro_figure}}

### 2019-06-25 chapters/2_rel_work.tex
Delete comments

@@
 \section{Related work} \label{sec:related_work}
-% Recent progress in semantic segmentation \cite{long2015fully,kong2018recurrent,chen2018deeplab}, boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, %, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet},
-% and pose estimation \cite{wei2016convolutional,cao2017realtime} was mostly associated with new key ideas and architectures in deep learning, like dilated convolutions \cite{yu2015multi,chen2018deeplab} or ``hourglass'' architectures with skip connections \cite{ronneberger2015u,paszke2016enet} increasing the receptive field of view of the model.
 \textbf{Proposal-based methods} have been highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}.
 They decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,liu2018path,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}.
-% Here I could have more: \cite{pinheiro2015learning,pinheiro2016learning,hu2017fastmask} and probably something more in Deep coloring
-% \item \emph{More references:} or generate generic proposal segments and then label each one with a semantic detector \cite{hariharan2014simultaneous,chen2015multi,hariharan2015hypercolumns,dai2015convolutional,uhrig2016pixel,he2017mask}.
 They commonly rely on {Faster-RCNN}~\cite{ren2015faster} and can be trained end-to-end using non-maximum suppression.
@@
 For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
-% encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; 
 a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
 Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,kulikov2018instance}.
-% Semi-convolutiona: \cite{novotny2018semi}
-% \TODO{What about \cite{liang2018proposal} using spectral clustering?}. 
 Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}.
-%  and introducing a ﬁxed number of labels (colors) and then dynamically assigning object instances to those labels during training (coloring) \cite{kulikov2018instance}
 
@@
 In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:
-% CNNs were introduced to this application in \cite{jain2007supervised}, but further progress in deep learning and 
-% the introduction of new architectures lead to a much more refined boundary detection. 
-% or trained an end-to-end watershed region growing algorithm \cite{wolf2017learned}.  
-% Subsequent postprocessing and superpixel-merging outputs final instances. 
 some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while flood-filling networks \cite{januszewski2018high} eliminate superpixels by training a recurrent CNN to perform region growing one region at the time.
 A structured learning approach was also proposed in \cite{funke2018large,turaga2009maximin}.
-% \SOURCE{SSHMT} Check Funke proposals
 
@@
 Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters.
-% \TODO{Roman, Cocoons, Benjamin?}
 The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical HAC linkage criteria, e.g.
@@
 Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2019mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
-% \TODO{Cannot-link constraints?}
-% Missing: Funke proposals, discussion about cannot-link constraints!!!
 

### 2019-06-25 chapters/3_algorithm.tex
Delete comments

@@
 \ref{sec:alg_update_rules}).
- % introduces the proposed generalized framework: 
-%that represents a simple \UPDATE{generalized} formalization of many agglomerative graph clustering algorithms.
-\UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive node similarities and signed clustering algorithms using attractive and repulsive cues.}\\
-% we  in Sec.~\ref{sec:notation}, introduce Algorithm \ref{main_alg} in  and finally show how it can be seen as a generalization of existing and new graph clustering algorithms in .
 
@@
 We also denote as $S_u$ the cluster associated with node $u$.
-% \begin{equation}
-% S_u \equiv S \in \Pi \,\, \text{s.t.} \,\, u \in S
-% \end{equation}
-% In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. 
 The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates to every edge a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}.
@@
 All the linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
-% For example, for a \emph{maximum} linkage criterion statistic (single-linkage), the inter-cluster interaction is given by:
-% \begin{equation}\label{eq:max_linkage}
-% \interact_{S_1,S_2} = \, \max_{e\in U(S_u,S_v)} \cost(e), \qquad \text{where}\quad E_{12} = \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \}.
-% \end{equation}
-% Other common choices are \emph{minimum} (complete linkage) or \emph{average} (average linkage). %and \emph{sum}.
 
@@
       \State Initial interactions between nodes given by $\cost_e = w^+_e - w^-_e$
-      % \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
-      % \State Sort edges in priority queue (PQ) in descending order of absolute weight $|\cost_e|=|w^+_e - w^-_e|$ 
-      % \State
       \Repeat
         \State Select pair of clusters $S_u,S_v\in\Pi$ with highest absolute interaction $|\interact{}(S_u,S_v)|$
-        % \State
         \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ are \textbf{not} constrained\big]}
           \State Merge cluster $S_u$ with $S_v$: update interactions and cannot-link constraints with all their neighbors
-        % \State
         \ElsIf{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big] \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
@@
       \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \big[all adjacent clusters have cannot-link constraints\big]}
-        % \If{({\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
-        %   \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
-        %   \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
-        %     % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
-        %     \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
-        %   \EndFor
-        % \EndIf
-        % \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
-        %   \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
-        % \EndIf
-
-      % \State
       \State
@@
 The algorithm terminates when all the remaining clusters are constrained.
-% The algorithm that we will present in the next section iteratively performs a sequence of so-called \emph{edge contractions} on the original graph $\mathcal{G}(V,E,w^+, w^-)$.
-% The graph clustering algorithm we will present in Sec.
-\ref{sec:algorithm} is a bottom-up approach starting with each node assigned to its own cluster and iteratively merging clusters.
-During the agglomeration, the current clustering $\Pi$ is represented by a \emph{contracted graph} $\mathcal{G'}(\mathcal{G}, \Pi)$, such that each of its nodes represents a cluster $S \in \Pi$ and \emph{adjacent} clusters are linked by an edge.
-% For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$.
-Thus, we can easily recompute these interactions by using a simple \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$.
-As an example, given the single-linkage criterion defined in Eq.
-\ref{eq:max_linkage}, the interaction between $S_u \cup S_v$ and one of its neighbors $S_t$ is simply given by:
-% \begin{equation}
-%   \interact_{S_u \cup S_v,S_t} = f( \interact_{S_u,S_t}, \interact_{S_v,S_t}) = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) = \max \{ \tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}) \}
-% \end{equation}
-% All the update rules tested in this article are listed in Table \ref{tab:linkage-criteria}.
 
 In Appendix \ref{sec:detailed_impl}, we comment on the algorithm's computational complexity $\mathcal{O}(N^2 \log N)$ and present our efficient implementation given by the edge contraction Algorithm \ref{detailed_alg} using a priority queue.
-
-% \UPDATE{\textbf{The proposed edge contraction algorithm } Algorithm \ref{main_alg} then proceeds as follows, similarly to the one presented in \cite{levinkov2017comparative}.
-It starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first.
-It then iteratively pops one edge $e_{uv}$ from PQ and, depending on the priority $\tilde{\cost}$, does the following: in case of attractive interaction $\tilde{\cost}>0$, provided that $e_{uv}$ was not flagged as a cannot-link constraint, then merge the connected clusters, perform an edge contraction of $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and update the priorities of new double edges as explained in Fig.
-\ref{fig:edge_contraction_and_contr_graph}.
-% % For every new pair of double edges in $\tilde{\mathcal{G}}_\Pi$, update their priorities according to one of the update rules listed in Table \ref{tab:linkage-criteria} together with their cannot-link relationships.
-% If, on the other hand, the interaction is repulsive ($\tilde{\cost}\leq 0$) and the option \texttt{addCannotLink} of Alg.
-\ref{main_alg} is \texttt{True}, then the edge $e_{uv}$ is flagged as cannot-link constraint.
-% In the Supplementary material we comment on the algorithm computational complexity (Sec. \ref{sec:complexity}).}
-
- %\TODO{use def of merging process of contracted graph to define merging tree?}.
-
-% \item Comment about must-not-link relations: they give high priority to the most confident repulsive edges {}
-
-% Given a clustering $\Pi$ and a graph $\mathcal{G}(V,E,W)$, the interaction between two clusters $S_1, S_2 \in \Pi$ is usually defined in terms of a \emph{linkage criterion}, i.e.
-a function of all the edge weights connecting the two clusters:
-% \begin{equation} 
-% \begin{gathered}
-% \mathcal{L}(S_1,S_2) = \mathcal{L}(\mathcal{W})\quad \\
-%    \text{where} \quad \mathcal{W} = \{ W(e_{uv})| u\in S_1, v\in S_2 \}.
-% \end{gathered}
-% \end{equation}
 
@@
         \begin{tabular}{c r  l | c | c  c}
-            % \toprule\toprule
             \multicolumn{3}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
-            % \cmidrule(l{.15em}){4-5}
-            % \cline{4-5}
-            % \multicolumn{2}{c||}{} &  &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
             \multicolumn{3}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\
@@
             \midrule
-            % \cmidrule[0.3em]{2-6}
-            % \morecmidrules \cmidrule[0.15em]{2-6}
-            % \midrule \midrule
-            % \multirow{5}{*}[-0.5em]{\begin{turn}{90}\thead{\textbf{Linkage criteria} $\,\,\interact(S_u ,S_v)$}\end{turn}} 
              & Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
@@
 Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} \\
-            % \cmidrule[0.07em]{2-6}
 
@@
                & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Mutex Watershed \cite{wolf2018mutex}} \\
-              % \cmidrule[0.07em]{2-6}
              & \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier.
@@
 Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
-            % \cmidrule[0.07em]{2-6}
-           % \midrule
 
             & Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
-            % \cmidrule[0.07em]{2-6}
 
@@
         \end{tabular}
-        % \caption{Linkage criteria}
     \end{subtable} 
@@
 \centering
-% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
 \includegraphics[width=\textwidth]{./figs/comparison_new.pdf} % left bottom right top
@@
 The \emph{Average} linkage without cannot-link constraints returned the best segmentation.
-% Only the involved segments are colored.
- % main ideas and contributions
 \label{fig:cremi_comparison}}
@@
 
-% \begin{table*}
-%     \centering
-%     \scriptsize
-%     \begin{subtable}[t!]{\textwidth}\centering
-%         \begin{tabular}{r  l || c | c | c}
-%             % \toprule\toprule
-%             \multicolumn{2}{c||}{}  &   & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
-%             % \cmidrule(l{.15em}){4-5}
-%             % \cline{4-5}
-%             \multicolumn{2}{c||}{} & \textbf{Unsigned graphs} &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
-%              &  &  &  \thead{\textsc{No}} & \thead{\textsc{Yes}} \\        
-%             % \cmidrule[0.3em]{3-5}
-%             % \midrule[0.15em]
-%             \midrule\midrule
-%             Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} & \thead{Sum Linkage\\Hier.
-Aggl.
-Clust.} & \thead{Greedy Additive \\ Edge Contraction \cite{keuper2015efficient}} & \thead{Greedy Fixation\\\cite{levinkov2017comparative}} \\ \midrule
+\subsection{\algname{} with different linkage criteria: new and existing algorithms} \label{sec:alg_update_rules}
 
-%             \makecell[r]{Absolute \\Max:} & \thead[l]{
-%             $
-%             f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
-%             \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
-%             \tilde{\cost}_2 & \text{otherwise}
-%              \end{cases} 
-%             $}
-%                & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Mutex Watershed \\\cite{wolf2018mutex}} & \thead{Mutex Watershed\\\cite{wolf2018mutex}} \\ \midrule
-%             \makecell[r]{Mean:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                                 & \thead{ Average Linkage\\ Hier.
-Aggl.
-Clust.
-\cite{lance1967general}} & \thead{Average Linkage\\Signed Aggl.
-Clust.
-(\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
-
-%             Max: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Single Linkage\\Hier.
-Aggl.
-Clust.
-\cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl.
-Clust.
-(\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule
-
-%             Min:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Complete Linkage\\ Hier.
-Aggl.
-Clust.
-\cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl.
-Clust.
-(\textbf{NEW})} & \thead{\textbf{NEW}}
-
-%         \end{tabular}
-%         % \caption{Linkage criteria}
-%     \end{subtable} 
-%     \caption{{\small The table lists the tested update rules $f$.
-Existing and new algorithms are given by a specific choice of update rule, type of graph (signed or unsigned) and optional use of cannot-link constraints.}}
-%     \label{tab:linkage-criteria}
-% \end{table*}
-
-\subsection{\algname{} with different linkage criteria: new and existing algorithms} \label{sec:alg_update_rules}
-%In this section, we show how the choice of different update rules for the presented generalized algorithm \algname{} leads to existing and new algorithms (see Table \ref{tab:linkage-criteria}).
-
-%TALK ABOUT TABLE 1 and wonderfully it sumarizes 
 Our main contribution is the generalized algorithm for signed graph partitioning, short GASP, that encompasses several known and novel agglomerative algorithms on display in Table \ref{tab:linkage-criteria}.
@@
 
-In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
+In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, 
  the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see Table \ref{tab:linkage-criteria}, unsigned graphs).
@@
 The Mutex Watershed \cite{wolf2018mutex} is another signed graph partitioning algorithm that introduces dynamical cannot-link constraints.
-In Appendix \ref{sec:appendix_abs_max} we prove that, surprisingly, it can also be seen as an efficient implementation of \algname{} with \emph{Absolute maximum} linkage (see def.
+In Proposition \ref{prop:equiv_MWS} (see Appendix \ref{sec:appendix_abs_max}) we prove that, surprisingly, it can also be seen as an efficient implementation of \algname{} with \emph{Absolute maximum} linkage (see def.
 in Table \ref{tab:linkage-criteria}).
-We observe that in this case \algname{} returns the same clustering with or without enforcing cannot-link constraints.
+Moreover, in Proposition \ref{prop:abs_max_cannot_link_property} we also prove that \algname{} with \emph{Abs Max} linkage returns the same clustering with or without enforcing cannot-link constraints.
 On the other hand, to our knowledge, \emph{Average}, \emph{Max} or \emph{Min} linkage criteria have never been used for signed graph agglomerative algorithms or been combined with cannot-link constraints.

### 2019-06-25 chapters/5_experiments_cityscapes.tex
Delete comments

@@
 We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
-% recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing.
-Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle.
 See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.
-%that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
-% Their trained model was made publicly available, so we simply replaced their final graph-merging algorithm (MultiStepHAC) with \algname{}.
-their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
-Results are summarized in Table \ref{tab:results_cityscapes_val} and Fig. \ref{fig:cityscapes}: \algname{} with \emph{Average} linkage is the proposal-free method that achieves the best scores.
+Results are summarized in Table \ref{tab:results_cityscapes_val} and Fig. \ref{fig:cityscapes}: \algname{} with \emph{Average} linkage achieves state-of-the-art results among proposal-free methods.
  Similarly to the previous experiments, other linkage criteria tend to over-cluster, like \emph{Abs Max}, or under-cluster and merge instances, like \emph{Sum}.
@@
         \begin{tabular}{l|l|cc}
-%             & & \multicolumn{2}{c}{AP} \\
-%            & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
-%           Method & method & \textsc{No} & \textsc{Yes} \\ \midrule
-% % DWT \cite{bai2017deep} & - & 21.2 & - \\
-% SGN \cite{liu2017sgn} & - & 29.2 & - \\
-% Mask R-CNN \cite{he2017mask} & - & 31.5 & - \\ \hline
-%  & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
-% \multirow{2}{*}{GMIS Model \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 & -  \\
-%  % & \algname{} Max &   24.3  &   32.5  \\
-%  & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
-%  & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
-
             Method & Agglomeration type & AP \\ \midrule
-% DWT \cite{bai2017deep} & - & 21.2 & - \\
-% SGN \cite{liu2017sgn} & - & 29.2 & - \\
             PANet \cite{liu2018path} & - & \textbf{36.5} \\
@@
             \multirow{2}{*}{GMIS Model \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 \\
- % & \algname{} Max &   24.3  &   32.5  \\
              & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
@@
              & \algname{} Sum \cite{keuper2015efficient} & 31.3 \\
-
- % & \algname{} Min &  0    & 0  \\
         \end{tabular}
@@
            DWT \cite{bai2017deep} & 19.4 & 35.3 \\
-           % SIAS\cite{} & 17.4 & 36.7 \\
            InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
-
         \end{tabular}

### 2019-06-25 chapters/5_experiments_intro.tex
Delete comments

@@
 Currently, only proof-reading or manual tracing yields sufficient accuracy for correct circuit reconstruction \cite{schlegel2017learning}, thus further progress is required in automated reconstruction methods.
-%First, we present how we predicted signed edge weights with a CNN.
-Then we introduce the CREMI challenge and our tested methods in Sec.
-\ref{sec:cremi_challenge} and finally we present our results in Sec.
-\ref{sec:results}.
 
-% \subsection{Experimental setup: pixel grid-graph with long-range connections} \label{sec:grid_graph}
 EM segmentation is commonly performed by first predicting 
-% which pixels belong to a cell membrane using a CNN.
-As described in Sec.
-\ref{sec:related_work}, different postprocessing methods are then used to obtain a segmentation.
-The CNN can either be trained to predict
 boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment.
@@
 and use them as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image.
-% In our experiments, we divided the set of edges $E$ in $E_{\mathrm{direct}}$ connecting direct neighboring voxels and $E_{\mathrm{long}}$. 
-% See Appendix \ref{sec:training_details} for more details on the chosen neighborhood structure.
-% , data augmentation and the training with L1 loss of the used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d}.
-% We evaluate how beneficial long-range connections are by adding 
-% The output layer of the CNN will then have $m_{\mathrm{direct}}+m_{\mathrm{long}}$ channels, where $m_{\mathrm{direct}}=6$ represents the direct neighbors in 3D and $m_{\mathrm{long}}$ is the number of long-range ones.
-% The output of the CNN can be represented as a weighted 3D grid graph, such that each node represents a pixel/voxel of the volume image.
-Each node is connected to its neighbors by $m_{\mathrm{direct}}$ edges ($E_{\mathrm{direct}}$) and $m_{\mathrm{long}}$ long-range ones ($E_{\mathrm{long}}$).
-% In our experiments we evaluate how beneficial long-range connections are for the final segmentation and we add them to the graph with a given probability $p_{\mathrm{long}}$ (if $p_{\mathrm{long}}=0$, then $E_{\mathrm{long}}=\emptyset$).
-% We note that the post-processing presented in \cite{lee2017superhuman} did not use any predicted long-range connection, whereas \cite{wolf2018mutex} introduced them with strides of 2 in the XY-plane.

### 2019-06-25 chapters/5_experiments_noise.tex
Delete comments

@@
 \subsection{Results and discussion}\label{sec:results}
-% \subsection{In-depth comparison of different linkage criteria for \algname{}} 
 \textbf{Comparison of linkage criteria} Table \ref{tab:results_cremi_train} shows how the agglomerative algorithms derived from our framework compare to each other.
 For a simple baseline, we also include a segmentation produced by thresholding the affinity predictions (THRESH).
-% The poor scores achieved by THRESH highlight the difficulty of the task. 
 \algname{} with \emph{Average} linkage, representing one of the new algorithms derived from our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC (\algname{} Sum) \cite{keuper2015efficient}, Greedy Fixation (\algname{} Sum + Constraints) \cite{levinkov2017comparative} or Mutex Watershed (\algname{} Abs.
@@
 \begin{minipage}[t]{0.56\textwidth}
-% \begin{table}
     \centering
     \scriptsize
-    % \begin{subtable}[t!]{0.5\textwidth}\centering
         \begin{tabular}[t]{l|c}
-        % \toprule
-        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
-         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
           & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
-         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
 \textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
 \algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
-% Our UNet + DTWS + MC & -& 0.310 \\
-% Our UNet + DTWS + LMC & -& 0.317 \\
 \algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
@@
 THRESH & 1.521 \\ 
-% \textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
-% Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
-% DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
-% DTWS + MC & -& 0.903 $\pm$ 0.017 \\
-% % DTWS + avgHC &-& \\
-% % DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
-% % DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
-% Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
-% GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
-% THRESH &-& 0.221  $\pm$ 0.067 \\ 
-% % DTWS + \algname{} & Average& \TODO{} \\
-% % DTWS  & -& 0.010 $\pm$ 0.003\\
         \end{tabular}
@@
 LFC \cite{parag2017anisotropic} & 0.616  \\
-% Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
-% PNI-UNet & 0.228 & 0.116 \\
-% Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
-% MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
-% CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
-% LFC \cite{parag2017anisotropic} & 0.616 & \\
         \end{tabular}
@@
 \centering
-    %     \begin{subfigure}[t]{0.49 \textwidth}
-    %     \centering
-    %     \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}
-
-    %     \caption{Without long-range edges: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
-    % \end{subfigure} \hfill
-    % \begin{subfigure}[t]{0.49 \textwidth}
-    %     \centering
-    %     \includegraphics[width=\textwidth,trim=0.53in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_long_range.pdf}
-    %     \caption{With long-range edges: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
-    % \end{subfigure}
     \begin{subfigure}[t]{0.49 \textwidth}
@@
         \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_0.pdf}
-        % \caption{Without long-range edges: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
     \end{subfigure} \hfill
@@
         \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
-        % \caption{With long-range edges: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
     \end{subfigure}
@@
 For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph.
-%\textbf{Bottom}: Multicut objective (Eq.
-\ref{eq:multicut_obj}), measuring how balanced the final clusterings are (lower is better); for a clearer comparison, an offset is added to the energy values, so that the method achieving the lowest energy is always assigned to value zero.
 }\label{fig:noise_plots}
 \end{figure}
-% \begin{minipage}[b]{0.48\textwidth}
-% % \begin{figure}
-%         % \begin{subfigure}[t]{0.48 \textwidth}
-%         \centering
-%         \includegraphics[width=0.98\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}
-%         \captionof{subfigure}{Merge-biased opensimplex noise} \label{fig:thresh}
-%     \end{minipage}\hfil
-% \begin{minipage}[b]{0.48\textwidth}
-%     % \end{subfigure}%
-%     % \begin{subfigure}[t]{0.48 \textwidth}
-%         \centering
-%         \includegraphics[width=0.98\textwidth,trim=0.29in 0.31in 0.31in 0.31in,clip]{./figs/split_noise.pdf}
-%         \captionof{subfigure}{Split-biased opensimplex noise} \label{fig:ws}
-%     % \end{subfigure}
-% \captionof{figure}{Plot illustrating Adapted RAND scores achieved by UGACA and different update rules when noise is added to the edge weights...
-Solid lines represent median values, whereas values between the 25th and the 75th percentile are shown in shade areas.
-\TODO{Label which uses only local-neighbors and which uses long-range connections}}\label{fig:noise_plots}
-% % \end{figure}
 
@@
 Adding this fraction is usually sufficient to improve the scores.}.
-%, both with and without use of long-range connections in the grid-graph.
-% In Fig.
-\ref{fig:noise_plots}, we used a merge-biased noise decreasing boundary evidence.
-See Fig.
-\ref{fig:noise_split} in Appendix for a split-biased version.
 
@@
 \textbf{Sum linkage } 
-% The \emph{Sum} linkage generally outputs the most balanced graph partitioning according to the objective defined in Eq.
-\ref{eq:multicut_obj} and is then confirmed to be a good choice for initializing more complex approximations of the multicut optimization problem like \cite{beier2016efficient}.
 All our experiments show that \algname{} with \emph{Sum} linkage is the algorithm with the highest tendency to under-cluster and incorrectly merge segments (see Fig.

### 2019-06-25 chapters/supplementary.tex
Delete comments

@@
   \begin{algorithmic}[1]
-    % \Procedure{GraphEdgeContr}{{\color{blue}bool \emph{addConstraints}}}
-      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
       \State $\tilde{\mathcal{G}}(\tilde{V},\tilde{E}) \gets \mathcal{G}(V,E,w^+,w^-)$  \Comment{Init. contracted graph}
       \State \texttt{UF} $\gets$ initUnionFind($V$) \Comment{Init. data structure representing clustering}
-    %   \State PQ $\gets$ Sort $e\in E$ in descending order of $|w_e|$
         \State PQ.push$(|w_e|, e) \quad \forall e \in E $  \Comment{Init. priority queue in desc. order of $|w_e|=|w_e^+ - w_e^-|$, $\mathcal{O}(|E|)$}
         \State \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$ \Comment{Init. cannot-link constraints}
-      % \State $E_\dagger \gets \{\}$ \Comment{Set of must-not-link edges}
-    %   \State PQ.push$(e,  ) \quad \forall e \in E $  
     \State
@@
         \State \textbf{assert} \texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$) \Comment{Edges in PQ always link nodes in different clusters}
-        % \If{ $e_{uv} \notin E' $} 
-        %     \State \textbf{continue}
-        % \EndIf
         \If{({\color{ForestGreen}\textbf{$\tilde{w} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
-        %   \State $u,v \gets u,v \in V' : $
-        %   \State $S_u \gets S \in \Pi$ : $ u \in S$
-        %   \State $S_v \gets S \in \Pi$ : $ v \in S$
           \State PQ, \texttt{canBeMerged}, $\tilde{E}$ $\gets$ \textsc{UpdateNeighbors}($u,v$)
-        %   \State mergeDoubleEdges($u,v$) \Comment{Update PQ, $E_\dagger, \mathcal{G}'$}
-
-        %   \State Update costs of double edges;
-        %   \State Propagate constrained flags of double edges;
           \State $\tilde{V} \gets \tilde{V} \setminus \{ v\}$, $\quad \tilde{E} \gets \tilde{E} \setminus \{ e_{uv}\}$ \Comment{Update contracted graph}
-        %   \State $ S_u \gets S_u \cup S_v$
           \State \texttt{UF}.merge($u,v$) \Comment{Merge clusters, $\mathcal{O}(\alpha(|E|))$}
-          % \For{every new double edge}
-          %   \State Delete double edges
-          %   \State Insert new one with updated cost
-          % \EndFor
         \ElsIf{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
@@
       \State
-    %   \State
       \Return Final clustering given by union-find data structure  \texttt{UF}
-      % \State
-    % \EndProcedure
   \end{algorithmic}
@@
     \Function{UpdateNeighbors}{$u,v$}
-      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
       \State $\mathcal{N}_u = \{ t \in \tilde{V} | e_{ut}\in \tilde{E}  \}$
@@
           \State PQ.push($ |f(\tilde{w}_{ut}, \tilde{w}_{vt})|, e_{ut}$) \Comment{$\mathcal{O}(\log |E|)$  }
-        % \EndIf
         \Else
@@
       \State
-    %   \State
       \Return PQ, \texttt{canBeMerged}, $\tilde{E}$
-    %   % \State
     \EndFunction
@@
   \label{detailed_alg}
-  % \caption{where $\alpha$ is the slowly growing inverse Ackerman function}
 \end{algorithm}
@@
 \centering
-        % \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
         \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
-% \captionof{figure}{ 
-% {\small Example of edge contraction.
-First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars).
-Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$.
-In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$.
-In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from edge contraction are replaced by single edge with updated interaction $f(\tilde{\cost}(e_{tu}), \tilde{\cost}(e_{tv}))$, see definitions in Tab.~\ref{tab:linkage-criteria}.
-}
-% \label{fig:edge_contraction_and_contr_graph}  }
     \end{minipage} \hfill
@@
             \toprule
-            % \multicolumn{2}{c||}{}  &   & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
-            % \cmidrule(l{.15em}){4-5}
-            % \cline{4-5}
-            % \multicolumn{2}{c||}{} & \textbf{Unsigned graphs} &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
             Linkage criteria & Update rule $f$ \\        
@@
         \end{tabular}
-    % \captionof{table}{}
-    % \label{tab:linkage_and_update_rules}
 \end{minipage}
@@
 
-% During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.  % given by the linkage criterion defined in Sec. \ref{sec:notation} and
-% Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, with $\tilde{V} \subseteq V$ such that node $u\in \tilde{V}$ represents the associated cluster $S_u \in \Pi$.
-Edges in $\tilde{E}$ are defined by adjacency-relationships between clusters and edge weights $\tilde{\cost}_{uv}$ represent inter-cluster interactions $\interact(S_u,S_v)$.
 \paragraph*{Update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed, as shown in Algorithm \ref{main_alg}.  
-% given by the linkage criterion defined in Sec.
-\ref{sec:notation} and
 An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph.
@@
 \begin{equation}
-  \interact(S_u \cup S_v,S_t) = f\Big[ \interact(S_u,S_t), \interact(S_v,S_t) \Big] = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) %= \max \{ \tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}) \}
+  \interact(S_u \cup S_v,S_t) = f\Big[ \interact(S_u,S_t), \interact(S_v,S_t) \Big] = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) 
 \end{equation}
@@
 \ref{fig:edge_contraction_and_contr_graph} we show an example of edge contraction and we list the update rules associated to the linkage criteria we introduced in Table \ref{tab:linkage-criteria}.
-  % As an example, given the single-linkage criterion defined in Table , the interaction between $S_u \cup S_v$ and one of its neighbors $S_t$ is simply given by:
-% All the update rules tested in this article are listed in Table \ref{tab:linkage-criteria}.
 
-% \algname{} was implemented by using a standard agglomerative clustering algorithm based on a priority queue and a union
 \paragraph{Implementation} As we show in Algorithm \ref{detailed_alg}, our implementation of \algname{} is based on an union-find data structure and a heap allowing deletion of its elements.
@@
 \ref{fig:edge_contraction_and_contr_graph}.
-% For every new pair of double edges in $\tilde{\mathcal{G}}_\Pi$, update their priorities according to one of the update rules listed in Table \ref{tab:linkage-criteria} together with their cannot-link relationships.
 If, on the other hand, the interaction is repulsive ($\tilde{\cost}_{uv}\leq 0$) and the option \texttt{addCannotLinkContraints} of Alg.
@@
 Nevertheless, in our practical applications the graph is much sparser, so $\mathcal{O}(|E|)=\mathcal{O}(N)$.
-% and \UPDATE{in Fig. \ref{fig:runtime_plot} we show how the empirical runtime of \algname{} is much closer to $\mathcal{O}(N \log N)$ than $\mathcal{O}(N^2 \log N)$.} 
 With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$.
@@
       \State \texttt{UF} $\gets$ initUnionFind($V$) 
-      % \State
       \For{$(u,v)=e\in E$ in descending order of $|w_e|=|w_e^+ - w_e^-|$}
@@
       \State
-    %   \State
       \Return Final clustering given by union-find data structure \texttt{UF}
-      % \State
-    % \EndProcedure
   \end{algorithmic}
   \label{alg:mutex_watershed}
-  % \caption{where $\alpha$ is the slowly growing inverse Ackerman function}
 \end{algorithm}
@@
 \end{proof}
-\begin{prop}
+\begin{prop} \label{prop:abs_max_cannot_link_property}
 The \algname{} Algorithm \ref{detailed_alg} with the Absolute Maximum linkage defined in Eq.
@@
 \begin{proof}
-% In Proposition \ref{prop:equiv_MWS} we observed that \algname{} with Abs. Max. linkage never updates the order by which edges are iterated over
 In the \algname{} Algorithm \ref{detailed_alg}, the clustering is updated only when two clusters are merged and the condition at line 9 is satisfied. 
@@
 \end{figure}
-
-% \subsection{Multicut and correlation clustering } 
-% \TODO{Omit completely?} For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^{\mathrm{internal}}_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^{\mathrm{external}}$ the complementary set of edges whose incident nodes belong to distinct clusters:
-% \begin{equation}
-% E_\Pi^{\mathrm{internal}} \equiv \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \qquad E^{\mathrm{external}}_\Pi \equiv E \setminus E^{\mathrm{internal}}_\Pi.
-% \end{equation}
-% % \begin{align}
-% % E_\Pi^0 &= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \\
-% % E^1_\Pi &= E \setminus E^0_\Pi.
-% % \end{align}
-% The set of edges $E_\Pi^{\mathrm{external}}$ is known as the \emph{multicut} of $\mathcal{G}$ w.r.t.
-clustering $\Pi$.
-The instance of the NP-hard \emph{weighted correlation clustering/multicut problem}
-% % w.r.t. $\mathcal{G}(V,E,\cost)$ 
-% corresponds to finding the partitioning that optimally balance attraction and repulsion in the graph and is given by the following binary integer program \cite{kappes2011globally,chopra1991multiway,andres2015lifting}:
-% \begin{equation}\label{eq:multicut_obj}
-% % \min_\Pi \texttt{MC}(\Pi) \equiv
-%  \min_\Pi \sum_{e\in E} \cost_e x_e^\Pi,  \qquad \text{where} \quad x^\Pi_e = 
-%  \begin{cases} 
-%  1 & \text{if } e\in E^{\mathrm{external}}_\Pi \\
-%  0 & \text{otherwise}.
-%  \end{cases}
-% \end{equation}
-% In the next chapters we will use this objective as measure of how balanced a clustering is.
 
@@
 This time, similarly to the methods mentioned in \cite{beier2016efficient}, we used a combination of approximate solvers consisting in GAEC and Kernighan-Lin.
-%and      Other state-of-the-art multi-step-pipelines for neuron-segmentation first find 2D superpixels using WSDT and then apply a graph partitioning algorithm: in our comparison, we include one pipeline using hierarchical agglomerative clustering with average linkage (avgHC) and one using an approximation of the Lifted Multicut Problem (LMC) \cite{beier2016efficient}.
 
@@
 Thus, we decided to pre-merge the most connected components of the graph that would be anyway clustered during the first iterations of \algname{}.
-To do this, we used a simple approach: we generated a boundary probability map by taking for each voxel an average over affinities in all directions (both short- and long-range ones) and we run THRESH to find the connected components.
-With this approach, pixels are pre-clustered only when they are far away (in all directions) from all predicted boundaries.
- To make sure that in this preprocessing step different neurons are never merged together by mistake, we intersected these segments given by the conservative THRESH with the segments given by WSDT.
-%\TODO{show figure?}
- By using this method, we initialized \algname{} with a reduced graph that represents a true over-segmentation.
-In our experiments, the use of this preprocessing method did not impact the final scores achieved by \algname{} and significantly reduced its runtime.
-On the full datasets, we used only 10 \% of the long-range connections in the pixel-graph, since adding all of them did not improve the scores and only made the simulations much slower and memory inefficient.
+To do this, we used a simple approach: we generated a boundary probability map by taking for each voxel an average over affinities in all directions (both short- and long-range ones) and we run THRESH with a conservative threshold parameter to find the connected components.
+With this approach, pixels are pre-clustered only when they are far away (in all directions) from predicted boundaries.
+ To make sure that in this preprocessing step different neurons are never merged together by mistake, we intersected the segments given by THRESH with the segments given by WSDT. 
+ In our experiments, the use of this preprocessing method did not introduce any major changes in the final segmentations and scores achieved, but significantly reduced the runtime.
+Moreover, to reduce the runtime and memory requirements even further, we used only 10 \% of the long-range connections in the pixel-graph, since adding all of them did not improve the scores.
 
@@
     \footnotesize
-% \begin{minipage}[T]{0.85\textwidth}
-%     \centering
         \begin{tabular}{l|c|c|c|c|c}
           \algname{} linkage & \makecell{CREMI-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
-          % Pipeline & method & \textsc{No} & \textsc{Yes} \\
-
-% Average & 0.226 & 0.936 & 0.315 & 0.494 & 
-% Sum + CLC & 0.282 & 0.906 & 0.358 & 0.510 & 
-% Abs Max & 0.322 & 0.897 & 0.286 & 0.735 & 
-% Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 
-% Sum & 0.334 & 0.872 & 0.461 & 0.444 & 
-% Average + CLC & 0.563 & 0.772 & 0.259 & 1.142 & 
-% Min & 2.522 & 0.030 & 0.197 & 6.365 & 
-% Min + CLC & 2.522 & 0.030 & 0.197 & 6.365 & 
-% Max & 2.626 & 0.028 & 7.069 & 0.026 & 
 Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 0.494 & 3.49 $\cdot$ 10$^4$ \\
@@
 \end{table}
-% \hfill
-% \begin{minipage}[T]{0.6\textwidth}
-% \centering
-%         \includegraphics[width=0.88\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
-%     \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise.
-Blue pixels represent boundary evidence.
-Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}).
-\TODO{Overlay raw-data}
-%     %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
-%     %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
-%     }
-%     \label{fig:noisy_affs}
-% \end{minipage}
-% \end{figure}
 
-\subsection{Experiments on neuron segmentation adding noise to CNN predictions} \label{sec:appendix_noise_gen}
-Additionally to the comparison on the full training dataset, we performed additional experiments on a crop of the more challenging CREMI training sample B, where we perturbed the predictions of the CNN with noise and we introduced additional artifacts like missing or fictitious boundary evidences.
-% Fig.
-\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}a} shows an example of uncertain CNN predictions on a part of the neuron segmentation CREMI dataset.
-We now present a way of modifying the CNN output to introduce additional artifacts like a missing or false boundary evidence.
+\subsection{\algname{} sensitivity to noise: adding artifacts to CNN predictions} \label{sec:appendix_noise_gen}
+Additionally to the comparison on the full training dataset, we performed more experiments on a crop of the more challenging CREMI training sample B, where we perturbed the predictions of the CNN with noise and we introduced additional artifacts like missing or fictitious boundary evidences.
 
@@
 \begin{equation}\label{eq:noise_biased_predictions}
-% \tilde{F}(x;\theta)=\begin{cases}
-% F(x;\theta)+\mathcal{K}\cdot\max\left(N(x),0\right) & \text{if merge-biased}\\
-% F(x;\theta)+\mathcal{K}\cdot\min\left(N(x),0\right) & \text{if split-biased}
-% \end{cases}
 \tilde{F}_{\pm}(x;\mathcal{K})=F(x)\pm\big|\mathcal{K}\cdot\max\left(\pm N(x),0\right)\big|,
@@
 For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
-% one of the dimensions has a lower resolution,   such that three dimensions represent the spatial ones a
-% \multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
-%  &Yes & 0.55  & {\color{Orange} 0.319 } & {\color{Orange} 0.527 } \\\midrule
-% % Abs. max. &- & 0.45  & {\color{Orange} 0.321 } & {\color{ForestGreen} 0.531 } \\\midrule
-% % \multirow{2}{*}{Mean} &No & 0.35  & {\color{ForestGreen} 0.343 } & {\color{ForestGreen} 0.552 } \\
-%  % &Yes & 0.25  & {\color{Orange} 0.339 } & {\color{ForestGreen} 0.548 } \\\midrule
-% \multirow{2}{*}{Max} &No & 0.85 & {\color{Red} 0.243 } & {\color{Red} 0.444 } \\
-%  &Yes & 0.50  & {\color{Orange} 0.325 } & {\color{ForestGreen} 0.530 } \\\midrule
-% \multirow{2}{*}{Min} &No & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\
-%  &Yes & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\\midrule
-% \cite{liu2018affinity} &-  & -  & {\color{ForestGreen} 0.341 } & {\color{ForestGreen} 0.547 } \\
 \begin{figure}[t]
@@
 \centering
-        % \includegraphics[width=0.88\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
         \includegraphics[width=\textwidth,trim=0.0in -0.in -0.0in -0.4in,clip]{figs/noisy_affs_comparison.pdf}
@@
 Long-range predictions are not shown.
-    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
-    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
     }
@@
           \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
-          % Pipeline & method & \textsc{No} & \textsc{Yes} \\ 
           Average & 34.3 & 0.35 \\

### 2019-06-27 chapters/1_intro.tex
Fix some mistakes and polish CS results

@@
 We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework.
-It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark and is state-of-the-art on CityScapes when compared to other proposal-free methods.
+It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark and represents the best-performing proposal-free method on CityScapes.
 Our code is available at \url{https://github.com/abailoni/GASP}.
@@
 The final clustering / instance segmentation is shown in 3a, overlaid with the raw image.
-The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black).
+The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown/red), or never (black).
 (\textbf{4}) Some iterations of \algname{} on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions.

### 2019-06-27 chapters/3_algorithm.tex
Fix some mistakes and polish CS results

@@
 The algorithm has two variants.
-The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual by repulsive interactions (see iterations on toy graphs in block 4 of Fig.
+The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual repulsive interactions (see iterations on toy graphs in block 4 of Fig.
 \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}).
@@
 
-In Appendix \ref{sec:detailed_impl}, we comment on the algorithm's computational complexity $\mathcal{O}(N^2 \log N)$ and present our efficient implementation given by the edge contraction Algorithm \ref{detailed_alg} using a priority queue.
+In Appendix \ref{sec:detailed_impl}, we comment on the algorithm's computational complexity $\mathcal{O}(N^2 \log N)$ and present our implementation given by the edge contraction Algorithm \ref{detailed_alg} based on a priority queue.
 
@@
 The Mutex Watershed \cite{wolf2018mutex} is another signed graph partitioning algorithm that introduces dynamical cannot-link constraints.
-In Proposition \ref{prop:equiv_MWS} (see Appendix \ref{sec:appendix_abs_max}) we prove that, surprisingly, it can also be seen as an efficient implementation of \algname{} with \emph{Absolute maximum} linkage (see def.
+In Proposition \ref{prop:equiv_MWS} (see Appendix \ref{sec:appendix_abs_max}) we prove that, surprisingly, it can also be seen as an efficient implementation of \algname{} with \emph{Absolute maximum} linkage (def.
 in Table \ref{tab:linkage-criteria}).

### 2019-06-27 chapters/5_experiments_cityscapes.tex
Fix some mistakes and polish CS results

@@
 % !TEX root = ../agglo_clust_review.tex
-\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
-We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
-See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.
-Results are summarized in Table \ref{tab:results_cityscapes_val} and Fig. \ref{fig:cityscapes}: \algname{} with \emph{Average} linkage achieves state-of-the-art results among proposal-free methods.
- Similarly to the previous experiments, other linkage criteria tend to over-cluster, like \emph{Abs Max}, or under-cluster and merge instances, like \emph{Sum}.
-The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by them, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.
-Appendix - Table \ref{tab:extended_results_cityscapes_val} includes the scores of all other tested \algname{} algorithms.
 \captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
@@
 \algname{} with \emph{Average} linkage combined with the GMIS Model \cite{liu2018affinity} represents the proposal-free method achieving the best results (May 2019).
-We only compare methods that did not use external data (e.g.
-COCO \cite{lin2014microsoft}) for training.}
+In order to have a fair comparison, we only compare methods that did not use external data (e.g.
+COCO \cite{lin2014microsoft}) for training.
+In Table (a) on the left we distinguish between proposal-based and proposal-free methods.}\label{tab:results_cityscapes}
 \end{table}
 
+\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
+We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
+We used the pipeline proposed in GMIS \cite{liu2018affinity}, representing the proposal-free method performing best on the dataset.
+The pipeline consists of two CNN with similar structures, one predicting pixel level semantic scores and the other predicting pixel affinities between instances.
+The code and the model are publicly available, so we provided its output affinities as input to \algname{}.
+In Appendix \ref{sec:appendix_cityscapes} we present how we fine-tuned the model by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.
+
+Results are summarized in Table \ref{tab:results_cityscapes} and Fig.
+\ref{fig:cityscapes}: the best scores are achieved by PANet \cite{liu2018path}, which is a proposal-based method strongly related to Mask R-CNN.
+\algname{} with \emph{Average} linkage achieves competitive results and outperforms all previously proposed proposal-free methods.
+Similarly to the experiments on neuron segmentation, other linkage criteria tend to over-cluster, like \emph{Abs Max}, or under-cluster and merge instances, like \emph{Sum}.
+The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and when we applied it to the affinities predicted by our fine-tuned model it achieved an AP score of 33.0 on the validation set, which is worse than the original value 34.1 reported in \cite{liu2018affinity}.
+This is probably due to the fact that the agglomeration MultiStepHAC was tailored to the output affinities of the original model.
+Table \ref{tab:extended_results_cityscapes_val} in Appendix includes the scores of all other tested \algname{} algorithms.
 \begin{figure}

### 2019-06-27 chapters/5_experiments_intro.tex
Fix some mistakes and polish CS results

@@
 boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment.
-The affinities do not have to be limited to immediately adjacent pixels
+The affinities do not have to be limited to immediately adjacent pixels.
 Thus, similarly to \cite{lee2017superhuman}, we train a CNN to predict both short- and long-range affinities

### 2019-06-27 chapters/supplementary.tex
Fix some mistakes and polish CS results

@@
 \paragraph{THRESH and WSDT} The basic post-processing methods we consider cannot take long-range affinities into account, so we only consider direct neighbors affinities and generate a boundary map by taking an average over the 3 directions.
-Based on this boundary map, we run connected components (THRESH) and we also introduce seeds at the maxima of the smoothed distance transform (WSDT).
+Based on this boundary map, we run connected components (THRESH) and we also run a watershed algorithm  seeded at the maxima of the smoothed distance transform (WSDT).
 For WSDT, the degree of smoothing was optimized such that each region receives as few seeds as possible, without however causing severe under-segmentation.
@@
  To make sure that in this preprocessing step different neurons are never merged together by mistake, we intersected the segments given by THRESH with the segments given by WSDT. 
- In our experiments, the use of this preprocessing method did not introduce any major changes in the final segmentations and scores achieved, but significantly reduced the runtime.
-Moreover, to reduce the runtime and memory requirements even further, we used only 10 \% of the long-range connections in the pixel-graph, since adding all of them did not improve the scores.
+ We tested \algname{} both on the full grid-graph and on this preprocessed graph and we did not notice any major differences in the final clustering or achieved scores, although the version with a pre-processed graph was significantly faster.
+To reduce the runtime and memory requirements even further, we used only 10 \% of the long-range connections in the pixel-graph, since adding all of them did not improve the scores.
 
@@
 For all algorithms, the chosen value of bias parameter was $\beta = 0$.
-We used a machine with CPU Intel(R) Xeon(R) X5650  @ 2.67GHz for our comparison experiments.}
+We used a machine with CPU Intel(R) Xeon(R) E7-4870 @ 2.40GHz for our comparison experiments.}
     \label{tab:extended_results_cremi}
@@
 For our experiments, we used the model from GMIS \cite{liu2018affinity} that is publicly available. 
+The model consists of two neural networks with similar structures, one predicting pixel level semantic scores and the other predicting pixel affinities between instances.
+We also used all the affinity post-processing methods proposed in \cite{liu2018affinity}, e.g.
+excluding background, resizing regions of interest or the proposed "affinity-refinement" method, which combines semantic and instance outputs.
  The instance-branch of the model was trained with a Binary Cross-Entropy loss, but we noticed how the short-range affinities were biased towards high probabilities, so that a strong short-range boundary evidence was never predicted by the model.
@@
 Since MultiStepHAC is a rather complex post-processing method that requires to tune several hyper-parameters, we opted for a different approach to solve the problem of the unbalanced affinities.
-We added two 1x1 convolutional layers to the instance-branch model and trained them by using the same loss used for example by \cite{wolf2018mutex} and is based on the S\o resen-Dice coefficient \cite{dice1945measures,sorensen1948method}.
+We added two 1x1 convolutional layers to the instance-branch model and trained them by using the same loss used by \cite{wolf2018mutex} and is based on the S\o resen-Dice coefficient \cite{dice1945measures,sorensen1948method}.
 Compared to Hamming-distance based loss like Binary Cross-Entropy or Mean Squared Error, the advantage of this loss is its being robust against prediction and / or target sparsity, that is a desirable quality in this application since boundaries between instances can be sparse.
@@
 In this way, these last two layers specialized in improving the predictions of boundary evidence between adjacent instances (especially those belonging to the same class).
-We then considered an average of these new fine-tuned affinities with the original unbalanced ones predicted by the model.
-During the fine-tuning process, only the parameters in the last two layers were updated.
+We then considered an average of these new fine-tuned affinities with the ones predicted by the original model.
+During the fine-tuning process, only the parameters of the last two convolutional layers were updated.
 
 Before to apply \algname{}, we performed a parameter-search for the bias $\beta$ defined in \ref{eq:mappings}.
-Table \ref{tab:extended_results_cityscapes_val} lists the best-case performances for each of the methods with the chosen bias $\beta$: note that depending on the version of \algname{}, it was necessary to bias more or less the predicted edge weights.
+Table \ref{tab:extended_results_cityscapes_val} lists the best-case performances for each of the methods: note that depending on the \algname{} linkage criterion, it was necessary to bias more or less the predicted edge weights.
 
-The semantic categories are assigned to each instance in the same way proposed by \cite{liu2018affinity}, i.e.
-with a majority vote based on the semantic output of the model.
-Moreover, we use the same method  proposed by \cite{liu2018affinity} to compute the edge weights of the graph by combining both semantic and instance outputs.
+The semantic categories are assigned to each instance in the same way proposed by \cite{liu2018affinity}, i.e. with a majority vote based on the semantic output of the model.

### 2019-11-05 chapters/2_rel_work.tex
Restructure for CVPR submission

@@
 Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,kulikov2018instance}.
+\TODO{Not convinced by the last deep coloring reference...}
 Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}.

### 2019-11-05 chapters/3_algorithm.tex
Small changes
Restructure for CVPR submission

@@
 
-\begin{figure}
-\centering
-        \begin{subfigure}[t]{0.46 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./figs/example_no_constr.pdf}
-        \caption{No constraints}\label{subfig:no_constraints}
-    \end{subfigure} \hfill
-    \begin{subfigure}[t]{0.46 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./figs/example_with_constr.pdf}
-        \caption{With cannot-link constraints}\label{subfig:with_constraints}
-    \end{subfigure}
-\caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints.
-The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges.
-We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
-\label{fig:algorithm_with_without_CLC}
-\end{figure}
-\begin{algorithm}[t]
-  \caption{\algname{}: generalized algorithm for signed graph partitioning}
-   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}\texttt{addCannotLinkConstraints}}  \\
-  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
-  \hspace*{\algorithmicindent} 
-  \begin{algorithmic}[1]
-      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$ with each node in its own cluster
-      \State Initial interactions between nodes given by $\cost_e = w^+_e - w^-_e$
-      \Repeat
-        \State Select pair of clusters $S_u,S_v\in\Pi$ with highest absolute interaction $|\interact{}(S_u,S_v)|$
-        \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ are \textbf{not} constrained\big]}
-          \State Merge cluster $S_u$ with $S_v$: update interactions and cannot-link constraints with all their neighbors
-        \ElsIf{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big] \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
-          \State Add CannotLink Constraint between clusters $S_u$ and $S_v$
-        \EndIf
-      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \big[all adjacent clusters have cannot-link constraints\big]}
-      \State
-      \Return $\Pi$
-  \end{algorithmic}
-  \label{main_alg}
-\end{algorithm}
+% \begin{algorithm}[t]
+%   \caption{\algname{}: generalized algorithm for signed graph partitioning}
+%    \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}\texttt{addCannotLinkConstraints}}  \\
+%   \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
+%   \hspace*{\algorithmicindent} 
+%   \begin{algorithmic}[1]
+%       \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$ with each node in its own cluster
+%       \State Initial interactions between nodes given by $\cost_e = w^+_e - w^-_e$
+%       \Repeat
+%         \State Select pair of clusters $S_u,S_v\in\Pi$ with highest absolute interaction $|\interact{}(S_u,S_v)|$
+%         \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ are \textbf{not} constrained\big]}
+%           \State Merge cluster $S_u$ with $S_v$: update interactions and cannot-link constraints with all their neighbors
+%         \ElsIf{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big] \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
+%           \State Add CannotLink Constraint between clusters $S_u$ and $S_v$
+%         \EndIf
+%       \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \big[all adjacent clusters have cannot-link constraints\big]}
+%       \State
+%       \Return $\Pi$
+%   \end{algorithmic}
+%   \label{main_alg}
+% \end{algorithm}
 
@@
 
-\begin{table*}[b]
-    \centering
-    \scriptsize
-    \begin{subtable}[t!]{\textwidth}\centering
-        \begin{tabular}{c r  l | c | c  c}
-            \multicolumn{3}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
-            \multicolumn{3}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\
+\begin{algorithm}[t]
+  \begin{flushleft}
+  \caption{\algname{}: generalized algorithm for signed graph partitioning}
+   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}addCannotLinkConstraints}  \\
+  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
+  \hspace*{\algorithmicindent} 
+  \begin{algorithmic}[1]
+  \footnotesize
+  % \small
+      \State Init. clustering $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$
+      \State Init. interactions between clusters with $\cost_e = w^+_e - w^-_e$
+      \Repeat
+        \State Get $S_u,S_v\in\Pi$ with highest interaction $|\interact{}(S_u,S_v)|$
+        \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ \textbf{not} constrained\big]}
+          \State Merge cluster $S_u$ with $S_v$.
+          \State Update interactions \& constraints with neighboring clusters.
+        \ElsIf{{\color{blue}addCannotLinkConstr} \textbf{and}  \big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big]}
+          \State Add CannotLink Constraint between $S_u$ and $S_v$
+        \EndIf
+      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \break\hspace*{2.5em} \big[all adjacent clusters have cannot-link constraints\big]}
+      \State
+      \Return $\Pi$
+  \end{algorithmic}
+    \label{main_alg}
+  \end{flushleft}
 
-            \midrule
-             & Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
-Aggl.
-Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} \\
-
-             &\makecell[r]{Absolute Max:} & 
-            $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
-               & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Mutex Watershed \cite{wolf2018mutex}} \\
-             & \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier.
-Aggl.
-Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
-
-            & Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
-
-            & Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}
-
-        \end{tabular}
-    \end{subtable} 
-    \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning \algname{}, given a linkage criterium, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
-The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e.
-$E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
-    \label{tab:linkage-criteria}
-\end{table*}
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{./figs/comparison_new.pdf} % left bottom right top
-\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data.
-The main \emph{wrongly} segmented regions are highlighted in different warm colors.
-Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.
-Red arrows point to wrongly split regions.
-Yellow arrows point out merge errors.
-The \emph{Average} linkage without cannot-link constraints returned the best segmentation.
-\label{fig:cremi_comparison}}
-\end{figure}
+\end{algorithm}
 
@@
 In our experiments, we decided to focus on the linkage criteria listed in Table \ref{tab:linkage-criteria}, since they represent the most common options.
+
+\begin{figure}
+\centering
+        \begin{subfigure}[t]{0.42 \textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/example_no_constr.pdf}
+        \caption{No constraints}\label{subfig:no_constraints}
+    \end{subfigure} \hfill
+    \begin{subfigure}[t]{0.42 \textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/example_with_constr.pdf}
+        \caption{With cannot-link constraints}\label{subfig:with_constraints}
+    \end{subfigure}
+\caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints.
+The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges.
+We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.
+\TODO{Explain yellow lines}}
+\label{fig:algorithm_with_without_CLC}
+\end{figure}
+
+% \begin{table*}[t]
+%     % \centering
+%     \scriptsize
+%     \begin{subtable}[t!]{0.6\textwidth}\centering
+%         \begin{tabular}{r  l | c | c  c}
+%             \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
+%             \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\
+
+%             \midrule
+%              Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
+Aggl.
+Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy\\Fixation \cite{levinkov2017comparative}} \\
+
+%              \makecell[r]{Abs. Max:} & 
+%             $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
+%                & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} \\
+%              \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier.
+Aggl.
+Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
+
+%             Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
+
+%             Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}
+
+%         \end{tabular}
+%     \end{subtable} 
+%     \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning \algname{}, given a linkage criterium, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
+The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e.
+$E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
+%     \label{tab:linkage-criteria}
+% \end{table*}
+
+\begin{table*}[t]
+    \centering
+    \footnotesize
+    \begin{subtable}[t!]{\textwidth}\centering
+        \begin{tabular}{c | c  c  c  c  c}
+        \multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} \\ $\,\,\interact(S_u ,S_v)$}}  & Sum & Absolute Maximum & Average & Maximum & Minimum \\
+ & $\displaystyle \sum_{e\in E_{uv}} \cost_e$  & $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$ & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big| $ &  $\displaystyle \max_{e\in E_{uv}} \cost_e$ & $\displaystyle \min_{e\in E_{uv}} \cost_e$ \\ \midrule
+
+            \thead{\textbf{Unsigned Graphs}} & \thead{Sum Linkage\\Hier.
+Aggl.
+Clust.} &\thead{Single Linkage\\Hier.
+Aggl.
+Clust.} &\thead{Average Linkage\\Hier.
+Aggl.
+Clust.} &\thead{Single Linkage\\Hier.
+Aggl.
+Clust.} &\thead{Complete Linkage\\Hier.
+Aggl.
+Clust.} \\
+            \thead{\textbf{Signed Graphs} \\\textbf{Without Constraints}} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
+            \thead{\textbf{Signed Graphs} \\\textbf{With Constraints}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
+            % \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
+            % \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\ \midrule
+
+            %  Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
+Aggl.
+Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy\\Fixation \cite{levinkov2017comparative}} \\
+
+            %  \makecell[r]{Abs. Max:} & 
+            % $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
+            %    & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} \\
+
+            %  \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier.
+Aggl.
+Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
+
+            % Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
+
+            % Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}
+
+        \end{tabular}
+    \end{subtable} 
+    \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning \algname{}, given a linkage criterium, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
+The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e.
+$E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
+    \label{tab:linkage-criteria}
+\end{table*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.9\textwidth]{./figs/comparison_new.pdf} % left bottom right top
+\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data.
+The main \emph{wrongly} segmented regions are highlighted in different warm colors.
+Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.
+Red arrows point to wrongly split regions.
+Yellow arrows point out merge errors.
+The \emph{Average} linkage without cannot-link constraints returned the best segmentation.
+\label{fig:cremi_comparison}}
+\end{figure*}

### 2019-11-05 chapters/5_experiments_cityscapes.tex
Small changes
Restructure for CVPR submission

@@
 % !TEX root = ../agglo_clust_review.tex
-\captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
-\renewcommand*{\thesubtable}{(\alph{subtable})}
-\begin{table}[t]
-\centering
-\begin{subtable}{0.5 \textwidth}
-    \centering
-    \scriptsize
-        \begin{tabular}{l|l|cc}
-            Method & Agglomeration type & AP \\ \midrule
-            PANet \cite{liu2018path} & - & \textbf{36.5} \\
-            Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
-             & \algname{} Average& 34.3 \\
-             & \algname{} Average + Constraints & 33.9 \\
-            \multirow{2}{*}{GMIS Model \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 \\
-             & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
-             & \algname{} Sum + Constraints  \cite{levinkov2017comparative} & 31.9  \\
-             & \algname{} Sum \cite{keuper2015efficient} & 31.3 \\
-        \end{tabular}
-    \caption{CityScapes \emph{validation} set}
-    \label{tab:results_cityscapes_val}
-\end{subtable}\hfill
-\begin{subtable}{0.46\textwidth}
-\centering
-    \scriptsize
-\begin{tabular}{l|cc}
-           Method & AP  & AP 50\% \\ \midrule
-           PANet \cite{liu2018path} & \textbf{31.8} & \textbf{57.1} \\
-           \textbf{Ours: GMIS Model + \algname{} Average} & 28.3 & 47.0 \\ 
-           GMIS \cite{liu2018affinity} & 27.3 & 45.6 \\
-           Mask R-CNN \cite{he2017mask} & 26.2 & 49.9 \\
-           SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
-           DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
-           DWT \cite{bai2017deep} & 19.4 & 35.3 \\
-           InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
-        \end{tabular}
-    \caption{CityScapes \emph{test} set}
-    \label{tab:results_cityscapes_test}
-\end{subtable}
-\caption{Average Precision scores (higher is better) on the CityScapes dataset.
+
+% \captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
+% \renewcommand*{\thesubtable}{(\alph{subtable})}
+% \begin{table}[t]
+% \centering
+% \begin{subtable}{0.5 \textwidth}
+%     \centering
+%     \scriptsize
+%         \begin{tabular}{l|l|cc}
+%             Method & Agglomeration type & AP \\ \midrule
+%             PANet \cite{liu2018path} & - & \textbf{36.5} \\
+%             Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
+%              & \algname{} Average& 34.3 \\
+%              & \algname{} Average + Constraints & 33.9 \\
+%             \multirow{2}{*}{GMIS Model \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 \\
+%              & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
+%              & \algname{} Sum + Constraints  \cite{levinkov2017comparative} & 31.9  \\
+%              & \algname{} Sum \cite{keuper2015efficient} & 31.3 \\
+%         \end{tabular}
+%     \caption{CityScapes \emph{validation} set}
+%     \label{tab:results_cityscapes_val}
+% \end{subtable}\hfill
+% \begin{subtable}{0.46\textwidth}
+% \centering
+%     \scriptsize
+% \begin{tabular}{l|cc}
+%            Method & AP  & AP 50\% \\ \midrule
+%            Panoptic-DeepLab \cite{cheng2019panopticdeeplab} & 34.6 & 57.3 \\
+%            UPSNet \cite{xiong2019upsnet} $\dagger$ & 33.0 & 59.6 \\
+%            SSAP \cite{Gao_2019_ICCV} & 32.7 & 51.8 \\
+%            PANet \cite{liu2018path} $\dagger$ & 31.8 & 57.1 \\
+%            \textbf{GMIS Model + \algname{} Average} & \textbf{28.3} & \textbf{47.0} \\ 
+%            JOSECB \cite{neven2019instance} & 27.7 & 50.9 \\
+%            GMIS \cite{liu2018affinity} & 27.3 & 45.6 \\
+%            Mask R-CNN \cite{he2017mask} $\dagger$ & 26.2 & 49.9 \\
+%            SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
+%            DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
+%            DWT \cite{bai2017deep} & 19.4 & 35.3 \\
+%            InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
+%         \end{tabular}
+%     \caption{CityScapes \emph{test} set}
+%     \label{tab:results_cityscapes_test}
+% \end{subtable}
+% \caption{Average Precision scores (higher is better) on the CityScapes dataset.
 \algname{} with \emph{Average} linkage combined with the GMIS Model \cite{liu2018affinity} represents the proposal-free method achieving the best results (May 2019).
@@
 COCO \cite{lin2014microsoft}) for training.
-In Table (a) on the left we distinguish between proposal-based and proposal-free methods.}\label{tab:results_cityscapes}
-\end{table}
+In Table (a) we distinguish between proposal-based and proposal-free methods.}\label{tab:results_cityscapes}
+% \end{table}
 
 \section{Experiments on CityScapes}\label{sec:cityscapes_exp}
-We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
+\TODO{Update} We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
 We used the pipeline proposed in GMIS \cite{liu2018affinity}, representing the proposal-free method performing best on the dataset.
@@
 Table \ref{tab:extended_results_cityscapes_val} in Appendix includes the scores of all other tested \algname{} algorithms.
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{./figs/cityscapes_compare_4.pdf} % left bottom right top
-\caption{Visual results given by different \algname{} linkage criteria on a crop of a CityScapes image}\label{fig:cityscapes}
-\end{figure}

### 2019-11-05 chapters/5_experiments_noise.tex
Fix some mistakes and polish CS results
Restructure for CVPR submission

@@
 
-\subsection{Results and discussion}\label{sec:results}
-\textbf{Comparison of linkage criteria} Table \ref{tab:results_cremi_train} shows how the agglomerative algorithms derived from our framework compare to each other.
-For a simple baseline, we also include a segmentation produced by thresholding the affinity predictions (THRESH).
-\algname{} with \emph{Average} linkage, representing one of the new algorithms derived from our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC (\algname{} Sum) \cite{keuper2015efficient}, Greedy Fixation (\algname{} Sum + Constraints) \cite{levinkov2017comparative} or Mutex Watershed (\algname{} Abs.
-Max.) \cite{wolf2018mutex}.
-The competitive performance of this simple parameter-free algorithm is also reported in Table \ref{tab:results_cremi_test}, showing the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the lifted multicut formulation of \cite{beier2017multicut} that uses several random forests to predict graph edge weights, relying not only on information derived from affinity maps but also raw data and shape information.
-Note that the test volumes contain several imaging artifacts that make segmentation particularly challenging and might profit from more robust edge statistics of super-pixel based approaches.
-On the other hand, the fact that our algorithm can operate on pixels directly removes the parameter tuning necessary to obtain good super-pixels and can also avoid errors that result from wrong superpixels that cannot be fixed during later agglomeration.
-In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets.
-Appendix Table \ref{tab:extended_results_cremi} lists the performances and the run-times for all tested \algname{} linkage.
-
-\begin{figure}[t]
-        \centering
-\begin{minipage}[t]{0.56\textwidth}
-    \centering
-    \scriptsize
-        \begin{tabular}[t]{l|c}
-          & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
-\textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
-\algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
-\algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
-\algname{} Max. + Constraints & 0.324 \\
-\algname{} Sum \cite{keuper2015efficient} & 0.334 \\
-\algname{} Average + Constraints & 0.563 \\
-THRESH & 1.521 \\ 
-        \end{tabular}
-    \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding.
-All methods use the affinity predictions from our CNN as input.
-Scores are averages over the three CREMI training datasets.}
-    \label{tab:results_cremi_train}
-\end{minipage}\hfill
-\begin{minipage}[t]{0.4\textwidth}
-    \centering
-    \scriptsize
-        \begin{tabular}[t]{l|c}
-         & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
-Our CNN + DTWS + LMC &  0.221\\
-PNI CNN \cite{lee2017superhuman} & 0.228 \\
-\textbf{Our CNN + \algname{} Average} & \textbf{0.241} \\
-MALA CNN + MC \cite{funke2018large} & 0.276 \\
-CRU-Net \cite{zeng2017deepem3d} & 0.566  \\
-LFC \cite{parag2017anisotropic} & 0.616  \\
-        \end{tabular}
-        \vspace*{1em}
-    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019). The scores are averages of the three test datasets.}
-    \label{tab:results_cremi_test}
-\end{minipage}
-\end{figure}
 \captionsetup[subfigure]{justification=centering, singlelinecheck=off}
-\begin{figure}
+\begin{figure*}
 \centering
@@
 For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph.
+Experiments are performed on a crop of CREMI training sample B.
 }\label{fig:noise_plots}
-\end{figure}
+\end{figure*}
+\begin{figure*}[t]
+        \centering
+\begin{minipage}[t]{0.31\textwidth}
+    \centering
+    \scriptsize
+        \begin{tabular}[t]{l|c}
+          & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
+\textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
+\algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
+\algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
+\algname{} Max. + Constraints & 0.324 \\
+\algname{} Sum \cite{keuper2015efficient} & 0.334 \\
+\algname{} Average + Constraints & 0.563 \\
+THRESH & 1.521 \\ 
+        \end{tabular}
+    \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding.
+All methods use the affinity predictions from our CNN as input.
+Scores are averages over the three CREMI training datasets.}
+    \label{tab:results_cremi_train}
+\end{minipage}\hfill
+\begin{minipage}[t]{0.3\textwidth}
+    \centering
+    \scriptsize
+        \begin{tabular}[t]{l|c}
+         & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
+Our CNN + DTWS + LMC &  0.221\\
+PNI CNN \cite{lee2017superhuman} & 0.228 \\
+\textbf{Our CNN + \algname{} Average} & \textbf{0.241} \\
+MALA CNN + MC \cite{funke2018large} & 0.276 \\
+CRU-Net \cite{zeng2017deepem3d} & 0.566  \\
+LFC \cite{parag2017anisotropic} & 0.616  \\
+        \end{tabular}
+        \vspace*{4.5em}
+    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019). The scores are averages of the three test datasets.}
+    \label{tab:results_cremi_test}
+\end{minipage}\hfill
+\begin{minipage}[t]{0.32\textwidth}
+\centering
+    \scriptsize
+    \vspace*{-1.5em}
+\begin{tabular}[t]{l|cc}
+            & AP  & AP 50\% \\ 
+        Method & \multicolumn{2}{c}{(higher is better)} \\ \midrule
+           Panoptic-DeepLab \cite{cheng2019panopticdeeplab} & 34.6 & 57.3 \\
+           UPSNet \cite{xiong2019upsnet} $\dagger$ & 33.0 & 59.6 \\
+           SSAP \cite{Gao_2019_ICCV} & 32.7 & 51.8 \\
+           PANet \cite{liu2018path} $\dagger$ & 31.8 & 57.1 \\
+           \textbf{GMIS Model + \algname{} Average} & \textbf{28.3} & \textbf{47.0} \\ 
+           JOSECB \cite{neven2019instance} & 27.7 & 50.9 \\
+           \textbf{GMIS Model} \cite{liu2018affinity} & \textbf{27.3} & \textbf{45.6} \\
+           Mask R-CNN \cite{he2017mask} $\dagger$ & 26.2 & 49.9 \\
+           SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
+           % DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
+           DWT \cite{bai2017deep} & 19.4 & 35.3 \\
+           InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
+        \end{tabular}
+    % \caption{CityScapes \emph{test} set}
+    \vspace*{0.7em}
+    \captionof{table}{Average Precision scores on CityScapes test. Methods marked with $\dagger$ are \emph{proposal-based}.}\label{tab:results_cityscapes}
+    \label{tab:results_cityscapes_test}
+\end{minipage}
+\end{figure*}
+
+\captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
+\renewcommand*{\thesubtable}{(\alph{subtable})}
+\begin{figure*}[t]
+\begin{minipage}{0.65 \textwidth}
+\centering
+\includegraphics[width=\textwidth]{./figs/cityscapes_compare_5.eps} % left bottom right top
+\caption{Visual results given by different \algname{} linkage criteria on a crop of a CityScapes image}\label{fig:cityscapes}
+\end{minipage}\hfill
+\begin{minipage}{0.3 \textwidth}
+    \centering
+    \small
+        \begin{tabular}[t]{l|cc}
+             Agglomeration type & AP \\ \midrule
+            % PANet \cite{liu2018path} & - & \textbf{36.5} \\
+            % Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
+              \algname{} Average& 34.3 \\
+              \algname{} Average + Constraints & 33.9 \\
+             MultiStepHAC \cite{liu2018affinity} & 33.0 \\
+              \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
+              \algname{} Sum + Constraints  \cite{levinkov2017comparative} & 31.9  \\
+              \algname{} Sum \cite{keuper2015efficient} & 31.3 \\
+        \end{tabular}
+    \vspace*{0.6em}
+    \caption{Average Precision scores on CityScapes \emph{val} achieved by the GMIS Model \cite{liu2018affinity} and different graph agglomeration methods.}
+    \label{tab:results_cityscapes_val}
+\end{minipage}
+\end{figure*}
+
+\subsection{Results and discussion}\label{sec:results}
+\textbf{Comparison of linkage criteria} Table \ref{tab:results_cremi_train} shows how the agglomerative algorithms derived from our framework compare to each other.
+For a simple baseline, we also include a segmentation produced by thresholding the affinity predictions (THRESH).
+\algname{} with \emph{Average} linkage, representing one of the new algorithms derived from our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC (\algname{} Sum) \cite{keuper2015efficient}, Greedy Fixation (\algname{} Sum + Constraints) \cite{levinkov2017comparative} or Mutex Watershed (\algname{} Abs.
+Max.) \cite{wolf2018mutex}.
+The competitive performance of this simple parameter-free algorithm is also reported in Table \ref{tab:results_cremi_test}, showing the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the lifted multicut formulation of \cite{beier2017multicut} that uses several random forests to predict graph edge weights, relying not only on information derived from affinity maps but also raw data and shape information.
+Note that the test volumes contain several imaging artifacts that make segmentation particularly challenging and might profit from more robust edge statistics of super-pixel based approaches.
+On the other hand, the fact that our algorithm can operate on pixels directly removes the parameter tuning necessary to obtain good super-pixels and can also avoid errors that result from wrong superpixels that cannot be fixed during later agglomeration.
+In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets.
+Appendix Table \ref{tab:extended_results_cremi} lists the performances and the run-times for all tested \algname{} linkage.
 

### 2019-11-08 chapters/1_intro.tex
Small changes
Restructure for CVPR submission
Add spectral exp; update Cityscapes sec. and App.

@@
 
-With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
-We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework.
-It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark and represents the best-performing proposal-free method on CityScapes.
-Our code is available at \url{https://github.com/abailoni/GASP}.
-
-\begin{figure}[t]
+\begin{figure*}[t]
 \centering
-\includegraphics[width=\textwidth]{./figs/intro_image_v3.pdf} % left bottom right top
+\includegraphics[width=0.9\textwidth]{figs/intro_image_v3.pdf} % left bottom right top
 \caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge.
@@
 \label{fig:intro_figure}}
-\end{figure}
+\end{figure*}
+
+With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
+We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework.
+\TODO{Update CS and spectral clustering}
+It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark and represents the best-performing proposal-free method on CityScapes.
+% Our code is available at \url{https://github.com/abailoni/GASP}.

### 2019-11-08 chapters/2_rel_work.tex
Add spectral exp; update Cityscapes sec. and App.

--- 2019-06-25 chapters/2_rel_work.tex
@@
 \textbf{Proposal-based methods} have been highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}.
-They decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,liu2018path,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}.
+They decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,porzi2019seamless,liu2018path,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}.
 They commonly rely on {Faster-RCNN}~\cite{ren2015faster} and can be trained end-to-end using non-maximum suppression.
@@
 a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
-Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,kulikov2018instance}.
+Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic}.
+% kulikov2018instance
 Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}. 
+\TODO{Add SSAP, predicting instance centers [Google+whatever], each instance one at the time, Seung paper}
 
@@
 Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2019mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
+\TODO{Mention spectral methods}
 

### 2019-11-08 chapters/5_experiments_cityscapes.tex
Add spectral exp; update Cityscapes sec. and App.

@@
 \section{Experiments on CityScapes}\label{sec:cityscapes_exp}
-\TODO{Update} We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
-We used the pipeline proposed in GMIS \cite{liu2018affinity}, representing the proposal-free method performing best on the dataset.
-The pipeline consists of two CNN with similar structures, one predicting pixel level semantic scores and the other predicting pixel affinities between instances.
-The code and the model are publicly available, so we provided its output affinities as input to \algname{}.
-In Appendix \ref{sec:appendix_cityscapes} we present how we fine-tuned the model by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.
+We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images.
+Several of the current top instance segmentation methods on cityscapes predict affinities, e.g. SSAP \cite{Gao_2019_ICCV} and GMIS \cite{liu2018affinity}. 
+Since \cite{liu2018affinity} made the code and model publicly available, we used their pipeline consisting of two CNNs with similar architectures (one predicting semantic scores and the other pixel affinities between instances) and applied all the post-processing methods proposed by them, e.g.
+excluding background and resizing regions of interest.
+We then provided the output instance-affinities of the model as input to \algname{}.
+In \cite{liu2018affinity} the instance-branch of the model was trained with a Binary Cross-Entropy loss, but we noticed how strong short-range boundary evidence was never predicted by the model.
+In Appendix \ref{sec:appendix_cityscapes} we present how we solved this problem by fine-tuning the model with \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.
+Finally, the semantic categories were assigned to each instance by a majority vote based on the semantic output.
 
-Results are summarized in Table \ref{tab:results_cityscapes} and Fig.
-\ref{fig:cityscapes}: the best scores are achieved by PANet \cite{liu2018path}, which is a proposal-based method strongly related to Mask R-CNN.
-\algname{} with \emph{Average} linkage achieves competitive results and outperforms all previously proposed proposal-free methods.
-Similarly to the experiments on neuron segmentation, other linkage criteria tend to over-cluster, like \emph{Abs Max}, or under-cluster and merge instances, like \emph{Sum}.
-The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and when we applied it to the affinities predicted by our fine-tuned model it achieved an AP score of 33.0 on the validation set, which is worse than the original value 34.1 reported in \cite{liu2018affinity}.
-This is probably due to the fact that the agglomeration MultiStepHAC was tailored to the output affinities of the original model.
+Results on the \emph{test} set are summarized in Table \ref{tab:results_cityscapes_test}.
+The best scores are achieved by Panoptic-DeepLab \cite{cheng2019panopticdeeplab} that proposes a more powerful CNN model and then simply predict instance centers.
+The second best \emph{proposal-free} method is SSAP \cite{Gao_2019_ICCV}, which predicts long-range instance-affinities similarly to GMIS \cite{liu2018affinity}, but trains the model with extra side-losses.
+\algname{} with \emph{Average} linkage also achieves competitive results and outperforms the previous agglomeration method proposed in \cite{liu2018affinity}.
+Similarly to the experiments on neuron segmentation, results on the \emph{val} set (see Table \ref{tab:results_cityscapes_val} and Fig.
+\ref{fig:cityscapes}) show that other \algname{} linkage criteria tend to over-cluster, e.g.
+\emph{Abs Max}, or under-cluster and merge instances, e.g.
+\emph{Sum}.
+The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and when we applied it to the affinities predicted by our fine-tuned model it achieved an AP score of 33.0 on the \emph{val} set, which is worse than the original value 34.1 reported in \cite{liu2018affinity}.
+This is probably due to the fact that MultiStepHAC was tailored to the output affinities of the original model.
 Table \ref{tab:extended_results_cityscapes_val} in Appendix includes the scores of all other tested \algname{} algorithms.

### 2019-11-08 chapters/5_experiments_noise.tex
Add spectral exp; update Cityscapes sec. and App.

@@
 \centering
-    \begin{subfigure}[t]{0.49 \textwidth}
+    \begin{subfigure}[t]{0.46 \textwidth}
         \centering
@@
     \end{subfigure} \hfill
-    \begin{subfigure}[t]{0.49 \textwidth}
+    \begin{subfigure}[t]{0.46 \textwidth}
         \centering
@@
 
-        \begin{subfigure}[t]{0.49 \textwidth}
+        \begin{subfigure}[t]{0.46 \textwidth}
         \centering
@@
         \begin{tabular}[t]{l|c}
-          & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
+         Method & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
 \textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
@@
 All methods use the affinity predictions from our CNN as input.
-Scores are averages over the three CREMI training datasets.}
+Scores are averaged over the three CREMI training datasets.}
     \label{tab:results_cremi_train}
@@
         \begin{tabular}[t]{l|c}
-         & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
+        Method & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
 Our CNN + DTWS + LMC &  0.221\\
@@
         \end{tabular}
-        \vspace*{4.5em}
-    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019). The scores are averages of the three test datasets.}
+        \vspace*{0.99em}
+    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (November 2019).
+All entries, apart from our using \algname{}, employ superpixel-based post-processing pipelines.}
     \label{tab:results_cremi_test}
 \end{minipage}\hfill
-\begin{minipage}[t]{0.32\textwidth}
+\begin{minipage}[t]{0.35\textwidth}
 \centering
@@
 \begin{tabular}[t]{l|cc}
-            & AP  & AP 50\% \\ 
-        Method & \multicolumn{2}{c}{(higher is better)} \\ \midrule
+        \multirow{2}{*}{Method}    & AP  & AP 50\% \\ 
+         & \multicolumn{2}{c}{(higher is better)} \\ \midrule
            Panoptic-DeepLab \cite{cheng2019panopticdeeplab} & 34.6 & 57.3 \\
@@
            SSAP \cite{Gao_2019_ICCV} & 32.7 & 51.8 \\
+           AdaptIS \cite{sofiiuk2019adaptis} & 32.5 & 52.5 \\
            PANet \cite{liu2018path} $\dagger$ & 31.8 & 57.1 \\
-           \textbf{GMIS Model + \algname{} Average} & \textbf{28.3} & \textbf{47.0} \\ 
+           \textbf{GMIS Model \cite{liu2018affinity} + \algname{} Average} & \textbf{28.3} & \textbf{47.0} \\ 
            JOSECB \cite{neven2019instance} & 27.7 & 50.9 \\
-           \textbf{GMIS Model} \cite{liu2018affinity} & \textbf{27.3} & \textbf{45.6} \\
+           \textbf{GMIS} \cite{liu2018affinity} & \textbf{27.3} & \textbf{45.6} \\
            Mask R-CNN \cite{he2017mask} $\dagger$ & 26.2 & 49.9 \\
@@
            % DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
-           DWT \cite{bai2017deep} & 19.4 & 35.3 \\
-           InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
+           % DWT \cite{bai2017deep} & 19.4 & 35.3 \\
+           % InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
         \end{tabular}
     % \caption{CityScapes \emph{test} set}
-    \vspace*{0.7em}
-    \captionof{table}{Average Precision scores on CityScapes test. Methods marked with $\dagger$ are \emph{proposal-based}.}\label{tab:results_cityscapes}
+    % \vspace*{0.6em}
+    \captionof{table}{Results on CityScapes test.
+Methods marked with~$\dagger$ are \emph{proposal-based}.
+Only methods that do not use external training data (e.g.
+MS COCO) are shown.}\label{tab:results_cityscapes}
     \label{tab:results_cityscapes_test}
@@
 \centering
-\includegraphics[width=\textwidth]{./figs/cityscapes_compare_5.eps} % left bottom right top
-\caption{Visual results given by different \algname{} linkage criteria on a crop of a CityScapes image}\label{fig:cityscapes}
+\includegraphics[width=\textwidth]{./figs/cityscapes_compare_6.pdf} % left bottom right top
+\caption{Visual results given by different \algname{} linkage criteria on a crop of a CityScapes image from the \emph{validation} set.}\label{fig:cityscapes}
 \end{minipage}\hfill
@@
         \begin{tabular}[t]{l|cc}
-             Agglomeration type & AP \\ \midrule
+             Agglomeration method & AP \\ \midrule
             % PANet \cite{liu2018path} & - & \textbf{36.5} \\
             % Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
-              \algname{} Average& 34.3 \\
+              \textbf{\algname{} Average}& \textbf{34.3} \\
               \algname{} Average + Constraints & 33.9 \\
@@
     \vspace*{0.6em}
-    \caption{Average Precision scores on CityScapes \emph{val} achieved by the GMIS Model \cite{liu2018affinity} and different graph agglomeration methods.}
+    \captionof{table}{Average Precision scores on CityScapes \emph{val} achieved by the GMIS Model trained in \cite{liu2018affinity} and different graph agglomeration methods.}
     \label{tab:results_cityscapes_val}
@@
 For a simple baseline, we also include a segmentation produced by thresholding the affinity predictions (THRESH).
-\algname{} with \emph{Average} linkage, representing one of the new algorithms derived from our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC (\algname{} Sum) \cite{keuper2015efficient}, Greedy Fixation (\algname{} Sum + Constraints) \cite{levinkov2017comparative} or Mutex Watershed (\algname{} Abs.
-Max.) \cite{wolf2018mutex}.
+\algname{} with \emph{Average} linkage, representing one of the new algorithms derived from our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC \cite{keuper2015efficient} (\algname{} Sum), Greedy Fixation \cite{levinkov2017comparative} (\algname{} Sum + Constraints) or Mutex Watershed \cite{wolf2018mutex} (\algname{} Abs.
+Max.).
 The competitive performance of this simple parameter-free algorithm is also reported in Table \ref{tab:results_cremi_test}, showing the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the lifted multicut formulation of \cite{beier2017multicut} that uses several random forests to predict graph edge weights, relying not only on information derived from affinity maps but also raw data and shape information.

### 2019-11-08 chapters/5_experiments_spectral.tex
Add spectral exp; update Cityscapes sec. and App.

% !TEX root = ../agglo_clust_review.tex

% \begin{figure*}[htp]
% \captionsetup{font=small}
% \hspace*{\fill}
% \begin{minipage}[t]{0.38\textwidth}
% \centering
% \vspace{0pt}
%         \includegraphics[width=\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf}
%         \captionof{figure}{Experiments on SSBM synthetic graphs}
%     \label{fig:SSBM_experiments}
% \end{minipage}\hfill
% \begin{minipage}[t]{0.25\textwidth}
% \centering
% \vspace{0pt}
%     \scriptsize
% \begin{tabular}{l|c}
%            Method & Rand-Score \\ \midrule
%            \textbf{GASP Average} & \textbf{0.8966} \\
% GASP Sum & 0.8965 \\
% GASP Abs Max & 0.8932 \\
% SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG} & 0.5839\\
% $L_{sym}$ \cite{kunegis2010spectral} & 0.1931 \\
% SPONGE \cite{Cucuringu2019SPONGEAG} & 0.0789 \\
% BNC \cite{chiang2012scalable} & 0.0074 \\
%         \end{tabular}
%     \captionof{table}{Experiments on a tiny crop of the CREMI dataset, training sample B.}
%     \label{tab:cremi_experiments}
% \end{minipage}
% \end{figure*}

\section{Comparison with spectral clustering} 
In this section we compare \algname{} to spectral clustering methods for signed graphs both on synthetic graphs and real ones from neuron segmentation. These methods \cite{Cucuringu2019SPONGEAG,chiang2012scalable,kunegis2010spectral} require the user to specify the number of clusters in advance, in contrast to our proposed agglomeration method that determines the cluster number based on the signed weights of the graph. In the following comparison, we make these baselines as strong as possible by specifying the true number of clusters for the spectral methods.

\textbf{Synthetic graphs} - First, we generated synthetic graphs from a signed stochastic block model (SSBM) where the true number of clusters is previously known. We used an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N=10^5$ vertices and edge probability $p=0.1$. Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k=100$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) had Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $0.1$. To model noise, we flipped the sign of each edge independently with probability $\eta \in [0, 0.4]$. Median scores, 25th and 75th percentiles over 30 repetitions are shown in Fig. \ref{fig:SSBM_spectral_experiments}: GASP achieved comparable scores to the spectral methods. The specific design choice of a \emph{sign flipping} noise used in the SSBM experiments turned out to favor GASP with \emph{Sum} linkage that, according to the experiments presented in Sec. \ref{sec:results}, is the one with the lowest tendency to over-cluster and grows one cluster at the time.

\textbf{Neuron segmentation} - We then extended the comparison with spectral methods to the task of neuron segmentation. Since the spectral methods cannot scale to the full CREMI dataset, we considered a random tiny crop of 10x100x100 voxels resulting in a graph with $10^5$ nodes and~$\sim10^6$ edges. Scores are summarized in Table \ref{tab:cremi_spectral_experiments}.
%suggested by the reviewer that performed best in the recent comparison \cite{Cucuringu2019SPONGEAG}: one based on the Balanced Normalized Cut (BNC) \cite{chiang2012scalable}; another on the symmetrically normalized Signed Laplacian ($L_{sym}$) \cite{kunegis2010spectral}; SPONGE and SPONGE$_{sym}$ algorithms were recently proposed in \cite{Cucuringu2019SPONGEAG}.
Despite the fact that the true number of GT clusters was given as an input to the spectral methods, GASP significantly outperformed them on neuro-data. Spectral methods seem to have more difficulties when the graph is sparse. Moreover, they did not handle well pixels on the boundaries between segments and tended to cluster them together. Increasing $k$ did not improve their scores either.

\begin{figure}
\centering
        \includegraphics[width=0.45\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf}
        \caption{Experiments on SSBM synthetic graphs \TODO{Update}}
    \label{fig:SSBM_spectral_experiments}
\end{figure}
\begin{table}
\centering
\begin{tabular}{l|c}
           Method & Rand-Score \\ \midrule
           \textbf{GASP Average} & \textbf{0.8966} \\
GASP Sum & 0.8965 \\
GASP Abs Max & 0.8932 \\
SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG} & 0.5839\\
$L_{sym}$ \cite{kunegis2010spectral} & 0.1931 \\
SPONGE \cite{Cucuringu2019SPONGEAG} & 0.0789 \\
BNC \cite{chiang2012scalable} & 0.0074 \\
        \end{tabular}
    \caption{Experiments on a tiny crop of the CREMI dataset, training sample B \TODO{Update}}
    \label{tab:cremi_spectral_experiments}
\end{table}

### 2019-11-08 chapters/6_conclusions.tex
Delete comments
Add spectral exp; update Cityscapes sec. and App.

@@
 the Mutex Watershed \cite{wolf2018mutex}, can be reformulated as special cases of one underlying agglomerative algorithm.
-This framework also allowed us to introduce new algorithms, one of which, based on an \emph{Average} linkage criterion, outperformed all the others: It proved to be a simple and remarkably robust approach to process short- and long-range predictions of a CNN applied to an instance segmentation task.
+This framework also allowed us to introduce new algorithms, one of which, based on an \emph{Average} linkage criterion, outperformed all the others: it proved to be a simple and remarkably robust approach to process short- and long-range predictions of a CNN applied to an instance segmentation task.
 On biological images, this simple average agglomeration algorithm can represent a valuable choice for user who is not willing to spend much time tuning complex task-dependent pipelines based on superpixels.
-% or test several dataset-dependent
-In future work we plan to extend the comparison to other types of non-image graphs and explore common theoretical properties of the algorithms included in the framework.
-% We presented a generalized framework and showed how one of the new algorithms included in it, \algname{} with average linkage, represent a simple agglomerative method that does not require the user to tune parameters or generate superpixels and showed extremely competitive performances in biological images, even on the challenging and competitive task of neuron segmentation.
-(good-quality superpixels are strongly dataset-dependent)
-% Compared to previously proposed agglomerative clustering methods for signed graphs, it proved to be the one making best use of the long-range predictions of the CNN; the fact that average is superior to abs max is not surprising, given the literature about HAC with single and average linkage (due to the greediness of the maximum linkage); and enforcing cannot-link constraints, we have also seen that introducing too many long-range mainly repulsive predictions can cause strong over-clustering; tendency to under-clustering of the sum linkage can be explained with the chain-reaction effect and its tendency to grow one cluster at the time that does not allow to build good statistics between adjacent clusters.
-This is partially fixed by constraints, but not really...
+In future work we plan to explore common theoretical properties of the algorithms included in the framework.

### 2019-11-08 chapters/supplementary.tex
Add spectral exp; update Cityscapes sec. and App.

@@
 
-\section{Supplementary material}
-
-\begin{algorithm}
+\begin{algorithm*}
   \caption{Implementation of \algname{}, generalized algorithm for signed graph partitioning}
@@
   \label{detailed_alg}
-\end{algorithm}
-\begin{figure}
+\end{algorithm*}
+
+\begin{figure*}
         \centering
@@
     \centering
-    \scriptsize
+    \small
                 \begin{tabular}[b]{r | l }
@@
 \label{fig:edge_contraction_and_contr_graph}  
-\end{figure}
+\end{figure*}
+
+\section{Supplementary material}
 
@@
 Thus, we can recompute these interactions by using an \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$:
-\begin{equation}
-  \interact(S_u \cup S_v,S_t) = f\Big[ \interact(S_u,S_t), \interact(S_v,S_t) \Big] = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) 
-\end{equation}
+\begin{align}
+  \interact(S_u \cup S_v,S_t) =& f\Big[ \interact(S_u,S_t), \interact(S_v,S_t) \Big] \\
+  =& f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) 
+\end{align}
 In Fig.
@@
 
-\begin{algorithm}
+\begin{algorithm*}
   \caption{Mutex Watershed Algorithm proposed by \cite{wolf2018mutex}}
@@
   \label{alg:mutex_watershed}
-\end{algorithm}
+\end{algorithm*}
 
-\subsection{Properties of \algname{} with \emph{Absolute Maximum} linkage}\label{sec:appendix_abs_max}
+\subsection{Properties of \algname{} with Absolute Maximum linkage}\label{sec:appendix_abs_max}
 \paragraph{Remark on graph notation} The definition of a graph proposed by \cite{wolf2018mutex} makes a distinction between a set of positive edges $E^+$, associated with a set $W^+$ of positive scalar attributes representing merge affinities, and a set of negative edges $E^-$, associated with a set $W^-$ of positive attributes representing split tendencies.
@@
 \begin{align}
-E^+ = \{ e \in E \,\,\text{s.t.} \,\,w_e = w_e^+ - w_e^- > 0\},& \qquad E^- = \{ e \in E \,\,\text{s.t.}\,\, w_e = w_e^+ - w_e^- \leq 0\} \\
-W^+ = \{ |w_e| \,\,\text{s.t.}\,\, e \in E^+\},& \qquad W^- = \{ |w_e| \,\,\text{s.t.}\,\, e \in E^-\}
+E^+ =&\,\, \{ e \in E \,\,\text{s.t.} \,\,w_e = w_e^+ - w_e^- > 0\}, \\
+E^- =&\,\, \{ e \in E \,\,\text{s.t.}\,\, w_e = w_e^+ - w_e^- \leq 0\}, \\
+W^+ =&\,\, \{ |w_e| \,\,\text{s.t.}\,\, e \in E^+\},\\
+ W^- =&\,\, \{ |w_e| \,\,\text{s.t.}\,\, e \in E^-\}.
 \end{align}
@@
 
-\begin{figure}
+\begin{figure*}
         \centering
@@
 \label{fig:abs_max_proof_example}  
-\end{figure}
+\end{figure*}
 
@@
 The most common approaches use \emph{additive} \cite{ailon2008aggregating} or \emph{logarithmic} \cite{finkel2008enforcing,andres2012globally} mappings:
-\begin{equation} \label{eq:mappings}
-\cost_{e,\mathrm{Add}} = p_e - \beta, \qquad \quad \cost_{e,\mathrm{Log}} = \log \left( \frac{p_e}{1-p_e} \right) - \log \left( \frac{\beta}{1-\beta} \right),
-\end{equation}
+\begin{align} 
+\cost_{e,\mathrm{Add}} =&\,\, p_e - \beta, \\
+\cost_{e,\mathrm{Log}} =&\,\, \log \left( \frac{p_e}{1-p_e} \right) - \log \left( \frac{\beta}{1-\beta} \right), \label{eq:mappings}
+\end{align}
 where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation.
@@
 
-\begin{table}[t]
+\begin{table*}[t]
 \centering
@@
     \label{tab:extended_results_cremi}
-\end{table}
+\end{table*}
 
@@
 For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
-\begin{figure}[t]
+\begin{figure*}[t]
 \centering
-\begin{minipage}[T]{0.6\textwidth}
+\begin{minipage}[T]{0.61\textwidth}
 \centering
@@
     \centering
-    \footnotesize
+    \small
+    \vspace*{1.6em}
         \begin{tabular}{l|c|c}
@@
         \end{tabular}
+    \vspace*{0.5em}
     \captionof{table}{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set.
@@
 \end{minipage}
-\end{figure}
+\end{figure*}
 

### 2019-11-11 chapters/0_abstract.tex
Add spectral exp; update Cityscapes sec. and App.
Small changes spectral clustering

@@
 An extensive comparison is performed to evaluate properties of the clustering algorithms in the context of instance segmentation in images, including robustness to noise and efficiency.
-We show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset.
+We compare GASP to spectral clustering methods on synthetic graphs and show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset.
 \end{abstract}

### 2019-11-11 chapters/1_intro.tex
Small changes spectral clustering

@@
 With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
-We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework.
-\TODO{Update CS and spectral clustering}
-It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark and represents the best-performing proposal-free method on CityScapes.
+We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework and 
+it achieves competitive performance on CityScapes and the challenging CREMI 2016 segmentation benchmark.
+
+In Sec. \ref{sec:spectral_clust}, we also show how \algname{} outperforms spectral clustering methods for signed graphs by testing it on synthetic graphs and neuron segmentation.
+
 % Our code is available at \url{https://github.com/abailoni/GASP}.

### 2019-11-11 chapters/2_rel_work.tex
Small changes spectral clustering

@@
 Recently, there has been a growing interest for such  methods that do not involve object detection, since, in certain types of data, object instances cannot be approximated by bounding boxes.
-For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
+For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation;
+% SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
 a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
-Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic}.
+Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{lee2019learning,fathi2017semantic,newell2017associative,de2017semantic}.
 % kulikov2018instance
 Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}. 
-\TODO{Add SSAP, predicting instance centers [Google+whatever], each instance one at the time, Seung paper}
+Other recent successful methods simply let the model predict the relative coordinates of the instance center \cite{neven2019instance,cheng2019panopticdeeplab}; in \cite{sofiiuk2019adaptis}, given a point $(x,y)$ in the image, the model generates the mask of the instance located at $(x,y)$.
 
-\textbf{Edge detection} also experienced recent progress thanks to deep learning, both on natural images \cite{xie2015holistically,kokkinos2015pushing} and biological data \cite{lee2017superhuman,schmidt2018cell,meirovitch2016multi,ciresan2012deep}.
+\textbf{Edge detection} also experienced recent progress thanks to deep learning, both on natural images \cite{Gao_2019_ICCV,liu2018affinity,xie2015holistically,kokkinos2015pushing} and biological data \cite{lee2017superhuman,schmidt2018cell,meirovitch2016multi,ciresan2012deep}.
 In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:
@@
 Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters.
-The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical HAC linkage criteria, e.g.
+The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical linkage criteria, e.g.
 average linkage \cite{liu2018affinity,lee2017superhuman}, median \cite{funke2018large} or a linkage learned by a random forest classifier \cite{nunez2013machine,knowles2016rhoananet}.
@@
 Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2019mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
-\TODO{Mention spectral methods}
+Another line of reseatch is given by spectral clustering methods that, on the other hand, require the user to specify the number of clusters in advance.
+Recently, some of these methods have been generalized to graphs with signed weights \cite{Cucuringu2019SPONGEAG,chiang2012scalable,kunegis2010spectral}, whereas others let the user specify must-link and cannot-link constraints between clusters \cite{rangapuram2012constrained,wang2014constrained,cucuringu2016simple}.
 

### 2019-11-11 chapters/5_experiments_cityscapes.tex
Small changes spectral clustering

@@
 Results on the \emph{test} set are summarized in Table \ref{tab:results_cityscapes_test}.
-The best scores are achieved by Panoptic-DeepLab \cite{cheng2019panopticdeeplab} that proposes a more powerful CNN model and then simply predict instance centers.
+The best scores are achieved by Panoptic-DeepLab \cite{cheng2019panopticdeeplab} that proposes a more powerful CNN model to regress the centers of hte instances.
 The second best \emph{proposal-free} method is SSAP \cite{Gao_2019_ICCV}, which predicts long-range instance-affinities similarly to GMIS \cite{liu2018affinity}, but trains the model with extra side-losses.
-\algname{} with \emph{Average} linkage also achieves competitive results and outperforms the previous agglomeration method proposed in \cite{liu2018affinity}.
+\algname{} with \emph{Average} linkage also achieves competitive results and outperforms the previous agglomeration method proposed in GMIS \cite{liu2018affinity}.
 Similarly to the experiments on neuron segmentation, results on the \emph{val} set (see Table \ref{tab:results_cityscapes_val} and Fig.

### 2019-11-11 chapters/5_experiments_compare_rules.tex
Small changes spectral clustering

@@
 % !TEX root = ../agglo_clust_review.tex
+
+\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
+\begin{figure*}
+\centering
+    \begin{subfigure}[t]{0.46 \textwidth}
+        \centering
+        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_0.pdf}
+    \end{subfigure} \hfill
+    \begin{subfigure}[t]{0.46 \textwidth}
+        \centering
+        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
+    \end{subfigure}
+
+        \begin{subfigure}[t]{0.46 \textwidth}
+        \centering
+        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
+        \caption{No long-range predictions: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
+    \end{subfigure} \hfill
+    \begin{subfigure}[t]{0.46 \textwidth}
+        \centering
+        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
+        \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
+    \end{subfigure}
+\caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust.
+Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions.
+Solid lines represent median values over 30 experiments.
+Values between the 25th and the 75th percentile are shown in shaded areas.
+The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details).
+For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph.
+Experiments are performed on a crop of CREMI training sample B.
+}\label{fig:noise_plots}
+\end{figure*}
+\begin{figure*}[t]
+        \centering
+\begin{minipage}[t]{0.31\textwidth}
+    \centering
+    \scriptsize
+        \begin{tabular}[t]{l|c}
+         Method & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
+\textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
+\algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
+\algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
+\algname{} Max. + Constraints & 0.324 \\
+\algname{} Sum \cite{keuper2015efficient} & 0.334 \\
+\algname{} Average + Constraints & 0.563 \\
+THRESH & 1.521 \\ 
+        \end{tabular}
+    \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding.
+All methods use the affinity predictions from our CNN as input.
+Scores are averaged over the three CREMI training datasets.}
+    \label{tab:results_cremi_train}
+\end{minipage}\hfill
+\begin{minipage}[t]{0.3\textwidth}
+    \centering
+    \scriptsize
+        \begin{tabular}[t]{l|c}
+        Method & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
+Our CNN + DTWS + LMC &  0.221\\
+PNI CNN \cite{lee2017superhuman} & 0.228 \\
+\textbf{Our CNN + \algname{} Average} & \textbf{0.241} \\
+MALA CNN + MC \cite{funke2018large} & 0.276 \\
+CRU-Net \cite{zeng2017deepem3d} & 0.566  \\
+LFC \cite{parag2017anisotropic} & 0.616  \\
+        \end{tabular}
+        \vspace*{0.99em}
+    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (November 2019).
+All entries, apart from our using \algname{}, employ superpixel-based post-processing pipelines.}
+    \label{tab:results_cremi_test}
+\end{minipage}\hfill
+\begin{minipage}[t]{0.35\textwidth}
+\centering
+    \scriptsize
+    \vspace*{-1.5em}
+\begin{tabular}[t]{l|cc}
+        \multirow{2}{*}{Method}    & AP  & AP 50\% \\ 
+         & \multicolumn{2}{c}{(higher is better)} \\ \midrule
+           Panoptic-DeepLab \cite{cheng2019panopticdeeplab} & 34.6 & 57.3 \\
+           UPSNet \cite{xiong2019upsnet} $\dagger$ & 33.0 & 59.6 \\
+           SSAP \cite{Gao_2019_ICCV} & 32.7 & 51.8 \\
+           AdaptIS \cite{sofiiuk2019adaptis} & 32.5 & 52.5 \\
+           PANet \cite{liu2018path} $\dagger$ & 31.8 & 57.1 \\
+           \textbf{GMIS Model \cite{liu2018affinity} + \algname{} Average} & \textbf{28.3} & \textbf{47.0} \\ 
+           JOSECB \cite{neven2019instance} & 27.7 & 50.9 \\
+           \textbf{GMIS} \cite{liu2018affinity} & \textbf{27.3} & \textbf{45.6} \\
+           Mask R-CNN \cite{he2017mask} $\dagger$ & 26.2 & 49.9 \\
+           SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
+           % DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
+           % DWT \cite{bai2017deep} & 19.4 & 35.3 \\
+           % InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
+        \end{tabular}
+    % \caption{CityScapes \emph{test} set}
+    % \vspace*{0.6em}
+    \captionof{table}{Results on CityScapes test.
+Methods marked with~$\dagger$ are \emph{proposal-based}.
+Only methods that do not use external training data (e.g.
+MS COCO) are shown.}\label{tab:results_cityscapes}
+    \label{tab:results_cityscapes_test}
+\end{minipage}
+\end{figure*}
+
+\captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
+\renewcommand*{\thesubtable}{(\alph{subtable})}
+\begin{figure*}[t]
+\begin{minipage}{0.65 \textwidth}
+\centering
+\includegraphics[width=\textwidth]{./figs/cityscapes_compare_6.pdf} % left bottom right top
+\caption{Visual results given by different \algname{} linkage criteria on a crop of a CityScapes image from the \emph{validation} set.}\label{fig:cityscapes}
+\end{minipage}\hfill
+\begin{minipage}{0.3 \textwidth}
+    \centering
+    \small
+        \begin{tabular}[t]{l|cc}
+             Agglomeration method & AP \\ \midrule
+            % PANet \cite{liu2018path} & - & \textbf{36.5} \\
+            % Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
+              \textbf{\algname{} Average}& \textbf{34.3} \\
+              \algname{} Average + Constraints & 33.9 \\
+             MultiStepHAC \cite{liu2018affinity} & 33.0 \\
+              \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
+              \algname{} Sum + Constraints  \cite{levinkov2017comparative} & 31.9  \\
+              \algname{} Sum \cite{keuper2015efficient} & 31.3 \\
+        \end{tabular}
+    \vspace*{0.6em}
+    \captionof{table}{Average Precision scores on CityScapes \emph{val} achieved by the GMIS Model trained in \cite{liu2018affinity} and different graph agglomeration methods.}
+    \label{tab:results_cityscapes_val}
+\end{minipage}
+\end{figure*}
 
@@
 The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth.
-The results submitted to the leaderboard are evaluated using the CREMI score (\url{https://cremi.org/leaderboard/}), based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}.
+The results submitted to the leaderboard are evaluated using the CREMI score (\TODO{Fix link} https://cremi.org/leaderboard/), based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}.
 In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.

### 2019-11-11 chapters/5_experiments_noise.tex
Small changes spectral clustering

--- 2019-06-25 chapters/5_experiments_noise.tex
@@
 Appendix Table \ref{tab:extended_results_cremi} lists the performances and the run-times for all tested \algname{} linkage.
-
-\begin{figure}[t]
-        \centering
-\begin{minipage}[t]{0.56\textwidth}
-    \centering
-    \scriptsize
-        \begin{tabular}[t]{l|c}
-          & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
-\textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
-\algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
-\algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
-\algname{} Max. + Constraints & 0.324 \\
-\algname{} Sum \cite{keuper2015efficient} & 0.334 \\
-\algname{} Average + Constraints & 0.563 \\
-THRESH & 1.521 \\ 
-        \end{tabular}
-    \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding.
-All methods use the affinity predictions from our CNN as input.
-Scores are averages over the three CREMI training datasets.}
-    \label{tab:results_cremi_train}
-\end{minipage}\hfill
-\begin{minipage}[t]{0.4\textwidth}
-    \centering
-    \scriptsize
-        \begin{tabular}[t]{l|c}
-         & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
-Our CNN + DTWS + LMC &  0.221\\
-PNI CNN \cite{lee2017superhuman} & 0.228 \\
-\textbf{Our CNN + \algname{} Average} & \textbf{0.241} \\
-MALA CNN + MC \cite{funke2018large} & 0.276 \\
-CRU-Net \cite{zeng2017deepem3d} & 0.566  \\
-LFC \cite{parag2017anisotropic} & 0.616  \\
-        \end{tabular}
-        \vspace*{1em}
-    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019). The scores are averages of the three test datasets.}
-    \label{tab:results_cremi_test}
-\end{minipage}
-\end{figure}
-\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
-\begin{figure}
-\centering
-    \begin{subfigure}[t]{0.49 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_0.pdf}
-    \end{subfigure} \hfill
-    \begin{subfigure}[t]{0.49 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
-    \end{subfigure}
-
-        \begin{subfigure}[t]{0.49 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
-        \caption{No long-range predictions: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
-    \end{subfigure} \hfill
-    \begin{subfigure}[t]{0.49 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
-        \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
-    \end{subfigure}
-\caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust.
-Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions.
-Solid lines represent median values over 30 experiments.
-Values between the 25th and the 75th percentile are shown in shaded areas.
-The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details).
-For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph.
-}\label{fig:noise_plots}
-\end{figure}
 

### 2019-11-11 chapters/5_experiments_spectral.tex
Small changes spectral clustering

@@
 
-\section{Comparison with spectral clustering} 
+\section{Comparison with spectral clustering} \label{sec:spectral_clust}
 In this section we compare \algname{} to spectral clustering methods for signed graphs both on synthetic graphs and real ones from neuron segmentation.
-These methods \cite{Cucuringu2019SPONGEAG,chiang2012scalable,kunegis2010spectral} require the user to specify the number of clusters in advance, in contrast to our proposed agglomeration method that determines the cluster number based on the signed weights of the graph.
+These methods require the user to specify the number of clusters in advance, in contrast to our proposed agglomeration method that determines the cluster number based on the signed weights of the graph.
 In the following comparison, we make these baselines as strong as possible by specifying the true number of clusters for the spectral methods.
@@
         \includegraphics[width=0.45\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf}
-        \caption{Experiments on SSBM synthetic graphs \TODO{Update}}
+        \caption{Performances of \algname{} compared to spectral clustering methods on SSBM synthetic graphs.}
     \label{fig:SSBM_spectral_experiments}
@@
 \centering
+\footnotesize
 \begin{tabular}{l|c}
@@
         \end{tabular}
-    \caption{Experiments on a tiny crop of the CREMI dataset, training sample B \TODO{Update}}
+    \caption{\algname{} compared to spectral clustering methods on a small crop of the CREMI dataset (sample B).}
     \label{tab:cremi_spectral_experiments}

### 2019-11-12 chapters/2_rel_work.tex
Minor changes

@@
 Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}. 
-Other recent successful methods simply let the model predict the relative coordinates of the instance center \cite{neven2019instance,cheng2019panopticdeeplab}; in \cite{sofiiuk2019adaptis}, given a point $(x,y)$ in the image, the model generates the mask of the instance located at $(x,y)$.
+Other recent successful methods simply let the model predict the relative coordinates of the instance center \cite{neven2019instance,cheng2019panopticdeeplab} or, given a point $(x,y)$ in the image, the model generates the mask of the instance located at $(x,y)$ \cite{sofiiuk2019adaptis}.
 

### 2019-11-12 chapters/3_algorithm.tex
Add spectral exp; update Cityscapes sec. and App.
Minor changes

@@
 
-In Appendix \ref{sec:detailed_impl}, we comment on the algorithm's computational complexity $\mathcal{O}(N^2 \log N)$ and present our implementation given by the edge contraction Algorithm \ref{detailed_alg} based on a priority queue.
+In Appendix \ref{sec:detailed_impl}, we comment on the algorithm's computational complexity $\mathcal{O}(N^2 \log N)$ and present our implementation given by the edge contraction Algorithm \ref{detailed_alg} based on a \emph{disjoint set data structure} and a \emph{priority queue}.
 
@@
 The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges.
-We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.
-\TODO{Explain yellow lines}}
+The edge selected at each iteration is highlighted in yellow.
+We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
 \label{fig:algorithm_with_without_CLC}

### 2019-11-12 chapters/2_rel_work.tex
Update related work

@@
 They decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,porzi2019seamless,liu2018path,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}.
-They commonly rely on {Faster-RCNN}~\cite{ren2015faster} and can be trained end-to-end using non-maximum suppression. 
+% They commonly rely on {Faster-RCNN}~\cite{ren2015faster} and can be trained end-to-end using non-maximum suppression. 
 Other methods use instead recurrent models to sequentially generate instances one-by-one \cite{romera2016recurrent,ren2017end}.
@@
 Recently, there has been a growing interest for such  methods that do not involve object detection, since, in certain types of data, object instances cannot be approximated by bounding boxes.
-For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation;
+For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation,
 % SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
-a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
+whereas a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction. 
+% whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
 Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{lee2019learning,fathi2017semantic,newell2017associative,de2017semantic}.
@@
 In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:
-some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while flood-filling networks \cite{januszewski2018high} eliminate superpixels by training a recurrent CNN to perform region growing one region at the time.
+some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while
+flood-filling networks \cite{januszewski2018high} and MaskExtend \cite{meirovitch2016multi} use a CNN to iteratively grow one region/neuron at the time; recently, the work of \cite{meirovitch2019cross} made the process more efficient by employing a combinatorial encoding of the segmentation.
 A structured learning approach was also proposed in \cite{funke2018large,turaga2009maximin}.
 
-\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts.
-Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters.
+\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{arbelaez2011contour,ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts.
+Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; 
+% ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold;
+the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters. 
 The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical linkage criteria, e.g.

### 2019-11-12 chapters/3_algorithm.tex
Update related work

@@
 The algorithm has two variants.
-The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual repulsive interactions (see iterations on toy graphs in block 4 of Fig.
+The first one (option \emph{addCannotLinkConstraints} is \texttt{False}) starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual repulsive interactions (see iterations on toy graphs in block 4 of Fig.
 \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}).
@@
 
-In the second variant, when \texttt{addCannotLinkConstraints=True}, Algorithm \ref{main_alg} also introduces \emph{cannot-link constraints}, which represent mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering.
+In the second variant (option \emph{addCannotLinkConstraints} is \texttt{True}), Algorithm \ref{main_alg} also introduces cannot-link constraints, which represent mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering.
 This variant
@@
         \caption{No constraints}\label{subfig:no_constraints}
-    \end{subfigure} \hfill
+    \end{subfigure} \\\vspace{8pt}
     \begin{subfigure}[t]{0.42 \textwidth}
@@
 \centering
-\includegraphics[width=0.9\textwidth]{./figs/comparison_new.pdf} % left bottom right top
+\includegraphics[width=0.96\textwidth]{./figs/comparison_new.pdf} % left bottom right top
 \caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data.

### 2019-11-12 chapters/5_experiments_compare_rules.tex
Update related work

@@
 The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth.
-The results submitted to the leaderboard are evaluated using the CREMI score (\TODO{Fix link} https://cremi.org/leaderboard/), based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}.
+The results submitted to the leaderboard are evaluated using the CREMI score, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}.
 In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.

### 2019-11-12 chapters/6_conclusions.tex
Update related work

@@
 \section{Conclusion}
+
 We have presented a novel unifying framework for agglomerative clustering of graphs with both positive and negative edge weights and we have shown that several existing clustering algorithms, e.g.

### 2019-11-13 chapters/1_intro.tex
Small typos and changes

@@
 
-In Sec. \ref{sec:spectral_clust}, we also show how \algname{} outperforms spectral clustering methods for signed graphs by testing it on synthetic graphs and neuron segmentation.
+In Sec.
+\ref{sec:spectral_clust}, we also show how \algname{} outperforms spectral clustering methods on the task of neuron segmentation and how on synthetic graphs it achieves similar scores to a recently proposed spectral method for signed graphs.
 

### 2019-11-13 chapters/2_rel_work.tex
Small typos and changes

@@
 Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2019mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
-Another line of reseatch is given by spectral clustering methods that, on the other hand, require the user to specify the number of clusters in advance.
+Another line of research is given by spectral clustering methods that, on the other hand, require the user to specify the number of clusters in advance.
 Recently, some of these methods have been generalized to graphs with signed weights \cite{Cucuringu2019SPONGEAG,chiang2012scalable,kunegis2010spectral}, whereas others let the user specify must-link and cannot-link constraints between clusters \cite{rangapuram2012constrained,wang2014constrained,cucuringu2016simple}.

### 2019-11-13 chapters/5_experiments_cityscapes.tex
Small typos and changes

@@
 Results on the \emph{test} set are summarized in Table \ref{tab:results_cityscapes_test}.
-The best scores are achieved by Panoptic-DeepLab \cite{cheng2019panopticdeeplab} that proposes a more powerful CNN model to regress the centers of hte instances.
+The best scores are achieved by Panoptic-DeepLab \cite{cheng2019panopticdeeplab} that proposes a more powerful CNN model to regress the centers of the instances.
 The second best \emph{proposal-free} method is SSAP \cite{Gao_2019_ICCV}, which predicts long-range instance-affinities similarly to GMIS \cite{liu2018affinity}, but trains the model with extra side-losses.

### 2019-11-13 chapters/5_experiments_spectral.tex
Update related work
Smaller plot for 8 page limit
Small typos and changes

@@
 Median scores, 25th and 75th percentiles over 30 repetitions are shown in Fig.
-\ref{fig:SSBM_spectral_experiments}: GASP achieved comparable scores to the spectral methods.
+\ref{fig:SSBM_spectral_experiments}: GASP achieved comparable scores to SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG}, a recently proposed spectral clustering method.
 The specific design choice of a \emph{sign flipping} noise used in the SSBM experiments turned out to favor GASP with \emph{Sum} linkage that, according to the experiments presented in Sec.
@@
 \centering
-        \includegraphics[width=0.45\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf}
-        \caption{Performances of \algname{} compared to spectral clustering methods on SSBM synthetic graphs.}
+        \includegraphics[width=0.4\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf} % 0.45
+        \caption{Performances of \algname{} compared to spectral clustering methods on SSBM synthetic graphs. \TODO{Fix refs}}
     \label{fig:SSBM_spectral_experiments}

### 2020-02-17 chapters/0_abstract.tex
Last updates before submission

--- 2019-05-23 chapters/0_abstract.tex
@@
 \begin{abstract}
-We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes.
+We propose a new theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes.
 This framework defines GASP, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints.
-We prove the equivalence of existing clustering methods to some of those combinations, and introduce new algorithms for combinations which have not been studied.
-An extensive comparison is performed to evaluate properties of the clustering algorithms in the context of instance segmentation in images, including robustness to noise and efficiency.
-We show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset.
+We prove the equivalence of existing clustering methods to some of those combinations, and introduce new algorithms for combinations which have not been studied before.
+On stochastic block model problems, GASP compares favorably to spectral clustering.
+More importantly, we conduct a systematic comparison of various instantiations of GASP in image instance segmentation problems, in terms of accuracy but also efficiency and robustness to noise.
+We find that one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset.
 \end{abstract}

### 2020-02-17 chapters/1_intro.tex
Update Fig 1
Last updates before submission

--- 2019-11-08 chapters/1_intro.tex
@@
 \section{Introduction}
-In computer vision, the partitioning of weighted graphs has been successfully applied to such tasks as image segmentation, object tracking and pose estimation. 
+In computer vision, the partitioning of weighted graphs has been successfully applied to tasks as diverse as image segmentation, object tracking and pose estimation. 
 Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes.
-These methods are parameter-based and require users to specify the desired numbers of clusters or a termination criterion (e.g.
-spectral clustering or iterated normalized cuts) or even to add a seed for each object  (e.g.
-seeded watershed or random walker).
+These methods require users to specify the desired numbers of clusters (as in spectral clustering) or a termination criterion (e.g.\ in iterated normalized cuts) or even to add a seed for each object  (e.g.\ seeded watershed or random walker).
 
 Other graph clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between nodes.
-The advantage of signed graphs over positive-weighted graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters.
-This can be done optimally by solving the so-called \emph{multicut optimization} or \emph{correlation clustering} problem \cite{kappes2011globally,chopra1991multiway}.
-This problem is NP-hard, but approximate solvers have already been proposed \cite{beier2016efficient}.
-Besides, the general problem of graph partitioning can be solved approximately by greedy agglomerative clustering \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}.
+The advantage of signed graphs over positive-weighted graphs is that balancing attraction and repulsion allows us to obtain a clustering without defining additional parameters.
+A canonical formulation of the signed graph partitioning problem is the \emph{multicut} or \emph{correlation clustering} problem \cite{kappes2011globally,chopra1991multiway}.
+This problem is NP-hard, though many approximate solvers have been proposed \cite{lange2018combinatorial,pape2017solving,beier2016efficient,yarkony2012fast}.
+The general problem of graph partitioning can also be solved approximately by greedy agglomerative clustering \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}.
+Agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter-free and efficient.
+Despite the fact that a variety of these algorithms exist, no overarching study has so far been conducted to compare their robustness and efficiency or to provide guidelines for matching an algorithm to the partitioning problem at hand.
 
-Agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter-free and efficient.
-Despite the fact that there exists a variety of these algorithms, no overarching study has so far been made to compare their robustness and efficiency or to provide guidelines for matching an algorithm to the partitioning problem at hand.
+In this paper, we propose a new theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering on positive-weighted graphs \cite{lance1967general}.
+This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}.
+We then formally prove that some of the combinations correspond to existing clustering algorithms and introduce new algorithms for combinations which have not been explored before.
 
-In this paper, we propose a novel theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering on positive-weighted graphs \cite{lance1967general}.
-This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}.
-We then formally prove that some of the combinations correspond to existing clustering algorithms and introduce new algorithms for combinations which have not been explored yet.
-
-We evaluate and compare these algorithms on \emph{instance segmentation} - a computer vision task of assigning each pixel of an image to an object instance. 
-We use a CNN to predict the edge weights of a graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms in our framework (see Fig.
-\ref{fig:intro_figure}).
+We evaluate and compare these algorithms on \emph{instance segmentation} -- a computer vision task of assigning each pixel of an image to an object instance. 
+We use a CNN to predict the edge weights of a graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms in our framework (see Fig.~\ref{fig:intro_figure}).
 
@@
 \centering
-\includegraphics[width=0.9\textwidth]{figs/intro_image_v3.pdf} % left bottom right top
-\caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge.
+\includegraphics[width=\textwidth]{figs/intro_image_v4.pdf} % left bottom right top
+\caption{\algname{} example.
+\textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge.
 \textbf{(2)} Some short- and long-range predictions of our CNN model, where white pixels represent boundary evidence.
@@
 
-With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
-We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework.
-\TODO{Update CS and spectral clustering}
-It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark and represents the best-performing proposal-free method on CityScapes.
+With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we benchmark all algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
+We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms all previously known agglomeration methods expressed in the framework and that
+it achieves competitive performance on CityScapes and the challenging CREMI 2016 segmentation benchmark.
+
+In Sec.~\ref{sec:spectral_clust}, we also show how \algname{} outperforms spectral clustering methods on the task of neuron segmentation and how on synthetic graphs it achieves similar scores to a recently proposed spectral method for signed graphs.
+
 % Our code is available at \url{https://github.com/abailoni/GASP}.

### 2020-02-17 chapters/2_rel_work.tex
Last updates before submission

@@
 Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}. 
-Other recent successful methods simply let the model predict the relative coordinates of the instance center \cite{neven2019instance,cheng2019panopticdeeplab} or, given a point $(x,y)$ in the image, the model generates the mask of the instance located at $(x,y)$ \cite{sofiiuk2019adaptis}.
+Other recent successful methods simply let the model predict the relative coordinates of the instance center \cite{neven2019instance,cheng2019panopticdeeplab} or, given a point $(x,y)$ in the image, they train a model to generate the mask of the instance located at $(x,y)$ \cite{sofiiuk2019adaptis}.
 
@@
 In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:
-some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while
+some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, whereas
 flood-filling networks \cite{januszewski2018high} and MaskExtend \cite{meirovitch2016multi} use a CNN to iteratively grow one region/neuron at the time; recently, the work of \cite{meirovitch2019cross} made the process more efficient by employing a combinatorial encoding of the segmentation.

### 2020-02-17 chapters/3_algorithm.tex
Small typos and changes
Last updates before submission

@@
 The algorithm has two variants.
-The first one (option \emph{addCannotLinkConstraints} is \texttt{False}) starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual repulsive interactions (see iterations on toy graphs in block 4 of Fig.
-\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}).
+The first one (option \emph{addCannotLinkConstraints} is \texttt{False}) starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual repulsive interactions (see iterations on toy graphs in block 4 of Fig.\ \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}).
 After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.
@@
 This variant
-selects the pair of clusters with the highest absolute interaction $|\interact(S_u, S_v)|$, so that the most attractive and the most repulsive pairs are analyzed first (see example in Fig.
-\ref{subfig:with_constraints}).
+selects the pair of clusters with the highest absolute interaction $|\interact(S_u, S_v)|$, so that the most attractive and the most repulsive pairs are analyzed first (see example in Fig.\ \ref{subfig:with_constraints}).
 If the interaction is repulsive, then the two clusters are constrained and its members can never merge in subsequent steps.
@@
   % \small
-      \State Init. clustering $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$
-      \State Init. interactions between clusters with $\cost_e = w^+_e - w^-_e$
+      \State Initial clustering: $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$
+      \State Initialize interactions between clusters with $\cost_e = w^+_e - w^-_e$
       \Repeat
@@
         \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ \textbf{not} constrained\big]}
-          \State Merge cluster $S_u$ with $S_v$.
-          \State Update interactions \& constraints with neighboring clusters.
+          \State Merge cluster $S_u$ with $S_v$
+          \State Update interactions \& constraints with neighboring clusters
         \ElsIf{{\color{blue}addCannotLinkConstr} \textbf{and}  \big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big]}
@@
 
-Our main contribution is the generalized algorithm for signed graph partitioning, short GASP, that encompasses several known and novel agglomerative algorithms on display in Table \ref{tab:linkage-criteria}.
+Our main contribution is the generalized algorithm for signed graph partitioning, GASP, that encompasses several known and new agglomerative algorithms on display in Table \ref{tab:linkage-criteria}.
 In our framework, individual algorithms are differentiated by the linkage criterion employed. We review them in the following paragraphs.
@@
 \cite{nunez2013machine} for example uses a learned approach where a random forest classifier updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas
-\cite{funke2018large} uses a \emph{quantile} linkage criteria by populating a histogram for each inter-cluster interaction.
+\cite{funke2018large} uses a \emph{quantile} linkage criterion by populating a histogram for each inter-cluster interaction.
 In our experiments, we decided to focus on the linkage criteria listed in Table \ref{tab:linkage-criteria}, since they represent the most common options.
@@
     \end{subtable} 
-    \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning \algname{}, given a linkage criterium, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
+    \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning, \algname{}, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
 The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e.
@@
 \caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data.
-The main \emph{wrongly} segmented regions are highlighted in different warm colors.
+Only the \emph{wrongly} segmented regions are highlighted in different warm colors.
 Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.

### 2020-02-17 chapters/5_experiments_cityscapes.tex
Last updates before submission

@@
 \section{Experiments on CityScapes}\label{sec:cityscapes_exp}
-We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images.
+The segmentation performance of \algname{} is evaluated on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images.
 Several of the current top instance segmentation methods on cityscapes predict affinities, e.g. SSAP \cite{Gao_2019_ICCV} and GMIS \cite{liu2018affinity}. 

### 2020-02-17 chapters/5_experiments_compare_rules.tex
Last updates before submission

@@
 Methods marked with~$\dagger$ are \emph{proposal-based}.
-Only methods that do not use external training data (e.g.
-MS COCO) are shown.}\label{tab:results_cityscapes}
+Only methods that do not use external training data (such as MS COCO) are shown.}\label{tab:results_cityscapes}
     \label{tab:results_cityscapes_test}
@@
 We evaluate all algorithms in the proposed framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available.
-The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth.
+The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which come with publicly available training ground truth.
 The results submitted to the leaderboard are evaluated using the CREMI score, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}.

### 2020-02-17 chapters/5_experiments_noise.tex
Last updates before submission

@@
 Max.).
-The competitive performance of this simple parameter-free algorithm is also reported in Table \ref{tab:results_cremi_test}, showing the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the lifted multicut formulation of \cite{beier2017multicut} that uses several random forests to predict graph edge weights, relying not only on information derived from affinity maps but also raw data and shape information.
+The competitive performance of this simple parameter-free algorithm is also reported in Table \ref{tab:results_cremi_test}, showing the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the lifted multicut formulation of \cite{beier2017multicut} that uses several random forests to predict graph edge weights, relying not only on information derived from affinity maps but also raw data and superpixel shape information.
 Note that the test volumes contain several imaging artifacts that make segmentation particularly challenging and might profit from more robust edge statistics of super-pixel based approaches.
@@
 In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets.
-Appendix Table \ref{tab:extended_results_cremi} lists the performances and the run-times for all tested \algname{} linkage.
+Appendix Table \ref{tab:extended_results_cremi} lists the performances and the run-times for all tested \algname{} linkage criteria.
 
@@
 Appendix \ref{sec:appendix_noise_gen} introduces the type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false positive boundary evidence.
-Fig.
-\ref{fig:noise_plots} summarizes our 12000 noise experiments: we focus on the best performing linkage criteria, i.e.
+Fig.~\ref{fig:noise_plots} summarizes our 12000 noise experiments: we focus on the best performing linkage criteria, i.e.
 \emph{Average}, \emph{Sum} and \emph{Abs Max}, and test them with different amount of noise.
@@
 \textbf{Sum linkage } 
-All our experiments show that \algname{} with \emph{Sum} linkage is the algorithm with the highest tendency to under-cluster and incorrectly merge segments (see Fig.
-\ref{fig:cremi_comparison} for an example).
-This property is related to the empirical observation that a \emph{Sum} statistic tends to grow clusters one after the other, as shown in Fig.
-\ref{fig:intro_figure} by the quite unique agglomeration order of the \emph{Sum} statistic.
+All our experiments show that \algname{} with \emph{Sum} linkage is the algorithm with the highest tendency to under-cluster and incorrectly merge segments (see Fig.\ \ref{fig:cremi_comparison} for an example).
+This property is related to the empirical observation that a \emph{Sum} statistic tends to grow clusters one after the other, as shown in Fig.\ \ref{fig:intro_figure} by the quite unique agglomeration order of the \emph{Sum} statistic.
 An intuitive explanation of this fact is the following: initially, most of the intra-cluster nodes present similar attractive interactions between each others; when the two nodes sharing the most attractive interaction are merged, there is a high chance that they both share an attractive interaction with a common neighboring node, so the new interaction with this common neighbor will be immediately assigned to a high priority in the agglomeration, given by the sum of two high weights; this usually starts a ``chain reaction'', where only a single cluster is agglomerated at the beginning.
-On the other hand, as we also see in Fig.
-\ref{fig:intro_figure}, other linkage criteria like \emph{Average} or \emph{Abs Max} grow clusters of similar sizes in parallel and accumulate in this way much more reliable inter-cluster statistics.
+On the other hand, as we also see in Fig.\ \ref{fig:intro_figure}, other linkage criteria like \emph{Average} or \emph{Abs Max} grow clusters of similar sizes in parallel and accumulate in this way much more reliable inter-cluster statistics.

### 2020-02-17 chapters/5_experiments_spectral.tex
Last updates before submission

@@
 \section{Comparison with spectral clustering} \label{sec:spectral_clust}
-In this section we compare \algname{} to spectral clustering methods for signed graphs both on synthetic graphs and real ones from neuron segmentation.
+In this section we compare \algname{} to spectral clustering (SC) methods for signed graphs both on synthetic graphs and real ones from neuron segmentation.
 These methods require the user to specify the number of clusters in advance, in contrast to our proposed agglomeration method that determines the cluster number based on the signed weights of the graph.
@@
 
-\textbf{Synthetic graphs} - First, we generated synthetic graphs from a signed stochastic block model (SSBM) where the true number of clusters is previously known.
-We used an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N=10^5$ vertices and edge probability $p=0.1$.
+\textbf{Synthetic graphs} -- First, we compare the clustering performance on synthetic graphs generated by a signed stochastic block model (SSBM), where SC performs well.
+In particular, we used an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N=10^5$ vertices and edge probability $p=0.1$.
 Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k=100$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) had Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $0.1$.
 To model noise, we flipped the sign of each edge independently with probability $\eta \in [0, 0.4]$.
-Median scores, 25th and 75th percentiles over 30 repetitions are shown in Fig.
-\ref{fig:SSBM_spectral_experiments}: GASP achieved comparable scores to SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG}, a recently proposed spectral clustering method.
-The specific design choice of a \emph{sign flipping} noise used in the SSBM experiments turned out to favor GASP with \emph{Sum} linkage that, according to the experiments presented in Sec.
-\ref{sec:results}, is the one with the lowest tendency to over-cluster and grows one cluster at the time.
+Median scores, 25th and 75th percentiles over 30 repetitions are shown in Fig.~\ref{fig:SSBM_spectral_experiments}: GASP achieved scores comparable to SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG}, a recently proposed SC method.
+The specific design choice of a \emph{sign flipping} noise used in the SSBM experiments turned out to favor GASP with \emph{Sum} linkage that, according to the experiments presented in Sec.~\ref{sec:results}, is the one with the lowest tendency to over-cluster and grows one cluster at the time.
 
-\textbf{Neuron segmentation} - We then extended the comparison with spectral methods to the task of neuron segmentation.
-Since the spectral methods cannot scale to the full CREMI dataset, we considered a random tiny crop of 10x100x100 voxels resulting in a graph with $10^5$ nodes and~$\sim10^6$ edges.
+\textbf{Neuron segmentation} -- We extended the comparison with spectral methods to the task of neuron segmentation.
+Since SC cannot scale to the full CREMI dataset, we evaluated \algname{} and SC on a smaller $10\times100\times100$ voxels volume resulting in a graph with $10^5$ nodes and~$\sim10^6$ edges.
 Scores are summarized in Table \ref{tab:cremi_spectral_experiments}.
 %suggested by the reviewer that performed best in the recent comparison \cite{Cucuringu2019SPONGEAG}: one based on the Balanced Normalized Cut (BNC) \cite{chiang2012scalable}; another on the symmetrically normalized Signed Laplacian ($L_{sym}$) \cite{kunegis2010spectral}; SPONGE and SPONGE$_{sym}$ algorithms were recently proposed in \cite{Cucuringu2019SPONGEAG}.
-Despite the fact that the true number of GT clusters was given as an input to the spectral methods, GASP significantly outperformed them on neuro-data.
-Spectral methods seem to have more difficulties when the graph is sparse.
+Despite the fact that the true number of ground truth clusters was given as an input to the SC methods, GASP significantly outperformed them on neuro-data.
+SC methods seem to have more difficulties when the graph is sparse.
 Moreover, they did not handle well pixels on the boundaries between segments and tended to cluster them together.
@@
         \includegraphics[width=0.4\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf} % 0.45
-        \caption{Performances of \algname{} compared to spectral clustering methods on SSBM synthetic graphs. \TODO{Fix refs}}
+        \caption{\algname{} performances compared to spectral methods on synthetic graphs. The spectral methods were given the true number of clusters as input, in contrast to \algname{}.}
     \label{fig:SSBM_spectral_experiments}

### 2020-02-17 chapters/6_conclusions.tex
Last updates before submission

@@
 
-We have presented a novel unifying framework for agglomerative clustering of graphs with both positive and negative edge weights and we have shown that several existing clustering algorithms, e.g.
-the Mutex Watershed \cite{wolf2018mutex}, can be reformulated as special cases of one underlying agglomerative algorithm.
+We have presented a novel unifying framework for agglomerative clustering of graphs with both positive and negative edge weights; and we have shown that several existing clustering algorithms, e.g.
+the Mutex Watershed, can be reformulated as special cases of one underlying agglomerative algorithm.
 This framework also allowed us to introduce new algorithms, one of which, based on an \emph{Average} linkage criterion, outperformed all the others: it proved to be a simple and remarkably robust approach to process short- and long-range predictions of a CNN applied to an instance segmentation task.
-On biological images, this simple average agglomeration algorithm can represent a valuable choice for user who is not willing to spend much time tuning complex task-dependent pipelines based on superpixels.
-In future work we plan to explore common theoretical properties of the algorithms included in the framework.
+On biological images, this simple average agglomeration algorithm can represent a valuable choice for a user who is not willing to spend much time tuning complex task-dependent pipelines based on superpixels.
+% In future work, we plan to explore common theoretical properties of the algorithms included in the framework.

### 2020-03-10 chapters/3_algorithm.tex
Update to ECCV template

@@
 
-\begin{figure}
+\begin{figure}[t]
 \centering
-        \begin{subfigure}[t]{0.42 \textwidth}
+        \begin{subfigure}[t]{0.46 \textwidth}
         \centering
@@
         \caption{No constraints}\label{subfig:no_constraints}
-    \end{subfigure} \\\vspace{8pt}
-    \begin{subfigure}[t]{0.42 \textwidth}
+    \end{subfigure} \hfill \vspace{8pt}
+    \begin{subfigure}[t]{0.46 \textwidth}
         \centering
@@
 
-% \begin{table*}[t]
-%     % \centering
-%     \scriptsize
-%     \begin{subtable}[t!]{0.6\textwidth}\centering
-%         \begin{tabular}{r  l | c | c  c}
-%             \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
-%             \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\
+\begin{table*}[t]
+    % \centering
+    \scriptsize
+    \begin{subtable}[t!]{\textwidth}\centering
+        \begin{tabular}{R{5em}  l | M{10em} | M{8em}  M{8em}}
+            \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria}\\ $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned} \\\textbf{Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
+            \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No \\Constraints}} & \thead{With\\ Constraints} \\
 
-%             \midrule
-%              Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
+            \midrule
+             Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
 Aggl.
@@
 
-%              \makecell[r]{Abs. Max:} & 
-%             $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
-%                & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} \\
-%              \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier.
+             \makecell[r]{Abs. Max:} & 
+            $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
+               & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} \\
+             \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier.
 Aggl.
@@
 
-%             Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
+            Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
 
-%             Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}
-
-%         \end{tabular}
-%     \end{subtable} 
-%     \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning \algname{}, given a linkage criterium, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
+            Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}
+        \end{tabular}
+    \end{subtable} 
+    \vspace{1em}
+    \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning, \algname{}, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
 The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e.
 $E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
-%     \label{tab:linkage-criteria}
-% \end{table*}
+    \label{tab:linkage-criteria}
+\end{table*}
 
-\begin{table*}[t]
-    \centering
-    \footnotesize
-    \begin{subtable}[t!]{\textwidth}\centering
-        \begin{tabular}{c | c  c  c  c  c}
-        \multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} \\ $\,\,\interact(S_u ,S_v)$}}  & Sum & Absolute Maximum & Average & Maximum & Minimum \\
- & $\displaystyle \sum_{e\in E_{uv}} \cost_e$  & $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$ & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big| $ &  $\displaystyle \max_{e\in E_{uv}} \cost_e$ & $\displaystyle \min_{e\in E_{uv}} \cost_e$ \\ \midrule
+% \begin{table*}[t]
+%     \centering
+%     \footnotesize
+%     \begin{subtable}[t!]{\textwidth}\centering
+%         \begin{tabular}{c | c  c  c  c  c}
+%         \multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} \\ $\,\,\interact(S_u ,S_v)$}}  & Sum & Absolute Maximum & Average & Maximum & Minimum \\
+%  & $\displaystyle \sum_{e\in E_{uv}} \cost_e$  & $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$ & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big| $ &  $\displaystyle \max_{e\in E_{uv}} \cost_e$ & $\displaystyle \min_{e\in E_{uv}} \cost_e$ \\ \midrule
 
-            \thead{\textbf{Unsigned Graphs}} & \thead{Sum Linkage\\Hier.
+%             \thead{\textbf{Unsigned Graphs}} & \thead{Sum Linkage\\Hier.
 Aggl.
@@
 Clust.} \\
-            \thead{\textbf{Signed Graphs} \\\textbf{Without Constraints}} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
-            \thead{\textbf{Signed Graphs} \\\textbf{With Constraints}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
-            % \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
-            % \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\ \midrule
+%             \thead{\textbf{Signed Graphs} \\\textbf{Without Constraints}} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
+%             \thead{\textbf{Signed Graphs} \\\textbf{With Constraints}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
+%             % \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
+%             % \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\ \midrule
 
-            %  Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
+%             %  Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
 Aggl.
@@
 
-            %  \makecell[r]{Abs. Max:} & 
-            % $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
-            %    & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} \\
+%             %  \makecell[r]{Abs. Max:} & 
+%             % $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
+%             %    & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} \\
 
-            %  \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier.
+%             %  \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier.
 Aggl.
@@
 
-            % Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
+%             % Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
 
-            % Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}
+%             % Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}
 
-        \end{tabular}
-    \end{subtable} 
-    \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning, \algname{}, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
+%         \end{tabular}
+%     \end{subtable} 
+%     % \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning, \algname{}, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
 The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e.
 $E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
-    \label{tab:linkage-criteria}
-\end{table*}
+%     % \label{tab:linkage-criteria}
+% \end{table*}
 
@@
 \centering
-\includegraphics[width=0.96\textwidth]{./figs/comparison_new.pdf} % left bottom right top
+\includegraphics[width=\textwidth]{./figs/comparison_new.pdf} % left bottom right top
 \caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data.

### 2020-03-10 chapters/5_experiments_cityscapes.tex
Update to ECCV template

@@
 Table \ref{tab:extended_results_cityscapes_val} in Appendix includes the scores of all other tested \algname{} algorithms.
+
+% \captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
+\renewcommand*{\thesubtable}{(\alph{subtable})}
+\begin{figure}[t]
+\centering
+\begin{minipage}[t]{0.48 \textwidth}
+\vspace{0pt}
+\centering
+\small
+\begin{tabular}[t]{l|cc}
+     Agglomeration method & AP \\ \midrule
+    % PANet \cite{liu2018path} & - & \textbf{36.5} \\
+    % Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
+      \textbf{\algname{} Average}& \textbf{34.3} \\
+      \algname{} Average + Constraints & 33.9 \\
+     MultiStepHAC \cite{liu2018affinity} & 33.0 \\
+      \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
+      \algname{} Sum + Constraints  \cite{levinkov2017comparative} & 31.9  \\
+      \algname{} Sum \cite{keuper2015efficient} & 31.3 
+\end{tabular}
+\vspace*{1.5em}
+\captionof{table}{Average Precision scores on CityScapes \emph{val} achieved by the GMIS Model trained in \cite{liu2018affinity} and different graph agglomeration methods.}
+\label{tab:results_cityscapes_val}
+\end{minipage}\hfill
+\begin{minipage}[t]{0.49\textwidth}
+% \centering
+\scriptsize
+\begin{tabular}[t]{l|cc}
+    \multirow{2}{*}{Method}    & AP  & AP 50\% \\ 
+     & \multicolumn{2}{c}{(higher is better)} \\ \midrule
+       Panoptic-DeepLab \cite{cheng2019panopticdeeplab} & 34.6 & 57.3 \\
+       UPSNet \cite{xiong2019upsnet} $\dagger$ & 33.0 & 59.6 \\
+       SSAP \cite{Gao_2019_ICCV} & 32.7 & 51.8 \\
+       AdaptIS \cite{sofiiuk2019adaptis} & 32.5 & 52.5 \\
+       PANet \cite{liu2018path} $\dagger$ & 31.8 & 57.1 \\
+       \textbf{GMIS\cite{liu2018affinity}+\algname{}Average} & \textbf{28.3} & \textbf{47.0} \\ 
+       JOSECB \cite{neven2019instance} & 27.7 & 50.9 \\
+       \textbf{GMIS} \cite{liu2018affinity} & \textbf{27.3} & \textbf{45.6} \\
+       Mask R-CNN \cite{he2017mask} $\dagger$ & 26.2 & 49.9 \\
+       SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
+       % DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
+       % DWT \cite{bai2017deep} & 19.4 & 35.3 \\
+       % InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
+    \end{tabular}
+% \caption{CityScapes \emph{test} set}
+% \vspace*{0.6em}
+\captionof{table}{Results on CityScapes test.
+Methods marked with~$\dagger$ are \emph{proposal-based}.
+Only methods that do not use external training data (such as MS COCO) are shown.}\label{tab:results_cityscapes}
+\label{tab:results_cityscapes_test}
+\end{minipage}
+\end{figure}
+\begin{figure}[t]
+\centering
+\begin{minipage}{\textwidth}
+\centering
+\includegraphics[width=\textwidth]{./figs/cityscapes_compare_6.pdf} % left bottom right top
+\caption{Visual results given by different \algname{} linkage criteria on a crop of a CityScapes image from the \emph{validation} set.}\label{fig:cityscapes}
+\end{minipage}
+\end{figure}

### 2020-03-10 chapters/5_experiments_compare_rules.tex
Update to ECCV template

@@
 \captionsetup[subfigure]{justification=centering, singlelinecheck=off}
-\begin{figure*}
+\begin{figure*}[t]
 \centering
-    \begin{subfigure}[t]{0.46 \textwidth}
+    \begin{subfigure}[t]{0.49 \textwidth}
         \centering
@@
     \end{subfigure} \hfill
-    \begin{subfigure}[t]{0.46 \textwidth}
+    \begin{subfigure}[t]{0.49 \textwidth}
         \centering
@@
 
-        \begin{subfigure}[t]{0.46 \textwidth}
+        \begin{subfigure}[t]{0.49 \textwidth}
         \centering
         \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
-        \caption{No long-range predictions: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
+        \caption{No long-range predictions: \\$p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
     \end{subfigure} \hfill
-    \begin{subfigure}[t]{0.46 \textwidth}
+    \begin{subfigure}[t]{0.49 \textwidth}
         \centering
@@
         \centering
-\begin{minipage}[t]{0.31\textwidth}
+\begin{minipage}[t]{0.48\textwidth}
     \centering
@@
 \end{minipage}\hfill
-\begin{minipage}[t]{0.3\textwidth}
+\begin{minipage}[t]{0.48\textwidth}
     \centering
@@
         \vspace*{0.99em}
-    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (November 2019).
+    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (March 2020).
 All entries, apart from our using \algname{}, employ superpixel-based post-processing pipelines.}
     \label{tab:results_cremi_test}
-\end{minipage}\hfill
-\begin{minipage}[t]{0.35\textwidth}
-\centering
-    \scriptsize
-    \vspace*{-1.5em}
-\begin{tabular}[t]{l|cc}
-        \multirow{2}{*}{Method}    & AP  & AP 50\% \\ 
-         & \multicolumn{2}{c}{(higher is better)} \\ \midrule
-           Panoptic-DeepLab \cite{cheng2019panopticdeeplab} & 34.6 & 57.3 \\
-           UPSNet \cite{xiong2019upsnet} $\dagger$ & 33.0 & 59.6 \\
-           SSAP \cite{Gao_2019_ICCV} & 32.7 & 51.8 \\
-           AdaptIS \cite{sofiiuk2019adaptis} & 32.5 & 52.5 \\
-           PANet \cite{liu2018path} $\dagger$ & 31.8 & 57.1 \\
-           \textbf{GMIS Model \cite{liu2018affinity} + \algname{} Average} & \textbf{28.3} & \textbf{47.0} \\ 
-           JOSECB \cite{neven2019instance} & 27.7 & 50.9 \\
-           \textbf{GMIS} \cite{liu2018affinity} & \textbf{27.3} & \textbf{45.6} \\
-           Mask R-CNN \cite{he2017mask} $\dagger$ & 26.2 & 49.9 \\
-           SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
-           % DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
-           % DWT \cite{bai2017deep} & 19.4 & 35.3 \\
-           % InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
-        \end{tabular}
-    % \caption{CityScapes \emph{test} set}
-    % \vspace*{0.6em}
-    \captionof{table}{Results on CityScapes test.
-Methods marked with~$\dagger$ are \emph{proposal-based}.
-Only methods that do not use external training data (such as MS COCO) are shown.}\label{tab:results_cityscapes}
-    \label{tab:results_cityscapes_test}
-\end{minipage}
-\end{figure*}
-
-\captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
-\renewcommand*{\thesubtable}{(\alph{subtable})}
-\begin{figure*}[t]
-\begin{minipage}{0.65 \textwidth}
-\centering
-\includegraphics[width=\textwidth]{./figs/cityscapes_compare_6.pdf} % left bottom right top
-\caption{Visual results given by different \algname{} linkage criteria on a crop of a CityScapes image from the \emph{validation} set.}\label{fig:cityscapes}
-\end{minipage}\hfill
-\begin{minipage}{0.3 \textwidth}
-    \centering
-    \small
-        \begin{tabular}[t]{l|cc}
-             Agglomeration method & AP \\ \midrule
-            % PANet \cite{liu2018path} & - & \textbf{36.5} \\
-            % Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
-              \textbf{\algname{} Average}& \textbf{34.3} \\
-              \algname{} Average + Constraints & 33.9 \\
-             MultiStepHAC \cite{liu2018affinity} & 33.0 \\
-              \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
-              \algname{} Sum + Constraints  \cite{levinkov2017comparative} & 31.9  \\
-              \algname{} Sum \cite{keuper2015efficient} & 31.3 \\
-        \end{tabular}
-    \vspace*{0.6em}
-    \captionof{table}{Average Precision scores on CityScapes \emph{val} achieved by the GMIS Model trained in \cite{liu2018affinity} and different graph agglomeration methods.}
-    \label{tab:results_cityscapes_val}
 \end{minipage}

### 2020-03-10 chapters/5_experiments_noise.tex
Update to ECCV template

@@
 In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets.
-Appendix Table \ref{tab:extended_results_cremi} lists the performances and the run-times for all tested \algname{} linkage criteria.
+Appendix Table \ref{tab:extended_results_cremi} lists the performances and the run-times for all tested \algname{} linkage criteria.\\
 
@@
 Thus, we perform a set of simulations without adding long-range connections to the grid-graph and another set where we introduce them with a 10\% probability\footnote{We also performed experiments adding all the long-range predictions given by the CNN model, but we did not note major differences when using only 10\% of them.
-Adding this fraction is usually sufficient to improve the scores.}.
+Adding this fraction is usually sufficient to improve the scores.}.\\
 
@@
 On the other hand, it is not a surprise that the \emph{Abs Max} statistic proposed by \cite{wolf2018mutex} is less robust to noise than the \emph{Average} linkage, but, as we show in the Appendix Table \ref{tab:extended_results_cremi}, \emph{Abs Max} represents a valid and considerably faster option.
-Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights, then \algname{} with cannot-link constraints shows a clear tendency to over-cluster.
+Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights, then \algname{} with cannot-link constraints shows a clear tendency to over-cluster. \\
 

### 2020-03-10 chapters/5_experiments_spectral.tex
Update to ECCV template

@@
 
+\begin{figure}[t]
+\centering
+\begin{minipage}[t]{\textwidth}
+\vspace{0pt}
+\centering
+% \footnotesize
+\begin{tabular}[t]{L{29em} M{7em}}
+           Method & Rand-Score \\ \midrule
+           \textbf{GASP Average} & \textbf{0.8966} \\
+GASP Sum & 0.8965 \\
+GASP Abs Max & 0.8932 \\
+SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG} & 0.5839\\
+$L_{sym}$ \cite{kunegis2010spectral} & 0.1931 \\
+SPONGE \cite{Cucuringu2019SPONGEAG} & 0.0789 \\
+BNC \cite{chiang2012scalable} & 0.0074 \\
+        \end{tabular}
+    \captionof{table}{\algname{} compared to spectral clustering methods on a small crop of the CREMI dataset (sample B).}
+    \label{tab:cremi_spectral_experiments}
+\end{minipage}\\\vspace{2em}
+\begin{minipage}[t]{\textwidth}
+\vspace{0pt}
+\centering
+        \includegraphics[width=0.8\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf} % 0.45
+        \caption{\algname{} performances compared to spectral methods on synthetic graphs. The spectral methods were given the true number of clusters as input, in contrast to \algname{}.}
+    \label{fig:SSBM_spectral_experiments}
+\end{minipage}
+\end{figure}
+
 \section{Comparison with spectral clustering} \label{sec:spectral_clust}
@@
 Increasing $k$ did not improve their scores either.
-
-\begin{figure}
-\centering
-        \includegraphics[width=0.4\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf} % 0.45
-        \caption{\algname{} performances compared to spectral methods on synthetic graphs. The spectral methods were given the true number of clusters as input, in contrast to \algname{}.}
-    \label{fig:SSBM_spectral_experiments}
-\end{figure}
-\begin{table}
-\centering
-\footnotesize
-\begin{tabular}{l|c}
-           Method & Rand-Score \\ \midrule
-           \textbf{GASP Average} & \textbf{0.8966} \\
-GASP Sum & 0.8965 \\
-GASP Abs Max & 0.8932 \\
-SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG} & 0.5839\\
-$L_{sym}$ \cite{kunegis2010spectral} & 0.1931 \\
-SPONGE \cite{Cucuringu2019SPONGEAG} & 0.0789 \\
-BNC \cite{chiang2012scalable} & 0.0074 \\
-        \end{tabular}
-    \caption{\algname{} compared to spectral clustering methods on a small crop of the CREMI dataset (sample B).}
-    \label{tab:cremi_spectral_experiments}
-\end{table}

### 2020-03-10 chapters/supplementary.tex
Update supplementary

@@
 
-\begin{figure*}
-        \centering
-\begin{minipage}{0.49\textwidth}
-\centering
-        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
-    \end{minipage} \hfill
-\begin{minipage}[T]{0.48\textwidth}
-    \centering
-    \small
-                \begin{tabular}[b]{r | l }
-            \toprule
-            Linkage criteria & Update rule $f$ \\        
-            \midrule
-            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} \\ 
-            \makecell[r]{Absolute \\Maximum:} & \thead[l]{
-            $
-            f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
-            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
-            \tilde{\cost}_2 & \text{otherwise}
-             \end{cases} 
-            $}
-               \\ 
-            \makecell[r]{Average:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                 \\ 
-            Maximum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} \\
-            Minimum:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} 
-        \end{tabular}
-\end{minipage}
-\caption{ 
-\textbf{Left:} Example of edge contraction.
-First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars).
-Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$.
-In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$.
-In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from the edge contraction are replaced by a single edge with updated interaction.
-\textbf{Right:} The table lists the update rules $f(\tilde{\cost}_1, \tilde{\cost}_2)$ associated to the linkage criteria of Table \ref{tab:linkage-criteria} and that are used to efficiently update the interactions between clusters.}
-\label{fig:edge_contraction_and_contr_graph}  
-\end{figure*}
-
 \section{Supplementary material}
@@
 In Fig.
-\ref{fig:edge_contraction_and_contr_graph} we show an example of edge contraction and we list the update rules associated to the linkage criteria we introduced in Table \ref{tab:linkage-criteria}.
+\ref{fig:edge_contraction_and_contr_graph} we show an example of edge contraction and in Table \ref{tab:linkage_criteria_explicit} we list the update rules associated to the linkage criteria we introduced in Table \ref{tab:linkage-criteria}.
 
@@
 %\TODO{Empirical complexity plot?}
+\begin{figure}[H]
+        \centering
+        \includegraphics[width=0.6\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
+    \centering
+    \caption{Example of edge contraction.
+First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars).
+Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$.
+In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$.
+In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from the edge contraction are replaced by a single edge with updated interaction.}\label{fig:edge_contraction_and_contr_graph}
+\end{figure}
+\begin{table}[H]
+\centering
+    \small
+    \vspace{-2em}
+\begin{tabular}[t]{r | l }
+            \toprule
+            Linkage criteria & Update rule $f$ \\        
+            \midrule
+            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} \\ 
+            \makecell[r]{Absolute \\Maximum:} & \thead[l]{
+            $
+            f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
+            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
+            \tilde{\cost}_2 & \text{otherwise}
+             \end{cases} 
+            $}
+               \\ 
+            \makecell[r]{Average:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                 \\ 
+            Maximum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} \\
+            Minimum:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} 
+        \end{tabular}\vspace{1em}
+        \caption{The table lists the update rules $f(\tilde{\cost}_1, \tilde{\cost}_2)$ associated to the linkage criteria of Table \ref{tab:linkage-criteria} and that are used to efficiently update the interactions between clusters.}
+\label{tab:linkage_criteria_explicit}  
+\end{table}
 
-\begin{algorithm*}
+\begin{figure*}[t]
+        \centering
+        \includegraphics[width=0.7\textwidth]{./figs/proof_abs_max_example.pdf} % left bottom right top
+\caption{\algname{} with \emph{AbsMax} linkage: Example representing the only case of edge contraction $e_{uv}$ that would introduce a positive attractive interaction between two constrained clusters.
+Note this can actually never happen with an \emph{AbsMax} linkage, because edge $e_{ut}$ has a lower absolute priority as compared to $e_{uv}$, so clusters $u$ and $t$ cannot have been constrained before $u$ and $v$ are merged.
+}
+\label{fig:abs_max_proof_example}  
+\end{figure*}
+\begin{algorithm*}[t]
   \caption{Mutex Watershed Algorithm proposed by \cite{wolf2018mutex}}
@@
 \begin{prop} \label{prop:equiv_MWS}
-The Mutex Watershed Algorithm \ref{alg:mutex_watershed} (MWS) with empirical $\mathcal{O}(N \log N)$ complexity introduced by \cite{wolf2018mutex} returns the same final clustering given by the \algname{} Algorithm \ref{detailed_alg} with the use of cannot-link constraints and an Absolute Maximum update rule:
+The Mutex Watershed Algorithm \ref{alg:mutex_watershed} (MWS) with empirical \linebreak $\mathcal{O}(N \log N)$ complexity introduced by \cite{wolf2018mutex} returns the same final clustering given by the \algname{} Algorithm \ref{detailed_alg} with the use of cannot-link constraints and an Absolute Maximum update rule:
 \begin{equation}\label{eq:def_abs_max}
@@
 \end{proof}
-
-\begin{figure*}
-        \centering
-
-        \includegraphics[width=0.7\textwidth]{./figs/proof_abs_max_example.pdf} % left bottom right top
-\caption{\algname{} with \emph{AbsMax} linkage: Example representing the only case of edge contraction $e_{uv}$ that would introduce a positive attractive interaction between two constrained clusters.
-Note this can actually never happen with an \emph{AbsMax} linkage, because edge $e_{ut}$ has a lower absolute priority as compared to $e_{uv}$, so clusters $u$ and $t$ cannot have been constrained before $u$ and $v$ are merged.
-}
-\label{fig:abs_max_proof_example}  
-\end{figure*}
 
@@
 \centering
-    \footnotesize
+    \scriptsize
         \begin{tabular}{l|c|c|c|c|c}
@@
 For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
-\begin{figure*}[t]
-\centering
-\begin{minipage}[T]{0.61\textwidth}
+\begin{figure}[t]
 \centering
         \includegraphics[width=\textwidth,trim=0.0in -0.in -0.0in -0.4in,clip]{figs/noisy_affs_comparison.pdf}
-    \captionof{figure}{CNN predictions on a slice of the CREMI neuron segmentation challenge with and without additional noise.
+    \caption{CNN predictions on a slice of the CREMI neuron segmentation challenge with and without additional noise.
 (\textbf{a}) Raw data (\textbf{b}) Original CNN predictions $F(x)$, where blue pixels represent boundary evidence (\textbf{c}) Under-clustering biased version $\tilde{F}_{+}(x;\mathcal{K})$ of the predictions defined in Eq.
@@
     \label{fig:noisy_affs}
-\end{minipage}\hfill
-\begin{minipage}[T]{0.35\textwidth}
+\end{figure}
+\begin{table}
     \centering
-    \small
-    \vspace*{1.6em}
+    % \small
+    \vspace*{0.6em}
         \begin{tabular}{l|c|c}
@@
         \end{tabular}
-    \vspace*{0.5em}
-    \captionof{table}{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set.
+    \vspace*{2em}
+    \caption{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set.
 A bias value $\beta=0$ returns one single cluster.
@@
     \label{tab:extended_results_cityscapes_val}
-\end{minipage}
-\end{figure*}
+\end{table}
 

### 2020-11-06 chapters/supplementary.tex
Small changes to supplementaries

@@
 To alleviate difficulties stemming from misalignment, we use a version of the data that was elastically realigned by the challenge organizers with the method of \cite{saalfeld2012elastic}.
-We train a 3D U-Net \cite{ronneberger2015u, cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
+We train a 3D U-Net \cite{ronneberger2015u,cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
 as described in \cite{lee2017superhuman}. In addition to the standard data augmentation techniques of random rotations, random flips and  elastic deformations, we simulate data artifacts.
@@
     \vspace*{0.6em}
-        \begin{tabular}{l|c|c}
+        \begin{tabular}{l M{7em} M{7em}}
           \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
@@
 A bias value $\beta=0$ returns one single cluster.
-CLC stands for cannot-link constraints}
+CLC stands for cannot-link constraints.}
     \label{tab:extended_results_cityscapes_val}

### 2020-11-06 extra/reviewers_reply.txt
Add extra files and move them to extra folder

---------------------------------------------------------
Reviewer #1
Questions

1. Contributions: Please list three things this paper contributes (e.g., theoretical, methodological, algorithmic, empirical contributions; bridging fields; or providing an important critical analysis). For each contribution, briefly state the level of significance (i.e., how much impact will this work have on researchers and practitioners in the future?). If you cannot think of three things, please explain why. Not all good papers will have three contributions.
(1) Algorithmic / Theoretical: A generic algorithm, special cases of which are a greedy approximate solver for the lifted multicut, and the mutex watershed. The generic formulation exposes variants that have not been considered.
(2) Empirical: A quantitative evaluation of a number of variants of the proposed algorithm on two benchmark datasets for instance segmentation (CREMI and CityScapes). A previously unexplored variant of the generic algorithm performs best (compared to other variants of the same algorithm). 
(3) Assessment of robustness to noise of the above variants. The same previously unexplored variant performs best on CREMI.
2. Detailed comments: Please provide a thorough review of the submission, including its originality, quality, clarity, and significance. Hover over the "?" next to this prompt to see a brief description of these metrics.
--- Summary ---
The authors provide a unified view on instance segmentation algorithms that work via agglomerative clustering in signed or unsigned graphs. In particular, a unified view on an approximate solver of the (lifted) multicut, and the mutex watershed algorithm, is provided. The unified view reveals previously unexplored algorithm variants for signed graphs, namely in terms of commonly used cluster linkage criteria.

The authors present a quantitative evaluation of the variants of their algorithm on two benchmark datasets. A core empirical finding is that a previously unexplored variant (with linkage criterion "average") outperforms the abs max linkage (i.e. the Mutex Watershed) and sum linkage with and without mutex constraints (i.e. GAEC and Greedy Fixation). (This variant is competitive but does not yield an absolute new state of the art on CREMI nor CityScapes).

--- Comments ---
The paper is clearly written, theoretically sound and easy to follow. 
The proposed unification is straightforward, yet is shown to have practical impact by revealing new and better variants of agglomerative clustering of signed graphs for instance segmentation than what had been studied previously.

Typo: line 122: "mutual by" --> mutually
3. Please provide an "overall score" for this submission.
8: Top 50% of accepted NeurIPS papers. A very good submission; a clear accept. I vote and argue for accepting this submission.
4. Please provide a "confidence score" for your assessment of this submission.
5: You are absolutely certain about your assessment. You are very familiar with the related work.
5. Improvements: What would the authors have to do for you to increase your score?
I don't see a straightforward way nor need to improve this manuscript. Most importantly I kindly ask the authors to please stick to their promise to release their code upon paper acceptance. 
An evaluation on the CityScapes test dataset would be interesting but I do not consider it vital for the paper. 
Same holds for an evaluation on the ISBI2012 EM Segmentation Challenge data, albeit this would be interesting as the Mutex Watershed achieved top performance on this data. How does average linkage perform in comparison? Should be easy to check as CNN predictions on ISBI test set were published with [79].

---------------------------------------------------------
Reviewer #2
Questions

1. Contributions: Please list three things this paper contributes (e.g., theoretical, methodological, algorithmic, empirical contributions; bridging fields; or providing an important critical analysis). For each contribution, briefly state the level of significance (i.e., how much impact will this work have on researchers and practitioners in the future?). If you cannot think of three things, please explain why. Not all good papers will have three contributions.
The paper formulates a framework that distinguishes a number of edge contraction algorithms for signed graph partitioning.
The authors show that this generalizes some known greedy algorithms and provides some new ones.
They compare the different algorithms on two instance segmentation problems.
The schema that the authors provide is interesting, but further analysis may be needed to gain more theoretical insight.
The numerical experiments show some benefits of one variant of the algorithm that may support further research.
2. Detailed comments: Please provide a thorough review of the submission, including its originality, quality, clarity, and significance. Hover over the "?" next to this prompt to see a brief description of these metrics.
The paper is well-structured and easy to read. The main contribution is a generalized greedy edge contraction algorithm for signed graph partitioning that depends on the linkage criterion to select the next edge. Since other algorithms have been proposed that can be categorized according to their framework, this seems to be an interesting approach.
My main concern with this framework is that it remains unclear as to which objective function the algorithms are "greedy". In each step the algorithm chooses some edge according to a linkage score. Is this score related to some objective function that is maximized greedily in each step?
If so, then the objective function should be formulated and serve as the distinguishing criterion. Then it would also allow to develop other algorithms based on the same objective function.
Without such an analysis I am unsure about the significance of this categorization.
In the numerical experiments the authors compare their algorithms on neuron segmentation and instance segmentation of street scenes. The empirical evidence suggests that one variant performs better than the other ones, albeit the margins appear fairly small.
The experimental results seem encouraging, but a better theoretical understanding may be needed to properly evaluate the potential of the different proposed linkage criteria.

Minor comments:
line 87: the related works [61,7,82] are not approximation algorithms in an optimization sense
Alg 1, line 9: the or-condition is wrong, it should be "all interactions are repulsive or constrained"
line 122: the sentence contains redundant words
Table 5: wrong heading of first column
3. Please provide an "overall score" for this submission.
6: Marginally above the acceptance threshold. I tend to vote for accepting this submission, but rejecting it would not be that bad.
4. Please provide a "confidence score" for your assessment of this submission.
4: You are confident in your assessment, but not absolutely certain. It is unlikely, but not impossible, that you did not understand some parts of the submission or that you are unfamiliar with some pieces of related work.
5. Improvements: What would the authors have to do for you to increase your score?
The authors should provide a more detailed analysis of their clustering algorithm and the associated optimization problem(s).

---------------------------------------------------------
Reviewer #3
Questions

1. Contributions: Please list three things this paper contributes (e.g., theoretical, methodological, algorithmic, empirical contributions; bridging fields; or providing an important critical analysis). For each contribution, briefly state the level of significance (i.e., how much impact will this work have on researchers and practitioners in the future?). If you cannot think of three things, please explain why. Not all good papers will have three contributions.
The main contribution is of methodological and algorithmic nature - the authors propose a framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering on positive-weighted graphs that explore various linkage criteria and cannot-link constraints.

Empirical contributions: the manuscript contains very thorough numerical experiments on challenging real-world data sets, from the imaging field.
2. Detailed comments: Please provide a thorough review of the submission, including its originality, quality, clarity, and significance. Hover over the "?" next to this prompt to see a brief description of these metrics.
The authors present an algorithm for agglomerative clustering on signed graphs, with a particular focus on image segmentation. 
While the numerical results seem encouraging, the various algorithms proposed seem as a marginal extension of various existing clustering techniques, though some of the combinations of linkage criteria and cannot-link constraints are new.

The authors seem to rather oblivious of the rich literature on constrained clustering, which allows for the user to specify must-link and cannot-link constraints, the latter of which play an important role in the algorithms proposed here.

Rangapuram, Hein, “Constrained 1-spectral clustering” AISTATS 2012
Wang, Qian, Davidson, “On constrained spectral clustering and its applications”. Data Min. Knowl. Discov., 2014
Cucuringu, Koutis, Chawla, Miller, Peng, "Simple and Scalable Constrained Clustering: A Generalized Spectral Method", AISTATS 2016

the last reference of which lead to an extension to the signed clustering setting
Cucuringu, M., Davies, P., Glielmo, A., & Tyagi, H. , "SPONGE: A generalized eigenproblem for clustering signed networks", AISTATS 2019
by incorporating the cannot-link constraints, it seems very much in the spirit of the present submission. Other very relevant references from the signed clustering literature include

Chiang, Kai-Yang, Joyce Jiyoung Whang, and Inderjit S. Dhillon. "Scalable clustering of signed networks using balance normalized cut." Proceedings of the 21st ACM international conference on Information and knowledge management. ACM, 2012.
and 
Kunegis, J., Schmidt, S., Lommatzsch, A., Lerner, J., De Luca, E. W., & Albayrak, S, “Spectral analysis of signed graphs for clustering, prediction and visualization”. In Proceedings of the 2010 SIAM International conference on Data Mining

Essentially, the authors propose a new algorithm for signed clustering, but no comparison has been made with existing state-of-the-art methods from the signed clustering literature. The authors do reference some work in correlation clustering, which is very closely related indeed to signed clustering, but no reference/comparison to existing standard signed clustering algorithms that are used in practice, such as the last 3 references above.

The algorithm does not have any sort of theoretical guarantees, which is somewhat expected/desirable for clustering-related work at this venue.

Comparing the proposed signed clustering algorithm with state-of-the-art could make the paper stronger, and so could the addition of synthetic experiments. In their work, the authors only consider real-world data sets (albeit very challenging) from the image processing literature, but a comparison on synthetic data (some variation of the stochastic block model) where clear ground truth is available, would make the case more convincing.

Given the application to instance segmentation to images, I feel that a venue closer to computer vision/image processing would be more suitable for this line of work. The numerical experiments on real data are very comprehensive.
3. Please provide an "overall score" for this submission.
4: An okay submission, but not good enough; a reject. I vote for rejecting this submission, although I would not be upset if it were accepted.
4. Please provide a "confidence score" for your assessment of this submission.
4: You are confident in your assessment, but not absolutely certain. It is unlikely, but not impossible, that you did not understand some parts of the submission or that you are unfamiliar with some pieces of related work.
5. Improvements: What would the authors have to do for you to increase your score?
Comparison of the proposed signed clustering algorithm with state-of-the-art on syhthetic data/ (hierarhical) stochastic block models.

### 2020-11-06 extra/rebuttal/neurips_2019_author_response.tex
Add extra files and move them to extra folder

\documentclass{article}

\usepackage{neurips_2019_author_response}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\usepackage{lipsum}

\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{mathrsfs}
\usepackage{datetime}

\usepackage{algorithm}% http://ctan.org/pkg/algorithm
\PassOptionsToPackage{noend}{algpseudocode}% comment out if want end's to show
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx

\makeatletter
\newcommand*{\skipnumber}[2][1]{%
   {\renewcommand*{\alglinenumber}[1]{}\State #2}%
   \addtocounter{ALG@line}{-#1}}
\renewcommand{\ALG@beginalgorithmic}{\small}
\makeatother

\usepackage{etoolbox}
% the following line injects our new indent handling code in place of the default spacing
% \patchcmd{\ALG@doentity}{\noindent\hskip\ALG@tlm}{\ALG@printindent}{}{\errmessage{failed to patch}}
% \makeatother
% end vertical rule patch for algorithmicx

\usepackage{tabularx}
\usepackage{lipsum}
\usepackage{makecell}
\renewcommand\theadfont{}
\usepackage{multirow}
\usepackage[labelformat=simple]{subcaption}
\renewcommand\thesubfigure{(\alph{subfigure})}
\usepackage{booktabs}
\usepackage{rotating}
\newcolumntype{?}{!{\vrule width 0.3em}}

\newcommand*{\cost}{w}%
\newcommand*{\interact}{\mathcal{W}}
\newcommand*{\algname}{GASP}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{mathrsfs}
\newcommand{\RED}[1]{#1}

\newcommand\TODO[1]{{\color{red}{TODO: #1}}}
\newcommand\UPDATE[1]{{\color{blue}{#1}}}
\newcommand\SOURCE[1]{{\color{green}{(from: #1)}}}
% \newcommand\CHANGED[2]{{{\color{blue}{#1}}\color{green}{#2}}}

\usepackage[dvipsnames]{xcolor}
\usepackage[shortlabels]{enumitem}

\usepackage{amsthm}
\usepackage{thmtools,thm-restate}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}[section]

\usepackage{authblk}

\usepackage{etoolbox}
% \renewcommand\refname{}
\setlength{\bibsep}{2pt plus 5.4ex}

\begin{document}

\begin{figure}[t]
\captionsetup{font=small}
        \centering
\begin{minipage}[b]{0.38\textwidth}
\centering
        \includegraphics[width=\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./SSBM_experiments.pdf}
        \captionof{figure}{Experiments on SSBM synthetic graphs}
    \label{fig:SSBM_experiments}
\end{minipage}\hfill
\begin{minipage}[b]{0.25\textwidth}
\centering
    \scriptsize
\begin{tabular}{l|c}
           Method & Rand-Score \\ \midrule
           GASP Average & 0.8966 \\
GASP Sum & 0.8965 \\
GASP Abs Max & 0.8932 \\
SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG} & 0.4389\\
$L_{sym}$ \cite{kunegis2010spectral} & 0.1931 \\
SPONGE \cite{Cucuringu2019SPONGEAG} & 0.0789 \\
BNC \cite{chiang2012scalable} & 0.0074 \\
        \end{tabular}
    \captionof{table}{Experiments on CREMI}
    \label{tab:cremi_experiments}
\end{minipage}\hfill
\begin{minipage}[b]{0.30\textwidth}
\centering
    \scriptsize
\begin{tabular}{l|cc}
           Method & AP  & AP 50\% \\ \midrule
           PANet \cite{liu2018path} & \textbf{31.8} & \textbf{57.1} \\
           \textbf{GMIS + \algname{} Avg} & 28.3 & 47.0 \\ 
           GMIS & 27.3 & 45.6 \\
           Mask R-CNN & 26.2 & 49.9 \\
           SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
           DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
           DWS \cite{bai2017deep} & 19.4 & 35.3 \\
           % InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
        \end{tabular}
    \captionof{table}{Scores on CityScapes \emph{test} set}
    \label{tab:cityscapes_test}
\end{minipage}
\end{figure}

We appreciate the very helpful comments by all reviewers and will address their concerns in the final version.

\textbf{Comparison with spectral clustering (R3)}: 
As kindly suggested by Reviewer 3, we include additional experiments comparing GASP with the spectral clustering methods proposed in \cite{Cucuringu2019SPONGEAG,chiang2012scalable,kunegis2010spectral}. 
Similarly to most of spectral clustering approaches, these methods need to previously specify the number $k$ of final clusters. %or use some additional heuristic criterion to determine $k$. 
On the other hand, in our article we focused on algorithms and tasks related to \emph{correlation clustering}, which has the goal of partitioning a signed graph when the true number of clusters is unknown. 
%\UPDATE{Comment from R3: optionally mention fusion-moves comparison for list of algorithms that are actually used in practice...?}
As suggested by R3, we then generated synthetic graphs from a signed stochastic block model (SSBM) where the true number of clusters is previously known. In the experiments, we used an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N=10^5$ vertices and edge probability $p=0.1$. Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k=100$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (\UPDATE{different clusters}) had Gaussian distributed edge weights centered at $\mu=1$ ($\mu=$-$1$) and with standard deviation $0.1$. To model noise, we flipped the sign of each edge independently with probability $\eta$. Results are shown in Fig. \ref{fig:SSBM_experiments}.
At the same time, we would also like to argue that computer vision is currently one of the most important machine learning application domains, so a success on real data from that domain should count no less than success on synthetic / toy data.
Thus, we extended the comparison with spectral methods to the task of neuron segmentation. Since the spectral methods cannot scale to the full CREMI dataset, we considered a random tiny crop of 10x100x100 voxels resulting in a graph with $10^5$ vertices and~$\sim10^6$ edges. Scores are summarized in Table \ref{tab:cremi_experiments}.\\
%suggested by the reviewer that performed best in the recent comparison \cite{Cucuringu2019SPONGEAG}: one based on the Balanced Normalized Cut (BNC) \cite{chiang2012scalable}; another on the symmetrically normalized Signed Laplacian ($L_{sym}$) \cite{kunegis2010spectral}; SPONGE and SPONGE$_{sym}$ algorithms were recently proposed in \cite{Cucuringu2019SPONGEAG}.
We would like to stress that in these experiments we compared GASP with the strongest possible baseline, by giving the true number of GT clusters as an input to the spectral methods. Despite this, GASP significantly outperformed other methods on neuro-data and achieved comparable scores on the SSBM synthetic data. The specific design choice of a \emph{sign flipping} noise used in the SSBM experiments turned out to favor GASP with \emph{Sum} linkage, which is the one with the lowest tendency to over-cluster and tends to grow one cluster at the time. \TODO{More?}
% abs max:  is sensitive to strong outliers
% In general, we think that different design choices for the synthetic SSBM experiments will favor different versions of GASP linkage.
% \UPDATE{We could easily think of alternative toy experiments that favor one linkage or the other}.

\textbf{Results on Cityscapes test (R1 and R2)}: To highlight the competitive and strong performances of GASP, in Table \ref{tab:cityscapes_test} we list the scores achieved on the CityScapes test set, as kindly suggested by R1. GASP with Average linkage outperforms all previously proposed proposal-free methods. The best performing method PANet \cite{liu2018path} is a proposal-based method strongly related to Mask R-CNN.  % \UPDATE{Mention comment from R2? ``albeit the margins appear fairly small''}

\textbf{GASP and objective function (R2)}: We  agree with Reviewer 2 and we also believe that a generalized objective function would give more significance to the framework. Currently, only the \emph{Sum} and the \emph{Abs Max} linkage have been shown to optimize specific objective functions \cite{wolf2019mutex,keuper2015efficient}.  At the same time, to our knowledge, the proposed framework is the first one that highlights a clear and simple connection between several partitioning algorithms for signed graph and hierarchical agglomerative clustering (HAC) of unsigned graphs. \UPDATE{HAC algorithms have been introduced more than 50 years ago \cite{lance1967general}, but only recent work started to better understand its analytical foundation \cite{moseley2017approximation,cohen2019hierarchical,dasgupta2015cost}. We then think that our framework can in principle suggest further connections between the recent findings about HAC and signed graph partitioning}. 
{\tiny
\bibliographystyle{abbrv}
\bibliography{rebuttal}
}

\end{document}

### 2020-11-06 extra/submissions_uploads/arXiv_submission/chapters/0_abstract.tex
Add extra files and move them to extra folder

% !TEX root = ../ms.tex
%%%%%%%%% ABSTRACT
\begin{abstract}
We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes. This framework defines GASP, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints. We prove the equivalence of existing clustering methods to some of those combinations, and introduce new algorithms for combinations which have not been studied. An extensive comparison is performed to evaluate properties of the clustering algorithms in the context of instance segmentation in images, including robustness to noise and efficiency. We show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset. 
\end{abstract}

### 2020-11-06 extra/submissions_uploads/arXiv_submission/chapters/1_intro.tex
Add extra files and move them to extra folder

% !TEX root = ../ms.tex

\section{Introduction}
In computer vision, the partitioning of weighted graphs has been successfully applied to such tasks as image segmentation, object tracking and pose estimation. 
Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes. These methods are parameter-based and require users to specify the desired numbers of clusters or a termination criterion (e.g. spectral clustering or iterated normalized cuts) or even to add a seed for each object  (e.g. seeded watershed or random walker).

Other graph clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between nodes. The advantage of signed graphs over positive-weighted graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters. This can be done optimally by solving the so-called \emph{multicut optimization} or \emph{correlation clustering} problem \cite{kappes2011globally,chopra1991multiway}. This problem is NP-hard, but approximate solvers have already been proposed \cite{beier2016efficient}. Besides, the general problem of graph partitioning can be solved approximately by greedy agglomerative clustering \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}.

Agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter-free and efficient. Despite the fact that there exists a variety of these algorithms, no overarching study has so far been made to compare their robustness and efficiency or to provide guidelines for matching an algorithm to the partitioning problem at hand.

In this paper, we propose a novel theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering on positive-weighted graphs \cite{lance1967general}. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}. 
We then formally prove that some of the combinations correspond to existing clustering algorithms and introduce new algorithms for combinations which have not been explored yet.

We evaluate and compare these algorithms on \emph{instance segmentation} - a computer vision task of assigning each pixel of an image to an object instance. 
We use a CNN to predict the edge weights of a graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms in our framework (see Fig. \ref{fig:intro_figure}).

With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework. It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark and represents the best-performing proposal-free method on CityScapes.
Our code is available at \url{https://github.com/abailoni/GASP}.

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{figs/intro_image_v3.pdf} % left bottom right top
\caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge. \textbf{(2)} Some short- and long-range predictions of our CNN model, where white pixels represent boundary evidence. \textbf{(3)} Outputs of two agglomerative algorithms included in our proposed generalized clustering framework, with \emph{Sum} and \emph{Average} linkage criteria. The final clustering / instance segmentation is shown in 3a, overlaid with the raw image.  The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown/red), or never (black). (\textbf{4}) Some iterations of \algname{} on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions. At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left in the graph.
\label{fig:intro_figure}}
\end{figure}

### 2020-11-06 extra/submissions_uploads/arXiv_submission/chapters/2_rel_work.tex
Add extra files and move them to extra folder

--- 2019-11-13 chapters/2_rel_work.tex
@@
-% !TEX root = ../agglo_clust_review.tex
+% !TEX root = ../ms.tex
 
@@
 \textbf{Proposal-based methods} have been highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}.
-They decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,porzi2019seamless,liu2018path,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}.
-% They commonly rely on {Faster-RCNN}~\cite{ren2015faster} and can be trained end-to-end using non-maximum suppression. 
+They decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,liu2018path,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}.
+They commonly rely on {Faster-RCNN}~\cite{ren2015faster} and can be trained end-to-end using non-maximum suppression.
 Other methods use instead recurrent models to sequentially generate instances one-by-one \cite{romera2016recurrent,ren2017end}.
@@
 Recently, there has been a growing interest for such  methods that do not involve object detection, since, in certain types of data, object instances cannot be approximated by bounding boxes.
-For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation,
-% SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
-whereas a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction. 
-% whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
-Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{lee2019learning,fathi2017semantic,newell2017associative,de2017semantic}.
-% kulikov2018instance
+For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
+a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
+Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,kulikov2018instance}.
 Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}.
-Other recent successful methods simply let the model predict the relative coordinates of the instance center \cite{neven2019instance,cheng2019panopticdeeplab} or, given a point $(x,y)$ in the image, the model generates the mask of the instance located at $(x,y)$ \cite{sofiiuk2019adaptis}.
 
-\textbf{Edge detection} also experienced recent progress thanks to deep learning, both on natural images \cite{Gao_2019_ICCV,liu2018affinity,xie2015holistically,kokkinos2015pushing} and biological data \cite{lee2017superhuman,schmidt2018cell,meirovitch2016multi,ciresan2012deep}.
+\textbf{Edge detection} also experienced recent progress thanks to deep learning, both on natural images \cite{xie2015holistically,kokkinos2015pushing} and biological data \cite{lee2017superhuman,schmidt2018cell,meirovitch2016multi,ciresan2012deep}.
 In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:
-some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while
-flood-filling networks \cite{januszewski2018high} and MaskExtend \cite{meirovitch2016multi} use a CNN to iteratively grow one region/neuron at the time; recently, the work of \cite{meirovitch2019cross} made the process more efficient by employing a combinatorial encoding of the segmentation.
+some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while flood-filling networks \cite{januszewski2018high} eliminate superpixels by training a recurrent CNN to perform region growing one region at the time.
 A structured learning approach was also proposed in \cite{funke2018large,turaga2009maximin}.
 
-\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{arbelaez2011contour,ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts.
-Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; 
-% ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold;
-the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters. 
-The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical linkage criteria, e.g.
+\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts.
+Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters.
+The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical HAC linkage criteria, e.g.
 average linkage \cite{liu2018affinity,lee2017superhuman}, median \cite{funke2018large} or a linkage learned by a random forest classifier \cite{nunez2013machine,knowles2016rhoananet}.
@@
 Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2019mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
-Another line of research is given by spectral clustering methods that, on the other hand, require the user to specify the number of clusters in advance.
-Recently, some of these methods have been generalized to graphs with signed weights \cite{Cucuringu2019SPONGEAG,chiang2012scalable,kunegis2010spectral}, whereas others let the user specify must-link and cannot-link constraints between clusters \cite{rangapuram2012constrained,wang2014constrained,cucuringu2016simple}.
 

### 2020-11-06 extra/submissions_uploads/arXiv_submission/chapters/3_algorithm.tex
Add extra files and move them to extra folder

--- 2019-11-12 chapters/3_algorithm.tex
@@
 
-% \begin{algorithm}[t]
-%   \caption{\algname{}: generalized algorithm for signed graph partitioning}
-%    \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}\texttt{addCannotLinkConstraints}}  \\
-%   \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
-%   \hspace*{\algorithmicindent} 
-%   \begin{algorithmic}[1]
-%       \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$ with each node in its own cluster
-%       \State Initial interactions between nodes given by $\cost_e = w^+_e - w^-_e$
-%       \Repeat
-%         \State Select pair of clusters $S_u,S_v\in\Pi$ with highest absolute interaction $|\interact{}(S_u,S_v)|$
-%         \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ are \textbf{not} constrained\big]}
-%           \State Merge cluster $S_u$ with $S_v$: update interactions and cannot-link constraints with all their neighbors
-%         \ElsIf{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big] \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
-%           \State Add CannotLink Constraint between clusters $S_u$ and $S_v$
-%         \EndIf
-%       \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \big[all adjacent clusters have cannot-link constraints\big]}
-%       \State
-%       \Return $\Pi$
-%   \end{algorithmic}
-%   \label{main_alg}
-% \end{algorithm}
+\begin{figure}
+\centering
+        \begin{subfigure}[t]{0.46 \textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/example_no_constr.pdf}
+        \caption{No constraints}\label{subfig:no_constraints}
+    \end{subfigure} \hfill
+    \begin{subfigure}[t]{0.46 \textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/example_with_constr.pdf}
+        \caption{With cannot-link constraints}\label{subfig:with_constraints}
+    \end{subfigure}
+\caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints.
+The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges.
+We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
+\label{fig:algorithm_with_without_CLC}
+\end{figure}
+\begin{algorithm}[t]
+  \caption{\algname{}: generalized algorithm for signed graph partitioning}
+   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}\texttt{addCannotLinkConstraints}}  \\
+  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
+  \hspace*{\algorithmicindent} 
+  \begin{algorithmic}[1]
+      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$ with each node in its own cluster
+      \State Initial interactions between nodes given by $\cost_e = w^+_e - w^-_e$
+      \Repeat
+        \State Select pair of clusters $S_u,S_v\in\Pi$ with highest absolute interaction $|\interact{}(S_u,S_v)|$
+        \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ are \textbf{not} constrained\big]}
+          \State Merge cluster $S_u$ with $S_v$: update interactions and cannot-link constraints with all their neighbors
+        \ElsIf{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big] \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
+          \State Add CannotLink Constraint between clusters $S_u$ and $S_v$
+        \EndIf
+      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \big[all adjacent clusters have cannot-link constraints\big]}
+      \State
+      \Return $\Pi$
+  \end{algorithmic}
+  \label{main_alg}
+\end{algorithm}
 
@@
 The algorithm has two variants.
-The first one (option \emph{addCannotLinkConstraints} is \texttt{False}) starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual repulsive interactions (see iterations on toy graphs in block 4 of Fig.
+The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual repulsive interactions (see iterations on toy graphs in block 4 of Fig.
 \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}).
@@
 
-In the second variant (option \emph{addCannotLinkConstraints} is \texttt{True}), Algorithm \ref{main_alg} also introduces cannot-link constraints, which represent mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering.
+In the second variant, when \texttt{addCannotLinkConstraints=True}, Algorithm \ref{main_alg} also introduces \emph{cannot-link constraints}, which represent mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering.
 This variant
@@
 
-In Appendix \ref{sec:detailed_impl}, we comment on the algorithm's computational complexity $\mathcal{O}(N^2 \log N)$ and present our implementation given by the edge contraction Algorithm \ref{detailed_alg} based on a \emph{disjoint set data structure} and a \emph{priority queue}.
+In Appendix \ref{sec:detailed_impl}, we comment on the algorithm's computational complexity $\mathcal{O}(N^2 \log N)$ and present our implementation given by the edge contraction Algorithm \ref{detailed_alg} based on a priority queue.
 
-\begin{algorithm}[t]
-  \begin{flushleft}
-  \caption{\algname{}: generalized algorithm for signed graph partitioning}
-   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}addCannotLinkConstraints}  \\
-  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
-  \hspace*{\algorithmicindent} 
-  \begin{algorithmic}[1]
-  \footnotesize
-  % \small
-      \State Init. clustering $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$
-      \State Init. interactions between clusters with $\cost_e = w^+_e - w^-_e$
-      \Repeat
-        \State Get $S_u,S_v\in\Pi$ with highest interaction $|\interact{}(S_u,S_v)|$
-        \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ \textbf{not} constrained\big]}
-          \State Merge cluster $S_u$ with $S_v$.
-          \State Update interactions \& constraints with neighboring clusters.
-        \ElsIf{{\color{blue}addCannotLinkConstr} \textbf{and}  \big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big]}
-          \State Add CannotLink Constraint between $S_u$ and $S_v$
-        \EndIf
-      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \break\hspace*{2.5em} \big[all adjacent clusters have cannot-link constraints\big]}
-      \State
-      \Return $\Pi$
-  \end{algorithmic}
-    \label{main_alg}
-  \end{flushleft}
+\begin{table*}[b]
+    \centering
+    \scriptsize
+    \begin{subtable}[t!]{\textwidth}\centering
+        \begin{tabular}{c r  l | c | c  c}
+            \multicolumn{3}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
+            \multicolumn{3}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\
 
-\end{algorithm}
+            \midrule
+             & Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
+Aggl.
+Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} \\
+
+             &\makecell[r]{Absolute Max:} & 
+            $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
+               & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Mutex Watershed \cite{wolf2018mutex}} \\
+             & \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier.
+Aggl.
+Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
+
+            & Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
+
+            & Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}
+
+        \end{tabular}
+    \end{subtable} 
+    \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning \algname{}, given a linkage criterium, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
+The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e.
+$E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
+    \label{tab:linkage-criteria}
+\end{table*}
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{./figs/comparison_new.pdf} % left bottom right top
+\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data.
+The main \emph{wrongly} segmented regions are highlighted in different warm colors.
+Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.
+Red arrows point to wrongly split regions.
+Yellow arrows point out merge errors.
+The \emph{Average} linkage without cannot-link constraints returned the best segmentation.
+\label{fig:cremi_comparison}}
+\end{figure}
 
@@
 In our experiments, we decided to focus on the linkage criteria listed in Table \ref{tab:linkage-criteria}, since they represent the most common options.
-
-\begin{figure}
-\centering
-        \begin{subfigure}[t]{0.42 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/example_no_constr.pdf}
-        \caption{No constraints}\label{subfig:no_constraints}
-    \end{subfigure} \\\vspace{8pt}
-    \begin{subfigure}[t]{0.42 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/example_with_constr.pdf}
-        \caption{With cannot-link constraints}\label{subfig:with_constraints}
-    \end{subfigure}
-\caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints.
-The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges.
-The edge selected at each iteration is highlighted in yellow.
-We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
-\label{fig:algorithm_with_without_CLC}
-\end{figure}
-
-% \begin{table*}[t]
-%     % \centering
-%     \scriptsize
-%     \begin{subtable}[t!]{0.6\textwidth}\centering
-%         \begin{tabular}{r  l | c | c  c}
-%             \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
-%             \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\
-
-%             \midrule
-%              Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
-Aggl.
-Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy\\Fixation \cite{levinkov2017comparative}} \\
-
-%              \makecell[r]{Abs. Max:} & 
-%             $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
-%                & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} \\
-%              \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier.
-Aggl.
-Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
-
-%             Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
-
-%             Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}
-
-%         \end{tabular}
-%     \end{subtable} 
-%     \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning \algname{}, given a linkage criterium, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
-The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e.
-$E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
-%     \label{tab:linkage-criteria}
-% \end{table*}
-
-\begin{table*}[t]
-    \centering
-    \footnotesize
-    \begin{subtable}[t!]{\textwidth}\centering
-        \begin{tabular}{c | c  c  c  c  c}
-        \multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} \\ $\,\,\interact(S_u ,S_v)$}}  & Sum & Absolute Maximum & Average & Maximum & Minimum \\
- & $\displaystyle \sum_{e\in E_{uv}} \cost_e$  & $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$ & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big| $ &  $\displaystyle \max_{e\in E_{uv}} \cost_e$ & $\displaystyle \min_{e\in E_{uv}} \cost_e$ \\ \midrule
-
-            \thead{\textbf{Unsigned Graphs}} & \thead{Sum Linkage\\Hier.
-Aggl.
-Clust.} &\thead{Single Linkage\\Hier.
-Aggl.
-Clust.} &\thead{Average Linkage\\Hier.
-Aggl.
-Clust.} &\thead{Single Linkage\\Hier.
-Aggl.
-Clust.} &\thead{Complete Linkage\\Hier.
-Aggl.
-Clust.} \\
-            \thead{\textbf{Signed Graphs} \\\textbf{Without Constraints}} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
-            \thead{\textbf{Signed Graphs} \\\textbf{With Constraints}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
-            % \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
-            % \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\ \midrule
-
-            %  Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
-Aggl.
-Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy\\Fixation \cite{levinkov2017comparative}} \\
-
-            %  \makecell[r]{Abs. Max:} & 
-            % $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
-            %    & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} \\
-
-            %  \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier.
-Aggl.
-Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
-
-            % Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
-
-            % Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}
-
-        \end{tabular}
-    \end{subtable} 
-    \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning \algname{}, given a linkage criterium, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
-The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e.
-$E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
-    \label{tab:linkage-criteria}
-\end{table*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.96\textwidth]{./figs/comparison_new.pdf} % left bottom right top
-\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data.
-The main \emph{wrongly} segmented regions are highlighted in different warm colors.
-Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.
-Red arrows point to wrongly split regions.
-Yellow arrows point out merge errors.
-The \emph{Average} linkage without cannot-link constraints returned the best segmentation.
-\label{fig:cremi_comparison}}
-\end{figure*}

### 2020-11-06 extra/submissions_uploads/arXiv_submission/chapters/5_experiments_cityscapes.tex
Add extra files and move them to extra folder

% !TEX root = ../ms.tex
\captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
\renewcommand*{\thesubtable}{(\alph{subtable})}
\begin{table}[t]
\centering
\begin{subtable}{0.5 \textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|l|cc}
            Method & Agglomeration type & AP \\ \midrule
            PANet \cite{liu2018path} & - & \textbf{36.5} \\
            Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
             & \algname{} Average& 34.3 \\
             & \algname{} Average + Constraints & 33.9 \\
            \multirow{2}{*}{GMIS Model \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 \\
             & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
             & \algname{} Sum + Constraints  \cite{levinkov2017comparative} & 31.9  \\
             & \algname{} Sum \cite{keuper2015efficient} & 31.3 \\
        \end{tabular}
    \caption{CityScapes \emph{validation} set}
    \label{tab:results_cityscapes_val}
\end{subtable}\hfill
\begin{subtable}{0.46\textwidth}
\centering
    \scriptsize
\begin{tabular}{l|cc}
           Method & AP  & AP 50\% \\ \midrule
           PANet \cite{liu2018path} & \textbf{31.8} & \textbf{57.1} \\
           \textbf{Ours: GMIS Model + \algname{} Average} & 28.3 & 47.0 \\ 
           GMIS \cite{liu2018affinity} & 27.3 & 45.6 \\
           Mask R-CNN \cite{he2017mask} & 26.2 & 49.9 \\
           SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
           DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
           DWT \cite{bai2017deep} & 19.4 & 35.3 \\
           InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
        \end{tabular}
    \caption{CityScapes \emph{test} set}
    \label{tab:results_cityscapes_test}
\end{subtable}
\caption{Average Precision scores (higher is better) on the CityScapes dataset. \algname{} with \emph{Average} linkage combined with the GMIS Model \cite{liu2018affinity} represents the proposal-free method achieving the best results (May 2019). In order to have a fair comparison, we only compare methods that did not use external data (e.g. COCO \cite{lin2014microsoft}) for training. In Table (a) we distinguish between proposal-based and proposal-free methods.}\label{tab:results_cityscapes}
\end{table}

\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
We used the pipeline proposed in GMIS \cite{liu2018affinity}, representing the proposal-free method performing best on the dataset. The pipeline consists of two CNN with similar structures, one predicting pixel level semantic scores and the other predicting pixel affinities between instances. The code and the model are publicly available, so we provided its output affinities as input to \algname{}.
In Appendix \ref{sec:appendix_cityscapes} we present how we fine-tuned the model by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.

Results are summarized in Table \ref{tab:results_cityscapes} and Fig. \ref{fig:cityscapes}: the best scores are achieved by PANet \cite{liu2018path}, which is a proposal-based method strongly related to Mask R-CNN. \algname{} with \emph{Average} linkage achieves competitive results and outperforms all previously proposed proposal-free methods. Similarly to the experiments on neuron segmentation, other linkage criteria tend to over-cluster, like \emph{Abs Max}, or under-cluster and merge instances, like \emph{Sum}. The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and when we applied it to the affinities predicted by our fine-tuned model it achieved an AP score of 33.0 on the validation set, which is worse than the original value 34.1 reported in \cite{liu2018affinity}. This is probably due to the fact that the agglomeration MultiStepHAC was tailored to the output affinities of the original model. 
Table \ref{tab:extended_results_cityscapes_val} in Appendix includes the scores of all other tested \algname{} algorithms.
\begin{figure}
\centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_4.pdf} % left bottom right top
\caption{Visual results given by different \algname{} linkage criteria on a crop of a CityScapes image}\label{fig:cityscapes}
\end{figure}

### 2020-11-06 extra/submissions_uploads/arXiv_submission/chapters/5_experiments_compare_rules.tex
Add extra files and move them to extra folder

--- 2020-03-10 chapters/5_experiments_compare_rules.tex
@@
-% !TEX root = ../agglo_clust_review.tex
-
-\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
-\begin{figure*}[t]
-\centering
-    \begin{subfigure}[t]{0.49 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_0.pdf}
-    \end{subfigure} \hfill
-    \begin{subfigure}[t]{0.49 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
-    \end{subfigure}
-
-        \begin{subfigure}[t]{0.49 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
-        \caption{No long-range predictions: \\$p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
-    \end{subfigure} \hfill
-    \begin{subfigure}[t]{0.49 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
-        \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
-    \end{subfigure}
-\caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust.
-Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions.
-Solid lines represent median values over 30 experiments.
-Values between the 25th and the 75th percentile are shown in shaded areas.
-The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details).
-For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph.
-Experiments are performed on a crop of CREMI training sample B.
-}\label{fig:noise_plots}
-\end{figure*}
-\begin{figure*}[t]
-        \centering
-\begin{minipage}[t]{0.48\textwidth}
-    \centering
-    \scriptsize
-        \begin{tabular}[t]{l|c}
-         Method & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
-\textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
-\algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
-\algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
-\algname{} Max. + Constraints & 0.324 \\
-\algname{} Sum \cite{keuper2015efficient} & 0.334 \\
-\algname{} Average + Constraints & 0.563 \\
-THRESH & 1.521 \\ 
-        \end{tabular}
-    \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding.
-All methods use the affinity predictions from our CNN as input.
-Scores are averaged over the three CREMI training datasets.}
-    \label{tab:results_cremi_train}
-\end{minipage}\hfill
-\begin{minipage}[t]{0.48\textwidth}
-    \centering
-    \scriptsize
-        \begin{tabular}[t]{l|c}
-        Method & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
-Our CNN + DTWS + LMC &  0.221\\
-PNI CNN \cite{lee2017superhuman} & 0.228 \\
-\textbf{Our CNN + \algname{} Average} & \textbf{0.241} \\
-MALA CNN + MC \cite{funke2018large} & 0.276 \\
-CRU-Net \cite{zeng2017deepem3d} & 0.566  \\
-LFC \cite{parag2017anisotropic} & 0.616  \\
-        \end{tabular}
-        \vspace*{0.99em}
-    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (March 2020).
-All entries, apart from our using \algname{}, employ superpixel-based post-processing pipelines.}
-    \label{tab:results_cremi_test}
-\end{minipage}
-\end{figure*}
+% !TEX root = ../ms.tex
 
@@
 We evaluate all algorithms in the proposed framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available.
-The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which come with publicly available training ground truth.
-The results submitted to the leaderboard are evaluated using the CREMI score, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}.
+The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth.
+The results submitted to the leaderboard are evaluated using the CREMI score (\url{https://cremi.org/leaderboard/}), based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}.
 In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.

### 2020-11-06 extra/submissions_uploads/arXiv_submission/chapters/5_experiments_noise.tex
Add extra files and move them to extra folder

% !TEX root = ../ms.tex

\subsection{Results and discussion}\label{sec:results}
\textbf{Comparison of linkage criteria} Table \ref{tab:results_cremi_train} shows how the agglomerative algorithms derived from our framework compare to each other. For a simple baseline, we also include a segmentation produced by thresholding the affinity predictions (THRESH).
\algname{} with \emph{Average} linkage, representing one of the new algorithms derived from our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC (\algname{} Sum) \cite{keuper2015efficient}, Greedy Fixation (\algname{} Sum + Constraints) \cite{levinkov2017comparative} or Mutex Watershed (\algname{} Abs. Max.) \cite{wolf2018mutex}. The competitive performance of this simple parameter-free algorithm is also reported in Table \ref{tab:results_cremi_test}, showing the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the lifted multicut formulation of \cite{beier2017multicut} that uses several random forests to predict graph edge weights, relying not only on information derived from affinity maps but also raw data and shape information.
Note that the test volumes contain several imaging artifacts that make segmentation particularly challenging and might profit from more robust edge statistics of super-pixel based approaches.
On the other hand, the fact that our algorithm can operate on pixels directly removes the parameter tuning necessary to obtain good super-pixels and can also avoid errors that result from wrong superpixels that cannot be fixed during later agglomeration.
In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets. Appendix Table \ref{tab:extended_results_cremi} lists the performances and the run-times for all tested \algname{} linkage.

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.56\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
          & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
\textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
\algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
\algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
\algname{} Max. + Constraints & 0.324 \\
\algname{} Sum \cite{keuper2015efficient} & 0.334 \\
\algname{} Average + Constraints & 0.563 \\
THRESH & 1.521 \\ 
        \end{tabular}
    \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding. All methods use the affinity predictions from our CNN as input. Scores are averages over the three CREMI training datasets.}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.4\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
Our CNN + DTWS + LMC &  0.221\\
PNI CNN \cite{lee2017superhuman} & 0.228 \\
\textbf{Our CNN + \algname{} Average} & \textbf{0.241} \\
MALA CNN + MC \cite{funke2018large} & 0.276 \\
CRU-Net \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
        \end{tabular}
        \vspace*{1em}
    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019). The scores are averages of the three test datasets.}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_0.pdf}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
    \end{subfigure}

        \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
        \caption{No long-range predictions: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
        \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
    \end{subfigure}
\caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust. Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions. Solid lines represent median values over 30 experiments. Values between the 25th and the 75th percentile are shown in shaded areas. The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph. Experiments are performed on a crop of CREMI training sample B.
}\label{fig:noise_plots}
\end{figure}

\textbf{Noise experiments }  Additionally, we conduct a set of experiments where the CNN predictions are perturbed by structured noise, in order to highlight the properties of each \algname{} variant and perform an in-depth comparison that is as quantitative as possible. Appendix \ref{sec:appendix_noise_gen} introduces the type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false positive boundary evidence. 
Fig. \ref{fig:noise_plots} summarizes our 12000 noise experiments: we focus on the best performing linkage criteria, i.e. \emph{Average}, \emph{Sum} and \emph{Abs Max}, and test them with different amount of noise. 
In these experiments, we also want to assess how beneficial it is to use long-range CNN predictions in the agglomeration. Thus, we perform a set of simulations without adding long-range connections to the grid-graph and another set where we introduce them with a 10\% probability\footnote{We also performed experiments adding all the long-range predictions given by the CNN model, but we did not note major differences when using only 10\% of them. Adding this fraction is usually sufficient to improve the scores.}.

\textbf{Average and Abs Max linkage } Our findings confirm that \algname{} with \emph{Average} linkage criterion represents the most robust algorithm tested and the one that benefits the most from using the long-range CNN predictions. On the other hand, it is not a surprise that the \emph{Abs Max} statistic proposed by \cite{wolf2018mutex} is less robust to noise than the \emph{Average} linkage, but, as we show in the Appendix Table \ref{tab:extended_results_cremi}, \emph{Abs Max} represents a valid and considerably faster option. 
Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights, then \algname{} with cannot-link constraints shows a clear tendency to over-cluster.

\textbf{Sum linkage } 
All our experiments show that \algname{} with \emph{Sum} linkage is the algorithm with the highest tendency to under-cluster and incorrectly merge segments (see Fig. \ref{fig:cremi_comparison} for an example). This property is related to the empirical observation that a \emph{Sum} statistic tends to grow clusters one after the other, as shown in Fig. \ref{fig:intro_figure} by the quite unique agglomeration order of the \emph{Sum} statistic. An intuitive explanation of this fact is the following: initially, most of the intra-cluster nodes present similar attractive interactions between each others; when the two nodes sharing the most attractive interaction are merged, there is a high chance that they both share an attractive interaction with a common neighboring node, so the new interaction with this common neighbor will be immediately assigned to a high priority in the agglomeration, given by the sum of two high weights; this usually starts a ``chain reaction'', where only a single cluster is agglomerated at the beginning. On the other hand, as we also see in Fig. \ref{fig:intro_figure}, other linkage criteria like \emph{Average} or \emph{Abs Max} grow clusters of similar sizes in parallel and accumulate in this way much more reliable inter-cluster statistics.

### 2020-11-06 extra/submissions_uploads/arXiv_submission/chapters/6_conclusions.tex
Add extra files and move them to extra folder

% !TEX root = ../ms.tex
\section{Conclusion}
We have presented a novel unifying framework for agglomerative clustering of graphs with both positive and negative edge weights and we have shown that several existing clustering algorithms, e.g. the Mutex Watershed \cite{wolf2018mutex}, can be reformulated as special cases of one underlying agglomerative algorithm. This framework also allowed us to introduce new algorithms, one of which, based on an \emph{Average} linkage criterion, outperformed all the others: It proved to be a simple and remarkably robust approach to process short- and long-range predictions of a CNN applied to an instance segmentation task.
On biological images, this simple average agglomeration algorithm can represent a valuable choice for user who is not willing to spend much time tuning complex task-dependent pipelines based on superpixels.  
In future work we plan to extend the comparison to other types of non-image graphs and explore common theoretical properties of the algorithms included in the framework.

### 2020-11-06 extra/submissions_uploads/arXiv_submission/chapters/supplementary.tex
Add extra files and move them to extra folder

--- 2019-11-08 chapters/supplementary.tex
@@
-% !TEX root = ../agglo_clust_review.tex
+% !TEX root = ../ms.tex
 
-\begin{algorithm*}
+\section{Supplementary material}
+
+\begin{algorithm}
   \caption{Implementation of \algname{}, generalized algorithm for signed graph partitioning}
@@
   \label{detailed_alg}
-\end{algorithm*}
-
-\begin{figure*}
+\end{algorithm}
+\begin{figure}
         \centering
@@
     \centering
-    \small
+    \scriptsize
                 \begin{tabular}[b]{r | l }
@@
 \label{fig:edge_contraction_and_contr_graph}  
-\end{figure*}
-
-\section{Supplementary material}
+\end{figure}
 
@@
 Thus, we can recompute these interactions by using an \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$:
-\begin{align}
-  \interact(S_u \cup S_v,S_t) =& f\Big[ \interact(S_u,S_t), \interact(S_v,S_t) \Big] \\
-  =& f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) 
-\end{align}
+\begin{equation}
+  \interact(S_u \cup S_v,S_t) = f\Big[ \interact(S_u,S_t), \interact(S_v,S_t) \Big] = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) 
+\end{equation}
 In Fig.
@@
 
-\begin{algorithm*}
+\begin{algorithm}
   \caption{Mutex Watershed Algorithm proposed by \cite{wolf2018mutex}}
@@
   \label{alg:mutex_watershed}
-\end{algorithm*}
+\end{algorithm}
 
-\subsection{Properties of \algname{} with Absolute Maximum linkage}\label{sec:appendix_abs_max}
+\subsection{Properties of \algname{} with \emph{Absolute Maximum} linkage}\label{sec:appendix_abs_max}
 \paragraph{Remark on graph notation} The definition of a graph proposed by \cite{wolf2018mutex} makes a distinction between a set of positive edges $E^+$, associated with a set $W^+$ of positive scalar attributes representing merge affinities, and a set of negative edges $E^-$, associated with a set $W^-$ of positive attributes representing split tendencies.
@@
 \begin{align}
-E^+ =&\,\, \{ e \in E \,\,\text{s.t.} \,\,w_e = w_e^+ - w_e^- > 0\}, \\
-E^- =&\,\, \{ e \in E \,\,\text{s.t.}\,\, w_e = w_e^+ - w_e^- \leq 0\}, \\
-W^+ =&\,\, \{ |w_e| \,\,\text{s.t.}\,\, e \in E^+\},\\
- W^- =&\,\, \{ |w_e| \,\,\text{s.t.}\,\, e \in E^-\}.
+E^+ = \{ e \in E \,\,\text{s.t.} \,\,w_e = w_e^+ - w_e^- > 0\},& \qquad E^- = \{ e \in E \,\,\text{s.t.}\,\, w_e = w_e^+ - w_e^- \leq 0\} \\
+W^+ = \{ |w_e| \,\,\text{s.t.}\,\, e \in E^+\},& \qquad W^- = \{ |w_e| \,\,\text{s.t.}\,\, e \in E^-\}
 \end{align}
@@
 
-\begin{figure*}
+\begin{figure}
         \centering
@@
 \label{fig:abs_max_proof_example}  
-\end{figure*}
+\end{figure}
 
@@
 The most common approaches use \emph{additive} \cite{ailon2008aggregating} or \emph{logarithmic} \cite{finkel2008enforcing,andres2012globally} mappings:
-\begin{align} 
-\cost_{e,\mathrm{Add}} =&\,\, p_e - \beta, \\
-\cost_{e,\mathrm{Log}} =&\,\, \log \left( \frac{p_e}{1-p_e} \right) - \log \left( \frac{\beta}{1-\beta} \right), \label{eq:mappings}
-\end{align}
+\begin{equation} \label{eq:mappings}
+\cost_{e,\mathrm{Add}} = p_e - \beta, \qquad \quad \cost_{e,\mathrm{Log}} = \log \left( \frac{p_e}{1-p_e} \right) - \log \left( \frac{\beta}{1-\beta} \right),
+\end{equation}
 where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation.
@@
 
-\begin{table*}[t]
+\begin{table}[t]
 \centering
@@
     \label{tab:extended_results_cremi}
-\end{table*}
+\end{table}
 
@@
 For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
-\begin{figure*}[t]
+\begin{figure}[t]
 \centering
-\begin{minipage}[T]{0.61\textwidth}
+\begin{minipage}[T]{0.6\textwidth}
 \centering
@@
     \centering
-    \small
-    \vspace*{1.6em}
+    \footnotesize
         \begin{tabular}{l|c|c}
@@
         \end{tabular}
-    \vspace*{0.5em}
     \captionof{table}{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set.
@@
 \end{minipage}
-\end{figure*}
+\end{figure}
 

### 2021-02-08 chapters/3_algorithm.tex
Add first version of new alg. and binary tree formulation

--- 2020-02-17 chapters/3_algorithm.tex
@@
 Some approaches directly compute $\cost_e$, whereas others compute $w_e^+$ and $w_e^-$ separately.
-In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$.
+In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$. \TODO{remove and add multicut energy, define HC}
 
 \textbf{Inter-cluster interaction } We call two clusters $S_u,S_v$ \emph{adjacent} if there exists at least one edge ${e_{ts}\in E}$ connecting a node $t\in S_u$ to a node $s\in S_v$.
-In hierarchical agglomerative clustering, the interaction $\interact(S_u,S_v)$ between the two clusters is usually defined as a function $\interact{}:\Pi \times \Pi \rightarrow \mathbb{R}$, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S_u$ and $S_v$, i.e.
+Let the interaction $\interact(S_u,S_v)$ between the two clusters be defined as a function $\interact{}:\Pi \times \Pi \rightarrow \mathbb{R}$, \TODO{Remove $\Pi$ from def.
+Problem of zero interactions} named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S_u$ and $S_v$, i.e.
 $(S_u \times S_v) \cap E$.
 All the linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
+
+\textbf{Hierarchical trees} In HC literature, a \emph{dendrogram} $T$ is a rooted binary tree\footnote{In general, one could look at trees that are not binary.
+However, the algorithms discussed in this paper always generate binary hierarchical trees, so nothing would be gained by this generalization.} whose leaves are in one-to-one correspondence with $V$, representing the merging order of an agglomerative algorithm.
+Let $T_{\mathrm{R}},T_{\mathrm{L}}\subset T$ denote the subtrees rooted at the two children of the root node in $T$.
+For any two leaves $u,v \in V$, let $T[u \vee v]$ be the subtree rooted at the least common ancestor of $u$ and $v$ (furthest from the root), and let \texttt{leaves}$(T[u \vee v])\subseteq V$ be the set of leaves of this subtree.
+\TODO{Here we talk about the algorithm already, so we could move it to next section and the flow could be better. But we need a tree in the alg. So we better do this later}
+For each pairs of leaves $u,v$, we can then assign a \emph{height} to their least common ancestor in the tree $T^*$ corresponding to the linkage/interaction between clusters $S_u$ and $S_v$ when $u$ and $v$ were merged by the algorithm:
+% Then, given a binary tree $T$ and a linkage criterion $\interact$, we can associate a \emph{signed similarity} function $\treeHeight$ to each pair of distinct original nodes $u\neq v$, with $u, v \in V$:
+\begin{equation}
+\treeHeight(u,v) \equiv \interact{} \big( \text{\texttt{leaves}}(T_{\mathrm{R}}[u \vee v]), \text{\texttt{leaves}}(T_{\mathrm{L}}[u \vee v]) \big)
+\end{equation}
+
+\textbf{Ultrametrics}  Let us define the function $d_T: V \times V \rightarrow \mathbb{R}^{+}$ as:
+\begin{align}
+d_T(u,v)\equiv &\begin{cases}
+0 & \text{if}\,\, u=v\\
+M-\treeHeight(u,v) & \text{if}\,\, u\neq v
+\end{cases}\quad \forall u,v\in V\\
+\mathrm{where}& \quad  M \equiv \max_{u',v'\in V,\,u'\neq v'}\treeHeight(u',v').
+\end{align}
+In the next section, we will show that for some specific choices of linkage $\interact{}$, then $(V, d_{T^*})$ is an ultrametric on the original graph, where $T^*$ is the hierarchical tree built by the \algname{} algorithm.
+
+\begin{itemize}
+\item Def: A metric space $(X,d)$ is an \emph{ultrametric} if for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.
+\item The connection between hierarchical trees and ultrametrics is well known.
+Normally, ultrametrics are associated to strictly positive \emph{similarity} or \emph{dissimilarity} measures on a graph.
+In our case, the interaction $\treeHeight{}$ can also be negative, so we first map these interactions to strictly positive values:
+
+\item By definition, we have that $d_T(u,v)\geq 0$, $d_T(u,v)=d_T(v,u)$, and $d_T(u,u)= 0$. So, to prove that $(V, d_{T^*})$ is an ultrametric, we need to prove that
+\begin{equation}
+\interact{}_{T^*}(u,v) \geq \min \{\interact{}_{T^*}(u,t), \interact{}_{T^*}(v,t)\}
+\end{equation}
+ $\forall u,v,t\in V$. In other words, we want to make sure that, at every iteration, the algorithm merges pairs of clusters with lower and lower interactions. 
+\begin{equation}
+\interact{}_{T^*}(u,v) \geq \interact{}_{T^*}(u,t) \Leftrightarrow T[u \vee t] \subseteq T[u \vee v] 
+\end{equation}
+This does not happen for all linkages (see Sum fig. 1) and when constraints are in place.  
+ % that have the most positive interaction   two clusters merged by the algorithm will always have an interaction that is more negative as compared to all clusters already merged and more positive than all clusters that will be merged at later iterations of the algorithm.
+\item We call a linkage invariant to $\alpha$-shift of weights, if by changing all edge weights of the graphs by a constant $w_e+\alpha$ the structure of the hierarchical tree  does not change and defines the same function $d_T$.
+(And correlation clustering problem is not like that).
+\end{itemize}
 
@@
 \begin{algorithm}[t]
+\footnotesize
   \begin{flushleft}
-  \caption{\algname{}: generalized algorithm for signed graph partitioning}
-   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}addCannotLinkConstraints}  \\
-  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
+  \footnotesize
+  \caption{\algname{}}
+  % \caption{\algname{}: generalized algorithm for signed graph partitioning}
+   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; \\ 
+   \hspace*{4.3em}boolean {\color{blue}addCannotLinkConstraints}  \\
+  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi^*$, rooted binary hierarchical tree $T^*$\\
   \hspace*{\algorithmicindent} 
@@
       \State Initial clustering: $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$
+      \State Initialize hierarchical tree $T$ with leaves nodes $V=\{v_1,\ldots,v_{|V|}\}$
       \State Initialize interactions between clusters with $\cost_e = w^+_e - w^-_e$
+      \State \emph{// Phase 1: Merge positive interactions (possibly using constraints)}
+      \State Push absolute interactions $|w_e|$ to priority queue $PQ$
       \Repeat 
-        \State Get $S_u,S_v\in\Pi$ with highest interaction $|\interact{}(S_u,S_v)|$
-        \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ \textbf{not} constrained\big]}
-          \State Merge cluster $S_u$ with $S_v$
+        \State Pop $S_u,S_v\in\Pi$ from $PQ$ with highest interaction $|\interact{}(S_u,S_v)|$
+        \If{\big[{\color{green}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ \textbf{not} constrained\big]}
+          \State Merge clusters $S_u$, $S_v$ and update hierarchical tree $T$
           \State Update interactions \& constraints with neighboring clusters
@@
         \EndIf
-      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \break\hspace*{2.5em} \big[all adjacent clusters have cannot-link constraints\big]}
+      \Until{\big[$PQ$ is empty\big]}
+      % \State
+      % \If{{\color{blue}addCannotLinkConstr}} % \Comment{Step 2: release constraints}
+      \State \emph{// Phase 2: Relax constraints \& merge remaining positive interactions}
+      \State Push signed interactions $\interact{}(S_u,S_v)$ to PQ, $\forall S_u, S_v \in \Pi$
+      \Repeat 
+        \State Pop $S_u,S_v\in\Pi$ from $PQ$ with highest interaction $\interact{}(S_u,S_v)$
+        \If{\big[{\color{green}\textbf{$\interact{}(S_u,S_v) > 0$}}\big]}
+          \State Merge clusters $S_u$, $S_v$ and update hierarchical tree $T$
+          \State Update interactions with neighboring clusters
+        \EndIf
+      \Until{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big]} 
+      \State Save the final clustering $\Pi^* \gets \Pi$ 
+      \State \emph{// Phase 3: Merge negative interactions until one single cluster is left}
+      \Repeat
+        \State Pop $S_u,S_v\in\Pi$ from $PQ$ with highest interaction $\interact{}(S_u,S_v)$
+        \State Merge clusters $S_u$, $S_v$ and update hierarchical tree $T$
+        \State Update interactions with neighboring clusters
+      \Until{\big[Only one cluster is left in $\Pi$\big]} 
+      % \EndIf
       \State
-      \Return $\Pi$
+      \Return $\Pi^*$, $T^*\gets T$
   \end{algorithmic}
@@
 %     \scriptsize
-%     \begin{subtable}[t!]{0.6\textwidth}\centering
-%         \begin{tabular}{r  l | c | c  c}
-%             \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
-%             \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\
+%     \begin{subtable}[t!]{\textwidth}\centering
+%         \begin{tabular}{R{5em}  l | M{10em} | M{8em}  M{8em}}
+%             \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria}\\ $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned} \\\textbf{Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
+%             \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No \\Constraints}} & \thead{With\\ Constraints} \\
 
@@
 %             Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}
-
 %         \end{tabular}
 %     \end{subtable} 
-%     \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning \algname{}, given a linkage criterium, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
+%     \vspace{1em}
+%     \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning, \algname{}, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
 The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e.
@@
 Clust.} \\
-            \thead{\textbf{Signed Graphs} \\\textbf{Without Constraints}} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
-            \thead{\textbf{Signed Graphs} \\\textbf{With Constraints}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
+            \thead{\textbf{Signed Graphs} \\\textbf{Without Constraints}} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Average Linkage\\Hier.
+Aggl.
+Clust.} &\thead{Single Linkage\\Hier.
+Aggl.
+Clust.} &\thead{Complete Linkage\\Hier.
+Aggl.
+Clust.} \\
+            \thead{\textbf{Signed Graphs} \\\textbf{With Constraints}} & \thead{\textbf{NEW}} % \thead{Greedy Fixation \cite{levinkov2017comparative}} 
+            & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
             % \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\

### 2021-02-08 chapters/5_experiments_spectral.tex
Add first version of new alg. and binary tree formulation

@@
 \centering
-\begin{minipage}[t]{\textwidth}
+\begin{minipage}[t]{0.48\textwidth}
 \vspace{0pt}
@@
 % \footnotesize
-\begin{tabular}[t]{L{29em} M{7em}}
+\begin{tabular}[t]{L{9em} M{7em}}
            Method & Rand-Score \\ \midrule
@@
 \end{minipage}\\\vspace{2em}
-\begin{minipage}[t]{\textwidth}
+\begin{minipage}[t]{0.48\textwidth}
 \vspace{0pt}
 \centering
-        \includegraphics[width=0.8\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf} % 0.45
+        \includegraphics[width=1.\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf} % 0.45
         \caption{\algname{} performances compared to spectral methods on synthetic graphs. The spectral methods were given the true number of clusters as input, in contrast to \algname{}.}

### 2021-02-08 chapters/3_algorithm.tex
Polish definition of binary trees and UM

@@
 Some approaches directly compute $\cost_e$, whereas others compute $w_e^+$ and $w_e^-$ separately.
-In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$. \TODO{remove and add multicut energy, define HC}
+In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$.
+\TODO{shorten and add multicut energy def, define HC abbrv.}
+
+\begin{itemize}
+\item Given a linkage $\interact{}$, we say that Algorithm \ref{main_alg} is invariant to a $\alpha$ weight-shift, if by changing all edge weights of the graphs by a constant $w_e+\alpha$ the structure of the hierarchical tree  does not change and defines the same function $d_T$.
+\item \TODO{Why do we care?} MC does not return nested/hierarchical solutions when shifting weights.
+Which of these algorithms behave the same, or, somehow are more related to correlation clustering?
+So, actually, we care more about the shifted-solutions being nested, and not really about the fact that the hierarchy tree built by the algorithm stays the same.
+Is this somehow equivalent...?
+\end{itemize}
 
@@
 All the linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
-
-\textbf{Hierarchical trees} In HC literature, a \emph{dendrogram} $T$ is a rooted binary tree\footnote{In general, one could look at trees that are not binary.
-However, the algorithms discussed in this paper always generate binary hierarchical trees, so nothing would be gained by this generalization.} whose leaves are in one-to-one correspondence with $V$, representing the merging order of an agglomerative algorithm.
-Let $T_{\mathrm{R}},T_{\mathrm{L}}\subset T$ denote the subtrees rooted at the two children of the root node in $T$.
-For any two leaves $u,v \in V$, let $T[u \vee v]$ be the subtree rooted at the least common ancestor of $u$ and $v$ (furthest from the root), and let \texttt{leaves}$(T[u \vee v])\subseteq V$ be the set of leaves of this subtree.
-\TODO{Here we talk about the algorithm already, so we could move it to next section and the flow could be better. But we need a tree in the alg. So we better do this later}
-For each pairs of leaves $u,v$, we can then assign a \emph{height} to their least common ancestor in the tree $T^*$ corresponding to the linkage/interaction between clusters $S_u$ and $S_v$ when $u$ and $v$ were merged by the algorithm:
-% Then, given a binary tree $T$ and a linkage criterion $\interact$, we can associate a \emph{signed similarity} function $\treeHeight$ to each pair of distinct original nodes $u\neq v$, with $u, v \in V$:
-\begin{equation}
-\treeHeight(u,v) \equiv \interact{} \big( \text{\texttt{leaves}}(T_{\mathrm{R}}[u \vee v]), \text{\texttt{leaves}}(T_{\mathrm{L}}[u \vee v]) \big)
-\end{equation}
-
-\textbf{Ultrametrics}  Let us define the function $d_T: V \times V \rightarrow \mathbb{R}^{+}$ as:
-\begin{align}
-d_T(u,v)\equiv &\begin{cases}
-0 & \text{if}\,\, u=v\\
-M-\treeHeight(u,v) & \text{if}\,\, u\neq v
-\end{cases}\quad \forall u,v\in V\\
-\mathrm{where}& \quad  M \equiv \max_{u',v'\in V,\,u'\neq v'}\treeHeight(u',v').
-\end{align}
-In the next section, we will show that for some specific choices of linkage $\interact{}$, then $(V, d_{T^*})$ is an ultrametric on the original graph, where $T^*$ is the hierarchical tree built by the \algname{} algorithm.
-
-\begin{itemize}
-\item Def: A metric space $(X,d)$ is an \emph{ultrametric} if for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.
-\item The connection between hierarchical trees and ultrametrics is well known.
-Normally, ultrametrics are associated to strictly positive \emph{similarity} or \emph{dissimilarity} measures on a graph.
-In our case, the interaction $\treeHeight{}$ can also be negative, so we first map these interactions to strictly positive values:
-
-\item By definition, we have that $d_T(u,v)\geq 0$, $d_T(u,v)=d_T(v,u)$, and $d_T(u,u)= 0$. So, to prove that $(V, d_{T^*})$ is an ultrametric, we need to prove that
-\begin{equation}
-\interact{}_{T^*}(u,v) \geq \min \{\interact{}_{T^*}(u,t), \interact{}_{T^*}(v,t)\}
-\end{equation}
- $\forall u,v,t\in V$. In other words, we want to make sure that, at every iteration, the algorithm merges pairs of clusters with lower and lower interactions. 
-\begin{equation}
-\interact{}_{T^*}(u,v) \geq \interact{}_{T^*}(u,t) \Leftrightarrow T[u \vee t] \subseteq T[u \vee v] 
-\end{equation}
-This does not happen for all linkages (see Sum fig. 1) and when constraints are in place.  
- % that have the most positive interaction   two clusters merged by the algorithm will always have an interaction that is more negative as compared to all clusters already merged and more positive than all clusters that will be merged at later iterations of the algorithm.
-\item We call a linkage invariant to $\alpha$-shift of weights, if by changing all edge weights of the graphs by a constant $w_e+\alpha$ the structure of the hierarchical tree  does not change and defines the same function $d_T$.
-(And correlation clustering problem is not like that).
-\end{itemize}
 
@@
 
-In Algorithm \ref{main_alg}, we provide simplified pseudo-code for the proposed \algname{} algorithm.
+\TODO{Update description to new pseudocode} In Algorithm \ref{main_alg}, we provide simplified pseudo-code for the proposed \algname{} algorithm.
 \algname{} implements a bottom-up approach that starts by assigning each node to its own cluster and then iteratively merges pairs of adjacent clusters.
@@
 
+\paragraph{Hierarchical trees and ultrametrics} In HC literature,  a \emph{dendrogram} $T$ is a rooted binary tree\footnote{In general, one could look at trees that are not binary.
+However, the algorithms discussed in this paper always generate binary hierarchical trees, so nothing would be gained by this generalization.} representing the merging order of an agglomerative algorithm, such that the leaves of this tree are in one-to-one correspondence with $V$.
+Let $T_{\mathrm{R}},T_{\mathrm{L}}\subset T$ denote the subtrees rooted at the two children of the root node in $T$.
+For any two leaves $u,v \in V$, let $T[u \vee v]$ be the subtree rooted at the least common ancestor of $u$ and $v$ (furthest from the root), and let \texttt{leaves}$(T[u \vee v])\subseteq V$ be the set of leaves of this subtree.
+% \TODO{Here we talk about the algorithm already, so we could move it to next section and the flow could be better. But we need a tree in the alg. So we better do this later}
+Algorithm \ref{main_alg} returns a binary tree denoted by $T^*$.
+For each pair of distinct leaves $u,v$, we can then assign a \emph{depth} \TODO{better name?} to their least common ancestor node in $T^*$ defined by the interaction between clusters $S_u$ and $S_v$, when $u$ and $v$ were merged: \TODO{See trees on toy graphs in Fig.
+1}
+% Then, given a binary tree $T$ and a linkage criterion $\interact$, we can associate a \emph{signed similarity} function $\treeHeight$ to each pair of distinct original nodes $u\neq v$, with $u, v \in V$:
+\begin{equation}
+\treeHeight(u,v) \equiv \interact{} \big( \text{\texttt{leaves}}(T^*_{\mathrm{R}}[u \vee v]), \text{\texttt{leaves}}(T^*_{\mathrm{L}}[u \vee v]) \big)
+\end{equation}
+
+The connection between hierarchical trees and ultrametrics is well known\footnote{A metric space $(X,d)$ is an \emph{ultrametric} if for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.}. 
+We now want to use the \emph{depth-measure} $\treeHeight{}$ to define an ultrametric on the graph.  
+Normally, ultrametrics are associated to strictly positive \emph{similarity} or \emph{dissimilarity} measures on a graph. Thus, we first need to map $\treeHeight{}$ to positive values:
+\begin{align}
+d_{T^*}(u,v)\equiv &\begin{cases}
+0 & \text{if}\,\, u=v\\
+M-\treeHeight(u,v) & \text{if}\,\, u\neq v
+\end{cases}\quad \forall u,v\in V\\
+\mathrm{where}& \quad  M \equiv \max_{u',v'\in V,\,u'\neq v'}\treeHeight(u',v').
+\end{align}
+By definition, we have that  $d_{T^*}: V \times V \rightarrow \mathbb{R}^{+}$, $d_{T^*}(u,v)=d_{T^*}(v,u)$, and $d_{T^*}(u,u)= 0$.
+Thus, to prove that $(V, d_{T^*})$ is an ultrametric, we only need to prove that
+\begin{equation}
+\interact{}_{T^*}(u,v) \geq \min \{\interact{}_{T^*}(u,t), \interact{}_{T^*}(v,t)\}
+\end{equation}
+ for every distinct $u,v,t\in V$.
+In other words, given two leaves nodes $u,v\in V$, the depth $\interact{}_{T^*}(u,v)$ associated to their least common ancestor $i\in T^*$ should be both lower than the depth of any $i$-descendant node in $T^*$ and higher than any $i$-ancestor node in $T^*$:
+ % that have the most positive interaction   two clusters merged by the algorithm will always have an interaction that is more negative as compared to all clusters already merged and more positive than all clusters that will be merged at later iterations of the algorithm.
+\begin{equation}
+\interact{}_{T^*}(u,v) \geq \interact{}_{T^*}(u,t) \Leftrightarrow T^*[u \vee t] \subseteq T^*[u \vee v] 
+\end{equation}
+ This happens only if, at every iteration, Algorithm \ref{main_alg} merges pairs of clusters with lower and lower interactions, which is true for only certain choices of linkage criteria.
+%In the next section \ref{sec:alg_update_rules}, we will show that this happens only for certain linkages and only when constraints are not enforced
+
 \subsection{\algname{} with different linkage criteria: new and existing algorithms} \label{sec:alg_update_rules}
 
-Our main contribution is the generalized algorithm for signed graph partitioning, GASP, that encompasses several known and new agglomerative algorithms on display in Table \ref{tab:linkage-criteria}.
+\TODO{Specify greediness wrt multicut energy, ultrametric properties, and shift-invariance properties} Our main contribution is the generalized algorithm for signed graph partitioning, GASP, that encompasses several known and new agglomerative algorithms on display in Table \ref{tab:linkage-criteria}.
 In our framework, individual algorithms are differentiated by the linkage criterion employed. We review them in the following paragraphs.
@@
 
-\begin{figure}[t]
-\centering
-        \begin{subfigure}[t]{0.46 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/example_no_constr.pdf}
-        \caption{No constraints}\label{subfig:no_constraints}
-    \end{subfigure} \hfill \vspace{8pt}
-    \begin{subfigure}[t]{0.46 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/example_with_constr.pdf}
-        \caption{With cannot-link constraints}\label{subfig:with_constraints}
-    \end{subfigure}
-\caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints.
+% \begin{figure}[t]
+% \centering
+%         \begin{subfigure}[t]{0.46 \textwidth}
+%         \centering
+%         \includegraphics[width=\textwidth]{figs/example_no_constr.pdf}
+%         \caption{No constraints}\label{subfig:no_constraints}
+%     \end{subfigure} \hfill \vspace{8pt}
+%     \begin{subfigure}[t]{0.46 \textwidth}
+%         \centering
+%         \includegraphics[width=\textwidth]{figs/example_with_constr.pdf}
+%         \caption{With cannot-link constraints}\label{subfig:with_constraints}
+%     \end{subfigure}
+% \caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints.
 The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges.
@@
 We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
-\label{fig:algorithm_with_without_CLC}
-\end{figure}
+% \label{fig:algorithm_with_without_CLC}
+% \end{figure}
 
@@
 
-            \thead{\textbf{Unsigned Graphs}} & \thead{Sum Linkage\\Hier.
-Aggl.
-Clust.} &\thead{Single Linkage\\Hier.
-Aggl.
-Clust.} &\thead{Average Linkage\\Hier.
-Aggl.
-Clust.} &\thead{Single Linkage\\Hier.
-Aggl.
-Clust.} &\thead{Complete Linkage\\Hier.
-Aggl.
-Clust.} \\
-            \thead{\textbf{Signed Graphs} \\\textbf{Without Constraints}} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Average Linkage\\Hier.
-Aggl.
-Clust.} &\thead{Single Linkage\\Hier.
-Aggl.
-Clust.} &\thead{Complete Linkage\\Hier.
-Aggl.
-Clust.} \\
-            \thead{\textbf{Signed Graphs} \\\textbf{With Constraints}} & \thead{\textbf{NEW}} % \thead{Greedy Fixation \cite{levinkov2017comparative}} 
-            & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
+            \thead{\textbf{Unsigned Graphs}} & \thead{HC-Sum-Link} &\thead{HC-Single-Link\\$(\dagger,\ddagger)$} &\thead{HC-Avg-Link\\$(\dagger,\ddagger)$} &\thead{HC-Single-Link\\$(\dagger,\ddagger)$} &\thead{HC-Complete-Link\\$(\dagger,\ddagger)$} \\
+            \thead{\textbf{Signed Graphs} \\\textbf{Without Constraints}} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Mutex Watershed \cite{wolf2018mutex}\\$(\dagger)$}& \thead{HC-Avg-Link\\$(\dagger,\ddagger)$} &\thead{HC-Single-Link\\$(\dagger,\ddagger)$} &\thead{HC-Complete-Link\\$(\dagger,\ddagger)$} \\
+            \thead{\textbf{Signed Graphs} \\\textbf{With Constraints}} & \thead{Constr-Sum-Link\\(\textbf{NEW})} % \thead{Greedy Fixation \cite{levinkov2017comparative}} 
+            & \thead{Mutex Watershed \cite{wolf2018mutex}\\$(\dagger)$}& \thead{Constr-Avg-Link\\(\textbf{NEW})} &  \thead{Constr-Single-Link\\(\textbf{NEW})} &  \thead{Constr-Complete-Link\\(\textbf{NEW})} \\
             % \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
@@
 The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e.
-$E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
+$E_{uv}=(S_u \times S_{v \neq u}) \cap E$.
+\TODO{$\dagger$ if the linkage defines ultrametric and $\ddagger$ if it defines a weight-shift invariant algorithm} }
     \label{tab:linkage-criteria}

### 2021-02-19 chapters/3_algorithm.tex
Several changes to alg. descr and linkages

@@
 \section{Generalized framework for agglomerative clustering of signed graphs} \label{sec:general_framework}
-In this section, we first define notation and then introduce one of our main contributions: a signed graph partitioning algorithm (Sec.
+% In this section, we first define notation and then introduce one of our main contributions: a signed graph partitioning algorithm (Sec.
 \ref{sec:algorithm}) that can be seen as a generalization of several existing and new clustering algorithms (Sec.
@@
 
-\subsection{Notation and graph formalism} \label{sec:notation}
+\subsection{Notation} \label{sec:notation}
 
-We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes.
-In computer vision applications, the nodes can represent either pixels, superpixels or voxels.
-We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{S\in\Pi} S $, $\,S \cap S' = \emptyset$ for different clusters $S, S'\in \Pi$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
-We also denote as $S_u$ the cluster associated with node $u$.
-The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates to every edge a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}.
-On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates to each edge a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters.
-Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are also often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring positive and negative edge weights $\cost_e\in \mathbb{R}$.
+\textbf{Graph formalism} -- We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes.
+% In computer vision applications, the nodes can represent either pixels, superpixels or voxels.  
+The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates to every edge a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure.
+% the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}.
+On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates to each edge a split tendency $w_e^- \in \mathbb{R}^+$: \OPTIONAL{the higher this number, the higher the inclination of the two incident vertices to be assigned to different clusters}.
+% the higher this weight, the more the incident vertices would like to be in different clusters. 
+Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring positive and negative edge weights $\cost_e\in \mathbb{R}$.
 Following the theoretical considerations in \cite{lange2018partial}, we define these signed weights as ${\cost_e = w_e^+ - w_e^-}$.
-Some approaches directly compute $\cost_e$, whereas others compute $w_e^+$ and $w_e^-$ separately.
-In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$.
-\TODO{shorten and add multicut energy def, define HC abbrv.}
+% Some approaches directly compute $\cost_e$, whereas others compute $w_e^+$ and $w_e^-$ separately.
+% In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$.
 
-\begin{itemize}
-\item Given a linkage $\interact{}$, we say that Algorithm \ref{main_alg} is invariant to a $\alpha$ weight-shift, if by changing all edge weights of the graphs by a constant $w_e+\alpha$ the structure of the hierarchical tree  does not change and defines the same function $d_T$.
-\item \TODO{Why do we care?} MC does not return nested/hierarchical solutions when shifting weights.
-Which of these algorithms behave the same, or, somehow are more related to correlation clustering?
-So, actually, we care more about the shifted-solutions being nested, and not really about the fact that the hierarchy tree built by the algorithm stays the same.
-Is this somehow equivalent...?
-\end{itemize}
+\textbf{Multicut objective} -- We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{S\in\Pi} S $, $\,S \cap S' = \emptyset$ for different clusters $S, S'\in \Pi$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
+For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^0_\Pi= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u,v \in S \}$ the set of edges linking nodes in the same cluster, and as $E_\Pi^1= E \setminus E^0_\Pi$ the set of edges whose linked nodes belong to distinct clusters.
+% \begin{equation}
+% E_\Pi^0 \equiv \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \qquad E^1_\Pi \equiv E \setminus E^0_\Pi.
+% \end{equation}
+% \begin{align}
+% E_\Pi^0 &= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \\
+% E^1_\Pi &= E \setminus E^0_\Pi.
+% \end{align}
+The set of edges $E_\Pi^1$ is known as the \emph{multicut} of $\mathcal{G}$ associated to clustering $\Pi$.
+The instance of the NP-hard \emph{minimum cost multicut problem} w.r.t.
+$\mathcal{G}(V,E,w_e)$ is the task of finding a clustering that optimally balance the attraction and repulsion in the graph and is given by the following binary integer program:
+\begin{equation}
+% \min_\Pi \texttt{MC}(\Pi) \equiv
+ \min_\Pi \sum_{e\in E} \cost_e x_e^\Pi,  \qquad \text{where} \quad x^\Pi_e = 
+ \begin{cases} 
+ 1 & \text{if } e\in E^1_\Pi \\
+ 0 & \text{otherwise}.
+ \end{cases}
+\end{equation}
+% In the next chapters we will use this objective as a way to measure how balanced is a clustering found by the tested agglomerative clustering algorithms.
 
-\textbf{Inter-cluster interaction } We call two clusters $S_u,S_v$ \emph{adjacent} if there exists at least one edge ${e_{ts}\in E}$ connecting a node $t\in S_u$ to a node $s\in S_v$.
-Let the interaction $\interact(S_u,S_v)$ between the two clusters be defined as a function $\interact{}:\Pi \times \Pi \rightarrow \mathbb{R}$, \TODO{Remove $\Pi$ from def.
-Problem of zero interactions} named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S_u$ and $S_v$, i.e.
-$(S_u \times S_v) \cap E$.
-All the linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
+\textbf{Weight-shift hierarchical algorithms} -- Given an algorithm that outputs a clustering $\Pi$ for a signed graph $\mathcal{G}(V,E,w_e)$, we call the algorithm \emph{weight-shift hierarchical} if, by adding a constant $\alpha \in \mathbb{R}$ to all edge weights $w_e$, the algorithm outputs a clustering $\Pi'$ which is a coarsening of $\Pi$ when $\alpha>0$ and a refinement of $\Pi$ when $\alpha<0$\footnote{A clustering $\Pi'$ is a coarsening of $\Pi$ when every $S' \in \Pi'$ is the union of one or more clusters in $\Pi$.
+Similarly, $\Pi'$ is a refinement of $\Pi$ when every $S \in \Pi$ is given by the union of one or more clusters in $\Pi'$}.
+
+\textbf{Linkage criteria and hierarchical trees} -- 
+% We also denote as $S_u$ the cluster associated with node $u$ \TODO{Needed?}.
+% We call two clusters $S,S'$ \emph{adjacent} if there exists at least one edge ${e_{ts}\in E}$ connecting a node $t\in S_u$ to a node $s\in S_v$. 
+Let the interaction $\interact(S,S')$ between two clusters $S,S'$ be defined as a function $\interact{}:2^{V} \times 2^{V} \rightarrow \mathbb{R}$, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S$ and $S'$, i.e.
+${(S \times S') \cap E}$.
+The linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
+In hierarchical clustering (HC) literature,  a \emph{dendrogram} $T$ is a rooted binary tree\footnote{In general, one could look at trees that are not binary.
+However, the algorithms discussed in this paper always generate binary hierarchical trees, so nothing would be gained by this generalization.} representing the merging order of an agglomerative algorithm, such that the leaves of the tree are in one-to-one correspondence with $V$.
+Let $T_{\mathrm{R}},T_{\mathrm{L}}\subset T$ denote the subtrees rooted at the two children of the root node in $T$.
+For any two leaves $u,v \in V$, let $T[u \vee v]$ be the subtree rooted at the least common ancestor $u \vee v\in T$ of nodes $u$ and $v$ (furthest from the root), and let \texttt{leaves}$(T[u \vee v])\subseteq V$ be the set of leaves of this subtree.
+% \TODO{Here we talk about the algorithm already, so we could move it to next section and the flow could be better. But we need a tree in the alg. So we better do this later}
+% Algorithm \ref{main_alg} returns a binary tree denoted by $T^*$.
+Given an agglomerative algorithm with merging tree $T$, let $h_T:T \rightarrow \mathbb{N}$ denote the \emph{dendrogram-height} of each $(u\vee v)\in T$, which is defined as the iteration number at which nodes $u,v\in V$ were merged (\TODO{Fig.~1}).
+We also define the interaction $\treeHeight(u,v)$ as the interaction $\interact{}(S,S')$ between the two clusters $S,S'$ that were merged at iteration $h_T(u\vee v)$:
+% Then, given a binary tree $T$ and a linkage criterion $\interact$, we can associate a \emph{signed similarity} function $\treeHeight$ to each pair of distinct original nodes $u\neq v$, with $u, v \in V$:
+\begin{equation}\label{eq:def_dendr_interact}
+\treeHeight(u,v) \equiv \interact{} \big( \text{\texttt{leaves}}(T_{\mathrm{R}}[u \vee v]), \text{\texttt{leaves}}(T_{\mathrm{L}}[u \vee v]) \big)
+\end{equation}
+% \OPTIONAL{In other words, $h_T(u,v)$ and $\treeHeight(u,v)$ represent the \emph{dendrogram-height} and \emph{signed-interaction} associated to each $u \vee v$ node in the tree $T$ (see toy example in \TODO{Fig.~1}).}
 
@@
 
-\subsection{\algname{}: generalized algorithm for signed graph partitioning} \label{sec:algorithm}
+\subsection{\algname{}: generalized agglomerative algorithm for signed graph partitioning} \label{sec:algorithm}
 
-\TODO{Update description to new pseudocode} In Algorithm \ref{main_alg}, we provide simplified pseudo-code for the proposed \algname{} algorithm.
+Our main contribution is a generalized agglomerative algorithm for signed graph partitioning (GASP) that generalizes hierarchical clustering (HC) to signed graphs. 
+The framework, defined in the following, encompasses several known and new agglomerative algorithms on display in Table \ref{tab:linkage-criteria}, which are differentiated by the linkage criterion employed, similarly to HC.
+
+\paragraph*{GASP Algorithm} -- In Algorithm \ref{main_alg}, we provide simplified pseudo-code for the proposed \algname{} algorithm.
 \algname{} implements a bottom-up approach that starts by assigning each node to its own cluster and then iteratively merges pairs of adjacent clusters.
-The algorithm has two variants.
-The first one (option \emph{addCannotLinkConstraints} is \texttt{False}) starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual repulsive interactions (see iterations on toy graphs in block 4 of Fig.\ \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}).
-After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.
+The algorithm proceeds in three phases.
+In \emph{Phase~One}, \algname{} selects the pair of clusters with the highest absolute interaction $|\interact(S, S')|$, so that the most attractive and the most repulsive pairs are analyzed first.
+If the interaction is repulsive and the algorithm option \emph{addCannotLinkConstraints} is \texttt{True}, then the two clusters are constrained so that their members can never merge in subsequent steps of \emph{Phase~One}.
+If the interaction is attractive, then the clusters are merged, provided that they were not previously constrained.
+After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S, S')$ listed in Table \ref{tab:linkage-criteria}.
+\emph{Phase~One} terminates when all the remaining clusters are either constrained or share repulsive interactions.
+In \emph{Phase~Two}, the algorithm removes all the constraints previously introduced in \emph{Phase~One} and merges the remaining clusters that share an attractive interaction, starting from those with the most attractive ones\footnote{Note that in the version of \algname{} with \emph{addCannotLinkConstraints} set to \texttt{False}, nothing happens in \emph{Phase~Two}.}.
+The final \algname{} clustering $\Pi^*$ is returned at the end of \emph{Phase~Two} and it will then be composed of clusters sharing only mutual repulsive interactions.
+Finally, in \emph{Phase~3}, the algorithm keeps merging all clusters until only a single one is left, so that the full sequence of merging steps is also returned in the form of a hierarchical tree $T^*$.
 
-In the second variant (option \emph{addCannotLinkConstraints} is \texttt{True}), Algorithm \ref{main_alg} also introduces cannot-link constraints, which represent mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering.
-This variant
-selects the pair of clusters with the highest absolute interaction $|\interact(S_u, S_v)|$, so that the most attractive and the most repulsive pairs are analyzed first (see example in Fig.\ \ref{subfig:with_constraints}).
-If the interaction is repulsive, then the two clusters are constrained and its members can never merge in subsequent steps.
-If the interaction is attractive, then the clusters are merged, provided that they were not previously constrained.
-The algorithm terminates when all the remaining clusters are constrained.
+The algorithm was implemented using a standard HC implementation with computational complexity $\mathcal{O}(N^2 \log N)$ (see Appendix \ref{sec:detailed_impl} for more details). 
+\TODO{mention fact that constraints make algorithm slower?}
 
-In Appendix \ref{sec:detailed_impl}, we comment on the algorithm's computational complexity $\mathcal{O}(N^2 \log N)$ and present our implementation given by the edge contraction Algorithm \ref{detailed_alg} based on a \emph{disjoint set data structure} and a \emph{priority queue}.
+% , we comment on the algorithm's computational complexity $\mathcal{O}(N^2 \log N)$ and present our implementation given by the edge contraction Algorithm \ref{detailed_alg} based on a \emph{disjoint set data structure} and a \emph{priority queue}.
 
@@
       \Repeat 
-        \State Pop $S_u,S_v\in\Pi$ from $PQ$ with highest interaction $|\interact{}(S_u,S_v)|$
-        \If{\big[{\color{green}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ \textbf{not} constrained\big]}
-          \State Merge clusters $S_u$, $S_v$ and update hierarchical tree $T$
+        \State Pop $S,S'\in\Pi$ from $PQ$ with highest interaction $|\interact{}(S,S')|$
+        \If{\big[{\color{green}\textbf{$\interact{}(S,S') > 0$}}\big] \textbf{and} \big[$S,S'$ \textbf{not} constrained\big]}
+          \State Merge clusters $S$, $S'$ and update hierarchical tree $T$
           \State Update interactions \& constraints with neighboring clusters
-        \ElsIf{{\color{blue}addCannotLinkConstr} \textbf{and}  \big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big]}
-          \State Add CannotLink Constraint between $S_u$ and $S_v$
+        \ElsIf{{\color{blue}addCannotLinkConstr} \textbf{and}  \big[{\color{red}\textbf{$\interact{}(S,S') \leq 0$}}\big]}
+          \State Add CannotLink Constraint between $S$ and $S'$
         \EndIf
@@
       % \If{{\color{blue}addCannotLinkConstr}} % \Comment{Step 2: release constraints}
-      \State \emph{// Phase 2: Relax constraints \& merge remaining positive interactions}
-      \State Push signed interactions $\interact{}(S_u,S_v)$ to PQ, $\forall S_u, S_v \in \Pi$
+      \State \emph{// Phase 2: Remove constraints \& merge all positive interactions}
+      \State Push signed interactions $\interact{}(S,S')$ to PQ, $\forall S, S' \in \Pi$
       \Repeat 
-        \State Pop $S_u,S_v\in\Pi$ from $PQ$ with highest interaction $\interact{}(S_u,S_v)$
-        \If{\big[{\color{green}\textbf{$\interact{}(S_u,S_v) > 0$}}\big]}
-          \State Merge clusters $S_u$, $S_v$ and update hierarchical tree $T$
+        \State Pop $S,S'\in\Pi$ from $PQ$ with highest interaction $\interact{}(S,S')$
+        \If{\big[{\color{green}\textbf{$\interact{}(S,S') > 0$}}\big]}
+          \State Merge clusters $S$, $S'$ and update hierarchical tree $T$
           \State Update interactions with neighboring clusters
         \EndIf
-      \Until{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big]} 
+      \Until{\big[{\color{red}\textbf{$\interact{}(S,S') \leq 0$}}\big]} 
       \State Save the final clustering $\Pi^* \gets \Pi$ 
@@
       \Repeat
-        \State Pop $S_u,S_v\in\Pi$ from $PQ$ with highest interaction $\interact{}(S_u,S_v)$
-        \State Merge clusters $S_u$, $S_v$ and update hierarchical tree $T$
+        \State Pop $S,S'\in\Pi$ from $PQ$ with highest interaction $\interact{}(S,S')$
+        \State Merge clusters $S$, $S'$ and update hierarchical tree $T$
         \State Update interactions with neighboring clusters
@@
 
-\paragraph{Hierarchical trees and ultrametrics} In HC literature,  a \emph{dendrogram} $T$ is a rooted binary tree\footnote{In general, one could look at trees that are not binary.
-However, the algorithms discussed in this paper always generate binary hierarchical trees, so nothing would be gained by this generalization.} representing the merging order of an agglomerative algorithm, such that the leaves of this tree are in one-to-one correspondence with $V$.
-Let $T_{\mathrm{R}},T_{\mathrm{L}}\subset T$ denote the subtrees rooted at the two children of the root node in $T$.
-For any two leaves $u,v \in V$, let $T[u \vee v]$ be the subtree rooted at the least common ancestor of $u$ and $v$ (furthest from the root), and let \texttt{leaves}$(T[u \vee v])\subseteq V$ be the set of leaves of this subtree.
-% \TODO{Here we talk about the algorithm already, so we could move it to next section and the flow could be better. But we need a tree in the alg. So we better do this later}
-Algorithm \ref{main_alg} returns a binary tree denoted by $T^*$.
-For each pair of distinct leaves $u,v$, we can then assign a \emph{depth} \TODO{better name?} to their least common ancestor node in $T^*$ defined by the interaction between clusters $S_u$ and $S_v$, when $u$ and $v$ were merged: \TODO{See trees on toy graphs in Fig.
-1}
-% Then, given a binary tree $T$ and a linkage criterion $\interact$, we can associate a \emph{signed similarity} function $\treeHeight$ to each pair of distinct original nodes $u\neq v$, with $u, v \in V$:
-\begin{equation}
-\treeHeight(u,v) \equiv \interact{} \big( \text{\texttt{leaves}}(T^*_{\mathrm{R}}[u \vee v]), \text{\texttt{leaves}}(T^*_{\mathrm{L}}[u \vee v]) \big)
-\end{equation}
-
-The connection between hierarchical trees and ultrametrics is well known\footnote{A metric space $(X,d)$ is an \emph{ultrametric} if for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.}. 
-We now want to use the \emph{depth-measure} $\treeHeight{}$ to define an ultrametric on the graph.  
-Normally, ultrametrics are associated to strictly positive \emph{similarity} or \emph{dissimilarity} measures on a graph. Thus, we first need to map $\treeHeight{}$ to positive values:
-\begin{align}
-d_{T^*}(u,v)\equiv &\begin{cases}
+\paragraph{Ultrametrics defined by \algname{}} -- The connection between HC and ultrametrics\footnote{A metric space $(X,d)$ is an \emph{ultrametric} if for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.} is well known \cite{johnson1967hierarchical,milligan1979ultrametric}.
+Normally, ultrametrics are associated to strictly positive \emph{similarity} or \emph{dissimilarity} measures on a graph.
+Here, we generalize this concept to signed graphs.
+To do so, we first map the signed interaction $\treeHeight{}$ defined in Eq.~\ref{eq:def_dendr_interact} to positive ``distances'' $d_{T}:V \times V \rightarrow \mathbb{R}^{+}$:
+\begin{align}\label{eq:UM_def}
+d_{T}(u,v)\equiv &\begin{cases}
 0 & \text{if}\,\, u=v\\
@@
 \end{cases}\quad \forall u,v\in V\\
-\mathrm{where}& \quad  M \equiv \max_{u',v'\in V,\,u'\neq v'}\treeHeight(u',v').
+\mathrm{where}& \quad  M \equiv  \epsilon + \max_{u',v'\in V,\,u'\neq v'}\treeHeight(u',v')
 \end{align}
-By definition, we have that  $d_{T^*}: V \times V \rightarrow \mathbb{R}^{+}$, $d_{T^*}(u,v)=d_{T^*}(v,u)$, and $d_{T^*}(u,u)= 0$.
-Thus, to prove that $(V, d_{T^*})$ is an ultrametric, we only need to prove that
+and where $\epsilon > 0$. By definition, we have that $d_{T}(u,v)=d_{T}(v,u)$ and $d_{T}(u,u)= 0$. We then prove the following two propositions (proofs are left in Appendix):
+\begin{prop}
+Consider a graph $\mathcal{G}(V,E,w_e)$, a linkage criteria $\interact{}$, and an AC algorithm returning a binary rooted tree $T$ with height $h_T$.
+The quantity $(V, d_{T})$ defined in Eq.~\ref{eq:UM_def} is an ultrametric iff, $\forall u,v,t \in V$:
 \begin{equation}
-\interact{}_{T^*}(u,v) \geq \min \{\interact{}_{T^*}(u,t), \interact{}_{T^*}(v,t)\}
+\interact{}_{T}(u,v) > \interact{}_{T}(u,t) \Leftrightarrow h_T(u \vee v) < h_T[u \vee t] 
 \end{equation}
- for every distinct $u,v,t\in V$.
-In other words, given two leaves nodes $u,v\in V$, the depth $\interact{}_{T^*}(u,v)$ associated to their least common ancestor $i\in T^*$ should be both lower than the depth of any $i$-descendant node in $T^*$ and higher than any $i$-ancestor node in $T^*$:
- % that have the most positive interaction   two clusters merged by the algorithm will always have an interaction that is more negative as compared to all clusters already merged and more positive than all clusters that will be merged at later iterations of the algorithm.
-\begin{equation}
-\interact{}_{T^*}(u,v) \geq \interact{}_{T^*}(u,t) \Leftrightarrow T^*[u \vee t] \subseteq T^*[u \vee v] 
-\end{equation}
- This happens only if, at every iteration, Algorithm \ref{main_alg} merges pairs of clusters with lower and lower interactions, which is true for only certain choices of linkage criteria.
-%In the next section \ref{sec:alg_update_rules}, we will show that this happens only for certain linkages and only when constraints are not enforced
+In words, $(V, d_{T})$ is an ultrametric iff the interaction $\interact{}_{T}(u, v)$ associated to the least common ancestor ${(u\vee v)\in T}$ is both lower than any other $(u\vee v)$-descendant node and higher than any other $(u\vee v)$-ancestor node in the tree $T$.
+\end{prop}
+\begin{prop}
+Consider the binary rooted tree $T^*$ returned by the \algname{} Algorithm~\ref{main_alg}, given a choice of linkage criteria $\interact{}$ and the use of CannotLinkConstraints.
+Then, the quantity $(V, d_{T^*})$ defined in Eq.~\ref{eq:UM_def} is an ultrametric only for the combinations of linkage and CannotLinkConstraints marked with $(\dagger)$ in Table~\ref{tab:linkage-criteria}.
+\end{prop}
 
@@
 
-\TODO{Specify greediness wrt multicut energy, ultrametric properties, and shift-invariance properties} Our main contribution is the generalized algorithm for signed graph partitioning, GASP, that encompasses several known and new agglomerative algorithms on display in Table \ref{tab:linkage-criteria}.
-In our framework, individual algorithms are differentiated by the linkage criterion employed. We review them in the following paragraphs.
+% \begin{prop} 
+% The Mutex Watershed Algorithm (MWS) introduced by \cite{wolf2018mutex} and with empirical $\mathcal{O}(N \log N)$ complexity outputs the same clustering $\Pi^*$ returned by  the \algname{} Algorithm \ref{main_alg} with the use of cannot-link constraints and an Absolute Maximum update rule:
+% \begin{equation}\label{eq:def_abs_max}
+% f_{\mathrm{Abs.Max.}}(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
+%             \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
+%             \tilde{\cost}_2 & \text{otherwise}
+%              \end{cases} 
+% \end{equation}
+% \end{prop}
+\begin{prop} 
+The \algname{} Algorithm \ref{main_alg} with Absolute Maximum linkage (see def.
+in Table \ref{tab:linkage-criteria}) returns the same final clustering $\Pi^*_{\mathrm{AbsMax}}$ whether cannot-link constraints are introduced or not.
+In particular, $\Pi^*_{\mathrm{AbsMax}}$ is equal to the clustering returned by the Mutex Watershed Algorithm (MWS) introduced by \cite{wolf2018mutex}, which has empirical complexity $\mathcal{O}(N \log N)$.
+\end{prop}
+
+\begin{itemize}
+\item Table \ref{tab:linkage-criteria} lists new and existing algorithms.
+Better: we test the five linkage criteria (columns of Table~\ref{tab:linkage-criteria}).
+Many more have been applied to unsigned graphs (CITS), but those five linkages represent the most common options.
+\item GASP with Average, Single, and Complete linkage criteria is equivalent to HC when a graph with only positive edges is considered
+\item These three criteria have been throughly studied on (positive) similarity graphs
+\item As it was already observed in CITE, we have the following observation:
+\item GASP with Average, Single, and Complete linkage criteria
+
+\item It can be shown that the correlation clustering or multicut problem is not \emph{intrinsically-hierarchical}.
+Similarly, only few of the algorithms presented in this paper are \emph{intrinsically-hierarchical}
+% \item Only few of the Given a linkage $\interact{}$, we say that Algorithm \ref{main_alg} is invariant to a $\alpha$ weight-shift, if by changing all edge weights of the graphs by a constant $w_e+\alpha$ the structure of the hierarchical tree  does not change and defines the same function $d_T$.
+% \item \TODO{Why do we care?} MC does not return nested/hierarchical solutions when shifting weights.
+Which of these algorithms behave the same, or, somehow are more related to correlation clustering?
+So, actually, we care more about the shifted-solutions being nested, and not really about the fact that the hierarchy tree built by the algorithm stays the same.
+Is this somehow equivalent...?
+\end{itemize}
+
+\TODO{Specify greediness wrt multicut energy, ultrametric properties, and shift-invariance properties}  We review them in the following paragraphs.
 
@@
     \begin{subtable}[t!]{\textwidth}\centering
-        \begin{tabular}{c | c  c  c  c  c}
-        \multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} \\ $\,\,\interact(S_u ,S_v)$}}  & Sum & Absolute Maximum & Average & Maximum & Minimum \\
+        \begin{tabular}{l |c  c  c  c  c}
+        % \multicolumn{1}{c}{}
+        % \multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} \\ $\,\,\interact(S_u ,S_v)$}}  
+        & \thead{Sum\\Linkage} & \thead{Absolute Maximum\\Linkage} & \thead{Average\\Linkage} & \thead{Single\\Linkage} & \thead{Complete\\Linkage} \\
+ % \multicolumn{1}{c}{} 
  & $\displaystyle \sum_{e\in E_{uv}} \cost_e$  & $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$ & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big| $ &  $\displaystyle \max_{e\in E_{uv}} \cost_e$ & $\displaystyle \min_{e\in E_{uv}} \cost_e$ \\ \midrule
+ % \cmidrule{2-6}
 
-            \thead{\textbf{Unsigned Graphs}} & \thead{HC-Sum-Link} &\thead{HC-Single-Link\\$(\dagger,\ddagger)$} &\thead{HC-Avg-Link\\$(\dagger,\ddagger)$} &\thead{HC-Single-Link\\$(\dagger,\ddagger)$} &\thead{HC-Complete-Link\\$(\dagger,\ddagger)$} \\
-            \thead{\textbf{Signed Graphs} \\\textbf{Without Constraints}} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Mutex Watershed \cite{wolf2018mutex}\\$(\dagger)$}& \thead{HC-Avg-Link\\$(\dagger,\ddagger)$} &\thead{HC-Single-Link\\$(\dagger,\ddagger)$} &\thead{HC-Complete-Link\\$(\dagger,\ddagger)$} \\
-            \thead{\textbf{Signed Graphs} \\\textbf{With Constraints}} & \thead{Constr-Sum-Link\\(\textbf{NEW})} % \thead{Greedy Fixation \cite{levinkov2017comparative}} 
-            & \thead{Mutex Watershed \cite{wolf2018mutex}\\$(\dagger)$}& \thead{Constr-Avg-Link\\(\textbf{NEW})} &  \thead{Constr-Single-Link\\(\textbf{NEW})} &  \thead{Constr-Complete-Link\\(\textbf{NEW})} \\
+            \thead[r]{GASP on positive-weighted graphs} & \thead{-} &\thead{\emph{\textbf{HC-Single}}} &\thead{\emph{\textbf{HC-Avg}}} &\thead{\emph{\textbf{HC-Single}}} &\thead{\emph{\textbf{HC-Complete}}} \\
+            \thead[r]{GASP on signed graphs} & \thead{GAEC \cite{keuper2015efficient}} & \thead{\emph{Mutex Watershed} \cite{wolf2018mutex}}& \thead{\emph{\textbf{HC-Avg}}} &\thead{\emph{\textbf{HC-Single}}} &\thead{\emph{\textbf{HC-Complete}}} \\
+            \thead[r]{GASP on signed graphs + constraints} & \thead{\colorbox{yellow}{HCC-Sum}} % \thead{Greedy Fixation \cite{levinkov2017comparative}} 
+            & \thead{\emph{Mutex Watershed} \cite{wolf2018mutex}}& \thead{\colorbox{yellow}{HCC-Avg}} &  \thead{\colorbox{yellow}{HCC-Single}} &  \thead{\colorbox{yellow}{HCC-Complete}} \\
             % \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
@@
     \end{subtable} 
-    \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning, \algname{}, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
-The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e.
-$E_{uv}=(S_u \times S_{v \neq u}) \cap E$.
-\TODO{$\dagger$ if the linkage defines ultrametric and $\ddagger$ if it defines a weight-shift invariant algorithm} }
+    \caption{Existing and new (highlighted in yellow) clustering algorithms that can be reformulated as special cases of the proposed generalized agglomerative algorithm for signed graph partitioning, \algname{}, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
+Given two clusters $S_i$ and $S_j$, the set $E_{ij}$ is defined as the set of all edges connecting the two cluster, i.e.
+$E_{ij}=(S_i \times S_{j}) \cap E$.
+\TODO{Algorithm in italic define an ultrametric; algorithms in bold are weight-shift hierarchical; new ones are highlighted in yellow} }
     \label{tab:linkage-criteria}
@@
 \end{figure*}
+
+\begin{table*}[t]
+    \centering
+    % \scriptsize
+    \tiny
+    \begin{subtable}[t!]{\textwidth}\centering
+        \begin{tabular}{l  c  c  c  c  c c c c c c c c c}
+        \toprule
+        Dataset & Graph-Type & $\#I$ & $|V|$ & $\bar{\text{deg}}(v)$ & GT & GAEC & MWS & HC-AvgL & HC-SingleL & HC-CompleteL & Constr-SumL & Constr-AvgL & Constr-SingleL \\ \midrule
+        \emph{Image Seg.} & \emph{rag} & 100 & 156-3764 &   & \HollowBox\\
+        \emph{Knott-3D (150-300-450)} & \emph{rag-3D} & 24 & 572-17k &  & \HollowBox\\
+        % \emph{Knott-3D-300} & \emph{rag-3D} & 8& & & \HollowBox\\
+        % \emph{Knott-3D-450}& \emph{rag-3D} & 8 & & & \HollowBox\\  
+        \emph{CREMI-OurUNet} & \emph{rag-3D} & 3&  & & \CrossedBox\\ 
+        \emph{Fruit-Fly Level 1-4} & \emph{rag-3D} & 4& 5m-11m &  & \HollowBox\\
+        \emph{Fruit-Fly Level Global} & \emph{rag-3D} & 1& 90m &  & \HollowBox\\ \midrule
+                \emph{CREMI-pixGrid-OurUNet} & \emph{gridGraph} & 12& $\sim$30m & 4 & \CrossedBox\\
+        % \emph{(CREMI-pixGrid-LSIMasksUNet)} & \emph{gridGraph} & 1 & & 4 & \CrossedBox\\
+        \emph{(CityScapesValidation-pixGrid)} & \emph{gridGraph} &  &  & & \CrossedBox\\\midrule
+        % \emph{CREMI-test....}\\\midrule
+        \emph{Stochastic Block Model (synthetic)} & \emph{non-planar} &-&- & - & \CrossedBox \\
+        \emph{Mod. Clustering} & \emph{complete} & 6& 34-115 & 33-114 & \HollowBox\\ 
+        \emph{(epinions and slashdot?)} & \emph{dense?} &  & & & \HollowBox\\
+
+        \end{tabular}
+    \end{subtable} 
+    \caption{List of used datasets and MC objectives achieved by different algorithms} 
+    \label{tab:datasets_and_energies}
+\end{table*}
+
+% \begin{table}[t]
+%     \centering
+%     % \scriptsize
+%     \tiny
+%     \begin{subtable}[t!]{0.5\textwidth}\centering
+%         \begin{tabular}{l  c  c  c  c  c}
+%         \toprule
+%         Dataset & HC-Avg & GAEC & MWS & Constr-Avg & Constr-Sum \\ \midrule
+%         \emph{Image Seg.} \\
+%         \emph{Knott-3D-150} \\
+%         \emph{Knott-3D-300} \\
+%         \emph{Knott-3D-450} \\  
+%         \emph{Mod. Clustering} \\
+%         \emph{Fruit-Fly Level 1-4} \\
+%         \emph{Fruit-Fly Level Global} \\
+%         \emph{(Epinions?)} \\
+
+%         \end{tabular}
+%     \end{subtable} 
+%     \caption{} 
+%     \label{tab:all_results}
+% \end{table}

### 2021-02-19 chapters/supplementary.tex
Add first version of new alg. and binary tree formulation
Several changes to alg. descr and linkages

@@
         \State \textbf{assert} \texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$) \Comment{Edges in PQ always link nodes in different clusters}
-        \If{({\color{ForestGreen}\textbf{$\tilde{w} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
+        \If{({\color{green}\textbf{$\tilde{w} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
           \State PQ, \texttt{canBeMerged}, $\tilde{E}$ $\gets$ \textsc{UpdateNeighbors}($u,v$)
@@
         \If{\texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$)} \Comment{Check if $u,v$ are already in the same cluster}
-          \If{({\color{ForestGreen}\textbf{$w_e > 0$}}) \textbf{and} \texttt{canBeMerged}($u,v$)}  \Comment{Check for cannot-link constraints}
+          \If{({\color{green}\textbf{$w_e > 0$}}) \textbf{and} \texttt{canBeMerged}($u,v$)}  \Comment{Check for cannot-link constraints}
             \State \texttt{UF}.merge($u,v$) and inherit constraints of parent clusters
@@
 Due to this fact, we chose different smoothing parameters to generate the noise in different directions.
+\TODO{Give these smoothing parameters...}
 
@@
 For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
-\begin{figure}[t]
+\begin{figure*}[t]
 \centering
@@
     \label{fig:noisy_affs}
-\end{figure}
+\end{figure*}
 \begin{table}
@@
 The semantic categories are assigned to each instance in the same way proposed by \cite{liu2018affinity}, i.e. with a majority vote based on the semantic output of the model.
+
+\subsection{Ultrametrics} 
+Thus, to prove that $(V, d_{T})$ is an ultrametric, we only need to prove that
+\begin{equation}
+\interact{}_{T}(u,v) \geq \min \{\interact{}_{T}(u,t), \interact{}_{T}(v,t)\}
+\end{equation}
+ for every distinct $u,v,t\in V$.
+In other words, given two leaves nodes $u,v\in V$, the depth $\interact{}_{T}(u,v)$ associated to their least common ancestor $i\in T$ should be both lower than the depth of any $i$-descendant node in $T$ and higher than any $i$-ancestor node in $T$:
+ % that have the most positive interaction   two clusters merged by the algorithm will always have an interaction that is more negative as compared to all clusters already merged and more positive than all clusters that will be merged at later iterations of the algorithm.
+\begin{equation}
+\interact{}_{T}(u,v) \geq \interact{}_{T}(u,t) \Leftrightarrow T[u \vee t] \subseteq T[u \vee v] 
+\end{equation}
+ This happens only if, at every iteration, Algorithm \ref{main_alg} merges pairs of clusters with lower and lower interactions, which is true for only certain choices of linkage criteria.
+%In the next section \ref{sec:alg_update_rules}, we will show that this happens only for certain linkages and only when constraints are not enforced

### 2021-02-19 chapters/3_algorithm.tex
Polish new theory section

@@
 $\mathcal{G}(V,E,w_e)$ is the task of finding a clustering that optimally balance the attraction and repulsion in the graph and is given by the following binary integer program:
-\begin{equation}
+\begin{equation}\label{eq:MC_objective}
 % \min_\Pi \texttt{MC}(\Pi) \equiv
@@
 % In the next chapters we will use this objective as a way to measure how balanced is a clustering found by the tested agglomerative clustering algorithms.
-
-\textbf{Weight-shift hierarchical algorithms} -- Given an algorithm that outputs a clustering $\Pi$ for a signed graph $\mathcal{G}(V,E,w_e)$, we call the algorithm \emph{weight-shift hierarchical} if, by adding a constant $\alpha \in \mathbb{R}$ to all edge weights $w_e$, the algorithm outputs a clustering $\Pi'$ which is a coarsening of $\Pi$ when $\alpha>0$ and a refinement of $\Pi$ when $\alpha<0$\footnote{A clustering $\Pi'$ is a coarsening of $\Pi$ when every $S' \in \Pi'$ is the union of one or more clusters in $\Pi$.
-Similarly, $\Pi'$ is a refinement of $\Pi$ when every $S \in \Pi$ is given by the union of one or more clusters in $\Pi'$}.
 
@@
 
-\paragraph*{GASP Algorithm} -- In Algorithm \ref{main_alg}, we provide simplified pseudo-code for the proposed \algname{} algorithm.
+In Algorithm \ref{main_alg}, we provide simplified pseudo-code for the proposed \algname{} algorithm.
 \algname{} implements a bottom-up approach that starts by assigning each node to its own cluster and then iteratively merges pairs of adjacent clusters.
 The algorithm proceeds in three phases.
+
 In \emph{Phase~One}, \algname{} selects the pair of clusters with the highest absolute interaction $|\interact(S, S')|$, so that the most attractive and the most repulsive pairs are analyzed first.
@@
 \emph{Phase~One} terminates when all the remaining clusters are either constrained or share repulsive interactions.
+
 In \emph{Phase~Two}, the algorithm removes all the constraints previously introduced in \emph{Phase~One} and merges the remaining clusters that share an attractive interaction, starting from those with the most attractive ones\footnote{Note that in the version of \algname{} with \emph{addCannotLinkConstraints} set to \texttt{False}, nothing happens in \emph{Phase~Two}.}.
 The final \algname{} clustering $\Pi^*$ is returned at the end of \emph{Phase~Two} and it will then be composed of clusters sharing only mutual repulsive interactions.
+
 Finally, in \emph{Phase~3}, the algorithm keeps merging all clusters until only a single one is left, so that the full sequence of merging steps is also returned in the form of a hierarchical tree $T^*$.
-
 The algorithm was implemented using a standard HC implementation with computational complexity $\mathcal{O}(N^2 \log N)$ (see Appendix \ref{sec:detailed_impl} for more details). 
@@
 
-\paragraph{Ultrametrics defined by \algname{}} -- The connection between HC and ultrametrics\footnote{A metric space $(X,d)$ is an \emph{ultrametric} if for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.} is well known \cite{johnson1967hierarchical,milligan1979ultrametric}.
+\subsection{New and existing algorithms included in \algname{}} \label{sec:alg_update_rules}
+
+% \begin{prop} 
+% The Mutex Watershed Algorithm (MWS) introduced by \cite{wolf2018mutex} and with empirical $\mathcal{O}(N \log N)$ complexity outputs the same clustering $\Pi^*$ returned by  the \algname{} Algorithm \ref{main_alg} with the use of cannot-link constraints and an Absolute Maximum update rule:
+% \begin{equation}\label{eq:def_abs_max}
+% f_{\mathrm{Abs.Max.}}(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
+%             \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
+%             \tilde{\cost}_2 & \text{otherwise}
+%              \end{cases} 
+% \end{equation}
+% \end{prop}
+In this paper we focus on five linkage criteria (see columns of Table~\ref{tab:linkage-criteria}).
+Many more linkage criteria have been applied to unsigned graphs \cite{nunez2013machine,felzenszwalb2004efficient,funke2018large}, but we decided to focus our experiments on those five because they represent the most common choices.
+
+\paragraph{Sum Linkage} -- 
+An agglomerative algorithm with sum linkage does only make sense for graphs with signed edge weights, because only for these graphs the sum of two attractive (or repulsive) interactions is still attractive (repulsive).
+On positive weighted graphs, on the other hand, a strong attractive interaction could be obtained by summing many weak interactions, which is not desirable.
+Such an algorithm was pioneered in \cite{levinkov2017comparative,keuper2015efficient} and was named Greedy Agglomerative Edge Contraction (GAEC)\footnote{An algorithm equivalent to GAEC was recently independently re-proposed in \cite{chehreghani2020hierarchical}.}.
+All variations of \algname{} decrease the multicut objective defined in Eq.~\ref{eq:MC_objective} each time two clusters with positive interaction are merged.
+But only GAEC always makes the \emph{greedy-choice} that will mostly decrease the multicut objective at every step.
+The authors of \cite{levinkov2017comparative} also proposed a version of GAEC with cannot-link constraints named \emph{GreedyFixation}, but the constrained sum-link version of \algname{} proposed here (named \emph{HCC-Sum} in Table~\ref{tab:linkage-criteria}) did perform better in our experiments.
+
+\paragraph{AbsMax Linkage} -- This linkage method is also specific to signed graphs, since on positive-weighted graphs it would be equivalent to single linkage.
+Here, we prove that the AbsMax-version of \algname{} was already introduced in the literature (see proof in Appendix):
+\begin{prop} 
+The \algname{} Algorithm \ref{main_alg} with AbsMax linkage (see def.
+in Table \ref{tab:linkage-criteria}) returns the same final clustering $\Pi^*_{\mathrm{AbsMax}}$ whether or not cannot-link constraints are introduced.
+In particular, $\Pi^*_{\mathrm{AbsMax}}$ is equal to the clustering returned by the Mutex Watershed Algorithm (MWS) introduced by \cite{wolf2018mutex}, which has empirical complexity $\mathcal{O}(N \log N)$.
+\end{prop}
+
+\paragraph{Average, Single, and Complete Linkage} -- These three linkage criteria have been throughly studied on positive-weighted graphs.
+In \cite{chehreghani2020hierarchical}, the authors proved that applying these three linkage methods to a signed graph is equivalent to applying them to the positive-weighted graph obtained by shifting all edge weights of a constant.
+Here, we prove which of the algorithms included in our generalized framework show this invariance-property: (proof in Appendix)
+\begin{prop} 
+We call an agglomerative algorithm ``weight-shift invariant'' if the structure of the merging tree $T$ returned by such algorithm is invariant w.r.t.
+a shift of all edge weights $w_e$  by a constant $\alpha\in \mathbb{R}$.
+Among all versions of \algname{} studied in this paper, only those using Average, Single, and Complete linkage criteria without cannotLinkConstraints are weight-shift-invariant (see algorithms highlighted in bold in Table~\ref{tab:linkage-criteria}).
+\end{prop}
+\noindent To our knowledge, Avg, Single, and Complete linkage methods have never been combined with cannot-link constraints on signed graphs, so the algorithms named \emph{HCC-Avg}, \emph{HCC-Single}, and \emph{HCC-Complete} in Table~\ref{tab:linkage-criteria} are new.
+
+% \textbf{Weight-shift hierarchical algorithms} -- Given an algorithm that outputs a clustering $\Pi$ for a signed graph $\mathcal{G}(V,E,w_e)$, we call the algorithm \emph{weight-shift hierarchical} if, by adding a constant $\alpha \in \mathbb{R}$ to all edge weights $w_e$, the algorithm outputs a clustering $\Pi'$ which is a coarsening of $\Pi$ when $\alpha>0$ and a refinement of $\Pi$ when $\alpha<0$\footnote{A clustering $\Pi'$ is a coarsening of $\Pi$ when every $S' \in \Pi'$ is the union of one or more clusters in $\Pi$.
+Similarly, $\Pi'$ is a refinement of $\Pi$ when every $S \in \Pi$ is given by the union of one or more clusters in $\Pi'$}.
+
+% \ref{tab:linkage-criteria}, additional ones were proposed in the literature:
+% \cite{nunez2013machine} for example uses a learned approach where a random forest classifier updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas
+% \cite{funke2018large} uses a \emph{quantile} linkage criterion by populating a histogram for each inter-cluster interaction.
+In our experiments, we decided to focus on the linkage criteria listed in Table \ref{tab:linkage-criteria}, since they represent the most common options.
+
+% In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, 
+%  the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see Table \ref{tab:linkage-criteria}, unsigned graphs).
+
+% Given a graph with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was pioneered in \cite{levinkov2017comparative,keuper2015efficient} (Table \ref{tab:linkage-criteria}, \emph{Sum} linkage).
+The authors present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms approximating the multicut optimization problem.
+% The Mutex Watershed \cite{wolf2018mutex} is another signed graph partitioning algorithm that introduces dynamical cannot-link constraints.
+In Proposition \ref{prop:equiv_MWS} (see Appendix \ref{sec:appendix_abs_max}) we prove that, surprisingly, it can also be seen as an efficient implementation of \algname{} with \emph{Absolute maximum} linkage (def.
+in Table \ref{tab:linkage-criteria}).
+Moreover, in Proposition \ref{prop:abs_max_cannot_link_property} we also prove that \algname{} with \emph{Abs Max} linkage returns the same clustering with or without enforcing cannot-link constraints.
+% On the other hand, to our knowledge, \emph{Average}, \emph{Max} or \emph{Min} linkage criteria have never been used for signed graph agglomerative algorithms or been combined with cannot-link constraints.
+
+\paragraph{Algorithms defining an ultrametric} -- The connection between agglomerative algorithms and ultrametrics\footnote{A metric space $(X,d)$ is an \emph{ultrametric} if for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.} is well known \cite{johnson1967hierarchical,milligan1979ultrametric}.
 Normally, ultrametrics are associated to strictly positive \emph{similarity} or \emph{dissimilarity} measures on a graph.
@@
 \begin{prop}
-Consider the binary rooted tree $T^*$ returned by the \algname{} Algorithm~\ref{main_alg}, given a choice of linkage criteria $\interact{}$ and the use of CannotLinkConstraints.
-Then, the quantity $(V, d_{T^*})$ defined in Eq.~\ref{eq:UM_def} is an ultrametric only for the combinations of linkage and CannotLinkConstraints marked with $(\dagger)$ in Table~\ref{tab:linkage-criteria}.
+Consider the binary rooted tree $T^*$ returned by the \algname{} Algorithm~\ref{main_alg}, given a choice of linkage criteria $\interact{}$ and the use (or not) of CannotLinkConstraints.
+Then, the quantity $(V, d_{T^*})$ defined in Eq.~\ref{eq:UM_def} is an ultrametric only for the combinations of linkage and CannotLinkConstraints reported in italic font in Table~\ref{tab:linkage-criteria}.
 \end{prop}
 
-\subsection{\algname{} with different linkage criteria: new and existing algorithms} \label{sec:alg_update_rules}
-
-% \begin{prop} 
-% The Mutex Watershed Algorithm (MWS) introduced by \cite{wolf2018mutex} and with empirical $\mathcal{O}(N \log N)$ complexity outputs the same clustering $\Pi^*$ returned by  the \algname{} Algorithm \ref{main_alg} with the use of cannot-link constraints and an Absolute Maximum update rule:
-% \begin{equation}\label{eq:def_abs_max}
-% f_{\mathrm{Abs.Max.}}(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
-%             \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
-%             \tilde{\cost}_2 & \text{otherwise}
-%              \end{cases} 
-% \end{equation}
-% \end{prop}
-\begin{prop} 
-The \algname{} Algorithm \ref{main_alg} with Absolute Maximum linkage (see def.
-in Table \ref{tab:linkage-criteria}) returns the same final clustering $\Pi^*_{\mathrm{AbsMax}}$ whether cannot-link constraints are introduced or not.
-In particular, $\Pi^*_{\mathrm{AbsMax}}$ is equal to the clustering returned by the Mutex Watershed Algorithm (MWS) introduced by \cite{wolf2018mutex}, which has empirical complexity $\mathcal{O}(N \log N)$.
-\end{prop}
-
-\begin{itemize}
-\item Table \ref{tab:linkage-criteria} lists new and existing algorithms.
-Better: we test the five linkage criteria (columns of Table~\ref{tab:linkage-criteria}).
-Many more have been applied to unsigned graphs (CITS), but those five linkages represent the most common options.
-\item GASP with Average, Single, and Complete linkage criteria is equivalent to HC when a graph with only positive edges is considered
-\item These three criteria have been throughly studied on (positive) similarity graphs
-\item As it was already observed in CITE, we have the following observation:
-\item GASP with Average, Single, and Complete linkage criteria
-
-\item It can be shown that the correlation clustering or multicut problem is not \emph{intrinsically-hierarchical}.
-Similarly, only few of the algorithms presented in this paper are \emph{intrinsically-hierarchical}
-% \item Only few of the Given a linkage $\interact{}$, we say that Algorithm \ref{main_alg} is invariant to a $\alpha$ weight-shift, if by changing all edge weights of the graphs by a constant $w_e+\alpha$ the structure of the hierarchical tree  does not change and defines the same function $d_T$.
-% \item \TODO{Why do we care?} MC does not return nested/hierarchical solutions when shifting weights.
-Which of these algorithms behave the same, or, somehow are more related to correlation clustering?
-So, actually, we care more about the shifted-solutions being nested, and not really about the fact that the hierarchy tree built by the algorithm stays the same.
-Is this somehow equivalent...?
-\end{itemize}
-
-\TODO{Specify greediness wrt multicut energy, ultrametric properties, and shift-invariance properties}  We review them in the following paragraphs.
-
-In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, 
- the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see Table \ref{tab:linkage-criteria}, unsigned graphs).
-
-Given a graph with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was pioneered in \cite{levinkov2017comparative,keuper2015efficient} (Table \ref{tab:linkage-criteria}, \emph{Sum} linkage).
-The authors present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms approximating the multicut optimization problem.
-The Mutex Watershed \cite{wolf2018mutex} is another signed graph partitioning algorithm that introduces dynamical cannot-link constraints.
-In Proposition \ref{prop:equiv_MWS} (see Appendix \ref{sec:appendix_abs_max}) we prove that, surprisingly, it can also be seen as an efficient implementation of \algname{} with \emph{Absolute maximum} linkage (def.
-in Table \ref{tab:linkage-criteria}).
-Moreover, in Proposition \ref{prop:abs_max_cannot_link_property} we also prove that \algname{} with \emph{Abs Max} linkage returns the same clustering with or without enforcing cannot-link constraints.
-On the other hand, to our knowledge, \emph{Average}, \emph{Max} or \emph{Min} linkage criteria have never been used for signed graph agglomerative algorithms or been combined with cannot-link constraints.
-
-Apart from the linkage criteria defined in Table \ref{tab:linkage-criteria}, additional ones were proposed in the literature:
-\cite{nunez2013machine} for example uses a learned approach where a random forest classifier updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas
-\cite{funke2018large} uses a \emph{quantile} linkage criterion by populating a histogram for each inter-cluster interaction.
+% Apart from the linkage criteria defined in Table \ref{tab:linkage-criteria}, additional ones were proposed in the literature:
+% \cite{nunez2013machine} for example uses a learned approach where a random forest classifier updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas
+% \cite{funke2018large} uses a \emph{quantile} linkage criterion by populating a histogram for each inter-cluster interaction.
 In our experiments, we decided to focus on the linkage criteria listed in Table \ref{tab:linkage-criteria}, since they represent the most common options.

### 2021-02-19 chapters/5_experiments_compare_rules.tex
Polish new theory section

@@
 
-        \begin{subfigure}[t]{0.49 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
-        \caption{No long-range predictions: \\$p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
-    \end{subfigure} \hfill
-    \begin{subfigure}[t]{0.49 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
-        \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
-    \end{subfigure}
+    %     \begin{subfigure}[t]{0.49 \textwidth}
+    %     \centering
+    %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
+    %     \caption{No long-range predictions: \\$p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
+    % \end{subfigure} \hfill
+    % \begin{subfigure}[t]{0.49 \textwidth}
+    %     \centering
+    %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
+    %     \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
+    % \end{subfigure}
 \caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust.

### 2021-02-19 chapters/5_experiments_intro.tex
Add spectral exp; update Cityscapes sec. and App.
Several changes to alg. descr and linkages
Polish new theory section

@@
 
-\section{Experiments on neuron segmentation}\label{sec:neuro_segm_exp}
+\section{Experiments}\label{sec:neuro_segm_exp}
+% \subsection{title}
+\begin{itemize}
+\item We test and compare the algorithms included in the proposed \algname{} framework over a large variety of signed graphs, whose specifications are listed in Table ??.
+\item OpenGM, CREMI, and other datasets. Define rag
+\item Common approach: predict affinities with CNN and then agglomerate pixel grid graph
+\item Details on the trained model are left in appendix
+\item Only some of the studied datasets have ground truth available. Define ARAND and VI-scores. 
+Table lists the values of the multicut objective achieved by different algorithms.
+\item In the next section, before to comment the results on these real-world datasets, we apply the studied algorithms to two types of synthetically generated graphs and highlight some of their fundamental properties.
+\end{itemize}
+
+\subsection{Synthetic graphs}
+\begin{itemize}
+\item  One is obtained by perturbing the output of our trained CNN (only merge mistakes)
+
+\item SUM: It grows one at the time (show already in ?, where they proposed a size-regularized version of it, but, as compared to HC-Avg, it is then biased towards ...?)
+\item AVG: grows clusters that are similarly sized
+\item MWS: the probability to make mistakes does not decrease as clusters increase in size
+\end{itemize}
+
+\subsection{Results and discussion}
+\begin{itemize}
+\item Our GT scores confirms the findings on synthetic graphs
+\item Comment energies (GAEC always achieves the best)
+\item At the very end, talk about cremi challenge, cremi-score and report our results. So far no other method was done from pixels
+\end{itemize}
 

### 2021-03-01 chapters/1_intro.tex
Add first version of new alg. and binary tree formulation
Several changes to alg. descr and linkages
Add dendrograms; finish rewriting experiments sec.

@@
 \centering
-\includegraphics[width=\textwidth]{figs/intro_image_v4.pdf} % left bottom right top
-\caption{\algname{} example.
+\includegraphics[width=0.5\textwidth]{figs/intro_image_v4.pdf} % left bottom right top
+\caption{\TODO{Redo figure}\algname{} example.
 \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge.
@@
 At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left in the graph.
+\TODO{Check if avg is correct}
 \label{fig:intro_figure}}
 \end{figure*}
+
+\begin{table*}[t]
+    \centering
+    \footnotesize
+    \begin{subtable}[t!]{\textwidth}\centering
+        \begin{tabular}{l |c  c  c  c  c}
+        % \multicolumn{1}{c}{}
+        % \multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} \\ $\,\,\interact(S_u ,S_v)$}}  
+        & \thead{Sum\\Linkage} & \thead{Absolute Maximum\\Linkage} & \thead{Average\\Linkage} & \thead{Single\\Linkage} & \thead{Complete\\Linkage} \\
+ % \multicolumn{1}{c}{} 
+ & $\displaystyle \sum_{e\in E_{ij}} \cost_e$  & $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{ij}} |\cost_t|$ & $\displaystyle \sum_{e\in E_{ij}} \cost_e \bigg/ \big|E_{ij}\big| $ &  $\displaystyle \max_{e\in E_{ij}} \cost_e$ & $\displaystyle \min_{e\in E_{ij}} \cost_e$ \\ \midrule
+ % \cmidrule{2-6}
+
+            \thead[r]{GASP on positive-weighted graphs} & \thead{-} &\thead{\textbf{HC-Single}} &\thead{\textbf{HC-Avg}} &\thead{\textbf{HC-Single}} &\thead{\textbf{HC-Complete}} \\
+            \thead[r]{GASP on signed graphs} & \thead{GAEC \cite{keuper2015efficient}} & \thead{\textbf{Mutex Watershed} \cite{wolf2018mutex}}& \thead{\textbf{HC-Avg}} &\thead{\textbf{HC-Single}} &\thead{\textbf{HC-Complete}} \\
+            \thead[r]{GASP on signed graphs + constraints} & \thead{\colorbox{yellow}{HCC-Sum}} % \thead{Greedy Fixation \cite{levinkov2017comparative}} 
+            & \thead{\textbf{Mutex Watershed} \cite{wolf2018mutex}}& \thead{\colorbox{yellow}{HCC-Avg}} &  \thead{\colorbox{yellow}{HCC-Single}} &  \thead{\colorbox{yellow}{HCC-Complete}} \\
+            % \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
+            % \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\ \midrule
+
+            %  Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
+Aggl.
+Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy\\Fixation \cite{levinkov2017comparative}} \\
+
+            %  \makecell[r]{Abs. Max:} & 
+            % $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
+            %    & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} \\
+
+            %  \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier.
+Aggl.
+Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
+
+            % Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
+
+            % Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}
+
+        \end{tabular}
+    \end{subtable} 
+    \caption{Clustering algorithms included in the proposed \algname{} framework, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
+New algorithms are highlighted in yellow.
+Algorithms typeset in bold font define an ultrametric on the graph (see Eq.~\ref{eq:UM_def}).
+Algorithms included in the green box, are weight-shift invariant (see Prop.~\ref{prop:weight_shift_invariant}).
+    We denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two cluster $S_i, S_j$. } 
+    \label{tab:linkage-criteria}
+\end{table*}
 
@@
 In Sec.~\ref{sec:spectral_clust}, we also show how \algname{} outperforms spectral clustering methods on the task of neuron segmentation and how on synthetic graphs it achieves similar scores to a recently proposed spectral method for signed graphs.
+\TODO{Define HC and AC abbrv}
 

### 2021-03-01 chapters/3_algorithm.tex
Add dendrograms; finish rewriting experiments sec.

@@
 % the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}.
-On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates to each edge a split tendency $w_e^- \in \mathbb{R}^+$: \OPTIONAL{the higher this number, the higher the inclination of the two incident vertices to be assigned to different clusters}.
+On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates to each edge a split tendency $w_e^- \in \mathbb{R}^+$.
+% : \OPTIONAL{the higher this number, the higher the inclination of the two incident vertices to be assigned to different clusters}.
 % the higher this weight, the more the incident vertices would like to be in different clusters. 
 Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring positive and negative edge weights $\cost_e\in \mathbb{R}$.
-Following the theoretical considerations in \cite{lange2018partial}, we define these signed weights as ${\cost_e = w_e^+ - w_e^-}$.
+Following the theoretical considerations in \cite{lange2018partial}, we define signed weights as ${\cost_e = w_e^+ - w_e^-}$.
 % Some approaches directly compute $\cost_e$, whereas others compute $w_e^+$ and $w_e^-$ separately.
@@
 \textbf{Multicut objective} -- We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{S\in\Pi} S $, $\,S \cap S' = \emptyset$ for different clusters $S, S'\in \Pi$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
-For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^0_\Pi= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u,v \in S \}$ the set of edges linking nodes in the same cluster, and as $E_\Pi^1= E \setminus E^0_\Pi$ the set of edges whose linked nodes belong to distinct clusters.
+For any clustering $\Pi$ of $\mathcal{G}$, we denote as $E^0_\Pi= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u,v \in S \}$ the set of edges linking nodes in the same cluster, and as $E_\Pi^1= E \setminus E^0_\Pi$ the set of edges whose linked nodes belong to distinct clusters, which is known as the \emph{multicut} of $\mathcal{G}$ associated to clustering $\Pi$.
+The instance of the NP-hard \emph{minimum cost multicut problem} w.r.t.
+$\mathcal{G}(V,E,w_e)$ is the task of finding a clustering that optimally balance the attraction and repulsion in the graph and is given by the following binary integer program:
 % \begin{equation}
@@
 % \end{align}
-The set of edges $E_\Pi^1$ is known as the \emph{multicut} of $\mathcal{G}$ associated to clustering $\Pi$.
-The instance of the NP-hard \emph{minimum cost multicut problem} w.r.t.
-$\mathcal{G}(V,E,w_e)$ is the task of finding a clustering that optimally balance the attraction and repulsion in the graph and is given by the following binary integer program:
 \begin{equation}\label{eq:MC_objective}
@@
 The linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
-In hierarchical clustering (HC) literature,  a \emph{dendrogram} $T$ is a rooted binary tree\footnote{In general, one could look at trees that are not binary.
+A \emph{dendrogram} $T$ is a rooted binary tree\footnote{In general, one could look at trees that are not binary.
 However, the algorithms discussed in this paper always generate binary hierarchical trees, so nothing would be gained by this generalization.} representing the merging order of an agglomerative algorithm, such that the leaves of the tree are in one-to-one correspondence with $V$.
 Let $T_{\mathrm{R}},T_{\mathrm{L}}\subset T$ denote the subtrees rooted at the two children of the root node in $T$.
-For any two leaves $u,v \in V$, let $T[u \vee v]$ be the subtree rooted at the least common ancestor $u \vee v\in T$ of nodes $u$ and $v$ (furthest from the root), and let \texttt{leaves}$(T[u \vee v])\subseteq V$ be the set of leaves of this subtree.
+For any two leaves $u,v \in V$, let $T[u \vee v]$ be the subtree rooted at the least common ancestor $(u \vee v)\in T$ of nodes $u$ and $v$ (furthest from the root), and let \texttt{leaves}$(T[u \vee v])\subseteq V$ be the set of leaves of this subtree.
 % \TODO{Here we talk about the algorithm already, so we could move it to next section and the flow could be better. But we need a tree in the alg. So we better do this later}
 % Algorithm \ref{main_alg} returns a binary tree denoted by $T^*$.
-Given an agglomerative algorithm with merging tree $T$, let $h_T:T \rightarrow \mathbb{N}$ denote the \emph{dendrogram-height} of each $(u\vee v)\in T$, which is defined as the iteration number at which nodes $u,v\in V$ were merged (\TODO{Fig.~1}).
-We also define the interaction $\treeHeight(u,v)$ as the interaction $\interact{}(S,S')$ between the two clusters $S,S'$ that were merged at iteration $h_T(u\vee v)$:
+Given an agglomerative algorithm with merging tree $T$, let $h_T:T \rightarrow \mathbb{N}$ denote the \emph{dendrogram-height} of each $(u\vee v)\in T$, which is defined as the iteration number at which nodes $u,v\in V$ were merged by the algorithm (\TODO{Fig.~1}).
+We also define $\treeHeight(u,v)$ as the signed interaction $\interact{}(S,S')$ between the two clusters $S,S'$ that were merged at iteration $h_T(u\vee v)$:
 % Then, given a binary tree $T$ and a linkage criterion $\interact$, we can associate a \emph{signed similarity} function $\treeHeight$ to each pair of distinct original nodes $u\neq v$, with $u, v \in V$:
@@
 
-\subsection{\algname{}: generalized agglomerative algorithm for signed graph partitioning} \label{sec:algorithm}
+\subsection{The \algname{} algorithm} \label{sec:algorithm} 
+% : generalized agglomerative algorithm for signed graph partitioning
 
@@
 If the interaction is attractive, then the clusters are merged, provided that they were not previously constrained.
-After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S, S')$ listed in Table \ref{tab:linkage-criteria}.
+After each merge, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S, S')$ listed in Table \ref{tab:linkage-criteria}.
 \emph{Phase~One} terminates when all the remaining clusters are either constrained or share repulsive interactions.
 
-In \emph{Phase~Two}, the algorithm removes all the constraints previously introduced in \emph{Phase~One} and merges the remaining clusters that share an attractive interaction, starting from those with the most attractive ones\footnote{Note that in the version of \algname{} with \emph{addCannotLinkConstraints} set to \texttt{False}, nothing happens in \emph{Phase~Two}.}.
-The final \algname{} clustering $\Pi^*$ is returned at the end of \emph{Phase~Two} and it will then be composed of clusters sharing only mutual repulsive interactions.
+\emph{Phase Two:} Now that the clusters have grown in size, the algorithm removes the constraints previously introduced in \emph{Phase~One} and merges all the clusters that still share an attractive interaction, merging the most attractive one first\footnote{Note that in the version of \algname{} with \emph{addCannotLinkConstraints} set to \texttt{False}, nothing happens in \emph{Phase~Two}.}.
+The final clustering $\Pi^*$ returned by \algname{} is found at the end of \emph{Phase~Two} and it is then composed of clusters sharing only mutual repulsive interactions.
 
-Finally, in \emph{Phase~3}, the algorithm keeps merging all clusters until only a single one is left, so that the full sequence of merging steps is also returned in the form of a hierarchical tree $T^*$.
+Finally, in \emph{Phase~3}, the algorithm keeps merging all clusters until only a single one is left and then returns the hierarchical tree $T^*$ representing the full sequence of merging steps.
 The algorithm was implemented using a standard HC implementation with computational complexity $\mathcal{O}(N^2 \log N)$ (see Appendix \ref{sec:detailed_impl} for more details).
-\TODO{mention fact that constraints make algorithm slower?}
 
@@
 % \end{prop}
-In this paper we focus on five linkage criteria (see columns of Table~\ref{tab:linkage-criteria}).
-Many more linkage criteria have been applied to unsigned graphs \cite{nunez2013machine,felzenszwalb2004efficient,funke2018large}, but we decided to focus our experiments on those five because they represent the most common choices.
+In this paper we focus on five linkage methods (see columns of Table~\ref{tab:linkage-criteria}).
+Many more linkage criteria have been applied to unsigned graphs \cite{nunez2013machine,felzenszwalb2004efficient,funke2018large}, involving median-based or size-regularized methods, but we decided to focus this paper on those five criteria because they represent the most known choices.
 
@@
 \paragraph{AbsMax Linkage} -- This linkage method is also specific to signed graphs, since on positive-weighted graphs it would be equivalent to single linkage.
-Here, we prove that the AbsMax-version of \algname{} was already introduced in the literature (see proof in Appendix):
+Here, we prove that the Mutex Watershed Algorithm \cite{wolf2018mutex} can be seen as an agglomerative algorithm with AbsMax linkage (see proof in Appendix):
 \begin{prop} 
@@
 in Table \ref{tab:linkage-criteria}) returns the same final clustering $\Pi^*_{\mathrm{AbsMax}}$ whether or not cannot-link constraints are introduced.
-In particular, $\Pi^*_{\mathrm{AbsMax}}$ is equal to the clustering returned by the Mutex Watershed Algorithm (MWS) introduced by \cite{wolf2018mutex}, which has empirical complexity $\mathcal{O}(N \log N)$.
+In particular, $\Pi^*_{\mathrm{AbsMax}}$ is equal to the clustering returned by the Mutex Watershed Algorithm (MWS) \cite{wolf2018mutex}, which has empirical complexity $\mathcal{O}(N \log N)$.
 \end{prop}
@@
 \paragraph{Average, Single, and Complete Linkage} -- These three linkage criteria have been throughly studied on positive-weighted graphs.
-In \cite{chehreghani2020hierarchical}, the authors proved that applying these three linkage methods to a signed graph is equivalent to applying them to the positive-weighted graph obtained by shifting all edge weights of a constant.
-Here, we prove which of the algorithms included in our generalized framework show this invariance-property: (proof in Appendix)
-\begin{prop} 
+In \cite{chehreghani2020hierarchical}, the authors proved that applying these three linkage methods to a signed graph is equivalent to applying them to the positive-weighted graph obtained by shifting all edge weights by a constant.
+Here, we prove which of the algorithms included in our generalized framework have this invariance-property: (proof in Appendix)
+\begin{prop} \label{prop:weight_shift_invariant}
 We call an agglomerative algorithm ``weight-shift invariant'' if the structure of the merging tree $T$ returned by such algorithm is invariant w.r.t.
 a shift of all edge weights $w_e$  by a constant $\alpha\in \mathbb{R}$.
-Among all versions of \algname{} studied in this paper, only those using Average, Single, and Complete linkage criteria without cannotLinkConstraints are weight-shift-invariant (see algorithms highlighted in bold in Table~\ref{tab:linkage-criteria}).
+Among the versions of \algname{} studied in this paper, only those using Average, Single, and Complete linkage criteria without cannotLinkConstraints are weight-shift-invariant (see algorithms typeset in bold font in Table~\ref{tab:linkage-criteria}).
 \end{prop}
-\noindent To our knowledge, Avg, Single, and Complete linkage methods have never been combined with cannot-link constraints on signed graphs, so the algorithms named \emph{HCC-Avg}, \emph{HCC-Single}, and \emph{HCC-Complete} in Table~\ref{tab:linkage-criteria} are new.
+\noindent To our knowledge, Avg, Single, and Complete linkage methods have never been combined with cannot-link constraints on signed graphs, so the algorithms that in Table~\ref{tab:linkage-criteria} are named \emph{HCC-Avg}, \emph{HCC-Single}, and \emph{HCC-Complete} are new.
 
@@
 \begin{prop}
-Consider the binary rooted tree $T^*$ returned by the \algname{} Algorithm~\ref{main_alg}, given a choice of linkage criteria $\interact{}$ and the use (or not) of CannotLinkConstraints.
-Then, the quantity $(V, d_{T^*})$ defined in Eq.~\ref{eq:UM_def} is an ultrametric only for the combinations of linkage and CannotLinkConstraints reported in italic font in Table~\ref{tab:linkage-criteria}.
+% Consider the binary rooted tree $T^*$ returned by the \TODO{all variants in Table 1} \algname{} Algorithm~\ref{main_alg}, given a choice of linkage criteria $\interact{}$ and the use (or not) of CannotLinkConstraints.
+Among the algorithms listed in Table \ref{tab:linkage-criteria} and included in the \algname{} framework, only Mutex Watershed and hierarchical clustering with Average (HC-Avg), Single (HC-Single) and Complete linkage (HC-Complete) define an ultrametric given by the quantity $(V, d_{T^*})$ defined in Eq.~\ref{eq:UM_def}, where $T^*$ is the tree returned by Algorithm~\ref{main_alg}.
 \end{prop}
@@
 
-\begin{table*}[t]
-    \centering
-    \footnotesize
-    \begin{subtable}[t!]{\textwidth}\centering
-        \begin{tabular}{l |c  c  c  c  c}
-        % \multicolumn{1}{c}{}
-        % \multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} \\ $\,\,\interact(S_u ,S_v)$}}  
-        & \thead{Sum\\Linkage} & \thead{Absolute Maximum\\Linkage} & \thead{Average\\Linkage} & \thead{Single\\Linkage} & \thead{Complete\\Linkage} \\
- % \multicolumn{1}{c}{} 
- & $\displaystyle \sum_{e\in E_{uv}} \cost_e$  & $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$ & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big| $ &  $\displaystyle \max_{e\in E_{uv}} \cost_e$ & $\displaystyle \min_{e\in E_{uv}} \cost_e$ \\ \midrule
- % \cmidrule{2-6}
-
-            \thead[r]{GASP on positive-weighted graphs} & \thead{-} &\thead{\emph{\textbf{HC-Single}}} &\thead{\emph{\textbf{HC-Avg}}} &\thead{\emph{\textbf{HC-Single}}} &\thead{\emph{\textbf{HC-Complete}}} \\
-            \thead[r]{GASP on signed graphs} & \thead{GAEC \cite{keuper2015efficient}} & \thead{\emph{Mutex Watershed} \cite{wolf2018mutex}}& \thead{\emph{\textbf{HC-Avg}}} &\thead{\emph{\textbf{HC-Single}}} &\thead{\emph{\textbf{HC-Complete}}} \\
-            \thead[r]{GASP on signed graphs + constraints} & \thead{\colorbox{yellow}{HCC-Sum}} % \thead{Greedy Fixation \cite{levinkov2017comparative}} 
-            & \thead{\emph{Mutex Watershed} \cite{wolf2018mutex}}& \thead{\colorbox{yellow}{HCC-Avg}} &  \thead{\colorbox{yellow}{HCC-Single}} &  \thead{\colorbox{yellow}{HCC-Complete}} \\
-            % \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
-            % \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\ \midrule
-
-            %  Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier.
-Aggl.
-Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy\\Fixation \cite{levinkov2017comparative}} \\
-
-            %  \makecell[r]{Abs. Max:} & 
-            % $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
-            %    & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} \\
-
-            %  \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier.
-Aggl.
-Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
-
-            % Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\
-
-            % Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}
-
-        \end{tabular}
-    \end{subtable} 
-    \caption{Existing and new (highlighted in yellow) clustering algorithms that can be reformulated as special cases of the proposed generalized agglomerative algorithm for signed graph partitioning, \algname{}, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
-Given two clusters $S_i$ and $S_j$, the set $E_{ij}$ is defined as the set of all edges connecting the two cluster, i.e.
-$E_{ij}=(S_i \times S_{j}) \cap E$.
-\TODO{Algorithm in italic define an ultrametric; algorithms in bold are weight-shift hierarchical; new ones are highlighted in yellow} }
-    \label{tab:linkage-criteria}
-\end{table*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{./figs/comparison_new.pdf} % left bottom right top
-\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data.
-Only the \emph{wrongly} segmented regions are highlighted in different warm colors.
-Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.
-Red arrows point to wrongly split regions.
-Yellow arrows point out merge errors.
-The \emph{Average} linkage without cannot-link constraints returned the best segmentation.
-\label{fig:cremi_comparison}}
-\end{figure*}
-
-\begin{table*}[t]
-    \centering
-    % \scriptsize
-    \tiny
-    \begin{subtable}[t!]{\textwidth}\centering
-        \begin{tabular}{l  c  c  c  c  c c c c c c c c c}
-        \toprule
-        Dataset & Graph-Type & $\#I$ & $|V|$ & $\bar{\text{deg}}(v)$ & GT & GAEC & MWS & HC-AvgL & HC-SingleL & HC-CompleteL & Constr-SumL & Constr-AvgL & Constr-SingleL \\ \midrule
-        \emph{Image Seg.} & \emph{rag} & 100 & 156-3764 &   & \HollowBox\\
-        \emph{Knott-3D (150-300-450)} & \emph{rag-3D} & 24 & 572-17k &  & \HollowBox\\
-        % \emph{Knott-3D-300} & \emph{rag-3D} & 8& & & \HollowBox\\
-        % \emph{Knott-3D-450}& \emph{rag-3D} & 8 & & & \HollowBox\\  
-        \emph{CREMI-OurUNet} & \emph{rag-3D} & 3&  & & \CrossedBox\\ 
-        \emph{Fruit-Fly Level 1-4} & \emph{rag-3D} & 4& 5m-11m &  & \HollowBox\\
-        \emph{Fruit-Fly Level Global} & \emph{rag-3D} & 1& 90m &  & \HollowBox\\ \midrule
-                \emph{CREMI-pixGrid-OurUNet} & \emph{gridGraph} & 12& $\sim$30m & 4 & \CrossedBox\\
-        % \emph{(CREMI-pixGrid-LSIMasksUNet)} & \emph{gridGraph} & 1 & & 4 & \CrossedBox\\
-        \emph{(CityScapesValidation-pixGrid)} & \emph{gridGraph} &  &  & & \CrossedBox\\\midrule
-        % \emph{CREMI-test....}\\\midrule
-        \emph{Stochastic Block Model (synthetic)} & \emph{non-planar} &-&- & - & \CrossedBox \\
-        \emph{Mod. Clustering} & \emph{complete} & 6& 34-115 & 33-114 & \HollowBox\\ 
-        \emph{(epinions and slashdot?)} & \emph{dense?} &  & & & \HollowBox\\
-
-        \end{tabular}
-    \end{subtable} 
-    \caption{List of used datasets and MC objectives achieved by different algorithms} 
-    \label{tab:datasets_and_energies}
-\end{table*}
-
 % \begin{table}[t]

### 2021-03-01 chapters/5_experiments_compare_rules.tex
Add dendrograms; finish rewriting experiments sec.

@@
 \captionsetup[subfigure]{justification=centering, singlelinecheck=off}
-\begin{figure*}[t]
+\begin{figure}[t]
 \centering
-    \begin{subfigure}[t]{0.49 \textwidth}
+    \begin{subfigure}[t]{0.47 \textwidth}
         \centering
-        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_0.pdf}
+        \includegraphics[width=\textwidth,trim=0.25in 0.in 0.5in 0.in,clip]{./figs/SSBM_experiments.pdf}
+        \caption{Scores on SSBM graphs}
     \end{subfigure} \hfill
-    \begin{subfigure}[t]{0.49 \textwidth}
+    \begin{subfigure}[t]{0.47 \textwidth}
         \centering
         \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
+        \caption{Scores on \emph{CREMI-gridGraph} perturbed with noise}
     \end{subfigure}
 
+    % \begin{subfigure}[t]{0.32 \textwidth}
+    %     \centering
+    %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
+    % \end{subfigure}\hfill
+    % \begin{subfigure}[t]{0.32 \textwidth}
+    %     \centering
+    %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
+    % \end{subfigure}
     %     \begin{subfigure}[t]{0.49 \textwidth}
@@
 Experiments are performed on a crop of CREMI training sample B.
+\algname{} performances compared to spectral methods on synthetic graphs.
+The spectral methods were given the true number of clusters as input, in contrast to \algname{}.
+\TODO{Define paramters SSB; explain percentile stuff (for both noise experiments)}
 }\label{fig:noise_plots}
-\end{figure*}
-\begin{figure*}[t]
-        \centering
-\begin{minipage}[t]{0.48\textwidth}
-    \centering
-    \scriptsize
-        \begin{tabular}[t]{l|c}
-         Method & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
-\textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
-\algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
-\algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
-\algname{} Max. + Constraints & 0.324 \\
-\algname{} Sum \cite{keuper2015efficient} & 0.334 \\
-\algname{} Average + Constraints & 0.563 \\
-THRESH & 1.521 \\ 
-        \end{tabular}
-    \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding.
-All methods use the affinity predictions from our CNN as input.
-Scores are averaged over the three CREMI training datasets.}
-    \label{tab:results_cremi_train}
-\end{minipage}\hfill
-\begin{minipage}[t]{0.48\textwidth}
-    \centering
-    \scriptsize
-        \begin{tabular}[t]{l|c}
-        Method & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
-Our CNN + DTWS + LMC &  0.221\\
-PNI CNN \cite{lee2017superhuman} & 0.228 \\
-\textbf{Our CNN + \algname{} Average} & \textbf{0.241} \\
-MALA CNN + MC \cite{funke2018large} & 0.276 \\
-CRU-Net \cite{zeng2017deepem3d} & 0.566  \\
-LFC \cite{parag2017anisotropic} & 0.616  \\
-        \end{tabular}
-        \vspace*{0.99em}
-    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (March 2020).
-All entries, apart from our using \algname{}, employ superpixel-based post-processing pipelines.}
-    \label{tab:results_cremi_test}
-\end{minipage}
-\end{figure*}
+\end{figure}
 
-\subsection{Data: CREMI challenge} \label{sec:cremi_challenge}
-We evaluate all algorithms in the proposed framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available.
+% \begin{figure}[t]
+% \centering
+% % \begin{minipage}[t]{0.48\textwidth}
+% % \vspace{0pt}
+% % \centering
+% % % \footnotesize
+% % \begin{tabular}[t]{L{9em} M{7em}}
+% %            Method & Rand-Score \\ \midrule
+% %            \textbf{GASP Average} & \textbf{0.8966} \\
+% % GASP Sum & 0.8965 \\
+% % GASP Abs Max & 0.8932 \\
+% % SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG} & 0.5839\\
+% % $L_{sym}$ \cite{kunegis2010spectral} & 0.1931 \\
+% % SPONGE \cite{Cucuringu2019SPONGEAG} & 0.0789 \\
+% % BNC \cite{chiang2012scalable} & 0.0074 \\
+% %         \end{tabular}
+% %     \captionof{table}{\algname{} compared to spectral clustering methods on a small crop of the CREMI dataset (sample B).}
+% %     \label{tab:cremi_spectral_experiments}
+% % \end{minipage}\\\vspace{2em}
+% \begin{minipage}[t]{0.38\textwidth}
+% \vspace{0pt}
+% \centering
+%         \includegraphics[width=1.\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf} % 0.45
+%         \caption{}
+%     \label{fig:SSBM_scores}
+% \end{minipage}
+% \end{figure}
+
+% \subsection{Data: CREMI challenge} \label{sec:cremi_challenge}
+% Test \ref{tab:cremi_leaderboard}
+% We evaluate all algorithms in the proposed framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available.
 The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which come with publicly available training ground truth.

### 2021-03-01 chapters/5_experiments_intro.tex
Add dendrograms; finish rewriting experiments sec.

--- 2019-06-27 chapters/5_experiments_intro.tex
@@
 
-\section{Experiments on neuron segmentation}\label{sec:neuro_segm_exp}
+\section{Experiments}\label{sec:neuro_segm_exp}
+\subsection{Signed graph clustering problems}
+We evaluate the agglomerative clustering algorithms included in our framework on a large collection of both synthetic and real-world graphs.
+The size of the graphs ranges from a few hundred to hundreds of millions of edges.
 
-We first evaluate and compare the agglomerative clustering algorithms described in the generalized framework on the task of neuron segmentation in electron microscopy (EM) image volumes.
+\textbf{Synthetic SSBM graphs} -- We first consider synthetic graphs generated by a signed stochastic block model (SSBM), following the approach in \cite{Cucuringu2019SPONGEAG}.
+We use an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N$ vertices and edge probability $p$.
+The graph is partitioned into $k$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) have Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $\sigma$.
+To model noise, the sign of the edge weights is flipped independently with probability $\eta$.
+
+\textbf{Existing signed graphs}  -- We use clustering instances from the OpenGM benchmark \cite{kappes2013comparative} as well as biomedical segmentation instances \cite{pape2017solving}.
+The dataset \emph{Image Segmentation} contains planar region-adjacency-graphs (\emph{rag}) that are constructed from superpixel adjacencies of photographs.
+The \emph{Knott-3D} datasets contains \emph{3D-rags} arising from volume images acquired by electron microscopy (EM).
+The set \emph{Modularity Clustering} contains complete graphs constructed from clustering problems on small social networks.
+The \emph{Fruit-Fly} 3D-rag instances were generated from volume image scans of fruit fly brain matter.
+Instances \emph{Level 1-4} are progressively simplified versions of the global problem obtained via block-wise domain decomposition \cite{pape2017solving}.
+
+\textbf{Grid-graphs from CNN predictions} -- We also evaluate the clustering methods on the task of neuron segmentation in EM image volumes using training data from the CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge}.
+We train a 3D U-Net \cite{ronneberger2015u,cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
+as described in \cite{lee2017superhuman}\footnote{See Appendix \ref{sec:cremi_details} for all details about training and data augmentation.}.
+The predicted affinities $a_e\in[0,1]$, which represent how likely it is for a pair of pixels to belong to the same neuron segment, are then mapped to signed edge weights $w_e=a_e-0.5$, resulting in a 3D grid-graph having a node for each pixel/voxel of the  image\footnote{To map affinities to signed weights, we also tested the \emph{logarithmic mapping} proposed in \cite{finkel2008enforcing,andres2012globally}, but it performed worse in our experiments.}.
+We divided the three training samples of the CREMI challenge, which consists of approximately 196 million voxels each, into five sub-blocks for a total of 15 graph clustering problems (named \emph{CREMI-gridGraph} in Table~\ref{tab:datasets_and_energies}).
+% \TODO{long-range probs}
+
+\textbf{3D-rag from CNN-predictions} -- Lastly, we use the predictions of our CNN model to generate three graph instances (one for each CREMI training sample, named \emph{CREMI-3D-rag} in Table~\ref{tab:datasets_and_energies}), which have very similar structure to the \emph{Knott-3D} and \emph{Fruit-Fly} instances.
+We obtain them by first computing 2D supervoxels from the CNN predictions (using a watershed algorithm seeded at the maxima of the smoothed boundary distance transform) and then building a 3D region-adjacency graph, whose edge weights are given by the CNN affinities averaged over the boundaries of adjacent supervoxels.
+
+% This is true for the neuron instances generated from the CREMI challenge, where training data is available, and for synthetic graphs generated with SSBM.
+
+% Fig.~\ref{fig:noise_plots} summarizes our 12000 noise experiments: we focus on the best performing linkage criteria, i.e.
+\emph{Average}, \emph{Sum} and \emph{Abs Max}, and test them with different amount of noise.
+% In these experiments, we also want to assess how beneficial it is to use long-range CNN predictions in the agglomeration.
+Thus, we perform a set of simulations without adding long-range connections to the grid-graph and another set where we introduce them with a 10\% probability\footnote{We also performed experiments adding all the long-range predictions given by the CNN model, but we did not note major differences when using only 10\% of them.
+Adding this fraction is usually sufficient to improve the scores.}.\\
+
+% , where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation and in our case was set to $\beta=0.5$.
+% Neuron segmentation is commonly performed by first predicting undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment.
+% Similarly to \cite{lee2017superhuman}, we train a UNet model CITE to predict both short- and long-range affinities that are not limited to adjacent pixels.
+These predictions are then used as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image.
+
+% ---
+% We first evaluate and compare the agglomerative clustering algorithms described in the generalized framework on the task of neuron segmentation in electron microscopy (EM) image volumes.
 This application is of key interest in connectomics, a field of neuro-science with the goal of reconstructing neural wiring diagrams spanning complete central nervous systems.
@@
 
-EM segmentation is commonly performed by first predicting 
-boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment.
-The affinities do not have to be limited to immediately adjacent pixels.
-Thus, similarly to \cite{lee2017superhuman}, we train a CNN to predict both short- and long-range affinities
-and use them as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image.
+% ----
+% We evaluate all algorithms in the proposed framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available.
+The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which come with publicly available training ground truth.
+The results submitted to the leaderboard are evaluated using the CREMI score, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}.
+In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.
+
+\begin{table*}[t]
+    \centering
+    \scriptsize
+    % \tiny
+    \begin{subtable}[t!]{\textwidth}
+    \centering
+
+        \begin{tabular}{l  c  r  c  c  c r r r r r r}
+        \toprule
+        Clustering problem & \makecell{Graph Type} & $\#I$ & $|V|$ & $|E|$ & GT & GAEC \cite{keuper2015efficient} & HCC-Sum & MWS \cite{wolf2018mutex} & HC-Avg & HCC-Avg \\ \midrule
+        \emph{Modularity Clustering} \cite{brandes2007modularity} & \emph{complete} & 6& 34-115 & 561-6555 & \HollowBox & -0.457 & -0.453 & -0.073 & \textbf{-0.467} & \textbf{-0.467} \\ 
+        \emph{Image Segmentation} \cite{andres2011probabilistic} & \emph{rag} & 100 & 156-3764 &  439-10970  & \HollowBox & \textbf{-2,955} & -2,953 & -2,901 & -2,903 & -2,896\\
+        \emph{Knott-3D (150-300-450)} \cite{andres2012globally} & \emph{3D-rag} & 24 & 572-17k & 3381-107k & \HollowBox & \textbf{-36,667} & -36,652 & -35,200 & -35,957 & -35,631\\
+        % \emph{Knott-3D-300} & \emph{3D-rag} & 8& & & \HollowBox\\
+        % \emph{Knott-3D-450}& \emph{3D-rag} & 8 & & & \HollowBox\\  
+        \emph{CREMI-3D-rag (OurCNN)}  & \emph{3D-rag} & 3& 134k-157k & 928k-1065k & \CrossedBox & \textbf{-1,112,287} & -1,112,286& -1,109,731 & -1,112,177 & -1,112,100\\ 
+        \emph{Fruit-Fly Level 1-4} \cite{pape2017solving} & \emph{3D-rag} & 4& 5m-11m & 28m-72m & \HollowBox & \textbf{-151,022} & -151,017 & -150,879 & -150,909 & -150,876\\
+        \emph{CREMI-gridGraph (OurCNN)} & \emph{gridGraph} & 15& 39m & 140m & \CrossedBox & -73,317,601 & -73,328,867 & -73,330,568 & \textbf{-73,502,947} & -73,474,856\\
+        \emph{Fruit-Fly Level Global} \cite{pape2017solving} & \emph{3D-rag} & 1& 90m & 650m & \HollowBox & \textbf{-151,688} & -151,596 & -146,315 & -150,466 & -150,171 \\
+        % \emph{(CREMI-pixGrid-LSIMasksUNet)} & \emph{gridGraph} & 1 & & 4 & \CrossedBox\\
+        % \emph{(CityScapesValidation-pixGrid)} & \emph{gridGraph} &  &  & & \CrossedBox\\
+        % \emph{CREMI-test....}\\\midrule
+        % \emph{Stochastic Block Model (synthetic)} & \emph{non-planar} &-&- & - & \CrossedBox \\
+        % \emph{(epinions and slashdot?)} & \emph{dense?} &  & & & \HollowBox\\
+
+% % Superpixels:
+% Mutex & -1109731264 \\
+% MEANconstr & -1112099691 \\
+% MEAN & -1112176981 \\
+% SUMconstrNoLogs & -1112286144 \\
+% SUMnoLogs & -1112286741 \\
+% Agglo type & multicut_energy \\
+
+% % Pixels:
+% SUM & -73317601 \\
+% SUMconstr & -73328867 \\
+% MutexPixGrid & -73330568 \\
+% MEANconstr & -73474856 \\
+% MEAN & -73502947 \\
+
+        \end{tabular}
+    \end{subtable} 
+    \caption{List of compared signed graph clustering problems: for each, we specify the number of instances $\# I$, nodes $|V|$, edges $|E|$, and whether a ground truth clustering is available.
+We compare algorithms in the \algname{} framework by evaluating which of the obtained clusterings is associated to the lowest value of the multicut objective defined in Eq.~\ref{eq:MC_objective} (\textbf{lower is better}).}
+    \label{tab:datasets_and_energies}
+\end{table*}
+\begin{table*}[t]
+        \centering
+% \begin{minipage}[t]{0.6\textwidth}
+%     \centering
+    \tiny
+        \begin{subtable}[t]{0.29\textwidth}
+        \centering
+        \begin{tabular}[t]{lcccc}
+        \toprule
+          & \makecell{ARAND\\Score} & \makecell{VOI\\split} & \makecell{VOI\\merge}&  \makecell{Runtime\\(s)} \\ \midrule 
+\textbf{HC-Avg} & \textbf{0.0487} & 0.387 & 0.258 & 2344 \\
+HCC-Avg & 0.0492 & 0.389 & 0.259 & 2892 \\
+MWS \cite{wolf2018mutex} & 0.0554 & 0.440 & 0.249 & 688 \\
+GAEC \cite{keuper2015efficient} & 0.0856 & 0.356 & 0.338 & 4717 \\
+HCC-Sum & 0.0872 & 0.365 & 0.337 & 4970 \\
+HCC-Complete & 0.9206 & 4.531 & \textbf{0.210} & 1330 \\
+HC-Complete & 0.9211 & 4.536 & 0.211 & 1020 \\
+HC-Single & 0.9264 & \textbf{0.060} & 4.887 & \textbf{312} \\
+HCC-Single & 0.9264 & \textbf{0.060} & 4.887 & 6440 \\
+% HC-Avg & \textbf{0.226}  \\
+% HCC-Sum & 0.282 \\
+% MWS \cite{wolf2018mutex} & 0.322 \\
+% GAEC \cite{keuper2015efficient} & 0.334 \\
+% HCC-Avg & 0.563 \\
+% HC-Single & 1.521 \\ 
+% HCC-Single & 0.324 \\
+% HC-Complete & 1.521 \\ 
+% HCC-Complete & 1.521 \\ 
+        \end{tabular}
+    % \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding.
+All methods use the affinity predictions from our CNN as input.
+Scores are averaged over the three CREMI training datasets.}
+    \caption{\emph{CREMI-gridGraph (OurCNN)}}
+    \label{tab:scores_gridGraph}
+    \centering
+    \tiny
+    \end{subtable}\hfill
+\begin{subtable}[t]{.29\textwidth}
+\centering
+        \begin{tabular}[t]{lcccc}
+        \toprule
+          & \makecell{ARAND\\Score} & \makecell{VOI\\split} & \makecell{VOI\\merge}&  \makecell{Runtime\\(s)} \\ \midrule 
+\textbf{HC-Avg} & \textbf{0.0896} & 0.603 & 0.323 & 86 \\
+HCC-Avg & 0.0898 & 0.600 & 0.325 & 87 \\
+GAEC \cite{keuper2015efficient} & 0.0905 & 0.606 & 0.323 & 89 \\
+HCC-Sum & 0.0910 & 0.608 & 0.323 & 85 \\
+MWS \cite{wolf2018mutex} & 0.1145 & 0.825 & 0.295 & 86 \\
+HCC-Single & 0.5282 & \textbf{0.437} & 1.367 & 88 \\
+HC-Single & 0.5282 & \textbf{0.437} & 1.367 & 85 \\
+HCC-Complete & 0.5564 & 2.220 & 0.254 & 89 \\
+HC-Complete & 0.5654 & 2.253 & \textbf{0.249} & 86 \\
+        \end{tabular}
+        \hspace*{5em}
+    \caption{\emph{CREMI-3D-rag (OurCNN)}}
+    \label{tab:scores_3drag}
+    \end{subtable}\hfill
+    \begin{subtable}[t]{.38\textwidth}
+    % \end{table}
+% \end{minipage}\hfill
+% \begin{minipage}[t]{0.38\textwidth}
+    \centering
+    \tiny
+        \begin{tabular}[t]{lcccc}
+        \toprule
+          & \makecell{CREMI\\Score} & \makecell{ARAND\\Score} & \makecell{VOI\\split} & \makecell{VOI\\merge}    \\ \midrule 
+\emph{OurCNN: 3D-rag + LMC} & \textbf{0.221} & \textbf{0.108} & \textbf{0.339} & 0.115 \\
+\textbf{\emph{OurCNN: gridGraph + HCC-Avg}} & 0.224 & 0.113 & 0.361 & 0.085  \\
+\emph{OurCNN: gridGraph + HC-Avg}  & 0.224 & 0.114 &  0.364 & 0.083 \\
+PNI CNN \cite{lee2017superhuman} & 0.228 & 0.116 & 0.345 & 0.106 \\
+LSI-Masks \cite{bailoni2020proposal}  & 0.246 & 0.125 & 0.383 & 0.107  \\
+\emph{OurCNN: 3D-rag + HCC-Avg} & 0.257 & 0.132 & 0.438& \textbf{0.063} \\  
+\emph{OurCNN: 3D-rag + HC-Avg} & 0.262 & 0.135 & 0.448 & \textbf{0.063}   \\  
+% \textbf{Our CNN + \algname{} Average} & \textbf{0.241 \\
+MALA CNN + MC \cite{funke2018large} & 0.276  & 0.132 &0.490  & 0.089  \\
+CRU-Net \cite{zeng2017deepem3d} & 0.566 & 0.229 & 1.081 &  0.389    \\
+LFC \cite{parag2017anisotropic} & 0.616 & 0.313 & 1.085 & 0.140     \\
+        \end{tabular}
+        \caption{CREMI Challenge leader-board}
+        \label{tab:cremi_leaderboard}
+        \end{subtable}
+        % \vspace*{0.99em}
+    % \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (March 2021)}
+    % \label{tab:results_cremi_test}
+    \caption{...
+We evaluate the algorithms by computing the Adapted Rand-Score (ARAND) and the Variation of Information Score (VI) \cite{arganda2015crowdsourcing}.
+And runtimes (\textbf{lower is better})}
+    \label{tab:scores}
+% \end{minipage}
+\end{table*}
+\begin{figure}
+\centering
+\includegraphics[width=0.48\textwidth,trim=12 76 150 13, clip]{./figs/comparison_new.pdf} % left bottom right top
+\caption{Failure cases of three algorithms included in \algname{} on challenging parts of the CREMI dataset.
+\emph{Wrongly} segmented regions are highlighted in different warm colors.
+Red arrows point to wrongly split regions; yellow ones to merge errors.
+HC-Avg returned the best segmentation.
+Data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.
+\label{fig:failure_cases}}
+\end{figure}
+\begin{figure}
+\centering
+\includegraphics[width=0.48\textwidth,trim=300 100 300 100, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
+\caption{Dendograms built by GAEC, MWS, and HC-Avg on a small SSBM (two ground truth communities represented by colors).
+The dendrograms are truncated at the level of the clustering $\Pi^*$ returned by the algorithms.
+\label{fig:dendrograms}}
+\end{figure}
+
+\subsection{Comparison results and discussion}
+% Before to evaluate the clustering algorithms on real-world graphs, we compare them on two types of synthetically generated graphs and highlight some of their fundamental properties.
+
+\textbf{Comparison to spectral clustering} -- 
+First, we compare \algname{} to spectral clustering methods for signed graphs. 
+In Fig.~\ref{fig:SSBM_scores}, we see that SPONGE$_{sym}$ and SPONGE proposed by \cite{Cucuringu2019SPONGEAG} perform particularly well on synthetic graphs generated with a SSB model.
+However, these methods do not scale up to the large graph instances considered here and they also require the user to specify the true number of clusters in advance, which is not known for most of other graph instances tested in this paper.
+For these reasons, we exclude them from our other comparison experiments.
+Table \ref{tab:cremi_spectral_experiments} in Appendix lists the scores achieved by these methods on a much smaller sub-instance of the \emph{CREMI-gridGraph} problem: even when the true number of clusters is specified in advance for the spectral methods, they perform much worse than other \algname{} algorithms, with performance drop of almost 50\%.
+
+\textbf{Complete and Single Linkage} -- In our experiments, we included these two linkage methods as baselines to highlight the difficulty of the considered graph clustering problems.
+Scores in Tables~\ref{tab:scores_3drag}-\ref{tab:scores_gridGraph} show the poor performances of these two linkage methods: Single linkage hierarchical clustering (HC-Single), which here is equivalent to thresholding the edge weights at $w_e=0$ and computing graph connected components, often returned few big under-segmented clusters.
+HC-Complete and HCC-Complete returned instead a lot of over-segmented clusters.
+% These algorithms are excluded from our next comparison experiments.
+
+\textbf{Multicut objective values} -- In Table~\ref{tab:datasets_and_energies}, we report the values of the multicut objective associated to the clusterings obtained with different \algname{} algorithms\footnote{Objective values achieved by Single and Complete linkage methods are much worse compared to other algorithms and are reported in Table \ref{tab:extended_results_cremi}, in Appendix.}.
+Although a lot of heuristics were proposed to better optimize this objective \cite{beier2016efficient,beier2014cut,kernighan1970efficient}, these methods are out of the scope of this paper, since they do not scale up to the largest graph instances considered here.
+By looking at results in Table~\ref{tab:datasets_and_energies}, we observe that GAEC almost always achieves the lowest objective values, apart from the \emph{CREMI-gridGraph} instances.
+Despite this, on graphs where a GT clustering is known, GAEC does not achieve the best ARAND scores (see Tables~\ref{tab:scores_gridGraph} and \ref{tab:scores_3drag}).
+To better understand these empirical results, we now make the following important observation.
+% This can also be observed in our experiments on synthetic graphs (Fig.
+?
+and ?), where the clustering with minimum multicut energy become very different from the ground truth clustering when the flip noise parameter $\eta$ is increased.
+
+\textbf{Size of growing clusters: Sum vs Avg linkage} -- 
+In all the studied clustering problems, we empirically observe that sum-linkage algorithms like GAEC tend to grow clusters one after the other, as shown in Fig.\ \ref{fig:intro_figure} by the unique agglomeration order of GAEC\footnote{This \emph{flooding agglomeration-strategy} of GAEC was also observed in \cite{kardoostsolving}.}.
+This is intuitively explained by the  following: initially, many of the most attractive edge weights have very similar values; when the two nodes $u,v$ with the highest attraction are merged, there is a high chance that they will have a common neighboring node $t$ belonging to the same cluster; thus, the interaction between the merged nodes $uv$ and $t$ is likely assigned to the highest priority, because it is given by the sum of two highly attractive edge weights.
+And this will start a ``chain reaction'' where only a single cluster is agglomerated at the time.
+% This \emph{flooding strategy} in the agglomeration is not observed with other linkage methods, e.g. Average, which grow clusters of similar sizes in parallel.
+In the following, we will show how this unique \emph{flooding strategy} of the sum-linkage methods can be both an advantage or a disadvantage, depending on the type of clustering problem.
+
+\textbf{Scores on SSBM graphs}  -- 
+% can be connected to any  that, depending on the edge-probability parameter $p$, are also \emph{dense}. 
+\algname{} algorithms using cannotLinkConstraints are not expected to perform well on these graphs, because of the type of employed flip noise, so we focus our comparison only on the GAEC, HC-Avg and MWS algorithms (using Sum, Average, and AbsMax linkage methods, respectively).
+Empirically, we observe that GAEC is the agglomerative algorithm performing best on SSBM graphs, almost as good as the spectral method SPONGE$_{sym}$, followed then by HC-Avg and then MWS (see Fig.~\ref{fig:SSBM_scores}).
+Given the simple properties of SSBM graphs, we will now give a specific explanation of these empirical results.
+In SSBM graphs, the number of edges $E_{ij}\equiv(S_i\times S_j)\cap E$ connecting two clusters $S_i,S_j$ is  proportional to the product $|S_i|\cdot|S_j|$ of cluster sizes.
+With Sum or Avg linkage methods, we expect the flipping noise to be ``averaged out'' as soon as the set $E_{ij}$ becomes larger and clusters grow in size.
+On the other hand, when clusters are small, it is more likely that several of the edges in $E_{ij}$ are flipped and the algorithm makes a mistake by merging two clusters belonging to different ground truth communities.
+From this observation, it follows that the \emph{flooding strategy} of the sum-linkage algorithm GAEC is a very good strategy on these types of graphs, because clusters are immediately grown in size (as compared to the avg-linkage method HC-Avg that grows small clusters and merge them only at the very end).
+This observation also explains the empirical results of \cite{chehreghani2020hierarchical}, which involved graph instances with very similar structure to the ones considered here.
+On the other hand, the MWS algorithm is not expected to perform well on these graphs because of the high sensitivity of the AbsMax linkage to flipping noise.
+In Propositions \ref{prop:MWS_SSBM_1} and \ref{prop:MWS_SSBM_2} (see Appendix), we prove that on SSBM graphs the merging steps of the MWS algorithm are given by a sequence of ``coin flip'' decisions with a probability proportional to the noise parameter $\eta$, independently on the cluster sizes.
+
+\textbf{Scores on CREMI instance-segmentation} -- 
+SSBM graphs are \emph{non-planar} graphs, where every edge has the same probability to be present in the graph.
+On the other hand, the \emph{gridGraph} and \emph{3D-rag} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: weather a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance).
+Tables~\ref{tab:scores_3drag}-\ref{tab:scores_gridGraph} show that average linkage methods (HC-Avg, HCC-Avg) strongly outperforms other methods on \emph{CREMI-gridGraph} instances and also achieves the best scores on \emph{CREMI-3D-rag} graphs.
+Sum-based linkage methods (GAEC, HCC-Sum) do not perform well on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}).
+This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods does not work well on grid-graphs, because of the sparse local edge connections with strongly spatially-correlated noise (given that edge weights are predicted by a CNN)\footnote{This effect is not as strong on \emph{3D-rag} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
+To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}.
+The plot in Fig.~\ref{fig:noise_plots} confirms that HC-Avg and HCC-Avg perform well even in the presence of strong structured noise, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (MWS).
+It is not a surprise that the AbsMax linkage used by MWS is not robust to this type of structured noise.
+However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} proves how MWS can achieve competitive performances with considerably lower runtimes.
+
+\textbf{Results on CREMI challenge} -- 
+Table~\ref{tab:cremi_leaderboard} shows how the \emph{HCC-Avg} and \emph{HC-Avg} clustering algorithms included in the proposed \algname{} framework achieve state-of-the-art performances on the CREMI challenge, when combined to the predictions of our CNN.
+Most of other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs.
+As we also showed in Table ~\ref{tab:scores_3drag}, this approach considerably reduces the size of the clustering problem and, consequently, the post-processing time.
+On the other hand, our method achieves better performances by operating directly on pixels and removing in this way the parameter tuning necessary to obtain good super-pixels, which are usually highly dataset dependent.
+
+% Note that the test volumes of the challenge contain several imaging artifacts that make segmentation particularly challenging.
+% However: handcrafted and dataset dependent, performs better, no
+
+% Given By building a grid-graph from our CNN predictions  and solving a clustering problem with the \emph{HCC-Avg} and \emph{HC-Avg} algorithms, representing the best performing algorithms included in the proposed \algname{} framework, we achieve state-of-the-art performances on the competitive CREMI challenge (see Table~\ref{tab:cremi_leaderboard}).
+
+Specify that we divided samples into four blocks and then run the agglomeration again (moreover, run seeded WS to get rid of small segments).
+Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights. 
+Long-range connections are more noisy. 10\% represents a good compromise.
+% then \algname{} with cannot-link constraints shows a clear tendency to over-cluster. \\
+
+% Superpixels are nice because they reduce runtime and represents the standard choices for connectomics (all bug LSI-Masks use some kind of similar form).
+But method is very dataset-dependent and require the user to set a series of parameters
+
+% So far no other method was done from pixels
+
+% The competitive performance of this simple parameter-free algorithm is also reported in Table \ref{tab:results_cremi_test}, showing the current leader-board of the challenge:
+
+% Note that the test volumes contain several imaging artifacts that make segmentation particularly challenging. 
+% and might profit from more robust edge statistics of super-pixel based approaches.
+
+% and can also avoid errors that result from wrong superpixels that cannot be fixed during later agglomeration.
+% In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets. 
+% Appendix Table \ref{tab:extended_results_cremi} lists the performances and the run-times for all tested \algname{} linkage criteria.\\
+
+% We first evaluate and compare the agglomerative clustering algorithms described in the generalized framework on the task of neuron segmentation in electron microscopy (EM) image volumes.
+This application is of key interest in connectomics, a field of neuro-science with the goal of reconstructing neural wiring diagrams spanning complete central nervous systems.
+Currently, only proof-reading or manual tracing yields sufficient accuracy for correct circuit reconstruction \cite{schlegel2017learning}, thus further progress is required in automated reconstruction methods.
+
+% EM segmentation is commonly performed by first predicting 
+% boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment.
+% The affinities do not have to be limited to immediately adjacent pixels.
+% Thus, similarly to \cite{lee2017superhuman}, we train a CNN to predict both short- and long-range affinities
+% and use them as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image.

### 2021-03-01 chapters/supplementary.tex
Add dendrograms; finish rewriting experiments sec.

@@
 \section{Supplementary material}
+\TODO{Use S notation for the sections!}
 
@@
         \begin{tabular}{l|c|c|c|c|c}
-          \algname{} linkage & \makecell{CREMI-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
+          \algname{} linkage & \makecell{CREMI-Score\\(lower better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
 Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 0.494 & 3.49 $\cdot$ 10$^4$ \\
@@
     CLC stands for cannot-link constraints.
-For all algorithms, the chosen value of bias parameter was $\beta = 0$.
-We used a machine with CPU Intel(R) Xeon(R) E7-4870 @ 2.40GHz for our comparison experiments.}
+For all algorithms, the chosen value of bias parameter was $\beta = 0.5$.
+We used a machine with CPU Intel(R) Xeon(R) E7-4870 @ 2.40GHz for our comparison experiments.
+\TODO{Need to include scores Single and Complete linkage!}}
     \label{tab:extended_results_cremi}
@@
 %In the next section \ref{sec:alg_update_rules}, we will show that this happens only for certain linkages and only when constraints are not enforced
+
+\begin{figure}[t]
+\centering
+\begin{minipage}[t]{0.48\textwidth}
+\vspace{0pt}
+\centering
+% \footnotesize
+\begin{tabular}[t]{L{9em} M{7em}}
+           Method & Rand-Score \\ \midrule
+           \textbf{GASP Average} & \textbf{0.8966} \\
+GASP Sum & 0.8965 \\
+GASP Abs Max & 0.8932 \\
+SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG} & 0.5839\\
+$L_{sym}$ \cite{kunegis2010spectral} & 0.1931 \\
+SPONGE \cite{Cucuringu2019SPONGEAG} & 0.0789 \\
+BNC \cite{chiang2012scalable} & 0.0074 \\
+        \end{tabular}
+    \captionof{table}{\algname{} compared to spectral clustering methods on a small crop of the CREMI dataset (sample B).}
+    \label{tab:cremi_spectral_experiments}
+\end{minipage}
+% \begin{minipage}[t]{0.38\textwidth}
+% \vspace{0pt}
+% \centering
+%         \includegraphics[width=1.\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf} % 0.45
+%         \caption{\algname{} performances compared to spectral methods on synthetic graphs.
+The spectral methods were given the true number of clusters as input, in contrast to \algname{}.
+\TODO{Define paramters SSB; explain percentile stuff (for both noise experiments, save space!)}}
+%     \label{fig:SSBM_scores}
+% \end{minipage}
+\end{figure}
+
+\section{Comparison with spectral clustering} \label{sec:spectral_clust}
+In this section we compare \algname{} to spectral clustering (SC) methods for signed graphs both on synthetic graphs and real ones from neuron segmentation.
+These methods require the user to specify the number of clusters in advance, in contrast to our proposed agglomeration method that determines the cluster number based on the signed weights of the graph.
+In the following comparison, we make these baselines as strong as possible by specifying the true number of clusters for the spectral methods.
+
+\textbf{Synthetic graphs} -- First, we compare the clustering performance on synthetic graphs generated by a signed stochastic block model (SSBM), where SC performs well.
+In particular, we used an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N=10^5$ vertices and edge probability $p=0.1$.
+Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k=100$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) had Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $0.1$.
+To model noise, we flipped the sign of each edge independently with probability $\eta \in [0, 0.4]$.
+Median scores, 25th and 75th percentiles over 30 repetitions are shown in Fig.~\ref{fig:SSBM_spectral_experiments}: GASP achieved scores comparable to SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG}, a recently proposed SC method.
+The specific design choice of a \emph{sign flipping} noise used in the SSBM experiments turned out to favor GASP with \emph{Sum} linkage that, according to the experiments presented in Sec.~\ref{sec:results}, is the one with the lowest tendency to over-cluster and grows one cluster at the time.
+
+\textbf{Neuron segmentation} -- We extended the comparison with spectral methods to the task of neuron segmentation.
+Since SC cannot scale to the full CREMI dataset, we evaluated \algname{} and SC on a smaller $10\times100\times100$ voxels volume resulting in a graph with $10^5$ nodes and~$\sim10^6$ edges.
+Scores are summarized in Table \ref{tab:cremi_spectral_experiments}.
+%suggested by the reviewer that performed best in the recent comparison \cite{Cucuringu2019SPONGEAG}: one based on the Balanced Normalized Cut (BNC) \cite{chiang2012scalable}; another on the symmetrically normalized Signed Laplacian ($L_{sym}$) \cite{kunegis2010spectral}; SPONGE and SPONGE$_{sym}$ algorithms were recently proposed in \cite{Cucuringu2019SPONGEAG}.
+Despite the fact that the true number of ground truth clusters was given as an input to the SC methods, GASP significantly outperformed them on neuro-data.
+SC methods seem to have more difficulties when the graph is sparse.
+Moreover, they did not handle well pixels on the boundaries between segments and tended to cluster them together.
+Increasing $k$ did not improve their scores either.
+
+\begin{prop}\label{prop:MWS_SSBM_1}
+Consider a graph $\mathcal{G}(V,E)$ generated with a SSBM with parameters $N,p,k,\sigma$ and an associated ground truth (GT) clustering $\hat{\Pi}=\{\hat{S}_1, \ldots, \hat{S}_k\}$.
+Then, assume that after some merging-iterations of the MWS algorithm the clustering $\Pi$ is found.
+Then, any two clusters $S_i,S_j\in \Pi$ have probability $|E_{ij}| / |E_{\Pi}^1|$ to be selected in the next iteration of the algorithm, where $E_{\Pi}^1$ is the multicut associated to $\Pi$ and $E_{ij}\equiv(S_i\times S_j)\cap E$ is the set of edges connecting the two clusters.
+\end{prop}
+
+\begin{prop}\label{prop:MWS_SSBM_2}
+Given the assumptions of Prop.~\ref{prop:MWS_SSBM_1}, let $E_{ij}^+=\{(u,v) \in E_{ij} | \exists \hat{S}\in \hat{\Pi} \, \mathrm{s.t.} \, u\in \hat{S} \wedge v\in \hat{S} \}$ denote the set of true attractive GT edges connecting two clusters $S_i,S_j$
+\begin{equation}
+\sum_{ij} \frac{|E_ij^+|}{||}
+\end{equation}
+\end{prop}
+
+Then, the MWS algorithm will assign highest priority to 
+Among these edges, we define the set of true attractive GT edges as . Finally, let $f^+=|E_{ij}^+| / |E_{ij}|$ denote the fraction of true attractive edges. Then, the Mutex Watershed algorithm
+
+\begin{itemize}
+\item each pair of clusters $S_i,S_j$ has probability $|E_{ij}| / |E_{\Pi}^1|$ to have the interaction with highest priority 
+\item if the pair of clusters $S_i,S_j$ is given the highest priority by the MWS Algorithm, then they have has a probability $p^+=f^+(1-\eta) + f^+ \eta$ to be merged and $p^-=1-p^+$ to be constrained.
+\end{itemize}
+will assign a positive interaction to clusters $S_i,S_j$ with probability $f^+(1-\eta) + f^+ \eta$. 
+Remarks: this quantity does not depend on the size of $|E_{ij}|$ (so it won't change when clusters grow in size); if $f^+=1$ (i.e.
+$S_i,S_j$ are subclusters of the same GT cluster), then MWS will merge them with probability $1-\eta$; if $f^+=0$ (i.e.
+$S_i,S_j$ are subclusters of two different GT clusters), then MWS will merge them with probability $\eta$.
+\TODO{Assumption about $\sigma$?}

### 2021-03-01 extra/rebuttal_CVPR/latex/egrebuttal.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{5813} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Rebuttal: GASP, a generalized framework for agglomerative clustering of signed graphs \\ and its application to Instance Segmentation}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

We thank the three reviewers for their helpful comments and for pointing out that our manuscript is very clear and well written (R1, R2, R3), is theoretically sound and provides a novel level of abstraction (R1) and is highly valuable in practice by achieving competitive accuracies on two publicly available benchmarks (R1, R3). \\

\textbf{Novelty and main contributions (R2, R3)} --
% Both R2 and R3 have raised questions regarding the novelty of our contribution. 
Our main contribution is GASP, a  framework that generalizes several existing and novel algorithms for agglomerative clustering of signed graphs, providing a powerful tool to study these methods.
R2 states that \emph{``exactly the same algorithms as GASP have been proposed''}, referring to GF [54] and GAEC [40]. 
Indeed, GF and GAEC are special cases of GASP, as we point out in Table 1 and lines 369-371. However, they are only two out of 14 algorithms described in our framework. In this paper we prove, for the first time, that Mutex Watershed [90] is another specialization of GASP -- an insight which we claim is nontrivial -- but all other algorithms are new at all, or at least in the context of signed graph partitioning. Indeed, one of the new algorithms, which on signed graphs has not been studied before, turns out to be the best among all variants we explored.
% Indeed, when using the sum linkage criterion, GASP is equivalent to GAEC (without cannot link constrants) or GF (with cannot link constraints) and we point out this relation in Table 1 and Section 3.3., lines 369-371. R2 also claims that \emph{``extension to include other linkage strategies is trivial''}, although, in our opinion, the fact that switching to another linkage criterion can be achieved with little changes shows one of the major strengths of our contribution: easy classification and comparison of agglomerative algorithms for signed graph clustering. Our framework can express the Mutex Watershed Algorithm [90] (so far never shown as agglomerative clustering algorithm), GAEC, and GF, as well as algorithms that, to the best of our knowledge, have not been studied systematically before, including signed graph clustering with average linkage.

R2 also states that \emph{``extension to include other linkage strategies is trivial''}. We agree wholeheartedly, and indeed consider this a great strength of the proposed framework, which allows an easy classification and comparison of agglomerative algorithms for signed graph clustering.

R3 points out that the use of signed graph clustering for instance segmentation is not novel and has been applied both in the context of natural images and EM connectomics. We agree, and cite pertinent prior work [42, 2, 7, 94]. Rather, we introduce a new framework that generalizes several existing methods and yields variants that have not been studied before. We believe that our contribution generates new insights into the utility of agglomerative clustering methods for Computer Vision and show their competitive performance when combined with predictions from neural networks, despite the fact that they are simple and efficient compared to other methods for signed graph partitioning. 
% Note that we cite important prior work, including several papers by the Hamprecht and Andres groups, who both have pioneered the use of signed graph clustering for instance segmentation.

\textbf{Comparison to multicut solvers (R2)} -- 
% R2 also quotes us as ``Authors say in lines 77-80 that no study has compared multicut solvers, while in fact there are plenty''. 
In lines 75-80 we write that \emph{``Agglomerative clustering algorithms for signed graphs have clear advantages: [...]. Despite the fact that a variety of these algorithms exist, no overarching study so far has been conducted to compare their robustness [...]''}. 
To the best of our knowledge, this claim pertaining to agglomerative algorithms is correct, and R2 does not offer references to the contrary.
% We do not claim, as suggested by R2, that there have not been any extensive studies for comparing \emph{multicut solvers}, but for \emph{agglomerative algorithms for signed graph clustering}. 
As R2 correctly points out, [54] contains an extensive evaluation of local search algorithms as multicut approximations, including the agglomerative methods GAEC and GF. However, [54] does not make a connection to agglomerative methods with different linkage criteria studied here. 
% Moreover, the other local search algorithms compared in [54] would not scale up well to the size of the problems studied in our work. 
Furthermore, R2 mentions the comparison of multicut solvers in [Beier et al., Cut, Glue \& Cut: A Fast, Approximate Solver for Multicut Partitioning]. We are aware of this work, but did not consider it sufficiently relevant in the context of our contribution, because it does not contain any comparison with agglomerative methods. Still, in the revised version we will cite it following R2.

\textbf{Experiments on larger graphs (R2)} --
R2 points out that we should conduct experiments on a broader set of problems and use graphs of larger size, referring to the experiments in [54]. We note that our experiments cover two important applications of instance segmentation from very different images (Cityscapes vs electron microscopy images) as well as clustering on random graphs, where we compare favorably to spectral methods. Regarding the problem size, note that the CREMI problem used for evaluation (Table 2) is solved on the pixel grid graph and contains $7\cdot 10^7$ nodes and $6\cdot 10^8$ edges, which is two orders of magnitude larger than the largest instance segmentation problem in [54] consisting of $10^5$ nodes and $10^7$ edges. In the revised version of the paper, we will add the specifications of the problem size on CREMI.

\textbf{Relevance of the results on CREMI (R2)} --
In the revised version, we will better define the CREMI score, which is given by the geometric mean of adapted Rand Error and Variation of Information, two commonly used metrics to evaluate clusterings. Given the small gap of 0.02 to the leading submission and the much bigger gap to other published methods, e.g. more than 0.3 gap for [95], it is fair to claim that we are competitive with state-of-the-art. In the revised version of the paper, we will comment on our standing in the CREMI leader-board.

\textbf{Clarifications about cityscapes experiments (R2)} --
R2 asks about the difference between the agglomeration method used in GMIS [63] and GASP. GMIS uses average linkage agglomerative clustering on an \emph{unsigned graph}, whereas GASP operates on a \emph{signed graph}. 
% As a consequence our algorithm can be applied without a hyper-parameter for the stopping criterion. 
In addition, as we point out in lines 769-771, the agglomeration procedure in GMIS is applied in multiple stages, which creates the need for further hyper-parameters and makes it more complex than our algorithm, which achieves comparable (slightly better) accuracy.

We have fine tuned the GMIS affinity predictions using the Dice Loss, which is a common approach to improve results for sparse spatial targets like affinities, see [90].

% {\small
% \bibliographystyle{ieee}
% \bibliography{egbib}
% }

\end{document}

### 2021-03-01 chapters/0_abstract.tex
Update to ECCV template
Update to CVPR2021 template
Small changes

@@
 \begin{abstract}
-We propose a new theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes.
+\TODO{Update} We propose a new theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes.
 This framework defines GASP, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints.
@@
 We find that one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset.
+% \keywords{Partitioning of Signed Graphs, Generalized Framework, Agglomerative Clustering, Instance Segmentation}
 \end{abstract}

### 2021-03-01 chapters/1_intro.tex
Small changes

@@
 \section{Introduction}
-In computer vision, the partitioning of weighted graphs has been successfully applied to tasks as diverse as image segmentation, object tracking and pose estimation. 
+\TODO{Update} In computer vision, the partitioning of weighted graphs has been successfully applied to tasks as diverse as image segmentation, object tracking and pose estimation. 
 Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes.
@@
 In Sec.~\ref{sec:spectral_clust}, we also show how \algname{} outperforms spectral clustering methods on the task of neuron segmentation and how on synthetic graphs it achieves similar scores to a recently proposed spectral method for signed graphs.
-\TODO{Define HC and AC abbrv}
+\TODO{Define HC abbrv}
 

### 2021-03-01 chapters/5_experiments_compare_rules.tex
Small changes

@@
 
-\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
 \begin{figure}[t]
 \centering
-    \begin{subfigure}[t]{0.47 \textwidth}
+\includegraphics[width=0.47\textwidth,trim=0.25in 0.in 0.5in 0.in,clip]{./figs/SSBM_experiments.pdf}
+        \caption{Scores on SSBM graphs}
+\end{figure}
+\begin{figure}[t]
 \centering
-        \includegraphics[width=\textwidth,trim=0.25in 0.in 0.5in 0.in,clip]{./figs/SSBM_experiments.pdf}
-        \caption{Scores on SSBM graphs}
-    \end{subfigure} \hfill
-    \begin{subfigure}[t]{0.47 \textwidth}
-        \centering
-        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
+\includegraphics[width=0.47\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
         \caption{Scores on \emph{CREMI-gridGraph} perturbed with noise}
-    \end{subfigure}
+\end{figure}
 
-    % \begin{subfigure}[t]{0.32 \textwidth}
+% \captionsetup[subfigure]{justification=centering, singlelinecheck=off}
+% \begin{figure}[t]
+% \centering
+%     \begin{subfigure}[t]{0.47 \textwidth}
+%         \centering
+%         \includegraphics[width=\textwidth,trim=0.25in 0.in 0.5in 0.in,clip]{./figs/SSBM_experiments.pdf}
+%         \caption{Scores on SSBM graphs}
+%     \end{subfigure} \hfill
+%     \begin{subfigure}[t]{0.47 \textwidth}
 %         \centering
 %         \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
-    % \end{subfigure}\hfill
-    % \begin{subfigure}[t]{0.32 \textwidth}
-    %     \centering
-    %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
+%         \caption{Scores on \emph{CREMI-gridGraph} perturbed with noise}
 %     \end{subfigure}
-    %     \begin{subfigure}[t]{0.49 \textwidth}
-    %     \centering
-    %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
-    %     \caption{No long-range predictions: \\$p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
-    % \end{subfigure} \hfill
-    % \begin{subfigure}[t]{0.49 \textwidth}
-    %     \centering
-    %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
-    %     \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
-    % \end{subfigure}
-\caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust.
+
+%     % \begin{subfigure}[t]{0.32 \textwidth}
+%     %     \centering
+%     %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
+%     % \end{subfigure}\hfill
+%     % \begin{subfigure}[t]{0.32 \textwidth}
+%     %     \centering
+%     %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
+%     % \end{subfigure}
+%     %     \begin{subfigure}[t]{0.49 \textwidth}
+%     %     \centering
+%     %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
+%     %     \caption{No long-range predictions: \\$p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
+%     % \end{subfigure} \hfill
+%     % \begin{subfigure}[t]{0.49 \textwidth}
+%     %     \centering
+%     %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
+%     %     \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
+%     % \end{subfigure}
+% \caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust.
 Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions.
@@
 Experiments are performed on a crop of CREMI training sample B.
-\algname{} performances compared to spectral methods on synthetic graphs.
+% \algname{} performances compared to spectral methods on synthetic graphs.
 The spectral methods were given the true number of clusters as input, in contrast to \algname{}.
-\TODO{Define paramters SSB; explain percentile stuff (for both noise experiments)}
-}\label{fig:noise_plots}
-\end{figure}
+\TODO{Define paramters SSB; explain percentile stuff (for both noise experiments), user ARAND-error}
+% }\label{fig:noise_plots}
+% \end{figure}
 

### 2021-03-01 chapters/5_experiments_intro.tex
Small changes

@@
 The predicted affinities $a_e\in[0,1]$, which represent how likely it is for a pair of pixels to belong to the same neuron segment, are then mapped to signed edge weights $w_e=a_e-0.5$, resulting in a 3D grid-graph having a node for each pixel/voxel of the  image\footnote{To map affinities to signed weights, we also tested the \emph{logarithmic mapping} proposed in \cite{finkel2008enforcing,andres2012globally}, but it performed worse in our experiments.}.
+\TODO{long-range 10\%} 
+% Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights. Long-range connections are more noisy. 10\% represents a good compromise.
 We divided the three training samples of the CREMI challenge, which consists of approximately 196 million voxels each, into five sub-blocks for a total of 15 graph clustering problems (named \emph{CREMI-gridGraph} in Table~\ref{tab:datasets_and_energies}).
-% \TODO{long-range probs}
 
@@
 
-        \begin{tabular}{l  c  r  c  c  c r r r r r r}
-        \toprule
-        Clustering problem & \makecell{Graph Type} & $\#I$ & $|V|$ & $|E|$ & GT & GAEC \cite{keuper2015efficient} & HCC-Sum & MWS \cite{wolf2018mutex} & HC-Avg & HCC-Avg \\ \midrule
-        \emph{Modularity Clustering} \cite{brandes2007modularity} & \emph{complete} & 6& 34-115 & 561-6555 & \HollowBox & -0.457 & -0.453 & -0.073 & \textbf{-0.467} & \textbf{-0.467} \\ 
-        \emph{Image Segmentation} \cite{andres2011probabilistic} & \emph{rag} & 100 & 156-3764 &  439-10970  & \HollowBox & \textbf{-2,955} & -2,953 & -2,901 & -2,903 & -2,896\\
-        \emph{Knott-3D (150-300-450)} \cite{andres2012globally} & \emph{3D-rag} & 24 & 572-17k & 3381-107k & \HollowBox & \textbf{-36,667} & -36,652 & -35,200 & -35,957 & -35,631\\
+        \begin{tabular}{l  c  r  c  c  | r r r r r r}
+        % \toprule
+        &&&&\multicolumn{1}{c}{}&\multicolumn{5}{c}{Multicut objective values associated to final clusterings:} \\
+        Clustering problem & \makecell{Graph Type} & $\#I$ & $|V|$ & $|E|$  & \multicolumn{1}{r}{GAEC \cite{keuper2015efficient}} & HCC-Sum & MWS \cite{wolf2018mutex} & HC-Avg & HCC-Avg \\ \midrule
+        \emph{Modularity Clustering} \cite{brandes2007modularity} & \emph{complete} & 6& 34-115 & 561-6555 & % \HollowBox & 
+        -0.457 & -0.453 & -0.073 & \textbf{-0.467} & \textbf{-0.467} \\ 
+        \emph{Image Segmentation} \cite{andres2011probabilistic} & \emph{rag} & 100 & 156-3764 &  439-10970  & % \HollowBox 
+        \textbf{-2,955} & -2,953 & -2,901 & -2,903 & -2,896\\
+        \emph{Knott-3D (150-300-450)} \cite{andres2012globally} & \emph{3D-rag} & 24 & 572-17k & 3381-107k & % \HollowBox & 
+        \textbf{-36,667} & -36,652 & -35,200 & -35,957 & -35,631\\
         % \emph{Knott-3D-300} & \emph{3D-rag} & 8& & & \HollowBox\\
         % \emph{Knott-3D-450}& \emph{3D-rag} & 8 & & & \HollowBox\\  
-        \emph{CREMI-3D-rag (OurCNN)}  & \emph{3D-rag} & 3& 134k-157k & 928k-1065k & \CrossedBox & \textbf{-1,112,287} & -1,112,286& -1,109,731 & -1,112,177 & -1,112,100\\ 
-        \emph{Fruit-Fly Level 1-4} \cite{pape2017solving} & \emph{3D-rag} & 4& 5m-11m & 28m-72m & \HollowBox & \textbf{-151,022} & -151,017 & -150,879 & -150,909 & -150,876\\
-        \emph{CREMI-gridGraph (OurCNN)} & \emph{gridGraph} & 15& 39m & 140m & \CrossedBox & -73,317,601 & -73,328,867 & -73,330,568 & \textbf{-73,502,947} & -73,474,856\\
-        \emph{Fruit-Fly Level Global} \cite{pape2017solving} & \emph{3D-rag} & 1& 90m & 650m & \HollowBox & \textbf{-151,688} & -151,596 & -146,315 & -150,466 & -150,171 \\
+        \emph{CREMI-3D-rag (OurCNN)}  & \emph{3D-rag} & 3& 134k-157k & 928k-1065k % & \CrossedBox 
+        & \textbf{-1,112,287} & -1,112,286& -1,109,731 & -1,112,177 & -1,112,100\\ 
+        \emph{Fruit-Fly Level 1-4} \cite{pape2017solving} & \emph{3D-rag} & 4& 5m-11m & 28m-72m %& \HollowBox 
+        & \textbf{-151,022} & -151,017 & -150,879 & -150,909 & -150,876\\
+        \emph{CREMI-gridGraph (OurCNN)} & \emph{gridGraph} & 15& 39m & 140m %& \CrossedBox 
+        & -73,317,601 & -73,328,867 & -73,330,568 & \textbf{-73,502,947} & -73,474,856\\
+        \emph{Fruit-Fly Level Global} \cite{pape2017solving} & \emph{3D-rag} & 1& 90m & 650m % & \HollowBox 
+        & \textbf{-151,688} & -151,596 & -146,315 & -150,466 & -150,171 \\
         % \emph{(CREMI-pixGrid-LSIMasksUNet)} & \emph{gridGraph} & 1 & & 4 & \CrossedBox\\
@@
     \end{subtable} 
-    \caption{List of compared signed graph clustering problems: for each, we specify the number of instances $\# I$, nodes $|V|$, edges $|E|$, and whether a ground truth clustering is available.
+    \caption{List of compared signed graph clustering problems: for each, we specify the number of instances $\# I$, number of nodes $|V|$, and number of edges $|E|$.
 We compare algorithms in the \algname{} framework by evaluating which of the obtained clusterings is associated to the lowest value of the multicut objective defined in Eq.~\ref{eq:MC_objective} (\textbf{lower is better}).}
@@
         \toprule
-          & \makecell{ARAND\\Score} & \makecell{VOI\\split} & \makecell{VOI\\merge}&  \makecell{Runtime\\(s)} \\ \midrule 
+          & \makecell{ARAND\\error} & \makecell{VOI\\split} & \makecell{VOI\\merge}&  \makecell{Runtime\\(s)} \\ \midrule 
 \textbf{HC-Avg} & \textbf{0.0487} & 0.387 & 0.258 & 2344 \\
@@
         \toprule
-          & \makecell{ARAND\\Score} & \makecell{VOI\\split} & \makecell{VOI\\merge}&  \makecell{Runtime\\(s)} \\ \midrule 
+          & \makecell{ARAND\\error} & \makecell{VOI\\split} & \makecell{VOI\\merge}&  \makecell{Runtime\\(s)} \\ \midrule 
 \textbf{HC-Avg} & \textbf{0.0896} & 0.603 & 0.323 & 86 \\
@@
         \toprule
-          & \makecell{CREMI\\Score} & \makecell{ARAND\\Score} & \makecell{VOI\\split} & \makecell{VOI\\merge}    \\ \midrule 
+          & \makecell{CREMI\\Score} & \makecell{ARAND\\error} & \makecell{VOI\\split} & \makecell{VOI\\merge}    \\ \midrule 
 \emph{OurCNN: 3D-rag + LMC} & \textbf{0.221} & \textbf{0.108} & \textbf{0.339} & 0.115 \\
@@
     % \label{tab:results_cremi_test}
-    \caption{...
-We evaluate the algorithms by computing the Adapted Rand-Score (ARAND) and the Variation of Information Score (VI) \cite{arganda2015crowdsourcing}.
-And runtimes (\textbf{lower is better})}
+    \caption{\textbf{(a-b)} Scores and run times of algorithms in the \algname{} framework on the \emph{CREMI-gridGraph} and \emph{CREMI-3D-rag} clustering problems: average linkage methods performed best.
+Measures shown are Adapted-Rand error (ARAND, lower is better), Variation of Information \cite{arganda2015crowdsourcing} (VOI-merge for under-clustering error, VOI-split for over-clustering error, lower is better).
+\textbf{(c)} Current leading entries in the CREMI challenge leaderboard (March 2021).
+CREMI-score is given by geometric mean of (VOI-split + VOI-merge)  and adapted RAND error (lower is better).}
     \label{tab:scores}
@@
 The dendrograms are truncated at the level of the clustering $\Pi^*$ returned by the algorithms.
-\label{fig:dendrograms}}
+\TODO{Update}  \label{fig:dendrograms}}
 \end{figure}
@@
 On the other hand, the \emph{gridGraph} and \emph{3D-rag} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: weather a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance).
-Tables~\ref{tab:scores_3drag}-\ref{tab:scores_gridGraph} show that average linkage methods (HC-Avg, HCC-Avg) strongly outperforms other methods on \emph{CREMI-gridGraph} instances and also achieves the best scores on \emph{CREMI-3D-rag} graphs.
-Sum-based linkage methods (GAEC, HCC-Sum) do not perform well on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}).
+Tables~\ref{tab:scores_3drag}-\ref{tab:scores_gridGraph} show that average linkage methods (\emph{HC-Avg}, \emph{HCC-Avg}) strongly outperforms other methods on \emph{CREMI-gridGraph} instances and also achieves the best scores on \emph{CREMI-3D-rag} graphs.
+Sum-based linkage methods (\emph{GAEC}, \emph{HCC-Sum}) do not perform well on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}).
 This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods does not work well on grid-graphs, because of the sparse local edge connections with strongly spatially-correlated noise (given that edge weights are predicted by a CNN)\footnote{This effect is not as strong on \emph{3D-rag} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
 To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}.
-The plot in Fig.~\ref{fig:noise_plots} confirms that HC-Avg and HCC-Avg perform well even in the presence of strong structured noise, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (MWS).
-It is not a surprise that the AbsMax linkage used by MWS is not robust to this type of structured noise.
-However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} proves how MWS can achieve competitive performances with considerably lower runtimes.
+The plot in Fig.~\ref{fig:noise_plots} confirms that \emph{HC-Avg} and \emph{HCC-Avg} perform well even in the presence of strong structured noise, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (\emph{MWS}).
+It is not a surprise that the AbsMax linkage used by \emph{MWS} is not robust to this type of structured noise.
+However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} proves how \emph{MWS} can achieve competitive performances with considerably lower runtimes.
 
@@
 As we also showed in Table ~\ref{tab:scores_3drag}, this approach considerably reduces the size of the clustering problem and, consequently, the post-processing time.
-On the other hand, our method achieves better performances by operating directly on pixels and removing in this way the parameter tuning necessary to obtain good super-pixels, which are usually highly dataset dependent.
-
+On the other hand, our method achieves better performances by operating directly on pixels (\emph{gridGraph+HCC-Avg}) and removes in this way the parameter tuning necessary to obtain good super-pixels, which are usually highly dataset dependent.
+To scale up the clustering algorithms to the pixel-based problem given by the full test-volumes, we divided each volume into four sub-blocks, and then combined the resulting clusterings by running the clustering algorithms again on the combined graph.
 % Note that the test volumes of the challenge contain several imaging artifacts that make segmentation particularly challenging.
@@
 
-Specify that we divided samples into four blocks and then run the agglomeration again (moreover, run seeded WS to get rid of small segments).
-Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights. 
-Long-range connections are more noisy. 10\% represents a good compromise.
+% To scale up the pixel-based aggSpecify that we divided samples into four blocks and then run the agglomeration again (moreover, run seeded WS to get rid of small segments).
+
 % then \algname{} with cannot-link constraints shows a clear tendency to over-cluster. \\

### 2021-03-02 chapters/0_abstract.tex
Shuffle stuff around; update intro

@@
 \begin{abstract}
-\TODO{Update} We propose a new theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes.
+We propose a new simple theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes.
 This framework defines GASP, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints.
 We prove the equivalence of existing clustering methods to some of those combinations, and introduce new algorithms for combinations which have not been studied before. 
-On stochastic block model problems, GASP compares favorably to spectral clustering.
-More importantly, we conduct a systematic comparison of various instantiations of GASP in image instance segmentation problems, in terms of accuracy but also efficiency and robustness to noise.
-We find that one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset.
+We also study theoretical properties of these combinations and prove which one of them define ultrametrics on the graph.
+% On stochastic block model problems, GASP compares favorably to spectral clustering. 
+We conduct a systematic comparison of various instantiations of GASP on a large variety of both synthetic and existing signed clustering problems, in terms of accuracy but also efficiency and robustness to noise.
+More importantly, we find that some of the algorithms proposed in our framework, when combined to the predictions from a CNN model, result in a simple instance segmentation pipeline that achieves state-of-the-art performances on the competitive CREMI 2016 EM segmentation benchmark.
 % \keywords{Partitioning of Signed Graphs, Generalized Framework, Agglomerative Clustering, Instance Segmentation}

### 2021-03-02 chapters/1_intro.tex
Shuffle stuff around; update intro

--- 2021-03-01 chapters/1_intro.tex
@@
 % !TEX root = ../agglo_clust_review.tex
-
-\section{Introduction}
-In computer vision, the partitioning of weighted graphs has been successfully applied to tasks as diverse as image segmentation, object tracking and pose estimation. 
-Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes.
-These methods require users to specify the desired numbers of clusters (as in spectral clustering) or a termination criterion (e.g.\ in iterated normalized cuts) or even to add a seed for each object  (e.g.\ seeded watershed or random walker).
-
-Other graph clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between nodes.
-The advantage of signed graphs over positive-weighted graphs is that balancing attraction and repulsion allows us to obtain a clustering without defining additional parameters.
-A canonical formulation of the signed graph partitioning problem is the \emph{multicut} or \emph{correlation clustering} problem \cite{kappes2011globally,chopra1991multiway}.
-This problem is NP-hard, though many approximate solvers have been proposed \cite{lange2018combinatorial,pape2017solving,beier2016efficient,yarkony2012fast}.
-The general problem of graph partitioning can also be solved approximately by greedy agglomerative clustering \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}.
-Agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter-free and efficient.
-Despite the fact that a variety of these algorithms exist, no overarching study has so far been conducted to compare their robustness and efficiency or to provide guidelines for matching an algorithm to the partitioning problem at hand.
-
-In this paper, we propose a new theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering on positive-weighted graphs \cite{lance1967general}.
-This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}.
-We then formally prove that some of the combinations correspond to existing clustering algorithms and introduce new algorithms for combinations which have not been explored before.
-
-We evaluate and compare these algorithms on \emph{instance segmentation} -- a computer vision task of assigning each pixel of an image to an object instance. 
-We use a CNN to predict the edge weights of a graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms in our framework (see Fig.~\ref{fig:intro_figure}).
 
@@
     \caption{Clustering algorithms included in the proposed \algname{} framework, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
-New algorithms are highlighted in yellow.
+New algorithms are highlighted in yellow (hierarchical clustering with constraints, HCC).
 Algorithms typeset in bold font define an ultrametric on the graph (see Eq.~\ref{eq:UM_def}).
 Algorithms included in the green box, are weight-shift invariant (see Prop.~\ref{prop:weight_shift_invariant}).
-    We denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two cluster $S_i, S_j$. } 
+    We denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two clusters $S_i, S_j$. } 
     \label{tab:linkage-criteria}
@@
 
-With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we benchmark all algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
-We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms all previously known agglomeration methods expressed in the framework and that
-it achieves competitive performance on CityScapes and the challenging CREMI 2016 segmentation benchmark.
+\section{Introduction}
+In computer vision, the partitioning of weighted graphs has been successfully applied to tasks as diverse as image segmentation, object tracking and pose estimation. 
+Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes.
+These methods require users to specify the desired numbers of clusters (as in spectral clustering) or a termination criterion (e.g.\ in iterated normalized cuts) or even to add a seed for each object  (e.g.\ seeded watershed or random walker).
 
-In Sec.~\ref{sec:spectral_clust}, we also show how \algname{} outperforms spectral clustering methods on the task of neuron segmentation and how on synthetic graphs it achieves similar scores to a recently proposed spectral method for signed graphs.
-\TODO{Define HC and AC abbrv}
+Other graph clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between nodes.
+The advantage of signed graphs over positive-weighted graphs is that balancing attraction and repulsion allows us to obtain a clustering without defining additional parameters.
+A canonical formulation of the signed graph partitioning problem is the \emph{multicut} or \emph{correlation clustering} problem \cite{kappes2011globally,chopra1991multiway}.
+This problem is NP-hard, though many approximate solvers have been proposed \cite{lange2018combinatorial,pape2017solving,beier2016efficient,yarkony2012fast}.
+The general problem of graph partitioning can also be solved approximately by greedy agglomerative clustering \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}.
+Agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter-free and efficient.
+Despite the fact that a variety of these algorithms exist, no overarching study has so far been conducted to compare their robustness and efficiency or to provide guidelines for matching an algorithm to the partitioning problem at hand.
+
+In this paper, we propose a simple theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical clustering (HC) on positive-weighted graphs \cite{lance1967general}.
+This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints} (see Table~\ref{tab:linkage-criteria}).
+We then formally prove that some of the combinations correspond to existing clustering algorithms, and introduce new algorithms for combinations which have not been explored before.
+By analyzing their theoretical properties, we also show which one of them define ultrametrics on the graph.
+
+We evaluate the algorithms on a large variety of existing and synthetic signed graph clustering problems. 
+Our experiments show that the choice of a linkage criteria strongly influence the way how clusters are grown by the agglomerative algorithms, making some linkage methods more suited for certain types of clustering problems.
+% We focus our comparison on three of the best-performing algorithms included in our framework, which are based on average, sum, and absolute maximum linkage criteria (see Table~\ref{tab:linkage-criteria}).
+We highlight their empirical properties by showing how clusters are grown differently depending on the algorithm.
+Moreover, we evaluate all algorithms on \emph{instance segmentation} -- a computer vision task consisting in assigning each pixel of an image to an object instance -- by predicting graph edge weights with a CNN (see Fig.~\ref{fig:intro_figure}).
+We benchmark the clustering algorithms by focusing on their efficiency, robustness and tendency to over- or under-cluster. 
+First, we observe that the tested agglomerative algorithms strongly outperform recently proposed spectral clustering methods.
+Then,  we also show that average-linkage based agglomerative algorithms achieve state of the art results on the competitive CREMI 2016 challenge for neuron segmentation of 3D electron microscopy image volumes of brain tissue.
+
+% In Sec.~\ref{sec:spectral_clust}, we also show how \algname{} outperforms spectral clustering methods on the task of neuron segmentation and how on synthetic graphs it achieves similar scores to a recently proposed spectral method for signed graphs.
+% \TODO{Define HC abbrv}
 

### 2021-03-02 chapters/2_rel_work.tex
Shuffle stuff around; update intro

@@
 \section{Related work} \label{sec:related_work}
-\textbf{Proposal-based methods} have been highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}.
+\textbf{Proposal-based methods} have been highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}and CityScapes \cite{cordts2016cityscapes}.
 They decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,porzi2019seamless,liu2018path,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}.
 % They commonly rely on {Faster-RCNN}~\cite{ren2015faster} and can be trained end-to-end using non-maximum suppression. 
-Other methods use instead recurrent models to sequentially generate instances one-by-one \cite{romera2016recurrent,ren2017end}.
+% Other methods use instead recurrent models to sequentially generate instances one-by-one \cite{romera2016recurrent,ren2017end}.
 
 \textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances.
-Recently, there has been a growing interest for such  methods that do not involve object detection, since, in certain types of data, object instances cannot be approximated by bounding boxes.
-For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation,
+Recently, there has been a growing interest for such  methods that do not involve object detection, since, in certain types of data, object instances cannot be approximated by bounding boxes \cite{kirillov2017instancecut,bai2017deep}.
+% For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation, 
 % SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
-whereas a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction. 
+% whereas a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction. 
 % whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
-Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{lee2019learning,fathi2017semantic,newell2017associative,de2017semantic}.
-% kulikov2018instance
-Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}. 
+Some use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other \cite{lee2019learning,fathi2017semantic,newell2017associative,de2017semantic}
+% , while mapping pixels belonging to different instances further apart \cite{lee2019learning,fathi2017semantic,newell2017associative,de2017semantic}. % kulikov2018instance
+and then retrieve final instances by applying a clustering algorithm \cite{kong2018recurrentPix}.
+% , like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}. 
 Other recent successful methods simply let the model predict the relative coordinates of the instance center \cite{neven2019instance,cheng2019panopticdeeplab} or, given a point $(x,y)$ in the image, they train a model to generate the mask of the instance located at $(x,y)$ \cite{sofiiuk2019adaptis}.
@@
 In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:
-some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, whereas
-flood-filling networks \cite{januszewski2018high} and MaskExtend \cite{meirovitch2016multi} use a CNN to iteratively grow one region/neuron at the time; recently, the work of \cite{meirovitch2019cross} made the process more efficient by employing a combinatorial encoding of the segmentation.
+some use a combinatorial framework \cite{beier2017multicut}, others use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy.
+Flood-filling networks \cite{januszewski2018high} and MaskExtend \cite{meirovitch2016multi} used a CNN to iteratively grow one region/neuron at the time.
+% recently, the work of \cite{meirovitch2019cross} made the process more efficient by employing a combinatorial encoding of the segmentation.
 A structured learning approach was also proposed in \cite{funke2018large,turaga2009maximin}.
@@
 
-This work reformulates the clustering algorithms of \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a generalized framework and adopt ideas from the proposal-free methods \cite{liu2018affinity,wolf2018mutex,lee2017superhuman} to predict long-range relationships between pixels.
+This work reformulates the clustering algorithms of \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a generalized framework and adopt ideas from the proposal-free instance segmentation methods \cite{liu2018affinity,wolf2018mutex,lee2017superhuman} to predict long-range affinities between pixels.

### 2021-03-02 chapters/3_algorithm.tex
Small changes
Shuffle stuff around; update intro

@@
 
-\subsection{New and existing algorithms included in \algname{}} \label{sec:alg_update_rules}
+\subsection{\algname{}: New and existing algorithms} \label{sec:alg_update_rules}
 
@@
 
-\paragraph{Average, Single, and Complete Linkage} -- These three linkage criteria have been throughly studied on positive-weighted graphs.
-In \cite{chehreghani2020hierarchical}, the authors proved that applying these three linkage methods to a signed graph is equivalent to applying them to the positive-weighted graph obtained by shifting all edge weights by a constant.
+\paragraph{Average, Single, and Complete Linkage} -- These three linkage criteria have been throughly studied on positive-weighted graphs, but never on signed graphs.
+In the recent related work \cite{chehreghani2020hierarchical}, the authors prove that applying these three linkage methods to a signed graph is equivalent to applying them to the positive-weighted graph obtained by shifting all edge weights by a constant.
 Here, we prove which of the algorithms included in our generalized framework have this invariance-property: (proof in Appendix)
@@
 \paragraph{Algorithms defining an ultrametric} -- The connection between agglomerative algorithms and ultrametrics\footnote{A metric space $(X,d)$ is an \emph{ultrametric} if for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.} is well known \cite{johnson1967hierarchical,milligan1979ultrametric}.
-Normally, ultrametrics are associated to strictly positive \emph{similarity} or \emph{dissimilarity} measures on a graph.
+Usually, ultrametrics are associated to strictly positive \emph{similarity} or \emph{dissimilarity} measures on a graph.
 Here, we generalize this concept to signed graphs.

### 2021-03-02 chapters/5_experiments_compare_rules.tex
Shuffle stuff around; update intro

@@
 \centering
-\includegraphics[width=0.47\textwidth,trim=0.25in 0.in 0.5in 0.in,clip]{./figs/SSBM_experiments.pdf}
-        \caption{Scores on SSBM graphs}
-\end{figure}
-\begin{figure}[t]
-\centering
 \includegraphics[width=0.47\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
-        \caption{Scores on \emph{CREMI-gridGraph} perturbed with noise}
+        \caption{
+ARAND errors (lower is better) on \emph{CREMI-gridGraph} clustering problems perturbed with structured noise. Average-linkage algorithms proved to be the most robust.
+We report median, 25th, and the 75th percentile values over \TODO{30} experiments.
+% \algname{} performances compared to spectral methods on synthetic graphs.
+The spectral methods were given the true number of clusters as input, in contrast to \algname{}.
+\TODO{Define paramters SSB; explain percentile stuff (for both noise experiments), user ARAND-error}
+}\label{fig:scores_structured_noise}
 \end{figure}

### 2021-03-02 chapters/5_experiments_intro.tex
Shuffle stuff around; update intro

@@
 % !TEX root = ../agglo_clust_review.tex
-
-\section{Experiments}\label{sec:neuro_segm_exp}
-\subsection{Signed graph clustering problems}
-We evaluate the agglomerative clustering algorithms included in our framework on a large collection of both synthetic and real-world graphs.
-The size of the graphs ranges from a few hundred to hundreds of millions of edges.
-
-\textbf{Synthetic SSBM graphs} -- We first consider synthetic graphs generated by a signed stochastic block model (SSBM), following the approach in \cite{Cucuringu2019SPONGEAG}.
-We use an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N$ vertices and edge probability $p$.
-The graph is partitioned into $k$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) have Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $\sigma$.
-To model noise, the sign of the edge weights is flipped independently with probability $\eta$.
-
-\textbf{Existing signed graphs}  -- We use clustering instances from the OpenGM benchmark \cite{kappes2013comparative} as well as biomedical segmentation instances \cite{pape2017solving}.
-The dataset \emph{Image Segmentation} contains planar region-adjacency-graphs (\emph{rag}) that are constructed from superpixel adjacencies of photographs.
-The \emph{Knott-3D} datasets contains \emph{3D-rags} arising from volume images acquired by electron microscopy (EM).
-The set \emph{Modularity Clustering} contains complete graphs constructed from clustering problems on small social networks.
-The \emph{Fruit-Fly} 3D-rag instances were generated from volume image scans of fruit fly brain matter.
-Instances \emph{Level 1-4} are progressively simplified versions of the global problem obtained via block-wise domain decomposition \cite{pape2017solving}.
-
-\textbf{Grid-graphs from CNN predictions} -- We also evaluate the clustering methods on the task of neuron segmentation in EM image volumes using training data from the CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge}.
-We train a 3D U-Net \cite{ronneberger2015u,cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
-as described in \cite{lee2017superhuman}\footnote{See Appendix \ref{sec:cremi_details} for all details about training and data augmentation.}.
-The predicted affinities $a_e\in[0,1]$, which represent how likely it is for a pair of pixels to belong to the same neuron segment, are then mapped to signed edge weights $w_e=a_e-0.5$, resulting in a 3D grid-graph having a node for each pixel/voxel of the  image\footnote{To map affinities to signed weights, we also tested the \emph{logarithmic mapping} proposed in \cite{finkel2008enforcing,andres2012globally}, but it performed worse in our experiments.}.
-\TODO{long-range 10\%} 
-% Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights. Long-range connections are more noisy. 10\% represents a good compromise.
-We divided the three training samples of the CREMI challenge, which consists of approximately 196 million voxels each, into five sub-blocks for a total of 15 graph clustering problems (named \emph{CREMI-gridGraph} in Table~\ref{tab:datasets_and_energies}).
-
-\textbf{3D-rag from CNN-predictions} -- Lastly, we use the predictions of our CNN model to generate three graph instances (one for each CREMI training sample, named \emph{CREMI-3D-rag} in Table~\ref{tab:datasets_and_energies}), which have very similar structure to the \emph{Knott-3D} and \emph{Fruit-Fly} instances.
-We obtain them by first computing 2D supervoxels from the CNN predictions (using a watershed algorithm seeded at the maxima of the smoothed boundary distance transform) and then building a 3D region-adjacency graph, whose edge weights are given by the CNN affinities averaged over the boundaries of adjacent supervoxels.
-
-% This is true for the neuron instances generated from the CREMI challenge, where training data is available, and for synthetic graphs generated with SSBM.
-
-% Fig.~\ref{fig:noise_plots} summarizes our 12000 noise experiments: we focus on the best performing linkage criteria, i.e.
-\emph{Average}, \emph{Sum} and \emph{Abs Max}, and test them with different amount of noise.
-% In these experiments, we also want to assess how beneficial it is to use long-range CNN predictions in the agglomeration.
-Thus, we perform a set of simulations without adding long-range connections to the grid-graph and another set where we introduce them with a 10\% probability\footnote{We also performed experiments adding all the long-range predictions given by the CNN model, but we did not note major differences when using only 10\% of them.
-Adding this fraction is usually sufficient to improve the scores.}.\\
-
-% , where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation and in our case was set to $\beta=0.5$.
-% Neuron segmentation is commonly performed by first predicting undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment.
-% Similarly to \cite{lee2017superhuman}, we train a UNet model CITE to predict both short- and long-range affinities that are not limited to adjacent pixels.
-These predictions are then used as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image.
-
-% ---
-% We first evaluate and compare the agglomerative clustering algorithms described in the generalized framework on the task of neuron segmentation in electron microscopy (EM) image volumes.
-This application is of key interest in connectomics, a field of neuro-science with the goal of reconstructing neural wiring diagrams spanning complete central nervous systems.
-Currently, only proof-reading or manual tracing yields sufficient accuracy for correct circuit reconstruction \cite{schlegel2017learning}, thus further progress is required in automated reconstruction methods.
-
-% ----
-% We evaluate all algorithms in the proposed framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available.
-The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which come with publicly available training ground truth.
-The results submitted to the leaderboard are evaluated using the CREMI score, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}.
-In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.
 
@@
     \caption{List of compared signed graph clustering problems: for each, we specify the number of instances $\# I$, number of nodes $|V|$, and number of edges $|E|$.
-We compare algorithms in the \algname{} framework by evaluating which of the obtained clusterings is associated to the lowest value of the multicut objective defined in Eq.~\ref{eq:MC_objective} (\textbf{lower is better}).}
+We compare algorithms in the \algname{} framework by evaluating which of the obtained clusterings is associated to the lowest value of the multicut objective defined in Eq.~\ref{eq:MC_objective} (lower is better).}
     \label{tab:datasets_and_energies}
 \end{table*}
+
+\section{Experiments}\label{sec:neuro_segm_exp}
+\subsection{Signed graph clustering problems}
+We evaluate the agglomerative clustering algorithms included in our framework on a large collection of both synthetic and real-world graphs.
+The size of the graphs ranges from a few hundred to hundreds of millions of edges.
+
+\textbf{Synthetic SSBM graphs} -- We first consider synthetic graphs generated by a signed stochastic block model (SSBM).
+We use an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N$ vertices and edge probability $p$.
+Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) have Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $\sigma$.
+To model noise, the sign of the edge weights is flipped independently with probability $\eta$.
+
+\textbf{Existing signed graphs}  -- We use clustering instances from the OpenGM benchmark \cite{kappes2013comparative} as well as biomedical segmentation instances \cite{pape2017solving}.
+The dataset \emph{Image Segmentation} contains planar region-adjacency-graphs (\emph{rag}) that are constructed from superpixel adjacencies of photographs.
+The \emph{Knott-3D} datasets contains \emph{3D-rags} arising from volume images acquired by electron microscopy (EM).
+The set \emph{Modularity Clustering} contains complete graphs constructed from clustering problems on small social networks.
+The \emph{Fruit-Fly} 3D-rag instances were generated from volume image scans of fruit fly brain matter.
+Instances \emph{Level 1-4} are progressively simplified versions of the global problem obtained via block-wise domain decomposition \cite{pape2017solving}.
+
+\textbf{Grid-graphs from CNN predictions} -- We also evaluate the clustering methods on the task of neuron segmentation in EM image volumes using training data from the CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge}.
+We train a 3D U-Net \cite{ronneberger2015u,cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
+as described in \cite{lee2017superhuman}\footnote{See Appendix \ref{sec:cremi_details} for all details about training and data augmentation.}.
+The predicted affinities $a_e\in[0,1]$, which represent how likely it is for a pair of pixels to belong to the same neuron segment, are then mapped to signed edge weights $w_e=a_e-0.5$, resulting in a 3D grid-graph having a node for each pixel/voxel of the  image\footnote{To map affinities to signed weights, we also tested the \emph{logarithmic mapping} proposed in \cite{finkel2008enforcing,andres2012globally}, but it performed worse in our experiments.}.
+Clustering algorithms largely benefits from long-range edge connections in the grid-graph, in addition to direct-neighbors ones.
+However, empirically, we found that long-range affinities predicted by the CNN are also more noisy, and adding only 10\% of them (by random sampling) gave the best results.
+% \TODO{long-range 10\%} 
+% Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights. Long-range connections are more noisy. 10\% represents a good compromise.
+We divided the three CREMI training samples, consisting of $\sim$196 million voxels each, into five sub-blocks for a total of 15 clustering problems (named \emph{CREMI-gridGraph} in Table~\ref{tab:datasets_and_energies}).
+
+\textbf{3D-rag from CNN-predictions} -- Lastly, we use the predictions of our CNN model to generate three graph instances (one for each CREMI training sample, named \emph{CREMI-3D-rag} in Table~\ref{tab:datasets_and_energies}), which have very similar structure to the \emph{Knott-3D} and \emph{Fruit-Fly} instances.
+We obtain them by first computing 2D supervoxels from the CNN predictions (using a watershed algorithm seeded at the maxima of the smoothed boundary distance transform) and then building a 3D region-adjacency graph, whose edge weights are given by the CNN affinities averaged over the boundaries of adjacent supervoxels.
+
+% This is true for the neuron instances generated from the CREMI challenge, where training data is available, and for synthetic graphs generated with SSBM.
+
+% Fig.~\ref{fig:noise_plots} summarizes our 12000 noise experiments: we focus on the best performing linkage criteria, i.e.
+\emph{Average}, \emph{Sum} and \emph{Abs Max}, and test them with different amount of noise.
+% In these experiments, we also want to assess how beneficial it is to use long-range CNN predictions in the agglomeration.
+Thus, we perform a set of simulations without adding long-range connections to the grid-graph and another set where we introduce them with a 10\% probability\footnote{We also performed experiments adding all the long-range predictions given by the CNN model, but we did not note major differences when using only 10\% of them.
+Adding this fraction is usually sufficient to improve the scores.}.\\
+
+% , where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation and in our case was set to $\beta=0.5$.
+% Neuron segmentation is commonly performed by first predicting undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment.
+% Similarly to \cite{lee2017superhuman}, we train a UNet model CITE to predict both short- and long-range affinities that are not limited to adjacent pixels.
+These predictions are then used as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image.
+
+% ---
+% We first evaluate and compare the agglomerative clustering algorithms described in the generalized framework on the task of neuron segmentation in electron microscopy (EM) image volumes.
+This application is of key interest in connectomics, a field of neuro-science with the goal of reconstructing neural wiring diagrams spanning complete central nervous systems.
+Currently, only proof-reading or manual tracing yields sufficient accuracy for correct circuit reconstruction \cite{schlegel2017learning}, thus further progress is required in automated reconstruction methods.
+
+% ----
+% We evaluate all algorithms in the proposed framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available.
+The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which come with publicly available training ground truth.
+The results submitted to the leaderboard are evaluated using the CREMI score, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}.
+In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.
+
+\subsection{Comparison results and discussion}
+% Before to evaluate the clustering algorithms on real-world graphs, we compare them on two types of synthetically generated graphs and highlight some of their fundamental properties.
+
+\textbf{Comparison to spectral clustering} -- 
+First, we compare \algname{} to spectral clustering methods for signed graphs. 
+In Fig.~\ref{fig:SSBM_scores}, we see that SPONGE$_{sym}$ and SPONGE proposed by \cite{Cucuringu2019SPONGEAG} perform particularly well on synthetic graphs generated with a SSB model.
+However, these methods do not scale up to the large graph instances considered here and they also require the user to specify the true number of clusters in advance, which is not known for most of other graph instances tested in this paper.
+In Appendix, Table \ref{tab:cremi_spectral_experiments}, we report the scores achieved by these methods on a much smaller sub-instance of the \emph{CREMI-gridGraph} problem: even when the true number of clusters is specified in advance for the spectral methods, they perform much worse than other \algname{} algorithms, with performance drop of almost 50\%.
+For these reasons, we exclude them from our other comparison experiments.
+
+\textbf{Complete and Single Linkage} -- In our experiments, we included these two linkage methods as baselines to highlight the difficulty of the considered graph clustering problems.
+Scores in Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show the poor performances of these two linkage methods: Single linkage hierarchical clustering (HC-Single), which here is equivalent to thresholding the edge weights at $w_e=0$ and computing graph connected components, often returned few big under-segmented clusters.
+HC-Complete and HCC-Complete returned instead a lot of over-segmented clusters.
+% These algorithms are excluded from our next comparison experiments.
+
 \begin{table*}[t]
@@
 GAEC \cite{keuper2015efficient} & 0.0905 & 0.606 & 0.323 & 89 \\
-HCC-Sum & 0.0910 & 0.608 & 0.323 & 85 \\
+HCC-Sum & 0.0910 & 0.608 & 0.323 & \textbf{85} \\
 MWS \cite{wolf2018mutex} & 0.1145 & 0.825 & 0.295 & 86 \\
 HCC-Single & 0.5282 & \textbf{0.437} & 1.367 & 88 \\
-HC-Single & 0.5282 & \textbf{0.437} & 1.367 & 85 \\
+HC-Single & 0.5282 & \textbf{0.437} & 1.367 & \textbf{85} \\
 HCC-Complete & 0.5564 & 2.220 & 0.254 & 89 \\
@@
           & \makecell{CREMI\\Score} & \makecell{ARAND\\error} & \makecell{VOI\\split} & \makecell{VOI\\merge}    \\ \midrule 
-\emph{OurCNN: 3D-rag + LMC} & \textbf{0.221} & \textbf{0.108} & \textbf{0.339} & 0.115 \\
-\textbf{\emph{OurCNN: gridGraph + HCC-Avg}} & 0.224 & 0.113 & 0.361 & 0.085  \\
+OurCNN: 3D-rag + LiftedMulticut & \textbf{0.221} & \textbf{0.108} & \textbf{0.339} & 0.115 \\
+\emph{OurCNN: gridGraph + HCC-Avg} & 0.224 & 0.113 & 0.361 & 0.085  \\
 \emph{OurCNN: gridGraph + HC-Avg}  & 0.224 & 0.114 &  0.364 & 0.083 \\
@@
 CRU-Net \cite{zeng2017deepem3d} & 0.566 & 0.229 & 1.081 &  0.389    \\
-LFC \cite{parag2017anisotropic} & 0.616 & 0.313 & 1.085 & 0.140     \\
+% LFC \cite{parag2017anisotropic} & 0.616 & 0.313 & 1.085 & 0.140     \\
         \end{tabular}
@@
     % \label{tab:results_cremi_test}
-    \caption{\textbf{(a-b)} Scores and run times of algorithms in the \algname{} framework on the \emph{CREMI-gridGraph} and \emph{CREMI-3D-rag} clustering problems: average linkage methods performed best.
+    \caption{\textbf{Tables a-b:} Scores and run times of algorithms in the \algname{} framework on the \emph{CREMI-gridGraph} and \emph{CREMI-3D-rag} clustering problems: average linkage methods performed best.
 Measures shown are Adapted-Rand error (ARAND, lower is better), Variation of Information \cite{arganda2015crowdsourcing} (VOI-merge for under-clustering error, VOI-split for over-clustering error, lower is better).
-\textbf{(c)} Current leading entries in the CREMI challenge leaderboard (March 2021).
+\textbf{Table c:} Current leading entries in the CREMI challenge leaderboard (March 2021).
 CREMI-score is given by geometric mean of (VOI-split + VOI-merge)  and adapted RAND error (lower is better).}
@@
 \end{table*}
-\begin{figure}
-\centering
-\includegraphics[width=0.48\textwidth,trim=12 76 150 13, clip]{./figs/comparison_new.pdf} % left bottom right top
-\caption{Failure cases of three algorithms included in \algname{} on challenging parts of the CREMI dataset.
-\emph{Wrongly} segmented regions are highlighted in different warm colors.
-Red arrows point to wrongly split regions; yellow ones to merge errors.
-HC-Avg returned the best segmentation.
-Data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.
-\label{fig:failure_cases}}
-\end{figure}
-\begin{figure}
-\centering
-\includegraphics[width=0.48\textwidth,trim=300 100 300 100, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
-\caption{Dendograms built by GAEC, MWS, and HC-Avg on a small SSBM (two ground truth communities represented by colors).
-The dendrograms are truncated at the level of the clustering $\Pi^*$ returned by the algorithms.
-\TODO{Update}  \label{fig:dendrograms}}
-\end{figure}
-
-\subsection{Comparison results and discussion}
-% Before to evaluate the clustering algorithms on real-world graphs, we compare them on two types of synthetically generated graphs and highlight some of their fundamental properties.
-
-\textbf{Comparison to spectral clustering} -- 
-First, we compare \algname{} to spectral clustering methods for signed graphs. 
-In Fig.~\ref{fig:SSBM_scores}, we see that SPONGE$_{sym}$ and SPONGE proposed by \cite{Cucuringu2019SPONGEAG} perform particularly well on synthetic graphs generated with a SSB model.
-However, these methods do not scale up to the large graph instances considered here and they also require the user to specify the true number of clusters in advance, which is not known for most of other graph instances tested in this paper.
-For these reasons, we exclude them from our other comparison experiments.
-Table \ref{tab:cremi_spectral_experiments} in Appendix lists the scores achieved by these methods on a much smaller sub-instance of the \emph{CREMI-gridGraph} problem: even when the true number of clusters is specified in advance for the spectral methods, they perform much worse than other \algname{} algorithms, with performance drop of almost 50\%.
-
-\textbf{Complete and Single Linkage} -- In our experiments, we included these two linkage methods as baselines to highlight the difficulty of the considered graph clustering problems.
-Scores in Tables~\ref{tab:scores_3drag}-\ref{tab:scores_gridGraph} show the poor performances of these two linkage methods: Single linkage hierarchical clustering (HC-Single), which here is equivalent to thresholding the edge weights at $w_e=0$ and computing graph connected components, often returned few big under-segmented clusters.
-HC-Complete and HCC-Complete returned instead a lot of over-segmented clusters.
-% These algorithms are excluded from our next comparison experiments.
 
@@
 In the following, we will show how this unique \emph{flooding strategy} of the sum-linkage methods can be both an advantage or a disadvantage, depending on the type of clustering problem.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.48\textwidth,trim=300 100 300 100, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
+\caption{Dendrograms built by three versions of \algname{} (GAEC, MWS, and HC-Avg) on a synthetic graph generated with SSBM (\TODO{parameters}).
+Red and blue colors represent the ground truth labels of each initial graph node.
+Dendrograms are truncated at the level of the final clustering $\Pi^*$ returned by \algname{}.
+\label{fig:dendrograms}}
+\end{figure}
+\begin{figure}
+\centering
+\includegraphics[width=0.48\textwidth,trim=12 76 150 13, clip]{./figs/comparison_new.pdf} % left bottom right top
+\caption{Failure cases of three algorithms included in \algname{} on challenging parts of the CREMI dataset.
+\emph{Wrongly} segmented regions are highlighted in different warm colors.
+Red arrows point to wrongly split regions; yellow ones to merge errors.
+HC-Avg returned the best segmentation.
+Data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.
+\label{fig:failure_cases}}
+\end{figure}
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.42\textwidth,trim=0.25in 0.in 0.5in 0.in,clip]{./figs/SSBM_experiments.pdf}
+        \caption{
+ARAND errors (lower is better) on synthetic graphs generated with SSBM (\TODO{parameters}). 
+% The spectral clustering methods, SPONGE and SPONGE$_sym$, were given the true number of clusters as input. 
+% Solid lines represent median values over \TODO{30} experiments. Values between the 25th and the 75th percentile are shown in shaded areas.
+We report median, 25th, and the 75th percentile values over \TODO{30} experiments.
+%         Scores on SSBM graphs
+% \algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust.
+Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions.
+The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details).
+For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph.
+Experiments are performed on a crop of CREMI training sample B.
+        } \label{fig:SSBM_scores}
+\end{figure}
 
@@
 To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}.
-The plot in Fig.~\ref{fig:noise_plots} confirms that \emph{HC-Avg} and \emph{HCC-Avg} perform well even in the presence of strong structured noise, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (\emph{MWS}).
+The plot in Fig.~\ref{fig:scores_structured_noise} confirms that \emph{HC-Avg} and \emph{HCC-Avg} perform well even in the presence of strong structured noise, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (\emph{MWS}).
 It is not a surprise that the AbsMax linkage used by \emph{MWS} is not robust to this type of structured noise.
@@
 \textbf{Results on CREMI challenge} -- 
-Table~\ref{tab:cremi_leaderboard} shows how the \emph{HCC-Avg} and \emph{HC-Avg} clustering algorithms included in the proposed \algname{} framework achieve state-of-the-art performances on the CREMI challenge, when combined to the predictions of our CNN.
+Table~\ref{tab:cremi_leaderboard} shows that the \emph{HCC-Avg} and \emph{HC-Avg} clustering algorithms included in the proposed \algname{} framework achieve state-of-the-art performances on the CREMI challenge, when combined to the predictions of our CNN.
 Most of other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs.
-As we also showed in Table ~\ref{tab:scores_3drag}, this approach considerably reduces the size of the clustering problem and, consequently, the post-processing time.
-On the other hand, our method achieves better performances by operating directly on pixels (\emph{gridGraph+HCC-Avg}) and removes in this way the parameter tuning necessary to obtain good super-pixels, which are usually highly dataset dependent.
-To scale up the clustering algorithms to the pixel-based problem given by the full test-volumes, we divided each volume into four sub-blocks, and then combined the resulting clusterings by running the clustering algorithms again on the combined graph.
+As we show in Table ~\ref{tab:scores_3drag}, using super-pixels considerably reduces the size of the clustering problem and, consequently, the post-processing time.
+However, our method operating directly on pixels (\emph{gridGraph+HCC-Avg}) achieves better performances than superpixel-based methods (\emph{3D-rag+HCC-Avg}) and does not require the parameter tuning necessary to obtain good super-pixels, which is usually highly dataset dependent.
+The method \emph{3D-rag+LiftedMulticut} based on the lifted multicut formulation of \cite{beier2017multicut} (see details in Appendix) achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and super-pixel shape information.
+To scale up our method operating on pixels, we divided each test-volume into four sub-blocks, and then combined the resulting clusterings by running the algorithms again on the combined graph.
 % Note that the test volumes of the challenge contain several imaging artifacts that make segmentation particularly challenging.

### 2021-03-02 chapters/supplementary.tex
Shuffle stuff around; update intro

@@
 \subsection{\algname{} sensitivity to noise: adding artifacts to CNN predictions} \label{sec:appendix_noise_gen}
+\TODO{ Experiments are performed on a crop of CREMI training sample B.}
 Additionally to the comparison on the full training dataset, we performed more experiments on a crop of the more challenging CREMI training sample B, where we perturbed the predictions of the CNN with noise and we introduced additional artifacts like missing or fictitious boundary evidences.

### 2021-03-04 chapters/1_intro.tex
Integrate Nathan comments

@@
 We evaluate the algorithms on a large variety of existing and synthetic signed graph clustering problems. 
-Our experiments show that the choice of a linkage criteria strongly influence the way how clusters are grown by the agglomerative algorithms, making some linkage methods more suited for certain types of clustering problems.
+Moreover, we evaluate all algorithms on \emph{instance segmentation} -- a computer vision task consisting in assigning each pixel of an image to an object instance -- by predicting graph edge weights with a CNN (see Fig.~\ref{fig:intro_figure}).
+Our experiments show that the choice of a linkage criterion strongly influences the way how clusters are grown by the agglomerative algorithms, making some linkage methods more suited for certain types of clustering problems.
 % We focus our comparison on three of the best-performing algorithms included in our framework, which are based on average, sum, and absolute maximum linkage criteria (see Table~\ref{tab:linkage-criteria}).
 We highlight their empirical properties by showing how clusters are grown differently depending on the algorithm.
-Moreover, we evaluate all algorithms on \emph{instance segmentation} -- a computer vision task consisting in assigning each pixel of an image to an object instance -- by predicting graph edge weights with a CNN (see Fig.~\ref{fig:intro_figure}).
 We benchmark the clustering algorithms by focusing on their efficiency, robustness and tendency to over- or under-cluster. 

### 2021-03-04 chapters/3_algorithm.tex
Integrate Nathan comments

@@
 
-\textbf{Multicut objective} -- We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{S\in\Pi} S $, $\,S \cap S' = \emptyset$ for different clusters $S, S'\in \Pi$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
-For any clustering $\Pi$ of $\mathcal{G}$, we denote as $E^0_\Pi= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u,v \in S \}$ the set of edges linking nodes in the same cluster, and as $E_\Pi^1= E \setminus E^0_\Pi$ the set of edges whose linked nodes belong to distinct clusters, which is known as the \emph{multicut} of $\mathcal{G}$ associated to clustering $\Pi$.
+\textbf{Multicut objective} -- We call the set $\Pi=\{S_1,\ldots,S_K\}$ a \emph{clustering} or \emph{partitioning} if $V = \cup_{S\in\Pi} S $, $\,S \cap S' = \emptyset$ for different clusters $S, S'\in \Pi$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
+For any clustering $\Pi$ of $\mathcal{G}$, we denote as $E^0_\Pi= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u,v \in S \}$ the set of edges linking nodes in the same cluster.
+The set of edges whose linked nodes belong to distinct clusters, denoted as $E_\Pi^1= E \setminus E^0_\Pi$, is known as the \emph{multicut} of $\mathcal{G}$ associated to clustering $\Pi$.
 The instance of the NP-hard \emph{minimum cost multicut problem} w.r.t.
@@
 Here, we generalize this concept to signed graphs.
-To do so, we first map the signed interaction $\treeHeight{}$ defined in Eq.~\ref{eq:def_dendr_interact} to positive ``distances'' $d_{T}:V \times V \rightarrow \mathbb{R}^{+}$:
+To do so, we first map the signed interaction $\treeHeight{}$ defined in Eq.~\ref{eq:def_dendr_interact} to positive ``pseudo-distances'' $d_{T}:V \times V \rightarrow \mathbb{R}^{+}$:
 \begin{align}\label{eq:UM_def}
@@
 \begin{prop}
-Consider a graph $\mathcal{G}(V,E,w_e)$, a linkage criteria $\interact{}$, and an AC algorithm returning a binary rooted tree $T$ with height $h_T$.
+Consider a graph $\mathcal{G}(V,E,w_e)$, a linkage criterion $\interact{}$, and an AC algorithm returning a binary rooted tree $T$ with height $h_T$.
 The quantity $(V, d_{T})$ defined in Eq.~\ref{eq:UM_def} is an ultrametric iff, $\forall u,v,t \in V$:

### 2021-03-04 chapters/5_experiments_intro.tex
Integrate Nathan comments

@@
 We evaluate the agglomerative clustering algorithms included in our framework on a large collection of both synthetic and real-world graphs.
-The size of the graphs ranges from a few hundred to hundreds of millions of edges.
+The size of the graphs ranges from a few hundred to hundreds of millions of edges and the graphs have very different structures, so that the algorithms are tested in different scenarios.
 
@@
 We use an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N$ vertices and edge probability $p$.
-Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) have Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $\sigma$.
+Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) have Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) with standard deviation $\sigma$.
 To model noise, the sign of the edge weights is flipped independently with probability $\eta$.
@@
 The predicted affinities $a_e\in[0,1]$, which represent how likely it is for a pair of pixels to belong to the same neuron segment, are then mapped to signed edge weights $w_e=a_e-0.5$, resulting in a 3D grid-graph having a node for each pixel/voxel of the  image\footnote{To map affinities to signed weights, we also tested the \emph{logarithmic mapping} proposed in \cite{finkel2008enforcing,andres2012globally}, but it performed worse in our experiments.}.
-Clustering algorithms largely benefits from long-range edge connections in the grid-graph, in addition to direct-neighbors ones.
+Clustering algorithms largely benefit from long-range edge connections in the grid-graph, in addition to direct-neighbors ones.
 However, empirically, we found that long-range affinities predicted by the CNN are also more noisy, and adding only 10\% of them (by random sampling) gave the best results.
@@
 First, we compare \algname{} to spectral clustering methods for signed graphs. 
-In Fig.~\ref{fig:SSBM_scores}, we see that SPONGE$_{sym}$ and SPONGE proposed by \cite{Cucuringu2019SPONGEAG} perform particularly well on synthetic graphs generated with a SSB model.
+In Fig.~\ref{fig:SSBM_scores}, we see that SPONGE$_{sym}$ and SPONGE proposed by \cite{Cucuringu2019SPONGEAG} perform particularly well on synthetic graphs generated with a SSBM.
 However, these methods do not scale up to the large graph instances considered here and they also require the user to specify the true number of clusters in advance, which is not known for most of other graph instances tested in this paper.
@@
 Despite this, on graphs where a GT clustering is known, GAEC does not achieve the best ARAND scores (see Tables~\ref{tab:scores_gridGraph} and \ref{tab:scores_3drag}).
-To better understand these empirical results, we now make the following important observation.
+% To better understand these empirical results, we now make the following important observation.
 % This can also be observed in our experiments on synthetic graphs (Fig.
@@
 In all the studied clustering problems, we empirically observe that sum-linkage algorithms like GAEC tend to grow clusters one after the other, as shown in Fig.\ \ref{fig:intro_figure} by the unique agglomeration order of GAEC\footnote{This \emph{flooding agglomeration-strategy} of GAEC was also observed in \cite{kardoostsolving}.}.
-This is intuitively explained by the  following: initially, many of the most attractive edge weights have very similar values; when the two nodes $u,v$ with the highest attraction are merged, there is a high chance that they will have a common neighboring node $t$ belonging to the same cluster; thus, the interaction between the merged nodes $uv$ and $t$ is likely assigned to the highest priority, because it is given by the sum of two highly attractive edge weights.
+This is intuitively explained by the  following: initially, many of the most attractive edge weights have very similar values; when the two nodes $u,v$ with the highest attraction are merged, there is a high chance that they will have a common neighboring node $t$ belonging to the same cluster; thus, the interaction between the merged nodes $uv$ and $t$ is likely assigned the highest priority, because it is given by the sum of two highly attractive edge weights.
 And this will start a ``chain reaction'' where only a single cluster is agglomerated at the time.
@@
 In SSBM graphs, the number of edges $E_{ij}\equiv(S_i\times S_j)\cap E$ connecting two clusters $S_i,S_j$ is  proportional to the product $|S_i|\cdot|S_j|$ of cluster sizes.
-With Sum or Avg linkage methods, we expect the flipping noise to be ``averaged out'' as soon as the set $E_{ij}$ becomes larger and clusters grow in size.
+With Sum or Avg linkage methods, due to the law of large numbers, the flipping noise is ``averaged out'' as soon as the set $E_{ij}$ becomes larger and clusters grow in size.
 On the other hand, when clusters are small, it is more likely that several of the edges in $E_{ij}$ are flipped and the algorithm makes a mistake by merging two clusters belonging to different ground truth communities.
@@
 This observation also explains the empirical results of \cite{chehreghani2020hierarchical}, which involved graph instances with very similar structure to the ones considered here.
-On the other hand, the MWS algorithm is not expected to perform well on these graphs because of the high sensitivity of the AbsMax linkage to flipping noise.
-In Propositions \ref{prop:MWS_SSBM_1} and \ref{prop:MWS_SSBM_2} (see Appendix), we prove that on SSBM graphs the merging steps of the MWS algorithm are given by a sequence of ``coin flip'' decisions with a probability proportional to the noise parameter $\eta$, independently on the cluster sizes.
+Lastly, the MWS algorithm is not expected to perform well on these graphs because of the high sensitivity of the AbsMax linkage to flipping noise.
+In Propositions \ref{prop:MWS_SSBM_1} and \ref{prop:MWS_SSBM_2} (see Appendix), we prove that on SSBM graphs the merging steps of the MWS algorithm are given by a sequence of ``coin flip'' decisions with a probability proportional to the noise parameter $\eta$, independently of the cluster sizes.
 
 \textbf{Scores on CREMI instance-segmentation} -- 
-SSBM graphs are \emph{non-planar} graphs, where every edge has the same probability to be present in the graph.
+SSBM graphs are \emph{non-planar} graphs, where every edge has the same probability to be present.
 On the other hand, the \emph{gridGraph} and \emph{3D-rag} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: weather a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance).
@@
 It is not a surprise that the AbsMax linkage used by \emph{MWS} is not robust to this type of structured noise.
-However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} proves how \emph{MWS} can achieve competitive performances with considerably lower runtimes.
+However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} prove how \emph{MWS} can achieve competitive performances with considerably lower runtimes.
 
@@
 Table~\ref{tab:cremi_leaderboard} shows that the \emph{HCC-Avg} and \emph{HC-Avg} clustering algorithms included in the proposed \algname{} framework achieve state-of-the-art performances on the CREMI challenge, when combined to the predictions of our CNN.
-Most of other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs.
+Most of the other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs.
 As we show in Table ~\ref{tab:scores_3drag}, using super-pixels considerably reduces the size of the clustering problem and, consequently, the post-processing time.

### 2021-03-04 chapters/1_intro.tex
Update figures, conclusions, and plots

@@
 \centering
-\includegraphics[width=0.5\textwidth]{figs/intro_image_v4.pdf} % left bottom right top
-\caption{\TODO{Redo figure}\algname{} example.
-\textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge.
-\textbf{(2)} Some short- and long-range predictions of our CNN model, where white pixels represent boundary evidence.
-\textbf{(3)} Outputs of two agglomerative algorithms included in our proposed generalized clustering framework, with \emph{Sum} and \emph{Average} linkage criteria.
-The final clustering / instance segmentation is shown in 3a, overlaid with the raw image.
-The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown/red), or never (black).
-(\textbf{4}) Some iterations of \algname{} on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions.
-At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left in the graph.
-\TODO{Check if avg is correct}
+\includegraphics[width=0.98\textwidth]{figs/intro_image_v5.pdf} % left bottom right top
+\caption{\textbf{(a)} Some iterations of \algname{}, the proposed Generalized Agglomerative Algorithm for Signed Graph Partitioning, on a toy graph with attractive/positive (green) and repulsive/negative (red) interactions.
+At each iteration, the yellow edge with highest interaction is contracted (average and sum linkage methods are shown).
+\textbf{(b)} List of linkage criteria used in this paper (see definitions in Table~\ref{tab:linkage-criteria} below), demonstrated on two small clusters.
+\textbf{(c)} Application of \algname{} to instance segmentation: we show raw data from the CREMI 2016 neuron-segmentation challenge and some predictions of our CNN model, where white pixels represent boundary evidence.
+\textbf{(d)} \algname{} agglomeration order for sum and average linkage: we show which pairs of neighboring pixels were merged first (white), later on (brown/red), or never (black).
 \label{fig:intro_figure}}
@@
 Algorithms typeset in bold font define an ultrametric on the graph (see Eq.~\ref{eq:UM_def}).
-Algorithms included in the green box, are weight-shift invariant (see Prop.~\ref{prop:weight_shift_invariant}).
+Algorithms included in the \TODO{green box}, are weight-shift invariant (see Prop.~\ref{prop:weight_shift_invariant}).
     We denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two clusters $S_i, S_j$. } 
@@
 In this paper, we propose a simple theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical clustering (HC) on positive-weighted graphs \cite{lance1967general}.
-This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints} (see Table~\ref{tab:linkage-criteria}).
+This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints} (see Fig.~\ref{fig:intro_figure}a-b and Table~\ref{tab:linkage-criteria}).
 We then formally prove that some of the combinations correspond to existing clustering algorithms, and introduce new algorithms for combinations which have not been explored before.

### 2021-03-04 chapters/3_algorithm.tex
Update figures, conclusions, and plots

@@
 % Algorithm \ref{main_alg} returns a binary tree denoted by $T^*$.
-Given an agglomerative algorithm with merging tree $T$, let $h_T:T \rightarrow \mathbb{N}$ denote the \emph{dendrogram-height} of each $(u\vee v)\in T$, which is defined as the iteration number at which nodes $u,v\in V$ were merged by the algorithm (\TODO{Fig.~1}).
+Given an agglomerative algorithm with merging tree $T$, let $h_T:T \rightarrow \mathbb{N}$ denote the \emph{dendrogram-height} of each $(u\vee v)\in T$, which is defined as the iteration number at which nodes $u,v\in V$ were merged by the algorithm (see example in Fig.~\ref{fig:intro_figure}b).
 We also define $\treeHeight(u,v)$ as the signed interaction $\interact{}(S,S')$ between the two clusters $S,S'$ that were merged at iteration $h_T(u\vee v)$:

### 2021-03-04 chapters/5_experiments_compare_rules.tex
Update figures, conclusions, and plots

@@
 \centering
-\includegraphics[width=0.47\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
+\includegraphics[width=0.47\textwidth,trim=0.2in 0.17in 0.2in 0.2in,clip]{./figs/noise_plots/noise_plots_adapted-rand_1.pdf}
         \caption{
-ARAND errors (lower is better) on \emph{CREMI-gridGraph} clustering problems perturbed with structured noise. Average-linkage algorithms proved to be the most robust.
-We report median, 25th, and the 75th percentile values over \TODO{30} experiments.
+ARAND errors (median values over 20 experiments, lower is better) on \emph{CREMI-gridGraph} clustering problems perturbed with structured noise.
+Average-linkage algorithms proved to be the most robust.
+% We report median, 25th, and the 75th percentile values over \TODO{30} experiments.
 % \algname{} performances compared to spectral methods on synthetic graphs.

### 2021-03-04 chapters/5_experiments_intro.tex
Update figures, conclusions, and plots

@@
         % \toprule
-        &&&&\multicolumn{1}{c}{}&\multicolumn{5}{c}{Multicut objective values associated to final clusterings:} \\
+        &&&& %\multicolumn{1}{c}{}
+        &\multicolumn{5}{c}{Multicut objective values associated to final clusterings (lower is better)} \\
         Clustering problem & \makecell{Graph Type} & $\#I$ & $|V|$ & $|E|$  & \multicolumn{1}{r}{GAEC \cite{keuper2015efficient}} & HCC-Sum & MWS \cite{wolf2018mutex} & HC-Avg & HCC-Avg \\ \midrule
@@
 We use an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N$ vertices and edge probability $p$.
-Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) have Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) with standard deviation $\sigma$.
+Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) have Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $\sigma=0.1$.
 To model noise, the sign of the edge weights is flipped independently with probability $\eta$.
@@
 \textbf{Complete and Single Linkage} -- In our experiments, we included these two linkage methods as baselines to highlight the difficulty of the considered graph clustering problems.
-Scores in Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show the poor performances of these two linkage methods: Single linkage hierarchical clustering (HC-Single), which here is equivalent to thresholding the edge weights at $w_e=0$ and computing graph connected components, often returned few big under-segmented clusters.
+Scores in Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show the poor performances of these two linkage methods: Single linkage hierarchical clustering (HC-Single), which here is equivalent to thresholding the edge weights at $w_e=0$ and computing connected components in the graph, often returned few big under-segmented clusters.
 HC-Complete and HCC-Complete returned instead a lot of over-segmented clusters.
@@
     % \label{tab:results_cremi_test}
-    \caption{\textbf{Tables a-b:} Scores and run times of algorithms in the \algname{} framework on the \emph{CREMI-gridGraph} and \emph{CREMI-3D-rag} clustering problems: average linkage methods performed best.
-Measures shown are Adapted-Rand error (ARAND, lower is better), Variation of Information \cite{arganda2015crowdsourcing} (VOI-merge for under-clustering error, VOI-split for over-clustering error, lower is better).
-\textbf{Table c:} Current leading entries in the CREMI challenge leaderboard (March 2021).
+    \caption{\textbf{Tables (a-b)}: Scores and run times of algorithms in the \algname{} framework on the \emph{CREMI-gridGraph} and \emph{CREMI-3D-rag} clustering problems: average linkage methods performed best.
+Measures shown are: Adapted-Rand error (ARAND, lower is better); Variation of Information (VOI) \cite{arganda2015crowdsourcing} (VOI-merge for under-clustering error and VOI-split for over-clustering error, lower values are better).
+\textbf{Table (c)}: Current leading entries in the CREMI challenge leaderboard (March 2021).
 CREMI-score is given by geometric mean of (VOI-split + VOI-merge)  and adapted RAND error (lower is better).}
@@
 \end{table*}
+\begin{figure}[t]
+\begin{subfigure}[t]{0.23\textwidth}
+\centering
+\includegraphics[width=\textwidth,trim=0.34in 0.34in 0.34in 0.34in,clip]{./figs/SSBM_scores/summary_SSBM_experiments_k20.pdf}
+\caption{$k=20$, $p=0.1$}
+\end{subfigure}\hfill
+\begin{subfigure}[t]{0.23\textwidth}
+\centering
+\includegraphics[width=\textwidth,trim=0.34in 0.34in 0.34in 0.34in,clip]{./figs/SSBM_scores/summary_SSBM_experiments_k50.pdf}
+\caption{$k=50$, $p=0.2$}
+\end{subfigure}
+        \caption{
+ARAND errors (median values over 20 experiments, lower is better) on synthetic graphs generated with SSBM, with $N=10000$ nodes, edges added with probability $p$, and $k$ ground truth communities of random size.
+% The spectral clustering methods, SPONGE and SPONGE$_sym$, were given the true number of clusters as input. 
+% Solid lines represent median values over \TODO{30} experiments. Values between the 25th and the 75th percentile are shown in shaded areas.
+% We report median, 25th, and the 75th percentile values over \TODO{30} experiments.
+%         Scores on SSBM graphs
+% \algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust.
+Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions.
+The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details).
+For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph.
+Experiments are performed on a crop of CREMI training sample B.
+        } \label{fig:SSBM_scores}
+\end{figure}
+
+\begin{figure}
+\centering
+% \includegraphics[width=0.48\textwidth,trim=300 100 300 100, clip]{./figs/dendrograms/new_agglo_order_OLD.png} % left bottom right top
+\includegraphics[width=0.48\textwidth,trim=80 10 60 0, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
+\caption{Dendrograms built by three versions of \algname{} (GAEC, MWS, and HC-Avg) on a synthetic graph generated with SSBM ($N=250$, $p=0.05$, $\eta=0.1$, and $k=2$ communities of equal size).
+Red and blue colors represent the true community of each initial node.
+At the top, dendrograms are truncated at the level of the final clustering $\Pi^*$ returned by \algname{} (y-axis shows the iteration number).
+\label{fig:dendrograms}}
+\end{figure}
 
@@
 
-\textbf{Size of growing clusters: Sum vs Avg linkage} -- 
+\textbf{Size of growing clusters: Sum vs Avg linkage} -- \TODO{Dendrogram}
 In all the studied clustering problems, we empirically observe that sum-linkage algorithms like GAEC tend to grow clusters one after the other, as shown in Fig.\ \ref{fig:intro_figure} by the unique agglomeration order of GAEC\footnote{This \emph{flooding agglomeration-strategy} of GAEC was also observed in \cite{kardoostsolving}.}.
-This is intuitively explained by the  following: initially, many of the most attractive edge weights have very similar values; when the two nodes $u,v$ with the highest attraction are merged, there is a high chance that they will have a common neighboring node $t$ belonging to the same cluster; thus, the interaction between the merged nodes $uv$ and $t$ is likely assigned the highest priority, because it is given by the sum of two highly attractive edge weights.
-And this will start a ``chain reaction'' where only a single cluster is agglomerated at the time.
+This is intuitively explained by the  following: initially, many of the most attractive edge weights have very similar values; when the two nodes $u,v$ with the highest attraction are merged, there is a high chance that they will have a common neighboring node $t$ belonging to the same cluster; thus, the interaction between the merged nodes $uv$ and $t$ is likely assigned to the highest priority, because it is given by the sum of two highly attractive edge weights.
+This will then start a ``chain reaction'' where only a single cluster is agglomerated at the time.
 % This \emph{flooding strategy} in the agglomeration is not observed with other linkage methods, e.g. Average, which grow clusters of similar sizes in parallel.
@@
 \centering
-\includegraphics[width=0.48\textwidth,trim=300 100 300 100, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
-\caption{Dendrograms built by three versions of \algname{} (GAEC, MWS, and HC-Avg) on a synthetic graph generated with SSBM (\TODO{parameters}).
-Red and blue colors represent the ground truth labels of each initial graph node.
-Dendrograms are truncated at the level of the final clustering $\Pi^*$ returned by \algname{}.
-\label{fig:dendrograms}}
-\end{figure}
-\begin{figure}
-\centering
-\includegraphics[width=0.48\textwidth,trim=12 76 150 13, clip]{./figs/comparison_new.pdf} % left bottom right top
-\caption{Failure cases of three algorithms included in \algname{} on challenging parts of the CREMI dataset.
+\includegraphics[width=0.48\textwidth,trim=90 10 60 0, clip]{./figs/comparison_GAEC_MWS_Avg.png} % left bottom right top
+\caption{Failure cases of three versions of \algname{} on challenging parts of the CREMI dataset.
 \emph{Wrongly} segmented regions are highlighted in different warm colors.
@@
 \end{figure}
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.42\textwidth,trim=0.25in 0.in 0.5in 0.in,clip]{./figs/SSBM_experiments.pdf}
-        \caption{
-ARAND errors (lower is better) on synthetic graphs generated with SSBM (\TODO{parameters}). 
-% The spectral clustering methods, SPONGE and SPONGE$_sym$, were given the true number of clusters as input. 
-% Solid lines represent median values over \TODO{30} experiments. Values between the 25th and the 75th percentile are shown in shaded areas.
-We report median, 25th, and the 75th percentile values over \TODO{30} experiments.
-%         Scores on SSBM graphs
-% \algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust.
-Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions.
-The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details).
-For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph.
-Experiments are performed on a crop of CREMI training sample B.
-        } \label{fig:SSBM_scores}
-\end{figure}
 
-\textbf{Scores on SSBM graphs}  -- 
+\textbf{Scores on synthetic SSBM graphs}  -- 
 % can be connected to any  that, depending on the edge-probability parameter $p$, are also \emph{dense}. 
 \algname{} algorithms using cannotLinkConstraints are not expected to perform well on these graphs, because of the type of employed flip noise, so we focus our comparison only on the GAEC, HC-Avg and MWS algorithms (using Sum, Average, and AbsMax linkage methods, respectively).
-Empirically, we observe that GAEC is the agglomerative algorithm performing best on SSBM graphs, almost as good as the spectral method SPONGE$_{sym}$, followed then by HC-Avg and then MWS (see Fig.~\ref{fig:SSBM_scores}).
+Empirically, we observe that GAEC is the agglomerative algorithm performing best on SSBM graphs, almost as good as the spectral method SPONGE$_{sym}$ (see Fig.~\ref{fig:SSBM_scores}).
 Given the simple properties of SSBM graphs, we will now give a specific explanation of these empirical results.
@@
 This observation also explains the empirical results of \cite{chehreghani2020hierarchical}, which involved graph instances with very similar structure to the ones considered here.
-Lastly, the MWS algorithm is not expected to perform well on these graphs because of the high sensitivity of the AbsMax linkage to flipping noise.
-In Propositions \ref{prop:MWS_SSBM_1} and \ref{prop:MWS_SSBM_2} (see Appendix), we prove that on SSBM graphs the merging steps of the MWS algorithm are given by a sequence of ``coin flip'' decisions with a probability proportional to the noise parameter $\eta$, independently of the cluster sizes.
+On the other hand, the MWS algorithm is not expected to perform well on these graphs because of the high sensitivity of the AbsMax linkage to flipping noise.
+In Propositions \ref{prop:MWS_SSBM_1} and \ref{prop:MWS_SSBM_2} (see Appendix), we prove that on SSBM graphs the merging steps of the MWS algorithm are given by a sequence of ``coin flip'' decisions with a probability proportional to the noise parameter $\eta$, independently on the cluster sizes.
 

### 2021-03-04 chapters/6_conclusions.tex
Update figures, conclusions, and plots

@@
 \section{Conclusion}
-
-We have presented a novel unifying framework for agglomerative clustering of graphs with both positive and negative edge weights; and we have shown that several existing clustering algorithms, e.g.
-the Mutex Watershed, can be reformulated as special cases of one underlying agglomerative algorithm.
-This framework also allowed us to introduce new algorithms, one of which, based on an \emph{Average} linkage criterion, outperformed all the others: it proved to be a simple and remarkably robust approach to process short- and long-range predictions of a CNN applied to an instance segmentation task.
-On biological images, this simple average agglomeration algorithm can represent a valuable choice for a user who is not willing to spend much time tuning complex task-dependent pipelines based on superpixels.
+We have presented an unifying framework for agglomerative clustering of graphs with both positive and negative edge weights; and we have shown that some existing clustering algorithms, e.g.
+the Mutex Watershed, can be reformulated as special cases of this framework.
+We have analyzed several theoretical and empirical properties of the algorithms included in this framework.
+On instance segmentation, algorithms based on an average linkage criterion outperformed all the others: they proved to be simple and remarkably robust approaches to process short- and long-range predictions of a CNN.
+ % applied to an instance segmentation task.
+On biological images, these simple average agglomeration algorithms achieve state-of-the-art results without requiring the user to spend much time tuning complex task-dependent pipelines based on super-pixels.
+% can represent a valuable choice for a user who is not willing to spend much time tuning complex task-dependent pipelines based on super-pixels.  
 % In future work, we plan to explore common theoretical properties of the algorithms included in the framework.
+% On biological images, this simple average agglomeration algorithm superpixels

### 2021-03-04 chapters/5_experiments_intro.tex
Shuffle paragraphs around

@@
 
-\subsection{Comparison results and discussion}
-% Before to evaluate the clustering algorithms on real-world graphs, we compare them on two types of synthetically generated graphs and highlight some of their fundamental properties.
-
-\textbf{Comparison to spectral clustering} -- 
-First, we compare \algname{} to spectral clustering methods for signed graphs. 
-In Fig.~\ref{fig:SSBM_scores}, we see that SPONGE$_{sym}$ and SPONGE proposed by \cite{Cucuringu2019SPONGEAG} perform particularly well on synthetic graphs generated with a SSBM.
-However, these methods do not scale up to the large graph instances considered here and they also require the user to specify the true number of clusters in advance, which is not known for most of other graph instances tested in this paper.
-In Appendix, Table \ref{tab:cremi_spectral_experiments}, we report the scores achieved by these methods on a much smaller sub-instance of the \emph{CREMI-gridGraph} problem: even when the true number of clusters is specified in advance for the spectral methods, they perform much worse than other \algname{} algorithms, with performance drop of almost 50\%.
-For these reasons, we exclude them from our other comparison experiments.
-
-\textbf{Complete and Single Linkage} -- In our experiments, we included these two linkage methods as baselines to highlight the difficulty of the considered graph clustering problems.
-Scores in Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show the poor performances of these two linkage methods: Single linkage hierarchical clustering (HC-Single), which here is equivalent to thresholding the edge weights at $w_e=0$ and computing connected components in the graph, often returned few big under-segmented clusters.
-HC-Complete and HCC-Complete returned instead a lot of over-segmented clusters.
-% These algorithms are excluded from our next comparison experiments.
-
 \begin{table*}[t]
@@
 \end{table*}
+
+\subsection{Comparison results and discussion}
+% Before to evaluate the clustering algorithms on real-world graphs, we compare them on two types of synthetically generated graphs and highlight some of their fundamental properties.
+
+\textbf{Multicut objective values} -- In Table~\ref{tab:datasets_and_energies}, we report the values of the multicut objective associated to the clusterings obtained with different \algname{} algorithms\footnote{Objective values achieved by Single and Complete linkage methods are much worse compared to other algorithms and are reported in Table \ref{tab:extended_results_cremi}, in Appendix.}.
+Although a lot of heuristics were proposed to better optimize this objective \cite{beier2016efficient,beier2014cut,kernighan1970efficient}, these methods are out of the scope of this paper, since they do not scale up to the largest graph instances considered here.
+By looking at results in Table~\ref{tab:datasets_and_energies}, we observe that GAEC almost always achieves the lowest objective values, apart from the \emph{CREMI-gridGraph} instances.
+Despite this, on graphs where a GT clustering is known, GAEC does not achieve the best ARAND scores (see Tables~\ref{tab:scores_gridGraph} and \ref{tab:scores_3drag}).
+% To better understand these empirical results, we now make the following important observation.
+% This can also be observed in our experiments on synthetic graphs (Fig.
+?
+and ?), where the clustering with minimum multicut energy become very different from the ground truth clustering when the flip noise parameter $\eta$ is increased.
+
+\textbf{Size of growing clusters: Sum vs Avg linkage} --
+In all the studied clustering problems, we empirically observe that sum-linkage algorithms like GAEC tend to grow clusters one after the other, as shown in Fig.\ \ref{fig:intro_figure} and \ref{fig:dendrograms} by the unique agglomeration order of GAEC\footnote{This \emph{flooding agglomeration-strategy} of GAEC was also observed in \cite{kardoostsolving}.}.
+This is intuitively explained by the  following: initially, many of the most attractive edge weights have very similar values; when the two nodes $u,v$ with the highest attraction are merged, there is a high chance that they will have a common neighboring node $t$ belonging to the same cluster; thus, the interaction between the merged nodes $uv$ and $t$ is likely assigned to the highest priority, because it is given by the sum of two highly attractive edge weights.
+This will then start a ``chain reaction'' where only a single cluster is agglomerated at the time.
+% This \emph{flooding strategy} in the agglomeration is not observed with other linkage methods, e.g. Average, which grow clusters of similar sizes in parallel.
+In the following, we will show how this unique \emph{flooding strategy} of the sum-linkage methods can be both an advantage or a disadvantage, depending on the type of clustering problem.
+
+\textbf{Comparison to spectral clustering} -- 
+The spectral clustering methods for signed graphs SPONGE$_{sym}$ and SPONGE proposed by \cite{Cucuringu2019SPONGEAG} achieved state of the art performances on SSBM synthetic graphs.
+Their competitive performances are also confirmed by our experiments in Fig.~\ref{fig:SSBM_scores}.
+% First, we compare \algname{} to spectral clustering methods for signed graphs. 
+% In Fig.~\ref{fig:SSBM_scores}, we see that SPONGE$_{sym}$ and SPONGE proposed by \cite{Cucuringu2019SPONGEAG} perform particularly well on synthetic graphs generated with a SSBM. 
+However, these methods do not scale up to the large graph instances considered here and they also require the user to specify the true number of clusters in advance, which is not known for other graph instances tested in this paper.
+In Appendix, Table \ref{tab:cremi_spectral_experiments}, we report the scores achieved by these methods on a much smaller sub-instance of the \emph{CREMI-gridGraph} problem: even when the true number of clusters is specified in advance for the spectral methods, they perform much worse than other \algname{} algorithms, with performance drop of almost 50\%.
+For these reasons, we exclude them from our other comparison experiments.
+
+\textbf{GASP on synthetic SSBM graphs}  -- 
+% can be connected to any  that, depending on the edge-probability parameter $p$, are also \emph{dense}. 
+\algname{} algorithms using cannotLinkConstraints are not expected to perform well on these graphs, because of the type of employed flip noise, so we focus our comparison only on the GAEC, HC-Avg and MWS algorithms (using Sum, Average, and AbsMax linkage methods, respectively).
+Empirically, we observe that GAEC is the agglomerative algorithm performing best on SSBM graphs, almost as good as the spectral method SPONGE$_{sym}$ (see Fig.~\ref{fig:SSBM_scores}).
+Given the simple properties of SSBM graphs, we will now give a specific explanation of these empirical results.
+In SSBM graphs, the number of edges $E_{ij}\equiv(S_i\times S_j)\cap E$ connecting two clusters $S_i,S_j$ is  proportional to the product $|S_i|\cdot|S_j|$ of cluster sizes. 
+With Sum or Avg linkage methods, due to the law of large numbers, the flipping noise is ``averaged out'' as soon as the set $E_{ij}$ becomes larger and clusters grow in size.
+On the other hand, when clusters are small, it is more likely that several of the edges in $E_{ij}$ are flipped and the algorithm makes a mistake by merging two clusters belonging to different ground truth communities.
+From this observation, it follows that the \emph{flooding strategy} of the sum-linkage algorithm GAEC is a very good strategy on these types of graphs, because clusters are immediately grown in size (see dendrograms in Fig.~\ref{fig:dendrograms}).
+Average linkage method HC-Avg instead performs much worse on these graphs because it grows small equally-sized clusters and makes several wrong merge-decisions at the beginning.
+% This observation also explains the empirical results of \cite{chehreghani2020hierarchical}, which involved graph instances with very similar structure to the ones considered here. 
+Lastly, the MWS algorithm is not expected to perform well on these graphs because of the high sensitivity of the AbsMax linkage to flipping noise.
+In Propositions \ref{prop:MWS_SSBM_1} and \ref{prop:MWS_SSBM_2} (see Appendix), we prove that on SSBM graphs the merging steps of the MWS algorithm are given by a sequence of ``coin flip'' decisions with a probability proportional to the noise parameter $\eta$, independently on the cluster sizes.
+
+\textbf{Complete and Single Linkage} -- We use these two linkage methods as baselines to highlight the difficulty of the studied graph clustering problems listed in Table~\ref{tab:datasets_and_energies}.
+Scores in Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show their poor performances: Single linkage hierarchical clustering (HC-Single), which here is equivalent to thresholding the edge weights at $w_e=0$ and computing connected components in the graph, often returned few big under-segmented clusters.
+HC-Complete and HCC-Complete returned instead a lot of over-segmented clusters.
+% These algorithms are excluded from our next comparison experiments.
+
 \begin{figure}[t]
@@
 
-\begin{figure}
-\centering
-% \includegraphics[width=0.48\textwidth,trim=300 100 300 100, clip]{./figs/dendrograms/new_agglo_order_OLD.png} % left bottom right top
-\includegraphics[width=0.48\textwidth,trim=80 10 60 0, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
-\caption{Dendrograms built by three versions of \algname{} (GAEC, MWS, and HC-Avg) on a synthetic graph generated with SSBM ($N=250$, $p=0.05$, $\eta=0.1$, and $k=2$ communities of equal size).
-Red and blue colors represent the true community of each initial node.
-At the top, dendrograms are truncated at the level of the final clustering $\Pi^*$ returned by \algname{} (y-axis shows the iteration number).
-\label{fig:dendrograms}}
-\end{figure}
-
-\textbf{Multicut objective values} -- In Table~\ref{tab:datasets_and_energies}, we report the values of the multicut objective associated to the clusterings obtained with different \algname{} algorithms\footnote{Objective values achieved by Single and Complete linkage methods are much worse compared to other algorithms and are reported in Table \ref{tab:extended_results_cremi}, in Appendix.}.
-Although a lot of heuristics were proposed to better optimize this objective \cite{beier2016efficient,beier2014cut,kernighan1970efficient}, these methods are out of the scope of this paper, since they do not scale up to the largest graph instances considered here.
-By looking at results in Table~\ref{tab:datasets_and_energies}, we observe that GAEC almost always achieves the lowest objective values, apart from the \emph{CREMI-gridGraph} instances.
-Despite this, on graphs where a GT clustering is known, GAEC does not achieve the best ARAND scores (see Tables~\ref{tab:scores_gridGraph} and \ref{tab:scores_3drag}).
-% To better understand these empirical results, we now make the following important observation.
-% This can also be observed in our experiments on synthetic graphs (Fig.
-?
-and ?), where the clustering with minimum multicut energy become very different from the ground truth clustering when the flip noise parameter $\eta$ is increased.
-
-\textbf{Size of growing clusters: Sum vs Avg linkage} -- \TODO{Dendrogram}
-In all the studied clustering problems, we empirically observe that sum-linkage algorithms like GAEC tend to grow clusters one after the other, as shown in Fig.\ \ref{fig:intro_figure} by the unique agglomeration order of GAEC\footnote{This \emph{flooding agglomeration-strategy} of GAEC was also observed in \cite{kardoostsolving}.}.
-This is intuitively explained by the  following: initially, many of the most attractive edge weights have very similar values; when the two nodes $u,v$ with the highest attraction are merged, there is a high chance that they will have a common neighboring node $t$ belonging to the same cluster; thus, the interaction between the merged nodes $uv$ and $t$ is likely assigned to the highest priority, because it is given by the sum of two highly attractive edge weights.
-This will then start a ``chain reaction'' where only a single cluster is agglomerated at the time.
-% This \emph{flooding strategy} in the agglomeration is not observed with other linkage methods, e.g. Average, which grow clusters of similar sizes in parallel.
-In the following, we will show how this unique \emph{flooding strategy} of the sum-linkage methods can be both an advantage or a disadvantage, depending on the type of clustering problem.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.48\textwidth,trim=90 10 60 0, clip]{./figs/comparison_GAEC_MWS_Avg.png} % left bottom right top
-\caption{Failure cases of three versions of \algname{} on challenging parts of the CREMI dataset.
-\emph{Wrongly} segmented regions are highlighted in different warm colors.
-Red arrows point to wrongly split regions; yellow ones to merge errors.
-HC-Avg returned the best segmentation.
-Data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.
-\label{fig:failure_cases}}
-\end{figure}
-
-\textbf{Scores on synthetic SSBM graphs}  -- 
-% can be connected to any  that, depending on the edge-probability parameter $p$, are also \emph{dense}. 
-\algname{} algorithms using cannotLinkConstraints are not expected to perform well on these graphs, because of the type of employed flip noise, so we focus our comparison only on the GAEC, HC-Avg and MWS algorithms (using Sum, Average, and AbsMax linkage methods, respectively).
-Empirically, we observe that GAEC is the agglomerative algorithm performing best on SSBM graphs, almost as good as the spectral method SPONGE$_{sym}$ (see Fig.~\ref{fig:SSBM_scores}).
-Given the simple properties of SSBM graphs, we will now give a specific explanation of these empirical results.
-In SSBM graphs, the number of edges $E_{ij}\equiv(S_i\times S_j)\cap E$ connecting two clusters $S_i,S_j$ is  proportional to the product $|S_i|\cdot|S_j|$ of cluster sizes. 
-With Sum or Avg linkage methods, due to the law of large numbers, the flipping noise is ``averaged out'' as soon as the set $E_{ij}$ becomes larger and clusters grow in size.
-On the other hand, when clusters are small, it is more likely that several of the edges in $E_{ij}$ are flipped and the algorithm makes a mistake by merging two clusters belonging to different ground truth communities.
-From this observation, it follows that the \emph{flooding strategy} of the sum-linkage algorithm GAEC is a very good strategy on these types of graphs, because clusters are immediately grown in size (as compared to the avg-linkage method HC-Avg that grows small clusters and merge them only at the very end).
-This observation also explains the empirical results of \cite{chehreghani2020hierarchical}, which involved graph instances with very similar structure to the ones considered here.
-On the other hand, the MWS algorithm is not expected to perform well on these graphs because of the high sensitivity of the AbsMax linkage to flipping noise.
-In Propositions \ref{prop:MWS_SSBM_1} and \ref{prop:MWS_SSBM_2} (see Appendix), we prove that on SSBM graphs the merging steps of the MWS algorithm are given by a sequence of ``coin flip'' decisions with a probability proportional to the noise parameter $\eta$, independently on the cluster sizes.
-
 \textbf{Scores on CREMI instance-segmentation} -- 
@@
 
+\begin{figure}
+\centering
+% \includegraphics[width=0.48\textwidth,trim=300 100 300 100, clip]{./figs/dendrograms/new_agglo_order_OLD.png} % left bottom right top
+\includegraphics[width=0.48\textwidth,trim=80 10 60 0, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
+\caption{Dendrograms built by three versions of \algname{} (GAEC, MWS, and HC-Avg) on a synthetic graph generated with SSBM ($N=250$, $p=0.05$, $\eta=0.1$, and $k=2$ communities of equal size).
+Red and blue colors represent the true community of each initial node.
+At the top, dendrograms are truncated at the level of the final clustering $\Pi^*$ returned by \algname{} (y-axis shows the iteration number).
+\label{fig:dendrograms}}
+\end{figure}
+
 \textbf{Results on CREMI challenge} -- 
-Table~\ref{tab:cremi_leaderboard} shows that the \emph{HCC-Avg} and \emph{HC-Avg} clustering algorithms included in the proposed \algname{} framework achieve state-of-the-art performances on the CREMI challenge, when combined to the predictions of our CNN.
+Table~\ref{tab:cremi_leaderboard} shows that the \emph{HCC-Avg} and \emph{HC-Avg} clustering algorithms achieve state-of-the-art performances on the CREMI challenge, when combined to the predictions of our CNN.
 Most of the other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs.
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.48\textwidth,trim=90 10 60 0, clip]{./figs/comparison_GAEC_MWS_Avg.png} % left bottom right top
+\caption{Failure cases of three versions of \algname{} on challenging parts of the CREMI dataset.
+\emph{Wrongly} segmented regions are highlighted in different warm colors.
+Red arrows point to wrongly split regions; yellow ones to merge errors.
+HC-Avg returned the best segmentation.
+Data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.
+\label{fig:failure_cases}}
+\end{figure}
+
 % The competitive performance of this simple parameter-free algorithm is also reported in Table \ref{tab:results_cremi_test}, showing the current leader-board of the challenge:

### 2021-03-04 chapters/3_algorithm.tex
More of Nathan comments

@@
 For any clustering $\Pi$ of $\mathcal{G}$, we denote as $E^0_\Pi= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u,v \in S \}$ the set of edges linking nodes in the same cluster.
-The set of edges whose linked nodes belong to distinct clusters, denoted as $E_\Pi^1= E \setminus E^0_\Pi$, is known as the \emph{multicut} of $\mathcal{G}$ associated to clustering $\Pi$.
+Its complementary set $E_\Pi^1= E \setminus E^0_\Pi$ of edges linking nodes belonging to distinct clusters, is known as the \emph{multicut} of $\mathcal{G}$ associated to clustering $\Pi$.
 The instance of the NP-hard \emph{minimum cost multicut problem} w.r.t.

### 2021-03-04 chapters/5_experiments_intro.tex
More of Nathan comments

@@
 We evaluate the agglomerative clustering algorithms included in our framework on a large collection of both synthetic and real-world graphs.
-The size of the graphs ranges from a few hundred to hundreds of millions of edges and the graphs have very different structures, so that the algorithms are tested in different scenarios.
+The size of the graphs ranges from a few hundred to hundreds of millions of edges and the graphs have very different structures, so that the algorithms are tested in very different scenarios.
 

### 2021-03-10 chapters/0_abstract.tex
Rewrite supplementary material and add proofs

@@
 This framework defines GASP, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints.
-We prove the equivalence of existing clustering methods to some of those combinations, and introduce new algorithms for combinations which have not been studied before. 
-We also study theoretical properties of these combinations and prove which one of them define ultrametrics on the graph.
+We prove the equivalence of existing clustering methods to some of those combinations and introduce new algorithms for combinations that have not been studied before. 
+We study both theoretical and empirical properties of these combinations and prove which ones of them define an ultrametric on the graph.
+We conduct a systematic comparison of various instantiations of GASP on a large variety of both synthetic and existing signed clustering problems, in terms of accuracy but also efficiency and robustness to noise.
+Lastly, we find that some of the algorithms included in our framework, when combined with the predictions from a CNN model, result in a simple instance segmentation pipeline that achieves state-of-the-art performances on the competitive CREMI 2016 EM segmentation benchmark.
+
 % On stochastic block model problems, GASP compares favorably to spectral clustering. 
-We conduct a systematic comparison of various instantiations of GASP on a large variety of both synthetic and existing signed clustering problems, in terms of accuracy but also efficiency and robustness to noise.
-More importantly, we find that some of the algorithms proposed in our framework, when combined to the predictions from a CNN model, result in a simple instance segmentation pipeline that achieves state-of-the-art performances on the competitive CREMI 2016 EM segmentation benchmark.
 % \keywords{Partitioning of Signed Graphs, Generalized Framework, Agglomerative Clustering, Instance Segmentation}

### 2021-03-10 chapters/1_intro.tex
Rewrite supplementary material and add proofs

@@
 \caption{\textbf{(a)} Some iterations of \algname{}, the proposed Generalized Agglomerative Algorithm for Signed Graph Partitioning, on a toy graph with attractive/positive (green) and repulsive/negative (red) interactions.
-At each iteration, the yellow edge with highest interaction is contracted (average and sum linkage methods are shown).
+At each iteration, the yellow edge with highest interaction is contracted.
+Average and sum linkage methods are shown.
 \textbf{(b)} List of linkage criteria used in this paper (see definitions in Table~\ref{tab:linkage-criteria} below), demonstrated on two small clusters.
@@
 
-            \thead[r]{GASP on positive-weighted graphs} & \thead{-} &\thead{\textbf{HC-Single}} &\thead{\textbf{HC-Avg}} &\thead{\textbf{HC-Single}} &\thead{\textbf{HC-Complete}} \\
-            \thead[r]{GASP on signed graphs} & \thead{GAEC \cite{keuper2015efficient}} & \thead{\textbf{Mutex Watershed} \cite{wolf2018mutex}}& \thead{\textbf{HC-Avg}} &\thead{\textbf{HC-Single}} &\thead{\textbf{HC-Complete}} \\
+            \thead[r]{GASP on positive-weighted graphs} & \thead{-} &\tikzmark{a} \thead{\textbf{HC-Single}} &\tikzmark{g} \thead{\textbf{HC-Avg}} &\thead{\textbf{HC-Single}}\tikzmark{z} &\thead{\textbf{HC-Complete}} \tikzmark{b} \\
+            \thead[r]{GASP on signed graphs} & \thead{GAEC \cite{keuper2015efficient}} &  \thead{\textbf{Mutex Watershed} \cite{wolf2018mutex}}& \tikzmark{f} \thead{\textbf{HC-Avg}} &\thead{\textbf{HC-Single}} \tikzmark{e} &\thead{\textbf{HC-Complete}}\tikzmark{w} \\
             \thead[r]{GASP on signed graphs + constraints} & \thead{\colorbox{yellow}{HCC-Sum}} % \thead{Greedy Fixation \cite{levinkov2017comparative}} 
-            & \thead{\textbf{Mutex Watershed} \cite{wolf2018mutex}}& \thead{\colorbox{yellow}{HCC-Avg}} &  \thead{\colorbox{yellow}{HCC-Single}} &  \thead{\colorbox{yellow}{HCC-Complete}} \\
+            & \thead{\textbf{Mutex Watershed} \cite{wolf2018mutex}}& \thead{\colorbox{yellow}{HCC-Avg}} &  \thead{\colorbox{yellow}{HCC-Single}} \tikzmark{d} &   \thead{\textbf{HC-Complete}} \tikzmark{c} \\
             % \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\
@@
     \caption{Clustering algorithms included in the proposed \algname{} framework, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
-New algorithms are highlighted in yellow (hierarchical clustering with constraints, HCC).
-Algorithms typeset in bold font define an ultrametric on the graph (see Eq.~\ref{eq:UM_def}).
-Algorithms included in the \TODO{green box}, are weight-shift invariant (see Prop.~\ref{prop:weight_shift_invariant}).
-    We denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two clusters $S_i, S_j$. } 
+New constrained hierarchical clustering algorithms (HCC) are highlighted in yellow.
+Algorithms typeset in bold-font define an ultrametric on the graph (Eq.~\ref{eq:UM_def}).
+Algorithms included in the green box, are weight-shift invariant (Prop.~\ref{prop:weight_shift_invariant}).
+    Given a graph $\mathcal{G}(V,E)$, we denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two clusters $S_i \subseteq V$, $S_j \subseteq V$. } 
     \label{tab:linkage-criteria}
@@
 In this paper, we propose a simple theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical clustering (HC) on positive-weighted graphs \cite{lance1967general}.
-This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints} (see Fig.~\ref{fig:intro_figure}a-b and Table~\ref{tab:linkage-criteria}).
+This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints} (see Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}, \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}b}, and Table~\ref{tab:linkage-criteria}).
 We then formally prove that some of the combinations correspond to existing clustering algorithms, and introduce new algorithms for combinations which have not been explored before.
-By analyzing their theoretical properties, we also show which one of them define ultrametrics on the graph.
+By analyzing their theoretical properties, we also show which one of them define an ultrametric on the graph.
 
-We evaluate the algorithms on a large variety of existing and synthetic signed graph clustering problems. 
-Moreover, we evaluate all algorithms on \emph{instance segmentation} -- a computer vision task consisting in assigning each pixel of an image to an object instance -- by predicting graph edge weights with a CNN (see Fig.~\ref{fig:intro_figure}).
-Our experiments show that the choice of a linkage criterion strongly influences the way how clusters are grown by the agglomerative algorithms, making some linkage methods more suited for certain types of clustering problems.
+We evaluate the algorithms on a large variety of both existing and synthetically generated signed graph clustering problems. 
+Next, we also test the algorithms on \emph{instance segmentation} -- a computer vision task consisting in assigning each pixel of an image to an object instance -- by predicting graph edge weights with a CNN (Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}c}).
+Our experiments show that the choice of a linkage criterion strongly influences the way how clusters are grown by the agglomerative algorithms (Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}d}), making some linkage methods more suited for certain types of clustering problems.
 % We focus our comparison on three of the best-performing algorithms included in our framework, which are based on average, sum, and absolute maximum linkage criteria (see Table~\ref{tab:linkage-criteria}).
@@
 We benchmark the clustering algorithms by focusing on their efficiency, robustness and tendency to over- or under-cluster. 
-First, we observe that the tested agglomerative algorithms strongly outperform recently proposed spectral clustering methods.
-Then,  we also show that average-linkage based agglomerative algorithms achieve state of the art results on the competitive CREMI 2016 challenge for neuron segmentation of 3D electron microscopy image volumes of brain tissue.
+On instance segmentation, we show that the tested agglomerative algorithms strongly outperform recently proposed spectral clustering methods, and that average-linkage based agglomerative algorithms achieve state of the art results on the competitive CREMI 2016 challenge for neuron segmentation of 3D electron microscopy image volumes of brain tissue.
+
+\begin{tikzpicture}[remember picture,overlay]
+% (shift_along_horizontal, shift_along_vertical)
+% a ---------------------------- b
+%            g -----------------
+%            f         e ------- 
+%                      d         c
+% 
+\draw [green,line]($(a)+(0,2ex)$)--($(b)+(0.9ex,2ex)$)--($(c)+(0.9ex,-1.5ex)$) -- ($(d)+(1.4ex,-1.5ex)$) -- ($(e)+(1.4ex,-1.2ex)$) -- ($(f)+(-0.3ex,-1.2ex)$)--($(g)+(-0.3ex,-1.2ex)$)--($(a)+(0,-1.2ex)$)--cycle;
+\end{tikzpicture}
 

### 2021-03-10 chapters/3_algorithm.tex
Rewrite supplementary material and add proofs

@@
 \paragraph{Sum Linkage} -- 
-An agglomerative algorithm with sum linkage does only make sense for graphs with signed edge weights, because only for these graphs the sum of two attractive (or repulsive) interactions is still attractive (repulsive).
-On positive weighted graphs, on the other hand, a strong attractive interaction could be obtained by summing many weak interactions, which is not desirable.
-Such an algorithm was pioneered in \cite{levinkov2017comparative,keuper2015efficient} and was named Greedy Agglomerative Edge Contraction (GAEC)\footnote{An algorithm equivalent to GAEC was recently independently re-proposed in \cite{chehreghani2020hierarchical}.}.
+On signed graphs, the sum of two attractive (or repulsive) interactions is still attractive (repulsive).
+On the other hand, on positive weighted graphs, a strong attractive interaction could be obtained by summing many weak interactions, which is often not desirable.
+This explains why, to our knowledge, an agglomerative algorithm with sum linkage has never been used on positive weighted graphs.
+On signed graphs, such an algorithm was pioneered in \cite{levinkov2017comparative,keuper2015efficient} and was named Greedy Agglomerative Edge Contraction (GAEC)\footnote{An algorithm equivalent to GAEC was recently independently re-proposed in \cite{chehreghani2020hierarchical}.}.
 All variations of \algname{} decrease the multicut objective defined in Eq.~\ref{eq:MC_objective} each time two clusters with positive interaction are merged.
@@
 \paragraph{AbsMax Linkage} -- This linkage method is also specific to signed graphs, since on positive-weighted graphs it would be equivalent to single linkage.
-Here, we prove that the Mutex Watershed Algorithm \cite{wolf2018mutex} can be seen as an agglomerative algorithm with AbsMax linkage (see proof in Appendix):
-\begin{prop} 
+Here, we prove that the Mutex Watershed Algorithm \cite{wolf2018mutex} can be seen as an agglomerative algorithm with AbsMax linkage (proofs of the following propositions are given in Appendix \ref{sec:proposition_proofs}):
+\begin{restatable}{prop}{absmaxmutex}
+\label{prop:absmax_mutex}
 The \algname{} Algorithm \ref{main_alg} with AbsMax linkage (see def.
@@
 In particular, $\Pi^*_{\mathrm{AbsMax}}$ is equal to the clustering returned by the Mutex Watershed Algorithm (MWS) \cite{wolf2018mutex}, which has empirical complexity $\mathcal{O}(N \log N)$.
-\end{prop}
+\end{restatable}
+% \begin{prop} 
+% \end{prop}
 
@@
 In the recent related work \cite{chehreghani2020hierarchical}, the authors prove that applying these three linkage methods to a signed graph is equivalent to applying them to the positive-weighted graph obtained by shifting all edge weights by a constant.
-Here, we prove which of the algorithms included in our generalized framework have this invariance-property: (proof in Appendix)
-\begin{prop} \label{prop:weight_shift_invariant}
+Here, we prove which of the algorithms included in our generalized framework have this invariance-property:
+\begin{restatable}{prop}{invariantAlgs}
+\label{prop:weight_shift_invariant}
 We call an agglomerative algorithm ``weight-shift invariant'' if the structure of the merging tree $T$ returned by such algorithm is invariant w.r.t.
 a shift of all edge weights $w_e$  by a constant $\alpha\in \mathbb{R}$.
-Among the versions of \algname{} studied in this paper, only those using Average, Single, and Complete linkage criteria without cannotLinkConstraints are weight-shift-invariant (see algorithms typeset in bold font in Table~\ref{tab:linkage-criteria}).
-\end{prop}
-\noindent To our knowledge, Avg, Single, and Complete linkage methods have never been combined with cannot-link constraints on signed graphs, so the algorithms that in Table~\ref{tab:linkage-criteria} are named \emph{HCC-Avg}, \emph{HCC-Single}, and \emph{HCC-Complete} are new.
+Among the versions of \algname{} studied in this paper, only hierarchical clustering using Average (HC-Avg), Single (HC-Single), and Complete linkage (HC-Complete) are weight-shift-invariant (see algorithms included in the green box in Table~\ref{tab:linkage-criteria}).
+\end{restatable}
+\noindent To our knowledge, Average and Single linkage methods have never been combined with cannot-link constraints on signed graphs, so the constrained hierarchical clustering algorithms that in Table~\ref{tab:linkage-criteria} are named \emph{HCC-Avg} and \emph{HCC-Single} are new.
+In Lemma \ref{lemma:absMax_and_complete_property} (Appendix \ref{sec:proposition_proofs}), we prove that with a Complete linkage the agglomeration order does not change whether constraints are introduced or not.
 
@@
 \end{align}
-and where $\epsilon > 0$. By definition, we have that $d_{T}(u,v)=d_{T}(v,u)$ and $d_{T}(u,u)= 0$. We then prove the following two propositions (proofs are left in Appendix):
-\begin{prop}
-Consider a graph $\mathcal{G}(V,E,w_e)$, a linkage criterion $\interact{}$, and an AC algorithm returning a binary rooted tree $T$ with height $h_T$.
-The quantity $(V, d_{T})$ defined in Eq.~\ref{eq:UM_def} is an ultrametric iff, $\forall u,v,t \in V$:
-\begin{equation}
-\interact{}_{T}(u,v) > \interact{}_{T}(u,t) \Leftrightarrow h_T(u \vee v) < h_T[u \vee t] 
+and where $\epsilon > 0$. By definition, we have that $d_{T}(u,v)=d_{T}(v,u)$ and $d_{T}(u,u)= 0$. We then prove the following two propositions:
+\begin{restatable}{prop}{firstUltraMetricProperty}
+\label{prop:ultraMetric1}
+Consider a graph $\mathcal{G}(V,E,w_e)$, a linkage criterion $\interact{}$, and an agglomerative algorithm returning a binary rooted tree $T$ with height $h_T$.
+Then, $(V, d_{T})$ defined in Eq.~\ref{eq:UM_def} is an ultrametric if and only if the following is true
+ % iff the interaction $\interact{}_{T}(u, v)$ associated to the least common ancestor ${(u\vee v)\in T}$ is both lower than the interaction of any other $(u\vee v)$-descendant node and higher than the interaction of any other $(u\vee v)$-ancestor node in the tree $T$.
+In formulae, this is equivalent to saying that, $\forall u,v,t \in V$:
+\begin{equation}\label{eq:UM_assumption}
+ h_T(u \vee v) < h_T(u \vee t) \Rightarrow \interact{}_{T}(u,v) \geq \interact{}_{T}(u,t),
+ % h_T(u \vee v) < h_T(u \vee t) \Leftrightarrow \interact{}_{T}(u,v) > \interact{}_{T}(u,t). 
 \end{equation}
-In words, $(V, d_{T})$ is an ultrametric iff the interaction $\interact{}_{T}(u, v)$ associated to the least common ancestor ${(u\vee v)\in T}$ is both lower than any other $(u\vee v)$-descendant node and higher than any other $(u\vee v)$-ancestor node in the tree $T$.
-\end{prop}
-\begin{prop}
+which in words means: if the algorithm merges nodes $u,v$ before to merge nodes $u,t$, then the signed interaction $\interact{}_{T}(u,v)$ between $u$ and $v$ has to be higher or equal than $\interact{}_{T}(u,t)$.
+% In words, $(V, d_{T})$ is an ultrametric iff the interaction $\interact{}_{T}(u, v)$ associated to the least common ancestor ${(u\vee v)\in T}$ is both lower than any other $(u\vee v)$-descendant node and higher than any other $(u\vee v)$-ancestor node in the tree $T$.
+\end{restatable}
+\begin{restatable}{prop}{secondUltraMetricProperty}
+\label{prop:ultraMetric2}
 % Consider the binary rooted tree $T^*$ returned by the \TODO{all variants in Table 1} \algname{} Algorithm~\ref{main_alg}, given a choice of linkage criteria $\interact{}$ and the use (or not) of CannotLinkConstraints.
-Among the algorithms listed in Table \ref{tab:linkage-criteria} and included in the \algname{} framework, only Mutex Watershed and hierarchical clustering with Average (HC-Avg), Single (HC-Single) and Complete linkage (HC-Complete) define an ultrametric given by the quantity $(V, d_{T^*})$ defined in Eq.~\ref{eq:UM_def}, where $T^*$ is the tree returned by Algorithm~\ref{main_alg}.
-\end{prop}
+Among the algorithms included in the \algname{} framework (see Table \ref{tab:linkage-criteria}), only Mutex Watershed and hierarchical clustering with Average (HC-Avg), Single (HC-Single) and Complete linkage (HC-Complete) define an ultrametric $(V, d_{T^*})$, where $d_{T^*}$ is defined in Eq.~\ref{eq:UM_def} and $T^*$ is the tree returned by the \algname{} Algorithm~\ref{main_alg}.
+\end{restatable}
 

### 2021-03-10 chapters/5_experiments_intro.tex
Rewrite supplementary material and add proofs

@@
 We train a 3D U-Net \cite{ronneberger2015u,cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
-as described in \cite{lee2017superhuman}\footnote{See Appendix \ref{sec:cremi_details} for all details about training and data augmentation.}.
+as described in \cite{lee2017superhuman}.
 The predicted affinities $a_e\in[0,1]$, which represent how likely it is for a pair of pixels to belong to the same neuron segment, are then mapped to signed edge weights $w_e=a_e-0.5$, resulting in a 3D grid-graph having a node for each pixel/voxel of the  image\footnote{To map affinities to signed weights, we also tested the \emph{logarithmic mapping} proposed in \cite{finkel2008enforcing,andres2012globally}, but it performed worse in our experiments.}.
-Clustering algorithms largely benefit from long-range edge connections in the grid-graph, in addition to direct-neighbors ones.
-However, empirically, we found that long-range affinities predicted by the CNN are also more noisy, and adding only 10\% of them (by random sampling) gave the best results.
 % \TODO{long-range 10\%} 
@@
 We divided the three CREMI training samples, consisting of $\sim$196 million voxels each, into five sub-blocks for a total of 15 clustering problems (named \emph{CREMI-gridGraph} in Table~\ref{tab:datasets_and_energies}).
+See Appendix \ref{sec:cremi_details} for extended details about training, data augmentation, and how we remove tiny clusters after running \algname{} on the \emph{CREMI-gridGraph} clustering problems.
 
 \textbf{3D-rag from CNN-predictions} -- Lastly, we use the predictions of our CNN model to generate three graph instances (one for each CREMI training sample, named \emph{CREMI-3D-rag} in Table~\ref{tab:datasets_and_energies}), which have very similar structure to the \emph{Knott-3D} and \emph{Fruit-Fly} instances.
-We obtain them by first computing 2D supervoxels from the CNN predictions (using a watershed algorithm seeded at the maxima of the smoothed boundary distance transform) and then building a 3D region-adjacency graph, whose edge weights are given by the CNN affinities averaged over the boundaries of adjacent supervoxels.
+We obtain these problems by using a pipeline that is very common in neuron segmentation: a watershed algorithm generates superpixels and from those a 3D region-adjacency graph is built, where edge weights are given by the CNN predictions averaged over the boundaries of adjacent superpixels (details in Appendix \ref{sec:cremi_details}).
+% them by first computing 2D supervoxels from the CNN predictions (using a watershed algorithm seeded at the maxima of the smoothed boundary distance transform) and then building a 3D region-adjacency graph, whose edge weights are given by the CNN affinities averaged over the boundaries of adjacent supervoxels.
 
@@
 HCC-Sum & 0.0872 & 0.365 & 0.337 & 4970 \\
-HCC-Complete & 0.9206 & 4.531 & \textbf{0.210} & 1330 \\
-HC-Complete & 0.9211 & 4.536 & 0.211 & 1020 \\
+% HCC-Complete & 0.9206 & 4.531 & \textbf{0.210} & 1330 \\
+HC-Complete & 0.9211 & 4.536 & \textbf{0.211} & 1020 \\
 HC-Single & 0.9264 & \textbf{0.060} & 4.887 & \textbf{312} \\
@@
         \end{tabular}
+        \vspace*{1em}
     % \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding.
@@
 HC-Single & 0.5282 & \textbf{0.437} & 1.367 & \textbf{85} \\
-HCC-Complete & 0.5564 & 2.220 & 0.254 & 89 \\
+% HCC-Complete & 0.5564 & 2.220 & 0.254 & 89 \\
 HC-Complete & 0.5654 & 2.253 & \textbf{0.249} & 86 \\
         \end{tabular}
-        \hspace*{5em}
+        % \hspace*{5em}
+        \vspace*{1em}
     \caption{\emph{CREMI-3D-rag (OurCNN)}}
@@
 
-\textbf{Multicut objective values} -- In Table~\ref{tab:datasets_and_energies}, we report the values of the multicut objective associated to the clusterings obtained with different \algname{} algorithms\footnote{Objective values achieved by Single and Complete linkage methods are much worse compared to other algorithms and are reported in Table \ref{tab:extended_results_cremi}, in Appendix.}.
+\textbf{Multicut objective values} -- In Table~\ref{tab:datasets_and_energies}, we report the values of the multicut objective associated to the clusterings obtained with different \algname{} algorithms\footnote{Objective values achieved by Single and Complete linkage methods are much worse compared to other algorithms and are reported in Table \ref{tab:all_multicut_energies}, in Appendix.}.
 Although a lot of heuristics were proposed to better optimize this objective \cite{beier2016efficient,beier2014cut,kernighan1970efficient}, these methods are out of the scope of this paper, since they do not scale up to the largest graph instances considered here.
@@
 \textbf{Size of growing clusters: Sum vs Avg linkage} --
-In all the studied clustering problems, we empirically observe that sum-linkage algorithms like GAEC tend to grow clusters one after the other, as shown in Fig.\ \ref{fig:intro_figure} and \ref{fig:dendrograms} by the unique agglomeration order of GAEC\footnote{This \emph{flooding agglomeration-strategy} of GAEC was also observed in \cite{kardoostsolving}.}.
+In all the studied clustering problems, we empirically observe that sum-linkage algorithms like GAEC tend to grow clusters one after the other, as shown in Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}d} and Fig.~\ref{fig:dendrograms} by the unique agglomeration order of GAEC\footnote{This \emph{flooding agglomeration-strategy} of GAEC was also observed in \cite{kardoostsolving}.}.
 This is intuitively explained by the  following: initially, many of the most attractive edge weights have very similar values; when the two nodes $u,v$ with the highest attraction are merged, there is a high chance that they will have a common neighboring node $t$ belonging to the same cluster; thus, the interaction between the merged nodes $uv$ and $t$ is likely assigned to the highest priority, because it is given by the sum of two highly attractive edge weights.
@@
 However, our method operating directly on pixels (\emph{gridGraph+HCC-Avg}) achieves better performances than superpixel-based methods (\emph{3D-rag+HCC-Avg}) and does not require the parameter tuning necessary to obtain good super-pixels, which is usually highly dataset dependent.
-The method \emph{3D-rag+LiftedMulticut} based on the lifted multicut formulation of \cite{beier2017multicut} (see details in Appendix) achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and super-pixel shape information.
+The method \emph{3D-rag+LiftedMulticut} based on the lifted multicut formulation of \cite{beier2017multicut} achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and super-pixel shape information.
 To scale up our method operating on pixels, we divided each test-volume into four sub-blocks, and then combined the resulting clusterings by running the algorithms again on the combined graph.

### 2021-03-10 chapters/supplementary.tex
Rewrite supplementary material and add proofs

--- 2021-02-19 chapters/supplementary.tex
@@
 
-\begin{algorithm*}
-  \caption{Implementation of \algname{}, generalized algorithm for signed graph partitioning}
+\renewcommand{\thesection}{A\arabic{section}}
+\renewcommand{\thetable}{A\arabic{table}}
+\renewcommand{\thefigure}{A\arabic{figure}}
+
+\section{Appendix}
+
+\subsection{Implementation and complexity of \algname{}} \label{sec:detailed_impl}
+
+\paragraph*{Update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed, as shown in Algorithm \ref{main_alg}.  
+An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph.
+Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that there exists exactly one representative $|\tilde{V} \cap S| = 1$ for every cluster $S \in \Pi$ .
+Edges in $\tilde{E}$ represent adjacency-relationships between clusters
+and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$. 
+For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$.
+Thus, we can recompute these interactions by using an \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$:
+\begin{align}
+  \interact(S_u \cup S_v,S_t) =& f\Big[ \interact(S_u,S_t), \interact(S_v,S_t) \Big] \\
+  =& f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) 
+\end{align}
+In Fig.
+\ref{fig:edge_contraction_and_contr_graph} we show an example of edge contraction and in Table \ref{tab:linkage_criteria_explicit} we list the update rules associated to the linkage criteria we introduced in Table \ref{tab:linkage-criteria}.
+
+\afterpage{ %
+  \begin{algorithm*}[p]
+    \caption{Implementation of \algname{} - Phase 1}
   \hspace*{\algorithmicindent} \textbf{Input:} $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes and $M$ edges; boolean \texttt{{\color{blue}addCannotLinkConstraints}} \\
@@
   \end{algorithm*}
-
-\section{Supplementary material}
-
-\subsection{Implementation details and complexity of \algname{}} \label{sec:detailed_impl}
-
-\paragraph*{Update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed, as shown in Algorithm \ref{main_alg}.  
-An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph.
-Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that there exists exactly one representative $|\tilde{V} \cap S| = 1$ for every cluster $S \in \Pi$ .
-Edges in $\tilde{E}$ represent adjacency-relationships between clusters
-and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$. 
-For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$.
-Thus, we can recompute these interactions by using an \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$:
-\begin{align}
-  \interact(S_u \cup S_v,S_t) =& f\Big[ \interact(S_u,S_t), \interact(S_v,S_t) \Big] \\
-  =& f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) 
-\end{align}
-In Fig.
-\ref{fig:edge_contraction_and_contr_graph} we show an example of edge contraction and in Table \ref{tab:linkage_criteria_explicit} we list the update rules associated to the linkage criteria we introduced in Table \ref{tab:linkage-criteria}.
-
-\paragraph{Implementation} As we show in Algorithm \ref{detailed_alg}, our implementation of \algname{} is based on an union-find data structure and a heap allowing deletion of its elements.
-The algorithm starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a heap/priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first.
-It then iteratively pops one edge $e_{uv}$ from PQ and, depending on the priority $\tilde{\cost}_{uv}$, does the following: in case of attractive interaction $\tilde{\cost}_{uv}>0$, provided that $e_{uv}$ was not flagged as a cannot-link constraint, then merge the connected clusters, perform an edge contraction of $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and update the priorities of new double edges as explained in Fig.
-\ref{fig:edge_contraction_and_contr_graph}.
-If, on the other hand, the interaction is repulsive ($\tilde{\cost}_{uv}\leq 0$) and the option \texttt{addCannotLinkContraints} of Alg.
-\ref{detailed_alg} is \texttt{True}, then the edge $e_{uv}$ is flagged as cannot-link constraint.
-
-\paragraph*{Complexity} In the main loop, the algorithm iterates over all edges, but the only iterations presenting a complexity different from $\mathcal{O}(1)$ are the ones involving a merge of two clusters, which are at most $N-1$.
-By using a union-find data structure (with path compression and union by rank) the time complexity of \texttt{merge}$(u, v)$ and \texttt{find}($u$) operations is $\mathcal{O}(\alpha(N))$, where $\alpha$ is the slowly growing inverse Ackerman function.
-The algorithm then iterates over the neighbors of the merged cluster (at most $N$) and updates/deletes values in the priority queue ($\mathcal{O}(\log |E|)$).
-Therefore, similarly to a heap-based implementation of hierarchical agglomerative clustering, our implementation of \algname{} has a complexity of $\mathcal{O}(N^2 \log N)$.
-In the worst case, when the graph is dense and $|E|=N^2$, the algorithm requires $\mathcal{O}(N^2)$ memory.
-Nevertheless, in our practical applications the graph is much sparser, so $\mathcal{O}(|E|)=\mathcal{O}(N)$.
-With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$.
-Moreover, in the next section, we present an efficient implementation of \algname{} with \emph{Absolute Maximum} linkage that has empirical $\mathcal{O}(N \log N)$ complexity.
-%\TODO{Empirical complexity plot?}
-\begin{figure}[H]
-        \centering
-        \includegraphics[width=0.6\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
-    \centering
-    \caption{Example of edge contraction.
-First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars).
-Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$.
-In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$.
-In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from the edge contraction are replaced by a single edge with updated interaction.}\label{fig:edge_contraction_and_contr_graph}
-\end{figure}
-\begin{table}[H]
-\centering
-    \small
-    \vspace{-2em}
-\begin{tabular}[t]{r | l }
-            \toprule
-            Linkage criteria & Update rule $f$ \\        
-            \midrule
-            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} \\ 
-            \makecell[r]{Absolute \\Maximum:} & \thead[l]{
-            $
-            f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
-            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
-            \tilde{\cost}_2 & \text{otherwise}
-             \end{cases} 
-            $}
-               \\ 
-            \makecell[r]{Average:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                 \\ 
-            Maximum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} \\
-            Minimum:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} 
-        \end{tabular}\vspace{1em}
-        \caption{The table lists the update rules $f(\tilde{\cost}_1, \tilde{\cost}_2)$ associated to the linkage criteria of Table \ref{tab:linkage-criteria} and that are used to efficiently update the interactions between clusters.}
-\label{tab:linkage_criteria_explicit}  
-\end{table}
-
-\begin{figure*}[t]
-        \centering
-        \includegraphics[width=0.7\textwidth]{./figs/proof_abs_max_example.pdf} % left bottom right top
-\caption{\algname{} with \emph{AbsMax} linkage: Example representing the only case of edge contraction $e_{uv}$ that would introduce a positive attractive interaction between two constrained clusters.
+  % \begin{figure*}[t]
+  %         \centering
+  %         \includegraphics[width=0.7\textwidth]{./figs/proof_abs_max_example.pdf} % left bottom right top
+  % \caption{\algname{} with \emph{AbsMax} linkage: Example representing the only case of edge contraction $e_{uv}$ that would introduce a positive attractive interaction between two constrained clusters.
 Note this can actually never happen with an \emph{AbsMax} linkage, because edge $e_{ut}$ has a lower absolute priority as compared to $e_{uv}$, so clusters $u$ and $t$ cannot have been constrained before $u$ and $v$ are merged.
-}
-\label{fig:abs_max_proof_example}  
-\end{figure*}
-\begin{algorithm*}[t]
+\TODO{Remove?}
+  % }
+  % \label{fig:abs_max_proof_example}  
+  % \end{figure*}
+  \begin{algorithm*}[p]
     \caption{Mutex Watershed Algorithm proposed by \cite{wolf2018mutex}}
@@
   \end{algorithm*}
+  \clearpage
+}
 
-\subsection{Properties of \algname{} with Absolute Maximum linkage}\label{sec:appendix_abs_max}
-\paragraph{Remark on graph notation} The definition of a graph proposed by \cite{wolf2018mutex} makes a distinction between a set of positive edges $E^+$, associated with a set $W^+$ of positive scalar attributes representing merge affinities, and a set of negative edges $E^-$, associated with a set $W^-$ of positive attributes representing split tendencies.
-On the other hand, in our definition $\mathcal{G}(V,E,w^+,w^-)$ each edge have both an attractive $w_e^+$ and a repulsive $w_e^-$ attribute, so we can make them equivalent by defining:
-\begin{align}
-E^+ =&\,\, \{ e \in E \,\,\text{s.t.} \,\,w_e = w_e^+ - w_e^- > 0\}, \\
-E^- =&\,\, \{ e \in E \,\,\text{s.t.}\,\, w_e = w_e^+ - w_e^- \leq 0\}, \\
-W^+ =&\,\, \{ |w_e| \,\,\text{s.t.}\,\, e \in E^+\},\\
- W^- =&\,\, \{ |w_e| \,\,\text{s.t.}\,\, e \in E^-\}.
-\end{align}
+\paragraph{Implementation} Our implementation of \algname{} is based on an union-find data structure and a heap allowing deletion of its elements. 
+In Phases 2 and 3, \algname{} is equivalent to a standard hierarchical agglomerative clustering algorithm for unsigned graphs.
+In Algorithm \ref{detailed_alg}, we show our implementation of Phase 1, involving cannot-link constraints.
+In phase 1, the algorithm starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a heap/priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first.
+It then iteratively pops one edge $e_{uv}$ from PQ and, depending on the priority $\tilde{\cost}_{uv}$, does the following: in case of attractive interaction $\tilde{\cost}_{uv}>0$, provided that $e_{uv}$ was not flagged as a cannot-link constraint, then merge the connected clusters, perform an edge contraction of $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and update the priorities of new double edges as explained in Fig.
+\ref{fig:edge_contraction_and_contr_graph}.
+If, on the other hand, the interaction is repulsive ($\tilde{\cost}_{uv}\leq 0$) and the option \texttt{addCannotLinkContraints} of Alg.
+\ref{detailed_alg} is \texttt{True}, then the edge $e_{uv}$ is flagged as cannot-link constraint.
 
-\begin{prop} \label{prop:equiv_MWS}
-The Mutex Watershed Algorithm \ref{alg:mutex_watershed} (MWS) with empirical \linebreak $\mathcal{O}(N \log N)$ complexity introduced by \cite{wolf2018mutex} returns the same final clustering given by the \algname{} Algorithm \ref{detailed_alg} with the use of cannot-link constraints and an Absolute Maximum update rule:
-\begin{equation}\label{eq:def_abs_max}
-f_{\mathrm{Abs.Max.}}(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
+\begin{table}[t]
+\centering
+    \small
+    % \vspace{-2em}
+\begin{tabular}[t]{r | l }
+            \toprule
+            Linkage criteria & Update rule $f$ \\        
+            \midrule
+            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} \\ 
+            \makecell[r]{Absolute \\Maximum:} & \thead[l]{
+            $
+            f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
             \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
@@
              \end{cases} 
-\end{equation}
-\end{prop}
+            $}
+               \\ 
+            \makecell[r]{Average:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                 \\ 
+            Single: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} \\
+            Complete:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} 
+        \end{tabular}\vspace{1em}
+        \caption{The table lists the update rules $f(\tilde{\cost}_1, \tilde{\cost}_2)$ associated to the linkage criteria of Table \ref{tab:linkage-criteria} and that are used to efficiently update the interactions between clusters.}
+\label{tab:linkage_criteria_explicit}  
+\end{table}
+\begin{figure}[t]
+        \centering
+        \includegraphics[width=0.48\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
+    \centering
+    \caption{Example of edge contraction.
+First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars).
+Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$.
+In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$.
+In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from the edge contraction are replaced by a single edge with updated interaction.}\label{fig:edge_contraction_and_contr_graph}
+\end{figure}
+
+\paragraph*{Complexity} 
+In the main loop of Phase 1, the algorithm iterates over all edges, but the only iterations presenting a complexity different from $\mathcal{O}(1)$ are the ones involving a merge of two clusters, which are at most $N-1$.
+By using a union-find data structure (with path compression and union by rank) the time complexity of \texttt{merge}$(u, v)$ and \texttt{find}($u$) operations is $\mathcal{O}(\alpha(N))$, where $\alpha$ is the slowly growing inverse Ackerman function.
+The algorithm then iterates over the neighbors of the merged cluster (at most $N$) and updates/deletes values in the priority queue ($\mathcal{O}(\log |E|)$).
+Therefore, 
+similarly to a heap-based implementation of hierarchical agglomerative clustering, our implementation of \algname{} has a complexity of $\mathcal{O}(N^2 \log N)$.
+In the worst case, when the graph is dense and $|E|=N^2$, the algorithm requires $\mathcal{O}(N^2)$ memory.
+Nevertheless, in our practical applications the graph is much sparser, so $\mathcal{O}(|E|)=\mathcal{O}(N)$.
+With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$.
+Moreover, \algname{} with \emph{Absolute Maximum} linkage can be implemented more efficiently (see next section). %\TODO{Empirical complexity plot?}
+
+\subsection{Proofs of Propositions \ref{prop:absmax_mutex}, \ref{prop:weight_shift_invariant}, \ref{prop:ultraMetric1}, and \ref{prop:ultraMetric2}  }
+\label{sec:proposition_proofs}
+% \subsubsection{Mutex Watershed and AbsMax linkage}\label{sec:appendix_abs_max}
+\begin{lemma} \label{lemma:absMax_and_complete_property}
+Let us consider the \algname{} Algorithm \ref{main_alg} with AbsMax or Complete linkage criteria (see linkage definition in Table \ref{tab:linkage-criteria}).
+If the algorithm enforces a constraint between two clusters in \emph{Phase 1}, then the interaction between the clusters will never become positive over the course of the following agglomeration steps.
+Moreover, we also have that with any of these two linkages: i) \algname{} returns the same final clustering whether or not cannot-link constraints are enforced; ii) no clusters are merged in \emph{Phase 2} (after constraints have been removed).
+\end{lemma}
 \begin{proof}
+First, we note that two clusters are constrained in \emph{Phase 1} only if their interaction is repulsive.
+We then also observe that with complete linkage (see Table~\ref{tab:linkage_criteria_explicit}) the signed interaction between two clusters can only decrease over the course of the agglomeration.
+Thus, if two clusters are constrained by the algorithm, their negative interaction cannot increase and become positive later on in the agglomeration process.
+
+If, on the other hand, we consider \algname{} with a Absolute Maximum linkage (see Table~\ref{tab:linkage_criteria_explicit}), during the agglomeration the interaction between two clusters can only increase in absolute value.
+Thus, the negative interaction $\interact{}(S_i,S_j)<0$ between two constrained clusters can possibly become positive over the course of next agglomeration steps only if there is at least another pair of clusters with positive interaction $\interact{}(S_l,S_t)>0$ higher in absolute value: $|\interact{}(S_l,S_t)| > |\interact{}(S_i,S_j)|$.
+If such clusters $S_l, S_t$ with positive interaction exist, we note that they must also be constrained (in the opposite case, the algorithm would have already merged them before to constrain $S_i$ and $S_j$, because their priority was higher).
+In other words, a constrained negative interaction can become positive only if there is already another positive constrained interaction: but this can never be the case because initially all constrained interactions are negative.
+
+Finally, we prove that \algname{} with either AbsMax or Complete linkage returns the same final clustering whether or not cannot-link constraints are enforced.
+In Algorithm \ref{detailed_alg}, the interactions between clusters are updated only when two clusters are merged and the condition at line 9 is satisfied (i.e.
+when an interaction is both positive and not constrained).
+However, we have just shown that with these two linkage methods an interaction can never be both positive and constrained at the same time, so we directly conclude that the constrained and unconstrained versions of the algorithm will perform precisely the same agglomeration steps.
+\end{proof}
+
+% We now prove Proposition \ref{prop:absmax_mutex}:
+
+\absmaxmutex*
+
+% \begin{prop} \label{prop:equiv_MWS}
+% The Mutex Watershed Algorithm \ref{alg:mutex_watershed} (MWS) with empirical \linebreak $\mathcal{O}(N \log N)$ complexity introduced by \cite{wolf2018mutex} returns the same final clustering given by the \algname{} Algorithm \ref{detailed_alg} with the use of cannot-link constraints and an Absolute Maximum update rule:
+% \begin{equation}\label{eq:def_abs_max}
+% f_{\mathrm{Abs.Max.}}(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
+%             \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
+%             \tilde{\cost}_2 & \text{otherwise}
+%              \end{cases} 
+% \end{equation}
+% \end{prop}
+
+% \paragraph{Remark on graph notation in \cite{wolf2018mutex}} The definition of a graph proposed by \cite{wolf2018mutex} makes a distinction between a set of positive edges $E^+$, associated with a set $W^+$ of positive scalar attributes representing merge affinities, and a set of negative edges $E^-$, associated with a set $W^-$ of positive attributes representing split tendencies.
+On the other hand, in our definition $\mathcal{G}(V,E,w^+,w^-)$ each edge have both an attractive $w_e^+$ and a repulsive $w_e^-$ attribute, so we can make them equivalent by defining:
+% \begin{align}
+% E^+ =&\,\, \{ e \in E \,\,\text{s.t.} \,\,w_e = w_e^+ - w_e^- > 0\}, \\
+% E^- =&\,\, \{ e \in E \,\,\text{s.t.}\,\, w_e = w_e^+ - w_e^- \leq 0\}, \\
+% W^+ =&\,\, \{ |w_e| \,\,\text{s.t.}\,\, e \in E^+\},\\
+%  W^- =&\,\, \{ |w_e| \,\,\text{s.t.}\,\, e \in E^-\}.
+% \end{align}
+
+\begin{proof}%[Proof of Proposition \ref{prop:absmax_mutex}]
+From Lemma~\ref{lemma:absMax_and_complete_property} it directly follows that \algname{} with AbsMax linkage criterion returns the same final clustering whether or not cannot-link constraints are enforced.
+In the following, we prove that MWS and the constrained AbsMax version of \algname{} also return the same clustering.
 Both algorithms sort edges in descending order of the absolute interactions $|w_e|$ and then iterate over all of them.
@@
 Thus, both algorithms perform precisely the same steps and return the same clustering.
+% Next, we prove that \algname{} with AbsMax linkage method returns the same final clustering whether or not cannot-link constraints are enforced.
+In the \algname{} Algorithm \ref{detailed_alg}, the interactions between clusters are updated only when two clusters are merged and the condition at line 9 is satisfied (an interaction is both positive and not constrained).
+% We also observe that, in the unconstrained version of \algname{}, the predicate \texttt{canBeMerged} at line 9 can never be false because cannot-link constraints are never introduced at line 14.
+\TODO{Rephrase}
+% Let us now contradict the initial hypothesis and assume by absurd that the constrained version of \algname{} introduces a cannot-link constraints between two clusters sharing a positive interaction $\tilde{w}>0$ and outputs a different clustering as compared to the unconstrained version.
+% This can happen only in the situation shown in Fig.
+\ref{fig:abs_max_proof_example}, when two clusters $u$ and $v$ are merged together and share a common neighboring node $t$ having the following two properties: a) $u$ and $t$ are already constrained and share a repulsive interaction $w_{ut}\leq0$, b) $v$ and $t$ share an attractive interaction $w_{vt}>0$ that is higher in absolute value $|w_{vt}|>|w_{ut}|$.
+% Then, according to Eq. \ref{eq:def_abs_max}, \TODO{} the new merged cluster $uv$ and $t$ are constrained and share a positive interaction. 
+% But this case can never happen, since if $|w_{vt}|>|w_{ut}|$ then clusters $v$ and $t$ are merged before clusters $u$ and $t$ are constrained.  
 \end{proof}
-\begin{prop} \label{prop:abs_max_cannot_link_property}
-The \algname{} Algorithm \ref{detailed_alg} with the Absolute Maximum linkage defined in Eq.
+% \begin{prop} \label{prop:abs_max_cannot_link_property}
+% The \algname{} Algorithm \ref{detailed_alg} with the Absolute Maximum linkage defined in Eq.
 \ref{eq:def_abs_max} returns the same final clustering whether or not cannot-link constraints are enforced.
-\end{prop}
+% \end{prop}
+% \begin{proof}
+% \end{proof}
+
+% \subsubsection{Weight-shift invariance of \algname{} algorithms}
+\invariantAlgs*
 \begin{proof}
-In the \algname{} Algorithm \ref{detailed_alg}, the clustering is updated only when two clusters are merged and the condition at line 9 is satisfied. 
-We also observe that, in the unconstrained version of \algname{}, the predicate \texttt{canBeMerged} at line 9 can never be false because cannot-link constraints are never introduced at line 14.
-Let us now contradict the initial hypothesis and assume by absurd that the constrained version of \algname{} introduces a cannot-link constraints between two clusters sharing a positive interaction $\tilde{w}>0$ and outputs a different clustering as compared to the unconstrained version.
-This can happen only in the situation shown in Fig.
-\ref{fig:abs_max_proof_example}, when two clusters $u$ and $v$ are merged together and share a common neighboring node $t$ having the following two properties: a) $u$ and $t$ are already constrained and share a repulsive interaction $w_{ut}\leq0$, b) $v$ and $t$ share an attractive interaction $w_{vt}>0$ that is higher in absolute value $|w_{vt}|>|w_{ut}|$.
-Then, according to Eq. \ref{eq:def_abs_max}, the new merged cluster $uv$ and $t$ are constrained and share a positive interaction. 
-But this case can never happen, since if $|w_{vt}|>|w_{ut}|$ then clusters $v$ and $t$ are merged before clusters $u$ and $t$ are constrained.  
+Theorem 1 in \cite{chehreghani2020hierarchical} proves that hierarchical clustering with Average (HC-Avg), Single (HC-Single), and Complete linkage (HC-Complete) are weight-shift invariant.
+
+The same is not true for \algname{} with Sum linkage criteria (GAEC and HCC-Sum), because by adding a constant $\alpha$ to all edge weights $w_e$, the interaction between two clusters $S_i$ and $S_j$ is increased by a factor $\alpha |E_{ij}|$, which depends on the number of edges  $|E_{ij}|$ connecting the two clusters.
+Thus, when all edge weighs of the graph are shifted, the agglomeration order may change, as we show in the counter-example of \TODO{FIG}.
+
+The constrained versions of \algname{} (HCC-Avg and HCC-Single) are also not weight-shift invariant: here, the algorithm merges or constrains clusters in a given order, depending on the absolute interactions $|\interact{}(S_i, S_j)|$ between clusters; so, when edge weights are shifted by a constant $\alpha$, the sorting by absolute value can change arbitrarily together with the agglomeration order, as we show in the counter-example of \TODO{FIG}.
+The same reasoning can also be applied to the Mutex Watershed algorithm (\algname{} with AbsMax linkage), which is clearly not weight-shift invariant (see again counter-example in \TODO{FIG}).
 \end{proof}
 
-\subsection{Predicting signed edge weights with a CNN}
-Our CNN model outputs affinities in the form of pseudo-probabilities $p:E \rightarrow [0,1]$, where $p=0$ represents a boundary evidence.
+% \subsubsection{Ultrametrics defined by \algname{}}
+
+\firstUltraMetricProperty*
+\begin{proof}
+% Let us first analyze assumption \ref{eq:UM_assumption}. From $(\Rightarrow)$, we have that:
+% \begin{equation}\label{eq:assumption_side_1}
+% h_T(u \vee v) < h_T(u \vee t) \Rightarrow \interact{}_{T}(u,v) > \interact{}_{T}(u,t). 
+% \end{equation}
+% In words, if the algorithm first merges node $v$ together with node $u$ and later on merges node $t$ with node $u$, then the signed interaction $\interact{}_{T}(u,v)$ between $u$ and $v$ has to be stronger than $\interact{}_{T}(u,t)$.
+On the other hand, the $(\Leftarrow)$ side of Eq.~\ref{eq:UM_assumption} can be rewritten as:
+% \begin{equation}\label{eq:assumption_side_2}
+% h_T(u \vee v) \geq h_T(u \vee t) \Rightarrow \interact{}_{T}(u,v) \leq \interact{}_{T}(u,t).
+% \end{equation}
+% % which in words means: if node $t$ was merged with $u$ at the same or at an earlier iteration  together with node $u$ and later on merges node $t$ with node $u$, then the interaction $\interact{}_{T}(u,v)$
+
+From the definition of $d_{T}$, we have that:
+\begin{align}
+d_{T}(u,u) &= 0 \qquad &\forall u\in V \label{eq:dist_1} \\ 
+d_{T}(u,v) &\geq 0 \qquad &\forall u,v \in V \label{eq:dist_2}\\
+d_{T}(u,v)& =d_{T}(v,u) \qquad &\forall u,v \in V \label{eq:dist_3}
+\end{align}
+ % $d_{T}(u,v)=d_{T}(v,u)$, $d_{T}(u,u)= 0$, and $d_{T}(u,v)\geq 0$ for each $u,v \in V$.
+Thus, to show that $(V, d_{T})$ is an ultrametric, we only need to prove the ultrametric property:
+\begin{equation}\label{eq:UM_property_original}
+d_T(u,v) \leq \max \{d_T(u,t), d_T(v,t)\} \quad \forall u,v,t \in V.
+\end{equation}
+When at least two of the three nodes $u,v,t \in V$ are the same, this property follows from Eq.~\ref{eq:dist_1} and Eq.~\ref{eq:dist_2}.
+When nodes $u,v,t\in V$ are distinct, then Eq.~\ref{eq:UM_property_original} is equivalent to:
+\begin{equation}\label{eq:UM_property}
+\interact{}_{T}(u,v) \geq \min \{\interact{}_{T}(u,t), \interact{}_{T}(v,t)\}.
+\end{equation}
+In the following, we prove both sides of the \emph{if and only if} statement in the proposition.
+First, we prove the $(\Leftarrow)$ side, i.e.
+that if assumption \ref{eq:UM_assumption} holds, then $(V, d_{T})$ is an ultrametric and \ref{eq:UM_property} holds.
+
+Case 1: in Eq.~\ref{eq:UM_property}, $t\in V$ is part of the sub-tree ${T[u \vee v]}$.
+In other words, the algorithm first merges node $t$ with either node $u$ or $v$, and then $u$ and $v$ are merged together.
+Let us assume that $t$ is first merged with $u$ (the following proof also holds for the opposite case in which $t$ is first merged with $v$):
+\begin{equation}
+h_T(u \vee t) < h_T(u \vee v) = h_T(v \vee t).
+\end{equation}
+Thus, from assumption \ref{eq:UM_assumption} we have that
+\begin{equation}
+\interact{}_{T}(u \vee t) \geq \interact{}_{T}(v \vee t) \quad  \wedge \quad \interact{}_{T}(u \vee v) = \interact{}_{T}(v \vee t)
+\end{equation}
+and Eq.~\ref{eq:UM_property} follows (becoming an equality in this case).
+
+Case 2: in Eq.~\ref{eq:UM_property}, $t\in V$ is \emph{not} part of the sub-tree ${T[u \vee v]}$.
+Thus, the algorithm first merges nodes $u$ and $v$, and then it merges node $t$ together with the cluster containing $u$ and $v$:
+\begin{equation}
+h_T(u \vee v) < h_T(u \vee t) = h_T(v \vee t).
+\end{equation}
+Thus, from assumption \ref{eq:UM_assumption} we have that
+\begin{equation}
+\interact{}_{T}(u \vee v) \geq \interact{}_{T}(u \vee t) \quad  \wedge \quad \interact{}_{T}(u \vee v) \geq \interact{}_{T}(v \vee t)
+\end{equation}
+and also in this case Eq.~\ref{eq:UM_property} follows.
+% for every distinct $u,v,t\in V$.
+In other words, given two leaves nodes $u,v\in V$, the depth $\interact{}_{T}(u,v)$ associated to their least common ancestor $i\in T$ should be both lower than the depth of any $i$-descendant node in $T$ and higher than any $i$-ancestor node in $T$:
+%  % that have the most positive interaction   two clusters merged by the algorithm will always have an interaction that is more negative as compared to all clusters already merged and more positive than all clusters that will be merged at later iterations of the algorithm.
+% \begin{equation}
+% \interact{}_{T}(u,v) \geq \interact{}_{T}(u,t) \Leftrightarrow T[u \vee t] \subseteq T[u \vee v] 
+% \end{equation}
+%  This happens only if, at every iteration, Algorithm \ref{main_alg} merges pairs of clusters with lower and lower interactions, which is true for only certain choices of linkage criteria.
+%In the next section \ref{sec:alg_update_rules}, we will show that this happens only for certain linkages and only when constraints are not enforced
+
+Next, we are left to prove the $(\Rightarrow)$ side of the \emph{if and only if} statement: if $(V, d_{T})$ is an ultrametric, then assumption \ref{eq:UM_assumption} holds.
+To prove this statement, we first rephrase it in the following equivalent form: if assumption \ref{eq:UM_assumption} does not hold, then $(V, d_{T})$ is not an ultrametric and \ref{eq:UM_property} does not hold.
+The negation of assumption \ref{eq:UM_assumption} is
+\begin{equation}
+h_T(u \vee v) < h_T(u \vee t) \quad \wedge \quad  \interact{}_{T}(u,v) < \interact{}_{T}(u,t).
+\end{equation}
+The first condition, in words, is again assuming that the algorithm first merges nodes $u$ and $v$, and later it also merges node $t$ with the cluster containing $u$ and $v$.
+Thus, we can rephrase this assumption as:
+\begin{equation}
+\interact{}_{T}(u \vee v) < \interact{}_{T}(u \vee t) = \interact{}_{T}(v \vee t).
+\end{equation}
+From this, it follows that
+\begin{equation}
+\interact{}_{T}(u \vee v) < \min \{\interact{}_{T}(u \vee t), \interact{}_{T}(v \vee t)\},
+\end{equation}
+which is exactly the negation of the ultrametric property \ref{eq:UM_property}.
+\end{proof}
+
+\secondUltraMetricProperty*
+\begin{proof}
+Thanks to Prop.~\ref{prop:ultraMetric1}, we know that $(V, d_{T^*})$ is an ultrametric if and only if assumption \ref{eq:UM_assumption} holds.
+Thus, in the following, we will prove which variations of the \algname{} Algorithm \ref{main_alg} satisfy assumption \ref{eq:UM_assumption}.
+In other words, we need to prove in which cases \algname{} merges clusters according to a monotonously decreasing order of signed interactions $\interact{}$.
+This happens only if both of the following conditions are true:
+\begin{itemize}
+\item Condition 1: Updated interactions involving a merged cluster are always lower or equal than previous interactions:
+\begin{align}\label{eq:condition1}
+& \forall S_i \in \Pi \setminus \{S_1, S_2\}, \nonumber \\
+\interact{}(S_1 \cup S_2, S_i) &\leq \max \{ \interact{}(S_1, S_i), \interact{}(S_2, S_i)\} 
+\end{align}
+where $\Pi$ is a clustering, $\interact{}$ is a linkage criteria, and $S_1,S_2\in \Pi$ are two clusters merged by the algorithm at a given iteration.
+If this condition is true then, in the following iterations, \algname{} can only merge clusters with lower (or equal) interaction values.
+\item Condition 2: Positive and constrained interactions are never skipped in Phase 1 (condition at line 8 of Algorithm \ref{main_alg}) and ``delayed'' to Phase 2.
+If this is the case, then \algname{} is not assured to merge clusters according to a monotonously decreasing order of interactions.
+\end{itemize}
+Condition 1 always holds for Average, Single, Complete, and Absolute Maximum linkage criteria, but not for a Sum linkage criteria, because the sum of two positive numbers $a,b$ is always higher than $\max\{a,b\}$.
+This is also demonstrated in the toy example of Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}, proving that, in general, Sum-linkage algorithms like GAEC or HCC-Sum do not define an ultrametric on the graph.
+
+Thanks to Lemma \ref{lemma:absMax_and_complete_property}, we have that condition 2 always holds for algorithms based on AbsMax and Complete linkage, proving that the Mutex Watershed and HC-Complete algorithms define an ultra-metric (whether or not cannot-link-constraints are enforced).
+On the other hand, condition 2 does not hold for other variations of \algname{} involving cannot-link-constraints (HCC-Sum, HCC-Avg, and HCC-Single), which do not define then an ultrametric.
+
+Finally, the remaining not constrained versions of \algname{} (HC-Avg, HC-Single, and HC-Complete) satisfy both conditions, so they define a ultrametric, confirming the well-known results of related work in hierarchical clustering on positive weighted graphs \cite{johnson1967hierarchical,milligan1979ultrametric}.
+
+% In formulae, this can be formulated as following.
+Assume that at iteration $i$ \algname{} merges clusters $S_i\in \Pi$ and $S_j\Pi$ resulting in a new clustering $\Pi'=\Pi \cup \{S_i\cup S_j\} \setminus \{S_i, S_j\}$
+
+% Initially, all the interactions between clusters are inserted into a priority queue (PQ) and the algorithm starts merging clusters with the highest interaction first.
+However, in the following iterations,
+
+% Since all three phases of \algname{}, the algorithm insert interactions into a priority queue and, at every iteration, picks
+% - GASP merges clusters starting from those with the highest positive interaction W.
+% However, assumption 5 holds only if both of the following conditions are true
+
+% Condition 1: interaction between two merged clusters is never higher than before
+% Condition 2: Positive and constrained interactions are not merged in phase 1 and "delayed" to phase 2 of the algorithm
+
+% \emph{Average, Single, and Complete Linkage} --
+
+% Given a signed graph, we can shift all edge weights by a constant $\alpha$ until they all become positive and, thanks to Prop.~\ref{prop:weight_shift_invariant}, we know that if we run hierarchical clustering (HC) with Avg, Single, or Complete linkage then the structure of the dendrogram (and the agglomeration order) will be the same for both the original signed graph and the weight-shifted positive graph.
+On positive weighted graphs, hierarchical clustering with any of these three linkage criteria is well known to define an ultrametric \cite{johnson1967hierarchical,milligan1979ultrametric}.
+Thus, if assumption \ref{eq:UM_assumption} holds for the weight-shifted positive graph $\mathcal{G}_{\alpha}$, it also has to hold for the original signed graph $\mathcal{G}$, because all interactions between clusters are simply shifted by a constant:
+\end{proof}
+
+% \subsection{Predicting signed edge weights with a CNN}
+% Our CNN model outputs affinities in the form of pseudo-probabilities $p:E \rightarrow [0,1]$, where $p=0$ represents a boundary evidence.
 In order to use them as input of the algorithms in our framework, we mapped them to positive and negative values\footnote{Note that in general attractive and repulsive interactions $w^+$ and $w^-$ can be independently estimated with different classifiers.}.
 The most common approaches use \emph{additive} \cite{ailon2008aggregating} or \emph{logarithmic} \cite{finkel2008enforcing,andres2012globally} mappings:
-\begin{align} 
-\cost_{e,\mathrm{Add}} =&\,\, p_e - \beta, \\
-\cost_{e,\mathrm{Log}} =&\,\, \log \left( \frac{p_e}{1-p_e} \right) - \log \left( \frac{\beta}{1-\beta} \right), \label{eq:mappings}
-\end{align}
-where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation.
+% \begin{align} 
+% \cost_{e,\mathrm{Add}} =&\,\, p_e - \beta, \\
+% \cost_{e,\mathrm{Log}} =&\,\, \log \left( \frac{p_e}{1-p_e} \right) - \log \left( \frac{\beta}{1-\beta} \right), \label{eq:mappings}
+% \end{align}
+% where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation.
 We evaluated both of them empirically with each of the tested linkage and found that the additive mapping is the best option in all cases apart from the \emph{Sum} linkage.
@@
 
-\subsection{Neuron segmentation and compared methods}\label{sec:cremi_details}
-\paragraph{Training details} The data from the CREMI challenge is highly anisotropic and contains artifacts like missing sections, staining precipitations and support film folds. 
+\subsection{Application to neuron segmentation}\label{sec:cremi_details}
+\paragraph{Training and data augmentation} The data from the CREMI challenge is highly anisotropic and contains artifacts like missing sections, staining precipitations and support film folds. 
 To alleviate difficulties stemming from misalignment, we use a version of the data that was elastically realigned by the challenge organizers with the method of \cite{saalfeld2012elastic}.
-We train a 3D U-Net \cite{ronneberger2015u,cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
-as described in \cite{lee2017superhuman}. In addition to the standard data augmentation techniques of random rotations, random flips and  elastic deformations, we simulate data artifacts.
-In more detail, we randomly zero-out slices, decrease the contrast of slices, simulate tears, introduce alignment jitter and paste artifacts extracted from the training data.
+% We train a 3D U-Net \cite{ronneberger2015u,cciccek20163d} using the same architecture as \cite{funke2018large} and predict the same set of long-and-short range affinities described in \cite{lee2017superhuman}.
+In addition to the standard data augmentation techniques of random rotations, random flips and  elastic deformations, we simulate data artifacts.
+We randomly zero-out slices, decrease the contrast of slices, simulate tears, introduce alignment jitter and paste artifacts extracted from the training data.
 Both \cite{funke2018large} and \cite{lee2017superhuman} have shown
@@
 
-\paragraph{THRESH and WSDT} The basic post-processing methods we consider cannot take long-range affinities into account, so we only consider direct neighbors affinities and generate a boundary map by taking an average over the 3 directions.
-Based on this boundary map, we run connected components (THRESH) and we also run a watershed algorithm  seeded at the maxima of the smoothed distance transform (WSDT).
-For WSDT, the degree of smoothing was optimized such that each region receives as few seeds as possible, without however causing severe under-segmentation.
-Due to the anisotropy of the data, we generate 2D WSDT superpixels by considering each 2D image in the stack singularly.
+\paragraph{CREMI-gridRag instances} 
+Our 3D UNet model predicts the same set of 12 long-and-short range affinities described in \cite{lee2017superhuman}. 
+When building the pixel-grid graph, we add both direct neighbors connections and the long-range connections predicted by our model (every voxel is connected to other six voxels via direct connections and other 18 voxels via long-range edges).
+Empirically, when long-range predictions of the CNN are added as long-range connections in the graph, \algname{} achieves better scores as compared to when only direct-neighbors predictions are used.
+% Empirically, we found that adding only 10\% of the long-range connections to the grid-graph (by sampling them at random) gave the best results.
+Our intuitive explanation of this is that, where there is a clear boundary evidence between two segments, the long-range predictions of the CNN model are more certain than the direct-neighbor ones, because it is often impossible to estimate the exact ground-truth label transition for pixels that are very close to a boundary evidence.
+However, empirically, we also find that \algname{} achieves the best scores when only 10\% of the long-range connections are randomly sampled and added to the grid-graph.
+When all the long-range connections predicted by the CNN are added to the graph (18 connections for every voxel), all versions of \algname{} tend to perform more over-clustering errors.
+In practice, we explain this by observing that many challenging parts of the studied neuron segmentation data involve thin and elongated segments, and our model sometimes fails to connect distant pairs of pixels that, according to the ground-truth labels, should belong to the same segment (even though, in this case, the direct neighboring predictions are correct).
+To sum up, the scores we report in Tables \ref{tab:scores_gridGraph} are obtained by using only 10\% of the long-range predictions, since this was the setup that performed the best.
+After running \algname{}, we use a simple post-processing step to delete small segments on the boundaries, most of which are given by single-voxel clusters.
+On the neuron segmentation predictions, we deleted all regions with less than 200 voxels and used a seeded watershed algorithm to expand the bigger segments.
 
-\paragraph{Multi-step pipelines} Given the 2D WSDT superpixels, we build a 3D region-adjacency graph such that each node represents a superpixel.
+\paragraph{CREMI-3D-rag instances} 
+We build these clustering problems by generating superpixels and then building a 3D region adjacency graph.
+Due to the anisotropy of the data, we generate 2D superpixels by considering each 2D image in the stack singularly.
+First, we generate a boundary-evidence map by taking an average over the two direct-neighbor predictions of the CNN model (one for each direction in the 2D image of the stack) and applying some additional smoothing.
+Then, we threshold the boundary map, compute a distance transform, and run a watershed algorithm seeded at the maxima of the distance transform (WSDT).
+The degree of smoothing was optimized such that each region receives as few seeds as possible, without however causing severe under-segmentation.
+The computed 2D superpixels are then used to build a 3D region-adjacency graph (3D-rag). The weights of the edges are given by averaging the CNN affinities over the boundaries of adjacent superpixels.
+
+% \paragraph{Lifted Multicut pipeline}
+% Similarly to what explained in the previous paragraph, we compute 2D superpixels using the WSDT procedure and build a 3D region-adjacency graph.
 The weights of the edges connecting neighboring superpixels are computed by taking an average over both short- and long-range affinities connecting the two regions.
-We then convert the edge probabilities to signed weights using the logarithmic mapping defined in Eq.
+% We then convert the edge probabilities to signed weights using the logarithmic mapping defined in Eq.
 \ref{eq:mappings} and solve the multicut problem on this graph.
@@
 Thus, in these cases we introduce additional \emph{lifted} edges in the graph and an instance of the lifted multicut problem (WSDT+LMC).
-This time, similarly to the methods mentioned in \cite{beier2016efficient}, we used a combination of approximate solvers consisting in GAEC and Kernighan-Lin.
+This time, similarly to the methods mentioned in \cite{beier2016efficient}, we used a combination of approximate solvers consisting of GAEC and Kernighan-Lin.
 
-\subsection{\algname{} on the full CREMI dataset} \label{sec:appendix_exps_full_cremi}
- \paragraph{Pre-merge processing} For the predictions on the full dataset from the CREMI challenge, we used  the padded volumes provided by the challenge.
+% \subsection{\algname{} on the full CREMI dataset} \label{sec:appendix_exps_full_cremi}
+ % \paragraph{Pre-merge processing} For the predictions on the full dataset from the CREMI challenge, we used  the padded volumes provided by the challenge.
 The crops on which we performed a prediction have a size of $1500\times1500\times127=2.86\cdot 10^8$ voxels or larger.
@@
 With this approach, pixels are pre-clustered only when they are far away (in all directions) from predicted boundaries.
- To make sure that in this preprocessing step different neurons are never merged together by mistake, we intersected the segments given by THRESH with the segments given by WSDT. 
- We tested \algname{} both on the full grid-graph and on this preprocessed graph and we did not notice any major differences in the final clustering or achieved scores, although the version with a pre-processed graph was significantly faster.
+ % To make sure that in this preprocessing step different neurons are never merged together by mistake, we intersected the segments given by THRESH with the segments given by WSDT. 
+ % We tested \algname{} both on the full grid-graph and on this preprocessed graph and we did not notice any major differences in the final clustering or achieved scores, although the version with a pre-processed graph was significantly faster.
 To reduce the runtime and memory requirements even further, we used only 10 \% of the long-range connections in the pixel-graph, since adding all of them did not improve the scores.
 
- \paragraph{Removing small segments} After running \algname{}, we use a simple post-processing step to delete small segments on the boundaries, most of which are given by single-voxel clusters.
-On the neuron segmentation predictions, we deleted all regions with less than 200 voxels and used a seeded watershed algorithm to expand the bigger segments.
-
- \paragraph{Enforcing local merge} In 2D images of urban-scenes, due to partial occlusion, one object instance can be given by multiple components that are not directly connected in the image plane.
+ % \paragraph{Enforcing local merge} In 2D images of urban-scenes, due to partial occlusion, one object instance can be given by multiple components that are not directly connected in the image plane.
 This is not the case in neuron-segmentation, where each neuron should be given by a single 3D connected component in the volume.
@@
 This then avoids the introduction of ``air-bridges'' between segments due to attractive long-range connections in the initial voxel grid-graph.
- This approach achieved superior performances to the one proposed in \cite{wolf2018mutex}, where all long-range connections in the grid-graph are associated to a negative repulsive edge weight.
+ % This approach achieved superior performances to the one proposed in \cite{wolf2018mutex}, where all long-range connections in the grid-graph are associated to a negative repulsive edge weight.
+
+% \begin{table*}[t]
+% \centering
+%     \scriptsize
+%         \begin{tabular}{l|c|c|c|c|c}
+%           \algname{} linkage & \makecell{CREMI-Score\\(lower better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
+% Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 0.494 & 3.49 $\cdot$ 10$^4$ \\
+% Sum + CLC \cite{levinkov2017comparative} & 0.282 & 0.906 & 0.358 & 0.510 & 4.64 $\cdot$ 10$^4$ \\
+% Abs Max \cite{wolf2018mutex} & 0.322 & 0.897 & 0.286 & 0.735 & 1.24 $\cdot$ 10$^4$ \\
+% Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 6.31 $\cdot$ 10$^4$ \\
+% Sum \cite{keuper2015efficient} & 0.334 & 0.872 & 0.461 & 0.444 & 4.74 $\cdot$ 10$^4$ \\
+% Average + CLC & 0.563 & 0.772 & 0.259  & 1.142 & 2.95 $\cdot$ 10$^4$ \\
+% Min & 2.522 & 0.030 & \textbf{0.197} & 6.365 & 2.97 $\cdot$ 10$^3$ \\
+% Min + CLC & 2.522 & 0.030 & \textbf{0.197}  & 6.365 & 4.77 $\cdot$ 10$^3$ \\
+% Max & 2.626 & 0.028 & 7.069 & \textbf{0.026} & \textbf{6.04 $\cdot$ 10$^\mathbf{2}$} \\
+%         \end{tabular}
+%         \vspace*{1.1em}
+%     \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set. 
+%     CREMI-Score \cite{cremiChallenge}, is given by a combination of the Adapted Rand-Score (Rand-Score) and the Variation of Information Score for under-clustering (VI-merge) and over-clustering (VI-split) \cite{arganda2015crowdsourcing}.
+%     CLC stands for cannot-link constraints. For all algorithms, the chosen value of bias parameter was $\beta = 0.5$. }
+%     \label{tab:extended_results_cremi}
+% \end{table*}
 
@@
     \scriptsize
-        \begin{tabular}{l|c|c|c|c|c}
-          \algname{} linkage & \makecell{CREMI-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
-Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 0.494 & 3.49 $\cdot$ 10$^4$ \\
-Sum + CLC \cite{levinkov2017comparative} & 0.282 & 0.906 & 0.358 & 0.510 & 4.64 $\cdot$ 10$^4$ \\
-Abs Max \cite{wolf2018mutex} & 0.322 & 0.897 & 0.286 & 0.735 & 1.24 $\cdot$ 10$^4$ \\
-Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 6.31 $\cdot$ 10$^4$ \\
-Sum \cite{keuper2015efficient} & 0.334 & 0.872 & 0.461 & 0.444 & 4.74 $\cdot$ 10$^4$ \\
-Average + CLC & 0.563 & 0.772 & 0.259  & 1.142 & 2.95 $\cdot$ 10$^4$ \\
-Min & 2.522 & 0.030 & \textbf{0.197} & 6.365 & 2.97 $\cdot$ 10$^3$ \\
-Min + CLC & 2.522 & 0.030 & \textbf{0.197}  & 6.365 & 4.77 $\cdot$ 10$^3$ \\
-Max & 2.626 & 0.028 & 7.069 & \textbf{0.026} & \textbf{6.04 $\cdot$ 10$^\mathbf{2}$} \\
+    % \tiny
+    \begin{subtable}[t!]{\textwidth}
+    \centering
+
+        \begin{tabular}{l | r r r r r r r r r}
+        % \toprule
+         %\multicolumn{1}{c}{}
+        % &\multicolumn{5}{c}{Multicut objective values associated to final clusterings (lower is better)} \\
+        Clustering problem & \multicolumn{1}{r}{GAEC \cite{keuper2015efficient}} & HCC-Sum & MWS \cite{wolf2018mutex} & HC-Avg & HCC-Avg & HC-Single & HCC-Single & HC-Complete \\ \midrule
+        \emph{Modularity Clustering} & 
+        -0.457 & -0.453 & -0.073 & \textbf{-0.467} & \textbf{-0.467} & 0.000 & 0.000 & -0.201 \\ 
+        \emph{Image Segmentation}  & 
+        \textbf{-2,955} & -2,953 & -2,901 & -2,903 & -2,896 & -1,384 & -1,384 & -2,102 \\
+        \emph{Knott-3D (150-300-450)}  & 
+        \textbf{-36,667} & -36,652 & -35,200 & -35,957 & -35,631 & -2,522 & -2,522 & 30,629 \\
+        % \emph{Knott-3D-300} & \emph{3D-rag} & 8& & & \HollowBox\\
+        % \emph{Knott-3D-450}& \emph{3D-rag} & 8 & & & \HollowBox\\  
+        \emph{CREMI-3D-rag}  
+        & \textbf{-1,112,287} & -1,112,286& -1,109,731 & -1,112,177 & -1,112,100 & -1,038,709 & -1,038,709 & -748,734,869 \\ 
+        \emph{Fruit-Fly Level 1-4}
+        & \textbf{-151,022} & -151,017 & -150,879 & -150,909 & -150,876 & -71,477 & -71,997 & -128,733 \\
+        \emph{CREMI-gridGraph} 
+        & -73,317,601 & -73,328,867 & -73,330,568 & \textbf{-73,502,947} & -73,474,856 & -45,194,180 &-45,194,443 & 311,598,700 \\
+        \emph{Fruit-Fly Level Global} 
+        & \textbf{-151,688} & -151,596 & -146,315 & -150,466 & -150,171 & -4,422 & - & 6,876 \\
+        % \emph{(CREMI-pixGrid-LSIMasksUNet)} & \emph{gridGraph} & 1 & & 4 & \CrossedBox\\
+        % \emph{(CityScapesValidation-pixGrid)} & \emph{gridGraph} &  &  & & \CrossedBox\\
+        % \emph{CREMI-test....}\\\midrule
+        % \emph{Stochastic Block Model (synthetic)} & \emph{non-planar} &-&- & - & \CrossedBox \\
+        % \emph{(epinions and slashdot?)} & \emph{dense?} &  & & & \HollowBox\\
+
+% fruitfly-large & -151687.891 & -151596.344 & -146315.031 & -150466.000 & -150171.203 & -4422.442 & - & 6875.726 & 6879.776 \\
+% modularity-clustering & -0.457 & -0.453 & -0.073 & -0.467 & -0.467 & 0.000 & 0.000 & -0.201 & -0.201 \\
+% knott & -36667 & -36652 & -35200 & -35957 & -35631 & -2522 & -2522 & 30629 & 30599 \\
+% fruitfly-medium & -151022 & -151017 & -150879 & -150909 & -150876 & -71477 & -71997 & -128733 & -128732 \\
+% image-seg & -2955 & -2953 & -2901 & -2903 & -2896 & -1384 & -1384 & -2102 & -2102 \\
+
+% % Superpixels:
+% Mutex & -1109731264 \\
+% MEANconstr & -1112099691 \\
+% MEAN & -1112176981 \\
+% SUMconstrNoLogs & -1112286144 \\
+% SUMnoLogs & -1112286741 \\
+% MAX & -1038708864 \\
+% MAXconstr & -1038708864 \\
+% MIN & -748734869 \\
+% MINconstr & -748766347 \\
+
+% % Pixels:
+% SUM & -73317601 \\
+% SUMconstr & -73328867 \\
+% MutexPixGrid & -73330568 \\
+% MEANconstr & -73474856 \\
+% MEAN & -73502947 \\
+% MAX & -45194180 \\
+% MAXconstr & -45194443 \\
+% MIN & 311598700 \\
+% MINconstr & 311520538 \\
+
         \end{tabular}
-        \vspace*{1.1em}
-    \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set. 
-    CREMI-Score \cite{cremiChallenge}, is given by a combination of the Adapted Rand-Score (Rand-Score) and the Variation of Information Score for under-clustering (VI-merge) and over-clustering (VI-split) \cite{arganda2015crowdsourcing}.
-    CLC stands for cannot-link constraints.
-For all algorithms, the chosen value of bias parameter was $\beta = 0$.
-We used a machine with CPU Intel(R) Xeon(R) E7-4870 @ 2.40GHz for our comparison experiments.}
-    \label{tab:extended_results_cremi}
+    \end{subtable} 
+    \caption{We compare algorithms in the \algname{} framework by evaluating which of the obtained clusterings is associated to the lowest value of the multicut objective defined in Eq.~\ref{eq:MC_objective} (lower is better).
+Single and complete linkage methods performed much worse than the others.
+Note that HCC-Single is the algorithm with the highest runtime (see Table \ref{tab:scores_gridGraph}) and it did not scale up to the very large clustering problem \emph{Fruit-Fly Level Global}.
+% We used a machine with CPU Intel(R) Xeon(R) E7-4870 @ 2.40GHz for our comparison experiments.
+    } 
+    \label{tab:all_multicut_energies}
 \end{table*}
 
-\subsection{\algname{} sensitivity to noise: adding artifacts to CNN predictions} \label{sec:appendix_noise_gen}
-Additionally to the comparison on the full training dataset, we performed more experiments on a crop of the more challenging CREMI training sample B, where we perturbed the predictions of the CNN with noise and we introduced additional artifacts like missing or fictitious boundary evidences.
+\subsection{Adding structured noise to CNN predictions} \label{sec:appendix_noise_gen}
+Additionally to the comparison on the full training dataset, we performed more experiments on a crop of the more challenging CREMI training sample B, where we perturbed the predictions of the CNN with noise and we introduced additional artifacts like missing boundary evidences.
 
@@
 This type of noise $n(x)\in[0,1]$ generates spatial random patterns that are locally smooth but have large and diverse variations on bigger scales.
-We then combined it with the CNN predictions $p(x)$ in the two following ways:
+We then combined it with the CNN predictions $p(x)$ in the following way:
 \begin{equation}\label{eq:noise_biased_predictions}
-\tilde{F}_{\pm}(x;\mathcal{K})=F(x)\pm\big|\mathcal{K}\cdot\max\left(\pm N(x),0\right)\big|,
+\tilde{F}(x;\mathcal{K})=F(x)+\mathcal{K}\cdot\max\left(N(x),0\right),
 \end{equation}
 where  $N(x)=\mathrm{Logit}[n(x)]$; $F(x)=\mathrm{Logit}[p(x)]$ and $\mathcal{K}\in \mathbb{R}^+$ is a positive factor representing the amount of added noise.
-$\tilde{F}_{+}(x;\mathcal{K})$ represents then a under-clustering biased prediction, such that the probability for two pixels to be in the same cluster is increased only if $N(x)>0$ (see Fig.
-\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b}), whereas $\tilde{F}_{-}(x;\mathcal{K})$ is a over-clustering biased prediction with decreased probabilities when $N(x)<0$ (Fig.
-\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}).
-In the implementation we used, the noise can be generated in an arbitrary number of dimensions and a smoothing factor can be specified for each direction independently.
+The resulting perturbed predictions $\tilde{F}(x;\mathcal{K})$ are then under-clustering biased, such that the probability for two pixels to be in the same cluster is increased only if $N(x)>0$ (see Fig.~\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b} and \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}).
+% whereas $\tilde{F}_{-}(x;\mathcal{K})$ is a over-clustering biased prediction with decreased probabilities when $N(x)<0$ (Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}).
+Note that in these experiments we focused only on predictions perturbed with under-clustering biased noise (and not over-clustering biased noise).
+The reason is that generating realistic over-clustering biased CNN predictions is more complex and cannot be simply done by adding Perlin noise: as we show in Fig.~\hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}, by adding Perlin noise we can easily ``remove'' parts of a boundary evidence, but it is not possible to generate random new realistic boundary evidence.
+% In the implementation we used, the noise can be generated in an arbitrary number of dimensions and a smoothing factor can be specified for each direction independently.
+
 In our experiments, each pixel is represented by a node in the grid-graph and it is linked to $n_{\mathrm{nb}}$ other nodes by short- and long-range edges.
-Thus, the output of our CNN model has $n_{\mathrm{nb}}$ channels: for each pixel / voxel, it outputs $n_{\mathrm{nb}}$ values representing the weights of different edge connections.
-We then generated a 4-dimensional noise that matches the dimension of the CNN output.
+Thus, the output volume of our CNN model is a four-dimensional tensor with $n_{\mathrm{nb}}$ channels: for each pixel / voxel, the model outputs $n_{\mathrm{nb}}$ values representing affinities of different edge connections.
+We then generated a 4-dimensional Perlin noise tensor that matches the dimension of the CNN output.
 The data is highly anisotropic, i.e.
@@
 Due to this fact, we chose different smoothing parameters to generate the noise in different directions.
-\TODO{Give these smoothing parameters...}
+% \TODO{Give these smoothing parameters...}
 
-The experiments summarized in Fig.
-\ref{fig:noise_plots} were performed in the following way: for each value $\mathcal{K}$, 30 random noise samples were drawn, from which median and percentiles statistics were computed for each different linkage criteria.
-For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
+% The experiments summarized in Fig.
+\ref{fig:scores_structured_noise} were performed in the following way: for each value $\mathcal{K}$, 20 random noise samples were drawn, from which median and percentiles statistics were computed for each different linkage criteria.
+% For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
 \begin{figure*}[t]
 \centering
-        \includegraphics[width=\textwidth,trim=0.0in -0.in -0.0in -0.4in,clip]{figs/noisy_affs_comparison.pdf}
-    \caption{CNN predictions on a slice of the CREMI neuron segmentation challenge with and without additional noise.
-(\textbf{a}) Raw data (\textbf{b}) Original CNN predictions $F(x)$, where blue pixels represent boundary evidence (\textbf{c}) Under-clustering biased version $\tilde{F}_{+}(x;\mathcal{K})$ of the predictions defined in Eq.
-\ref{eq:noise_biased_predictions} with $\mathcal{K}=8$ (\textbf{d}) Over-clustering biased version $\tilde{F}_{-}(x;\mathcal{K})$.
+        \includegraphics[width=\textwidth,trim=0.0in -0.in -0.0in -0.4in,clip]{figs/noisy_affs_comparison_v2.pdf}
+    \caption{CNN predictions on a slice of the CREMI neuron segmentation challenge with and without additional spatially-correlated noise.
+(\textbf{a}) Raw data (\textbf{b}) Original CNN predictions $F(x)$, where blue pixels represent boundary evidence (\textbf{c}) Strongly perturbed version $\tilde{F}(x;\mathcal{K})$ of the predictions defined in Eq.
+\ref{eq:noise_biased_predictions} with $\mathcal{K}=8$.
 Long-range predictions are not shown.
@@
 \end{figure*}
-\begin{table}
-    \centering
-    % \small
-    \vspace*{0.6em}
-        \begin{tabular}{l M{7em} M{7em}}
-          \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
-          Average & 34.3 & 0.35 \\
-          Average + CLC & 33.9 & 0.25\\
-          Max + CLC & 32.5 & 0.50 \\
-          Abs Max & 32.1 & 0.45\\
-          Sum + CLC & 31.9 & 0.55 \\
-          Sum & 31.3 & 0.55 \\
-          Max & 24.3 & 0.85 \\
-          Min & 0.00 & 0.50 \\
-          Min + CLC & 0.00 & 0.50 \\
-        \end{tabular}
-    \vspace*{2em}
-    \caption{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set.
+% \begin{table}
+%     \centering
+%     % \small
+%     \vspace*{0.6em}
+%         \begin{tabular}{l M{7em} M{7em}}
+%           \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
+%           Average & 34.3 & 0.35 \\
+%           Average + CLC & 33.9 & 0.25\\
+%           Max + CLC & 32.5 & 0.50 \\
+%           Abs Max & 32.1 & 0.45\\
+%           Sum + CLC & 31.9 & 0.55 \\
+%           Sum & 31.3 & 0.55 \\
+%           Max & 24.3 & 0.85 \\
+%           Min & 0.00 & 0.50 \\
+%           Min + CLC & 0.00 & 0.50 \\
+%         \end{tabular}
+%     \vspace*{2em}
+%     \caption{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set.
 A bias value $\beta=0$ returns one single cluster.
 CLC stands for cannot-link constraints.}
-    \label{tab:extended_results_cityscapes_val}
-\end{table}
+%     \label{tab:extended_results_cityscapes_val}
+% \end{table}
 
-\subsection{Fine-tuning the GMIS pipeline on CityScapes} \label{sec:appendix_cityscapes}
-For our experiments, we used the model from GMIS \cite{liu2018affinity} that is publicly available. 
-The model consists of two neural networks with similar structures, one predicting pixel level semantic scores and the other predicting pixel affinities between instances.
+% \subsection{Fine-tuning the GMIS pipeline on CityScapes} \label{sec:appendix_cityscapes}
+% For our experiments, we used the model from GMIS \cite{liu2018affinity} that is publicly available. 
+% The model consists of two neural networks with similar structures, one predicting pixel level semantic scores and the other predicting pixel affinities between instances.
 We also used all the affinity post-processing methods proposed in \cite{liu2018affinity}, e.g.
 excluding background, resizing regions of interest or the proposed "affinity-refinement" method, which combines semantic and instance outputs.
-The instance-branch of the model was trained with a Binary Cross-Entropy loss, but we noticed how the short-range affinities were biased towards high probabilities, so that a strong short-range boundary evidence was never predicted by the model.
+% The instance-branch of the model was trained with a Binary Cross-Entropy loss, but we noticed how the short-range affinities were biased towards high probabilities, so that a strong short-range boundary evidence was never predicted by the model.
 In \cite{liu2018affinity}, they handle this problem by proposing a modified version of HAC that is done in stages (MultiStepHAC): initially only short-range affinities are used to run HAC and a low threshold in the hierarchy is chosen to define a first clustering; then a new HAC problem including long-range affinities is  initialized with the first clustering; in the method proposed by \cite{liu2018affinity}, these steps are repeated three times.
 
-Since MultiStepHAC is a rather complex post-processing method that requires to tune several hyper-parameters, we opted for a different approach to solve the problem of the unbalanced affinities.
+% Since MultiStepHAC is a rather complex post-processing method that requires to tune several hyper-parameters, we opted for a different approach to solve the problem of the unbalanced affinities.
 We added two 1x1 convolutional layers to the instance-branch model and trained them by using the same loss used by \cite{wolf2018mutex} and is based on the S\o resen-Dice coefficient \cite{dice1945measures,sorensen1948method}.
 Compared to Hamming-distance based loss like Binary Cross-Entropy or Mean Squared Error, the advantage of this loss is its being robust against prediction and / or target sparsity, that is a desirable quality in this application since boundaries between instances can be sparse.
-During training, all the affinities involving at least one pixel belonging to the background were ignored in the loss.
+% During training, all the affinities involving at least one pixel belonging to the background were ignored in the loss.
 In this way, these last two layers specialized in improving the predictions of boundary evidence between adjacent instances (especially those belonging to the same class).
@@
 
-Before to apply \algname{}, we performed a parameter-search for the bias $\beta$ defined in \ref{eq:mappings}.
+% Before to apply \algname{}, we performed a parameter-search for the bias $\beta$ defined in \ref{eq:mappings}.
 Table \ref{tab:extended_results_cityscapes_val} lists the best-case performances for each of the methods: note that depending on the \algname{} linkage criterion, it was necessary to bias more or less the predicted edge weights.
 
-The semantic categories are assigned to each instance in the same way proposed by \cite{liu2018affinity}, i.e. with a majority vote based on the semantic output of the model.
+% The semantic categories are assigned to each instance in the same way proposed by \cite{liu2018affinity}, i.e. with a majority vote based on the semantic output of the model.
 
-\subsection{Ultrametrics} 
-Thus, to prove that $(V, d_{T})$ is an ultrametric, we only need to prove that
+\begin{table*}[t]
+\centering
+% \begin{minipage}[t]{0.48\textwidth}
+% \vspace{0pt}
+% \centering
+% \footnotesize
+\begin{tabular}[t]{l c}
+           Method & ARAND Error \\ \midrule
+           \textbf{HC-Avg} (GASP with Avg Linkage) & \textbf{0.1034} \\
+GAEC \cite{keuper2015efficient} (GASP with Sum Linkage) & 0.1035 \\
+MWS \cite{wolf2018mutex} (GASP with AbsMax linkage) & 0.1068 \\
+SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG} & 0.4161\\
+$L_{sym}$ \cite{kunegis2010spectral} & 0.8069 \\
+SPONGE \cite{Cucuringu2019SPONGEAG} & 0.9211 \\
+BNC \cite{chiang2012scalable} & 0.9926 \\
+        \end{tabular}
+    \caption{\algname{} compared to spectral clustering methods on a small crop of the CREMI neuron segmentation dataset. 
+    Since spectral methods cannot scale to the full CREMI dataset, we evaluated them on a smaller $10\times100\times100$ sub-volume of CREMI training sample B.
+    Despite the fact that the true number of ground truth clusters was given as an input to the spectral methods, GASP significantly outperformed them. 
+    % SC methods seem to have more difficulties when the graph is sparse. 
+    % Spectral methods did not handle well pixels on the boundaries between segments and tended to cluster them together. 
+    % We also tried to vary the input number of clusters ncreasing $k$ did not improve their scores either.
+% resulting in a graph with $10^5$ nodes and~$\sim10^6$ edges.
+    }
+    \label{tab:cremi_spectral_experiments}
+% \end{minipage}
+% \begin{minipage}[t]{0.38\textwidth}
+% \vspace{0pt}
+% \centering
+%         \includegraphics[width=1.\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf} % 0.45
+%         \caption{\algname{} performances compared to spectral methods on synthetic graphs.
+The spectral methods were given the true number of clusters as input, in contrast to \algname{}.
+\TODO{Define paramters SSB; explain percentile stuff (for both noise experiments, save space!)}}
+%     \label{fig:SSBM_scores}
+% \end{minipage}
+\end{table*}
+
+% \subsection{Comparison with spectral clustering} \label{sec:spectral_clust}
+% In this section we compare \algname{} to spectral clustering (SC) methods on signed graphs from neuron segmentation.
+These methods require the user to specify the number of clusters in advance, in contrast to our proposed agglomeration method that determines the cluster number based on the signed weights of the graph.
+In the following comparison, we make these baselines as strong as possible by specifying the true number of clusters for the spectral methods.
+% % \textbf{Synthetic graphs} -- First, we compare the clustering performance on synthetic graphs generated by a signed stochastic block model (SSBM), where SC performs well.
+In particular, we used an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N=10^5$ vertices and edge probability $p=0.1$.
+Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k=100$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) had Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $0.1$.
+To model noise, we flipped the sign of each edge independently with probability $\eta \in [0, 0.4]$.
+Median scores, 25th and 75th percentiles over 30 repetitions are shown in Fig.~\ref{fig:SSBM_spectral_experiments}: GASP achieved scores comparable to SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG}, a recently proposed SC method.
+The specific design choice of a \emph{sign flipping} noise used in the SSBM experiments turned out to favor GASP with \emph{Sum} linkage that, according to the experiments presented in Sec.~\ref{sec:results}, is the one with the lowest tendency to over-cluster and grows one cluster at the time.
+% We extended the comparison with spectral methods to the task of neuron segmentation.
+Since SC cannot scale to the full CREMI dataset \TODO{}, we evaluated \algname{} and SC on a smaller $10\times100\times100$ voxels volume resulting in a graph with $10^5$ nodes and~$\sim10^6$ edges.
+Scores are summarized in Table \ref{tab:cremi_spectral_experiments}.
+% %suggested by the reviewer that performed best in the recent comparison \cite{Cucuringu2019SPONGEAG}: one based on the Balanced Normalized Cut (BNC) \cite{chiang2012scalable}; another on the symmetrically normalized Signed Laplacian ($L_{sym}$) \cite{kunegis2010spectral}; SPONGE and SPONGE$_{sym}$ algorithms were recently proposed in \cite{Cucuringu2019SPONGEAG}.
+% Despite the fact that the true number of ground truth clusters was given as an input to the SC methods, GASP significantly outperformed them on neuro-data.
+SC methods seem to have more difficulties when the graph is sparse.
+Moreover, they did not handle well pixels on the boundaries between segments and tended to cluster them together.
+Increasing $k$ did not improve their scores either.
+
+\subsection{MWS on SSBM graphs}
+
+\begin{prop}\label{prop:MWS_SSBM_1}
+Consider a graph $\mathcal{G}(V,E)$ generated with a SSBM with parameters $N,p,k,\sigma$ and an associated ground truth (GT) clustering $\hat{\Pi}=\{\hat{S}_1, \ldots, \hat{S}_k\}$.
+Then, assume that after some merging-iterations of the MWS algorithm the clustering $\Pi$ is found.
+Then, any two clusters $S_i,S_j\in \Pi$ have probability $|E_{ij}| / |E_{\Pi}^1|$ to be selected in the next iteration of the algorithm, where $E_{\Pi}^1$ is the multicut associated to $\Pi$ and $E_{ij}\equiv(S_i\times S_j)\cap E$ is the set of edges connecting the two clusters.
+\end{prop}
+
+\begin{prop}\label{prop:MWS_SSBM_2}
+Given the assumptions of Prop.~\ref{prop:MWS_SSBM_1}, let $E_{ij}^+=\{(u,v) \in E_{ij} | \exists \hat{S}\in \hat{\Pi} \, \mathrm{s.t.} \, u\in \hat{S} \wedge v\in \hat{S} \}$ denote the set of true attractive GT edges connecting two clusters $S_i,S_j$
 \begin{equation}
-\interact{}_{T}(u,v) \geq \min \{\interact{}_{T}(u,t), \interact{}_{T}(v,t)\}
+\sum_{ij} \frac{|E_ij^+|}{||}
 \end{equation}
- for every distinct $u,v,t\in V$.
-In other words, given two leaves nodes $u,v\in V$, the depth $\interact{}_{T}(u,v)$ associated to their least common ancestor $i\in T$ should be both lower than the depth of any $i$-descendant node in $T$ and higher than any $i$-ancestor node in $T$:
- % that have the most positive interaction   two clusters merged by the algorithm will always have an interaction that is more negative as compared to all clusters already merged and more positive than all clusters that will be merged at later iterations of the algorithm.
-\begin{equation}
-\interact{}_{T}(u,v) \geq \interact{}_{T}(u,t) \Leftrightarrow T[u \vee t] \subseteq T[u \vee v] 
-\end{equation}
- This happens only if, at every iteration, Algorithm \ref{main_alg} merges pairs of clusters with lower and lower interactions, which is true for only certain choices of linkage criteria.
-%In the next section \ref{sec:alg_update_rules}, we will show that this happens only for certain linkages and only when constraints are not enforced
+\end{prop}
+
+Then, the MWS algorithm will assign highest priority to 
+Among these edges, we define the set of true attractive GT edges as . Finally, let $f^+=|E_{ij}^+| / |E_{ij}|$ denote the fraction of true attractive edges. Then, the Mutex Watershed algorithm
+
+\begin{itemize}
+\item each pair of clusters $S_i,S_j$ has probability $|E_{ij}| / |E_{\Pi}^1|$ to have the interaction with highest priority 
+\item if the pair of clusters $S_i,S_j$ is given the highest priority by the MWS Algorithm, then they have has a probability $p^+=f^+(1-\eta) + f^+ \eta$ to be merged and $p^-=1-p^+$ to be constrained.
+\end{itemize}
+will assign a positive interaction to clusters $S_i,S_j$ with probability $f^+(1-\eta) + f^+ \eta$. 
+Remarks: this quantity does not depend on the size of $|E_{ij}|$ (so it won't change when clusters grow in size); if $f^+=1$ (i.e.
+$S_i,S_j$ are subclusters of the same GT cluster), then MWS will merge them with probability $1-\eta$; if $f^+=0$ (i.e.
+$S_i,S_j$ are subclusters of two different GT clusters), then MWS will merge them with probability $\eta$.
+\TODO{Assumption about $\sigma$?}

### 2021-03-10 chapters/3_algorithm.tex
Add image, small changes

@@
 On signed graphs, the sum of two attractive (or repulsive) interactions is still attractive (repulsive).
-On the other hand, on positive weighted graphs, a strong attractive interaction could be obtained by summing many weak interactions, which is often not desirable.
+On the other hand, on positive weighted graphs, a strong attractive interaction could be obtained by summing many weak interactions, which is often not desirable \TODO{Update}.
 This explains why, to our knowledge, an agglomerative algorithm with sum linkage has never been used on positive weighted graphs.

### 2021-03-10 chapters/5_experiments_intro.tex
Add image, small changes

@@
 \textbf{Scores on CREMI instance-segmentation} -- 
-SSBM graphs are \emph{non-planar} graphs, where every edge has the same probability to be present.
+SSBM graphs are \emph{non-planar}, where every edge has the same probability to be present in the graph.
 On the other hand, the \emph{gridGraph} and \emph{3D-rag} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: weather a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance).
@@
 Sum-based linkage methods (\emph{GAEC}, \emph{HCC-Sum}) do not perform well on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}).
-This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods does not work well on grid-graphs, because of the sparse local edge connections with strongly spatially-correlated noise (given that edge weights are predicted by a CNN)\footnote{This effect is not as strong on \emph{3D-rag} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
+This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods performs poorly on grid-graphs, because in this setup edge weights are predicted by a CNN and noise is strongly spatially-correlated \footnote{This effect is not as strong on \emph{3D-rag} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
 To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}.

### 2021-03-10 chapters/supplementary.tex
Minor update supplementary

@@
 
+\subsection{Mutex Watershed on SSBM graphs}
+\TODO{}
+
+% \begin{prop}\label{prop:MWS_SSBM_1}
+% Consider a graph $\mathcal{G}(V,E)$ generated with a SSBM with parameters $N,p,k,\sigma$ and an associated ground truth (GT) clustering $\hat{\Pi}=\{\hat{S}_1, \ldots, \hat{S}_k\}$.
+Then, assume that after some merging-iterations of the MWS algorithm the clustering $\Pi$ is found.
+Then, any two clusters $S_i,S_j\in \Pi$ have probability $|E_{ij}| / |E_{\Pi}^1|$ to be selected in the next iteration of the algorithm, where $E_{\Pi}^1$ is the multicut associated to $\Pi$ and $E_{ij}\equiv(S_i\times S_j)\cap E$ is the set of edges connecting the two clusters.
+% \end{prop}
+
+% \begin{prop}\label{prop:MWS_SSBM_2}
+% Given the assumptions of Prop.~\ref{prop:MWS_SSBM_1}, let $E_{ij}^+=\{(u,v) \in E_{ij} | \exists \hat{S}\in \hat{\Pi} \, \mathrm{s.t.} \, u\in \hat{S} \wedge v\in \hat{S} \}$ denote the set of true attractive GT edges connecting two clusters $S_i,S_j$
+% \begin{equation}
+% \sum_{ij} \frac{|E_ij^+|}{||}
+% \end{equation}
+% \end{prop}
+
+% Then, the MWS algorithm will assign highest priority to 
+% Among these edges, we define the set of true attractive GT edges as . Finally, let $f^+=|E_{ij}^+| / |E_{ij}|$ denote the fraction of true attractive edges. Then, the Mutex Watershed algorithm
+
+% \begin{itemize}
+% \item each pair of clusters $S_i,S_j$ has probability $|E_{ij}| / |E_{\Pi}^1|$ to have the interaction with highest priority 
+% \item if the pair of clusters $S_i,S_j$ is given the highest priority by the MWS Algorithm, then they have has a probability $p^+=f^+(1-\eta) + f^+ \eta$ to be merged and $p^-=1-p^+$ to be constrained.
+% \end{itemize}
+% will assign a positive interaction to clusters $S_i,S_j$ with probability $f^+(1-\eta) + f^+ \eta$. 
+% Remarks: this quantity does not depend on the size of $|E_{ij}|$ (so it won't change when clusters grow in size); if $f^+=1$ (i.e.
+$S_i,S_j$ are subclusters of the same GT cluster), then MWS will merge them with probability $1-\eta$; if $f^+=0$ (i.e.
+$S_i,S_j$ are subclusters of two different GT clusters), then MWS will merge them with probability $\eta$.
+% \TODO{Assumption about $\sigma$?}
+
 \subsection{Application to neuron segmentation}\label{sec:cremi_details}
@@
 Increasing $k$ did not improve their scores either.
-
-\subsection{MWS on SSBM graphs}
-
-\begin{prop}\label{prop:MWS_SSBM_1}
-Consider a graph $\mathcal{G}(V,E)$ generated with a SSBM with parameters $N,p,k,\sigma$ and an associated ground truth (GT) clustering $\hat{\Pi}=\{\hat{S}_1, \ldots, \hat{S}_k\}$.
-Then, assume that after some merging-iterations of the MWS algorithm the clustering $\Pi$ is found.
-Then, any two clusters $S_i,S_j\in \Pi$ have probability $|E_{ij}| / |E_{\Pi}^1|$ to be selected in the next iteration of the algorithm, where $E_{\Pi}^1$ is the multicut associated to $\Pi$ and $E_{ij}\equiv(S_i\times S_j)\cap E$ is the set of edges connecting the two clusters.
-\end{prop}
-
-\begin{prop}\label{prop:MWS_SSBM_2}
-Given the assumptions of Prop.~\ref{prop:MWS_SSBM_1}, let $E_{ij}^+=\{(u,v) \in E_{ij} | \exists \hat{S}\in \hat{\Pi} \, \mathrm{s.t.} \, u\in \hat{S} \wedge v\in \hat{S} \}$ denote the set of true attractive GT edges connecting two clusters $S_i,S_j$
-\begin{equation}
-\sum_{ij} \frac{|E_ij^+|}{||}
-\end{equation}
-\end{prop}
-
-Then, the MWS algorithm will assign highest priority to 
-Among these edges, we define the set of true attractive GT edges as . Finally, let $f^+=|E_{ij}^+| / |E_{ij}|$ denote the fraction of true attractive edges. Then, the Mutex Watershed algorithm
-
-\begin{itemize}
-\item each pair of clusters $S_i,S_j$ has probability $|E_{ij}| / |E_{\Pi}^1|$ to have the interaction with highest priority 
-\item if the pair of clusters $S_i,S_j$ is given the highest priority by the MWS Algorithm, then they have has a probability $p^+=f^+(1-\eta) + f^+ \eta$ to be merged and $p^-=1-p^+$ to be constrained.
-\end{itemize}
-will assign a positive interaction to clusters $S_i,S_j$ with probability $f^+(1-\eta) + f^+ \eta$. 
-Remarks: this quantity does not depend on the size of $|E_{ij}|$ (so it won't change when clusters grow in size); if $f^+=1$ (i.e.
-$S_i,S_j$ are subclusters of the same GT cluster), then MWS will merge them with probability $1-\eta$; if $f^+=0$ (i.e.
-$S_i,S_j$ are subclusters of two different GT clusters), then MWS will merge them with probability $\eta$.
-\TODO{Assumption about $\sigma$?}

### 2021-03-11 chapters/1_intro.tex
Small changes intro

@@
     \caption{Clustering algorithms included in the proposed \algname{} framework, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
-New constrained hierarchical clustering algorithms (HCC) are highlighted in yellow.
+New constrained hierarchical clustering algorithms (HCC) proposed in this paper are highlighted in yellow.
 Algorithms typeset in bold-font define an ultrametric on the graph (Eq.~\ref{eq:UM_def}).
 Algorithms included in the green box, are weight-shift invariant (Prop.~\ref{prop:weight_shift_invariant}).
-    Given a graph $\mathcal{G}(V,E)$, we denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two clusters $S_i \subseteq V$, $S_j \subseteq V$. } 
+    Given a signed graph $\mathcal{G}(V,E, w_e)$, we denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two clusters $S_i \subseteq V$, $S_j \subseteq V$. } 
     \label{tab:linkage-criteria}
@@
 
-In this paper, we propose a simple theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical clustering (HC) on positive-weighted graphs \cite{lance1967general}.
+Our first main contribution is a simple theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical clustering (HC) on positive-weighted graphs \cite{lance1967general}.
 This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints} (see Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}, \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}b}, and Table~\ref{tab:linkage-criteria}).

### 2021-03-11 chapters/3_algorithm.tex
Small changes intro

@@
 Finally, in \emph{Phase~3}, the algorithm keeps merging all clusters until only a single one is left and then returns the hierarchical tree $T^*$ representing the full sequence of merging steps.
-The algorithm was implemented using a standard HC implementation with computational complexity $\mathcal{O}(N^2 \log N)$ (see Appendix \ref{sec:detailed_impl} for more details).
+The algorithm was implemented using a standard HC implementation with computational complexity $\mathcal{O}(N^2 \log N)$ (see extended details in Appendix \ref{sec:detailed_impl}).
 

### 2021-03-11 chapters/5_experiments_intro.tex
Small changes intro

@@
 We divided the three CREMI training samples, consisting of $\sim$196 million voxels each, into five sub-blocks for a total of 15 clustering problems (named \emph{CREMI-gridGraph} in Table~\ref{tab:datasets_and_energies}).
-See Appendix \ref{sec:cremi_details} for extended details about training, data augmentation, and how we remove tiny clusters after running \algname{} on the \emph{CREMI-gridGraph} clustering problems.
+See Appendix \ref{sec:cremi_details} for extended details about training, data augmentation, and how we remove tiny clusters left after running \algname{} on the \emph{CREMI-gridGraph} clustering problems.
 
@@
 Lastly, the MWS algorithm is not expected to perform well on these graphs because of the high sensitivity of the AbsMax linkage to flipping noise.
-In Propositions \ref{prop:MWS_SSBM_1} and \ref{prop:MWS_SSBM_2} (see Appendix), we prove that on SSBM graphs the merging steps of the MWS algorithm are given by a sequence of ``coin flip'' decisions with a probability proportional to the noise parameter $\eta$, independently on the cluster sizes.
+In Propositions \ref{prop:MWS_SSBM_1} and \ref{prop:MWS_SSBM_2} (see \TODO{Appendix}), we prove that on SSBM graphs the merging steps of the MWS algorithm are given by a sequence of ``coin flip'' decisions with a probability proportional to the noise parameter $\eta$, independently on the cluster sizes.
 
@@
         \caption{
-ARAND errors (median values over 20 experiments, lower is better) on synthetic graphs generated with SSBM, with $N=10000$ nodes, edges added with probability $p$, and $k$ ground truth communities of random size.
+ARAND errors (median values over 20 experiments, lower is better) on synthetic graphs generated with SSBM.
+We consider $k$ ground truth communities of random size.
+Graphs have $N=10000$ nodes and edges are randomly added with probability $p$.
 % The spectral clustering methods, SPONGE and SPONGE$_sym$, were given the true number of clusters as input. 

### 2021-03-12 chapters/0_abstract.tex
Comments from Fred; move prop to appendix

@@
 We prove the equivalence of existing clustering methods to some of those combinations and introduce new algorithms for combinations that have not been studied before. 
-We study both theoretical and empirical properties of these combinations and prove which ones of them define an ultrametric on the graph.
+We study both theoretical and empirical properties of these combinations and prove which of these define an ultrametric on the graph.
 We conduct a systematic comparison of various instantiations of GASP on a large variety of both synthetic and existing signed clustering problems, in terms of accuracy but also efficiency and robustness to noise.
-Lastly, we find that some of the algorithms included in our framework, when combined with the predictions from a CNN model, result in a simple instance segmentation pipeline that achieves state-of-the-art performances on the competitive CREMI 2016 EM segmentation benchmark.
+Lastly, we find that some of the algorithms included in our framework, when combined with the predictions from a CNN model, result in a simple bottom-up instance segmentation pipeline that achieves state-of-the-art accuracy on the CREMI 2016 EM segmentation benchmark.
 

### 2021-03-12 chapters/1_intro.tex
Comments from Fred; move prop to appendix

@@
 \centering
-\includegraphics[width=0.98\textwidth]{figs/intro_image_v5.pdf} % left bottom right top
+\includegraphics[width=0.98\textwidth]{figs/intro_image_v6.pdf} % left bottom right top
 \caption{\textbf{(a)} Some iterations of \algname{}, the proposed Generalized Agglomerative Algorithm for Signed Graph Partitioning, on a toy graph with attractive/positive (green) and repulsive/negative (red) interactions.
 At each iteration, the yellow edge with highest interaction is contracted.
-Average and sum linkage methods are shown.
+An example with sum linkage criterion is shown.
 \textbf{(b)} List of linkage criteria used in this paper (see definitions in Table~\ref{tab:linkage-criteria} below), demonstrated on two small clusters.
@@
         \begin{tabular}{l |c  c  c  c  c}
-        % \multicolumn{1}{c}{}
-        % \multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} \\ $\,\,\interact(S_u ,S_v)$}}  
+        % 
+        \multicolumn{1}{c|}{\multirow{2}{*}[-1.5em]{{\Large GASP}}} 
         & \thead{Sum\\Linkage} & \thead{Absolute Maximum\\Linkage} & \thead{Average\\Linkage} & \thead{Single\\Linkage} & \thead{Complete\\Linkage} \\
@@
 
-            \thead[r]{GASP on positive-weighted graphs} & \thead{-} &\tikzmark{a} \thead{\textbf{HC-Single}} &\tikzmark{g} \thead{\textbf{HC-Avg}} &\thead{\textbf{HC-Single}}\tikzmark{z} &\thead{\textbf{HC-Complete}} \tikzmark{b} \\
+            \thead[r]{GASP on unsigned graphs} & \thead{-} &\tikzmark{a} \thead{\textbf{HC-Single}} &\tikzmark{g} \thead{\textbf{HC-Avg}} &\thead{\textbf{HC-Single}}\tikzmark{z} &\thead{\textbf{HC-Complete}} \tikzmark{b} \\
             \thead[r]{GASP on signed graphs} & \thead{GAEC \cite{keuper2015efficient}} &  \thead{\textbf{Mutex Watershed} \cite{wolf2018mutex}}& \tikzmark{f} \thead{\textbf{HC-Avg}} &\thead{\textbf{HC-Single}} \tikzmark{e} &\thead{\textbf{HC-Complete}}\tikzmark{w} \\
@@
     \end{subtable} 
-    \caption{Clustering algorithms included in the proposed \algname{} framework, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
+    \caption{Conceptual contribution: Properties of clustering algorithms included in the proposed \algname{} framework, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints.
 New constrained hierarchical clustering algorithms (HCC) proposed in this paper are highlighted in yellow.
-Algorithms typeset in bold-font define an ultrametric on the graph (Eq.~\ref{eq:UM_def}).
-Algorithms included in the green box, are weight-shift invariant (Prop.~\ref{prop:weight_shift_invariant}).
+Algorithms typeset in bold font define an ultrametric on the graph (Eq.~\ref{eq:UM_def}).
+Algorithms included in the green box are weight-shift invariant (Prop.~\ref{prop:weight_shift_invariant}).
     Given a signed graph $\mathcal{G}(V,E, w_e)$, we denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two clusters $S_i \subseteq V$, $S_j \subseteq V$. } 
@@
 
-Other graph clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between nodes.
-The advantage of signed graphs over positive-weighted graphs is that balancing attraction and repulsion allows us to obtain a clustering without defining additional parameters.
+Other graph clustering methods work with so-called \emph{signed graphs}, which feature both positive and negative edge weights corresponding to attraction and repulsion between nodes.
+The advantage of signed graphs over unsigned graphs is that balancing attraction and repulsion allows us to obtain a clustering without defining additional parameters.
 A canonical formulation of the signed graph partitioning problem is the \emph{multicut} or \emph{correlation clustering} problem \cite{kappes2011globally,chopra1991multiway}.
-This problem is NP-hard, though many approximate solvers have been proposed \cite{lange2018combinatorial,pape2017solving,beier2016efficient,yarkony2012fast}.
-The general problem of graph partitioning can also be solved approximately by greedy agglomerative clustering \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}.
+This problem is NP-hard, though many approximate solvers have been proposed \cite{lange2018combinatorial,pape2017solving,beier2016efficient,yarkony2012fast} together with greedy agglomerative clustering algorithms \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}.
 Agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter-free and efficient.
@@
 
-Our first main contribution is a simple theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical clustering (HC) on positive-weighted graphs \cite{lance1967general}.
+Our first contribution is a simple theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical clustering (HC) on unsigned graphs (Section \ref{sec:algorithm}).
 This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints} (see Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}, \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}b}, and Table~\ref{tab:linkage-criteria}).
-We then formally prove that some of the combinations correspond to existing clustering algorithms, and introduce new algorithms for combinations which have not been explored before.
-By analyzing their theoretical properties, we also show which one of them define an ultrametric on the graph.
+As second contribution, in Section \ref{sec:alg_update_rules}, we formally prove that some of the combinations correspond to existing clustering algorithms, and introduce new algorithms for combinations which have not been explored before.
+By analyzing their theoretical properties, we also show which ones define an ultrametric on the graph (see Table~\ref{tab:linkage-criteria}).
 
-We evaluate the algorithms on a large variety of both existing and synthetically generated signed graph clustering problems. 
-Next, we also test the algorithms on \emph{instance segmentation} -- a computer vision task consisting in assigning each pixel of an image to an object instance -- by predicting graph edge weights with a CNN (Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}c}).
-Our experiments show that the choice of a linkage criterion strongly influences the way how clusters are grown by the agglomerative algorithms (Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}d}), making some linkage methods more suited for certain types of clustering problems.
+We evaluate the algorithms on a large variety of both existing and synthetically generated signed graph clustering problems (third contribution, Section \ref{sec:neuro_segm_exp}). 
+Finally, we also test the algorithms on \emph{instance segmentation} -- a computer vision task consisting of assigning each pixel of an image to an object instance -- by partitioning graphs whose edge weights are estimated by a CNN (fourth contribution, see Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}c} and Section \ref{sec:experiments_discussion}).
+Our experiments show that the choice of linkage criterion markedly influences how clusters are grown by the agglomerative algorithms (Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}d}), making some linkage methods more suited for certain types of clustering problems.
 % We focus our comparison on three of the best-performing algorithms included in our framework, which are based on average, sum, and absolute maximum linkage criteria (see Table~\ref{tab:linkage-criteria}).
@@
 We benchmark the clustering algorithms by focusing on their efficiency, robustness and tendency to over- or under-cluster. 
-On instance segmentation, we show that the tested agglomerative algorithms strongly outperform recently proposed spectral clustering methods, and that average-linkage based agglomerative algorithms achieve state of the art results on the competitive CREMI 2016 challenge for neuron segmentation of 3D electron microscopy image volumes of brain tissue.
+On instance segmentation, we show that the tested agglomerative algorithms strongly outperform recently proposed spectral clustering methods, and that average-linkage based agglomerative algorithms achieve state of the art results on the CREMI 2016 challenge for neuron segmentation of 3D electron microscopy image volumes of brain tissue.
 

### 2021-03-12 chapters/2_rel_work.tex
Comments from Fred; move prop to appendix

@@
 \section{Related work} \label{sec:related_work}
-\textbf{Proposal-based methods} have been highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}and CityScapes \cite{cordts2016cityscapes}.
+% \textbf{Proposal-based methods} have been highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}and CityScapes \cite{cordts2016cityscapes}.
 They decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,porzi2019seamless,liu2018path,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}.
-% They commonly rely on {Faster-RCNN}~\cite{ren2015faster} and can be trained end-to-end using non-maximum suppression. 
-% Other methods use instead recurrent models to sequentially generate instances one-by-one \cite{romera2016recurrent,ren2017end}.
 
-\textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances.
+\textbf{Proposal-free instance segmentation methods} adopt a bottom-up approach by directly grouping pixels into instances.
 Recently, there has been a growing interest for such  methods that do not involve object detection, since, in certain types of data, object instances cannot be approximated by bounding boxes \cite{kirillov2017instancecut,bai2017deep}.
@@
 % , like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}. 
-Other recent successful methods simply let the model predict the relative coordinates of the instance center \cite{neven2019instance,cheng2019panopticdeeplab} or, given a point $(x,y)$ in the image, they train a model to generate the mask of the instance located at $(x,y)$ \cite{sofiiuk2019adaptis}.
+Other recent methods let the model predict the relative coordinates of the instance center \cite{neven2019instance,cheng2019panopticdeeplab} or, given a pixel $(x,y)$, they train a model to generate the mask of the instance located at $(x,y)$ \cite{sofiiuk2019adaptis}.
 
@@
 
-This work reformulates the clustering algorithms of \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a generalized framework and adopt ideas from the proposal-free instance segmentation methods \cite{liu2018affinity,wolf2018mutex,lee2017superhuman} to predict long-range affinities between pixels.
+This work reformulates the clustering algorithms of \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a generalized framework and adopt ideas from the proposal-free instance segmentation methods \cite{liu2018affinity,wolf2018mutex,lee2017superhuman} to predict edge weights of a graph.

### 2021-03-12 chapters/3_algorithm.tex
Comments from Fred; move prop to appendix

--- 2021-03-10 chapters/3_algorithm.tex
@@
 
-\textbf{Multicut objective} -- We call the set $\Pi=\{S_1,\ldots,S_K\}$ a \emph{clustering} or \emph{partitioning} if $V = \cup_{S\in\Pi} S $, $\,S \cap S' = \emptyset$ for different clusters $S, S'\in \Pi$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
+\textbf{Multicut objective} -- We call the set $\Pi=\{S_1,\ldots,S_K\}$ a \emph{clustering} or \emph{partitioning} if $V = \cup_{S\in\Pi} S $, $\,S \cap S' = \emptyset$ for different clusters $S, S'$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.
 For any clustering $\Pi$ of $\mathcal{G}$, we denote as $E^0_\Pi= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u,v \in S \}$ the set of edges linking nodes in the same cluster.
@@
 % Algorithm \ref{main_alg} returns a binary tree denoted by $T^*$.
-Given an agglomerative algorithm with merging tree $T$, let $h_T:T \rightarrow \mathbb{N}$ denote the \emph{dendrogram-height} of each $(u\vee v)\in T$, which is defined as the iteration number at which nodes $u,v\in V$ were merged by the algorithm (see example in Fig.~\ref{fig:intro_figure}b).
+Given an agglomerative algorithm with merging tree $T$, let $h_T:T \rightarrow \mathbb{N}$ denote the \emph{dendrogram-height} of each $(u\vee v)\in T$, which is defined as the iteration number at which nodes $u,v\in V$ were merged by the algorithm (see example in Fig.~\ref{fig:intro_figure}a).
 We also define $\treeHeight(u,v)$ as the signed interaction $\interact{}(S,S')$ between the two clusters $S,S'$ that were merged at iteration $h_T(u\vee v)$:
@@
 \emph{Phase~One} terminates when all the remaining clusters are either constrained or share repulsive interactions.
+Note that, on unsigned graphs, in \emph{Phase 1} \algname{} merges all nodes in a single cluster and is then equivalent to a standard hierarchical clustering algorithm.
 
-\emph{Phase Two:} Now that the clusters have grown in size, the algorithm removes the constraints previously introduced in \emph{Phase~One} and merges all the clusters that still share an attractive interaction, merging the most attractive one first\footnote{Note that in the version of \algname{} with \emph{addCannotLinkConstraints} set to \texttt{False}, nothing happens in \emph{Phase~Two}.}.
+\emph{Phase Two:} Now that the clusters have grown in size, the algorithm removes the constraints previously introduced in \emph{Phase~One} and merges all the clusters that still share an attractive interaction, merging the most attractive one first\footnote{Note that in the version of \algname{} without \emph{cannotLinkConstraints}, nothing happens in \emph{Phase~Two} because all remaining interactions are repulsive.}.
 The final clustering $\Pi^*$ returned by \algname{} is found at the end of \emph{Phase~Two} and it is then composed of clusters sharing only mutual repulsive interactions.
@@
 Finally, in \emph{Phase~3}, the algorithm keeps merging all clusters until only a single one is left and then returns the hierarchical tree $T^*$ representing the full sequence of merging steps.
-The algorithm was implemented using a standard HC implementation with computational complexity $\mathcal{O}(N^2 \log N)$ (see Appendix \ref{sec:detailed_impl} for more details).
+The algorithm was implemented using a standard HC implementation with computational complexity $\mathcal{O}(N^2 \log N)$ (details left in Appendix \ref{sec:detailed_impl}).
 
@@
       \State Initial clustering: $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$
-      \State Initialize hierarchical tree $T$ with leaves nodes $V=\{v_1,\ldots,v_{|V|}\}$
+      \State Initialize hierarchical tree $T$ with leaf nodes  $V=\{v_1,\ldots,v_{|V|}\}$
       \State Initialize interactions between clusters with $\cost_e = w^+_e - w^-_e$
@@
 On signed graphs, the sum of two attractive (or repulsive) interactions is still attractive (repulsive).
-On the other hand, on positive weighted graphs, a strong attractive interaction could be obtained by summing many weak interactions, which is often not desirable.
-This explains why, to our knowledge, an agglomerative algorithm with sum linkage has never been used on positive weighted graphs.
+On the other hand, on unsigned graphs, a strong attractive interaction could be obtained by summing many weak interactions, which depending on the application could be undesirable.
+This explains why, to our knowledge, an agglomerative algorithm with sum linkage has never been used on unsigned graphs.
 On signed graphs, such an algorithm was pioneered in \cite{levinkov2017comparative,keuper2015efficient} and was named Greedy Agglomerative Edge Contraction (GAEC)\footnote{An algorithm equivalent to GAEC was recently independently re-proposed in \cite{chehreghani2020hierarchical}.}.
 All variations of \algname{} decrease the multicut objective defined in Eq.~\ref{eq:MC_objective} each time two clusters with positive interaction are merged.
-But only GAEC always makes the \emph{greedy-choice} that will mostly decrease the multicut objective at every step.
+But only GAEC always makes the \emph{greedy-choice} that mostly decreases the multicut objective at each iteration.
 The authors of \cite{levinkov2017comparative} also proposed a version of GAEC with cannot-link constraints named \emph{GreedyFixation}, but the constrained sum-link version of \algname{} proposed here (named \emph{HCC-Sum} in Table~\ref{tab:linkage-criteria}) did perform better in our experiments.
 
-\paragraph{AbsMax Linkage} -- This linkage method is also specific to signed graphs, since on positive-weighted graphs it would be equivalent to single linkage.
-Here, we prove that the Mutex Watershed Algorithm \cite{wolf2018mutex} can be seen as an agglomerative algorithm with AbsMax linkage (proofs of the following propositions are given in Appendix \ref{sec:proposition_proofs}):
+\paragraph{AbsMax Linkage} -- This linkage method is also specific to signed graphs, since on unsigned graphs it would be equivalent to single linkage.
+Here, we prove that the Mutex Watershed Algorithm \cite{wolf2018mutex} can be seen as an agglomerative algorithm with AbsMax linkage (proofs of the following three propositions are given in Appendix \ref{sec:proposition_proofs}):
 \begin{restatable}{prop}{absmaxmutex}
@@
 
-\paragraph{Average, Single, and Complete Linkage} -- These three linkage criteria have been throughly studied on positive-weighted graphs, but never on signed graphs.
-In the recent related work \cite{chehreghani2020hierarchical}, the authors prove that applying these three linkage methods to a signed graph is equivalent to applying them to the positive-weighted graph obtained by shifting all edge weights by a constant.
+\paragraph{Average, Single, and Complete Linkage} -- These three linkage criteria have been throughly studied on unsigned graphs, but never on signed graphs.
+In the recent related work \cite{chehreghani2020hierarchical}, the authors prove that applying these three linkage methods to a signed graph is equivalent to applying them to the unsigned graph obtained by shifting all edge weights by a constant.
 Here, we prove which of the algorithms included in our generalized framework have this invariance-property:
@@
 \end{restatable}
-\noindent To our knowledge, Average and Single linkage methods have never been combined with cannot-link constraints on signed graphs, so the constrained hierarchical clustering algorithms that in Table~\ref{tab:linkage-criteria} are named \emph{HCC-Avg} and \emph{HCC-Single} are new.
+\noindent To our knowledge, Average and Single linkage methods have never been combined with cannot-link constraints on signed graphs, so the constrained hierarchical clustering algorithms \emph{HCC-Avg} and \emph{HCC-Single} are new (see Table~\ref{tab:linkage-criteria}).
 In Lemma \ref{lemma:absMax_and_complete_property} (Appendix \ref{sec:proposition_proofs}), we prove that with a Complete linkage the agglomeration order does not change whether constraints are introduced or not.
@@
 \end{align}
-and where $\epsilon > 0$. By definition, we have that $d_{T}(u,v)=d_{T}(v,u)$ and $d_{T}(u,u)= 0$. We then prove the following two propositions:
-\begin{restatable}{prop}{firstUltraMetricProperty}
-\label{prop:ultraMetric1}
-Consider a graph $\mathcal{G}(V,E,w_e)$, a linkage criterion $\interact{}$, and an agglomerative algorithm returning a binary rooted tree $T$ with height $h_T$.
-Then, $(V, d_{T})$ defined in Eq.~\ref{eq:UM_def} is an ultrametric if and only if the following is true
- % iff the interaction $\interact{}_{T}(u, v)$ associated to the least common ancestor ${(u\vee v)\in T}$ is both lower than the interaction of any other $(u\vee v)$-descendant node and higher than the interaction of any other $(u\vee v)$-ancestor node in the tree $T$.
-In formulae, this is equivalent to saying that, $\forall u,v,t \in V$:
-\begin{equation}\label{eq:UM_assumption}
- h_T(u \vee v) < h_T(u \vee t) \Rightarrow \interact{}_{T}(u,v) \geq \interact{}_{T}(u,t),
- % h_T(u \vee v) < h_T(u \vee t) \Leftrightarrow \interact{}_{T}(u,v) > \interact{}_{T}(u,t). 
-\end{equation}
-which in words means: if the algorithm merges nodes $u,v$ before to merge nodes $u,t$, then the signed interaction $\interact{}_{T}(u,v)$ between $u$ and $v$ has to be higher or equal than $\interact{}_{T}(u,t)$.
-% In words, $(V, d_{T})$ is an ultrametric iff the interaction $\interact{}_{T}(u, v)$ associated to the least common ancestor ${(u\vee v)\in T}$ is both lower than any other $(u\vee v)$-descendant node and higher than any other $(u\vee v)$-ancestor node in the tree $T$.
-\end{restatable}
+and where $\epsilon > 0$. 
+% By definition, we have that $d_{T}(u,v)=d_{T}(v,u)$ and $d_{T}(u,u)= 0$. 
+We then prove the following proposition:
 \begin{restatable}{prop}{secondUltraMetricProperty}

### 2021-03-12 chapters/5_experiments_intro.tex
Comments from Fred; move prop to appendix

@@
 \subsection{Signed graph clustering problems}
-We evaluate the agglomerative clustering algorithms included in our framework on a large collection of both synthetic and real-world graphs.
-The size of the graphs ranges from a few hundred to hundreds of millions of edges and the graphs have very different structures, so that the algorithms are tested in very different scenarios.
+We evaluate the agglomerative clustering algorithms included in our framework on a large collection of both synthetic and real-world graphs with very different structures.
+The size of the graphs ranges from a few hundred to hundreds of millions of edges.
 
@@
 We use an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N$ vertices and edge probability $p$.
-Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) have Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $\sigma=0.1$.
+Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k$ \emph{ground-truth} clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) have Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $\sigma=0.1$.
 To model noise, the sign of the edge weights is flipped independently with probability $\eta$.
@@
 
-\subsection{Comparison results and discussion}
+\subsection{Comparison results and discussion}\label{sec:experiments_discussion}
 % Before to evaluate the clustering algorithms on real-world graphs, we compare them on two types of synthetically generated graphs and highlight some of their fundamental properties.
@@
 By looking at results in Table~\ref{tab:datasets_and_energies}, we observe that GAEC almost always achieves the lowest objective values, apart from the \emph{CREMI-gridGraph} instances.
-Despite this, on graphs where a GT clustering is known, GAEC does not achieve the best ARAND scores (see Tables~\ref{tab:scores_gridGraph} and \ref{tab:scores_3drag}).
+Despite this, on graphs where a GT clustering is known, GAEC does not achieve the lowest ARAND errors (see Tables~\ref{tab:scores_gridGraph} and \ref{tab:scores_3drag}).
 % To better understand these empirical results, we now make the following important observation.
@@
 \algname{} algorithms using cannotLinkConstraints are not expected to perform well on these graphs, because of the type of employed flip noise, so we focus our comparison only on the GAEC, HC-Avg and MWS algorithms (using Sum, Average, and AbsMax linkage methods, respectively).
-Empirically, we observe that GAEC is the agglomerative algorithm performing best on SSBM graphs, almost as good as the spectral method SPONGE$_{sym}$ (see Fig.~\ref{fig:SSBM_scores}).
+Empirically, we observe that GAEC is the agglomerative algorithm performing best on SSBM graphs, on par with spectral method SPONGE$_{sym}$ (see Fig.~\ref{fig:SSBM_scores}).
 Given the simple properties of SSBM graphs, we will now give a specific explanation of these empirical results.
@@
 Scores in Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show their poor performances: Single linkage hierarchical clustering (HC-Single), which here is equivalent to thresholding the edge weights at $w_e=0$ and computing connected components in the graph, often returned few big under-segmented clusters.
-HC-Complete and HCC-Complete returned instead a lot of over-segmented clusters.
+HC-Complete returned instead a lot of over-segmented clusters.
 % These algorithms are excluded from our next comparison experiments.
@@
 On the other hand, the \emph{gridGraph} and \emph{3D-rag} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: weather a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance).
-Tables~\ref{tab:scores_3drag}-\ref{tab:scores_gridGraph} show that average linkage methods (\emph{HC-Avg}, \emph{HCC-Avg}) strongly outperforms other methods on \emph{CREMI-gridGraph} instances and also achieves the best scores on \emph{CREMI-3D-rag} graphs.
-Sum-based linkage methods (\emph{GAEC}, \emph{HCC-Sum}) do not perform well on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}).
+Tables~\ref{tab:scores_3drag}-\ref{tab:scores_gridGraph} show that average linkage methods (HC-Avg, HCC-Avg) strongly outperforms other methods on \emph{CREMI-gridGraph} instances and also achieves the best scores on \emph{CREMI-3D-rag} graphs.
+Sum-based linkage methods (GAEC, HCC-Sum) do not perform well on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}).
 This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods performs poorly on grid-graphs, because in this setup edge weights are predicted by a CNN and noise is strongly spatially-correlated \footnote{This effect is not as strong on \emph{3D-rag} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
 To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}.
-The plot in Fig.~\ref{fig:scores_structured_noise} confirms that \emph{HC-Avg} and \emph{HCC-Avg} perform well even in the presence of strong structured noise, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (\emph{MWS}).
-It is not a surprise that the AbsMax linkage used by \emph{MWS} is not robust to this type of structured noise.
-However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} prove how \emph{MWS} can achieve competitive performances with considerably lower runtimes.
+The plot in Fig.~\ref{fig:scores_structured_noise} confirms that HC-Avg and HCC-Avg perform well even in the presence of strong structured noise, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (MWS).
+It is not a surprise that the AbsMax linkage used by MWS is not robust to this type of structured noise.
+However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} prove how MWS can achieve competitive performances with considerably lower runtimes.
 
@@
 \includegraphics[width=0.48\textwidth,trim=80 10 60 0, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
-\caption{Dendrograms built by three versions of \algname{} (GAEC, MWS, and HC-Avg) on a synthetic graph generated with SSBM ($N=250$, $p=0.05$, $\eta=0.1$, and $k=2$ communities of equal size).
-Red and blue colors represent the true community of each initial node.
+\caption{Dendrograms built by three versions of \algname{} (GAEC, MWS, and HC-Avg) on a synthetic graph generated with SSBM ($N=250$ nodes, edge probability $p=0.05$, flipping probability $\eta=0.1$).
+Red and blue colors represent the ground-truth community of each node (two communities of equal size).
 At the top, dendrograms are truncated at the level of the final clustering $\Pi^*$ returned by \algname{} (y-axis shows the iteration number).
@@
 \textbf{Results on CREMI challenge} -- 
-Table~\ref{tab:cremi_leaderboard} shows that the \emph{HCC-Avg} and \emph{HC-Avg} clustering algorithms achieve state-of-the-art performances on the CREMI challenge, when combined to the predictions of our CNN.
+Table~\ref{tab:cremi_leaderboard} shows that the HCC-Avg and HC-Avg clustering algorithms achieve state-of-the-art performances on the CREMI challenge, when combined to the predictions of our CNN.
 Most of the other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs.
@@
 However, our method operating directly on pixels (\emph{gridGraph+HCC-Avg}) achieves better performances than superpixel-based methods (\emph{3D-rag+HCC-Avg}) and does not require the parameter tuning necessary to obtain good super-pixels, which is usually highly dataset dependent.
-The method \emph{3D-rag+LiftedMulticut} based on the lifted multicut formulation of \cite{beier2017multicut} achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and super-pixel shape information.
+The method \emph{3D-rag+LiftedMulticut} based on the lifted multicut approximation of \cite{beier2017multicut} achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and super-pixel shape information.
 To scale up our method operating on pixels, we divided each test-volume into four sub-blocks, and then combined the resulting clusterings by running the algorithms again on the combined graph.
@@
 \includegraphics[width=0.48\textwidth,trim=90 10 60 0, clip]{./figs/comparison_GAEC_MWS_Avg.png} % left bottom right top
-\caption{Failure cases of three versions of \algname{} on challenging parts of the CREMI dataset.
+\caption{Failure cases of three versions of \algname{} (GAEC, MWS, and HC-Avg) applied to neuron segmentation.
 \emph{Wrongly} segmented regions are highlighted in different warm colors.
-Red arrows point to wrongly split regions; yellow ones to merge errors.
+Red arrows point to wrongly split regions; yellow arrows point to merge errors.
 HC-Avg returned the best segmentation.

### 2021-03-12 chapters/supplementary.tex
Comments from Fred; move prop to appendix

@@
 
-\firstUltraMetricProperty*
+\begin{restatable}{prop}{firstUltraMetricProperty}
+\label{prop:ultraMetric1}
+Consider a graph $\mathcal{G}(V,E,w_e)$, a linkage criterion $\interact{}$, and an agglomerative algorithm returning a binary rooted tree $T$ with height $h_T$.
+Then, $(V, d_{T})$ defined in Eq.~\ref{eq:UM_def} is an ultrametric if and only if the following is true:
+ % iff the interaction $\interact{}_{T}(u, v)$ associated to the least common ancestor ${(u\vee v)\in T}$ is both lower than the interaction of any other $(u\vee v)$-descendant node and higher than the interaction of any other $(u\vee v)$-ancestor node in the tree $T$.
+In formulae, this is equivalent to saying that, $\forall u,v,t \in V$:
+\begin{equation}\label{eq:UM_assumption}
+ h_T(u \vee v) < h_T(u \vee t) \Rightarrow \interact{}_{T}(u,v) \geq \interact{}_{T}(u,t).
+ % h_T(u \vee v) < h_T(u \vee t) \Leftrightarrow \interact{}_{T}(u,v) > \interact{}_{T}(u,t). 
+\end{equation}
+In words, condition \ref{eq:UM_assumption} means: if the algorithm merges nodes $u,v$ before to merge nodes $u,t$, then the signed interaction $\interact{}_{T}(u,v)$ between $u$ and $v$ has to be higher or equal than $\interact{}_{T}(u,t)$.
+% In words, $(V, d_{T})$ is an ultrametric iff the interaction $\interact{}_{T}(u, v)$ associated to the least common ancestor ${(u\vee v)\in T}$ is both lower than any other $(u\vee v)$-descendant node and higher than any other $(u\vee v)$-ancestor node in the tree $T$.
+\end{restatable}
 \begin{proof}
@@
 Thanks to Lemma \ref{lemma:absMax_and_complete_property}, we have that condition 2 always holds for algorithms based on AbsMax and Complete linkage, proving that the Mutex Watershed and HC-Complete algorithms define an ultra-metric (whether or not cannot-link-constraints are enforced).
-On the other hand, condition 2 does not hold for other variations of \algname{} involving cannot-link-constraints (HCC-Sum, HCC-Avg, and HCC-Single), which do not define then an ultrametric.
+On the other hand, condition 2 does not hold for other variations of \algname{} involving cannot-link-constraints (HCC-Sum, HCC-Avg, and HCC-Single), which do not then define an ultrametric.
 

### 2021-03-13 chapters/3_algorithm.tex
Intregrate overleaf comments

@@
 % We call two clusters $S,S'$ \emph{adjacent} if there exists at least one edge ${e_{ts}\in E}$ connecting a node $t\in S_u$ to a node $s\in S_v$. 
-Let the interaction $\interact(S,S')$ between two clusters $S,S'$ be defined as a function $\interact{}:2^{V} \times 2^{V} \rightarrow \mathbb{R}$, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S$ and $S'$, i.e.
+Let the interaction $\interact(S,S')\in\mathbb{R}$ between two clusters $S,S'$ be defined as a function, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S$ and $S'$, i.e.
 ${(S \times S') \cap E}$.
@@
 
-In \emph{Phase~One}, \algname{} selects the pair of clusters with the highest absolute interaction $|\interact(S, S')|$, so that the most attractive and the most repulsive pairs are analyzed first.
-If the interaction is repulsive and the algorithm option \emph{addCannotLinkConstraints} is \texttt{True}, then the two clusters are constrained so that their members can never merge in subsequent steps of \emph{Phase~One}.
+In phase one, \algname{} selects the pair of clusters with the highest absolute interaction $|\interact(S, S')|$, so that the most attractive and the most repulsive pairs are analyzed first.
+If the interaction is repulsive and the algorithm option \emph{addCannotLinkConstraints} is \texttt{True}, then the two clusters are constrained so that their members can never merge in subsequent steps of phase one.
 If the interaction is attractive, then the clusters are merged, provided that they were not previously constrained.
 After each merge, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S, S')$ listed in Table \ref{tab:linkage-criteria}.
-\emph{Phase~One} terminates when all the remaining clusters are either constrained or share repulsive interactions.
-Note that, on unsigned graphs, in \emph{Phase 1} \algname{} merges all nodes in a single cluster and is then equivalent to a standard hierarchical clustering algorithm.
+Phase one terminates when all the remaining clusters are either constrained or share repulsive interactions.
+Note that, on unsigned graphs, in phase one \algname{} merges all nodes in a single cluster and is then equivalent to a standard hierarchical clustering algorithm.
 
-\emph{Phase Two:} Now that the clusters have grown in size, the algorithm removes the constraints previously introduced in \emph{Phase~One} and merges all the clusters that still share an attractive interaction, merging the most attractive one first\footnote{Note that in the version of \algname{} without \emph{cannotLinkConstraints}, nothing happens in \emph{Phase~Two} because all remaining interactions are repulsive.}.
-The final clustering $\Pi^*$ returned by \algname{} is found at the end of \emph{Phase~Two} and it is then composed of clusters sharing only mutual repulsive interactions.
+Phase two: Now that the clusters have grown in size, the algorithm removes the constraints previously introduced in phase one and merges all the clusters that still share an attractive interaction, merging the most attractive one first\footnote{Note that in the version of \algname{} without \emph{cannotLinkConstraints}, nothing happens in phase two because all remaining interactions are repulsive.}.
+The final clustering $\Pi^*$ returned by \algname{} is found at the end of phase two and it is then composed of clusters sharing only mutual repulsive interactions.
 
-Finally, in \emph{Phase~3}, the algorithm keeps merging all clusters until only a single one is left and then returns the hierarchical tree $T^*$ representing the full sequence of merging steps.
+Finally, in phase three, the algorithm keeps merging all clusters until only a single one is left and then returns the hierarchical tree $T^*$ representing the full sequence of merging steps.
 The algorithm was implemented using a standard HC implementation with computational complexity $\mathcal{O}(N^2 \log N)$ (details left in Appendix \ref{sec:detailed_impl}).
@@
       \State Initial clustering: $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$
-      \State Initialize hierarchical tree $T$ with leaf nodes  $V=\{v_1,\ldots,v_{|V|}\}$
-      \State Initialize interactions between clusters with $\cost_e = w^+_e - w^-_e$
+      \State Initialize hierarchical tree $T^*$ with leaf nodes  $V=\{v_1,\ldots,v_{|V|}\}$
+      \State Initialize  cluster interactions with $\cost_e = w^+_e - w^-_e$, $\forall e\in E$
       \State \emph{// Phase 1: Merge positive interactions (possibly using constraints)}
-      \State Push absolute interactions $|w_e|$ to priority queue $PQ$
+      \State For all edges $e\in E$, push incident nodes of $e$ to PQ with priority $|w_e|$
       \Repeat 
@@
         \If{\big[{\color{green}\textbf{$\interact{}(S,S') > 0$}}\big] \textbf{and} \big[$S,S'$ \textbf{not} constrained\big]}
-          \State Merge clusters $S$, $S'$ and update hierarchical tree $T$
+          \State Merge clusters $S$, $S'$ and update hierarchical tree $T^*$
           \State Update interactions \& constraints with neighboring clusters
@@
         \If{\big[{\color{green}\textbf{$\interact{}(S,S') > 0$}}\big]}
-          \State Merge clusters $S$, $S'$ and update hierarchical tree $T$
+          \State Merge clusters $S$, $S'$ and update hierarchical tree $T^*$
           \State Update interactions with neighboring clusters
@@
         \State Pop $S,S'\in\Pi$ from $PQ$ with highest interaction $\interact{}(S,S')$
-        \State Merge clusters $S$, $S'$ and update hierarchical tree $T$
+        \State Merge clusters $S$, $S'$ and update hierarchical tree $T^*$
         \State Update interactions with neighboring clusters
@@
       \State
-      \Return $\Pi^*$, $T^*\gets T$
+      \Return $\Pi^*$, $T^*$
   \end{algorithmic}
@@
 But only GAEC always makes the \emph{greedy-choice} that mostly decreases the multicut objective at each iteration.
-The authors of \cite{levinkov2017comparative} also proposed a version of GAEC with cannot-link constraints named \emph{GreedyFixation}, but the constrained sum-link version of \algname{} proposed here (named \emph{HCC-Sum} in Table~\ref{tab:linkage-criteria}) did perform better in our experiments.
+The authors of \cite{levinkov2017comparative} propose an algorithm named \emph{GreedyFixation}, which, in our framework, is equivalent to phase one of \algname{} using cannot-link-constraints and a sum linkage.
+However, running both phase one and two of \algname{} with sum linkage (algorithm named HCC-Sum in this paper) performed better than GreedyFixation in our experiments, because some clusters are wrongly constrained in phase one and only merged in phase two.
+% removing constraints in phase two   However, in our experiments, we noted that constrained sum-link version of \algname{} proposed here (named \emph{HCC-Sum} in Table~\ref{tab:linkage-criteria}) .
 

### 2021-03-13 chapters/supplementary.tex
Intregrate overleaf comments

@@
 An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph.
-Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that there exists exactly one representative $|\tilde{V} \cap S| = 1$ for every cluster $S \in \Pi$ .
+Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that there exists exactly one representative node $|\tilde{V} \cap S| = 1$ for every cluster $S \in \Pi$ .
 Edges in $\tilde{E}$ represent adjacency-relationships between clusters
-and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$. 
-For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$.
+and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$, where $S_u$ denotes the clustering including node $u$. 
+For the linkage criteria tested in this article, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$.
 Thus, we can recompute these interactions by using an \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$:
@@
 \paragraph{Implementation} Our implementation of \algname{} is based on an union-find data structure and a heap allowing deletion of its elements. 
-In Phases 2 and 3, \algname{} is equivalent to a standard hierarchical agglomerative clustering algorithm for unsigned graphs.
+In Phases 2 and 3, \algname{} is equivalent to a standard hierarchical agglomerative clustering algorithm with complexity $\mathcal{O}(N^2 \log N)$.
 In Algorithm \ref{detailed_alg}, we show our implementation of Phase 1, involving cannot-link constraints.
@@
 Therefore, 
-similarly to a heap-based implementation of hierarchical agglomerative clustering, our implementation of \algname{} has a complexity of $\mathcal{O}(N^2 \log N)$.
+similarly to a heap-based implementation of hierarchical agglomerative clustering, our implementation of \algname{} - Phase 1 has a complexity of $\mathcal{O}(N^2 \log N)$.
 In the worst case, when the graph is dense and $|E|=N^2$, the algorithm requires $\mathcal{O}(N^2)$ memory.
 Nevertheless, in our practical applications the graph is much sparser, so $\mathcal{O}(|E|)=\mathcal{O}(N)$.
-With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$.
+With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$, but only when cannotLinkConstraints are not used.
 Moreover, \algname{} with \emph{Absolute Maximum} linkage can be implemented more efficiently (see next section). %\TODO{Empirical complexity plot?}
@@
 If, on the other hand, we consider \algname{} with a Absolute Maximum linkage (see Table~\ref{tab:linkage_criteria_explicit}), during the agglomeration the interaction between two clusters can only increase in absolute value.
-Thus, the negative interaction $\interact{}(S_i,S_j)<0$ between two constrained clusters can possibly become positive over the course of next agglomeration steps only if there is at least another pair of clusters with positive interaction $\interact{}(S_l,S_t)>0$ higher in absolute value: $|\interact{}(S_l,S_t)| > |\interact{}(S_i,S_j)|$.
-If such clusters $S_l, S_t$ with positive interaction exist, we note that they must also be constrained (in the opposite case, the algorithm would have already merged them before to constrain $S_i$ and $S_j$, because their priority was higher).
+Thus, the negative interaction $\interact{}(S_i,S_j)<0$ between two constrained clusters can possibly become positive over the course of next agglomeration steps only if there is at least another pair of clusters in the graph that has a positive interaction $\interact{}(S_l,S_t)>0$ higher in absolute value: $|\interact{}(S_l,S_t)| > |\interact{}(S_i,S_j)|$.
+If such clusters $S_l, S_t$ with positive interaction exist, we note that they must also be constrained (in the opposite case, the algorithm would have already merged them before to constrain $S_i$ and $S_j$, because their priority is higher).
 In other words, a constrained negative interaction can become positive only if there is already another positive constrained interaction: but this can never be the case because initially all constrained interactions are negative.
@@
 Finally, we prove that \algname{} with either AbsMax or Complete linkage returns the same final clustering whether or not cannot-link constraints are enforced.
-In Algorithm \ref{detailed_alg}, the interactions between clusters are updated only when two clusters are merged and the condition at line 9 is satisfied (i.e.
+In Algorithm \ref{detailed_alg}, two clusters are merged only if the condition at line 9 is satisfied (i.e.
 when an interaction is both positive and not constrained).
@@
 From Lemma~\ref{lemma:absMax_and_complete_property} it directly follows that \algname{} with AbsMax linkage criterion returns the same final clustering whether or not cannot-link constraints are enforced.
-In the following, we prove that MWS and the constrained AbsMax version of \algname{} also return the same clustering.
+In the following, we prove that MWS (see pseudocode \ref{alg:mutex_watershed}) and the constrained AbsMax version of \algname{} also return the same clustering.
 Both algorithms sort edges in descending order of the absolute interactions $|w_e|$ and then iterate over all of them.
@@
 The constrained versions of \algname{} (HCC-Avg and HCC-Single) are also not weight-shift invariant: here, the algorithm merges or constrains clusters in a given order, depending on the absolute interactions $|\interact{}(S_i, S_j)|$ between clusters; so, when edge weights are shifted by a constant $\alpha$, the sorting by absolute value can change arbitrarily together with the agglomeration order, as we show in the counter-example of \TODO{FIG}.
-The same reasoning can also be applied to the Mutex Watershed algorithm (\algname{} with AbsMax linkage), which is clearly not weight-shift invariant (see again counter-example in \TODO{FIG}).
+Similarly, the Mutex Watershed algorithm is not weight-shift invariant because it uses a linkage criterion that compares weights by their absolute values (see again counter-example in \TODO{FIG}).
 \end{proof}
@@
 When at least two of the three nodes $u,v,t \in V$ are the same, this property follows from Eq.~\ref{eq:dist_1} and Eq.~\ref{eq:dist_2}.
-When nodes $u,v,t\in V$ are distinct, then Eq.~\ref{eq:UM_property_original} is equivalent to:
+When nodes $u,v,t\in V$ are distinct, from the definition of $d_{T}$ it follows that Eq.~\ref{eq:UM_property_original} is equivalent to:
 \begin{equation}\label{eq:UM_property}
@@
 \begin{equation}
-\interact{}_{T}(u \vee t) \geq \interact{}_{T}(v \vee t) \quad  \wedge \quad \interact{}_{T}(u \vee v) = \interact{}_{T}(v \vee t)
+\interact{}_{T}(u \vee t) \geq \interact{}_{T}(v \vee t) \quad  \text{and} \quad \interact{}_{T}(u \vee v) = \interact{}_{T}(v \vee t)
 \end{equation}
@@
 \begin{equation}
-\interact{}_{T}(u \vee v) \geq \interact{}_{T}(u \vee t) \quad  \wedge \quad \interact{}_{T}(u \vee v) \geq \interact{}_{T}(v \vee t)
+\interact{}_{T}(u \vee v) \geq \interact{}_{T}(u \vee t) \quad  \text{and} \quad \interact{}_{T}(u \vee v) \geq \interact{}_{T}(v \vee t),
 \end{equation}
-and also in this case Eq.~\ref{eq:UM_property} follows.
+so also in this case Eq.~\ref{eq:UM_property} follows.
 % for every distinct $u,v,t\in V$.
@@
 where $\Pi$ is a clustering, $\interact{}$ is a linkage criteria, and $S_1,S_2\in \Pi$ are two clusters merged by the algorithm at a given iteration.
-If this condition is true then, in the following iterations, \algname{} can only merge clusters with lower (or equal) interaction values.
+If this condition is true then, in the following iterations, \algname{} will only merge clusters with lower (or equal) interaction values.
 \item Condition 2: Positive and constrained interactions are never skipped in Phase 1 (condition at line 8 of Algorithm \ref{main_alg}) and ``delayed'' to Phase 2.
@@
 
-Finally, the remaining not constrained versions of \algname{} (HC-Avg, HC-Single, and HC-Complete) satisfy both conditions, so they define a ultrametric, confirming the well-known results of related work in hierarchical clustering on positive weighted graphs \cite{johnson1967hierarchical,milligan1979ultrametric}.
+Finally, the remaining not constrained versions of \algname{} (HC-Avg, HC-Single, and HC-Complete) satisfy both conditions, so they define a ultrametric, confirming the well-known results of related work in hierarchical clustering on unsigned graphs \cite{johnson1967hierarchical,milligan1979ultrametric}.
 
@@
 \subsection{Mutex Watershed on SSBM graphs}
-\TODO{}
+\textbf{Proposition} \\
+Consider a graph generated by an Erd\H os-R\'enyi signed stochastic block model as described in section 4 and let $S, S'$ be two clusters occurring during the agglomeration of this graph using the MWS algorithm.
+The expected probability that the MWS assigns a positive interaction to the boundary between those clusters is bounded by $\eta \leq P\big(\interact(S,S')>0\big) \leq 1-\eta$ where $\eta$ is the sign flip probability of the SSBM.
+
+\textbf{Proof} \\
+Let us write the two clusters as $S=(s_1, ..., s_k)$ and $S'=(s'_1, ..., s'_k)$ where $s_i$ indicates the number of nodes in cluster S belonging to GT-colour i.
+In the MWS algorithm the interaction $\interact(S,S')$ between the two clusters is determined only by the one edge with the highest absolute weight.
+By construction of the SSBM, every single edge in the boundary has the identical probability of having the highest absolute weight.
+The probability that the MWS assigns a positive interaction to the boundary between those cluster is therefore simply the fraction of positive weighted edges in the boundary.
+The expected total number of edges in the boundary is $E_{SS'}=p|S||S'|=p\sum_{i=1}^{k}s_i \sum_{i=1}^{k}s'_i$ where p is the probability for each individual edge to be present in the graph.
+An edge in this boundary is positive if it either connects two nodes of the same GT-colour and did not have its sign flipped or if it connects two nodes of different GT-colors and did have its sign flipped.
+We can write the expected number of positive edges as $P_{SS'}=p\big(\sum_{i=1}^{k}s_is'_i\big)(1-\eta)+p\big(\sum_{i=1}^{k}s_i \sum_{i=1}^{k}s'_i - \sum_{i=1}^{k}s_is'_i\big)\eta$.
+The expected probability can then be written as
+\begin{equation}
+    P\big(\interact(S,S')>0\big)=\eta +  \frac{\big(\sum_{i=1}^{k}s_is'_i\big)(1-2\eta)}{\sum_{i=1}^{k}s_i \sum_{i=1}^{k}s'_i}
+\end{equation}
+For $\eta <0.5$ this probability is bounded by $\eta \leq P\big(\interact(S,S')>0\big) \leq 1-\eta$. \\
+So weather we consider a merge or a split of the two clusters as the correct decision, in both cases we do not make that decision with a probability of at least $\eta$.
+Notably while the exact probabilities depend on the cluster sizes, the lower and upper bound do not.
+This confirms the intuition that the MWS, unlike Sum or Avg linkage methods, cannot properly correct for sign flip noise by agglomerating larger boundaries and profiting from the law of large numbers.
+
+\subsection{Mutex Watershed on SSBM graphs}
+\textbf{Proposition} \\
+Consider a graph generated by an Erd\H os-R\'enyi signed stochastic block model as described in section 4.
+When using the MWS algorithm, the expected probability to make a wrong decision is at least $\eta $ at every iteration, independent of the size of the considered boundary.
+
+\textbf{Proof} \\
+At any given iteration, the MWS considers the boundary between two clusters $S$ and $S'$ and either merges or splits these clusters, based on the sign of the interaction $\interact(S,S')$.
+The algorithm employs an absolute maximum linkage criterion, the interaction $\interact(S,S')$ between the two clusters is determined only by the one edge with the highest absolute weight.
+By construction of the SSBM, every single edge in the boundary has the identical probability of having the highest absolute weight.
+The probability that the MWS assigns a positive interaction to the boundary between those cluster is therefore simply the fraction of positive weighted edges in the boundary.
+\\
+Let us write the two clusters as $S=(s_1, ..., s_k)$ and $S'=(s'_1, ..., s'_k)$ where $s_i$ indicates the number of nodes in cluster S belonging to GT-colour i.
+The expected total number of edges in the boundary is $E_{SS'}=p|S||S'|=p\sum_{i=1}^{k}s_i \sum_{i=1}^{k}s'_i$ where p is the probability for each individual edge to be present in the graph.
+An edge in this boundary is positive if it either connects two nodes of the same GT-colour and did not have its sign flipped or if it connects two nodes of different GT-colors and did have its sign flipped.
+We can write the expected number of positive edges as $P_{SS'}=p\big(\sum_{i=1}^{k}s_is'_i\big)(1-\eta)+p\big(\sum_{i=1}^{k}s_i \sum_{i=1}^{k}s'_i - \sum_{i=1}^{k}s_is'_i\big)\eta$.
+The expected probability can then be written as
+\begin{equation}
+    P\big(\interact(S,S')>0\big)=\eta +  \frac{\big(\sum_{i=1}^{k}s_is'_i\big)(1-2\eta)}{\sum_{i=1}^{k}s_i \sum_{i=1}^{k}s'_i}
+\end{equation}
+For $\eta <0.5$ this probability is bounded by $\eta \leq P\big(\interact(S,S')>0\big) \leq 1-\eta$. \\
+So weather we consider a merge or a split of the two clusters as the correct decision, in both cases the expected probability to not make that decision is at least $\eta$.
+Notably while the exact probabilities depend on the cluster sizes, the lower bound does not.
+This confirms the intuition that the MWS, unlike Sum or Avg linkage methods, cannot properly correct for sign flip noise by agglomerating larger boundaries and profiting from the law of large numbers.
 

### 2021-03-13 chapters/5_experiments_intro.tex
Intregrate overleaf comments
Add new version of MWS prop on SSBM

@@
 \section{Experiments}\label{sec:neuro_segm_exp}
-\subsection{Signed graph clustering problems}
+\subsection{Signed graph clustering problems} \label{sec:clustering_problems}
 We evaluate the agglomerative clustering algorithms included in our framework on a large collection of both synthetic and real-world graphs with very different structures.
@@
 \caption{Dendrograms built by three versions of \algname{} (GAEC, MWS, and HC-Avg) on a synthetic graph generated with SSBM ($N=250$ nodes, edge probability $p=0.05$, flipping probability $\eta=0.1$).
-Red and blue colors represent the ground-truth community of each node (two communities of equal size).
+Red and blue colors represent the ground-truth community of each node (two ground-truth communities of equal size).
 At the top, dendrograms are truncated at the level of the final clustering $\Pi^*$ returned by \algname{} (y-axis shows the iteration number).

### 2021-03-13 chapters/supplementary.tex
Add new version of MWS prop on SSBM

@@
 \subsection{Mutex Watershed on SSBM graphs}
+\begin{prop}
+Consider a graph generated by an Erd\H os-R\'enyi signed stochastic block model (SSBM) as described in Section \ref{sec:clustering_problems}, with $N$ graph nodes, edges added with probability $p$, sign-flip probability $\eta$, $k$ ground-truth clusters, and edge weights Gaussian-distributed with standard deviation $\sigma$.
+Then, at every iteration, \algname{} with Absolute Maximum linkage (or, in other words, the Mutex Watershed algorithm) always makes a mistake with at least probability $\eta$.
+\end{prop}
+\begin{proof}
+Thanks to Lemma \ref{lemma:absMax_and_complete_property} we know that \algname{} with Absolute Maximum linkage returns the same clustering whether or not cannot-link-constraints are used.
+Thus, in the following, we prove the proposition considering the version enforcing constraints.
+Let us consider a generic iteration of the algorithm, where two clusters $S_\alpha$ and $S_\beta$ have the highest priority and are popped from priority queue.
+Then, the MWS algorithm will either merge or constrain them depending on the fact that their interaction $\interact_{\mathrm{AbsMax}}(S_\alpha,S_\beta)$ is  positive or negative (note that, with AbsMax linkage, an interaction can never be positive and constrained, as shown in Lemma \ref{lemma:absMax_and_complete_property}).
+By construction of the SSBM, every edge $e\in E$ in the graph has a absolute weight distributed around one: $|w_e|\sim \mathcal{N}(1,\sigma^2)$.
+Thus, every edge $e'\in(S_{\alpha} \times S_{\beta})\cap E$ connecting the two clusters has the same probability to have the highest absolute weight, and the sign of the interaction $\interact_{\mathrm{AbsMax}}(S_\alpha,S_\beta)$ will only depend on the sign of this highest edge.
+Therefore, the probability that the MWS merges two clusters is simply given by the fraction of positive weighted edges connecting them.
+
+Let $\tilde{\Pi}=\{\tilde{S}_1,\ldots,\tilde{S}_k\}$ denote the ground truth clustering, and $\tilde{S}_{\alpha i}=S_\alpha\cap \tilde{S}_i$ denote the intersection between cluster $S_{\alpha}$ and a ground-truth cluster $\tilde{S}_i$.
+If the generated graph is dense and $p=1$, then the total number of edges connecting clusters $S_{\alpha}$ and $S_{\beta}$ that have a true attractive or repulsive weight is (according to the ground truth labels):
+\begin{equation}
+\NBE^+=\sum_{i=1}^k |\tilde{S}_{\alpha i}||\tilde{S}_{\beta i}|, \quad \NBE^-=\sum_{i=1}^k \sum_{j=1,j\neq i}^k |\tilde{S}_{\alpha i}||\tilde{S}_{\beta j}|.
+\end{equation}
+When we edges in the graph are randomly added with a probability $p$, then the actual number of true attractive and repulsive interactions connecting the two clusters is (according to the ground truth labels):
+\begin{equation}
+\nBE^+ \sim \mathcal{B}(\NBE^+,p), \qquad \nBE^- \sim \mathcal{B}(\NBE^-,p), 
+\end{equation}
+where $\mathcal{B}(\NBE,p)$ is the binomial distribution:
+\begin{equation}
+\mathcal{B}(\nBE;\NBE,p) = \frac{\NBE !}{\nBE! (\NBE-\nBE)!} p^\nBE (1-p)^{\NBE-\nBE}.
+\end{equation}
+Here, we only assume that $\nBE^+ + \nBE^- >0$, i.e.
+there is at least one edge connecting the two clusters (otherwise their interaction would be zero and the MWS would not have popped them from priority queue).
+
+So far we have been talking about attractive and repulsive connections according to the ground truth labels.
+The actual number of attractive interactions connecting the two clusters will be instead given by the sum of the true attractive interactions $\nBE^+_{\mathrm{nf}}\sim \mathcal{B}(\nBE^+,1-\eta)$ that have not been flipped, plus the true negative interactions $\nBE^-_{\mathrm{f}}\sim \mathcal{B}(\nBE^-,\eta)$ that have been flipped.
+
+Putting everything together, given two clusters with $\nBE^+$ true attractive interactions and $\nBE^-$ true negative ones, the highest-absolute-weight edge connecting them has the following probability to be positive:
+\begin{align}
+ \mathbb{P}[\interact_{\mathrm{AbsMax}}&(S_\alpha,S_\beta)>0;\nBE^+,\nBE^-] = \nonumber \\
+=&\sum_{\nBE^+_{\mathrm{nf}}=0}^{\nBE^+}\sum_{\nBE^-_{\mathrm{f}}=0}^{\nBE^-} 
+\mathcal{B}(\nBE^-_{\mathrm{f}};\nBE^-,\eta) \mathcal{B}(\nBE^+_{\mathrm{nf}};\nBE^-,1-\eta)\cdot  \nonumber\\
+& \qquad \qquad  \cdot \frac{\nBE^+_{\mathrm{nf}}+\nBE^-_{\mathrm{f}}}{\nBE^+ + \nBE^-} \nonumber\\
+\stackrel{(*)}{=}&\frac{\nBE^+(1-\eta)+\nBE^-\eta}{\nBE^+ + \nBE^-}
+\end{align}  
+where in $(*)$ we used the fact that the expected value of a binomial distribution $\mathcal{B}(\nBE,\eta)$ is $\nBE \eta$.
+
+Now we note that this probability is always bounded in the interval $[\eta, 1-\eta]$ (or $[1-\eta, \eta]$, if $\eta>0.5$).
+Remarkably, these lower and upper bounds do not depend on the total number of edges $\nBE^+ + \nBE^-$ connecting the two clusters (and, thus, on the sizes of the two clusters).
+\TODO{Write conclusion} 
+% So weather we consider a merge or a split of the two clusters as the correct decision, in both cases the expected probability to not make that decision is at least $\eta$.
+Notably while the exact probabilities depend on the cluster sizes, the lower bound does not.
+This confirms the intuition that the MWS, unlike Sum or Avg linkage methods, cannot properly correct for sign flip noise by agglomerating larger boundaries and profiting from the law of large numbers.
+\end{proof}
+
+\subsection{Mutex Watershed on SSBM graphs}
 \textbf{Proposition} \\
@@
 This confirms the intuition that the MWS, unlike Sum or Avg linkage methods, cannot properly correct for sign flip noise by agglomerating larger boundaries and profiting from the law of large numbers.
-
-\subsection{Mutex Watershed on SSBM graphs}
-\textbf{Proposition} \\
-Consider a graph generated by an Erd\H os-R\'enyi signed stochastic block model as described in section 4.
-When using the MWS algorithm, the expected probability to make a wrong decision is at least $\eta $ at every iteration, independent of the size of the considered boundary.
 

### 2021-03-15 chapters/3_algorithm.tex
Comments from Steffen

@@
 The authors of \cite{levinkov2017comparative} propose an algorithm named \emph{GreedyFixation}, which, in our framework, is equivalent to phase one of \algname{} using cannot-link-constraints and a sum linkage.
-However, running both phase one and two of \algname{} with sum linkage (algorithm named HCC-Sum in this paper) performed better than GreedyFixation in our experiments, because some clusters are wrongly constrained in phase one and only merged in phase two.
+However, running both phase one and two of \algname{} with sum linkage (algorithm named HCC-Sum in this paper) performed better than GreedyFixation in our experiments.
+% , because some clusters are wrongly constrained in phase one and only merged in phase two. 
 % removing constraints in phase two   However, in our experiments, we noted that constrained sum-link version of \algname{} proposed here (named \emph{HCC-Sum} in Table~\ref{tab:linkage-criteria}) .
@@
 in Table \ref{tab:linkage-criteria}) returns the same final clustering $\Pi^*_{\mathrm{AbsMax}}$ whether or not cannot-link constraints are introduced.
-In particular, $\Pi^*_{\mathrm{AbsMax}}$ is equal to the clustering returned by the Mutex Watershed Algorithm (MWS) \cite{wolf2018mutex}, which has empirical complexity $\mathcal{O}(N \log N)$.
+Also, $\Pi^*_{\mathrm{AbsMax}}$ is equal to the clustering returned by the Mutex Watershed Algorithm (MWS) \cite{wolf2018mutex}, which has empirical complexity $\mathcal{O}(N \log N)$.
 \end{restatable}
@@
 \label{prop:weight_shift_invariant}
-We call an agglomerative algorithm ``weight-shift invariant'' if the structure of the merging tree $T$ returned by such algorithm is invariant w.r.t.
+We call an agglomerative algorithm ``weight-shift invariant'' if the structure of the merging tree $T$ returned by the algorithm is invariant w.r.t.
 a shift of all edge weights $w_e$  by a constant $\alpha\in \mathbb{R}$.
@@
 \end{restatable}
-\noindent To our knowledge, Average and Single linkage methods have never been combined with cannot-link constraints on signed graphs, so the constrained hierarchical clustering algorithms \emph{HCC-Avg} and \emph{HCC-Single} are new (see Table~\ref{tab:linkage-criteria}).
-In Lemma \ref{lemma:absMax_and_complete_property} (Appendix \ref{sec:proposition_proofs}), we prove that with a Complete linkage the agglomeration order does not change whether constraints are introduced or not.
+\noindent To our knowledge, Average and Single linkage methods have never been combined with cannot-link constraints on signed graphs, so we name these algorithms \emph{HCC-Avg} and \emph{HCC-Single}.
+In Lemma \ref{lemma:absMax_and_complete_property} (Appendix \ref{sec:proposition_proofs}), we prove that with Complete linkage the agglomeration order does not change whether constraints are introduced or not.
 

### 2021-03-15 chapters/supplementary.tex
Comments from Steffen

@@
 In phase 1, the algorithm starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a heap/priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first.
-It then iteratively pops one edge $e_{uv}$ from PQ and, depending on the priority $\tilde{\cost}_{uv}$, does the following: in case of attractive interaction $\tilde{\cost}_{uv}>0$, provided that $e_{uv}$ was not flagged as a cannot-link constraint, then merge the connected clusters, perform an edge contraction of $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and update the priorities of new double edges as explained in Fig.
+It then iteratively pops one edge $e_{uv}$ from PQ and, depending on the priority $\tilde{\cost}_{uv}$, does the following: in case of attractive interaction $\tilde{\cost}_{uv}>0$, provided that $e_{uv}$ was not flagged as a cannot-link constraint, merge the connected clusters, perform an edge contraction of $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and update the priorities of new double edges as explained in Fig.
 \ref{fig:edge_contraction_and_contr_graph}.
@@
 \begin{equation}\label{eq:UM_assumption}
- h_T(u \vee v) < h_T(u \vee t) \Rightarrow \interact{}_{T}(u,v) \geq \interact{}_{T}(u,t).
+ h_T(u \vee v) < h_T(u \vee t) \Rightarrow \interact{}_{T}(u,v) \geq \interact{}_{T}(u,t) \quad \forall u,v,t \in V.
  % h_T(u \vee v) < h_T(u \vee t) \Leftrightarrow \interact{}_{T}(u,v) > \interact{}_{T}(u,t). 
@@
 \end{equation}
-Thus, from assumption \ref{eq:UM_assumption} we have that
+Thus, from assumption (\ref{eq:UM_assumption}) we have that
 \begin{equation}
@@
 \begin{equation}
-h_T(u \vee v) < h_T(u \vee t) \quad \wedge \quad  \interact{}_{T}(u,v) < \interact{}_{T}(u,t).
+h_T(u \vee v) < h_T(u \vee t) \quad \text{and} \quad  \interact{}_{T}(u,v) < \interact{}_{T}(u,t).
 \end{equation}
@@
 \begin{prop}
-Consider a graph generated by an Erd\H os-R\'enyi signed stochastic block model (SSBM) as described in Section \ref{sec:clustering_problems}, with $N$ graph nodes, edges added with probability $p$, sign-flip probability $\eta$, $k$ ground-truth clusters, and edge weights Gaussian-distributed with standard deviation $\sigma$.
+Consider a graph generated by an Erd\H os-R\'enyi signed stochastic block model (SSBM) as described in Section \ref{sec:clustering_problems}, with $N$ nodes, edges added with probability $p$, sign-flip probability $\eta$, $k$ ground-truth clusters, and edge weights Gaussian-distributed with standard deviation $\sigma$.
 Then, at every iteration, \algname{} with Absolute Maximum linkage (or, in other words, the Mutex Watershed algorithm) always makes a mistake with at least probability $\eta$.
@@
 Then, the MWS algorithm will either merge or constrain them depending on the fact that their interaction $\interact_{\mathrm{AbsMax}}(S_\alpha,S_\beta)$ is  positive or negative (note that, with AbsMax linkage, an interaction can never be positive and constrained, as shown in Lemma \ref{lemma:absMax_and_complete_property}).
-By construction of the SSBM, every edge $e\in E$ in the graph has a absolute weight distributed around one: $|w_e|\sim \mathcal{N}(1,\sigma^2)$.
+By construction of the SSBM, every edge $e\in E$ in the graph has a absolute weight distributed as $|w_e|\sim \mathcal{N}(1,\sigma^2)$.
 Thus, every edge $e'\in(S_{\alpha} \times S_{\beta})\cap E$ connecting the two clusters has the same probability to have the highest absolute weight, and the sign of the interaction $\interact_{\mathrm{AbsMax}}(S_\alpha,S_\beta)$ will only depend on the sign of this highest edge.
@@
 The actual number of attractive interactions connecting the two clusters will be instead given by the sum of the true attractive interactions $\nBE^+_{\mathrm{nf}}\sim \mathcal{B}(\nBE^+,1-\eta)$ that have not been flipped, plus the true negative interactions $\nBE^-_{\mathrm{f}}\sim \mathcal{B}(\nBE^-,\eta)$ that have been flipped.
-
 Putting everything together, given two clusters with $\nBE^+$ true attractive interactions and $\nBE^-$ true negative ones, the highest-absolute-weight edge connecting them has the following probability to be positive:
@@
 \mathcal{B}(\nBE^-_{\mathrm{f}};\nBE^-,\eta) \mathcal{B}(\nBE^+_{\mathrm{nf}};\nBE^-,1-\eta)\cdot  \nonumber\\
-& \qquad \qquad  \cdot \frac{\nBE^+_{\mathrm{nf}}+\nBE^-_{\mathrm{f}}}{\nBE^+ + \nBE^-} \nonumber\\
+& \qquad \qquad  \cdot \left(\frac{\nBE^+_{\mathrm{nf}}+\nBE^-_{\mathrm{f}}}{\nBE^+ + \nBE^-} \right) \nonumber\\
 \stackrel{(*)}{=}&\frac{\nBE^+(1-\eta)+\nBE^-\eta}{\nBE^+ + \nBE^-}
@@
 Now we note that this probability is always bounded in the interval $[\eta, 1-\eta]$ (or $[1-\eta, \eta]$, if $\eta>0.5$).
-Remarkably, these lower and upper bounds do not depend on the total number of edges $\nBE^+ + \nBE^-$ connecting the two clusters (and, thus, on the sizes of the two clusters).
+Remarkably, these lower and upper bounds do not depend on the number of edges connecting the two clusters, i.e.
+$\nBE^+ + \nBE^-$ (and, thus, on the sizes of the two clusters).
 \TODO{Write conclusion} 

### 2021-03-16 chapters/0_abstract.tex
Rephrase proofs in appendix

@@
 \begin{abstract}
-We propose a new simple theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes.
+We propose a simple theoretical framework that generalizes simple and fast algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes.
 This framework defines GASP, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints.
@@
 We conduct a systematic comparison of various instantiations of GASP on a large variety of both synthetic and existing signed clustering problems, in terms of accuracy but also efficiency and robustness to noise.
-Lastly, we find that some of the algorithms included in our framework, when combined with the predictions from a CNN model, result in a simple bottom-up instance segmentation pipeline that achieves state-of-the-art accuracy on the CREMI 2016 EM segmentation benchmark.
-
+Lastly, we find that some of the algorithms included in our framework, when combined with the predictions from a CNN model, result in a simple bottom-up instance segmentation pipeline.
+Going all the way from pixels to final segments with a simple procedure, we achieve state-of-the-art accuracy on the CREMI 2016 EM segmentation benchmark without requiring domain-specific superpixels.
 % On stochastic block model problems, GASP compares favorably to spectral clustering. 

### 2021-03-16 chapters/1_intro.tex
Rephrase proofs in appendix

@@
 \textbf{(c)} Application of \algname{} to instance segmentation: we show raw data from the CREMI 2016 neuron-segmentation challenge and some predictions of our CNN model, where white pixels represent boundary evidence.
-\textbf{(d)} \algname{} agglomeration order for sum and average linkage: we show which pairs of neighboring pixels were merged first (white), later on (brown/red), or never (black).
+\textbf{(d)}
+Seemingly similar linkage criteria can result in very different clustering dynamics, as shown in this example: color coded sequence of merges from early (white) via late (brown) to never (black).
+% \algname{} agglomeration order for sum and average linkage: we show which pairs of neighboring pixels were merged first (white), later on (brown/red), or never (black).
 \label{fig:intro_figure}}
@@
 New constrained hierarchical clustering algorithms (HCC) proposed in this paper are highlighted in yellow.
-Algorithms typeset in bold font define an ultrametric on the graph (Eq.~\ref{eq:UM_def}).
-Algorithms included in the green box are weight-shift invariant (Prop.~\ref{prop:weight_shift_invariant}).
-    Given a signed graph $\mathcal{G}(V,E, w_e)$, we denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two clusters $S_i \subseteq V$, $S_j \subseteq V$. } 
+For algorithms typeset in bold font we prove that they define an ultrametric on the graph (Eq.~\ref{eq:UM_def}).
+For algorithms in the green box we show that they are weight-shift invariant (Prop.~\ref{prop:weight_shift_invariant}).
+    Notation: given a signed graph $\mathcal{G}(V,E, w_e)$, we denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two clusters $S_i \subseteq V$, $S_j \subseteq V$. } 
     \label{tab:linkage-criteria}
@@
 
-We evaluate the algorithms on a large variety of both existing and synthetically generated signed graph clustering problems (third contribution, Section \ref{sec:neuro_segm_exp}). 
-Finally, we also test the algorithms on \emph{instance segmentation} -- a computer vision task consisting of assigning each pixel of an image to an object instance -- by partitioning graphs whose edge weights are estimated by a CNN (fourth contribution, see Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}c} and Section \ref{sec:experiments_discussion}).
+Third, we evaluate the algorithms on a large variety of both existing and synthetically generated signed graph clustering problems (Section \ref{sec:neuro_segm_exp}). 
+Fourth and finally, we also test the algorithms on \emph{instance segmentation} -- a computer vision task consisting of assigning each pixel of an image to an object instance -- by partitioning graphs whose edge weights are estimated by a CNN (see Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}c} and Section \ref{sec:experiments_discussion}).
 Our experiments show that the choice of linkage criterion markedly influences how clusters are grown by the agglomerative algorithms (Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}d}), making some linkage methods more suited for certain types of clustering problems.

### 2021-03-16 chapters/2_rel_work.tex
Rephrase proofs in appendix

@@
 \textbf{Proposal-free instance segmentation methods} adopt a bottom-up approach by directly grouping pixels into instances.
-Recently, there has been a growing interest for such  methods that do not involve object detection, since, in certain types of data, object instances cannot be approximated by bounding boxes \cite{kirillov2017instancecut,bai2017deep}.
+Recently, there has been a growing interest in such  methods that do not involve object detection because, in certain types of data, object instances cannot be approximated by bounding boxes \cite{kirillov2017instancecut,bai2017deep}.
 % For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation, 
@@
 
-\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{arbelaez2011contour,ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts.
+\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{arbelaez2011contour,ren2013image,liu2016image,salembier2000binary} because of its efficiency as compared to other divisive approaches like graph cuts.
 Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; 
@@
 the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters. 
-The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical linkage criteria, e.g.
-average linkage \cite{liu2018affinity,lee2017superhuman}, median \cite{funke2018large} or a linkage learned by a random forest classifier \cite{nunez2013machine,knowles2016rhoananet}.
+The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical linkage criteria, e.g.~average linkage \cite{liu2018affinity,lee2017superhuman}, median \cite{funke2018large} or a linkage learned by a random forest classifier \cite{nunez2013machine,knowles2016rhoananet}.
 
@@
 
-This work reformulates the clustering algorithms of \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a generalized framework and adopt ideas from the proposal-free instance segmentation methods \cite{liu2018affinity,wolf2018mutex,lee2017superhuman} to predict edge weights of a graph.
+This work reformulates the clustering algorithms of \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a generalized framework and adopts ideas from the proposal-free instance segmentation methods \cite{liu2018affinity,wolf2018mutex,lee2017superhuman} to predict edge weights of a graph.

### 2021-03-16 chapters/3_algorithm.tex
Rephrase proofs in appendix

@@
 The instance of the NP-hard \emph{minimum cost multicut problem} w.r.t.
-$\mathcal{G}(V,E,w_e)$ is the task of finding a clustering that optimally balance the attraction and repulsion in the graph and is given by the following binary integer program:
+$\mathcal{G}(V,E,w_e)$ is the task of finding a clustering that optimally balances the attraction and repulsion in the graph and is given by the following binary integer program:
 % \begin{equation}
@@
       \State \emph{// Phase 1: Merge positive interactions (possibly using constraints)}
-      \State For all edges $e\in E$, push incident nodes of $e$ to PQ with priority $|w_e|$
+      \State Push incident nodes of every edge $e\in E$ to priority queue (PQ) with priority $|w_e|$
       \Repeat 
-        \State Pop $S,S'\in\Pi$ from $PQ$ with highest interaction $|\interact{}(S,S')|$
+        \State Pop $S,S'\in\Pi$ with highest interaction $|\interact{}(S,S')|$ from PQ
         \If{\big[{\color{green}\textbf{$\interact{}(S,S') > 0$}}\big] \textbf{and} \big[$S,S'$ \textbf{not} constrained\big]}
@@
       \Repeat 
-        \State Pop $S,S'\in\Pi$ from $PQ$ with highest interaction $\interact{}(S,S')$
+        \State Pop $S,S'\in\Pi$ with highest interaction $\interact{}(S,S')$ from PQ
         \If{\big[{\color{green}\textbf{$\interact{}(S,S') > 0$}}\big]}
@@
       \Repeat
-        \State Pop $S,S'\in\Pi$ from $PQ$ with highest interaction $\interact{}(S,S')$
+        \State Pop $S,S'\in\Pi$ with highest interaction $\interact{}(S,S')$ from PQ 
         \State Merge clusters $S$, $S'$ and update hierarchical tree $T^*$
@@
 In this paper we focus on five linkage methods (see columns of Table~\ref{tab:linkage-criteria}).
-Many more linkage criteria have been applied to unsigned graphs \cite{nunez2013machine,felzenszwalb2004efficient,funke2018large}, involving median-based or size-regularized methods, but we decided to focus this paper on those five criteria because they represent the most known choices.
+Many more linkage criteria have been applied to unsigned graphs \cite{nunez2013machine,felzenszwalb2004efficient,funke2018large}, involving median-based or size-regularized methods, but we decided to focus this paper on those five criteria because they represent the most popular choices.
 
@@
 All variations of \algname{} decrease the multicut objective defined in Eq.~\ref{eq:MC_objective} each time two clusters with positive interaction are merged.
-But only GAEC always makes the \emph{greedy-choice} that mostly decreases the multicut objective at each iteration.
+But only GAEC always makes the \emph{greedy choice} that most decreases the multicut objective at each iteration.
 The authors of \cite{levinkov2017comparative} propose an algorithm named \emph{GreedyFixation}, which, in our framework, is equivalent to phase one of \algname{} using cannot-link-constraints and a sum linkage.
@@
 \end{restatable}
+
+Now that we have defined the algorithms and managed to characterize them from a theoretical point of view, we move to empirical evaluation.
 

### 2021-03-16 chapters/5_experiments_intro.tex
Rephrase proofs in appendix

@@
         &&&& %\multicolumn{1}{c}{}
-        &\multicolumn{5}{c}{Multicut objective values associated to final clusterings (lower is better)} \\
+        &\multicolumn{5}{c}{Multicut objective values of final clusterings (average across instances, lower is better)} \\
         Clustering problem & \makecell{Graph Type} & $\#I$ & $|V|$ & $|E|$  & \multicolumn{1}{r}{GAEC \cite{keuper2015efficient}} & HCC-Sum & MWS \cite{wolf2018mutex} & HC-Avg & HCC-Avg \\ \midrule
@@
         \emph{CREMI-3D-rag (OurCNN)}  & \emph{3D-rag} & 3& 134k-157k & 928k-1065k % & \CrossedBox 
-        & \textbf{-1,112,287} & -1,112,286& -1,109,731 & -1,112,177 & -1,112,100\\ 
+        & \textbf{-1,112,287} & \textbf{-1,112,286}& -1,109,731 & -1,112,177 & -1,112,100\\ 
         \emph{Fruit-Fly Level 1-4} \cite{pape2017solving} & \emph{3D-rag} & 4& 5m-11m & 28m-72m %& \HollowBox 
@@
     \end{subtable} 
-    \caption{List of compared signed graph clustering problems: for each, we specify the number of instances $\# I$, number of nodes $|V|$, and number of edges $|E|$.
-We compare algorithms in the \algname{} framework by evaluating which of the obtained clusterings is associated to the lowest value of the multicut objective defined in Eq.~\ref{eq:MC_objective} (lower is better).}
+    \caption{List of compared signed graph clustering problems: for each, we specify the number of instances $\# I$, number of nodes $|V|$, and number of edges $|E|$ per instance.
+We compare algorithms in the \algname{} framework by their value of the multicut objective defined in Eq.~\ref{eq:MC_objective} (lower is better).}
     \label{tab:datasets_and_energies}
@@
     % \label{tab:results_cremi_test}
-    \caption{\textbf{Tables (a-b)}: Scores and run times of algorithms in the \algname{} framework on the \emph{CREMI-gridGraph} and \emph{CREMI-3D-rag} clustering problems: average linkage methods performed best.
+    \caption{\textbf{Tables (a-b)}: Scores and run times of algorithms in the \algname{} framework on the \emph{CREMI-gridGraph} and \emph{CREMI-3D-rag} clustering problems: average linkage methods achieved the best accuracy.
 Measures shown are: Adapted-Rand error (ARAND, lower is better); Variation of Information (VOI) \cite{arganda2015crowdsourcing} (VOI-merge for under-clustering error and VOI-split for over-clustering error, lower values are better).
 \textbf{Table (c)}: Current leading entries in the CREMI challenge leaderboard (March 2021).
-CREMI-score is given by geometric mean of (VOI-split + VOI-merge)  and adapted RAND error (lower is better).}
+CREMI-score is given by the geometric mean of (VOI-split + VOI-merge)  and ARAND error (lower is better).}
     \label{tab:scores}
@@
 
-\subsection{Comparison results and discussion}\label{sec:experiments_discussion}
+\subsection{Comparison of results and discussion}\label{sec:experiments_discussion}
 % Before to evaluate the clustering algorithms on real-world graphs, we compare them on two types of synthetically generated graphs and highlight some of their fundamental properties.
 
-\textbf{Multicut objective values} -- In Table~\ref{tab:datasets_and_energies}, we report the values of the multicut objective associated to the clusterings obtained with different \algname{} algorithms\footnote{Objective values achieved by Single and Complete linkage methods are much worse compared to other algorithms and are reported in Table \ref{tab:all_multicut_energies}, in Appendix.}.
-Although a lot of heuristics were proposed to better optimize this objective \cite{beier2016efficient,beier2014cut,kernighan1970efficient}, these methods are out of the scope of this paper, since they do not scale up to the largest graph instances considered here.
-By looking at results in Table~\ref{tab:datasets_and_energies}, we observe that GAEC almost always achieves the lowest objective values, apart from the \emph{CREMI-gridGraph} instances.
-Despite this, on graphs where a GT clustering is known, GAEC does not achieve the lowest ARAND errors (see Tables~\ref{tab:scores_gridGraph} and \ref{tab:scores_3drag}).
+\textbf{Multicut objective values} -- In Table~\ref{tab:datasets_and_energies}, we report the values of the multicut objective obtained for clustering with different \algname{} algorithms\footnote{Objective values achieved by Single and Complete linkage methods are much worse compared to other algorithms and are reported in Table \ref{tab:all_multicut_energies}, in Appendix.}.
+Although many heuristics were proposed to better optimize this objective \cite{beier2016efficient,beier2014cut,kernighan1970efficient}, these methods are out of the scope of this paper, since they do not scale to the largest graph instances considered here.
+By looking at results in Table~\ref{tab:datasets_and_energies}, we observe that GAEC almost always achieves the lowest objective values, expect in the \emph{CREMI-gridGraph} instances.
+Despite this, on graphs where a ground truth clustering is known, GAEC does not achieve the lowest ARAND errors (see Tables~\ref{tab:scores_gridGraph} and \ref{tab:scores_3drag}).
 % To better understand these empirical results, we now make the following important observation.
@@
 However, these methods do not scale up to the large graph instances considered here and they also require the user to specify the true number of clusters in advance, which is not known for other graph instances tested in this paper.
-In Appendix, Table \ref{tab:cremi_spectral_experiments}, we report the scores achieved by these methods on a much smaller sub-instance of the \emph{CREMI-gridGraph} problem: even when the true number of clusters is specified in advance for the spectral methods, they perform much worse than other \algname{} algorithms, with performance drop of almost 50\%.
+In Appendix, Table \ref{tab:cremi_spectral_experiments}, we report the scores achieved by these methods on a much smaller sub-instance of the \emph{CREMI-gridGraph} problem: even when the true number of clusters is specified in advance for the spectral methods, they perform much worse than other \algname{} algorithms, with an accuracy penalty of almost 50\%.
 For these reasons, we exclude them from our other comparison experiments.
@@
 % can be connected to any  that, depending on the edge-probability parameter $p$, are also \emph{dense}. 
-\algname{} algorithms using cannotLinkConstraints are not expected to perform well on these graphs, because of the type of employed flip noise, so we focus our comparison only on the GAEC, HC-Avg and MWS algorithms (using Sum, Average, and AbsMax linkage methods, respectively).
+\algname{} algorithms using cannotLinkConstraints are not expected to perform well on these graphs, because of the type of employed sign noise, so we focus our comparison only on the GAEC, HC-Avg and MWS algorithms (using Sum, Average, and AbsMax linkage methods, respectively).
 Empirically, we observe that GAEC is the agglomerative algorithm performing best on SSBM graphs, on par with spectral method SPONGE$_{sym}$ (see Fig.~\ref{fig:SSBM_scores}).
-Given the simple properties of SSBM graphs, we will now give a specific explanation of these empirical results.
+Given the simple properties of SSBM graphs, we can now give a detailed explanation of these empirical results.
 In SSBM graphs, the number of edges $E_{ij}\equiv(S_i\times S_j)\cap E$ connecting two clusters $S_i,S_j$ is  proportional to the product $|S_i|\cdot|S_j|$ of cluster sizes. 
 With Sum or Avg linkage methods, due to the law of large numbers, the flipping noise is ``averaged out'' as soon as the set $E_{ij}$ becomes larger and clusters grow in size.
-On the other hand, when clusters are small, it is more likely that several of the edges in $E_{ij}$ are flipped and the algorithm makes a mistake by merging two clusters belonging to different ground truth communities.
+On the other hand, when clusters are small, it can happen that, for few clusters, several of their edges in $E_{ij}$ are flipped and the algorithm makes a mistake by merging two clusters belonging to different ground truth communities.
 From this observation, it follows that the \emph{flooding strategy} of the sum-linkage algorithm GAEC is a very good strategy on these types of graphs, because clusters are immediately grown in size (see dendrograms in Fig.~\ref{fig:dendrograms}).
@@
 Lastly, the MWS algorithm is not expected to perform well on these graphs because of the high sensitivity of the AbsMax linkage to flipping noise.
-In Propositions \ref{prop:MWS_SSBM_1} and \ref{prop:MWS_SSBM_2} (see \TODO{Appendix}), we prove that on SSBM graphs the merging steps of the MWS algorithm are given by a sequence of ``coin flip'' decisions with a probability proportional to the noise parameter $\eta$, independently on the cluster sizes.
+In Proposition \ref{prop:MWS_on_SSBM} (see Appendix), we prove that, at every iteration, the MWS algorithm makes a mistake with at least probability $\eta$, independently on the sizes of the two clusters that are popped from priority queue.
+In summary, for the SSBM, we can obtain a deep understanding of the dynamics induced by various linkage criteria, and find that GAEC gives highest accuracy by a large margin.
 
 \textbf{Complete and Single Linkage} -- We use these two linkage methods as baselines to highlight the difficulty of the studied graph clustering problems listed in Table~\ref{tab:datasets_and_energies}.
-Scores in Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show their poor performances: Single linkage hierarchical clustering (HC-Single), which here is equivalent to thresholding the edge weights at $w_e=0$ and computing connected components in the graph, often returned few big under-segmented clusters.
+Scores in Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show their poor performance: Single linkage hierarchical clustering (HC-Single), which here is equivalent to thresholding the edge weights at $w_e=0$ and computing connected components in the graph, often returned few big under-segmented clusters.
 HC-Complete returned instead a lot of over-segmented clusters.
@@
 \textbf{Scores on CREMI instance-segmentation} -- 
-SSBM graphs are \emph{non-planar}, where every edge has the same probability to be present in the graph.
-On the other hand, the \emph{gridGraph} and \emph{3D-rag} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: weather a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance).
-Tables~\ref{tab:scores_3drag}-\ref{tab:scores_gridGraph} show that average linkage methods (HC-Avg, HCC-Avg) strongly outperforms other methods on \emph{CREMI-gridGraph} instances and also achieves the best scores on \emph{CREMI-3D-rag} graphs.
+SSBM graphs are \emph{non-planar}, and every edge has the same probability to be present in the graph.
+On the other hand, the \emph{gridGraph} and \emph{3D-rag} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: regardless of whether a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance).
+Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show that average linkage methods (HC-Avg, HCC-Avg) strongly outperform other methods on \emph{CREMI-gridGraph} instances and also achieve the best scores on \emph{CREMI-3D-rag} graphs.
 Sum-based linkage methods (GAEC, HCC-Sum) do not perform well on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}).
@@
 \includegraphics[width=0.48\textwidth,trim=80 10 60 0, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
-\caption{Dendrograms built by three versions of \algname{} (GAEC, MWS, and HC-Avg) on a synthetic graph generated with SSBM ($N=250$ nodes, edge probability $p=0.05$, flipping probability $\eta=0.1$).
-Red and blue colors represent the ground-truth community of each node (two ground-truth communities of equal size).
-At the top, dendrograms are truncated at the level of the final clustering $\Pi^*$ returned by \algname{} (y-axis shows the iteration number).
+\caption{Clustering dynamics and accuracy of GASP variations on stochastic block models.
+The dendrograms result from three versions of \algname{} (GAEC, MWS, and HC-Avg) on a synthetic graph generated with SSBM ($N=250$ nodes, edge probability $p=0.05$, flipping probability $\eta=0.1$).
+Red and blue colors show which of the two equal-sized ground-truth communities each node belongs to.
+At the top, dendrograms are truncated at the level of the final clustering $\Pi^*$ returned by \algname{}.
 \label{fig:dendrograms}}
@@
 \textbf{Results on CREMI challenge} -- 
-Table~\ref{tab:cremi_leaderboard} shows that the HCC-Avg and HC-Avg clustering algorithms achieve state-of-the-art performances on the CREMI challenge, when combined to the predictions of our CNN.
+Table~\ref{tab:cremi_leaderboard} shows that the HCC-Avg and HC-Avg clustering algorithms achieve state-of-the-art performances on the CREMI challenge, when combined with predictions of our CNN.
 Most of the other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs.
@@
 However, our method operating directly on pixels (\emph{gridGraph+HCC-Avg}) achieves better performances than superpixel-based methods (\emph{3D-rag+HCC-Avg}) and does not require the parameter tuning necessary to obtain good super-pixels, which is usually highly dataset dependent.
-The method \emph{3D-rag+LiftedMulticut} based on the lifted multicut approximation of \cite{beier2017multicut} achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and super-pixel shape information.
 To scale up our method operating on pixels, we divided each test-volume into four sub-blocks, and then combined the resulting clusterings by running the algorithms again on the combined graph.
+The method \emph{3D-rag+LiftedMulticut} based on the lifted multicut approximation of \cite{beier2017multicut} achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and shape information from highly engineered super-pixels.
 % Note that the test volumes of the challenge contain several imaging artifacts that make segmentation particularly challenging.
@@
 \caption{Failure cases of three versions of \algname{} (GAEC, MWS, and HC-Avg) applied to neuron segmentation.
-\emph{Wrongly} segmented regions are highlighted in different warm colors.
-Red arrows point to wrongly split regions; yellow arrows point to merge errors.
+Only \emph{wrongly} segmented regions are highlighted in different warm colors.
+Red arrows point to wrongly split regions; yellow arrows point to false merge errors.
 HC-Avg returned the best segmentation.

### 2021-03-16 chapters/6_conclusions.tex
Rephrase proofs in appendix

@@
 \section{Conclusion}
-We have presented an unifying framework for agglomerative clustering of graphs with both positive and negative edge weights; and we have shown that some existing clustering algorithms, e.g.
+We have presented a unifying framework for agglomerative clustering of graphs with both positive and negative edge weights; and we have shown that some existing clustering algorithms, e.g.
 the Mutex Watershed, can be reformulated as special cases of this framework.

### 2021-03-16 chapters/supplementary.tex
Rephrase proofs in appendix

@@
 In Phases 2 and 3, \algname{} is equivalent to a standard hierarchical agglomerative clustering algorithm with complexity $\mathcal{O}(N^2 \log N)$.
-In Algorithm \ref{detailed_alg}, we show our implementation of Phase 1, involving cannot-link constraints.
+In Algorithm \ref{detailed_alg}, we show our implementation of phase 1, involving cannot-link constraints.
 In phase 1, the algorithm starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a heap/priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first.
@@
 
-\subsection{Proofs of Propositions \ref{prop:absmax_mutex}, \ref{prop:weight_shift_invariant}, \ref{prop:ultraMetric1}, and \ref{prop:ultraMetric2}  }
+\subsection{Proofs of Propositions \ref{prop:absmax_mutex}, \ref{prop:weight_shift_invariant}, \ref{prop:ultraMetric1}, and \ref{prop:ultraMetric2}}
 \label{sec:proposition_proofs}
-% \subsubsection{Mutex Watershed and AbsMax linkage}\label{sec:appendix_abs_max}
-\begin{lemma} \label{lemma:absMax_and_complete_property}
-Let us consider the \algname{} Algorithm \ref{main_alg} with AbsMax or Complete linkage criteria (see linkage definition in Table \ref{tab:linkage-criteria}).
-If the algorithm enforces a constraint between two clusters in \emph{Phase 1}, then the interaction between the clusters will never become positive over the course of the following agglomeration steps.
-Moreover, we also have that with any of these two linkages: i) \algname{} returns the same final clustering whether or not cannot-link constraints are enforced; ii) no clusters are merged in \emph{Phase 2} (after constraints have been removed).
+
+\begin{lemma} \label{lemma:absMax_and_complete_not_positive}
+If \algname{} Algorithm \ref{main_alg} with \textbf{Complete linkage criteria} enforces a constraint between two clusters in \emph{Phase 1}, then the interaction between the clusters will never become positive over the course of the following agglomeration steps.
 \end{lemma}
 \begin{proof}
-First, we note that two clusters are constrained in \emph{Phase 1} only if their interaction is repulsive.
-We then also observe that with complete linkage (see Table~\ref{tab:linkage_criteria_explicit}) the signed interaction between two clusters can only decrease over the course of the agglomeration.
+Two clusters are constrained in \emph{Phase 1} only if their interaction is repulsive and, with complete linkage,  the signed interaction between two clusters can only decrease over the course of the agglomeration.
 Thus, if two clusters are constrained by the algorithm, their negative interaction cannot increase and become positive later on in the agglomeration process.
+\end{proof}
 
-If, on the other hand, we consider \algname{} with a Absolute Maximum linkage (see Table~\ref{tab:linkage_criteria_explicit}), during the agglomeration the interaction between two clusters can only increase in absolute value.
+\begin{lemma} \label{lemma:absMax_and_complete_not_positive}
+If \algname{} Algorithm \ref{main_alg} with \textbf{AbsMax linkage criteria} enforces a constraint between two clusters in \emph{Phase 1}, then the interaction between the clusters will never become positive over the course of the following agglomeration steps.
+\end{lemma}
+\begin{proof}
+During the agglomeration the interaction between two clusters can only increase in absolute value.
 Thus, the negative interaction $\interact{}(S_i,S_j)<0$ between two constrained clusters can possibly become positive over the course of next agglomeration steps only if there is at least another pair of clusters in the graph that has a positive interaction $\interact{}(S_l,S_t)>0$ higher in absolute value: $|\interact{}(S_l,S_t)| > |\interact{}(S_i,S_j)|$.
@@
 In other words, a constrained negative interaction can become positive only if there is already another positive constrained interaction: but this can never be the case because initially all constrained interactions are negative.
+\end{proof}
 
-Finally, we prove that \algname{} with either AbsMax or Complete linkage returns the same final clustering whether or not cannot-link constraints are enforced.
-In Algorithm \ref{detailed_alg}, two clusters are merged only if the condition at line 9 is satisfied (i.e.
+\begin{lemma} \label{lemma:absMax_and_complete_property}
+In the \algname{} Algorithm \ref{main_alg} with AbsMax or Complete linkage criteria (see linkage definition in Table \ref{tab:linkage-criteria}), the same final clustering is returned whether or not cannot-link constraints are enforced.
+\end{lemma}
+\begin{proof}
+In phase 1 of Algorithm \ref{detailed_alg}, two clusters are merged only if the condition at line 9 is satisfied (i.e.
 when an interaction is both positive and not constrained).
-However, we have just shown that with these two linkage methods an interaction can never be both positive and constrained at the same time, so we directly conclude that the constrained and unconstrained versions of the algorithm will perform precisely the same agglomeration steps.
+From Lemma \ref{lemma:absMax_and_complete_not_positive} and Lemma \ref{lemma:absMax_and_complete_not_positive} follows that with Complete and AbsMax linkage an interaction can never be both positive and constrained at the same time, so we directly conclude that the constrained and unconstrained versions of the algorithm will perform precisely the same agglomeration steps in phase 1.
+In phase 2 (after constraints have been removed) no clusters are merged because all interactions are already negative (whether they previously constrained or not).
+Thus, both constrained and unconstrained versions of \algname{} return the same clustering $\Pi^*$.
 \end{proof}
@@
 The same is not true for \algname{} with Sum linkage criteria (GAEC and HCC-Sum), because by adding a constant $\alpha$ to all edge weights $w_e$, the interaction between two clusters $S_i$ and $S_j$ is increased by a factor $\alpha |E_{ij}|$, which depends on the number of edges  $|E_{ij}|$ connecting the two clusters.
-Thus, when all edge weighs of the graph are shifted, the agglomeration order may change, as we show in the counter-example of \TODO{FIG}.
+Thus, when all edge weighs of the graph are shifted, the agglomeration order may change.
+For a simple example of this, it is enough to consider the toy graph in Fig.~\ref{fig:intro_figure}a and shift the weights of the graph by $\alpha=-3$ (see Fig.~\ref{fig:counter_examples_shift_inv_GAEC}).
 
-The constrained versions of \algname{} (HCC-Avg and HCC-Single) are also not weight-shift invariant: here, the algorithm merges or constrains clusters in a given order, depending on the absolute interactions $|\interact{}(S_i, S_j)|$ between clusters; so, when edge weights are shifted by a constant $\alpha$, the sorting by absolute value can change arbitrarily together with the agglomeration order, as we show in the counter-example of \TODO{FIG}.
-Similarly, the Mutex Watershed algorithm is not weight-shift invariant because it uses a linkage criterion that compares weights by their absolute values (see again counter-example in \TODO{FIG}).
+The constrained versions of \algname{} (HCC-Avg and HCC-Single) are also not weight-shift invariant: here, the algorithm merges or constrains clusters in a given order, depending on the absolute interactions $|\interact{}(S_i, S_j)|$ between clusters; so, when edge weights are shifted by a constant $\alpha$, the sorting by absolute value can change arbitrarily together with the agglomeration order, as we show in the counter-example of Fig.~\ref{fig:counter_examples_shift_inv}.
+Similarly, the Mutex Watershed algorithm is not weight-shift invariant because it uses a linkage criterion that compares weights by their absolute values (see again counter-example in Fig.~\ref{fig:counter_examples_shift_inv}.
 \end{proof}
@@
 In formulae, this is equivalent to saying that, $\forall u,v,t \in V$:
-\begin{equation}\label{eq:UM_assumption}
- h_T(u \vee v) < h_T(u \vee t) \Rightarrow \interact{}_{T}(u,v) \geq \interact{}_{T}(u,t) \quad \forall u,v,t \in V.
+\begin{gather}
+\forall u,v,t \in V \nonumber \\
+ h_T(u \vee v) < h_T(u \vee t) \Rightarrow \interact{}_{T}(u,v) \geq \interact{}_{T}(u,t) \label{eq:UM_assumption}
  % h_T(u \vee v) < h_T(u \vee t) \Leftrightarrow \interact{}_{T}(u,v) > \interact{}_{T}(u,t). 
-\end{equation}
+\end{gather}
 In words, condition \ref{eq:UM_assumption} means: if the algorithm merges nodes $u,v$ before to merge nodes $u,t$, then the signed interaction $\interact{}_{T}(u,v)$ between $u$ and $v$ has to be higher or equal than $\interact{}_{T}(u,t)$.
@@
 
-From the definition of $d_{T}$, we have that:
+From the definition of $d_{T}$, it follows that:
 \begin{align}
@@
 d_{T}(u,v) &\geq 0 \qquad &\forall u,v \in V \label{eq:dist_2}\\
-d_{T}(u,v)& =d_{T}(v,u) \qquad &\forall u,v \in V \label{eq:dist_3}
+d_{T}(u,v)& =d_{T}(v,u) \qquad &\forall u,v \in V. \label{eq:dist_3}
 \end{align}
  % $d_{T}(u,v)=d_{T}(v,u)$, $d_{T}(u,u)= 0$, and $d_{T}(u,v)\geq 0$ for each $u,v \in V$.
-Thus, to show that $(V, d_{T})$ is an ultrametric, we only need to prove the ultrametric property:
+In order to show that $(V, d_{T})$ is an ultrametric, we only need to prove the ultrametric property:
 \begin{equation}\label{eq:UM_property_original}
@@
 Let us assume that $t$ is first merged with $u$ (the following proof also holds for the opposite case in which $t$ is first merged with $v$):
-\begin{equation}
+\begin{equation}\label{eq:case_1}
 h_T(u \vee t) < h_T(u \vee v) = h_T(v \vee t).
 \end{equation}
-Thus, from assumption (\ref{eq:UM_assumption}) we have that
+Thus, by combining the last equation with assumption (\ref{eq:UM_assumption}), it follows that
 \begin{equation}
@@
 To prove this statement, we first rephrase it in the following equivalent form: if assumption \ref{eq:UM_assumption} does not hold, then $(V, d_{T})$ is not an ultrametric and \ref{eq:UM_property} does not hold.
-The negation of assumption \ref{eq:UM_assumption} is
+If we negate assumption \ref{eq:UM_assumption}, there must be at least three $u,v,t \in V$ such that:
 \begin{equation}
@@
 
-Finally, the remaining not constrained versions of \algname{} (HC-Avg, HC-Single, and HC-Complete) satisfy both conditions, so they define a ultrametric, confirming the well-known results of related work in hierarchical clustering on unsigned graphs \cite{johnson1967hierarchical,milligan1979ultrametric}.
+Finally, the remaining not constrained versions of \algname{} (HC-Avg, HC-Single, and HC-Complete) satisfy both conditions, so they define an ultrametric, confirming the well-known results of related work in hierarchical clustering on unsigned graphs \cite{johnson1967hierarchical,milligan1979ultrametric}.
 
@@
 
+\begin{figure}[t]
+% \begin{subfigure}[t]{0.48\textwidth}
+\centering
+\includegraphics[width=0.48\textwidth,trim=0in 0in 0in 0in,clip]{./figs/counter-examples/counter-example-GAEC.pdf}
+% \caption{Original graph and dendrogram}
+% \end{subfigure}
+
+% \vspace{2em}
+% \begin{subfigure}[t]{0.48\textwidth}
+% \centering
+% \includegraphics[width=\textwidth,trim=0in 0in 0in 0in,clip]{./figs/counter-examples/counter-example-GAEC-shifted.pdf}
+% \caption{Graph with shifted edge-weights ($\alpha=-3$) and GAEC dendrogram}
+% \end{subfigure}
+        \caption{ Counter-example showing that GAEC is not weight-shift invariant.
+        } \label{fig:counter_examples_shift_inv_GAEC}
+\end{figure}
+\begin{figure}[t!]
+% \begin{subfigure}[t]{0.48\textwidth}
+\centering
+\includegraphics[width=0.48\textwidth,trim=0in 0in 0in 0in,clip]{./figs/counter-examples/counter-example.pdf}
+% \caption{Original graph and dendrogram}
+% \end{subfigure}
+
+% \vspace{2em}
+% \begin{subfigure}[t]{0.48\textwidth}
+% \centering
+% \includegraphics[width=\textwidth,trim=0in 0in 0in 0in,clip]{./figs/counter-examples/counter-example-shifted.pdf}
+% \caption{Graph with shifted edge-weights ($\alpha=+2$) and dendrogram}
+% \end{subfigure}
+        \caption{ Counter-example showing that HCC-Sum, MWS, HCC-Avg, and HCC-Single are not weight-shift invariant.
+        } \label{fig:counter_examples_shift_inv}
+\end{figure}
+
 \subsection{Mutex Watershed on SSBM graphs}
-\begin{prop}
-Consider a graph generated by an Erd\H os-R\'enyi signed stochastic block model (SSBM) as described in Section \ref{sec:clustering_problems}, with $N$ nodes, edges added with probability $p$, sign-flip probability $\eta$, $k$ ground-truth clusters, and edge weights Gaussian-distributed with standard deviation $\sigma$.
+\begin{prop} \label{prop:MWS_on_SSBM}
+Consider a graph generated by an Erd\H os-R\'enyi signed stochastic block model (SSBM) as described in Section \ref{sec:clustering_problems}, with $N$ nodes, edges added with probability $p$, sign-flip probability $\eta<0.5$, $k$ ground-truth clusters, and edge weights Gaussian-distributed with standard deviation $\sigma$.
 Then, at every iteration, \algname{} with Absolute Maximum linkage (or, in other words, the Mutex Watershed algorithm) always makes a mistake with at least probability $\eta$.
@@
 Let $\tilde{\Pi}=\{\tilde{S}_1,\ldots,\tilde{S}_k\}$ denote the ground truth clustering, and $\tilde{S}_{\alpha i}=S_\alpha\cap \tilde{S}_i$ denote the intersection between cluster $S_{\alpha}$ and a ground-truth cluster $\tilde{S}_i$.
-If the generated graph is dense and $p=1$, then the total number of edges connecting clusters $S_{\alpha}$ and $S_{\beta}$ that have a true attractive or repulsive weight is (according to the ground truth labels):
+If the generated graph is dense, i.e.
+$p=1$, then the total number of edges connecting clusters $S_{\alpha}$ and $S_{\beta}$ that have a true attractive or repulsive weight is (according to the ground truth labels)
 \begin{equation}
@@
 \end{equation}
-When we edges in the graph are randomly added with a probability $p$, then the actual number of true attractive and repulsive interactions connecting the two clusters is (according to the ground truth labels):
+When the edges in the graph are randomly added with a probability $p$, then the actual number of true attractive and repulsive interactions connecting the two clusters is (according to the ground truth labels):
 \begin{equation}
@@
 So far we have been talking about attractive and repulsive connections according to the ground truth labels.
-The actual number of attractive interactions connecting the two clusters will be instead given by the sum of the true attractive interactions $\nBE^+_{\mathrm{nf}}\sim \mathcal{B}(\nBE^+,1-\eta)$ that have not been flipped, plus the true negative interactions $\nBE^-_{\mathrm{f}}\sim \mathcal{B}(\nBE^-,\eta)$ that have been flipped.
+In our SSBM however every edge has a uniform probability $\eta$ to have its sign flip, so  the actual number of attractive interactions connecting the two clusters will be instead given by the sum of the true attractive interactions $\nBE^+_{\mathrm{nf}}\sim \mathcal{B}(\nBE^+,1-\eta)$ that have not been flipped, plus the true negative interactions $\nBE^-_{\mathrm{f}}\sim \mathcal{B}(\nBE^-,\eta)$ that have been flipped.
 Putting everything together, given two clusters with $\nBE^+$ true attractive interactions and $\nBE^-$ true negative ones, the highest-absolute-weight edge connecting them has the following probability to be positive:
-\begin{align}
+\begin{align}\label{eq:mws_prob}
  \mathbb{P}[\interact_{\mathrm{AbsMax}}&(S_\alpha,S_\beta)>0;\nBE^+,\nBE^-] = \nonumber \\
@@
 
-Now we note that this probability is always bounded in the interval $[\eta, 1-\eta]$ (or $[1-\eta, \eta]$, if $\eta>0.5$).
+%Now we note that this probability is always bounded in the interval $[\eta, 1-\eta]$ (or $[1-\eta, \eta]$, if $\eta>0.5$).
 Remarkably, these lower and upper bounds do not depend on the number of edges connecting the two clusters, i.e.
 $\nBE^+ + \nBE^-$ (and, thus, on the sizes of the two clusters).
-\TODO{Write conclusion} 
+Now we note that this probability is bounded in the interval $[\eta, 1-\eta]$.
+So, regardless of whether the two clusters $S_\alpha$ and $S_\beta$ should be merged or constraint according to ground truth labels, the probability not to make the correct decision is always at least $\eta$.
 % So weather we consider a merge or a split of the two clusters as the correct decision, in both cases the expected probability to not make that decision is at least $\eta$.
@@
 This confirms the intuition that the MWS, unlike Sum or Avg linkage methods, cannot properly correct for sign flip noise by agglomerating larger boundaries and profiting from the law of large numbers.
+Remarkably, while the exact probability in Eq.~\ref{eq:mws_prob} depends on the number of edges connecting the two clusters $\nBE^++\nBE^-$ and thus on the cluster sizes, the bounds do not.
+Thus, this result shows that, unlike Sum or Avg linkage methods, the MWS algorithm is unable to reliably correct for the sign flip noise even for big clusters linked by many edges.
 \end{proof}
 
-\subsection{Mutex Watershed on SSBM graphs}
-\textbf{Proposition} \\
-Consider a graph generated by an Erd\H os-R\'enyi signed stochastic block model as described in section 4 and let $S, S'$ be two clusters occurring during the agglomeration of this graph using the MWS algorithm.
+% \subsection{Mutex Watershed on SSBM graphs}
+% \textbf{Proposition} \\
+% Consider a graph generated by an Erd\H os-R\'enyi signed stochastic block model as described in section 4 and let $S, S'$ be two clusters occurring during the agglomeration of this graph using the MWS algorithm.
 The expected probability that the MWS assigns a positive interaction to the boundary between those clusters is bounded by $\eta \leq P\big(\interact(S,S')>0\big) \leq 1-\eta$ where $\eta$ is the sign flip probability of the SSBM.
 
-\textbf{Proof} \\
-Let us write the two clusters as $S=(s_1, ..., s_k)$ and $S'=(s'_1, ..., s'_k)$ where $s_i$ indicates the number of nodes in cluster S belonging to GT-colour i.
+% \textbf{Proof} \\
+% Let us write the two clusters as $S=(s_1, ..., s_k)$ and $S'=(s'_1, ..., s'_k)$ where $s_i$ indicates the number of nodes in cluster S belonging to GT-colour i.
 In the MWS algorithm the interaction $\interact(S,S')$ between the two clusters is determined only by the one edge with the highest absolute weight.
@@
 The probability that the MWS assigns a positive interaction to the boundary between those cluster is therefore simply the fraction of positive weighted edges in the boundary.
+% The expected total number of edges in the boundary is $E_{SS'}=p|S||S'|=p\sum_{i=1}^{k}s_i \sum_{i=1}^{k}s'_i$ where p is the probability for each individual edge to be present in the graph.
+An edge in this boundary is positive if it either connects two nodes of the same GT-colour and did not have its sign flipped or if it connects two nodes of different GT-colors and did have its sign flipped.
+We can write the expected number of positive edges as $P_{SS'}=p\big(\sum_{i=1}^{k}s_is'_i\big)(1-\eta)+p\big(\sum_{i=1}^{k}s_i \sum_{i=1}^{k}s'_i - \sum_{i=1}^{k}s_is'_i\big)\eta$.
+The expected probability can then be written as
+% \begin{equation}
+%     P\big(\interact(S,S')>0\big)=\eta +  \frac{\big(\sum_{i=1}^{k}s_is'_i\big)(1-2\eta)}{\sum_{i=1}^{k}s_i \sum_{i=1}^{k}s'_i}
+% \end{equation}
+% For $\eta <0.5$ this probability is bounded by $\eta \leq P\big(\interact(S,S')>0\big) \leq 1-\eta$. \\
+% So weather we consider a merge or a split of the two clusters as the correct decision, in both cases we do not make that decision with a probability of at least $\eta$.
+Notably while the exact probabilities depend on the cluster sizes, the lower and upper bound do not.
+This confirms the intuition that the MWS, unlike Sum or Avg linkage methods, cannot properly correct for sign flip noise by agglomerating larger boundaries and profiting from the law of large numbers.
+
+% \textbf{Proof} \\
+% At any given iteration, the MWS considers the boundary between two clusters $S$ and $S'$ and either merges or splits these clusters, based on the sign of the interaction $\interact(S,S')$.
+The algorithm employs an absolute maximum linkage criterion, the interaction $\interact(S,S')$ between the two clusters is determined only by the one edge with the highest absolute weight.
+By construction of the SSBM, every single edge in the boundary has the identical probability of having the highest absolute weight.
+The probability that the MWS assigns a positive interaction to the boundary between those cluster is therefore simply the fraction of positive weighted edges in the boundary.
+\\
+% Let us write the two clusters as $S=(s_1, ..., s_k)$ and $S'=(s'_1, ..., s'_k)$ where $s_i$ indicates the number of nodes in cluster S belonging to GT-colour i.
 The expected total number of edges in the boundary is $E_{SS'}=p|S||S'|=p\sum_{i=1}^{k}s_i \sum_{i=1}^{k}s'_i$ where p is the probability for each individual edge to be present in the graph.
@@
 The expected probability can then be written as
-\begin{equation}
-    P\big(\interact(S,S')>0\big)=\eta +  \frac{\big(\sum_{i=1}^{k}s_is'_i\big)(1-2\eta)}{\sum_{i=1}^{k}s_i \sum_{i=1}^{k}s'_i}
-\end{equation}
-For $\eta <0.5$ this probability is bounded by $\eta \leq P\big(\interact(S,S')>0\big) \leq 1-\eta$. \\
-So weather we consider a merge or a split of the two clusters as the correct decision, in both cases we do not make that decision with a probability of at least $\eta$.
-Notably while the exact probabilities depend on the cluster sizes, the lower and upper bound do not.
-This confirms the intuition that the MWS, unlike Sum or Avg linkage methods, cannot properly correct for sign flip noise by agglomerating larger boundaries and profiting from the law of large numbers.
-
-\textbf{Proof} \\
-At any given iteration, the MWS considers the boundary between two clusters $S$ and $S'$ and either merges or splits these clusters, based on the sign of the interaction $\interact(S,S')$.
-The algorithm employs an absolute maximum linkage criterion, the interaction $\interact(S,S')$ between the two clusters is determined only by the one edge with the highest absolute weight.
-By construction of the SSBM, every single edge in the boundary has the identical probability of having the highest absolute weight.
-The probability that the MWS assigns a positive interaction to the boundary between those cluster is therefore simply the fraction of positive weighted edges in the boundary.
-\\
-Let us write the two clusters as $S=(s_1, ..., s_k)$ and $S'=(s'_1, ..., s'_k)$ where $s_i$ indicates the number of nodes in cluster S belonging to GT-colour i.
-The expected total number of edges in the boundary is $E_{SS'}=p|S||S'|=p\sum_{i=1}^{k}s_i \sum_{i=1}^{k}s'_i$ where p is the probability for each individual edge to be present in the graph.
-An edge in this boundary is positive if it either connects two nodes of the same GT-colour and did not have its sign flipped or if it connects two nodes of different GT-colors and did have its sign flipped.
-We can write the expected number of positive edges as $P_{SS'}=p\big(\sum_{i=1}^{k}s_is'_i\big)(1-\eta)+p\big(\sum_{i=1}^{k}s_i \sum_{i=1}^{k}s'_i - \sum_{i=1}^{k}s_is'_i\big)\eta$.
-The expected probability can then be written as
-\begin{equation}
-    P\big(\interact(S,S')>0\big)=\eta +  \frac{\big(\sum_{i=1}^{k}s_is'_i\big)(1-2\eta)}{\sum_{i=1}^{k}s_i \sum_{i=1}^{k}s'_i}
-\end{equation}
-For $\eta <0.5$ this probability is bounded by $\eta \leq P\big(\interact(S,S')>0\big) \leq 1-\eta$. \\
-So weather we consider a merge or a split of the two clusters as the correct decision, in both cases the expected probability to not make that decision is at least $\eta$.
+% \begin{equation}
+%     P\big(\interact(S,S')>0\big)=\eta +  \frac{\big(\sum_{i=1}^{k}s_is'_i\big)(1-2\eta)}{\sum_{i=1}^{k}s_i \sum_{i=1}^{k}s'_i}
+% \end{equation}
+% For $\eta <0.5$ this probability is bounded by $\eta \leq P\big(\interact(S,S')>0\big) \leq 1-\eta$. \\
+% So weather we consider a merge or a split of the two clusters as the correct decision, in both cases the expected probability to not make that decision is at least $\eta$.
 Notably while the exact probabilities depend on the cluster sizes, the lower bound does not.
@@
 that these kinds of augmentations can help to alleviate issues caused by EM-imaging artifacts.
-We use L2 loss and Adam optimizer to train the network. The model was trained on all the three samples with available ground truth labels.
+We use L2 loss and Adam optimizer to train the network. The model was trained on all three samples with available ground truth labels.
 
 \paragraph{CREMI-gridRag instances} 
-Our 3D UNet model predicts the same set of 12 long-and-short range affinities described in \cite{lee2017superhuman}. 
+Our 3D UNet model predicts the same set of 12 long-and-short range affinities as described in \cite{lee2017superhuman}. 
 When building the pixel-grid graph, we add both direct neighbors connections and the long-range connections predicted by our model (every voxel is connected to other six voxels via direct connections and other 18 voxels via long-range edges).

### 2021-03-16 chapters/1_intro.tex
Integrate last Fred's comments

@@
 \centering
-\includegraphics[width=0.98\textwidth]{figs/intro_image_v6.pdf} % left bottom right top
-\caption{\textbf{(a)} Some iterations of \algname{}, the proposed Generalized Agglomerative Algorithm for Signed Graph Partitioning, on a toy graph with attractive/positive (green) and repulsive/negative (red) interactions.
-At each iteration, the yellow edge with highest interaction is contracted.
-An example with sum linkage criterion is shown.
-\textbf{(b)} List of linkage criteria used in this paper (see definitions in Table~\ref{tab:linkage-criteria} below), demonstrated on two small clusters.
-\textbf{(c)} Application of \algname{} to instance segmentation: we show raw data from the CREMI 2016 neuron-segmentation challenge and some predictions of our CNN model, where white pixels represent boundary evidence.
+\includegraphics[width=0.92\textwidth]{figs/intro_image_v6.pdf} % left bottom right top
+\caption{\textbf{(a)} Some iterations of \algname{} on a graph with attractive (green) and repulsive (red) interactions.
+At each iteration, the yellow edge with highest interaction is contracted (example with sum linkage criterion is shown).
+\textbf{(b)} Linkage criteria used in this paper demonstrated on two small clusters (see definitions in Table~\ref{tab:linkage-criteria} below).
+\textbf{(c)} Application of \algname{} to instance segmentation: we show raw data from the CREMI neuron-segmentation challenge and some predictions of our CNN model, where white pixels represent boundary evidence.
 \textbf{(d)}
@@
 For algorithms in the green box we show that they are weight-shift invariant (Prop.~\ref{prop:weight_shift_invariant}).
-    Notation: given a signed graph $\mathcal{G}(V,E, w_e)$, we denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two clusters $S_i \subseteq V$, $S_j \subseteq V$. } 
+    Notation: 
+    % given a signed graph $\mathcal{G}(V,E, w_e)$, we denote as 
+    $E_{ij}=(S_i \times S_{j}) \cap E$ denotes the set of edges connecting two clusters $S_i, S_j \subseteq V$. } 
     \label{tab:linkage-criteria}
@@
 As second contribution, in Section \ref{sec:alg_update_rules}, we formally prove that some of the combinations correspond to existing clustering algorithms, and introduce new algorithms for combinations which have not been explored before.
-By analyzing their theoretical properties, we also show which ones define an ultrametric on the graph (see Table~\ref{tab:linkage-criteria}).
+By analyzing their theoretical properties, we also show that some of them define an ultrametric on the graph (see Table~\ref{tab:linkage-criteria}).
 

### 2021-03-16 chapters/3_algorithm.tex
Integrate last Fred's comments

@@
 \paragraph{Average, Single, and Complete Linkage} -- These three linkage criteria have been throughly studied on unsigned graphs, but never on signed graphs.
-In the recent related work \cite{chehreghani2020hierarchical}, the authors prove that applying these three linkage methods to a signed graph is equivalent to applying them to the unsigned graph obtained by shifting all edge weights by a constant.
-Here, we prove which of the algorithms included in our generalized framework have this invariance-property:
+In recent independent related work \cite{chehreghani2020hierarchical}, the authors prove that applying these three linkage methods to a signed graph is equivalent to applying them to the unsigned graph obtained by shifting all edge weights by a constant.
+Here, we prove which of the algorithms studied here is ``intrinsically'' signed and do not have this invariance-property:
 \begin{restatable}{prop}{invariantAlgs}
@@
 \noindent To our knowledge, Average and Single linkage methods have never been combined with cannot-link constraints on signed graphs, so we name these algorithms \emph{HCC-Avg} and \emph{HCC-Single}.
-In Lemma \ref{lemma:absMax_and_complete_property} (Appendix \ref{sec:proposition_proofs}), we prove that with Complete linkage the agglomeration order does not change whether constraints are introduced or not.
+On the other hand, we prove that enforcing constraints with a Complete linkage does not change the final clustering (Lemma \ref{lemma:absMax_and_complete_property}, in Appendix).
+% , we prove that with Complete linkage the agglomeration order does not change whether constraints are introduced or not.
 

### 2021-03-16 chapters/5_experiments_intro.tex
Integrate last Fred's comments

@@
         &&&& %\multicolumn{1}{c}{}
-        &\multicolumn{5}{c}{Multicut objective values of final clusterings (average across instances, lower is better)} \\
+        &\multicolumn{5}{c}{Multicut objective values (average across instances, lower is better)} \\
         Clustering problem & \makecell{Graph Type} & $\#I$ & $|V|$ & $|E|$  & \multicolumn{1}{r}{GAEC \cite{keuper2015efficient}} & HCC-Sum & MWS \cite{wolf2018mutex} & HC-Avg & HCC-Avg \\ \midrule
@@
         -0.457 & -0.453 & -0.073 & \textbf{-0.467} & \textbf{-0.467} \\ 
-        \emph{Image Segmentation} \cite{andres2011probabilistic} & \emph{rag} & 100 & 156-3764 &  439-10970  & % \HollowBox 
+        \emph{Image Segmentation} \cite{andres2011probabilistic} & \emph{RAG} & 100 & 156-3764 &  439-10970  & % \HollowBox 
         \textbf{-2,955} & -2,953 & -2,901 & -2,903 & -2,896\\
-        \emph{Knott-3D (150-300-450)} \cite{andres2012globally} & \emph{3D-rag} & 24 & 572-17k & 3381-107k & % \HollowBox & 
+        \emph{Knott-3D (150-300-450)} \cite{andres2012globally} & \emph{3D-RAG} & 24 & 572-17k & 3381-107k & % \HollowBox & 
         \textbf{-36,667} & -36,652 & -35,200 & -35,957 & -35,631\\
-        % \emph{Knott-3D-300} & \emph{3D-rag} & 8& & & \HollowBox\\
-        % \emph{Knott-3D-450}& \emph{3D-rag} & 8 & & & \HollowBox\\  
-        \emph{CREMI-3D-rag (OurCNN)}  & \emph{3D-rag} & 3& 134k-157k & 928k-1065k % & \CrossedBox 
+        % \emph{Knott-3D-300} & \emph{3D-RAG} & 8& & & \HollowBox\\
+        % \emph{Knott-3D-450}& \emph{3D-RAG} & 8 & & & \HollowBox\\  
+        \emph{CREMI-3D-RAG (OurCNN)}  & \emph{3D-RAG} & 3& 134k-157k & 928k-1065k % & \CrossedBox 
         & \textbf{-1,112,287} & \textbf{-1,112,286}& -1,109,731 & -1,112,177 & -1,112,100\\ 
-        \emph{Fruit-Fly Level 1-4} \cite{pape2017solving} & \emph{3D-rag} & 4& 5m-11m & 28m-72m %& \HollowBox 
+        \emph{Fruit-Fly Level 1-4} \cite{pape2017solving} & \emph{3D-RAG} & 4& 5m-11m & 28m-72m %& \HollowBox 
         & \textbf{-151,022} & -151,017 & -150,879 & -150,909 & -150,876\\
@@
         & -73,317,601 & -73,328,867 & -73,330,568 & \textbf{-73,502,947} & -73,474,856\\
-        \emph{Fruit-Fly Level Global} \cite{pape2017solving} & \emph{3D-rag} & 1& 90m & 650m % & \HollowBox 
+        \emph{Fruit-Fly Level Global} \cite{pape2017solving} & \emph{3D-RAG} & 1& 90m & 650m % & \HollowBox 
         & \textbf{-151,688} & -151,596 & -146,315 & -150,466 & -150,171 \\
@@
 \textbf{Existing signed graphs}  -- We use clustering instances from the OpenGM benchmark \cite{kappes2013comparative} as well as biomedical segmentation instances \cite{pape2017solving}.
-The dataset \emph{Image Segmentation} contains planar region-adjacency-graphs (\emph{rag}) that are constructed from superpixel adjacencies of photographs.
-The \emph{Knott-3D} datasets contains \emph{3D-rags} arising from volume images acquired by electron microscopy (EM).
+The dataset \emph{Image Segmentation} contains planar region-adjacency-graphs (RAG) that are constructed from superpixel adjacencies of photographs.
+The \emph{Knott-3D} datasets contains 3D-RAGs arising from volume images acquired by electron microscopy (EM).
 The set \emph{Modularity Clustering} contains complete graphs constructed from clustering problems on small social networks.
-The \emph{Fruit-Fly} 3D-rag instances were generated from volume image scans of fruit fly brain matter.
+The \emph{Fruit-Fly} 3D-RAG instances were generated from volume image scans of fruit fly brain matter.
 Instances \emph{Level 1-4} are progressively simplified versions of the global problem obtained via block-wise domain decomposition \cite{pape2017solving}.
@@
 
-\textbf{3D-rag from CNN-predictions} -- Lastly, we use the predictions of our CNN model to generate three graph instances (one for each CREMI training sample, named \emph{CREMI-3D-rag} in Table~\ref{tab:datasets_and_energies}), which have very similar structure to the \emph{Knott-3D} and \emph{Fruit-Fly} instances.
+\textbf{3D-RAG from CNN-predictions} -- Lastly, we use the predictions of our CNN model to generate three graph instances (one for each CREMI training sample, named \emph{CREMI-3D-RAG} in Table~\ref{tab:datasets_and_energies}), which have very similar structure to the \emph{Knott-3D} and \emph{Fruit-Fly} instances.
 We obtain these problems by using a pipeline that is very common in neuron segmentation: a watershed algorithm generates superpixels and from those a 3D region-adjacency graph is built, where edge weights are given by the CNN predictions averaged over the boundaries of adjacent superpixels (details in Appendix \ref{sec:cremi_details}).
@@
     \tiny
-        \begin{subtable}[t]{0.29\textwidth}
+        \begin{subtable}[t]{0.27\textwidth}
         \centering
-        \begin{tabular}[t]{lcccc}
+        \begin{tabular}[t]{@{\hspace{0.7\tabcolsep}}l c @{\hspace{1\tabcolsep}} c @{\hspace{1.1\tabcolsep}} c @{\hspace{1\tabcolsep}} c @{\hspace{1\tabcolsep}}}
         \toprule
-          & \makecell{ARAND\\error} & \makecell{VOI\\split} & \makecell{VOI\\merge}&  \makecell{Runtime\\(s)} \\ \midrule 
+          & ARAND & VOI & VOI&  Runtime \\ 
+          & Error & split & merge&  (s) \\ \midrule 
 \textbf{HC-Avg} & \textbf{0.0487} & 0.387 & 0.258 & 2344 \\
@@
         \end{tabular}
-        \vspace*{1em}
+        \vspace*{1.1em}
     % \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding.
@@
     \end{subtable}\hfill
-\begin{subtable}[t]{.29\textwidth}
+\begin{subtable}[t]{.27\textwidth}
 \centering
-        \begin{tabular}[t]{lcccc}
+        \begin{tabular}[t]{@{\hspace{0.7\tabcolsep}}l c @{\hspace{1\tabcolsep}} c @{\hspace{1.1\tabcolsep}} c @{\hspace{1\tabcolsep}} c @{\hspace{1\tabcolsep}}}
         \toprule
-          & \makecell{ARAND\\error} & \makecell{VOI\\split} & \makecell{VOI\\merge}&  \makecell{Runtime\\(s)} \\ \midrule 
+          & ARAND & VOI & VOI&  Runtime \\ 
+          & Error & split & merge&  (s) \\ \midrule 
 \textbf{HC-Avg} & \textbf{0.0896} & 0.603 & 0.323 & 86 \\
@@
         % \hspace*{5em}
-        \vspace*{1em}
-    \caption{\emph{CREMI-3D-rag (OurCNN)}}
+        \vspace*{1.1em}
+    \caption{\emph{CREMI-3D-RAG (OurCNN)}}
     \label{tab:scores_3drag}
-    \end{subtable}\hfill
-    \begin{subtable}[t]{.38\textwidth}
+    \end{subtable} \hfill
+    \begin{subtable}[t]{.43\textwidth}
     % \end{table}
@@
     \tiny
-        \begin{tabular}[t]{lcccc}
+        \begin{tabular}[t]{l @{\hspace{1.2\tabcolsep}} c @{\hspace{1\tabcolsep}} c @{\hspace{1\tabcolsep}} c @{\hspace{0.8\tabcolsep}} c @{\hspace{1\tabcolsep}} c}
+        % \begin{tabular}[t]{lcccc}
         \toprule
-          & \makecell{CREMI\\Score} & \makecell{ARAND\\error} & \makecell{VOI\\split} & \makecell{VOI\\merge}    \\ \midrule 
-OurCNN: 3D-rag + LiftedMulticut & \textbf{0.221} & \textbf{0.108} & \textbf{0.339} & 0.115 \\
-\emph{OurCNN: gridGraph + HCC-Avg} & 0.224 & 0.113 & 0.361 & 0.085  \\
-\emph{OurCNN: gridGraph + HC-Avg}  & 0.224 & 0.114 &  0.364 & 0.083 \\
-PNI CNN \cite{lee2017superhuman} & 0.228 & 0.116 & 0.345 & 0.106 \\
-LSI-Masks \cite{bailoni2020proposal}  & 0.246 & 0.125 & 0.383 & 0.107  \\
-\emph{OurCNN: 3D-rag + HCC-Avg} & 0.257 & 0.132 & 0.438& \textbf{0.063} \\  
-\emph{OurCNN: 3D-rag + HC-Avg} & 0.262 & 0.135 & 0.448 & \textbf{0.063}   \\  
+        & Needs & CREMI& ARAND & VOI & VOI\\ 
+          & superpixels? & Score & Error & split & merge\\ \midrule 
+          % & \makecell{CREMI\\Score} & \makecell{ARAND\\error} & \makecell{VOI\\split} & \makecell{VOI\\merge}    \\ \midrule 
+OurCNN: 3D-RAG + LiftedMulticut & \CrossedBox & \textbf{0.221} & \textbf{0.108} & \textbf{0.339} & 0.115 \\
+\emph{GASP: OurCNN + gridGraph + HCC-Avg} & \HollowBox & 0.224 & 0.113 & 0.361 & 0.085  \\
+\emph{GASP: OurCNN + gridGraph + HC-Avg}  & \HollowBox &0.224 & 0.114 &  0.364 & 0.083 \\
+PNI CNN \cite{lee2017superhuman} & \CrossedBox &0.228 & 0.116 & 0.345 & 0.106 \\
+LSI-Masks \cite{bailoni2020proposal}  & \HollowBox &0.246 & 0.125 & 0.383 & 0.107  \\
+\emph{GASP: OurCNN + 3D-RAG + HCC-Avg} & \HollowBox &0.257 & 0.132 & 0.438& \textbf{0.063} \\  
+\emph{GASP: OurCNN + 3D-RAG + HC-Avg} & \HollowBox &0.262 & 0.135 & 0.448 & \textbf{0.063}   \\  
 % \textbf{Our CNN + \algname{} Average} & \textbf{0.241 \\
-MALA CNN + MC \cite{funke2018large} & 0.276  & 0.132 &0.490  & 0.089  \\
-CRU-Net \cite{zeng2017deepem3d} & 0.566 & 0.229 & 1.081 &  0.389    \\
+MALA CNN + MC \cite{funke2018large} & \CrossedBox & 0.276  & 0.132 &0.490  & 0.089  \\
+CRU-Net \cite{zeng2017deepem3d} & \CrossedBox &0.566 & 0.229 & 1.081 &  0.389    \\
 % LFC \cite{parag2017anisotropic} & 0.616 & 0.313 & 1.085 & 0.140     \\
@@
     % \label{tab:results_cremi_test}
-    \caption{\textbf{Tables (a-b)}: Scores and run times of algorithms in the \algname{} framework on the \emph{CREMI-gridGraph} and \emph{CREMI-3D-rag} clustering problems: average linkage methods achieved the best accuracy.
+    \caption{\textbf{Tables (a-b)}: Scores and run times of algorithms in the \algname{} framework on the \emph{CREMI-gridGraph} and \emph{CREMI-3D-RAG} clustering problems: average linkage methods achieved the best accuracy.
 Measures shown are: Adapted-Rand error (ARAND, lower is better); Variation of Information (VOI) \cite{arganda2015crowdsourcing} (VOI-merge for under-clustering error and VOI-split for over-clustering error, lower values are better).
@@
 
-\textbf{Complete and Single Linkage} -- We use these two linkage methods as baselines to highlight the difficulty of the studied graph clustering problems listed in Table~\ref{tab:datasets_and_energies}.
-Scores in Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show their poor performance: Single linkage hierarchical clustering (HC-Single), which here is equivalent to thresholding the edge weights at $w_e=0$ and computing connected components in the graph, often returned few big under-segmented clusters.
-HC-Complete returned instead a lot of over-segmented clusters.
-% These algorithms are excluded from our next comparison experiments.
-
 \begin{figure}[t]
@@
 SSBM graphs are \emph{non-planar}, and every edge has the same probability to be present in the graph.
-On the other hand, the \emph{gridGraph} and \emph{3D-rag} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: regardless of whether a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance).
+On the other hand, the \emph{gridGraph} and \emph{3D-RAG} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: regardless of whether a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance).
 Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show that average linkage methods (HC-Avg, HCC-Avg) strongly outperform other methods on \emph{CREMI-gridGraph} instances and also achieve the best scores on \emph{CREMI-3D-rag} graphs.
-Sum-based linkage methods (GAEC, HCC-Sum) do not perform well on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}).
-This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods performs poorly on grid-graphs, because in this setup edge weights are predicted by a CNN and noise is strongly spatially-correlated \footnote{This effect is not as strong on \emph{3D-rag} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
+Sum-based linkage methods (GAEC, HCC-Sum) have a two times higher ARAND error on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}).
+This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods does not work on grid-graphs, because in this setup edge weights are predicted by a CNN and noise is strongly spatially-correlated \footnote{This effect is not as strong on \emph{3D-RAG} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
 To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}.
@@
 It is not a surprise that the AbsMax linkage used by MWS is not robust to this type of structured noise.
-However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} prove how MWS can achieve competitive performances with considerably lower runtimes.
+However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} prove how MWS can achieve high accuracy with considerably lower runtimes.
+
+\textbf{Complete and Single Linkage} -- We use these two linkage methods as baselines to highlight the difficulty of the studied graph clustering problems listed in Table~\ref{tab:datasets_and_energies}.
+Scores in Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show their poor performance: Single linkage hierarchical clustering (HC-Single), which here is equivalent to thresholding the edge weights at $w_e=0$ and computing connected components in the graph, often returned few big under-segmented clusters.
+HC-Complete returned instead a lot of over-segmented clusters.
+% These algorithms are excluded from our next comparison experiments.
 
@@
 \caption{Clustering dynamics and accuracy of GASP variations on stochastic block models.
-The dendrograms result from three versions of \algname{} (GAEC, MWS, and HC-Avg) on a synthetic graph generated with SSBM ($N=250$ nodes, edge probability $p=0.05$, flipping probability $\eta=0.1$).
+The dendrograms result from three versions of \algname{} on a synthetic graph generated with SSBM ($250$ nodes, edge probability $p=0.05$, flipping probability $\eta=0.1$).
 Red and blue colors show which of the two equal-sized ground-truth communities each node belongs to.
@@
 \textbf{Results on CREMI challenge} -- 
-Table~\ref{tab:cremi_leaderboard} shows that the HCC-Avg and HC-Avg clustering algorithms achieve state-of-the-art performances on the CREMI challenge, when combined with predictions of our CNN.
+Table~\ref{tab:cremi_leaderboard} shows that the HCC-Avg and HC-Avg clustering algorithms achieve state-of-the-art accuracy on the CREMI challenge, when combined with predictions of our CNN.
 Most of the other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs.
 As we show in Table ~\ref{tab:scores_3drag}, using super-pixels considerably reduces the size of the clustering problem and, consequently, the post-processing time.
-However, our method operating directly on pixels (\emph{gridGraph+HCC-Avg}) achieves better performances than superpixel-based methods (\emph{3D-rag+HCC-Avg}) and does not require the parameter tuning necessary to obtain good super-pixels, which is usually highly dataset dependent.
+However, our method operating directly on pixels (\emph{gridGraph + HCC-Avg}) achieves better performances than superpixel-based methods (\emph{3D-RAG + HCC-Avg}) and does not require the parameter tuning necessary to obtain good super-pixels, which is usually highly dataset dependent.
 To scale up our method operating on pixels, we divided each test-volume into four sub-blocks, and then combined the resulting clusterings by running the algorithms again on the combined graph.
-The method \emph{3D-rag+LiftedMulticut} based on the lifted multicut approximation of \cite{beier2017multicut} achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and shape information from highly engineered super-pixels.
+The method \emph{3D-RAG + LiftedMulticut} based on the lifted multicut approximation of \cite{beier2017multicut} achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and shape information from highly engineered super-pixels.
 % Note that the test volumes of the challenge contain several imaging artifacts that make segmentation particularly challenging.
@@
 \includegraphics[width=0.48\textwidth,trim=90 10 60 0, clip]{./figs/comparison_GAEC_MWS_Avg.png} % left bottom right top
-\caption{Failure cases of three versions of \algname{} (GAEC, MWS, and HC-Avg) applied to neuron segmentation.
+\caption{Failure cases of three versions of \algname{} applied to neuron segmentation.
 Only \emph{wrongly} segmented regions are highlighted in different warm colors.

### 2021-03-16 chapters/2_rel_work.tex
Shorten text

@@
 \textbf{Proposal-free instance segmentation methods} adopt a bottom-up approach by directly grouping pixels into instances.
-Recently, there has been a growing interest in such  methods that do not involve object detection because, in certain types of data, object instances cannot be approximated by bounding boxes \cite{kirillov2017instancecut,bai2017deep}.
+In the last years, there has been a growing interest in such  methods that do not involve object detection because, in certain types of data, object instances cannot be approximated by bounding boxes \cite{kirillov2017instancecut,bai2017deep}.
 % For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation, 

### 2021-03-16 chapters/3_algorithm.tex
Shorten text

@@
 Let the interaction $\interact(S,S')\in\mathbb{R}$ between two clusters $S,S'$ be defined as a function, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S$ and $S'$, i.e.
-${(S \times S') \cap E}$.
+${(S \times S') \cap E}$ where $\times$ denotes the outer product.
 The linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
 A \emph{dendrogram} $T$ is a rooted binary tree\footnote{In general, one could look at trees that are not binary.
-However, the algorithms discussed in this paper always generate binary hierarchical trees, so nothing would be gained by this generalization.} representing the merging order of an agglomerative algorithm, such that the leaves of the tree are in one-to-one correspondence with $V$.
+However, the algorithms discussed in this paper always generate binary hierarchical trees, so nothing would be gained by this generalization.} representing the merging order of an agglomerative algorithm, such that the leaves of the tree are in one-to-one correspondence with $V$ and each node of the tree represents a merge between two clusters.
 Let $T_{\mathrm{R}},T_{\mathrm{L}}\subset T$ denote the subtrees rooted at the two children of the root node in $T$.
@@
 % Algorithm \ref{main_alg} returns a binary tree denoted by $T^*$.
-Given an agglomerative algorithm with merging tree $T$, let $h_T:T \rightarrow \mathbb{N}$ denote the \emph{dendrogram-height} of each $(u\vee v)\in T$, which is defined as the iteration number at which nodes $u,v\in V$ were merged by the algorithm (see example in Fig.~\ref{fig:intro_figure}a).
-We also define $\treeHeight(u,v)$ as the signed interaction $\interact{}(S,S')$ between the two clusters $S,S'$ that were merged at iteration $h_T(u\vee v)$:
+Given an agglomerative algorithm with merging tree $T$, let $h_T:V \times V \rightarrow \mathbb{N}$ denote the \emph{dendrogram-height} of each $(u\vee v)\in T$, which is defined as the iteration number at which nodes $u,v\in V$ were merged by the algorithm (see example in Fig.~\ref{fig:intro_figure}a).
+We also define $\treeHeight(u,v)$ as the signed interaction $\interact{}(S,S')$ between the two clusters $S,S'$ that were merged at iteration $h_T(u, v)$:
 % Then, given a binary tree $T$ and a linkage criterion $\interact$, we can associate a \emph{signed similarity} function $\treeHeight$ to each pair of distinct original nodes $u\neq v$, with $u, v \in V$:
@@
 Phase one terminates when all the remaining clusters are either constrained or share repulsive interactions.
-Note that, on unsigned graphs, in phase one \algname{} merges all nodes in a single cluster and is then equivalent to a standard hierarchical clustering algorithm.
+Note that, on unsigned graphs, in phase one all nodes are merged into a single cluster and \algname{} is then equivalent to a standard hierarchical clustering algorithm.
 
@@
 \label{prop:absmax_mutex}
-The \algname{} Algorithm \ref{main_alg} with AbsMax linkage (see def.
-in Table \ref{tab:linkage-criteria}) returns the same final clustering $\Pi^*_{\mathrm{AbsMax}}$ whether or not cannot-link constraints are introduced.
-Also, $\Pi^*_{\mathrm{AbsMax}}$ is equal to the clustering returned by the Mutex Watershed Algorithm (MWS) \cite{wolf2018mutex}, which has empirical complexity $\mathcal{O}(N \log N)$.
+The \algname{} Algorithm \ref{main_alg} with AbsMax linkage, regardless of whether constraints are enforced or not, returns the same final clustering $\Pi^*_{\mathrm{AbsMax}}$ also returned by the Mutex Watershed Algorithm (MWS) \cite{wolf2018mutex}, which has empirical complexity $\mathcal{O}(N \log N)$.
 \end{restatable}
@@
 \label{prop:weight_shift_invariant}
-We call an agglomerative algorithm ``weight-shift invariant'' if the structure of the merging tree $T$ returned by the algorithm is invariant w.r.t.
+We call an agglomerative algorithm ``weight-shift invariant'' if the dendrogram $T$ returned by the algorithm is invariant w.r.t.
 a shift of all edge weights $w_e$  by a constant $\alpha\in \mathbb{R}$.
-Among the versions of \algname{} studied in this paper, only hierarchical clustering using Average (HC-Avg), Single (HC-Single), and Complete linkage (HC-Complete) are weight-shift-invariant (see algorithms included in the green box in Table~\ref{tab:linkage-criteria}).
+Among the variations of \algname{}, only hierarchical clustering with Average (HC-Avg), Single (HC-Single), and Complete linkage (HC-Complete) are weight-shift-invariant (see green box in Table~\ref{tab:linkage-criteria}).
 \end{restatable}
 \noindent To our knowledge, Average and Single linkage methods have never been combined with cannot-link constraints on signed graphs, so we name these algorithms \emph{HCC-Avg} and \emph{HCC-Single}.
-On the other hand, we prove that enforcing constraints with a Complete linkage does not change the final clustering (Lemma \ref{lemma:absMax_and_complete_property}, in Appendix).
+On the other hand, we prove that an agglomerative algorithm with Complete linkage (HC-Complete) returns the same clustering whether cannot-link-constraints are enforced or not (Lemma \ref{lemma:absMax_and_complete_property}, in Appendix).
 % , we prove that with Complete linkage the agglomeration order does not change whether constraints are introduced or not.
@@
 
-\paragraph{Algorithms defining an ultrametric} -- The connection between agglomerative algorithms and ultrametrics\footnote{A metric space $(X,d)$ is an \emph{ultrametric} if for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.} is well known \cite{johnson1967hierarchical,milligan1979ultrametric}.
+\paragraph{Algorithms defining an ultrametric} -- The connection between agglomerative algorithms and ultrametrics\footnote{A metric space $(X,d)$ is an \emph{ultrametric} if for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.} is well known.
 Usually, ultrametrics are associated to strictly positive \emph{similarity} or \emph{dissimilarity} measures on a graph.
-Here, we generalize this concept to signed graphs.
-To do so, we first map the signed interaction $\treeHeight{}$ defined in Eq.~\ref{eq:def_dendr_interact} to positive ``pseudo-distances'' $d_{T}:V \times V \rightarrow \mathbb{R}^{+}$:
+In our framework, a trivial ultrametric is always given by the height $h_T$ of the dendrogram.
+However, we now prove that, similarly to what has been done for HC on unsigned graphs \cite{johnson1967hierarchical,milligan1979ultrametric}, for some of the \algname{} variations we can define an ultrametric based on the edge weights and the interactions between clusters.
+To define this measure, we first map the signed interaction $\treeHeight{}$ defined in Eq.~\ref{eq:def_dendr_interact} to positive ``pseudo-distances'' $d_{T}:V \times V \rightarrow \mathbb{R}^{+}$:
 \begin{align}\label{eq:UM_def}
@@
 \end{restatable}
-
-Now that we have defined the algorithms and managed to characterize them from a theoretical point of view, we move to empirical evaluation.
+Now that we have defined the algorithms and characterized them from a theoretical point of view, we move to empirical evaluation in the next section.
 

### 2021-03-16 chapters/5_experiments_intro.tex
Shorten text

@@
 LSI-Masks \cite{bailoni2020proposal}  & \HollowBox &0.246 & 0.125 & 0.383 & 0.107  \\
-\emph{GASP: OurCNN + 3D-RAG + HCC-Avg} & \HollowBox &0.257 & 0.132 & 0.438& \textbf{0.063} \\  
-\emph{GASP: OurCNN + 3D-RAG + HC-Avg} & \HollowBox &0.262 & 0.135 & 0.448 & \textbf{0.063}   \\  
+\emph{GASP: OurCNN + 3D-RAG + HCC-Avg} & \CrossedBox &0.257 & 0.132 & 0.438& \textbf{0.063} \\  
+\emph{GASP: OurCNN + 3D-RAG + HC-Avg} & \CrossedBox &0.262 & 0.135 & 0.448 & \textbf{0.063}   \\  
 % \textbf{Our CNN + \algname{} Average} & \textbf{0.241 \\
@@
 \textbf{Size of growing clusters: Sum vs Avg linkage} --
-In all the studied clustering problems, we empirically observe that sum-linkage algorithms like GAEC tend to grow clusters one after the other, as shown in Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}d} and Fig.~\ref{fig:dendrograms} by the unique agglomeration order of GAEC\footnote{This \emph{flooding agglomeration-strategy} of GAEC was also observed in \cite{kardoostsolving}.}.
+In all the studied clustering problems, we empirically observe that sum-linkage algorithms like GAEC grow clusters one after the other, as shown in Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}d} and Fig.~\ref{fig:dendrograms} by the agglomeration order of GAEC\footnote{This \emph{flooding agglomeration-strategy} of GAEC was also observed in \cite{kardoostsolving}.}.
 This is intuitively explained by the  following: initially, many of the most attractive edge weights have very similar values; when the two nodes $u,v$ with the highest attraction are merged, there is a high chance that they will have a common neighboring node $t$ belonging to the same cluster; thus, the interaction between the merged nodes $uv$ and $t$ is likely assigned to the highest priority, because it is given by the sum of two highly attractive edge weights.
@@
 To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}.
-The plot in Fig.~\ref{fig:scores_structured_noise} confirms that HC-Avg and HCC-Avg perform well even in the presence of strong structured noise, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (MWS).
+The plot in Fig.~\ref{fig:scores_structured_noise} confirms that HC-Avg and HCC-Avg are very robust algorihtms on this data, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (MWS).
 It is not a surprise that the AbsMax linkage used by MWS is not robust to this type of structured noise.
@@
 % \includegraphics[width=0.48\textwidth,trim=300 100 300 100, clip]{./figs/dendrograms/new_agglo_order_OLD.png} % left bottom right top
-\includegraphics[width=0.48\textwidth,trim=80 10 60 0, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
+\includegraphics[width=0.48\textwidth,trim=0 10 60 0, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
 \caption{Clustering dynamics and accuracy of GASP variations on stochastic block models.
@@
 \centering
-\includegraphics[width=0.48\textwidth,trim=90 10 60 0, clip]{./figs/comparison_GAEC_MWS_Avg.png} % left bottom right top
+\includegraphics[width=0.48\textwidth,trim=0 10 60 0, clip]{./figs/comparison_GAEC_MWS_Avg.png} % left bottom right top
 \caption{Failure cases of three versions of \algname{} applied to neuron segmentation.

### 2021-03-16 chapters/6_conclusions.tex
Shorten text

@@
 We have analyzed several theoretical and empirical properties of the algorithms included in this framework.
-On instance segmentation, algorithms based on an average linkage criterion outperformed all the others: they proved to be simple and remarkably robust approaches to process short- and long-range predictions of a CNN.
+On instance segmentation, algorithms based on an average linkage criterion outperformed all the others: they proved to be simple and robust approaches to process short- and long-range predictions of a CNN.
  % applied to an instance segmentation task.

### 2021-03-17 chapters/3_algorithm.tex
Last minor changes

@@
 
-\paragraph{Average, Single, and Complete Linkage} -- These three linkage criteria have been throughly studied on unsigned graphs, but never on signed graphs.
+\paragraph{Average, Single, and Complete Linkage} -- These three linkage criteria have been thoroughly studied on unsigned graphs, but never on signed graphs.
 In recent independent related work \cite{chehreghani2020hierarchical}, the authors prove that applying these three linkage methods to a signed graph is equivalent to applying them to the unsigned graph obtained by shifting all edge weights by a constant.
-Here, we prove which of the algorithms studied here is ``intrinsically'' signed and do not have this invariance-property:
+Here, we prove which of the algorithms studied here is ``intrinsically signed'' and do not have this invariance-property:
 \begin{restatable}{prop}{invariantAlgs}
@@
 \end{restatable}
-\noindent To our knowledge, Average and Single linkage methods have never been combined with cannot-link constraints on signed graphs, so we name these algorithms \emph{HCC-Avg} and \emph{HCC-Single}.
-On the other hand, we prove that an agglomerative algorithm with Complete linkage (HC-Complete) returns the same clustering whether cannot-link-constraints are enforced or not (Lemma \ref{lemma:absMax_and_complete_property}, in Appendix).
+\noindent Although average and single linkage methods have been largely studied on unsigned graphs, to our knowledge, they have never been combined with cannot-link constraints on signed graphs\footnote{Note that Complete linkage methods return the same clustering whether constraints are enforced or not (proof in Lemma \ref{lemma:absMax_and_complete_property}, in Appendix).}, so we name these algorithms \emph{HCC-Avg} and \emph{HCC-Single}.
+% On the other hand, we prove that an agglomerative algorithm with Complete linkage (HC-Complete) returns the same clustering whether cannot-link-constraints are enforced or not (Lemma \ref{lemma:absMax_and_complete_property}, in Appendix).
 % , we prove that with Complete linkage the agglomeration order does not change whether constraints are introduced or not.
@@
 
-\paragraph{Algorithms defining an ultrametric} -- The connection between agglomerative algorithms and ultrametrics\footnote{A metric space $(X,d)$ is an \emph{ultrametric} if for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.} is well known.
+\paragraph{Algorithms defining an ultrametric} -- The connection between agglomerative algorithms and ultrametrics\footnote{A metric space $(X,d)$ is an \emph{ultrametric} if, for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.} is well known.
 Usually, ultrametrics are associated to strictly positive \emph{similarity} or \emph{dissimilarity} measures on a graph.
 In our framework, a trivial ultrametric is always given by the height $h_T$ of the dendrogram.
-However, we now prove that, similarly to what has been done for HC on unsigned graphs \cite{johnson1967hierarchical,milligan1979ultrametric}, for some of the \algname{} variations we can define an ultrametric based on the edge weights and the interactions between clusters.
-To define this measure, we first map the signed interaction $\treeHeight{}$ defined in Eq.~\ref{eq:def_dendr_interact} to positive ``pseudo-distances'' $d_{T}:V \times V \rightarrow \mathbb{R}^{+}$:
+However, for some of the \algname{} variations, we now define an ultrametric based on the edge weights and the signed interactions between clusters, generalizing what has been done for HC on unsigned graphs \cite{johnson1967hierarchical,milligan1979ultrametric}.
+To define this measure and prove its ultrametric property, we first map the signed interaction $\treeHeight{}$ defined in Eq.~\ref{eq:def_dendr_interact} to positive ``pseudo-distances'' $d_{T}:V \times V \rightarrow \mathbb{R}^{+}$:
 \begin{align}\label{eq:UM_def}
@@
 \end{restatable}
-Now that we have defined the algorithms and characterized them from a theoretical point of view, we move to empirical evaluation in the next section.
+Now that we have extended the family of HC algorithms \cite{johnson1967hierarchical,milligan1979ultrametric} with ``weight-based ultrametrics'' to signed graphs, we move on to their empirical evaluation.
 

### 2021-03-17 chapters/5_experiments_intro.tex
Last minor changes

@@
 It is not a surprise that the AbsMax linkage used by MWS is not robust to this type of structured noise.
-However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} prove how MWS can achieve high accuracy with considerably lower runtimes.
+However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} prove how MWS can achieve high accuracy with 70\% lower runtime compared to HC-Avg.
 
@@
 Most of the other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs.
-As we show in Table ~\ref{tab:scores_3drag}, using super-pixels considerably reduces the size of the clustering problem and, consequently, the post-processing time.
+As we show in Table ~\ref{tab:scores_3drag}, using superpixels considerably reduces the size of the clustering problem and, consequently, the post-processing time.
 However, our method operating directly on pixels (\emph{gridGraph + HCC-Avg}) achieves better performances than superpixel-based methods (\emph{3D-RAG + HCC-Avg}) and does not require the parameter tuning necessary to obtain good super-pixels, which is usually highly dataset dependent.

### 2021-03-17 chapters/supplementary.tex
Shorten text
Last minor changes

@@
           \State $\tilde{E} \gets \tilde{E} \setminus \{e_{vt}\}$
-          \State $\tilde{w}_{vt} \gets$ PQ.delete($e_{vt}$) \Comment{$\mathcal{O}(\log |E|)$}
+          \State $\tilde{w}_{vt} \gets$ PQ.delete($e_{vt}$) \Comment{Delete edge $e_{vt}$ from PQ and get the old edge weight, $\mathcal{O}(\log |E|)$}
           \State \texttt{canBeMerged}$[e_{ut}] \gets$ \texttt{canBeMerged}$[e_{ut}]$ \textbf{and} \texttt{canBeMerged}$[e_{vt}]$
-          \If{$t \in \mathcal{N}_u$ }\Comment{$t$ is a common neighbor of $u$ and $v$}
+          \If{$t \in \mathcal{N}_u$ }\Comment{Check if $t$ is a common neighbor of $u$ and $v$}
             \State $\tilde{w}_{ut} \gets$ PQ.delete($e_{ut}$)  \Comment{$\mathcal{O}(\log |E|)$}
@@
 % \subsubsection{Weight-shift invariance of \algname{} algorithms}
+\begin{figure}[t]
+% \begin{subfigure}[t]{0.48\textwidth}
+\centering
+\includegraphics[width=0.48\textwidth,trim=0in 0in 0in 0in,clip]{./figs/counter-examples/counter-example-GAEC.pdf}
+% \caption{Original graph and dendrogram}
+% \end{subfigure}
+
+% \vspace{2em}
+% \begin{subfigure}[t]{0.48\textwidth}
+% \centering
+% \includegraphics[width=\textwidth,trim=0in 0in 0in 0in,clip]{./figs/counter-examples/counter-example-GAEC-shifted.pdf}
+% \caption{Graph with shifted edge-weights ($\alpha=-3$) and GAEC dendrogram}
+% \end{subfigure}
+        \caption{ Counter-example showing that GAEC is not weight-shift invariant.
+        } \label{fig:counter_examples_shift_inv_GAEC}
+\end{figure}
+\begin{figure}[t!]
+% \begin{subfigure}[t]{0.48\textwidth}
+\centering
+\includegraphics[width=0.48\textwidth,trim=0in 0in 0in 0in,clip]{./figs/counter-examples/counter-example.pdf}
+% \caption{Original graph and dendrogram}
+% \end{subfigure}
+
+% \vspace{2em}
+% \begin{subfigure}[t]{0.48\textwidth}
+% \centering
+% \includegraphics[width=\textwidth,trim=0in 0in 0in 0in,clip]{./figs/counter-examples/counter-example-shifted.pdf}
+% \caption{Graph with shifted edge-weights ($\alpha=+2$) and dendrogram}
+% \end{subfigure}
+        \caption{ Counter-example showing that HCC-Sum, MWS, HCC-Avg, and HCC-Single are not weight-shift invariant.
+        } \label{fig:counter_examples_shift_inv}
+\end{figure}
+
 \invariantAlgs*
@@
 \forall u,v,t \in V \nonumber \\
- h_T(u \vee v) < h_T(u \vee t) \Rightarrow \interact{}_{T}(u,v) \geq \interact{}_{T}(u,t) \label{eq:UM_assumption}
- % h_T(u \vee v) < h_T(u \vee t) \Leftrightarrow \interact{}_{T}(u,v) > \interact{}_{T}(u,t). 
+ h_T(u, v) < h_T(u, t) \Rightarrow \interact{}_{T}(u,v) \geq \interact{}_{T}(u,t) \label{eq:UM_assumption}
+ % h_T(u, v) < h_T(u, t) \Leftrightarrow \interact{}_{T}(u,v) > \interact{}_{T}(u,t). 
 \end{gather}
@@
 \begin{equation}\label{eq:case_1}
-h_T(u \vee t) < h_T(u \vee v) = h_T(v \vee t).
+h_T(u, t) < h_T(u, v) = h_T(v, t).
 \end{equation}
@@
 \begin{equation}
-\interact{}_{T}(u \vee t) \geq \interact{}_{T}(v \vee t) \quad  \text{and} \quad \interact{}_{T}(u \vee v) = \interact{}_{T}(v \vee t)
+\interact{}_{T}(u, t) \geq \interact{}_{T}(v, t) \quad  \text{and} \quad \interact{}_{T}(u, v) = \interact{}_{T}(v, t)
 \end{equation}
@@
 \begin{equation}
-h_T(u \vee v) < h_T(u \vee t) = h_T(v \vee t).
+h_T(u, v) < h_T(u, t) = h_T(v, t).
 \end{equation}
@@
 \begin{equation}
-\interact{}_{T}(u \vee v) \geq \interact{}_{T}(u \vee t) \quad  \text{and} \quad \interact{}_{T}(u \vee v) \geq \interact{}_{T}(v \vee t),
+\interact{}_{T}(u, v) \geq \interact{}_{T}(u, t) \quad  \text{and} \quad \interact{}_{T}(u, v) \geq \interact{}_{T}(v, t),
 \end{equation}
@@
 \begin{equation}
-h_T(u \vee v) < h_T(u \vee t) \quad \text{and} \quad  \interact{}_{T}(u,v) < \interact{}_{T}(u,t).
+h_T(u, v) < h_T(u, t) \quad \text{and} \quad  \interact{}_{T}(u,v) < \interact{}_{T}(u,t).
 \end{equation}
@@
 \begin{equation}
-\interact{}_{T}(u \vee v) < \interact{}_{T}(u \vee t) = \interact{}_{T}(v \vee t).
+\interact{}_{T}(u, v) < \interact{}_{T}(u, t) = \interact{}_{T}(v, t).
 \end{equation}
@@
 \begin{equation}
-\interact{}_{T}(u \vee v) < \min \{\interact{}_{T}(u \vee t), \interact{}_{T}(v \vee t)\},
+\interact{}_{T}(u, v) < \min \{\interact{}_{T}(u, t), \interact{}_{T}(v, t)\},
 \end{equation}
@@
 In other words, we need to prove in which cases \algname{} merges clusters according to a monotonously decreasing order of signed interactions $\interact{}$.
-This happens only if both of the following conditions are true:
-\begin{itemize}
-\item Condition 1: Updated interactions involving a merged cluster are always lower or equal than previous interactions:
+
+\algname{} puts clusters in a priority queue (Algorithm \ref{main_alg}, lines 5 and 15) and merges them starting from those with the highest interaction (lines 9, 19, and 26).
+However, the priority queue is updated each time two clusters are merged (lines 10, 20, and 27).
+Thus, to ensure a monotonously decreasing merging order, updated interactions involving a merged cluster should always be lower or equal than previously existing interactions (\textbf{condition 1}):
 \begin{align}\label{eq:condition1}
@@
 where $\Pi$ is a clustering, $\interact{}$ is a linkage criteria, and $S_1,S_2\in \Pi$ are two clusters merged by the algorithm at a given iteration.
-If this condition is true then, in the following iterations, \algname{} will only merge clusters with lower (or equal) interaction values.
-\item Condition 2: Positive and constrained interactions are never skipped in Phase 1 (condition at line 8 of Algorithm \ref{main_alg}) and ``delayed'' to Phase 2.
-If this is the case, then \algname{} is not assured to merge clusters according to a monotonously decreasing order of interactions.
-\end{itemize}
-Condition 1 always holds for Average, Single, Complete, and Absolute Maximum linkage criteria, but not for a Sum linkage criteria, because the sum of two positive numbers $a,b$ is always higher than $\max\{a,b\}$.
+If this condition is true then, in the following iterations, \algname{} can only merge clusters with lower (or equal) interaction values.
+
+We also note that, in phase 1, the algorithm skips interactions that are both positive and constraint (condition at line 8 in Algorithm \ref{main_alg}) and merges them only later in phase 2 (line 19), when constraints are removed.
+Clearly, whenever this happens, a decreasing merging order is no longer ensured. 
+Thus, on top of condition 1, we also have that no merging decisions should be ``delayed'' from phase 1 to phase 2 (\textbf{condition 2}).
+
+Condition 1 always holds for Average, Single, Complete, and AbsMax linkage criteria, but not for a Sum linkage criteria, because the sum of two positive numbers $a,b$ is always higher than $\max\{a,b\}$.
 This is also demonstrated in the toy example of Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}, proving that, in general, Sum-linkage algorithms like GAEC or HCC-Sum do not define an ultrametric on the graph.
@@
 
-\begin{figure}[t]
-% \begin{subfigure}[t]{0.48\textwidth}
-\centering
-\includegraphics[width=0.48\textwidth,trim=0in 0in 0in 0in,clip]{./figs/counter-examples/counter-example-GAEC.pdf}
-% \caption{Original graph and dendrogram}
-% \end{subfigure}
-
-% \vspace{2em}
-% \begin{subfigure}[t]{0.48\textwidth}
-% \centering
-% \includegraphics[width=\textwidth,trim=0in 0in 0in 0in,clip]{./figs/counter-examples/counter-example-GAEC-shifted.pdf}
-% \caption{Graph with shifted edge-weights ($\alpha=-3$) and GAEC dendrogram}
-% \end{subfigure}
-        \caption{ Counter-example showing that GAEC is not weight-shift invariant.
-        } \label{fig:counter_examples_shift_inv_GAEC}
-\end{figure}
-\begin{figure}[t!]
-% \begin{subfigure}[t]{0.48\textwidth}
-\centering
-\includegraphics[width=0.48\textwidth,trim=0in 0in 0in 0in,clip]{./figs/counter-examples/counter-example.pdf}
-% \caption{Original graph and dendrogram}
-% \end{subfigure}
-
-% \vspace{2em}
-% \begin{subfigure}[t]{0.48\textwidth}
-% \centering
-% \includegraphics[width=\textwidth,trim=0in 0in 0in 0in,clip]{./figs/counter-examples/counter-example-shifted.pdf}
-% \caption{Graph with shifted edge-weights ($\alpha=+2$) and dendrogram}
-% \end{subfigure}
-        \caption{ Counter-example showing that HCC-Sum, MWS, HCC-Avg, and HCC-Single are not weight-shift invariant.
-        } \label{fig:counter_examples_shift_inv}
-\end{figure}
-
 \subsection{Mutex Watershed on SSBM graphs}
@@
 =&\sum_{\nBE^+_{\mathrm{nf}}=0}^{\nBE^+}\sum_{\nBE^-_{\mathrm{f}}=0}^{\nBE^-} 
-\mathcal{B}(\nBE^-_{\mathrm{f}};\nBE^-,\eta) \mathcal{B}(\nBE^+_{\mathrm{nf}};\nBE^-,1-\eta)\cdot  \nonumber\\
+\mathcal{B}(\nBE^-_{\mathrm{f}};\nBE^-,\eta) \mathcal{B}(\nBE^+_{\mathrm{nf}};\nBE^+,1-\eta)\cdot  \nonumber\\
 & \qquad \qquad  \cdot \left(\frac{\nBE^+_{\mathrm{nf}}+\nBE^-_{\mathrm{f}}}{\nBE^+ + \nBE^-} \right) \nonumber\\

### 2021-03-17 chapters/1_intro.tex
Add comments from Anna

@@
 \caption{\textbf{(a)} Some iterations of \algname{} on a graph with attractive (green) and repulsive (red) interactions.
-At each iteration, the yellow edge with highest interaction is contracted (example with sum linkage criterion is shown).
+At each iteration, the yellow edge with highest weight is contracted (example with sum linkage criterion is shown).
 \textbf{(b)} Linkage criteria used in this paper demonstrated on two small clusters (see definitions in Table~\ref{tab:linkage-criteria} below).
@@
 
-            \thead[r]{GASP on unsigned graphs} & \thead{-} &\tikzmark{a} \thead{\textbf{HC-Single}} &\tikzmark{g} \thead{\textbf{HC-Avg}} &\thead{\textbf{HC-Single}}\tikzmark{z} &\thead{\textbf{HC-Complete}} \tikzmark{b} \\
-            \thead[r]{GASP on signed graphs} & \thead{GAEC \cite{keuper2015efficient}} &  \thead{\textbf{Mutex Watershed} \cite{wolf2018mutex}}& \tikzmark{f} \thead{\textbf{HC-Avg}} &\thead{\textbf{HC-Single}} \tikzmark{e} &\thead{\textbf{HC-Complete}}\tikzmark{w} \\
-            \thead[r]{GASP on signed graphs + constraints} & \thead{\colorbox{yellow}{HCC-Sum}} % \thead{Greedy Fixation \cite{levinkov2017comparative}} 
+            \thead[r]{Unsigned graphs} & \thead{-} &\tikzmark{a} \thead{\textbf{HC-Single}} &\tikzmark{g} \thead{\textbf{HC-Avg}} &\thead{\textbf{HC-Single}}\tikzmark{z} &\thead{\textbf{HC-Complete}} \tikzmark{b} \\
+            \thead[r]{Signed graphs} & \thead{GAEC \cite{keuper2015efficient}} &  \thead{\textbf{Mutex Watershed} \cite{wolf2018mutex}}& \tikzmark{f} \thead{\textbf{HC-Avg}} &\thead{\textbf{HC-Single}} \tikzmark{e} &\thead{\textbf{HC-Complete}}\tikzmark{w} \\
+            \thead[r]{Signed graphs + cannot-link constraints} & \thead{\colorbox{yellow}{HCC-Sum}} % \thead{Greedy Fixation \cite{levinkov2017comparative}} 
             & \thead{\textbf{Mutex Watershed} \cite{wolf2018mutex}}& \thead{\colorbox{yellow}{HCC-Avg}} &  \thead{\colorbox{yellow}{HCC-Single}} \tikzmark{d} &   \thead{\textbf{HC-Complete}} \tikzmark{c} \\

### 2021-03-17 chapters/3_algorithm.tex
Add comments from Anna

@@
 \label{prop:absmax_mutex}
-The \algname{} Algorithm \ref{main_alg} with AbsMax linkage, regardless of whether constraints are enforced or not, returns the same final clustering $\Pi^*_{\mathrm{AbsMax}}$ also returned by the Mutex Watershed Algorithm (MWS) \cite{wolf2018mutex}, which has empirical complexity $\mathcal{O}(N \log N)$.
+The \algname{} Algorithm \ref{main_alg} with AbsMax linkage, with or without cannot link constraints, returns the same final clustering $\Pi^*_{\mathrm{AbsMax}}$ also returned by the Mutex Watershed Algorithm (MWS) \cite{wolf2018mutex}, which has empirical complexity $\mathcal{O}(N \log N)$.
 \end{restatable}
@@
 
-\paragraph{Average, Single, and Complete Linkage} -- These three linkage criteria have been thoroughly studied on unsigned graphs, but never on signed graphs.
-In recent independent related work \cite{chehreghani2020hierarchical}, the authors prove that applying these three linkage methods to a signed graph is equivalent to applying them to the unsigned graph obtained by shifting all edge weights by a constant.
-Here, we prove which of the algorithms studied here is ``intrinsically signed'' and do not have this invariance-property:
+\paragraph{Average, Single, and Complete Linkage} -- These three linkage criteria have been thoroughly studied on unsigned graphs, but never - until very recently - on signed graphs.
+In concurrent independent related work \cite{chehreghani2020hierarchical}, the authors prove that applying these three linkage methods to a signed graph is equivalent to applying them to the unsigned graph obtained by shifting all edge weights by a constant.
+Here, we prove which of the algorithms studied here are ``intrinsically signed'' and do not have this invariance-property:
 \begin{restatable}{prop}{invariantAlgs}
@@
 \end{restatable}
-Now that we have extended the family of HC algorithms \cite{johnson1967hierarchical,milligan1979ultrametric} with ``weight-based ultrametrics'' to signed graphs, we move on to their empirical evaluation.
+\noindent In summary, in this section we have extended the family of HC algorithms \cite{johnson1967hierarchical,milligan1979ultrametric} with ``weight-based ultrametrics'' to signed graphs.
+Next, we move to their empirical evaluation.
 

### 2021-03-17 chapters/6_conclusions.tex
Add comments from Anna

@@
 \section{Conclusion}
-We have presented a unifying framework for agglomerative clustering of graphs with both positive and negative edge weights; and we have shown that some existing clustering algorithms, e.g.
-the Mutex Watershed, can be reformulated as special cases of this framework.
-We have analyzed several theoretical and empirical properties of the algorithms included in this framework.
+We have presented a unifying framework for agglomerative clustering of graphs with both positive and negative edge weights.
+This framework allowed us to explore new combinations of constraints and linkage criteria and to perform a consistent evaluation of all algorithms in it.
+% and we have shown that some existing clustering algorithms, e.g. the Mutex Watershed, can be reformulated as special cases of this framework. 
+We have then analyzed several theoretical and empirical properties of these algorithms.
 On instance segmentation, algorithms based on an average linkage criterion outperformed all the others: they proved to be simple and robust approaches to process short- and long-range predictions of a CNN.

### 2022-05-19 chapters/0_abstract.tex
Integrate last Fred's comments
Camera ready changes

@@
 \begin{abstract}
-We propose a simple theoretical framework that generalizes simple and fast algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes.
-This framework defines GASP, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints.
+We propose a theoretical framework that generalizes simple and fast algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes.
+This framework defines GASP, a Generalized Algorithm for Signed graph Partitioning\footnote{Code available at: \url{https://github.com/abailoni/GASP}}, and allows us to explore many combinations of different linkage criteria and cannot-link constraints.
 We prove the equivalence of existing clustering methods to some of those combinations and introduce new algorithms for combinations that have not been studied before. 
-We study both theoretical and empirical properties of these combinations and prove which of these define an ultrametric on the graph.
+We study both theoretical and empirical properties of these combinations and prove that some of these define an ultrametric on the graph.
 We conduct a systematic comparison of various instantiations of GASP on a large variety of both synthetic and existing signed clustering problems, in terms of accuracy but also efficiency and robustness to noise.
-Lastly, we find that some of the algorithms included in our framework, when combined with the predictions from a CNN model, result in a simple bottom-up instance segmentation pipeline.
+Lastly, we show that some of the algorithms included in our framework, when combined with the predictions from a CNN model, result in a simple bottom-up instance segmentation pipeline.
 Going all the way from pixels to final segments with a simple procedure, we achieve state-of-the-art accuracy on the CREMI 2016 EM segmentation benchmark without requiring domain-specific superpixels.

### 2022-05-19 chapters/3_algorithm.tex
Camera ready changes

@@
 % We call two clusters $S,S'$ \emph{adjacent} if there exists at least one edge ${e_{ts}\in E}$ connecting a node $t\in S_u$ to a node $s\in S_v$. 
-Let the interaction $\interact(S,S')\in\mathbb{R}$ between two clusters $S,S'$ be defined as a function, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S$ and $S'$, i.e.
-${(S \times S') \cap E}$ where $\times$ denotes the outer product.
+Let the interaction $\interact(S \cup S')\in\mathbb{R}$ between two clusters $S,S'$ be defined as a function, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S$ and $S'$.
+% , i.e. ${(S \times S') \cap E}$ where $\times$ denotes the outer product. 
 The linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
@@
 Given an agglomerative algorithm with merging tree $T$, let $h_T:V \times V \rightarrow \mathbb{N}$ denote the \emph{dendrogram-height} of each $(u\vee v)\in T$, which is defined as the iteration number at which nodes $u,v\in V$ were merged by the algorithm (see example in Fig.~\ref{fig:intro_figure}a).
-We also define $\treeHeight(u,v)$ as the signed interaction $\interact{}(S,S')$ between the two clusters $S,S'$ that were merged at iteration $h_T(u, v)$:
+We also define $\treeHeight(u,v)$ as the signed interaction $\interact{}(S \cup S')$ between the two clusters $S,S'$ that were merged at iteration $h_T(u, v)$:
 % Then, given a binary tree $T$ and a linkage criterion $\interact$, we can associate a \emph{signed similarity} function $\treeHeight$ to each pair of distinct original nodes $u\neq v$, with $u, v \in V$:
 \begin{equation}\label{eq:def_dendr_interact}
-\treeHeight(u,v) \equiv \interact{} \big( \text{\texttt{leaves}}(T_{\mathrm{R}}[u \vee v]), \text{\texttt{leaves}}(T_{\mathrm{L}}[u \vee v]) \big)
+\treeHeight(u,v) \equiv \interact{} \big( \text{\texttt{leaves}}(T_{\mathrm{R}}[u \vee v])  \cup  \text{\texttt{leaves}}(T_{\mathrm{L}}[u \vee v]) \big)
 \end{equation}
@@
 
-In phase one, \algname{} selects the pair of clusters with the highest absolute interaction $|\interact(S, S')|$, so that the most attractive and the most repulsive pairs are analyzed first.
+In phase one, \algname{} selects the pair of clusters with the highest absolute interaction $|\interact(S  \cup  S')|$, so that the most attractive and the most repulsive pairs are analyzed first.
 If the interaction is repulsive and the algorithm option \emph{addCannotLinkConstraints} is \texttt{True}, then the two clusters are constrained so that their members can never merge in subsequent steps of phase one.
 If the interaction is attractive, then the clusters are merged, provided that they were not previously constrained.
-After each merge, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S, S')$ listed in Table \ref{tab:linkage-criteria}.
+After each merge, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S \cup  S')$ listed in Table \ref{tab:linkage-criteria}.
 Phase one terminates when all the remaining clusters are either constrained or share repulsive interactions.
@@
       \Repeat 
-        \State Pop $S,S'\in\Pi$ with highest interaction $|\interact{}(S,S')|$ from PQ
-        \If{\big[{\color{green}\textbf{$\interact{}(S,S') > 0$}}\big] \textbf{and} \big[$S,S'$ \textbf{not} constrained\big]}
+        \State Pop $S,S'\in\Pi$ with highest interaction $|\interact{}(S  \cup  S')|$ from PQ
+        \If{\big[{\color{green}\textbf{$\interact{}(S \cup S') > 0$}}\big] \textbf{and} \big[$S,S'$ \textbf{not} constrained\big]}
           \State Merge clusters $S$, $S'$ and update hierarchical tree $T^*$
           \State Update interactions \& constraints with neighboring clusters
-        \ElsIf{{\color{blue}addCannotLinkConstr} \textbf{and}  \big[{\color{red}\textbf{$\interact{}(S,S') \leq 0$}}\big]}
+        \ElsIf{{\color{blue}addCannotLinkConstr} \textbf{and}  \big[{\color{red}\textbf{$\interact{}(S \cup  S') \leq 0$}}\big]}
           \State Add CannotLink Constraint between $S$ and $S'$
@@
       \State \emph{// Phase 2: Remove constraints \& merge all positive interactions}
-      \State Push signed interactions $\interact{}(S,S')$ to PQ, $\forall S, S' \in \Pi$
+      \State Push signed interactions $\interact{}(S \cup S')$ to PQ, $\forall S, S' \in \Pi$
       \Repeat 
-        \State Pop $S,S'\in\Pi$ with highest interaction $\interact{}(S,S')$ from PQ
-        \If{\big[{\color{green}\textbf{$\interact{}(S,S') > 0$}}\big]}
+        \State Pop $S,S'\in\Pi$ with highest interaction $\interact{}(S \cup S')$ from PQ
+        \If{\big[{\color{green}\textbf{$\interact{}(S \cup S') > 0$}}\big]}
           \State Merge clusters $S$, $S'$ and update hierarchical tree $T^*$
@@
         \EndIf
-      \Until{\big[{\color{red}\textbf{$\interact{}(S,S') \leq 0$}}\big]} 
+      \Until{\big[{\color{red}\textbf{$\interact{}(S \cup S') \leq 0$}}\big]} 
       \State Save the final clustering $\Pi^* \gets \Pi$ 
@@
       \Repeat
-        \State Pop $S,S'\in\Pi$ with highest interaction $\interact{}(S,S')$ from PQ 
+        \State Pop $S,S'\in\Pi$ with highest interaction $\interact{}(S \cup S')$ from PQ 
         \State Merge clusters $S$, $S'$ and update hierarchical tree $T^*$
@@
 % , we prove that with Complete linkage the agglomeration order does not change whether constraints are introduced or not.
+% \TODO{} in terms of scores, the advantage of one linkage over the other seems to be application dependent, but the median linkage has higher runtime.
+
+% Minor objection: in section 3.1, the input graph is undirected, i.e., E \subseteq {V\choose 2}.
+Therefore, (S\times S')\cap E should be {{S\cup S'}\choose 2} \cap E.
+Note, this are edges of the subgraph induced by nodes S\cup S'.
+In fact, writing W(S,S') is confusing because W depends only on S\cup S', so I'd rather write W(S\cup S').
 
@@
 
-\paragraph{Algorithms defining an ultrametric} -- The connection between agglomerative algorithms and ultrametrics\footnote{A metric space $(X,d)$ is an \emph{ultrametric} if, for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.} is well known.
+\paragraph{Algorithms defining an ultrametric} -- 
+GASP cannot be seen as a local search algorithm of the multicut optimization problem \ref{eq:MC_objective} (see more details in Appendix \ref{sec:relation_to_multicut}).
+However, the connection between agglomerative algorithms and ultrametrics\footnote{A metric space $(X,d)$ is an \emph{ultrametric} if, for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.} is well known.
 Usually, ultrametrics are associated to strictly positive \emph{similarity} or \emph{dissimilarity} measures on a graph.

### 2022-05-19 chapters/5_experiments_intro.tex
Update to CVPR2022 style
Camera ready changes

@@
 The size of the graphs ranges from a few hundred to hundreds of millions of edges.
+In this way, we will highlight the strengths and limitations of the different linkage criteria introduced in the last section.
 
@@
 Measures shown are: Adapted-Rand error (ARAND, lower is better); Variation of Information (VOI) \cite{arganda2015crowdsourcing} (VOI-merge for under-clustering error and VOI-split for over-clustering error, lower values are better).
-\textbf{Table (c)}: Current leading entries in the CREMI challenge leaderboard (March 2021).
+\textbf{Table (c)}: Current leading entries in the CREMI challenge leaderboard (November 2021).
 CREMI-score is given by the geometric mean of (VOI-split + VOI-merge)  and ARAND error (lower is better).}
@@
 Given the simple properties of SSBM graphs, we can now give a detailed explanation of these empirical results.
-In SSBM graphs, the number of edges $E_{ij}\equiv(S_i\times S_j)\cap E$ connecting two clusters $S_i,S_j$ is  proportional to the product $|S_i|\cdot|S_j|$ of cluster sizes. 
+In SSBM graphs, the number of edges $E_{ij}$
+% \equiv(S_i\times S_j)\cap E$ 
+connecting two clusters $S_i,S_j$ is  proportional to the product $|S_i|\cdot|S_j|$ of cluster sizes. 
 With Sum or Avg linkage methods, due to the law of large numbers, the flipping noise is ``averaged out'' as soon as the set $E_{ij}$ becomes larger and clusters grow in size.
@@
 \centering
-\includegraphics[width=0.48\textwidth,trim=0 10 60 0, clip]{./figs/comparison_GAEC_MWS_Avg.png} % left bottom right top
+\includegraphics[width=0.48\textwidth,trim=0 10 60 0, clip]{./figs/comparison_GAEC_MWS_Avg.pdf} % left bottom right top
 \caption{Failure cases of three versions of \algname{} applied to neuron segmentation.

### 2022-05-19 chapters/supplementary.tex
Update to CVPR2022 style
Camera ready changes

@@
 
+% Our code is available anonymously here: \url{https://anonymous.4open.science/r/GASP-4EDF}.
+
 \subsection{Implementation and complexity of \algname{}} \label{sec:detailed_impl}
@@
 Edges in $\tilde{E}$ represent adjacency-relationships between clusters
-and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$, where $S_u$ denotes the clustering including node $u$. 
+and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u \cup S_v}$, where $S_u$ denotes the clustering including node $u$. 
 For the linkage criteria tested in this article, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$.
@@
 \begin{align}
-  \interact(S_u \cup S_v,S_t) =& f\Big[ \interact(S_u,S_t), \interact(S_v,S_t) \Big] \\
+  \interact(S_u \cup S_v  \cup S_t) =& f\Big[ \interact(S_u  \cup  S_t), \interact(S_v  \cup  S_t) \Big] \\
   =& f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) 
@@
 
+\begin{figure}
+% \vspace{-0.3cm}
+\includegraphics[width=\linewidth]{figs/runtime-MWS.pdf}\\
+% \vspace{-0.6cm}
+\caption{Runtimes for different implementation of GASP with AbsMax linkage criterion. Runtimes are averaged over 5 runs.}
+  \label{fig:runtimes_plot}
+\end{figure}
+
+\paragraph*{Efficiency of different GASP implementations with AbsMax linkage criteria} 
+In Fig.~\ref{fig:runtimes_plot}, we compare the runtimes of three implementations of the AbsMax criteria: the implementation from \cite{wolf2019mutex} for pixel graphs (\emph{Pixel-grid implementation}) and for general graphs (\emph{Efficient graph implementation}) as well as the HC implementation with AbsMax linkage (\emph{Naive graph implementation}).
+The specialized implementations can exploit the properties of the underlying graph and are faster.
+But our generalization does not carry a large computational penalty and only requires a few extra seconds for partitioning graphs of a million nodes.
+Note that we have always used the most efficient implementation for the results reported in the paper.
+We will clarify this fact.
+
+\paragraph{Median linkage} We implemented median linkage in our library from the beginning but did not report on it in the main paper for two reasons: we consider the other criteria to span the range of interesting behavior well; and it performs no better than some of the other criteria (like average linkage) which are faster to evaluate.
+% Table~\ref{table:median_scores} compares average and median linkage on two clustering problems: 
+% in terms of scores, the advantage of one linkage over the other seems to be application dependent, but the median linkage has higher runtime.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{figs/counterexample_cropped.png}\\
+\caption{GASP agglomeration with the Abs Max criterion: contracted edges are marked green. The last contraction increases the MC objective from -1 to 0.}\label{counterexample}
+\end{figure}
+
+\subsection{GASP relation to the multicut objective} \label{sec:relation_to_multicut}
+For some of the linkage criteria, e.g.
+sum and average, GASP can be understood as a local search to the objective of the multicut optimization problem \ref{eq:MC_objective}, see \cite{levinkov2017comparative}.
+But this does not hold in general: the Abs Max linkage for example does not always decrease the MC objective (see counter example in Fig.~\ref{counterexample}).
+Moreover, GASP cannot be seen as a k-approximation, because it is a polynomial algorithm and \cite{chawla2006hardness} has shown that approximating the multicut objective with any constant factor is in itself NP-hard.
+
 \subsection{Proofs of Propositions \ref{prop:absmax_mutex}, \ref{prop:weight_shift_invariant}, \ref{prop:ultraMetric1}, and \ref{prop:ultraMetric2}}
@@
 During the agglomeration the interaction between two clusters can only increase in absolute value.
-Thus, the negative interaction $\interact{}(S_i,S_j)<0$ between two constrained clusters can possibly become positive over the course of next agglomeration steps only if there is at least another pair of clusters in the graph that has a positive interaction $\interact{}(S_l,S_t)>0$ higher in absolute value: $|\interact{}(S_l,S_t)| > |\interact{}(S_i,S_j)|$.
+Thus, the negative interaction $\interact{}(S_i \cup S_j)<0$ between two constrained clusters can possibly become positive over the course of next agglomeration steps only if there is at least another pair of clusters in the graph that has a positive interaction $\interact{}(S_l \cup S_t)>0$ higher in absolute value: $|\interact{}(S_l \cup S_t)| > |\interact{}(S_i \cup S_j)|$.
 If such clusters $S_l, S_t$ with positive interaction exist, we note that they must also be constrained (in the opposite case, the algorithm would have already merged them before to constrain $S_i$ and $S_j$, because their priority is higher).
@@
 
-The constrained versions of \algname{} (HCC-Avg and HCC-Single) are also not weight-shift invariant: here, the algorithm merges or constrains clusters in a given order, depending on the absolute interactions $|\interact{}(S_i, S_j)|$ between clusters; so, when edge weights are shifted by a constant $\alpha$, the sorting by absolute value can change arbitrarily together with the agglomeration order, as we show in the counter-example of Fig.~\ref{fig:counter_examples_shift_inv}.
+The constrained versions of \algname{} (HCC-Avg and HCC-Single) are also not weight-shift invariant: here, the algorithm merges or constrains clusters in a given order, depending on the absolute interactions $|\interact{}(S_i \cup  S_j)|$ between clusters; so, when edge weights are shifted by a constant $\alpha$, the sorting by absolute value can change arbitrarily together with the agglomeration order, as we show in the counter-example of Fig.~\ref{fig:counter_examples_shift_inv}.
 Similarly, the Mutex Watershed algorithm is not weight-shift invariant because it uses a linkage criterion that compares weights by their absolute values (see again counter-example in Fig.~\ref{fig:counter_examples_shift_inv}.
@@
 & \forall S_i \in \Pi \setminus \{S_1, S_2\}, \nonumber \\
-\interact{}(S_1 \cup S_2, S_i) &\leq \max \{ \interact{}(S_1, S_i), \interact{}(S_2, S_i)\} 
+\interact{}(S_1 \cup S_2 \cup  S_i) &\leq \max \{ \interact{}(S_1  \cup  S_i), \interact{}(S_2  \cup  S_i)\} 
 \end{align}
@@
 Let us consider a generic iteration of the algorithm, where two clusters $S_\alpha$ and $S_\beta$ have the highest priority and are popped from priority queue.
-Then, the MWS algorithm will either merge or constrain them depending on the fact that their interaction $\interact_{\mathrm{AbsMax}}(S_\alpha,S_\beta)$ is  positive or negative (note that, with AbsMax linkage, an interaction can never be positive and constrained, as shown in Lemma \ref{lemma:absMax_and_complete_property}).
+Then, the MWS algorithm will either merge or constrain them depending on the fact that their interaction $\interact_{\mathrm{AbsMax}}(S_\alpha  \cup S_\beta)$ is  positive or negative (note that, with AbsMax linkage, an interaction can never be positive and constrained, as shown in Lemma \ref{lemma:absMax_and_complete_property}).
 By construction of the SSBM, every edge $e\in E$ in the graph has a absolute weight distributed as $|w_e|\sim \mathcal{N}(1,\sigma^2)$.
-Thus, every edge $e'\in(S_{\alpha} \times S_{\beta})\cap E$ connecting the two clusters has the same probability to have the highest absolute weight, and the sign of the interaction $\interact_{\mathrm{AbsMax}}(S_\alpha,S_\beta)$ will only depend on the sign of this highest edge.
+Thus, every edge $e'\in(S_{\alpha} \times S_{\beta})\cap E$ connecting the two clusters has the same probability to have the highest absolute weight, and the sign of the interaction $\interact_{\mathrm{AbsMax}}(S_\alpha  \cup  S_\beta)$ will only depend on the sign of this highest edge.
 Therefore, the probability that the MWS merges two clusters is simply given by the fraction of positive weighted edges connecting them.
@@
 \begin{align}\label{eq:mws_prob}
- \mathbb{P}[\interact_{\mathrm{AbsMax}}&(S_\alpha,S_\beta)>0;\nBE^+,\nBE^-] = \nonumber \\
+ \mathbb{P}[\interact_{\mathrm{AbsMax}}&(S_\alpha  \cup  S_\beta)>0;\nBE^+,\nBE^-] = \nonumber \\
 =&\sum_{\nBE^+_{\mathrm{nf}}=0}^{\nBE^+}\sum_{\nBE^-_{\mathrm{f}}=0}^{\nBE^-} 
